### 2023-06-09 paperCharts.Rmd
initial commit

---
title: "2040 greenhouse gas reduction targets"
output:
  html_document:
    theme: paper
    toc: true
    toc_float:
      collapsed: false
---

<style>
  .main-container {
    max-width: 95% !important;
  }
  .toc-content {
    padding-left: 0px !important;
  }
  .svg-container {
    margin: auto !important;
  }
</style>

Description:
Charts created for the paper:

Rodrigues, R., Pietzcker, R., Luderer, G., Sitarz, J., Merfort, A., Hasse, R., Hoppe, J., Pehl, M., Ershad, A. M., Baumstark, L. 2040 greenhouse gas reduction targets and energy transitions in line with the EU Green Deal. in preparation (2023).

<!-- Options -->
```{r options, echo=FALSE}

forceUpdateData = FALSE

mainScen <- "Nzero_55_bio7p5" # "Nzero_55_ff55Eff_bio7p5" #Nzero_55_ff55Eff_bio12" # #Nzero_55_bio12" #"Nzero_55_ff55Eff_bio12"

tgt2030Scen <- c(55,57,59)

```

<!-- Loading required packages -->
```{r Loading_required_packages, echo=FALSE}

# install.packages("remotes")
#remotes::install_github("coolbutuseless/ggpattern")

  packagesList <- c("quitte","dplyr","ggplot2","geomtextpath","tidyr","grid","stringr","gridExtra","ggrepel","kableExtra")
  packages <- suppressWarnings(suppressMessages(lapply(packagesList, function(x){ if(!require(x, character.only = T, quietly = T)){ install.packages(x); return(paste0("installed missing package: ", x)) } else paste0("required package is installed: ", x) } )))
```

<!-- Setting default chunk options -->
```{r chunkOptions, echo=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
# setting global R chunk options (https://yihui.name/knitr/options/#chunk_options)
  knitr::opts_chunk$set(dev='svglite', # svg, png,...
                        fig.ext = ".svg",
                        #fig.asp = .8 # default aspect ratio
                        fig.width = 12,
                        fig.height = 6,
                        dpi=100
                        )
```

<!-- Aesthetics -->
```{r loading_aesthetics, echo=FALSE, include=FALSE}

#loading theme and colors
source("./R/aesthetics.R")

```

<!-- load data -->
```{r loading_data, echo=FALSE, include=FALSE}

#loading data
source("./R/loadData.R")

```

<!-- loading reference emissions -->
```{r loading_referenceEmissions, echo=FALSE}

#loading reference emissions
source("./R/loadReferenceEmissions.R")

```

<!-- harmonizing data -->
```{r harmonizingData, echo=FALSE}

#harmonizing data (scale emissions)
source("./R/harmonizeData.R")

```

<!-- efficiency target -->
```{r loading_efficiencyTarget, echo=FALSE}

#loading reference emissions
source("./R/efficiencyTarget.R")

```

---

# Data {.tabset}

<!-- Outputs -->

## Reference emissions

```{r, echo=FALSE}

selectedTgt %>%
  replace(is.na(.),"") %>% 
  select(target,region,period,tgt55,tgt57,tgt59,tgt61,tgt63,tgt65) %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

---

## Efficiency targets

```{r, echo=FALSE}

effTgt %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

---

## 2040 Emission Reductions

```{r, echo=FALSE}

reductions2040 <- rbind(
  remindEmi %>% 
  filter(variable == "Emissions with LULUCF and with international transport", region == "EU27", period == 2040, tgt2050 != "Npi") %>% 
  mutate(value = 1-(value / tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)))
  ,
  remindEmi %>% 
  filter(variable == "Emissions without LULUCF and with international transport", region == "EU27", period == 2040, tgt2050 != "Npi") %>% 
  mutate(value = 1-(value / tgt %>% filter(target == "Emissions without LULUCF and with international transport") %>% pull(reference)))
  ,
  remindEmi %>% 
  filter(variable == "Emissions with LULUCF and with intra-EU aviation", region == "EU27", period == 2040, tgt2050 != "Npi") %>% 
  mutate(value = 1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)))
  ,
  remindEmi %>% 
  filter(variable == "Emissions without LULUCF and with intra-EU aviation", region == "EU27", period == 2040, tgt2050 != "Npi") %>% 
  mutate(value = 1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)))
)

reductions2040 %>% 
  filter(tgt2030 %in% tgt2030Scen) %>% 
  group_by(variable) %>%
  summarize(minTarget = min(value), maxTarget=max(value),.groups = "keep") %>%
  mutate(minTarget = paste0(round(minTarget*100), "%"),
         maxTarget = paste0(round(maxTarget*100), "%"),
         period = 2040) %>% 
  rename(TargetReference = variable) %>%
  relocate(period, .after=TargetReference) %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

---

## Results

```{r, echo=FALSE}

coal_in_generation <- left_join(
  df %>%
  filter(region == "EU27", period == 2040, variable %in% c("SE|Electricity|Coal")) %>%  
  select(scenario,tgt2030,value)
  ,
  df %>% 
  filter(region == "EU27", period == 2040, variable %in% c("SE|Electricity")) %>%
  mutate(total = value) %>%  
  select(scenario,tgt2030,total)
  , by = join_by(scenario == scenario, tgt2030 == tgt2030)
  ) %>%
  mutate(percentage = value/total)

gas_in_generation <- left_join(
  df %>%
  filter(region == "EU27", period == 2040, variable %in% c("SE|Electricity|Gas|w/o CC","SE|Electricity|Gas|w/ CC")) %>%
  group_by(scenario,tgt2030) %>%
  summarize(value = sum(value),.groups = "keep")
  ,
  df %>% 
  filter(region == "EU27", period == 2040, variable %in% c("SE|Electricity")) %>%
  mutate(total = value) %>%  
  select(scenario,tgt2030,total)
  , by = join_by(scenario == scenario, tgt2030 == tgt2030)
  ) %>%
  mutate(percentage = value/total)

wind_and_Solar_gen <- left_join(
  df %>%
  filter(region == "EU27", period == 2040, variable %in% c("SE|Electricity|Wind|Offshore", "SE|Electricity|Wind|Onshore", "SE|Electricity|Solar|PV", "SE|Electricity|Solar|CSP")) %>%
  group_by(scenario,tgt2030) %>%
  summarize(value = sum(value),.groups = "keep")
  ,
  df %>% 
  filter(region == "EU27", period == 2040, variable %in% c("SE|Electricity")) %>%
  mutate(total = value) %>%  
  select(scenario,tgt2030,total)
  , by = join_by(scenario == scenario, tgt2030 == tgt2030)
  ) %>%
  mutate(percentage = value/total)

wind_and_Solar_cap <- df %>%
  filter(region == "EU27", period == 2040, variable %in% c("Cap|Electricity|Wind|Offshore", "Cap|Electricity|Wind|Onshore", "Cap|Electricity|Solar|PV", "Cap|Electricity|Solar|CSP")) %>%
  group_by(scenario,tgt2030) %>%
  summarize(value = sum(value),.groups = "keep")

Generation <- data.frame(
  Electricity_Generation=c("coal_in_generation_(%)","gas_in_generation_(%)","wind_and_Solar_gen_(%)","wind_and_Solar_cap_(TW)"),
  reference_value=c(
    round(coal_in_generation %>% filter(scenario == mainScen) %>% pull(percentage)*100,1),
    round(gas_in_generation %>% filter(scenario == mainScen) %>% pull(percentage)*100,1),
    round(wind_and_Solar_gen %>% filter(scenario == mainScen) %>% pull(percentage)*100,1),
    round(wind_and_Solar_cap %>% filter(scenario == mainScen) %>% pull(value)/ 1000,1)

    ),
  min = c(
   round(min(coal_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(min(gas_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(min(wind_and_Solar_gen %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(min(wind_and_Solar_cap %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(value)/ 1000),1)
   ),
  max = c(
   round(max(coal_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(max(gas_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(max(wind_and_Solar_gen %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(max(wind_and_Solar_cap %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(value)/ 1000),1)
   )
)

pe <- df %>% 
  filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable %in% c("PE|Biomass","PE|Coal","PE|Gas","PE|Oil"))

primaryEnergy <- data.frame(
  Primary_Energy=c("Biomass","Coal","Gas","Oil"),
  relative_to_2020=c(
    round((pe %>% filter(period == 2040, scenario == mainScen, variable == "PE|Biomass") %>% mutate(value = value / (pe %>% filter(period == 2020, scenario == mainScen, variable == "PE|Biomass") %>% pull(value)))%>% pull(value))*100, 1),
    round((pe %>% filter(period == 2040, scenario == mainScen, variable == "PE|Coal") %>% mutate(value = value / (pe %>% filter(period == 2020, scenario == mainScen, variable == "PE|Coal") %>% pull(value)))%>% pull(value))*100, 1),
    round((pe %>% filter(period == 2040, scenario == mainScen, variable == "PE|Gas") %>% mutate(value = value / (pe %>% filter(period == 2020, scenario == mainScen, variable == "PE|Gas") %>% pull(value)))%>% pull(value))*100, 1),
    round((pe %>% filter(period == 2040, scenario == mainScen, variable == "PE|Oil") %>% mutate(value = value / (pe %>% filter(period == 2020, scenario == mainScen, variable == "PE|Oil") %>% pull(value)))%>% pull(value))*100, 1))
)

fe_transport_electricity <- left_join(
  df %>%
  filter(region == "EU27", period == 2040, variable %in% c("FE|Transport|Electricity")) %>%  
  select(scenario,tgt2030,value)
  ,
  df %>% 
  filter(region == "EU27", period == 2030, variable %in% c("FE|Transport|Electricity")) %>%
  mutate(base = value) %>%  
  select(scenario,tgt2030,base)
  , by = join_by(scenario == scenario, tgt2030 == tgt2030)
  ) %>%
  mutate(percentage = value/base)

FE <- data.frame(
  FE=c("transport_electricity_(%)"),
  reference_value=c(round(fe_transport_electricity %>% filter(scenario == mainScen) %>% pull(percentage)*100,1)),
  min = c(round(min(fe_transport_electricity %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1)),
  max = c(round(max(fe_transport_electricity %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1))
)

Bunkers <- list(
  "Aviation" = c(
      "FE|Transport|Pass|Aviation|International|Electricity" = "Electricity",
      "FE|Transport|Pass|Aviation|International|Gases" = "Gases",
      "FE|Transport|Pass|Aviation|International|Hydrogen" = "Hydrogen",
#     "FE|Transport|Pass|Aviation|International|Liquids" = "Liquids"
      "FE|Transport|Pass|Aviation|International|Liquids|Fossil" = "Liquids - Fossil",
      "FE|Transport|Pass|Aviation|International|Liquids|Biomass" = "Liquids - Biomass",
      "FE|Transport|Pass|Aviation|International|Liquids|Hydrogen" = "Liquids - Synthetic"
    ),
    "Shipping" = c(
      "FE|Transport|Freight|Navigation|Electricity" = "Electricity",
      "FE|Transport|Freight|Navigation|Gases" = "Gases",
      "FE|Transport|Freight|Navigation|Hydrogen" = "Hydrogen",
#     "FE|Transport|Freight|Navigation|Liquids" = "Liquids",
      "FE|Transport|Freight|Navigation|Liquids|Fossil" = "Liquids - Fossil",
      "FE|Transport|Freight|Navigation|Liquids|Biomass" = "Liquids - Biomass",
      "FE|Transport|Freight|Navigation|Liquids|Hydrogen" = "Liquids - Synthetic",
      "FE|Transport|Freight|International Shipping|Electricity" = "Electricity",
      "FE|Transport|Freight|International Shipping|Gases" = "Gases",
      "FE|Transport|Freight|International Shipping|Hydrogen" = "Hydrogen",
#     "FE|Transport|Freight|International Shipping|Liquids" = "Liquids"
      "FE|Transport|Freight|International Shipping|Liquids|Fossil" = "Liquids - Fossil",
      "FE|Transport|Freight|International Shipping|Liquids|Biomass" = "Liquids - Biomass",
      "FE|Transport|Freight|International Shipping|Liquids|Hydrogen" = "Liquids - Synthetic"
    )
)

cleanAviation <- c("FE|Transport|Pass|Aviation|International|Electricity", "FE|Transport|Pass|Aviation|International|Hydrogen", "FE|Transport|Pass|Aviation|International|Liquids|Biomass", "FE|Transport|Pass|Aviation|International|Liquids|Hydrogen")

AviationData <- left_join(
  df %>% 
  filter(region == "EU27", period == 2040, variable %in% cleanAviation) %>%
  group_by(scenario,tgt2030) %>%
  summarize(value = sum(value),.groups = "keep")
  ,
  df %>% 
  filter(region == "EU27", period == 2040, variable %in% c(names(Bunkers$Aviation))) %>%
  group_by(scenario,tgt2030) %>%
  summarize(total = sum(value),.groups = "keep")
  , by = join_by(scenario == scenario, tgt2030 == tgt2030)
) %>%
  mutate(percentage = value/total)

cleanShipping <- c("FE|Transport|Freight|Navigation|Electricity", "FE|Transport|Freight|Navigation|Hydrogen", "FE|Transport|Freight|Navigation|Liquids|Biomass",  "FE|Transport|Freight|Navigation|Liquids|Hydrogen", "FE|Transport|Freight|International Shipping|Electricity", "FE|Transport|Freight|International Shipping|Hydrogen", "FE|Transport|Freight|International Shipping|Liquids|Biomass", "FE|Transport|Freight|International Shipping|Liquids|Hydrogen")

ShippingData <- left_join(
  df %>% 
  filter(region == "EU27", period == 2040, variable %in% cleanShipping) %>%
  group_by(scenario,tgt2030) %>%
  summarize(value = sum(value),.groups = "keep")
  ,
  df %>% 
  filter(region == "EU27", period == 2040, variable %in% c(names(Bunkers$Shipping))) %>%
  group_by(scenario,tgt2030) %>%
  summarize(total = sum(value),.groups = "keep")
  , by = join_by(scenario == scenario, tgt2030 == tgt2030)
) %>%
  mutate(percentage = value/total)

share_of_sustainable_fuel <- data.frame(
  FE=c("share_of_sustainable_fuel_in_aviation_(%)","share_of_sustainable_fuel_in_shipping_(%)"),
  reference_value=c(round(AviationData %>% filter(scenario == mainScen) %>% pull(percentage)*100,1),
                    round(ShippingData %>% filter(scenario == mainScen) %>% pull(percentage)*100,1)),
  min = c(round(min(AviationData %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
          round(min(ShippingData %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1)),
  max = c(round(max(AviationData %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
          round(max(ShippingData %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1))
)

Generation %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

primaryEnergy %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

FE %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

share_of_sustainable_fuel %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

---

<!-- Paper Figures -->
```{r, echo=FALSE}
### Initialize plot objects
g <- NULL

```

# Figure 1. Emission results panel

(a) Total GHG emissions (Mt CO2eq/yr)                    (b) Emission reductions (%)

```{r, echo=FALSE}

# all emission reductions were calculated relative to 1990 emissions with LULUCF and international transport (4814 Mt CO2e), except for 2030 emission reduction calculated relative to 1990 emissions with LULUCF and intra-EU aviation only (4713 Mt CO2e).

plotData <- df %>% 
  filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen) %>% 
  calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T)  %>%
  group_by(model,region,variable,period) %>% 
  filter(tgt2050 != "Npi") %>% 
  mutate(ribbon.max=max(value),
         ribbon.min=min(value))

minValue <- min(plotData$value)

h <- refEmi %>% filter(variable == "Emissions with LULUCF and with international transport", region == "EU27", pollutant == "All greenhouse gases - (CO2 equivalent)") %>% ungroup() %>% select(region,variable,period,value)

emi1990 <- tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)

g[["GHG emi"]] <- ggplot(plotData, aes(x=period,y=value)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
     geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min), alpha = 0.5, fill = "#545454") + 
     geom_segment(data=plotData %>% filter(scenario == mainScen, period == 2040), aes(x=2040, xend=2040, y=0, yend=value), linetype="dashed", color="black") +
     geom_line(data=plotData %>% filter(scenario == mainScen), linewidth=1.5) +
     #geom_line(data=plotData, color= "#545454", linewidth=0.2, alpha=0.2, aes(group=scenario)) +
     geom_line(data=h,linewidth=0.7,linetype="dashed") +
     geom_point(data=plotData %>% filter(scenario == mainScen, period == 2040),size=3,shape=21,fill="white",stroke=1.5) +
     theme_doubleColumn() +
#    ggtitle("GHG Emissions") +
    theme(axis.title.y=element_blank()) +
     expand_limits(y=emi1990) +
#     ylab(expression(paste("Mt ", CO[2],"eq/yr"))) +
     scale_y_continuous(breaks = c(0,1000,2000,3000,4000,5000))

plotData <- rbind(
  df %>% 
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>% 
    mutate(reduction = round(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference) ,2)) %>% 
    select(-variable)
  ,
  df %>% 
    filter(region == "EU27", period %in% c(2035:2050), tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>% 
    mutate(reduction = round(value / tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference) ,2)) %>% 
    select(-variable)
  ) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(x=ifelse(reduction>0,period+1,NA),
         xend=ifelse(reduction>0,period+1,NA),
         y=ifelse(reduction>0,1,NA),
         yend=ifelse(reduction>0,ifelse(reduction<=0,0,reduction),NA),
         bar = ifelse(period==2040,"2040","emi"),
         #label = ifelse(value>0,paste0( "- ", (1-value) * 100, "% (-", (1-intraEURed) * 100 ,"%)"),NA),
         labelY = reduction + (1-reduction)/2,
         labelX=period+1) %>%
  group_by(model,region,period) %>% 
  mutate(max=max(reduction),
         min=min(reduction),
         range=max-min,
         label= paste0(round((1-max) * 100), "% to ", round((1-min) * 100) ,"%"))

g[["target"]] <- ggplot(data=plotData,aes(x=period,y=reduction,fill=bar)) +
  geom_bar(data=plotData %>% filter(scenario == mainScen), stat='identity', show.legend = FALSE, alpha = 0.7, color="black") +
  geom_errorbar(aes(ymin=min, ymax=max), width=1, colour="black", alpha=0.9, linewidth=1.3) +
  geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
  theme_doubleColumn() +
  scale_fill_manual(values = c("emi" = "black", "2040" = "#5a788b")) + 
  guides(y = "none") +
  theme(axis.title.y=element_blank()) +
  geom_segment(data=plotData %>% filter(scenario == mainScen), aes(x=x, y=y, xend=xend, yend=yend), arrow = arrow(length=unit(.5, 'cm')), na.rm=TRUE) +
  geom_text(data=plotData %>% filter(scenario == mainScen), aes(label = label, y=labelY, x=labelX, color=factor(period)), vjust=-1, hjust=0.5, na.rm=TRUE, size = geom.text.single.size, angle = 90) +
  scale_color_manual(values = c("2030" = "black", "2035" = "#777777","2040" = "black", "2045" = "#777777","2050" = "black"), breaks=c("2030", "2035","2040", "2045","2050")) +
  expand_limits(y=minValue/emi1990) +
  annotate("text", x=2052, y=1, label= "1990 emissions", vjust=-1, hjust=1, size = geom.text.single.size) +
  geom_hline(yintercept=1, color = "black", linetype="dashed", linewidth=2, alpha = 0.5) +
  coord_cartesian(clip = 'off') +
  scale_y_continuous(breaks = c(0,1000/emi1990,2000/emi1990,3000/emi1990,4000/emi1990,5000/emi1990)) + 
  theme(legend.position = "none")

g[["GHG Emission reductions"]] <- gridExtra::arrangeGrob(
  g[["GHG emi"]], #+ theme(plot.margin=margin(10,10,30,10)),
  g[["target"]], # + theme(plot.margin=margin(10,10,10,10)),
  layout_matrix = rbind(c(1, 1, 1, 1, 2, 2),
                          c(1, 1, 1, 1, 2, 2))
   )

 ggsave(paste0(outFolder,"/GHG Emission reductions.svg"), g[["GHG Emission reductions"]] , device="svg", width = 12, height = 5, dpi=100, units = "in")
 ggsave(paste0(outFolder,"/GHG Emission reductions.png"), g[["GHG Emission reductions"]] , device="png", width = 12, height = 5, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=12, fig.height=5}

grid.newpage()
grid.draw(g[["GHG Emission reductions"]])

```

(c) Breakdown of residual CO2 emissions from energy and industrial processes (% in relation to 2020)

```{r, echo=FALSE}

vars <- list(
  "Industrial\nProcesses" = "Emi|GHG|Industrial Processes",
  "Industry" = "Emi|GHG|Gross|Energy|Demand|Industry",
  "Buildings" ="Emi|GHG|Energy|Demand|Buildings",
  "Transportation" ="Emi|GHG|Energy|Demand|Transport",
  "Bunkers" = "Emi|CO2|Energy|Demand|Transport|International Bunkers",
#  "CDR" = "Emi|GHG|Gross|Energy|Demand|CDR",
#  "AFOFI" = "Emissions|CO2|Energy|Demand|AFOFI",
#  "Other Sector" ="Emissions|CO2|Energy|Demand|Other Sector",
  "Hydrogen" ="Emi|CO2|Gross|Energy|Supply|Hydrogen",
  "Liquids"="Emi|CO2|Gross|Energy|Supply|Liquids",
  "Gases"="Emi|CO2|Gross|Energy|Supply|Gases",
  "Solids"="Emi|CO2|Gross|Energy|Supply|Solids",
#  "Other"="Emissions|CO2|Energy|Supply|Other",
  "Heat"="Emi|CO2|Gross|Energy|Supply|Heat",
  "Electricity"="Emi|GHG|Gross|Energy|Supply|Electricity"
)

# "Emi|GHG|Agriculture",
#   "Emi|GHG|Land-Use Change",
#   "Emi|GHG|Waste",
#   "Emi|CO2|CDR|BECCS",
#   "Emi|CO2|CDR|Industry CCS|Synthetic Fuels",
#   "Emi|CO2|CDR|DACCS",
#   "Emi|CO2|CDR|EW"

plotColor <- c(
  "Electricity"= "#ffb200",
  "Heat"= "#cc0000",
  "Gases"= "#999959",
  "Liquids"= "#0000cc",
  "Solids"= "#0c0c0c",
  "Other" = "#79a6d2",
  "Hydrogen" = "#5ed5b0",
  "Transportation" = "#a1dd70",
  "Bunkers" = "#ffc0cb",
  "Buildings" = "#5edfff",
  "Other Sector" = "#999959",
  "AFOFI" = "#005900",
  "Industry" = "#5f6769",
  "Industrial\nProcesses" = "#5c5c5c",
  "Other" = "#5b0d8f",
  "Waste" = "#A52A2A",
  "AFOLU" = "#4DAF4A",
  "Agriculture" = "#357933",
  "LULUCF" = "#6ec16b"
)

plotData <- df %>%
  filter(region == "EU27",
         period %in% c(2020,2030,2040),
         tgt2030 %in% tgt2030Scen,
         variable %in% unlist(vars),
         scenario == mainScen)

labels <- setNames(names(vars),vars[names(vars)])

plotData$labels <- labels[as.character(plotData$variable)]

plotData[plotData$value <= 0,]$value <- 0

data <-
  plotData %>%
  mutate(complement = FALSE) %>%
  group_by(variable) %>%
  mutate(pct = paste0(round(value / value[period==2020],2)*100, "%")) %>%
  bind_rows(
    plotData %>%
      mutate(complement = TRUE) %>%
      group_by(variable) %>%
      mutate(value = value[period==2020] - value) %>%
      mutate(labels=NA)
  ) %>%
  mutate(ext_Var = ifelse(complement, paste0(as.character(variable),"_"), as.character(variable))) %>%
  arrange(period,ext_Var) %>%
  arrange(match(variable, c("25pct",vars))) %>%
  group_by(period) %>%
  mutate(ymid = as.numeric(sub("\\D+", "", period)),
         ymax = ymid + 4, ymin = ymid - 4,
         xmin = c(0, head(cumsum(value), -1)),
         xmax = cumsum(value),
         xmid = (xmax + xmin) / 2,
         )

data[data$period!=2020,]$labels <- NA
data[data$period != 2040,]$pct <- NA
data[data$variable == "25pct",]$pct <- NA

max <- data %>%
  filter(variable == tail(vars,1), complement == TRUE) %>% 
  group_by(period)

data$labelsPosY <- data$ymid
data[data$labels %in% c("Solids"),]$labelsPosY <- 2015
data[data$labels %in% c("Bunkers","Industrial Processes","Liquids"),]$labelsPosY <- 2016
data[data$labels %in% c("Hydrogen"),]$labelsPosY <- 2010

data$pctPosY <- data$ymid
#data[data$Variable %in% c("Emi|GHG|Industrial Processes","Emi|CO2|Gross|Energy|Supply|Gases","Emi|GHG|Gross|Energy|Supply|Electricity"),]$pctPosY <- 2047
data[data$variable %in% c("Emi|CO2|Gross|Energy|Supply|Solids","Emi|CO2|Gross|Energy|Supply|Heat","Emi|CO2|Gross|Energy|Supply|Hydrogen"),]$pctPosY <- 2100
data[data$variable %in% c("Emi|CO2|Gross|Energy|Supply|Liquids"),]$pctPosY <- 2043
data$pctPosX <- data$xmid
#data[data$variable %in% c("Emi|GHG|Industrial Processes"),]$pctPosX <- data[data$variable %in% c("Emi|GHG|Industrial Processes"),]$pctPosX - 100
#data[data$variable %in% c("Emi|GHG|Gross|Energy|Demand|Industry"),]$pctPosX <- data[data$variable %in% c("Emi|GHG|Gross|Energy|Demand|Industry"),]$pctPosX + 100

#data$ext_Var <- as.character(data$ext_Var)

#remove labels for small values
data <- data %>% mutate(pct = ifelse(variable %in% vars[c("Hydrogen","Solids","Heat")], NA, pct))

g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] <- data %>%
  ggplot(aes(xmid, ymid, fill = ext_Var)) +
  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax,
                alpha = factor(period), color = variable)) +
  #geom_text(data=max, aes(label = period, y=period, x=xmax), vjust=0.5, hjust=-0.5) + 
  geom_text(aes(y = 2015, label = labels, group = labels, hjust=1, angle = 90), vjust=0.5, hjust=1.1, na.rm=TRUE, size = geom.text.single.size, angle = 90) +
  #geom_label_repel(aes(y = 2014, label = labels, group = labels), vjust=0.5, hjust=1, na.rm=TRUE, size = geom.text.single.size, angle = 90) +
  #geomtextpath::geom_textpath(aes(y = 2014, label = labels, group = labels, vjust=0.5, hjust=1, angle = 90),text_only = TRUE, na.rm=TRUE, size = geom.text.double.size) +
  geom_text(aes(x=pctPosX , y = 2045, label = pct), vjust=0.5, hjust=-0.1, na.rm=TRUE, size = geom.text.single.size, angle = 90) +
  #geomtextpath::geom_textpath(aes(x=pctPosX , y = 2046, label = pct),text_only = TRUE, na.rm=TRUE, size = geom.text.double.size) +
  #geom_text(aes(y = ymid + 3, label = labels, group = labels)) +
  scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars),setNames(rep("transparent",length(vars)),paste0(vars,"_"))), labels = setNames(names(vars), vars)) +
  scale_alpha_manual(values = c(0.2, 0.3, 1)) +
  scale_color_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) +
  #scale_fill_manual(values = c("#cd9900", "#00817e")) +
  #scale_colour_manual(values = c("#cd9900", "#00817e")) +
  #scale_y_continuous(limits = c(1990, 2045)) +
  #scale_y_reverse(limits = c(2065, 2013)) +
  theme_doubleColumn() +
  theme(legend.position = "none") +
  scale_y_continuous(breaks=c(2020,2030,2040), minor_breaks = NULL, limits=c(2008,2047)) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank()) +
  scale_x_continuous(breaks = NULL) +
  coord_cartesian(clip="off") +
  theme(plot.margin = unit(c(1,0,2,0), "cm"))

ggsave(paste0(outFolder,"/2040 Emissions - Energy and Industrial Processes - horizontal bar.svg"), g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] , device="svg", width = 12, height = 3, dpi=100, units = "in")
ggsave(paste0(outFolder,"/2040 Emissions - Energy and Industrial Processes - horizontal bar.png"), g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] , device="png", width = 12, height = 3, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=12, fig.height=3}

  g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]]

```

Figure 1. Emission results panel. Reference scenario: Net-zero by 2050, 55% reduction by 2030, REMIND future final energy projections, biomass availability limited to 7.5 EJ/yr and default CCS assumption.

---

# Figure 2. Electricity panel

:::: {style="display: flex;"}

::: {}

(a) Electricity Generation (%)

```{r, echo=FALSE}

vars <- c(
  "Net Imports" = "SE|Electricity|Net Imports",
  "Coal w/ CC" = "SE|Electricity|Coal|w/ CC",
  "Coal w/o CC" = "SE|Electricity|Coal|w/o CC",
  "Oil" = "SE|Electricity|Oil",
  "Gas w/ CC" = "SE|Electricity|Gas|w/ CC",
  "Gas w/o CC" = "SE|Electricity|Gas|w/o CC",
  "Hydrogen" = "SE|Electricity|Hydrogen",
  "Nuclear" = "SE|Electricity|Nuclear",
  "Geothermal" = "SE|Electricity|Geothermal",
  "Hydro" = "SE|Electricity|Hydro",
  "Biomass w/ CC" = "SE|Electricity|Biomass|w/ CC",
  "Biomass w/o CC" = "SE|Electricity|Biomass|w/o CC",
  "Solar CSP" = "SE|Electricity|Solar|CSP",
  "Solar PV" = "SE|Electricity|Solar|PV",
  "Wind Onshore" = "SE|Electricity|Wind|Onshore",
  "Wind Offshore" = "SE|Electricity|Wind|Offshore")

inv_vars <- setNames(names(vars),vars)

color <- c(
  "Net Imports"   = "#472b62",
  "Coal w/ CC"    = "#b2b2b2",
  "Coal w/o CC"   = "#0c0c0c",
  "Oil"           = "#b30000",
  "Gas w/ CC"     = "#b79e38",
  "Gas w/o CC"    = "#999959",
  "Hydrogen"      = "#5ed5b0",
  "Nuclear"       = "#ff33ff",
  "Geothermal"    = "#e51900",
  "Hydro"         = "#191999",
  "Biomass w/ CC" = "#33ff00",
  "Biomass w/o CC"= "#005900",
  "Solar CSP"     = "#ffcc00",
  "Solar PV"      = "#ffe600",
  "Wind Onshore"  = "#193F7F",
  "Wind Offshore" = "#337fff")

plotData <- df %>% 
  filter(region == "EU27", period >= 2020, period <= 2060, scenario  == mainScen, variable %in% unlist(vars)) %>% 
  mutate(variable = factor(variable, levels=vars)) %>% 
  arrange(factor(variable, levels = rev(vars))) %>%
  group_by(model,scenario,region,period) %>%
  mutate(cumValue = cumsum(value),
         n = sum(value),
         percentage = value / n,
         cumPercentage = cumValue / n)

plotData2040 <- plotData[plotData$period == 2040,]
#plotData$value <- plotData$value / plotData[plotData$period == "2020",]$value
#plotData$period <- as.character(plotData$period)
#plotData$period <- factor(plotData$period , levels = rev(c("2020","2030","2040","2050")))

plotData2040$xPos <- 2042.5
#plotData2040[plotData2040$variable %in% c("SE|Electricity|Hydro"),]$xPos <- 2028.5
#plotData2040[plotData2040$variable %in% c("SE|Electricity|Biomass|w/o CC"),]$xPos <- 2020
plotData2040[plotData2040$variable %in% c("SE|Electricity|Nuclear","SE|Electricity|Biomass|w/o CC"),]$xPos <- 2035

plotDataRenewables <- plotData %>%
  filter(variable %in% c("SE|Electricity|Geothermal","SE|Electricity|Hydro","SE|Electricity|Biomass|w/ CC","SE|Electricity|Biomass|w/o CC","SE|Electricity|Solar|CSP","SE|Electricity|Solar|PV","SE|Electricity|Wind|Onshore","SE|Electricity|Wind|Offshore","SE|Electricity|Nuclear")) %>%
  group_by(model,scenario,region,period) %>%
  summarize(percentage = sum(percentage),.groups = "keep")

g[["Electricity Generation"]] <- 
  ggplot(plotData,aes(x=period,y=percentage)) +
  geom_area(aes(fill=variable),alpha=0.4) +
  geom_line(data=plotDataRenewables, linetype = "dashed", linewidth = 1.5, color="#666666") +
  geom_bar(data=plotData2040,aes(fill=variable),stat='identity', show.legend = FALSE, alpha = 0.7, color="white", width = 3, linewidth = 1.5) +
  #ggrepel::geom_text_repel(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(round(percentage,2)*100,"%"), y=cumPercentage-percentage/2, x = 2043.5), vjust=0.5, hjust=0.5, na.rm=TRUE, color = "black", size = 12) +
  #geom_text(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(inv_vars[variable], " (",round(percentage,2)*100,"%)"), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size = 12) +
  geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geom.text.double.size) +
  theme_doubleColumn()  +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(breaks=c(2020,2040,2060)) +
  scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
  theme(axis.title.y=element_blank()) +
  guides(fill=guide_legend(nrow=8,override.aes = list(alpha=1), byrow = TRUE)) +
  #annotate(geom = "text", x = 2022, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage + 0.06, label = "renewables", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) +
  #annotate(geom = "text", x = 2023, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage - 0.06, label = "and nuclear", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) +
  annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geom.text.double.size) +
  theme(axis.text.y=element_blank()) +
  theme(legend.key.height = unit(0.8, "cm"),
    legend.key.width = unit(0.8,"cm")) +
  theme(legend.spacing.y = unit(0.1, 'cm'))

ggsave(paste0(outFolder,"/Electricity Generation.svg"), g[["Electricity Generation"]] , device="svg", width = 6, height = 10, dpi=100, units = "in")
ggsave(paste0(outFolder,"/Electricity Generation.png"), g[["Electricity Generation"]] , device="png", width = 6, height = 10, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=6, fig.height=10}

g[["Electricity Generation"]]

```

:::

::: {}

(b) Solar Photovoltaics capacity (GW)

```{r, echo=FALSE}

# Solar photovoltaics roll out
plotData <- df %>% 
  filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable == "Cap|Electricity|Solar|PV") %>% 
  filter(tgt2050 != "Npi") %>% 
  group_by(model,region,variable,period) %>% 
  mutate(ribbon.max=max(value),
         ribbon.min=min(value))

target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2025,2030),value=c(320,600))

#value <- data.frame(period=c(2025,2030,2040),value=c(plotData[plotData$period==2025,]$value,plotData[plotData$period==2030,]$value,plotData[plotData$period==2040,]$value))

# historical data
h <- hist %>% filter(model == "IRENA", region == "EU27", variable == "Cap|Electricity|Solar|PV", period >= 2005) %>% drop_na(value)

g[["Solar Photovoltaics capacity"]] <- ggplot(plotData,aes(x=period,y=value)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_segment(aes(x=2040, y=0, xend=2040, yend=plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value)), linetype="dashed", color="black") +
    geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min), alpha = 0.5, fill = "#545454") + 
    geom_line(data=plotData %>% filter(scenario == mainScen),linewidth=1.5) +
    geom_line(data=h,linewidth=1,linetype="dashed") +
    geom_point(data=plotData %>% filter(scenario == mainScen, period %in% c(2030,2040)),size=3,shape=21,fill="white",stroke=1.5) +
    geom_point(data=target, size=3, shape=4, stroke = 1.5) +
    geom_label_repel(data=target, aes(label = paste0(round(value),"GW - ", target)),box.padding = 0.1,
                  #segment.curvature = -0.1,
                  segment.square = TRUE,
                  point.padding = 0.6,
                  nudge_x = 5,
                  #nudge_y = -0.02,
                  #force = 0.5,
                  hjust = 0,
                  direction="y", size = geom.text.double.size*0.9, xlim = c(2020, 2070)) +
  geom_label_repel(data=plotData %>% filter(scenario == mainScen, period == 2030), aes(label = paste0(round(value),"GW")),box.padding = 0.1,
                  point.padding = 1,
                  nudge_x = -2,
                  nudge_y = 500,
                  hjust = 1, direction="y",
                  size = geom.text.double.size) +
  geom_label_repel(data=plotData %>% filter(scenario == mainScen, period == 2040), aes(label = paste0(round(value),"GW")),box.padding = 0.1,
                  point.padding = 1,
                  nudge_x = -2,
                  nudge_y =500,
                  #hjust = 0, 
                  direction="y",
                  size = geom.text.double.size) +
    theme_doubleColumn() + 
    theme(axis.title.y = element_blank())+
    coord_cartesian(clip = 'off')

ggsave(paste0(outFolder,"/Solar Photovoltaics capacity.svg"), g[["Solar Photovoltaics capacity"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
ggsave(paste0(outFolder,"/Solar Photovoltaics capacity.png"), g[["Solar Photovoltaics capacity"]] , device="png", width = 6, height = 4, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=6, fig.height=4}

g[["Solar Photovoltaics capacity"]]

```

(c) Electricity share in final energy (%)

```{r, echo=FALSE}

# Electricity share
vars <- c("Total" = "Final Energy|Electricity Share",
          "Transport"="Final Energy|Transport|Electricity Share",
          "Industry"="Final Energy|Industry|Electricity Share",
          "Buildings"="Final Energy|Buildings|Electricity Share")

plotData <- df %>% 
  filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
  group_by(model,region,variable,period) %>% 
  filter(tgt2050 != "Npi") %>% 
  mutate(ribbon.max=max(value),
         ribbon.min=min(value))

h_Orig <- hist[hist$model == "IEA" & hist$region == "EU27" & hist$variable %in% c("FE","FE|Electricity","FE|Transport","FE|Transport|Electricity","FE|Industry", "FE|Industry|Electricity","FE|Buildings","FE|Buildings|Electricity"),] %>% drop_na(value)

h <- rbind(
  h_Orig %>% calc_addVariable("`Final Energy|Electricity Share`" = "`FE|Electricity` / `FE`", units = "%", only.new=T),
  h_Orig %>% calc_addVariable("`Final Energy|Transport|Electricity Share`" = "`FE|Transport|Electricity` / `FE|Transport`", units = "%", only.new=T),
  h_Orig %>% calc_addVariable("`Final Energy|Industry|Electricity Share`"  = "`FE|Industry|Electricity`  / `FE|Industry`", units = "%", only.new=T),
  h_Orig %>% calc_addVariable("`Final Energy|Buildings|Electricity Share`" = "`FE|Buildings|Electricity` / `FE|Buildings`", units = "%", only.new=T))

g[["Electricity Share"]] <- ggplot(plotData,aes(x=period,y=value)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_segment(aes(x=2040, y=0, xend=2040, yend=max(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value))), linetype="dashed", color="black") +
    geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min, fill=variable), alpha = 0.3) + 
    geom_line(data=plotData %>% filter(scenario == mainScen), linewidth=1.5,aes(color=variable)) +
    #geom_line(data=h,linewidth=1,linetype="dashed") +
    geom_point(data=plotData %>% filter(scenario == mainScen, period == 2040),size=3,shape=21,fill="white",stroke=1.5) +
    geom_line(data=h %>% filter(period >= 2005),linetype="dashed", linewidth = 1, aes(color=variable)) +
    geom_label_repel(data= plotData %>% filter(scenario == mainScen, period == 2040),
                         aes(
                           label = paste0(round(value*100),"%")),
                      box.padding = 3,
                      #segment.curvature = -0.1,
                      segment.square = TRUE,
                      point.padding = 0.6,
                      nudge_x = 5,
                      nudge_y = c(0.55,0.27,-0.05,-0.6),
                      #force = 0.5,
                      #hjust = 0,
                      direction="y"
                      , size = geom.text.double.size*0.9
                      #, xlim = c(2020, 2070)
                      ) +
    scale_colour_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
    scale_fill_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
    theme_doubleColumn() + 
    scale_y_continuous(labels = scales::percent) +
    expand_limits(y=c(0,1)) +
    guides(color=guide_legend(nrow=2)) +
  theme(axis.title.y = element_blank())

ggsave(paste0(outFolder,"/Electricity Share.svg"), g[["Electricity Share"]] , device="svg", width = 6, height = 6, dpi=100, units = "in")
ggsave(paste0(outFolder,"/Electricity Share.png"), g[["Electricity Share"]] , device="png", width = 6, height = 6, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=6, fig.height=6}

g[["Electricity Share"]]

```

:::

::::

---

# Figure 3. Energy supply panel

:::: {style="display: flex;"}

::: {}

(a) Primary energy (EJ/yr)

```{r, echo=FALSE}

# Primary Energy
vars <- c("Biomass" = "PE|Biomass",
          "Coal"="PE|Coal",
          "Gas"="PE|Gas",
          "Oil"="PE|Oil")

plotData <- df %>% 
  filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
  group_by(model,region,variable,period) %>% 
  filter(tgt2050 != "Npi") %>% 
  mutate(ribbon.max=max(value),
         ribbon.min=min(value))

# historical data
h <- hist %>% filter(model == "IEA", region == "EU27", variable %in% vars, period >= 2005, period <= 2020) %>% drop_na(value) %>% filter(value != 0)

g[["Primary Energy"]] <- ggplot(plotData,aes(x=period,y=value)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_segment(aes(x=2040, y=0, xend=2040, yend=max(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value))), linetype="dashed", color="black") +
    geom_line(data=plotData %>% filter(scenario == mainScen), aes(color=variable), linewidth=1.5) +
    geom_line(data=h,aes(color=variable),linewidth=1,linetype="dashed") +
    geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min, fill=variable), alpha = 0.3) + 
    #geom_point(data=plotData[plotData$period %in% c(2020,2030,2040),],size=4,shape=21,fill="white") +
    geom_point(data=plotData %>% filter(scenario == mainScen, period == 2040),aes(color=variable),size=3,shape=21,fill="white",stroke=1.5) +
    #annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geom.text.double.size) +
    scale_color_manual(values = c(setNames(options$aesthetics$legend$color[names(vars)],vars)), labels = setNames(names(vars), vars)) +
    scale_fill_manual(values = c(setNames(options$aesthetics$legend$color[names(vars)],vars)), labels = setNames(names(vars), vars)) +
    theme_doubleColumn() + 
    expand_limits(y=c(0,1)) +
    guides(color=guide_legend(nrow=2)) +
    theme(axis.title.y = element_blank()) #+
    #guides(fill = FALSE)

ggsave(paste0(outFolder,"/Primary Energy.svg"), g[["Primary Energy"]] , device="svg", width = 6, height = 6, dpi=100, units = "in")
ggsave(paste0(outFolder,"/Primary Energy.png"), g[["Primary Energy"]] , device="png", width = 6, height = 6, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=6, fig.height=6}

g[["Primary Energy"]]

```

(c) Natural gas and syngas final energy demand (EJ/yr)

```{r, echo=FALSE}

vars <- c(
  "Hydrogen"="FE|Hydrogen",
  "Gases"="FE|Gases"
)

plotData <- df %>% 
  filter(region == "EU27", period %in% c(2020,2030,2040,2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
  mutate(variable = factor(variable, levels=vars))  %>% 
  filter(tgt2050 != "Npi")  %>%
  group_by(model,scenario,region,period) %>% 
  mutate(cumsum = cumsum(value),
         sum = sum(value)) %>% 
  group_by(model,region,variable,period) %>% 
  mutate(ribbon.max=max(cumsum),
         ribbon.min=min(cumsum)) %>% 
  group_by(model,region,period) %>% 
  mutate(ribbon.max.total=max(sum),
         ribbon.min.total=min(sum))

g[["FE Gases"]] <- 
  ggplot(plotData,aes(x=period,y=value)) +
  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = variable)) +
  #geom_errorbar(data=plotData %>% filter(period != 2020), aes(ymin=ribbon.min, ymax=ribbon.max, group=variable), width=8, colour="black", alpha=0.9, size=1,position = position_dodge(width=2)) +
  geom_errorbar(data=plotData %>% filter(period != 2020, variable == vars[1], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, size=1,position = position_dodge(width=2)) +
  # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
  coord_flip() +
  theme_doubleColumn() +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank()) +
  #guides(y = "none") +
  theme(axis.title.y=element_blank()) +
  #theme(legend.position = "none") #+
  scale_fill_manual(values = setNames(options$aesthetics$legend$color[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(reverse = TRUE, nrow = 1)) +
  theme(legend.text=element_text(size=theme.double.text.size)) +
  theme(legend.key.height = unit(0.7, "cm"),
    legend.key.width = unit(0.7,"cm")) +
  scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == 2020) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2030) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value)),1))) +
  scale_x_reverse()

ggsave(paste0(outFolder,"/FE Gases.svg"), g[["FE Gases"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
ggsave(paste0(outFolder,"/FE Gases.png"), g[["FE Gases"]] , device="png", width = 6, height = 4, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=6, fig.height=4}

g[["FE Gases"]]

```

:::

::: {}

(b) Fossil trade (EJ/yr)

```{r, echo=FALSE}

vars <- list(
 "Coal" = c("Trade|Imports|Coal","Trade|Exports|Coal"),
 "Oil" = c("Trade|Imports|Oil","Trade|Exports|Oil"),
 "Gas" = c("Trade|Imports|Gas","Trade|Exports|Gas"),
 "Biomass" = c("Trade|Imports|Biomass","Trade|Exports|Biomass")
)

# plotData <- plotData %>% 
#   arrange(factor(variable, levels = rev(vars))) %>%
#   group_by(model,scenario,region,period) %>%
#   mutate(cumValue = cumsum(value),
#          n = sum(value),
#          percentage = value / n,
#          cumPercentage = cumValue / n)

plotData <- df %>% 
  filter(region == "EU27", period  %in% c(2020,2030,2040,2050,2060), scenario == mainScen, variable %in% unlist(vars))

carrier <- c()
for(c in names(vars)){
  for(var in vars[[c]]){
    v <- c
    names(v) <- var
    carrier <- c(carrier,v)
  }
}

plotData <- plotData %>%
  mutate(type = ifelse(grepl("Imports",variable),"Imports","Exports"),
         carrier = carrier[as.character(variable)])

plotData[plotData$type == "Exports",]$value <- -plotData[plotData$type == "Exports",]$value

plotData$carrier <- factor(plotData$carrier, levels=c("Coal","Oil","Gas","Biomass"))

plotDataTotal <- plotData %>%
  group_by(model,scenario,region,unit,period,carrier) %>%
  summarize(value=sum(value),.groups = "keep") %>%
  mutate(type="Total")

plotColor <- c(
  "Imports"= "#e56b6f",
  "Exports"= "#355070"
)

g[["security of supply"]] <- ggplot(plotData,aes(x=period,y=value)) +
  geom_bar(aes(fill=type),stat='identity') +
  geom_errorbar(data  = plotDataTotal, aes(y=value, ymax=value, ymin=value, color=type), size=1) +
  facet_wrap(~carrier,nrow=1) +
   theme_doubleColumn() +
   theme(axis.title.y=element_blank()) +
   scale_fill_manual(values = plotColor, guide = guide_legend(nrow = 1)) + #, guide = guide_legend(nrow = 2) setNames(options$aesthetics$legend$color[names(vars)],vars)
  scale_color_manual(values = c("Total"="black")) +
   scale_x_continuous(breaks = c(2020,2030,2040,2050, 2060)) + 
  #theme(
  #  strip.background = element_blank(),
  #  strip.text.x = element_blank()) +
  theme(legend.text=element_text(size=theme.single.text.size)) +
  theme(legend.key.height = unit(0.7, "cm"),
    legend.key.width = unit(0.7,"cm")) + 
  theme(axis.text = element_text(size=theme.single.text.size)) #+                                                              
  #theme(strip.text.x = element_text(size=0.8*theme.single.text.size)) +
  #theme(strip.clip = "off")

 ggsave(paste0(outFolder,"/security of supply.svg"), g[["security of supply"]] , device="svg", width = 6, height = 5, dpi=100, units = "in")
 ggsave(paste0(outFolder,"/security of supply.png"), g[["security of supply"]] , device="png", width = 6, height = 5, dpi=300, units = "in")

g[["security of supply - fossil"]] <- ggplot(plotData %>% filter(period <= 2050, carrier != "Biomass"),aes(x=period,y=value)) +
  geom_bar(aes(fill=type),stat='identity') +
  geom_errorbar(data  = plotDataTotal %>% filter(period <= 2050, carrier != "Biomass"), aes(y=value, ymax=value, ymin=value, color=type), size=1) +
  facet_wrap(~carrier,nrow=1) +
   theme_doubleColumn() +
   theme(axis.title.y=element_blank()) +
   scale_fill_manual(values = plotColor, guide = guide_legend(nrow = 1)) + #, guide = guide_legend(nrow = 2) setNames(options$aesthetics$legend$color[names(vars)],vars)
  scale_color_manual(values = c("Total"="black")) +
   scale_x_continuous(breaks = c(2020,2030,2040,2050, 2060)) + 
  #theme(
  #  strip.background = element_blank(),
  #  strip.text.x = element_blank()) +
  theme(legend.text=element_text(size=theme.single.text.size)) +
  theme(legend.key.height = unit(0.7, "cm"),
    legend.key.width = unit(0.7,"cm")) + 
  theme(axis.text = element_text(size=theme.single.text.size)) #+                                                              
  #theme(strip.text.x = element_text(size=0.8*theme.single.text.size)) +
  #theme(strip.clip = "off")

ggsave(paste0(outFolder,"/security of supply - fossil.svg"), g[["security of supply - fossil"]] , device="svg", width = 6, height = 6, dpi=100, units = "in")
ggsave(paste0(outFolder,"/security of supply - fossil.png"), g[["security of supply - fossil"]] , device="png", width = 6, height = 6, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=6, fig.height=5}

  g[["security of supply"]]

```

(d) Hydrogen production (EJ/yr)

```{r, echo=FALSE}

vars <- c(
  "Biomass w/ CC" = "SE|Hydrogen|Biomass|w/ CC",
  "Biomass w/o CC" = "SE|Hydrogen|Biomass|w/o CC",
  "Coal w/ CC" = "SE|Hydrogen|Coal|w/ CC",
  "Coal w/o CC" = "SE|Hydrogen|Coal|w/o CC",
  "Gas w/ CC" = "SE|Hydrogen|Gas|w/ CC",
  "Gas w/o CC" = "SE|Hydrogen|Gas|w/o CC",
  "Electrolysis" = "SE|Hydrogen|Electricity",
  #"VRE Storage Electrolysis" = "SE|Hydrogen|Electricity|VRE Storage Electrolysis",
  #"Standard Electrolysis" = "SE|Hydrogen|Electricity|Standard Electrolysis",
  "Net Imports" = "SE|Hydrogen|Net Imports")

#1EJ <- 7 million tons #https://hydrogencouncil.com/wp-content/uploads/2017/11/Hydrogen-Scaling-up_Hydrogen-Council_2017.compressed.pdf
#1EJ <- 8 million tons adrian

color <- setNames(options$aesthetics$legend$color[names(vars)],vars)
color["SE|Hydrogen|Biomass|w/ CC"] <- color["SE|Hydrogen|Biomass|w/o CC"]

target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2030,2030),value=c(10,20)) %>%
  mutate(value = value/8)

plotData <- df %>% 
  filter(region == "EU27", period %in% c(2020,2030,2040,2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
  mutate(#value = value*8, #1EJ <- 8 million tons adrian
    variable = factor(variable, levels=vars))  %>% 
  filter(tgt2050 != "Npi")  %>%
  group_by(model,scenario,region,period) %>% 
  mutate(cumsum = cumsum(value),
         sum = sum(value)) %>% 
  group_by(model,region,variable,period) %>% 
  mutate(ribbon.max=max(cumsum),
         ribbon.min=min(cumsum)) %>% 
  group_by(model,region,period) %>% 
  mutate(ribbon.max.total=max(sum),
         ribbon.min.total=min(sum))

g[["Hydrogen"]] <- 
  ggplot(plotData,aes(x=period,y=value)) +
  geom_hline(yintercept= target[1,]$value, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = 2015, y = target[1,]$value, label = "REPowerEU\ndomestic", angle=90, vjust = 0.4, hjust = 1, color = "black", alpha = 0.5, size = 0.3*theme.single.text.size) +
  geom_hline(yintercept= target[2,]$value, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = 2015, y = target[2,]$value, label = "REPowerEU\ntotal", angle=90, vjust = 0.4, hjust = 1, color = "black", alpha = 0.5, size = 0.3*theme.single.text.size) +
  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = variable)) +
  geom_errorbar(data=plotData %>% filter(period != 2020, variable == vars[1], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, size=1,position = position_dodge(width=2)) +
  # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
  coord_flip() +
  theme_doubleColumn() +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank()) +
  #guides(y = "none") +
  theme(axis.title.y=element_blank()) +
  #theme(legend.position = "none") #+
  scale_fill_manual(values = color,
                    labels = setNames(names(vars), vars)[c("SE|Hydrogen|Electricity", "SE|Hydrogen|Gas|w/o CC", "SE|Hydrogen|Biomass|w/ CC")],
                    breaks = c("SE|Hydrogen|Electricity", "SE|Hydrogen|Gas|w/o CC", "SE|Hydrogen|Biomass|w/ CC"), guide = guide_legend(nrow = 1)) +
  theme(legend.text=element_text(size=theme.double.text.size)) +
  theme(legend.key.height = unit(0.7, "cm"),
    legend.key.width = unit(0.7,"cm")) +
  scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == 2030) %>% pull(value))),round(sum(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value))),round(sum(plotData %>% filter(scenario == mainScen, period == 2050) %>% pull(value))))) +
  scale_x_reverse() +
  theme(legend.margin=margin(l = -2, unit='cm'))

ggsave(paste0(outFolder,"/Hydrogen.svg"), g[["Hydrogen"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
ggsave(paste0(outFolder,"/Hydrogen.png"), g[["Hydrogen"]] , device="png", width = 6, height = 4, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=6, fig.height=4}

g[["Hydrogen"]]

```

:::

::::

---

# Figure 4. Demand panel

(a) Transport final energy (EJ/yr)

```{r, echo=FALSE}

FEvars <- list(
  "Domestic" = list(
    "LDV" = c(
      "FE|Transport|Pass|Road|LDV|Electricity" = "Electricity",
      "FE|Transport|Pass|Road|LDV|Gases" = "Gases",
      "FE|Transport|Pass|Road|LDV|Hydrogen" = "Hydrogen",
#      "FE|Transport|Pass|Road|LDV|Liquids" = "Liquids"
       "FE|Transport|Pass|Road|LDV|Liquids|Fossil" = "Liquids - Fossil",
       "FE|Transport|Pass|Road|LDV|Liquids|Biomass" = "Liquids - Biomass",
        "FE|Transport|Pass|Road|LDV|Liquids|Hydrogen" = "Liquids - Synthetic"
    ),
    "Buses" = c(
      "FE|Transport|Pass|Road|Bus|Electricity" = "Electricity",
      "FE|Transport|Pass|Road|Bus|Gases" = "Gases",
      "FE|Transport|Pass|Road|Bus|Hydrogen" = "Hydrogen",
#      "FE|Transport|Pass|Road|Bus|Liquids" = "Liquids"
        "FE|Transport|Pass|Road|Bus|Liquids|Fossil" = "Liquids - Fossil",
        "FE|Transport|Pass|Road|Bus|Liquids|Biomass" = "Liquids - Biomass",
        "FE|Transport|Pass|Road|Bus|Liquids|Hydrogen" = "Liquids - Synthetic"

    ),
    "Trucks" = c(
      "FE|Transport|Freight|Road|Electricity" = "Electricity",
      "FE|Transport|Freight|Road|Gases" = "Gases",
      "FE|Transport|Freight|Road|Hydrogen" = "Hydrogen",
#      "FE|Transport|Freight|Road|Liquids" = "Liquids"
        "FE|Transport|Freight|Road|Liquids|Fossil" = "Liquids - Fossil",
        "FE|Transport|Freight|Road|Liquids|Biomass" = "Liquids - Biomass",
        "FE|Transport|Freight|Road|Liquids|Hydrogen" = "Liquids - Synthetic"
    ),
    "Rail" = c(
      "FE|Transport|Pass|Rail|Electricity" = "Electricity",
      "FE|Transport|Pass|Rail|Gases" = "Gases",
      "FE|Transport|Pass|Rail|Hydrogen" = "Hydrogen",
#      "FE|Transport|Pass|Rail|Liquids" = "Liquids",
        "FE|Transport|Pass|Rail|Liquids|Fossil" = "Liquids - Fossil",
        "FE|Transport|Pass|Rail|Liquids|Biomass" = "Liquids - Biomass",
        "FE|Transport|Pass|Rail|Liquids|Hydrogen" = "Liquids - Synthetic",
      "FE|Transport|Freight|Rail|Electricity" = "Electricity",
      "FE|Transport|Freight|Rail|Gases" = "Gases",
      "FE|Transport|Freight|Rail|Hydrogen" = "Hydrogen",
#      "FE|Transport|Freight|Rail|Liquids" = "Liquids"
        "FE|Transport|Freight|Rail|Liquids|Fossil" = "Liquids - Fossil",
        "FE|Transport|Freight|Rail|Liquids|Biomass" = "Liquids - Biomass",
        "FE|Transport|Freight|Rail|Liquids|Hydrogen" = "Liquids - Synthetic"
    ),
    "Aviation" = c(
      "FE|Transport|Pass|Aviation|Domestic|Electricity" = "Electricity",
      "FE|Transport|Pass|Aviation|Domestic|Gases" = "Gases",
      "FE|Transport|Pass|Aviation|Domestic|Hydrogen" = "Hydrogen",
#      "FE|Transport|Pass|Aviation|Domestic|Liquids" = "Liquids"
        "FE|Transport|Pass|Aviation|Domestic|Liquids|Fossil" = "Liquids - Fossil",
        "FE|Transport|Pass|Aviation|Domestic|Liquids|Biomass" = "Liquids - Biomass",
        "FE|Transport|Pass|Aviation|Domestic|Liquids|Hydrogen" = "Liquids - Synthetic"
    )
  ),
  "International" = list(
    "Aviation" = c(
      "FE|Transport|Pass|Aviation|International|Electricity" = "Electricity",
      "FE|Transport|Pass|Aviation|International|Gases" = "Gases",
      "FE|Transport|Pass|Aviation|International|Hydrogen" = "Hydrogen",
#      "FE|Transport|Pass|Aviation|International|Liquids" = "Liquids"
        "FE|Transport|Pass|Aviation|International|Liquids|Fossil" = "Liquids - Fossil",
        "FE|Transport|Pass|Aviation|International|Liquids|Biomass" = "Liquids - Biomass",
        "FE|Transport|Pass|Aviation|International|Liquids|Hydrogen" = "Liquids - Synthetic"
    ),
    "Shipping" = c(
      "FE|Transport|Freight|Navigation|Electricity" = "Electricity",
      "FE|Transport|Freight|Navigation|Gases" = "Gases",
      "FE|Transport|Freight|Navigation|Hydrogen" = "Hydrogen",
#      "FE|Transport|Freight|Navigation|Liquids" = "Liquids",
        "FE|Transport|Freight|Navigation|Liquids|Fossil" = "Liquids - Fossil",
        "FE|Transport|Freight|Navigation|Liquids|Biomass" = "Liquids - Biomass",
        "FE|Transport|Freight|Navigation|Liquids|Hydrogen" = "Liquids - Synthetic",
      "FE|Transport|Freight|International Shipping|Electricity" = "Electricity",
      "FE|Transport|Freight|International Shipping|Gases" = "Gases",
      "FE|Transport|Freight|International Shipping|Hydrogen" = "Hydrogen",
#      "FE|Transport|Freight|International Shipping|Liquids" = "Liquids"
        "FE|Transport|Freight|International Shipping|Liquids|Fossil" = "Liquids - Fossil",
        "FE|Transport|Freight|International Shipping|Liquids|Biomass" = "Liquids - Biomass",
        "FE|Transport|Freight|International Shipping|Liquids|Hydrogen" = "Liquids - Synthetic"
    )
  )
)

FEvarList <- unlist(c(FEvars$Domestic$LDV,FEvars$Domestic$Buses,FEvars$Domestic$Trucks,FEvars$Domestic$Rail,FEvars$Domestic$Aviation,FEvars$International$Aviation,FEvars$International$Shipping))

typeVar <- c()
for(national in names(FEvars)){
  for(mode in names(FEvars[[national]])){
    for(var in names(FEvars[[national]][[mode]])){
      v <- mode
      names(v) <- var
      typeVar <- c(typeVar,v)
    }
  }
}

FEplotData <- df %>% 
  filter(region == "EU27", period >= 2020, period <= 2060, scenario == mainScen, variable %in% names(FEvarList))

FEplotData <- FEplotData %>%
  mutate(national = ifelse(variable %in% names(c(FEvars$Domestic$LDV,FEvars$Domestic$Buses,FEvars$Domestic$Trucks,FEvars$Domestic$Rail,FEvars$Domestic$Aviation)), "Domestic", "International"),
         name = FEvarList[as.character(variable)],
         type="Final Energy",
         mode = typeVar[as.character(variable)]) %>%
  group_by(model,scenario,region,unit,period,national,name,type,mode) %>%
  summarize(value=sum(value),.groups = "keep")

FEplotData$mode <- factor(FEplotData$mode, levels=c("LDV","Buses","Trucks","Rail","Shipping","Aviation"))

FEplotData$name <- factor(FEplotData$name, levels=c("Electricity","Hydrogen","Liquids","Liquids - Biomass","Liquids - Synthetic","Liquids - Fossil","Gases"))

plotColor <- c(
  "Electricity" = "#F3E16B",
  "Hydrogen" = "#82c9d9",
  "Liquids" = "#282828",
  "Liquids - Fossil" = "#282828",
  "Liquids - Biomass" = "#005900",
  "Liquids - Synthetic" = "#b56576",
  "Gases" = "#999959"
)

g[["transport fe"]] <- ggplot(FEplotData,aes(x=period,y=value)) +
   geom_bar(aes(fill=name),stat='identity') +
   facet_wrap(type~national+mode,nrow=1) +
   theme_singleColumn() +
   theme(axis.title.y=element_blank()) +
   scale_fill_manual(values = plotColor, guide = guide_legend(nrow = 2)) + #, guide = guide_legend(nrow = 2)
   scale_x_continuous(breaks = c(2020,2040,2060)) + 
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()) +
  theme(legend.text=element_text(size=theme.single.text.size)) +
  theme(legend.key.height = unit(0.7, "cm"),
    legend.key.width = unit(0.7,"cm"))
#+ scale_y_continuous(name = "Final Energy")

ggsave(paste0(outFolder,"/transport fe.svg"), g[["transport fe"]] , device="svg", width = 12, height = 5, dpi=100, units = "in")
ggsave(paste0(outFolder,"/transport fe.png"), g[["transport fe"]] , device="png", width = 12, height = 5, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=12, fig.height=5}

g[["transport fe"]]

```

:::: {style="display: flex;"}

::: {}

(b) LDV sales and ICE stock (Millions of vehicles)

```{r, echo=FALSE}

#LDV

Sales <- list(
  "BEV" = "Sales|Transport|LDV|BEV",
  "FCEV" = "Sales|Transport|LDV|FCEV",
  "Hybrid Electric" =	"Sales|Transport|LDV|Hybrid Electric",
  "Liquids" = "Sales|Transport|LDV|Liquids",
  "Gases" = "Sales|Transport|LDV|NG"
)

Stock <- list(
  "BEV" = "Stock|Transport|LDV|BEV",
  "FCEV" = "Stock|Transport|LDV|FCEV",
  "Hybrid Electric" =	"Stock|Transport|LDV|Hybrid Electric",
  "Liquids" = "Stock|Transport|LDV|Liquids",
  "Gases" = "Stock|Transport|LDV|NG"
)

plotColor <- c(
  "BEV" = "#F3E16B",
  "FCEV" = "#82c9d9",
  "Hybrid Electric" =	"#F37A5E",
  "Liquids" = "#282828",
  "Gases" = "#F7EFE8" 
)

vars <- Sales

plotData <- df %>% 
  filter(region == "EU27", period >= 2020, period <= 2060, scenario == mainScen, variable %in% unlist(vars)) %>% 
  mutate(variable = factor(variable, levels=vars))

labels <- setNames(names(vars),vars[names(vars)])

plotData$labels <- labels[as.character(plotData$variable)]

#stock
stockData <- df %>% 
  filter(region == "EU27", period >= 2020, period <= 2060, scenario == mainScen, variable %in% unlist(Stock)) %>% 
  mutate(variable = factor(variable, levels=Stock)) %>%
  filter(variable %in% c("Stock|Transport|LDV|Liquids","Stock|Transport|LDV|NG")) %>%
  group_by(period) %>%
  summarize(value = sum(value),.groups = "keep") %>%
  mutate(variable = "ICE Stock")
stockData$value <- stockData$value/10

g[["LDV Sales"]] <-
  ggplot(plotData,aes(x=period,y=value)) +
  geom_bar(aes(fill=variable),stat='identity') +
  geom_line(data=stockData, aes(color=variable),linetype=11, lwd = 1) +
# geom_line(data=h,linetype="dashed", linewidth = 1, color="black") +
 geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 1) +
 geom_label_repel(data=data.frame(period=2030,value=stockData %>% filter(period == 2030) %>% pull(value)), label = "Stock",
                  #box.padding = 0.1,
                  #segment.curvature = -0.1,
                  #segment.square = TRUE,
                  #point.padding = 0.6,
                  nudge_x = 5,
                  nudge_y = 5,
                  #nudge_y = -0.02,
                  #force = 0.5,
                  hjust = 0,
                  direction="x", size = geom.text.double.size*0.9) +
  theme_doubleColumn() +
 #ylab(expression(paste("Energy and Industrial Processes Emissions - Mt" , CO[2], "eq/yr"))) +
 scale_fill_manual(values = setNames(plotColor[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(nrow = 2, order = 1)) + #, guide = guide_legend(nrow = 2)
 scale_color_manual(values = c("ICE Stock"="black"), guide = guide_legend(order = 2, keywidth = unit(2, 'cm'))) +
 scale_x_continuous(breaks=c(2020,2030,2040,2050,2060)) +
 # theme(legend.margin=margin(l = -2, unit='cm')) + 
 #theme(legend.position="right", legend.justification = "bottom") +
 #theme(axis.title.y = element_blank()) +
 scale_y_continuous(name = "Sales", # - Million vehicles", 
                     #breaks = c(round(emi1990), round(emi1990*0.6), round(emi1990*0.45), round(emi1990*0.3), round(emi1990*0.15), 0),
                     sec.axis = sec_axis( trans=~.*10, name="Stock")) +
                                          #, labels = scales::percent, breaks = c(1,0.4,0.55,0.7,0.85, 0))) +
  theme(legend.text=element_text(size=theme.double.text.size),
        legend.spacing.x = unit(0.2, 'cm'))  +
  guides(color = "none")
                                                      #+
 # theme(legend.key.height = unit(0.7, "cm"),
 #   legend.key.width = unit(0.4,"cm"))

ggsave(paste0(outFolder,"/LDV Sales.svg"), g[["LDV Sales"]] , device="svg", width = 6, height = 5, dpi=100, units = "in")
ggsave(paste0(outFolder,"/LDV Sales.png"), g[["LDV Sales"]] , device="png", width = 6, height = 5, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=6, fig.height=5}

   g[["LDV Sales"]]

```

(e) Industry CO2 emissions per sub-sector (Mt CO2/yr)

```{r, echo=FALSE}

# Industry Emissions
vars <- c("Cement" = "Emi|CO2|Energy|Demand|Industry|Cement",
          "Steel"="Emi|CO2|Energy|Demand|Industry|Steel",
          "Chemicals"="Emi|CO2|Energy|Demand|Industry|Chemicals",
          "Other Industry"="Emi|CO2|Energy|Demand|Industry|Other Industry")

plotColor <- c(
  "Cement" = "#355070",
  "Steel" = "#219ebc",
  "Chemicals" = "#eaac8b",
  "Other Industry" = "#e56b6f"
)

plotData <- df %>% 
  filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
  mutate(variable = factor(variable, levels=vars)) %>%
  group_by(model,region,variable,period) %>% 
  filter(tgt2050 != "Npi") %>% 
  mutate(ribbon.max=max(value),
         ribbon.min=min(value))

# historical data #missing non-energy
#h <- hist[hist$model == "UNFCCC" & hist$region == "EU27" & hist$variable %in% vars,] %>% drop_na(value)

#View(hist[hist$model == "UNFCCC" & hist$region == "EU27" & hist$variable == "Emi|CO2|Industrial Processes",] %>% drop_na(value))
# Emi|CO2|Energy|Demand|Industry
# Emi|CO2|Energy|Demand|Industry|Cement
# Emi|CO2|Energy|Demand|Industry|Chemicals
# Emi|CO2|Energy|Demand|Industry|Other Industry
# Emi|CO2|Energy|Demand|Industry|Other Industry|AFOFI
# Emi|CO2|Energy|Demand|Industry|Steel
# Emi|CO2|Industrial Processes
# Emi|CO2|Industrial Processes|Chemicals
# Emi|CO2|Industrial Processes|Metals
# Emi|CO2|Industrial Processes|Minerals
# Emi|GHG|Energy|Demand|Industry
# Emi|GHG|Industrial Processes

g[["Industry Emissions"]] <- ggplot(plotData,aes(x=period,y=value)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_segment(aes(x=2040, y=0, xend=2040, yend=max(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value))), linetype="dashed", color="black") +
    geom_line(data=plotData %>% filter(scenario == mainScen), aes(color=variable), linewidth=1.5) +
    #geom_line(data=h,linewidth=1,linetype="dashed") +
    geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min, fill=variable), alpha = 0.3) + 
    geom_point(data=plotData %>% filter(scenario == mainScen, period == 2040), aes(color=variable),size=3,shape=21,fill="white",stroke=1.5) +
    scale_color_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) +
    scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) +
    theme_doubleColumn() + 
    expand_limits(y=c(0,1)) +
    guides(color=guide_legend(nrow=2)) +
  theme(axis.title.y = element_blank())

ggsave(paste0(outFolder,"/Industry Emissions.svg"), g[["Industry Emissions"]] , device="svg", width = 6, height = 6, dpi=100, units = "in")
ggsave(paste0(outFolder,"/Industry Emissions.png"), g[["Industry Emissions"]] , device="png", width = 6, height = 6, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=6, fig.height=6}

g[["Industry Emissions"]]

```

:::

::: {}

(c) Buildings useful energy
    Electricity based heating (EJ/yr)

```{r, echo=FALSE}

vars <- c(
  "Heat pump" = "UE|Buildings|Heating|Electricity|Heat pump",
  #"District\nHeating" = "UE|Buildings|Heating|District Heating",
  "Resistance" = "UE|Buildings|Heating|Electricity|Resistance"
#  "non-Heating Electricity" = "UE|Buildings|non-Heating|Electricity|Conventional"
)

plotData <- df %>% 
  filter(region == "EU27", period %in% c(2020,2030,2040,2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
  mutate(variable = factor(variable, levels=vars))  %>% 
  filter(tgt2050 != "Npi")  %>%
  group_by(model,scenario,region,period) %>% 
  mutate(cumsum = cumsum(value),
         sum = sum(value)) %>% 
  group_by(model,region,variable,period) %>% 
  mutate(ribbon.max=max(cumsum),
         ribbon.min=min(cumsum)) %>% 
  group_by(model,region,period) %>% 
  mutate(ribbon.max.total=max(sum),
         ribbon.min.total=min(sum))

colors <- c(
  "Heat pump" = "#D62828",
  "District\nHeating" = "#E07A5F",
  "Resistance" = "#F77F00",
  "Heating - Gases" = as.vector(options$aesthetics$legend$color["Gases"]),
  "Heating - Hydrogen" = as.vector(options$aesthetics$legend$color["Hydrogen"]),
  "Heating - Liquids" = as.vector(options$aesthetics$legend$color["Liquids"]),
  "Heating - Solids" = as.vector(options$aesthetics$legend$color["Solids"]),
  "non-Heating Electricity" = as.vector(options$aesthetics$legend$color["Electricity"])
)

g[["Buildings Heating - Useful energy - Electricity Based"]] <- 
  ggplot(plotData,aes(x=period,y=value)) +
  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = variable)) +
  geom_errorbar(data=plotData %>% filter(period != 2020, variable == vars[1], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, size=1,position = position_dodge(width=2)) +
  # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
  coord_flip() +
  theme_doubleColumn() +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank()) +
  #guides(y = "none") +
  theme(axis.title.y=element_blank()) +
  #theme(legend.position = "none") #+
  scale_fill_manual(values = setNames(colors[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(reverse = TRUE, nrow = 1)) +
  theme(legend.text=element_text(size=theme.double.text.size)) +
  theme(legend.key.height = unit(0.7, "cm"),
    legend.key.width = unit(0.7,"cm")) +
  scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == "2020") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2030") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2040") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2050") %>% pull(value)),1))) +
  scale_x_reverse()

ggsave(paste0(outFolder,"/Buildings Heating - Useful energy - Electricity Based.svg"), g[["Buildings Heating - Useful energy - Electricity Based"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
ggsave(paste0(outFolder,"/Buildings Heating - Useful energy - Electricity Based.png"), g[["Buildings Heating - Useful energy - Electricity Based"]] , device="png", width = 6, height = 4, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=6, fig.height=4}

g[["Buildings Heating - Useful energy - Electricity Based"]]

```

(f) Carbon Management (Mt CO2/yr)

```{r, echo=FALSE}

vars <- list(
  "atmospheric/biogenic CO2 (CDR)" = "Carbon Management|atmospheric/biogenic CO2 - CDR",
  "CCS of fossil origin" = "Carbon Management|CCS of fossil origin",
  "DAC" = "Carbon Management|Storage|DAC",
  "BECCS" = "Carbon Management|Storage|Biomass|Pe2Se", 
  "Fossil CCS" = "Carbon Management|Storage|Fossil|Pe2Se", 
  "Industry CCS" = "Carbon Management|Storage|Industry CCS"
    # "Industry Energy" = "Carbon Management|Storage|Industry Energy",
    # "Industry Process" = "Carbon Management|Storage|Industry Process"
)

plotColor <- c(
  "atmospheric/biogenic CO2 (CDR)" = "#c1d8f0",
  "CCS of fossil origin" = "#6b5b4b",
  "DAC" = "#CC6666",
  "BECCS" = "#8bc18b",
  "Industry CCS" = "#5f6769",
  "Fossil CCS" = "#47331f"
)

plotData <- df %>% 
  filter(region == "EU27", period %in% c(2030, 2040, 2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
  mutate(CDRGroup = ifelse(as.character(variable) %in% c("Carbon Management|CCS of fossil origin","Carbon Management|atmospheric/biogenic CO2 - CDR"), "CDR", "CCS"), 
         variable = factor(variable, levels=vars),
         value = ifelse(grepl("Emi",variable,fixed = TRUE), -value, value))  %>% 
  mutate(CDRGroup = factor(CDRGroup, levels=c("CDR","CCS"))) %>%
  group_by(model,scenario,region,period, CDRGroup) %>% 
  mutate(cumsum = cumsum(value),
         sum = sum(value)) %>% 
  group_by(model,region,variable,period, CDRGroup) %>% 
  mutate(ribbon.max=max(cumsum),
         ribbon.min=min(cumsum)) %>% 
  group_by(model,region,period, CDRGroup) %>% 
  mutate(ribbon.max.total=max(sum),
         ribbon.min.total=min(sum))

 g[["Carbon Management"]] <- ggplot(plotData,aes(x=CDRGroup,y=value)) +
  #geom_area(aes(fill=variable)) +
  geom_bar(data=plotData %>% filter(scenario == mainScen), aes(fill=variable),stat='identity') + 
  geom_errorbar(data=plotData %>% filter(variable == vars[1], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=0.4, colour="black", alpha=0.9, size=1,position = position_dodge(width=2)) +
  facet_wrap(period ~ ., ncol=1, strip.position="left") +
  coord_flip() +
  theme_doubleColumn() +
  scale_fill_manual(values = setNames(plotColor[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(nrow = 4, reverse = TRUE)) + 
  theme(legend.margin=margin(l = -2, unit='cm')) +
  theme(axis.title.x=element_blank()) +
    theme(legend.title = element_blank()) +
  theme(axis.title.y = element_blank()) +
  theme(legend.text=element_text(size=theme.double.text.size)) +
  theme(legend.key.height = unit(0.7, "cm"),
    legend.key.width = unit(0.7,"cm")) +
  theme(legend.margin=margin(l = -2.5, unit='cm')) + 
  theme(strip.text.y.left = element_text(angle = 0)) +
  # theme(
  #   strip.background = element_blank(),
  #   strip.text.x = element_blank()
  # ) +
  theme(axis.text.y=element_blank(), #remove x axis labels
        axis.ticks.y=element_blank(), #remove x axis ticks
        )

 ggsave(paste0(outFolder,"/Carbon Management.svg"), g[["Carbon Management"]] , device="svg", width = 6, height = 5, dpi=100, units = "in")
 ggsave(paste0(outFolder,"/Carbon Management.png"), g[["Carbon Management"]] , device="png", width = 6, height = 5, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=6, fig.height=5}

g[["Carbon Management"]]

```

:::

::::

---

# Figure 5. Targets update

```{r, echo=FALSE}

# “existent targets”
# emission reduction - 2030 (FitFor55) - 2030 scenarios - 2040 scenarios
# energy savings  - 2030 (FitFor55 and REPowerEU) - 2030 scenarios - 2040 scenarios
# renewables target - 2030 (RED II, RED II revised, REPowerEU) - 2030 scenarios - 2040 scenarios
# solar photovoltaics capacity - 2030 (REPowerEU) - 2030 scenarios - 2040 scenarios
# CCS capacity target - 2030 EU-wide 50 MtCO2/y “Net-Zero Industry Act"
# “implicit targets”
# electrification? -> fe electrification share -> 45%
# “carbon-content in electricity” ->“carbon-free electricity” (>95%) 
# Total Residual Fossil emissions
# sectoral emissions -> Transport emissions -> 23% of 2020 
#                                   -> Industry and buildings emissions -> 27% of 2020
# “residual fossil”     -> Complete coal-phase by 2040
#                                  -> natural gas
#                                 -> oil
# “net trade” -> net-supply independency of gas by 2040
#                       -> one third of oil imports by 2040

#Emissions Reduction
plotData <- rbind(
    df %>% 
      filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
      calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>% 
      mutate(value = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)) ,2)) %>% 
      select(-variable)
    ,
    df %>% 
      filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>%
      calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>% 
      mutate(value = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)) ,2)) %>% 
      select(-variable)
  ) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Emissions\nreductions") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

g[["Emissions reductions"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Emissions\nreductions", y = 0.55, label = "FitFor55", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_y_continuous(labels = scales::percent) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = theme.double.text.size))

# Energy savings
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "FE|w/o Non-energy Use w/o Bunkers") %>% select(-variable) %>%
  mutate(value = round(value * 23.8845896627496)) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Energy\nsavings") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

g[["Energy savings"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Energy\nsavings", y = 750, label = "FitFor55", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
  geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Energy\nsavings", y = 787, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0.7, color = "black", alpha = 0.5) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  expand_limits(y=c(400,900)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = theme.double.text.size))

# Renewables share
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "SE|Renewables Share") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Renewables\nshare")

plotData$value <- plotData$value*(
  addHist$res %>% filter(type == "RES", period == 2020) %>% pull(value) /
   df %>% filter(region == "EU27", period == 2020, variable == "SE|Renewables Share", scenario == mainScen) %>% pull(value) 
)

plotData <- plotData %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

g[["Renewables share"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Renewables\nshare", y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0.5, color = "black", alpha = 0.5) +
  geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Renewables\nshare", y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0.6, color = "black", alpha = 0.5) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  scale_y_continuous(labels = scales::percent) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = theme.double.text.size))

#

# Solar photovoltaics
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Cap|Electricity|Solar|PV") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Solar\nphotovoltaics") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

#target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2025,2030),value=c(320,600)) 
g[["Solar photovoltaics"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Solar\nphotovoltaics", y = 600, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0.6, color = "black", alpha = 0.5) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  expand_limits(y=c(0,2500)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = theme.double.text.size))

# Carbon Capture and Storage 
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Carbon Management|Storage") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Carbon\nCapture and\nStorage") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

g[["Carbon Capture and Storage"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Carbon\nCapture and\nStorage", y = 50, label = "Net-Zero\nIndustry Act", angle=90, vjust = -0.2, hjust = 0.6, color = "black", alpha = 0.5) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  expand_limits(y=c(0,ceiling(max(plotData$value)/50)*50)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = theme.double.text.size))

# Novel CDR = atmospheric/biogenic CO2 (CDR) 
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Carbon Management|atmospheric/biogenic CO2 - CDR") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Novel CDR") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

g[["Novel CDR"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  expand_limits(y=c(0,ceiling(max(plotData$value)/50)*50)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = theme.double.text.size))

# Direct Electrification
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Final Energy|Electricity Share") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Direct\nElectrification") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

g[["Direct Electrification"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
    geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  scale_y_continuous(labels = scales::percent) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = theme.double.text.size))

# Carbon-free electricity share
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "SE|Electricity|carbon-free") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Carbon-free\nelectricity\nshare") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

g[["Carbon-free electricity share"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
    geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  scale_y_continuous(labels = scales::percent) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = theme.double.text.size))

# Residual Fossil Emissions
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Residual\nFossil\nEmissions") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

g[["Residual Fossil Emissions"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  expand_limits(y=c(0,2500)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = theme.double.text.size))

g[["Targets"]] <- gridExtra::arrangeGrob(
  g[["Emissions reductions"]] + theme(strip.text.x = element_blank()) + theme(plot.margin=margin(b=20, l = 30)), #+ theme(plot.margin=margin(10,10,30,10)),margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
  g[["Energy savings"]] + theme(plot.margin=margin(b=20, l = 57)),
  g[["Renewables share"]] + theme(plot.margin=margin(b=20, l = 15)),
  g[["Solar photovoltaics"]] + theme(plot.margin=margin(b=20, l = 10)),
  g[["Carbon Capture and Storage"]] + theme(plot.margin=margin(b=20, l = 15)),
  g[["Novel CDR"]] + theme(plot.margin=margin(b=20, l = 25)),
  g[["Direct Electrification"]] + theme(plot.margin=margin(b=20, l = 19)),
  g[["Carbon-free electricity share"]] + theme(plot.margin=margin(b=20, l = 24)),
  g[["Residual Fossil Emissions"]] + theme(plot.margin=margin(b=20, l = 39)),
  ncol = 1
)

ggsave(paste0(outFolder,"/targets.svg"), g[["Targets"]] , device="svg", width = 12, height = 17, dpi=100, units = "in")
ggsave(paste0(outFolder,"/targets.png"), g[["Targets"]] , device="png", width = 12, height = 17, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=12, fig.height=17}

grid.newpage()
grid.draw(g[["Targets"]])

```

### 2023-06-09 R/aesthetics.R

@@ -1,0 +1,281 @@
+
+# Aestethics
+
+baseTextSize <- 2
+
+options <- list()
+options$aesthetics <- list(
+  "text" = list(
+    "size" = list(
+      "text" = 30*baseTextSize,
+      "axis.title" = 30*baseTextSize,
+      "legend.text" = 20*baseTextSize
+    )
+  )
+  ,
+  "line" = list(
+    "size" = 1.5
+  ),
+  "legend" = list (
+    "color" = c(
+      #sector
+      "Industry" = "#5f6769",
+      "Residential and Commercial" = "#5edfff",
+      "Buildings" = "#5edfff",
+      "Transportation" = "#a1dd70",
+      "Carbon Dioxide Removal" = "#f7be16",
+      "Other Sector" = "#e9e5dd",
+      
+      "Energy" = "#3D4849",
+      
+      "Energy Supply - Electricity" = "#ffb200",
+      "Energy Supply - Gases"       = "#999959",
+      "Energy Supply - Heat"        = "#cc0000",
+      "Energy Supply - Hydrogen"    = "#5ed5b0",
+      "Energy Supply - Liquids"     = "#0000cc",
+      "Energy Supply - Solids"      = "#0c0c0c",
+      "Energy Supply - Other"       = "#79a6d2",
+      
+      "Electricity" = "#ffb200",
+      "Gases"       = "#999959",
+      "Gases - Fossil"  = "#999959", # #a1a161",
+      "Gases - Biomass" = "#999959", # "#999959",
+      "Gases - Efuel"   = "#999959", # "#caca8a",
+      "Heat"        = "#cc0000",
+      "Hydrogen"    = "#5ed5b0",
+      "Liquids"     = "#0000cc",
+      "Liquids - Fossil"  = "#0000cc", #"#000068",
+      "Liquids - Biomass" = "#0000cc", #"#0000cc",
+      "Liquids - Efuel"   = "#0000cc", #"#5050ff",
+      "Solids"      = "#0c0c0c",
+      "Solids - Fossil"  = "#0c0c0c", # "#0c0c0c",
+      "Solids - Biomass" = "#0c0c0c", # "#353535",
+      "Other Carrier" = "#79a6d2",
+      
+      "Biomass"     = "#005900",
+      "Coal"         = "#000000",
+      "Gas"       = "#999959",
+      
+      "Industrial Processes" = "#b2b2b2",
+      "Energy use - Buildings"   = "#5edfff",
[…]

### 2023-06-09 R/efficiencyTarget.R

@@ -1,0 +1,22 @@
+
+# Efficiency targets
+# REPOWER EU ACTION PLAN
+# https://eur-lex.europa.eu/legal-content/EN/TXT/PDF/?uri=CELEX:52022SC0230&from=EN 
+# PRIMES modelling results - Energy consumption in final demand sectors
+# RePowerEU = 712 Mtoe 
+# Fit-for-55 = 748 Mtoe
+
+# Old legislation
+# https://www.europarl.europa.eu/legislative-train/package-fit-for-55/file-revision-of-the-energy-efficiency-directive
+# 'fit for 55' legislative package
+# final (-36 %) energy consumption by 2030
+# 787 Mtoe in final energy consumption (compared to 846 Mtoe under the 2018 EED, EU energy efficiency directive (EED))
+
+# conversion factor
+Mtoe2TWa <- 41.868 * 0.001 * (1/31.526) # GJ/toe * (Mtoe/toe*EJ/GJ = 1e6/1e9) * EJ/TWa
+
+effTgt <- data.frame(target = c("reference","FitFor55 eff","RePowerEU eff"), #,"FitFor55 rev eff","RePowerEU rev eff"
+                     Final_Energy_Mtoe = c(846, 787, 750)) %>% #, round(748), round(712))) %>%
+  mutate(Final_Energy_Twa = c(round(Final_Energy_Mtoe*Mtoe2TWa,4)))
+
+#846*Mtoe2TWa

### 2023-06-09 R/harmonizeData.R

@@ -1,0 +1,42 @@
+
+#harmonizing data
+harmonizeData <- function(data,scaleFactor){ #,nzero=NULL
+  
+  # scaling emission variables by 95% to match historical values
+  # Total net emissions with international transport (EEA) (https://www.eea.europa.eu/data-and-maps/data/data-viewers/eea-greenhouse-gas-projections-data-viewer)
+  # 2005	  2010	  2015	  2020
+  # 4485.2	4072.8	3777.4	3527.5
+  #data[data$variable == "Emi|GHG|w/ Bunkers|LULUCF national accounting" & data$region == "EU27" & data$scenario == "06_NZero"  & data$period %in% c("2005","2010","2015","2020"),]$value*0.95
+  data[data$variable %in% grep("Emi\\|", unique(data$variable), value = TRUE),]$value <- data[data$variable %in% grep("Emi\\|", unique(data$variable), value = TRUE),]$value / scaleFactor
+  data[data$variable %in% grep("Carbon Management\\|", unique(data$variable), value = TRUE),]$value <- data[data$variable %in% grep("Carbon Management\\|", unique(data$variable), value = TRUE),]$value / scaleFactor
+  
+  # #copying prices from NZero_bioLim7p5 to other scenarios
+  # if (is.null(nzero)){
+  #   nzero <- data 
+  # }
+  # 
+  # #lapply(unique(data$scenario), function(scen){
+  # for(scen in unique(data$scenario)){
+  #   if(grepl("flex",scen)){
+  #     data[data$variable == "Price|Carbon" & data$scenario == scen & data$period %in% c(2005,2010,2015,2020),]$value <- nzero[nzero$variable == "Price|Carbon" & nzero$scenario == "NZero_bioLim7p5" & nzero$period %in% c(2005,2010,2015,2020),]$value
+  #   } else if(grepl("def",scen)){
+  #     data[data$variable == "Price|Carbon" & data$scenario == scen & data$period %in% c(2005,2010,2015,2020,2025),]$value <- nzero[nzero$variable == "Price|Carbon" & nzero$scenario  == "NZero_bioLim7p5" & nzero$period %in% c(2005,2010,2015,2020,2025),]$value
+  #   } else if(grepl("rigid",scen)){
[…]

### 2023-06-09 R/loadData.R

@@ -1,0 +1,227 @@
+
+
+# commands to modify input data
+modifyData <- function(data){
+  
+  # #removing edge-t duplicates
+  # data <- data[!data$variable %in% c("ES|Transport|Freight", "ES|Transport|Pass", "FE|Transport", "FE|Transport|Electricity", "FE|Transport|Gases", "FE|Transport|Hydrogen", "FE|Transport|Liquids", "FE|Transport|Freight", "FE|Transport|Freight|Electricity", "FE|Transport|Freight|Gases", "FE|Transport|Freight|Hydrogen", "FE|Transport|Freight|Liquids", "FE|Transport|Pass", "FE|Transport|Pass|Electricity", "FE|Transport|Pass|Gases", "FE|Transport|Pass|Hydrogen", "FE|Transport|Pass|Liquids", "FE|Transport|w/o Bunkers", "FE|Transport|w/o Bunkers|Electricity", "FE|Transport|w/o Bunkers|Gases", "FE|Transport|w/o Bunkers|Hydrogen", "FE|Transport|w/o Bunkers|Liquids", "ES|Transport|Road", "ES|Transport|Road", "ES|Transport|Pass", "ES|Transport|Freight", "FE|Transport|Pass", "FE|Transport|Freight", "FE|Transport", "FE|Transport|w/o bunkers", "FE|Transport|Pass|Liquids", "FE|Transport|Pass|Hydrogen", "FE|Transport|Pass|Gases", "FE|Transport|Pass|Electricity", "FE|Transport|Freight|Liquids", "FE|Transport|Freight|Hydrogen", "FE|Transport|Freight|Gases", "FE|Transport|Freight|Electricity", "FE|Transport|Liquids", "FE|Transport|Hydrogen", "FE|Transport|Gases", "FE|Transport|Electricity", "FE|Transport|w/o bunkers|Liquids", "FE|Transport|w/o bunkers|Hydrogen", "FE|Transport|w/o bunkers|Gases", "FE|Transport|w/o bunkers|Electricity"),]
+  
+  #remove pluses
+  data <- remind2::deletePlus(data)
+  
+  #remove number at the beginning of the scenario name
+  data$scenario <- gsub("^\\d\\d\\_*","",data$scenario)
+  #remove "0b" at the beginning of the scenario name
+  data$scenario <- gsub("^0b_","",data$scenario)
[…]

### 2023-06-09 R/loadReferenceEmissions.R

@@ -1,0 +1,226 @@
+
+## Reference emissions 
+
+# Emission Reduction targets
+#https://www.dehst.de/EN/european-emissions-trading/aircraft-operators/emissions-trading-in-aviation/emissions-trading-in-aviation_node.html
+
+#Miles intra-eu numbers
+#EC_CTP Table 39 MIX scenario, Intra-EU share in bunkers memo item (%), Intra-EU share in projected bunkers (MtCO2)	assume 2015 intra-extra split maintained to 2050
+intraEUCheck <- data.frame(
+  period = 1990:2050,
+  Miles = c(57.3, 56.3, 58.2, 59.5, 60.6, 61.7, 65.3, 69.7, 73.0, 74.2, 78.1, 79.5, 80.7, 83.0, 87.8, 91.3, 96.2, 99.6, 98.6, 88.0, 87.7, 88.0, 83.0, 79.7, 78.5, 79.7, 83.2, 86.9, 89.9, 90.4, 59.6, 89.4, 88.4, 87.5, 86.5, 84.5, 83.7, 82.9, 82.0, 81.2, 80.4, 77.3, 74.2, 71.2, 68.1, 65.1, 62.0, 59.0, 55.9, 52.8, 49.8, 46.7, 43.7, 40.6, 37.6, 34.5, 31.4, 28.4, 25.3, 22.3, 19.2), 
+  ourEstimation = c(round(addHist$eeaEmissions %>% filter(Sector_name == "Intra-EU International Aviation", Pollutant_name == "All greenhouse gases - (CO2 equivalent)", Country == "EU27") %>% pull(emissions), 1), rep(NA,2050-2022+1))
+) %>%
+  mutate(diff_MtCO2eq = ourEstimation - Miles,
+         pctg = round(diff_MtCO2eq/Miles * 100,1))
+
+eeaTotalsList <- list (
+  "Total net emissions (UNFCCC)" = c(
+    "1 - Energy",
+    "2 - Industrial Processes and Product Use",      
+    "3 - Agriculture",   
+    "4 - Land Use, Land-Use Change and Forestry",    
+    "5 - Waste management", 
+    "6 - Other Sector",     
+    "ind_CO2 - Indirect CO2" 
+  ),
+  "Total emissions (UNFCCC)" = c(
+    "1 - Energy",
+    "2 - Industrial Processes and Product Use",      
+    "3 - Agriculture",   
+    "5 - Waste management", 
[…]

### 2023-06-15 paperCharts.Rmd
additional paper data and charts improvements

@@
 
+bdgt <- remindEmi %>% 
+  filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen) %>%
+    mutate(weight = ifelse(period %in% c(2020,2050),2.5,5),
+           budget = value*weight) %>%
+    group_by(model,scenario,region,variable,tgt2050,tgt2030,efficiency,bioLim,limCCS) %>%
+    summarize(budget=round(sum(budget)/1000,2),.groups = "keep")
+
+budget <- data.frame(
+  Budget=c("Emissions with LULUCF and with international transport","Emissions without LULUCF and with international transport","Emissions with LULUCF and with intra-EU aviation","Emissions without LULUCF and with intra-EU aviation"),
+  reference_value=c(round(bdgt %>% filter(variable == "Emissions with LULUCF and with international transport", scenario == mainScen) %>% pull(budget)),
+                    round(bdgt %>% filter(variable == "Emissions without LULUCF and with international transport", scenario == mainScen) %>% pull(budget)),
+                    round(bdgt %>% filter(variable == "Emissions with LULUCF and with intra-EU aviation", scenario == mainScen) %>% pull(budget)),
+                    round(bdgt %>% filter(variable == "Emissions without LULUCF and with intra-EU aviation", scenario == mainScen) %>% pull(budget))),
+  min = c(round(min(bdgt %>% filter(variable == "Emissions with LULUCF and with international transport") %>% pull(budget))),
+                    round(min(bdgt %>% filter(variable == "Emissions without LULUCF and with international transport") %>% pull(budget))),
+                    round(min(bdgt %>% filter(variable == "Emissions with LULUCF and with intra-EU aviation") %>% pull(budget))),
+                    round(min(bdgt %>% filter(variable == "Emissions without LULUCF and with intra-EU aviation") %>% pull(budget)))),
+  max = c(round(max(bdgt %>% filter(variable == "Emissions with LULUCF and with international transport") %>% pull(budget))),
+                    round(max(bdgt %>% filter(variable == "Emissions without LULUCF and with international transport") %>% pull(budget))),
+                    round(max(bdgt %>% filter(variable == "Emissions with LULUCF and with intra-EU aviation") %>% pull(budget))),
+                    round(max(bdgt %>% filter(variable == "Emissions without LULUCF and with intra-EU aviation") %>% pull(budget))))
+)
+
+budget %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
 ```
@@
 
+nuclear_in_generation <- left_join(
+  df %>%
+  filter(region == "EU27", period == 2040, variable %in% c("SE|Electricity|Nuclear")) %>%  
+  select(scenario,tgt2030,value)
+  ,
+  df %>% 
+  filter(region == "EU27", period == 2040, variable %in% c("SE|Electricity")) %>%
+  mutate(total = value) %>%  
+  select(scenario,tgt2030,total)
+  , by = join_by(scenario == scenario, tgt2030 == tgt2030)
+  ) %>%
+  mutate(percentage = value/total)
+
 Generation <- data.frame(
-  Electricity_Generation=c("coal_in_generation_(%)","gas_in_generation_(%)","wind_and_Solar_gen_(%)","wind_and_Solar_cap_(TW)"),
+  Electricity_Generation=c("coal_in_generation_(%)","gas_in_generation_(%)","nuclear_in_generation_(%)","wind_and_Solar_gen_(%)","wind_and_Solar_cap_(TW)"),
   reference_value=c(
@@
     round(gas_in_generation %>% filter(scenario == mainScen) %>% pull(percentage)*100,1),
+    round(nuclear_in_generation %>% filter(scenario == mainScen) %>% pull(percentage)*100,1),
     round(wind_and_Solar_gen %>% filter(scenario == mainScen) %>% pull(percentage)*100,1),
@@
    round(min(gas_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
+   round(min(nuclear_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
    round(min(wind_and_Solar_gen %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
@@
    round(max(gas_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
+   round(max(nuclear_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
    round(max(wind_and_Solar_gen %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
@@
    )
+)
+
+share_of_fossil_in_electricity <- data.frame(
+  FE=c("share_of_fossil_without_CCS_in_electricity_(%)"),
+  reference_value_2020=c(
+    round((1-df %>% filter(region == "EU27", period == 2020, variable == "SE|Electricity|carbon-free", tgt2030 %in% tgt2030Scen, scenario == mainScen) %>% pull(value))*100 )),
+  reference_value_2040=c(
+    round((1-df %>% filter(region == "EU27", period == 2040, variable == "SE|Electricity|carbon-free", tgt2030 %in% tgt2030Scen, scenario == mainScen) %>% pull(value))*100 )),
+  min = c(round(min((1-df %>% filter(region == "EU27", period == 2040, variable == "SE|Electricity|carbon-free", tgt2030 %in% tgt2030Scen) %>% pull(value))*100))),
+  max = c(round(max((1-df %>% filter(region == "EU27", period == 2040, variable == "SE|Electricity|carbon-free", tgt2030 %in% tgt2030Scen) %>% pull(value))*100)))
 )
@@
 
+build_UE_heat <- c(
+  "Heat pump" = "UE|Buildings|Heating|Electricity|Heat pump",
+  "District Heating" = "UE|Buildings|Heating|District Heating",
+  "Resistance" = "UE|Buildings|Heating|Electricity|Resistance",
+  "Hydrogen" = "UE|Buildings|Heating|Hydrogen",
+  "Gases" = "UE|Buildings|Heating|Gases",
+  "Liquids" = "UE|Buildings|Heating|Liquids",
+  "Solids" = "UE|Buildings|Heating|Solids"#,
+#  "non-Heating Electricity" = "UE|Buildings|non-Heating|Electricity|Conventional"
+)
+
+build_UE_heating_data <- left_join(
+  df %>% 
+  filter(region == "EU27", period == 2040, variable %in% build_UE_heat[c("Heat pump","District Heating","Resistance")], tgt2030 %in% tgt2030Scen) %>%
+  group_by(scenario) %>%    
+  summarize(value = sum(value),.groups = "keep")
+  ,
+  df %>% 
+  filter(region == "EU27", period == 2040, variable %in% build_UE_heat, tgt2030 %in% tgt2030Scen) %>%
+  group_by(scenario) %>%  
+  summarize(total = sum(value)) %>% 
+  select(scenario,total)  
+  ,
+  by = join_by(scenario == scenario)
+) %>% 
+  mutate(pctg = value/total)
+
+build_UE_liq_gas_data <- left_join(
+  df %>% 
+  filter(region == "EU27", period == 2040, variable %in% build_UE_heat[c("Gases","Hydrogen","Liquids")], tgt2030 %in% tgt2030Scen) %>%
+  group_by(scenario) %>%    
+  summarize(value = sum(value),.groups = "keep")
+  ,
+  df %>% 
+  filter(region == "EU27", period == 2040, variable %in% build_UE_heat, tgt2030 %in% tgt2030Scen) %>%
+  group_by(scenario) %>%  
+  summarize(total = sum(value)) %>% 
+  select(scenario,total)  
+  ,
+  by = join_by(scenario == scenario)
+) %>% 
+  mutate(pctg = value/total)
+
+build_UE_solids_data <- left_join(
+  df %>% 
+  filter(region == "EU27", period == 2040, variable %in% build_UE_heat[c("Solids")], tgt2030 %in% tgt2030Scen) %>%
+  group_by(scenario) %>%    
+  summarize(value = sum(value),.groups = "keep")
+  ,
+  df %>% 
+  filter(region == "EU27", period == 2040, variable %in% build_UE_heat, tgt2030 %in% tgt2030Scen) %>%
+  group_by(scenario) %>%  
+  summarize(total = sum(value)) %>% 
+  select(scenario,total)  
+  ,
+  by = join_by(scenario == scenario)
+) %>% 
+  mutate(pctg = value/total)
+
+share_of_build_UE_heating <- data.frame(
+  FE=c("share_of_electric_and_district_buildings_heating_useful energy_(%)","share_of_liquids_and_gases_buildings_heating_useful_energy_(%)","share_of_solids_buildings_heating_useful energy_(%)"),
+  reference_value=c(round(build_UE_heating_data %>% filter(scenario == mainScen) %>% summarize(total = sum(pctg),.groups = "keep") %>% pull(total)*100 ),
+                    round(build_UE_liq_gas_data %>% filter(scenario == mainScen) %>% summarize(total = sum(pctg),.groups = "keep") %>% pull(total)*100 ),
+                    round(build_UE_solids_data %>% filter(scenario == mainScen) %>% summarize(total = sum(pctg),.groups = "keep") %>% pull(total)*100 )),
+  min = c(round(min(build_UE_heating_data %>% pull(pctg) *100)),
+          round(min(build_UE_liq_gas_data %>% pull(pctg) *100)),
+          round(min(build_UE_solids_data %>% pull(pctg) *100))),
+  max = c(round(max(build_UE_heating_data %>% pull(pctg) *100)),
+          round(max(build_UE_liq_gas_data %>% pull(pctg) *100)),
+          round(max(build_UE_solids_data %>% pull(pctg) *100)))
+)
+
+build_FE_data <- left_join(
+  df %>% 
+  filter(region == "EU27", period == 2040, variable == "FE|Buildings|Heating", tgt2030 %in% tgt2030Scen) %>% 
+  select(scenario,value)  
+  ,
+  df %>% 
+  filter(region == "EU27", period == 2020, variable == "FE|Buildings|Heating", tgt2030 %in% tgt2030Scen) %>%
+  mutate(base = value) %>% 
+  select(scenario,base)  
+  ,
+  by = join_by(scenario == scenario)
+) %>% 
+  mutate(pctg = value/base)
+
+share_of_build_FE_in_relation_to_2020 <- data.frame(
+  FE=c("share_of_build_FE_in_relation_to_2020_(%)"),
+  reference_value=c(round((1-build_FE_data %>% filter(scenario == mainScen) %>% pull(pctg))*100 )),
+  min = c(round(min((1-build_FE_data %>% pull(pctg)) *100))),
+  max = c(round(max((1-build_FE_data %>% pull(pctg)) *100)))
+)
+
+```
+
+```{r, echo=FALSE, fig.width=12, fig.height=5}
+
 Generation %>% 
@@
 
+share_of_fossil_in_electricity %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
 primaryEnergy %>% 
@@
 share_of_sustainable_fuel %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+share_of_build_UE_heating %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+share_of_build_FE_in_relation_to_2020 %>% 
   kbl() %>%
@@
   df %>% 
-    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
+    filter(region == "EU27", period %in% c(2030:2040), tgt2030 %in% tgt2030Scen) %>%
     calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
@@
   df %>% 
-    filter(region == "EU27", period %in% c(2035:2050), tgt2030 %in% tgt2030Scen) %>%
+    filter(region == "EU27", period %in% c(2045:2050), tgt2030 %in% tgt2030Scen) %>%
     calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%
@@
   theme_doubleColumn()  +
-  scale_y_continuous(labels = scales::percent) +
+  scale_y_continuous(minor_breaks = seq(0.2, 0.8, 0.2), breaks=c(0,1),labels = scales::percent) +
   scale_x_continuous(breaks=c(2020,2040,2060)) +
@@
   annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geom.text.double.size) +
-  theme(axis.text.y=element_blank()) +
+  #theme(axis.text.y=element_blank()) +
   theme(legend.key.height = unit(0.8, "cm"),
     legend.key.width = unit(0.8,"cm")) +
-  theme(legend.spacing.y = unit(0.1, 'cm'))
+  theme(legend.spacing.y = unit(0.1, 'cm')) +
+  theme(legend.margin=margin(l = -2, unit='cm'))
 
@@
     theme(axis.title.y = element_blank())+
-    coord_cartesian(clip = 'off')
+    coord_cartesian(clip = 'off') +
+    expand_limits(y = 3000)
 
@@
     theme_doubleColumn() + 
-    scale_y_continuous(labels = scales::percent) +
+    scale_y_continuous(breaks = seq(0, 1, 0.2),labels = scales::percent) +
     expand_limits(y=c(0,1)) +
@@
     guides(color=guide_legend(nrow=2)) +
-    theme(axis.title.y = element_blank()) #+
+    theme(axis.title.y = element_blank()) +
+    expand_limits(y = 30)
     #guides(fill = FALSE)
@@
   #geom_errorbar(data=plotData %>% filter(period != 2020), aes(ymin=ribbon.min, ymax=ribbon.max, group=variable), width=8, colour="black", alpha=0.9, size=1,position = position_dodge(width=2)) +
-  geom_errorbar(data=plotData %>% filter(period != 2020, variable == vars[1], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, size=1,position = position_dodge(width=2)) +
+  geom_errorbar(data=plotData %>% filter(period != 2020, variable == vars[1], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, linewidth=1,position = position_dodge(width=2)) +
   # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
@@
     legend.key.width = unit(0.7,"cm")) +
-  scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == 2020) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2030) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value)),1))) +
-  scale_x_reverse()
+  scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == 2020) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2030) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value)),1))) #+
+  #scale_x_reverse()
 
@@
 plotData <- df %>% 
-  filter(region == "EU27", period  %in% c(2020,2030,2040,2050,2060), scenario == mainScen, variable %in% unlist(vars))
+  filter(region == "EU27", period  %in% c(2020,2030,2040,2050), scenario == mainScen, variable %in% unlist(vars))
 
@@
   summarize(value=sum(value),.groups = "keep") %>%
-  mutate(type="Total")
+  mutate(type="EU-27 Net-trade")
 
@@
 
-g[["security of supply"]] <- ggplot(plotData,aes(x=period,y=value)) +
-  geom_bar(aes(fill=type),stat='identity') +
-  geom_errorbar(data  = plotDataTotal, aes(y=value, ymax=value, ymin=value, color=type), size=1) +
+# g[["security of supply"]] <- ggplot(plotData,aes(x=period,y=value)) +
+#   geom_bar(aes(fill=type),stat='identity') +
+#   geom_errorbar(data  = plotDataTotal, aes(y=value, ymax=value, ymin=value, color=type), size=1) +
+#   facet_wrap(~carrier,nrow=1) +
+#    theme_doubleColumn() +
+#    theme(axis.title.y=element_blank()) +
+#    scale_fill_manual(values = plotColor, guide = guide_legend(nrow = 1)) + #, guide = guide_legend(nrow = 2) setNames(options$aesthetics$legend$color[names(vars)],vars)
+#   scale_color_manual(values = c("Total"="black")) +
+#    scale_x_continuous(breaks = c(2020,2030,2040,2050)) + 
+#   #theme(
+#   #  strip.background = element_blank(),
+#   #  strip.text.x = element_blank()) +
+#   theme(legend.text=element_text(size=theme.single.text.size)) +
+#   theme(legend.key.height = unit(0.7, "cm"),
+#     legend.key.width = unit(0.7,"cm")) + 
+#   theme(axis.text = element_text(size=theme.single.text.size)) #+                                                              
+#   #theme(strip.text.x = element_text(size=0.8*theme.single.text.size)) +
+#   #theme(strip.clip = "off")
+# 
+# 
+#  ggsave(paste0(outFolder,"/security of supply.svg"), g[["security of supply"]] , device="svg", width = 6, height = 5, dpi=100, units = "in")
+#  ggsave(paste0(outFolder,"/security of supply.png"), g[["security of supply"]] , device="png", width = 6, height = 5, dpi=300, units = "in")
+
+g[["security of supply - fossil"]] <- ggplot(plotData %>% filter(period <= 2050, carrier != "Biomass"),aes(x=period,y=value)) +
+  geom_bar(aes(fill=type),stat='identity', alpha = 0.7) +
+  geom_errorbar(data  = plotDataTotal %>% filter(period <= 2050, carrier != "Biomass"), aes(y=value, ymax=value, ymin=value, color=type), linewidth=1.5) +
   facet_wrap(~carrier,nrow=1) +
@@
   theme(axis.title.y=element_blank()) +
-   scale_fill_manual(values = plotColor, guide = guide_legend(nrow = 1)) + #, guide = guide_legend(nrow = 2) setNames(options$aesthetics$legend$color[names(vars)],vars)
-  scale_color_manual(values = c("Total"="black")) +
-   scale_x_continuous(breaks = c(2020,2030,2040,2050, 2060)) + 
+  scale_fill_manual(values = plotColor, guide = guide_legend(ncol = 1, order = 2)) + #, guide = guide_legend(nrow = 2) setNames(options$aesthetics$legend$color[names(vars)],vars)
+  scale_color_manual(values = c("EU-27 Net-trade"="black"), guide = guide_legend(order = 1)) +
+  scale_x_continuous(breaks = c(2020,2030,2040,2050)) + 
   #theme(
@@
   theme(legend.key.height = unit(0.7, "cm"),
-    legend.key.width = unit(0.7,"cm")) + 
-  theme(axis.text = element_text(size=theme.single.text.size)) #+                                                              
+    legend.key.width = unit(1.5,"cm")) #+ 
+  #theme(axis.text = element_text(size=theme.single.text.size)) #+                                                              
   #theme(strip.text.x = element_text(size=0.8*theme.single.text.size)) +
@@
 
- ggsave(paste0(outFolder,"/security of supply.svg"), g[["security of supply"]] , device="svg", width = 6, height = 5, dpi=100, units = "in")
- ggsave(paste0(outFolder,"/security of supply.png"), g[["security of supply"]] , device="png", width = 6, height = 5, dpi=300, units = "in")
-
-g[["security of supply - fossil"]] <- ggplot(plotData %>% filter(period <= 2050, carrier != "Biomass"),aes(x=period,y=value)) +
-  geom_bar(aes(fill=type),stat='identity') +
-  geom_errorbar(data  = plotDataTotal %>% filter(period <= 2050, carrier != "Biomass"), aes(y=value, ymax=value, ymin=value, color=type), size=1) +
-  facet_wrap(~carrier,nrow=1) +
-   theme_doubleColumn() +
-   theme(axis.title.y=element_blank()) +
-   scale_fill_manual(values = plotColor, guide = guide_legend(nrow = 1)) + #, guide = guide_legend(nrow = 2) setNames(options$aesthetics$legend$color[names(vars)],vars)
-  scale_color_manual(values = c("Total"="black")) +
-   scale_x_continuous(breaks = c(2020,2030,2040,2050, 2060)) + 
-  #theme(
-  #  strip.background = element_blank(),
-  #  strip.text.x = element_blank()) +
-  theme(legend.text=element_text(size=theme.single.text.size)) +
-  theme(legend.key.height = unit(0.7, "cm"),
-    legend.key.width = unit(0.7,"cm")) + 
-  theme(axis.text = element_text(size=theme.single.text.size)) #+                                                              
-  #theme(strip.text.x = element_text(size=0.8*theme.single.text.size)) +
-  #theme(strip.clip = "off")
-
 ggsave(paste0(outFolder,"/security of supply - fossil.svg"), g[["security of supply - fossil"]] , device="svg", width = 6, height = 6, dpi=100, units = "in")
@@
 
-  g[["security of supply"]]
+  g[["security of supply - fossil"]]
 
@@
   geom_hline(yintercept= target[1,]$value, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = 2015, y = target[1,]$value, label = "REPowerEU\ndomestic", angle=90, vjust = 0.4, hjust = 1, color = "black", alpha = 0.5, size = 0.3*theme.single.text.size) +
+  annotate("text", x = 2015, y = target[1,]$value, label = "REPowerEU\ndomestic", angle=90, vjust = 0.4, hjust = 0, color = "black", alpha = 0.5, size = 0.3*theme.single.text.size) +
   geom_hline(yintercept= target[2,]$value, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = 2015, y = target[2,]$value, label = "REPowerEU\ntotal", angle=90, vjust = 0.4, hjust = 1, color = "black", alpha = 0.5, size = 0.3*theme.single.text.size) +
+  annotate("text", x = 2015, y = target[2,]$value, label = "REPowerEU\ntotal", angle=90, vjust = 0.4, hjust = 0, color = "black", alpha = 0.5, size = 0.3*theme.single.text.size) +
   geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = variable)) +
@@
   scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == 2030) %>% pull(value))),round(sum(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value))),round(sum(plotData %>% filter(scenario == mainScen, period == 2050) %>% pull(value))))) +
-  scale_x_reverse() +
+  #scale_x_reverse() +
   theme(legend.margin=margin(l = -2, unit='cm'))
@@
     legend.key.width = unit(0.7,"cm")) +
-  scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == "2020") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2030") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2040") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2050") %>% pull(value)),1))) +
-  scale_x_reverse()
+  scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == "2020") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2030") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2040") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2050") %>% pull(value)),1))) #+
+  #scale_x_reverse()
 
@@
   mutate(ribbon.max.total=max(sum),
-         ribbon.min.total=min(sum))
+         ribbon.min.total=min(sum)) %>% 
+  mutate(period = factor(period, levels=c(2050,2040,2030)))
 
@@
 
- ggsave(paste0(outFolder,"/Carbon Management.svg"), g[["Carbon Management"]] , device="svg", width = 6, height = 5, dpi=100, units = "in")
- ggsave(paste0(outFolder,"/Carbon Management.png"), g[["Carbon Management"]] , device="png", width = 6, height = 5, dpi=300, units = "in")
-
-```
-
-```{r, echo=FALSE, fig.width=6, fig.height=5}
+ ggsave(paste0(outFolder,"/Carbon Management.svg"), g[["Carbon Management"]] , device="svg", width = 6, height = 6, dpi=100, units = "in")
+ ggsave(paste0(outFolder,"/Carbon Management.png"), g[["Carbon Management"]] , device="png", width = 6, height = 6, dpi=300, units = "in")
+
+```
+
+```{r, echo=FALSE, fig.width=6, fig.height=6}
 
@@
   theme(strip.text.y = element_blank()) +
-  scale_y_continuous(labels = scales::percent) +
+  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
   expand_limits(y=c(0,1)) + 
@@
   theme(strip.text.x = element_blank()) +
-  expand_limits(y=c(400,900)) + 
+  expand_limits(y=c(400,1000)) + 
   theme(panel.spacing = unit(4, "lines")) +
@@
   theme(strip.text.x = element_blank()) +
-  scale_y_continuous(labels = scales::percent) +
+  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
   expand_limits(y=c(0,1)) + 
@@
   theme(strip.text.x = element_blank()) +
-  expand_limits(y=c(0,ceiling(max(plotData$value)/50)*50)) + 
+  #expand_limits(y=c(0,ceiling(max(plotData$value)/50)*50)) + 
+  expand_limits(y=c(0,400)) + 
   theme(panel.spacing = unit(4, "lines")) +
@@
   theme(strip.text.x = element_blank()) +
-  expand_limits(y=c(0,ceiling(max(plotData$value)/50)*50)) + 
+  expand_limits(y=c(0,250)) + 
+  #expand_limits(y=c(0,ceiling(max(plotData$value)/50)*50)) + 
   theme(panel.spacing = unit(4, "lines")) +

### 2023-06-22 paperCharts.Rmd
adding carbon management results and general charts improvements

@@
 
+## Carbon Management Results
+
+```{r, echo=FALSE}
+
+#Carbon Management|Storage in 2030 (Minimum and Maximum of your scenario range)
+
+#Carbon Management|Storage in 2040 (Minimum and Maximum of your scenario range)
+
+#tenth root (because the period is 10 years) and then the division of 2040 CCS to 2030 CCS, i.e.:
+#10√(Carbon Management|Storage in 2040 / Carbon Management|Storage in 2030)
+#(here also minimum and maximum value across your scenario range)
+
+#Here again we need the tenth (because 10 years) root of the ratio of CDR in 2040 divided by CDR in 2030
+#For CDR quantity calculation see next comment :)
+
+#Total CDR = (Emi|CO2|CDR|BECCS + Emi|CO2|CDR|DACCS + Emi|CO2|CDR|Industry CCS|Synthetic Fuels) in 2040
+#(and then span the scenario range)
+
+totalCDR <- df %>% filter(region == "EU27", period %in% c(2030,2040), variable %in% c("Emi|CO2|CDR|BECCS","Emi|CO2|CDR|DACCS","Emi|CO2|CDR|Industry CCS|Synthetic Fuels"), tgt2030 %in% tgt2030Scen) %>% group_by(period,scenario) %>% summarize(value = sum(-value),.groups = "keep")
+
+rateCCS <- left_join(
+  df %>%
+    filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>%
+    mutate(numerator=value) %>%
+    select(scenario,numerator)
+  ,
+  df %>%
+    filter(region == "EU27", period == 2030, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>%
+    mutate(denominator=value) %>%
+    select(scenario,denominator)
+  , by = join_by(scenario == scenario)
+) %>%
+  mutate(percentage = numerator/denominator,
+         rate = percentage ^ (1/10))
+
+rateCDR <- left_join(
+  totalCDR %>%
+    filter(period == 2040) %>%
+    mutate(numerator=value) %>%
+    ungroup() %>%
+    select(scenario,numerator)
+  ,
+  totalCDR %>%
+    filter(period == 2030) %>%
+    mutate(denominator=value) %>%
+    ungroup() %>%
+    select(scenario,denominator)
+  , by = join_by(scenario == scenario)
+) %>%
+  mutate(percentage = numerator/denominator,
+         rate = percentage ^ (1/10))
+
+CDR <- data.frame(
+  result=c("CCS_deployment_in_2030_MtCO2","CCS_deployment_in_2040_MtCO2","CCS_upscaling_rates_2030_2040_%","novel_CDR_upscaling_rates_2030_2040_%","novel_CDR_deployment_in_2040_MtCO2"),
+  reference_value=c(
+    round(df %>% filter(region == "EU27", period == 2030, variable == "Carbon Management|Storage", scenario == mainScen) %>% pull(value)),
+    round(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", scenario == mainScen) %>% pull(value)),
+    round(rateCCS %>% filter(scenario == mainScen) %>% pull(rate)*100),
+    round(rateCDR %>% filter(scenario == mainScen) %>% pull(rate)*100),
+    round(totalCDR %>% filter(period == 2040, scenario == mainScen) %>% pull(value))
+  ),
+  min = c(
+    round(min(df %>% filter(region == "EU27", period == 2030, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
+    round(min(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
+    round(min(rateCCS %>% pull(rate))*100),
+    round(min(rateCDR %>% pull(rate))*100),
+    round(min(totalCDR %>% pull(value)))
+  ),
+  max = c(
+    round(max(df %>% filter(region == "EU27", period == 2030, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
+    round(max(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
+    round(max(rateCCS %>% pull(rate))*100),
+    round(max(rateCDR %>% pull(rate))*100),
+    round(max(totalCDR %>% pull(value)))
+  )
+)
+
+```
+
+```{r, echo=FALSE, fig.width=12, fig.height=5}
+
+CDR %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+```
+
+---
+
 <!-- Paper Figures -->
@@
 #     ylab(expression(paste("Mt ", CO[2],"eq/yr"))) +
-     scale_y_continuous(breaks = c(0,1000,2000,3000,4000,5000))
+     scale_y_continuous(breaks = c(0,1000,2000,3000,4000,5000)) +
+  scale_x_continuous(breaks = seq(1990,2060,10))
 
@@
 
+#df <- rbind(df,df %>% calc_addVariable("`Emi|CO2|Gross|Other Energy Conversion`" = "`Emi|CO2|Gross|Energy|Supply|Hydrogen` + `Emi|CO2|Gross|Energy|Supply|Liquids` #+ `Emi|CO2|Gross|Energy|Supply|Liquids` + `Emi|CO2|Gross|Energy|Supply|Solids`", units = "Mt CO2/yr", only.new=T))
+
 vars <- list(
@@
 #  "Other Sector" ="Emissions|CO2|Energy|Demand|Other Sector",
-  "Hydrogen" ="Emi|CO2|Gross|Energy|Supply|Hydrogen",
-  "Liquids"="Emi|CO2|Gross|Energy|Supply|Liquids",
-  "Gases"="Emi|CO2|Gross|Energy|Supply|Gases",
-  "Solids"="Emi|CO2|Gross|Energy|Supply|Solids",
+  "Heat"="Emi|CO2|Gross|Energy|Supply|Heat",
+  "Other Energy\nConversion" = "Emi|CO2|Gross|Other Energy Conversion",
+    #"Hydrogen" ="Emi|CO2|Gross|Energy|Supply|Hydrogen",
+    #"Liquids"="Emi|CO2|Gross|Energy|Supply|Liquids",
+    #"Gases"="Emi|CO2|Gross|Energy|Supply|Gases",
+    #"Solids"="Emi|CO2|Gross|Energy|Supply|Solids",
 #  "Other"="Emissions|CO2|Energy|Supply|Other",
-  "Heat"="Emi|CO2|Gross|Energy|Supply|Heat",
   "Electricity"="Emi|GHG|Gross|Energy|Supply|Electricity"
 )
-
 # "Emi|GHG|Agriculture",
@@
   "Heat"= "#cc0000",
-  "Gases"= "#999959",
-  "Liquids"= "#0000cc",
-  "Solids"= "#0c0c0c",
-  "Other" = "#79a6d2",
-  "Hydrogen" = "#5ed5b0",
+  "Other Energy\nConversion" = "#0000cc",
+  #"Gases"= "#999959",
+  #"Liquids"= "#0000cc",
+  #"Solids"= "#0c0c0c",
+  #"Other" = "#79a6d2",
+  #"Hydrogen" = "#5ed5b0",
   "Transportation" = "#a1dd70",
@@
 
-plotData <- df %>%
+labels <- setNames(names(vars),vars[names(vars)])
+
+fulldata <- df %>%
   filter(region == "EU27",
@@
          tgt2030 %in% tgt2030Scen,
-         variable %in% unlist(vars),
-         scenario == mainScen)
-
-labels <- setNames(names(vars),vars[names(vars)])
-
-plotData$labels <- labels[as.character(plotData$variable)]
-
-plotData[plotData$value <= 0,]$value <- 0
-
-data <-
-  plotData %>%
+         variable %in% unlist(vars)) %>%
+  mutate(labels = factor(labels[as.character(variable)],levels = names(vars)),
+         variable = factor(variable, levels = vars)) %>%
+  group_by(period,variable) %>%
+  mutate(min = min(value),
+         max = max(value))
+
+plotData <- fulldata %>%
+  filter(scenario == mainScen) %>%
   mutate(complement = FALSE) %>%
@@
   bind_rows(
-    plotData %>%
+    fulldata %>%
+      filter(scenario == mainScen) %>%
       mutate(complement = TRUE) %>%
@@
   arrange(period,ext_Var) %>%
-  arrange(match(variable, c("25pct",vars))) %>%
   group_by(period) %>%
+  arrange(variable) %>%
   mutate(ymid = as.numeric(sub("\\D+", "", period)),
@@
          xmid = (xmax + xmin) / 2,
-         )
-
-data[data$period!=2020,]$labels <- NA
-data[data$period != 2040,]$pct <- NA
-data[data$variable == "25pct",]$pct <- NA
-
-max <- data %>%
-  filter(variable == tail(vars,1), complement == TRUE) %>% 
-  group_by(period)
-
-data$labelsPosY <- data$ymid
-data[data$labels %in% c("Solids"),]$labelsPosY <- 2015
-data[data$labels %in% c("Bunkers","Industrial Processes","Liquids"),]$labelsPosY <- 2016
-data[data$labels %in% c("Hydrogen"),]$labelsPosY <- 2010
-
-data$pctPosY <- data$ymid
-#data[data$Variable %in% c("Emi|GHG|Industrial Processes","Emi|CO2|Gross|Energy|Supply|Gases","Emi|GHG|Gross|Energy|Supply|Electricity"),]$pctPosY <- 2047
-data[data$variable %in% c("Emi|CO2|Gross|Energy|Supply|Solids","Emi|CO2|Gross|Energy|Supply|Heat","Emi|CO2|Gross|Energy|Supply|Hydrogen"),]$pctPosY <- 2100
-data[data$variable %in% c("Emi|CO2|Gross|Energy|Supply|Liquids"),]$pctPosY <- 2043
-data$pctPosX <- data$xmid
-#data[data$variable %in% c("Emi|GHG|Industrial Processes"),]$pctPosX <- data[data$variable %in% c("Emi|GHG|Industrial Processes"),]$pctPosX - 100
-#data[data$variable %in% c("Emi|GHG|Gross|Energy|Demand|Industry"),]$pctPosX <- data[data$variable %in% c("Emi|GHG|Gross|Energy|Demand|Industry"),]$pctPosX + 100
-
-#data$ext_Var <- as.character(data$ext_Var)
-
-#remove labels for small values
-data <- data %>% mutate(pct = ifelse(variable %in% vars[c("Hydrogen","Solids","Heat")], NA, pct))
-
-g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] <- data %>%
+         ) %>%
+  ungroup() %>%
+  filter(complement == FALSE)
+
+g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] <- plotData %>% 
   ggplot(aes(xmid, ymid, fill = ext_Var)) +
@@
                 alpha = factor(period), color = variable)) +
-  #geom_text(data=max, aes(label = period, y=period, x=xmax), vjust=0.5, hjust=-0.5) + 
-  geom_text(aes(y = 2015, label = labels, group = labels, hjust=1, angle = 90), vjust=0.5, hjust=1.1, na.rm=TRUE, size = geom.text.single.size, angle = 90) +
-  #geom_label_repel(aes(y = 2014, label = labels, group = labels), vjust=0.5, hjust=1, na.rm=TRUE, size = geom.text.single.size, angle = 90) +
-  #geomtextpath::geom_textpath(aes(y = 2014, label = labels, group = labels, vjust=0.5, hjust=1, angle = 90),text_only = TRUE, na.rm=TRUE, size = geom.text.double.size) +
-  geom_text(aes(x=pctPosX , y = 2045, label = pct), vjust=0.5, hjust=-0.1, na.rm=TRUE, size = geom.text.single.size, angle = 90) +
-  #geomtextpath::geom_textpath(aes(x=pctPosX , y = 2046, label = pct),text_only = TRUE, na.rm=TRUE, size = geom.text.double.size) +
-  #geom_text(aes(y = ymid + 3, label = labels, group = labels)) +
-  scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars),setNames(rep("transparent",length(vars)),paste0(vars,"_"))), labels = setNames(names(vars), vars)) +
+  geom_errorbar(data=plotData %>% filter(period == 2040), aes(xmin=xmax-value+min, xmax=xmax-value+max), width=4, colour="black", alpha=0.9, linewidth=0.8) +
+  geom_text(data=plotData %>% filter(period == 2020), aes(y = 2015, label = labels, group = labels, hjust=1, angle = 90), vjust=0.5, hjust=1.1, na.rm=TRUE, size = geom.text.single.size, angle = 90, lineheight = 0.8) +
+  geom_text(data=plotData %>% filter(period == 2040), aes(x=xmid , y = 2045, label = pct), vjust=0.5, hjust=-0.1, na.rm=TRUE, size = geom.text.single.size, angle = 90) +
+  scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) + 
   scale_alpha_manual(values = c(0.2, 0.3, 1)) +
   scale_color_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) +
-  #scale_fill_manual(values = c("#cd9900", "#00817e")) +
-  #scale_colour_manual(values = c("#cd9900", "#00817e")) +
-  #scale_y_continuous(limits = c(1990, 2045)) +
-  #scale_y_reverse(limits = c(2065, 2013)) +
   theme_doubleColumn() +
   theme(legend.position = "none") +
-  scale_y_continuous(breaks=c(2020,2030,2040), minor_breaks = NULL, limits=c(2008,2047)) +
+  scale_y_continuous(breaks=c(2020,2030,2040), labels=c("today",2030,2040), minor_breaks = NULL, limits=c(2008,2047)) +
   theme(axis.title.x=element_blank(),
@@
   coord_cartesian(clip="off") +
-  theme(plot.margin = unit(c(1,0,2,0), "cm"))
-
-ggsave(paste0(outFolder,"/2040 Emissions - Energy and Industrial Processes - horizontal bar.svg"), g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] , device="svg", width = 12, height = 3, dpi=100, units = "in")
-ggsave(paste0(outFolder,"/2040 Emissions - Energy and Industrial Processes - horizontal bar.png"), g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] , device="png", width = 12, height = 3, dpi=300, units = "in")
-
-```
-
-```{r, echo=FALSE, fig.width=12, fig.height=3}
+  theme(plot.margin = margin(t = 30, r = 0, b = 85, l = 0, unit = "pt"))
+
+ggsave(paste0(outFolder,"/2040 Emissions - Energy and Industrial Processes - horizontal bar.svg"), g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] , device="svg", width = 12, height = 3.2, dpi=100, units = "in")
+ggsave(paste0(outFolder,"/2040 Emissions - Energy and Industrial Processes - horizontal bar.png"), g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] , device="png", width = 12, height = 3.2, dpi=300, units = "in")
+
+```
+
+```{r, echo=FALSE, fig.width=12, fig.height=3.2}
 
@@
   annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geom.text.double.size) +
-  #theme(axis.text.y=element_blank()) +
+  theme(axis.text.y=element_blank()) +
   theme(legend.key.height = unit(0.8, "cm"),
@@
   theme(legend.spacing.y = unit(0.1, 'cm')) +
-  theme(legend.margin=margin(l = -2, unit='cm'))
+  theme() +
+  annotate(geom = "text", label = "100%", x = 2020, y = 1, hjust=1.2, color = "#666666", size=geom.text.double.size) +
+  annotate(geom = "text", label = "0%", x = 2020, y = 0, hjust=1.2, color = "#666666", size=geom.text.double.size) +
+  coord_cartesian(clip = 'off') +
+  theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 20, unit = "pt")
+        #,legend.margin=margin(l = -2, unit='cm')
+        )
 
@@
   ggplot(plotData,aes(x=period,y=value)) +
-  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = variable)) +
+  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = variable, alpha=factor(period))) +
   #geom_errorbar(data=plotData %>% filter(period != 2020), aes(ymin=ribbon.min, ymax=ribbon.max, group=variable), width=8, colour="black", alpha=0.9, size=1,position = position_dodge(width=2)) +
@@
   scale_fill_manual(values = setNames(options$aesthetics$legend$color[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(reverse = TRUE, nrow = 1)) +
+  scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
   theme(legend.text=element_text(size=theme.double.text.size)) +
@@
     legend.key.width = unit(0.7,"cm")) +
-  scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == 2020) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2030) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value)),1))) #+
+  scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == 2020) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2030) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value)),1))) +
   #scale_x_reverse()
+  theme(legend.margin=margin(l = -2, unit='cm'))
 
@@
   annotate("text", x = 2015, y = target[2,]$value, label = "REPowerEU\ntotal", angle=90, vjust = 0.4, hjust = 0, color = "black", alpha = 0.5, size = 0.3*theme.single.text.size) +
-  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = variable)) +
-  geom_errorbar(data=plotData %>% filter(period != 2020, variable == vars[1], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, size=1,position = position_dodge(width=2)) +
+  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = variable, alpha=factor(period))) +
+  geom_errorbar(data=plotData %>% filter(period != 2020, variable == vars[1], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, linewidth=1,position = position_dodge(width=2)) +
   # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
@@
                     breaks = c("SE|Hydrogen|Electricity", "SE|Hydrogen|Gas|w/o CC", "SE|Hydrogen|Biomass|w/ CC"), guide = guide_legend(nrow = 1)) +
+  scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
   theme(legend.text=element_text(size=theme.double.text.size)) +
@@
     legend.key.width = unit(0.7,"cm")) +
-  scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == 2030) %>% pull(value))),round(sum(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value))),round(sum(plotData %>% filter(scenario == mainScen, period == 2050) %>% pull(value))))) +
+  scale_y_continuous(breaks = c(0,plotData %>% filter(scenario == mainScen, period == 2030, variable == vars[1]) %>% pull(sum),plotData %>% filter(scenario == mainScen, period == 2040, variable == vars[1]) %>% pull(sum),plotData %>% filter(scenario == mainScen, period == 2050, variable == vars[1]) %>% pull(sum)),
+                     labels = c(format(0,nsmall = 1),format(round(plotData %>% filter(scenario == mainScen, period == 2030, variable == vars[1]) %>% pull(sum),1),nsmall = 1),format(round(plotData %>% filter(scenario == mainScen, period == 2040, variable == vars[1]) %>% pull(sum),1),nsmall = 1),format(round(plotData %>% filter(scenario == mainScen, period == 2050, variable == vars[1]) %>% pull(sum),1),nsmall = 1))) +
+  #scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == 2030) %>% pull(value))),round(sum(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value))),round(sum(plotData %>% filter(scenario == mainScen, period == 2050) %>% pull(value))))) +
   #scale_x_reverse() +
@@
 g[["transport fe"]] <- ggplot(FEplotData,aes(x=period,y=value)) +
-   geom_bar(aes(fill=name),stat='identity') +
+   geom_bar(aes(fill=name, alpha=factor(period)),stat='identity') +
    facet_wrap(type~national+mode,nrow=1) +
@@
    scale_fill_manual(values = plotColor, guide = guide_legend(nrow = 2)) + #, guide = guide_legend(nrow = 2)
+   scale_alpha_manual(values = c("2020"=0.7,"2025"=0.7,"2030"=0.7,"2035"=0.7,"2040"=1,"2045"=0.7,"2050"=0.7,"2055"=0.7,"2060"=0.7), guide = 'none') +
    scale_x_continuous(breaks = c(2020,2040,2060)) + 
@@
   ggplot(plotData,aes(x=period,y=value)) +
-  geom_bar(aes(fill=variable),stat='identity') +
+  geom_bar(aes(fill=variable, alpha=factor(period)),stat='identity') +
   geom_line(data=stockData, aes(color=variable),linetype=11, lwd = 1) +
@@
  scale_color_manual(values = c("ICE Stock"="black"), guide = guide_legend(order = 2, keywidth = unit(2, 'cm'))) +
+ scale_alpha_manual(values = c("2020"=0.7,"2025"=0.7,"2030"=0.7,"2035"=0.7,"2040"=1,"2045"=0.7,"2050"=0.7,"2055"=0.7,"2060"=0.7), guide = 'none') +
  scale_x_continuous(breaks=c(2020,2030,2040,2050,2060)) +
@@
         legend.spacing.x = unit(0.2, 'cm'))  +
-  guides(color = "none")
+  guides(color = "none") +
+  theme(axis.title.y = element_text(colour = "#666666"))
+
 #+
@@
   ggplot(plotData,aes(x=period,y=value)) +
-  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = variable)) +
+  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = variable, alpha=factor(period))) +
   geom_errorbar(data=plotData %>% filter(period != 2020, variable == vars[1], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, size=1,position = position_dodge(width=2)) +
@@
   scale_fill_manual(values = setNames(colors[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(reverse = TRUE, nrow = 1)) +
+  scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
   theme(legend.text=element_text(size=theme.double.text.size)) +
@@
   #geom_area(aes(fill=variable)) +
-  geom_bar(data=plotData %>% filter(scenario == mainScen), aes(fill=variable),stat='identity') + 
-  geom_errorbar(data=plotData %>% filter(variable == vars[1], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=0.4, colour="black", alpha=0.9, size=1,position = position_dodge(width=2)) +
+  geom_bar(data=plotData %>% filter(scenario == mainScen), aes(fill=variable, alpha=factor(period)),stat='identity') + 
+  geom_errorbar(data=plotData %>% filter(variable == vars[1], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=0.4, colour="black", alpha=0.9, size=1) +
   facet_wrap(period ~ ., ncol=1, strip.position="left") +
@@
   scale_fill_manual(values = setNames(plotColor[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(nrow = 4, reverse = TRUE)) + 
+  scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
   theme(legend.margin=margin(l = -2, unit='cm')) +
@@
   theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(size = theme.double.text.size))
-
-# Energy savings
+  theme(axis.text.x = element_text(size = theme.double.text.size)) +
+  geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.4, na.rm = TRUE)
+
+# Final Energy Demand - Energy savings
 plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "FE|w/o Non-energy Use w/o Bunkers") %>% select(-variable) %>%
@@
   filter(tgt2050 != "Npi") %>%
-  mutate(target = "Energy\nsavings") %>%
+  mutate(target = "Final Energy\nDemand") %>%
   group_by(period) %>% 
@@
   geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Energy\nsavings", y = 750, label = "FitFor55", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
+  annotate("text", x = "Final Energy\nDemand", y = 750, label = "FitFor55", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
   geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Energy\nsavings", y = 787, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0.7, color = "black", alpha = 0.5) +
+  annotate("text", x = "Final Energy\nDemand", y = 787, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0.7, color = "black", alpha = 0.5) +
   facet_grid(target~period, scales="free") +
@@
   theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(size = theme.double.text.size))
+  theme(axis.text.x = element_text(size = theme.double.text.size)) +
+  geom_text(data=data.frame(period=c(2030,2040),label=c("(Mtoe)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.2, na.rm = TRUE)
 
@@
   filter(tgt2050 != "Npi") %>%
-  mutate(target = "Renewables\nshare")
+  mutate(target = "Renewables\nShare in\nFinal Energy")
 
@@
 
-g[["Renewables share"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
+g[["Renewables Share"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
@@
   geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Renewables\nshare", y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0.5, color = "black", alpha = 0.5) +
+  annotate("text", x = "Renewables\nShare in\nFinal Energy", y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0.5, color = "black", alpha = 0.5) +
   geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Renewables\nshare", y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0.6, color = "black", alpha = 0.5) +
+  annotate("text", x = "Renewables\nShare in\nFinal Energy", y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0.6, color = "black", alpha = 0.5) +
   facet_grid(target~period, scales="free") +
@@
   theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(size = theme.double.text.size))
+  theme(axis.text.x = element_text(size = theme.double.text.size)) +
+  geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.4, na.rm = TRUE)
 
@@
   theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(size = theme.double.text.size))
+  theme(axis.text.x = element_text(size = theme.double.text.size)) +
+  geom_text(data=data.frame(period=c(2030,2040),label=c("(GW)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.3, na.rm = TRUE)
 
@@
   theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(size = theme.double.text.size))
+  theme(axis.text.x = element_text(size = theme.double.text.size)) +
+  geom_text(data=data.frame(period=c(2030,2040),label=c("(Mt CO2/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.1, na.rm = TRUE)
 
@@
   filter(tgt2050 != "Npi") %>%
-  mutate(target = "Direct\nElectrification") %>%
+  mutate(target = "Electricity\nShare in\nFinal Energy") %>%
   group_by(period) %>% 
@@
   theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(size = theme.double.text.size))
+  theme(axis.text.x = element_text(size = theme.double.text.size)) +
+  geom_text(data=data.frame(period=c(2030,2040),label=c("(Mt CO2/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.05, na.rm = TRUE)
 
@@
   g[["Emissions reductions"]] + theme(strip.text.x = element_blank()) + theme(plot.margin=margin(b=20, l = 30)), #+ theme(plot.margin=margin(10,10,30,10)),margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
-  g[["Energy savings"]] + theme(plot.margin=margin(b=20, l = 57)),
+  g[["Energy savings"]] + theme(plot.margin=margin(b=20, l = 10)),
   g[["Renewables share"]] + theme(plot.margin=margin(b=20, l = 15)),
@@
   g[["Carbon Capture and Storage"]] + theme(plot.margin=margin(b=20, l = 15)),
-  g[["Novel CDR"]] + theme(plot.margin=margin(b=20, l = 25)),
+  g[["Novel CDR"]] + theme(plot.margin=margin(b=20, l = 30)),
   g[["Direct Electrification"]] + theme(plot.margin=margin(b=20, l = 19)),

### 2023-06-22 R/efficiencyTarget.R

@@ -15,8 +15,10 @@
 # conversion factor
 Mtoe2TWa <- 41.868 * 0.001 * (1/31.526) # GJ/toe * (Mtoe/toe*EJ/GJ = 1e6/1e9) * EJ/TWa
 
+referenceScenario2020 <- (787/(1-0.09) + 750/(1-0.13)) / 2
+
 effTgt <- data.frame(target = c("reference","FitFor55 eff","RePowerEU eff"), #,"FitFor55 rev eff","RePowerEU rev eff"
                      Final_Energy_Mtoe = c(846, 787, 750)) %>% #, round(748), round(712))) %>%
-  mutate(Final_Energy_Twa = c(round(Final_Energy_Mtoe*Mtoe2TWa,4)))
-
-#846*Mtoe2TWa
+  mutate(
+    Final_Energy_Twa = c(round(Final_Energy_Mtoe*Mtoe2TWa,4)),
+    reduction_from_2020_Reference_Scenario = round(1-(Final_Energy_Mtoe/referenceScenario2020),2))

### 2023-06-22 paperCharts.Rmd
Update LDV sales plot

--- 2023-06-15 paperCharts.Rmd
@@
   "Hybrid Electric" =	"#F37A5E",
-  "Liquids" = "#282828",
-  "Gases" = "#F7EFE8" 
+  "Gases" = "#F7EFE8", 
+  "Liquids" = "#282828"
 )
@@
   mutate(variable = factor(variable, levels=vars))
+
+salestot <- df %>% 
+  filter(region == "EU27", period >= 2020, period <= 2060, scenario == mainScen, variable == "Sales|Transport|LDV") %>% 
+  group_by(period, value) %>%
+  summarize(.groups = "keep") %>%
+  rename(tot = value)
+
+plotData <- 
+  inner_join(plotData, salestot, by = "period") %>%
+  mutate(value = value/tot, by = "period")
 
@@
   mutate(variable = "ICE Stock")
-stockData$value <- stockData$value/10
+
+totstockData <- df %>% 
+  filter(region == "EU27", period >= 2020, period <= 2060, scenario == mainScen, variable == "Stock|Transport|LDV") %>% 
+  group_by(period, value) %>%
+  summarize(.groups = "keep") %>%
+  rename(tot = value)
+
+stockData <- 
+  inner_join(stockData,totstockData, by = "period") %>% 
+  summarize(value = value/tot) %>%
+  mutate(variable = "ICE Stock")
 
@@
  #theme(axis.title.y = element_blank()) +
- scale_y_continuous(name = "Sales", # - Million vehicles", 
+ scale_y_continuous(limits = c(0, 1.1), breaks=c(0,1), name = "Sales", # - Million vehicles", 
                      #breaks = c(round(emi1990), round(emi1990*0.6), round(emi1990*0.45), round(emi1990*0.3), round(emi1990*0.15), 0),
-                     sec.axis = sec_axis( trans=~.*10, name="Stock")) +
+                     sec.axis = sec_axis( trans=~.*1, name="Stock")) +
                                           #, labels = scales::percent, breaks = c(1,0.4,0.55,0.7,0.85, 0))) +

### 2023-06-22 paperCharts.Rmd
additional paper numbers and target charts

--- 2023-06-22 paperCharts.Rmd
@@
 ```{r, echo=FALSE}
+
+indirect_electrification <- data.frame(
+  indirect_electrification_EJ = c("total","buildings","transport","industry"),
+  reference_value=c(
+    round(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Hydrogen","FE|Gases|Hydrogen","FE|Liquids|Hydrogen"), scenario == mainScen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value),1),
+    round(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Buildings|Hydrogen","FE|Buildings|Gases|Hydrogen","FE|Buildings|Liquids|Hydrogen"), scenario == mainScen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value),1),
+    round(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Transport|Hydrogen","FE|Transport|Gases|Hydrogen","FE|Transport|Liquids|Hydrogen"), scenario == mainScen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value),1),
+    round(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Industry|Hydrogen","FE|Industry|Gases|Hydrogen","FE|Industry|Liquids|Hydrogen"), scenario == mainScen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value),1)
+  ),
+  min=c(
+    round(min(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Hydrogen","FE|Gases|Hydrogen","FE|Liquids|Hydrogen"), tgt2030 %in% tgt2030Scen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value)),1),
+    round(min(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Buildings|Hydrogen","FE|Buildings|Gases|Hydrogen","FE|Buildings|Liquids|Hydrogen"), tgt2030 %in% tgt2030Scen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value)),1),
+    round(min(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Transport|Hydrogen","FE|Transport|Gases|Hydrogen","FE|Transport|Liquids|Hydrogen"), tgt2030 %in% tgt2030Scen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value)),1),
+    round(min(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Industry|Hydrogen","FE|Industry|Gases|Hydrogen","FE|Industry|Liquids|Hydrogen"), tgt2030 %in% tgt2030Scen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value)),1)
+  ),
+  max=c(
+    round(max(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Hydrogen","FE|Gases|Hydrogen","FE|Liquids|Hydrogen"), tgt2030 %in% tgt2030Scen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value)),1),
+    round(max(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Buildings|Hydrogen","FE|Buildings|Gases|Hydrogen","FE|Buildings|Liquids|Hydrogen"), tgt2030 %in% tgt2030Scen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value)),1),
+    round(max(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Transport|Hydrogen","FE|Transport|Gases|Hydrogen","FE|Transport|Liquids|Hydrogen"), tgt2030 %in% tgt2030Scen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value)),1),
+    round(max(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Industry|Hydrogen","FE|Industry|Gases|Hydrogen","FE|Industry|Liquids|Hydrogen"), tgt2030 %in% tgt2030Scen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value)),1)
+  )
+)
+
+electricity_demand_increase <- left_join(
+  df %>%
+  filter(region == "EU27", period %in% c(2030,2040), variable %in% c("FE|Electricity"), tgt2050 != "Npi")
+  ,
+  df %>%
+  filter(region == "EU27", period == 2020, variable %in% c("FE|Electricity"), tgt2050 != "Npi") %>%
+  mutate(base = value,.groups = "keep") %>%
+  select(scenario,base)
+  , by = join_by(scenario == scenario)
+) %>%
+  mutate(upscale = value/base)
+
+electricity_demand_upscale <- data.frame(
+  wind_and_Solar_gen_upscale=c("2030","2040"),
+  reference_value=c(
+    round(electricity_demand_increase %>% filter(scenario == mainScen, period == "2030") %>% pull(upscale)*100),
+    round(electricity_demand_increase %>% filter(scenario == mainScen, period == "2040") %>% pull(upscale)*100)
+    ),
+  min = c(
+   round(min(electricity_demand_increase %>% filter(tgt2030 %in% tgt2030Scen, period == "2030") %>% pull(upscale)*100)),
+   round(min(electricity_demand_increase %>% filter(tgt2030 %in% tgt2030Scen, period == "2040") %>% pull(upscale)*100))
+   ),
+  max = c(
+   round(max(electricity_demand_increase %>% filter(tgt2030 %in% tgt2030Scen, period == "2030") %>% pull(upscale)*100)),
+   round(max(electricity_demand_increase %>% filter(tgt2030 %in% tgt2030Scen, period == "2040") %>% pull(upscale)*100))
+   )
+)
+
+electricity_share_in_FE <- data.frame(
+  electricity_share_in_FE = c("2040"),
+  reference_value=c(
+    round(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share"), scenario == mainScen) %>% pull(value)*100)
+  ),
+  min=c(
+    round(min(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100))
+  ),
+  max=c(
+    round(max(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100))
+  )
+)
+
+wind_and_Solar_gen_upscale <- left_join(
+  df %>%
+  filter(region == "EU27", period %in% c(2030,2040), variable %in% c("SE|Electricity|Wind|Offshore", "SE|Electricity|Wind|Onshore", "SE|Electricity|Solar|PV", "SE|Electricity|Solar|CSP"), tgt2050 != "Npi") %>%
+  group_by(scenario,tgt2030,period) %>%
+  summarize(value = sum(value),.groups = "keep")
+  ,
+  df %>%
+  filter(region == "EU27", period == 2020, variable %in% c("SE|Electricity|Wind|Offshore", "SE|Electricity|Wind|Onshore", "SE|Electricity|Solar|PV", "SE|Electricity|Solar|CSP"), tgt2050 != "Npi") %>%
+  group_by(scenario,tgt2030) %>%
+  summarize(base = sum(value),.groups = "keep")
+  , by = join_by(scenario == scenario, tgt2030 == tgt2030)
+) %>%
+  mutate(upscale = value/base)
+
+gen_upscale <- data.frame(
+  wind_and_Solar_gen_upscale=c("2030","2040"),
+  reference_value=c(
+    round(wind_and_Solar_gen_upscale %>% filter(scenario == mainScen, period == "2030") %>% pull(upscale),1),
+    round(wind_and_Solar_gen_upscale %>% filter(scenario == mainScen, period == "2040") %>% pull(upscale),1)
+    ),
+  min = c(
+   round(min(wind_and_Solar_gen_upscale %>% filter(tgt2030 %in% tgt2030Scen, period == "2030") %>% pull(upscale)),1),
+   round(min(wind_and_Solar_gen_upscale %>% filter(tgt2030 %in% tgt2030Scen, period == "2040") %>% pull(upscale)),1)
+   ),
+  max = c(
+   round(max(wind_and_Solar_gen_upscale %>% filter(tgt2030 %in% tgt2030Scen, period == "2030") %>% pull(upscale)),1),
+   round(max(wind_and_Solar_gen_upscale %>% filter(tgt2030 %in% tgt2030Scen, period == "2040") %>% pull(upscale)),1)
+   )
+)
 
@@
 
+indirect_electrification %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+electricity_demand_upscale %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+electricity_share_in_FE %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+gen_upscale %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
 Generation %>% 
@@
     round(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", scenario == mainScen) %>% pull(value)),
-    round(rateCCS %>% filter(scenario == mainScen) %>% pull(rate)*100),
-    round(rateCDR %>% filter(scenario == mainScen) %>% pull(rate)*100),
+    round((rateCCS %>% filter(scenario == mainScen) %>% pull(rate)-1)*100),
+    round((rateCDR %>% filter(scenario == mainScen) %>% pull(rate)-1)*100),
     round(totalCDR %>% filter(period == 2040, scenario == mainScen) %>% pull(value))
@@
     round(min(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
-    round(min(rateCCS %>% pull(rate))*100),
-    round(min(rateCDR %>% pull(rate))*100),
+    round((min(rateCCS %>% pull(rate))-1)*100),
+    round((min(rateCDR %>% pull(rate))-1)*100),
     round(min(totalCDR %>% pull(value)))
@@
     round(max(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
-    round(max(rateCCS %>% pull(rate))*100),
-    round(max(rateCDR %>% pull(rate))*100),
+    round((max(rateCCS %>% pull(rate))-1)*100),
+    round((max(rateCDR %>% pull(rate))-1)*100),
     round(max(totalCDR %>% pull(value)))
@@
   "Gases"="FE|Gases"
+  #"Syngas" = "FE|Gases|Hydrogen",
+  #"Biogas" = "FE|Gases|Biomass",
+  #"Natural gas" = "FE|Gases|Fossil"
 )
@@
 plotData <- df %>% 
-  filter(region == "EU27", period %in% c(2020,2030,2040,2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
+  filter(region == "EU27", period %in% c(2020,2030,2040,2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars), tgt2050 != "Npi") %>% 
   mutate(variable = factor(variable, levels=vars))  %>% 
-  filter(tgt2050 != "Npi")  %>%
   group_by(model,scenario,region,period) %>% 
@@
 ggsave(paste0(outFolder,"/FE Gases.png"), g[["FE Gases"]] , device="png", width = 6, height = 4, dpi=300, units = "in")
+
+# vars <- c(
+#   "Hydrogen"="FE|Hydrogen",
+#   #"Gases"="FE|Gases"
+#   "Syngas" = "FE|Gases|Hydrogen",
+#   "Biogas" = "FE|Gases|Biomass",
+#   "Natural gas" = "FE|Gases|Fossil"
+# )
+# 
+# plotData <- df %>% 
+#   filter(region == "EU27", period %in% c(2020,2030,2040,2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars), tgt2050 != "Npi") %>% 
+#   mutate(variable = factor(variable, levels=vars))  %>% 
+#   group_by(model,scenario,region,period,bioLim) %>% 
+#   mutate(cumsum = cumsum(value),
+#          sum = sum(value)) %>% 
+#   group_by(model,region,variable,period,bioLim) %>% 
+#   mutate(ribbon.max=max(cumsum),
+#          ribbon.min=min(cumsum)) %>% 
+#   group_by(model,region,period) %>% 
+#   mutate(ribbon.max.total=max(sum),
+#          ribbon.min.total=min(sum))
+# 
+#   
+# g[["FE Gases"]] <- 
+#   ggplot(plotData,aes(x=period,y=value)) +
+#   geom_col(data=plotData %>% filter(scenario %in% c(mainScen,"Nzero_55_bio12")), aes(fill = variable, alpha=factor(period))) +
+#   #geom_errorbar(data=plotData %>% filter(period != 2020), aes(ymin=ribbon.min, ymax=ribbon.max, group=variable), width=8, colour="black", alpha=0.9, size=1,position = position_dodge(width=2)) +
+#   geom_errorbar(data=plotData %>% filter(period != 2020, variable == vars[1], scenario %in%  c(mainScen,"Nzero_55_bio12")), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, linewidth=1,position = position_dodge(width=2)) +
+#   # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
+#   coord_flip() +
+#   facet_grid(bioLim~.) +
+#   theme_doubleColumn() +
+#   theme(panel.grid.minor.x = element_blank(),
+#         panel.grid.major.y = element_blank()) +
+#   #guides(y = "none") +
+#   theme(axis.title.y=element_blank()) +
+#   #theme(legend.position = "none") #+
+#   scale_fill_manual(values = setNames(options$aesthetics$legend$color[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(reverse = TRUE, nrow = 1)) +
+#   scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
+#   theme(legend.text=element_text(size=theme.double.text.size)) +
+#   theme(legend.key.height = unit(0.7, "cm"),
+#     legend.key.width = unit(0.7,"cm")) +
+#   scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == 2020) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2030) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value)),1))) +
+#   #scale_x_reverse()
+#   theme(legend.margin=margin(l = -2, unit='cm'))
 
@@
   theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(size = theme.double.text.size)) +
+  theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
   geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.4, na.rm = TRUE)
@@
   geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Final Energy\nDemand", y = 750, label = "FitFor55", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
+  annotate("text", x = "Final Energy\nDemand", y = 787, label = "FitFor55", angle=90, vjust = 1.5, hjust = 1, color = "black", alpha = 0.5) +
   geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Final Energy\nDemand", y = 787, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0.7, color = "black", alpha = 0.5) +
+  annotate("text", x = "Final Energy\nDemand", y = 750, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0.7, color = "black", alpha = 0.5) +
   facet_grid(target~period, scales="free") +
@@
   theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(size = theme.double.text.size)) +
+  theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
   geom_text(data=data.frame(period=c(2030,2040),label=c("(Mtoe)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.2, na.rm = TRUE)
+
+# Electricity Demand
+plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "FE|Electricity") %>% select(-variable) %>%
+  mutate(value = round(value * 1/0.0036)) %>%
+  filter(tgt2050 != "Npi") %>%
+  mutate(target = "Electricity\nDemand") %>%
+  group_by(period) %>% 
+  mutate(min = min(value),
+        max = max(value))
+
+g[["Electricity Demand"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
+  geom_boxplot(outlier.shape = NA, width=0.6) +
+  geom_hline(yintercept=2641, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = "Electricity\nDemand", y = 2641, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5) +
+  facet_grid(target~period, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  theme(strip.text.x = element_blank()) +
+  expand_limits(y=c(0,5000)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
+  geom_text(data=data.frame(period=c(2030,2040),label=c("(TWh)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.2, na.rm = TRUE)
 
@@
   theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(size = theme.double.text.size)) +
+  theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
   geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.4, na.rm = TRUE)
 
-#
+# Wind
+plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Cap|Electricity|Wind") %>% select(-variable) %>%
+  filter(tgt2050 != "Npi") %>%
+  mutate(target = "Wind\ncapacity") %>%
+  group_by(period) %>% 
+  mutate(min = min(value),
+        max = max(value))
+
+#target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2025,2030),value=c(320,600)) 
+g[["Wind capacity"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
+  geom_boxplot(outlier.shape = NA, width=0.6) +
+  geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = "Wind\ncapacity", y = 255, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5) +
+  facet_grid(target~period, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  theme(strip.text.x = element_blank()) +
+  expand_limits(y=c(0,1000)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
+  geom_text(data=data.frame(period=c(2030,2040),label=c("(GW)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.3, na.rm = TRUE)
 
@@
   annotate("text", x = "Solar\nphotovoltaics", y = 600, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0.6, color = "black", alpha = 0.5) +
+  geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = "Solar\nphotovoltaics", y = 208.9, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5) +
   facet_grid(target~period, scales="free") +
@@
   theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(size = theme.double.text.size)) +
+  theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
   geom_text(data=data.frame(period=c(2030,2040),label=c("(GW)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.3, na.rm = TRUE)
@@
   theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(size = theme.double.text.size)) +
+  theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
   geom_text(data=data.frame(period=c(2030,2040),label=c("(Mt CO2/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.1, na.rm = TRUE)
@@
   theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(size = theme.double.text.size)) +
+  theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
   geom_text(data=data.frame(period=c(2030,2040),label=c("(Mt CO2/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.05, na.rm = TRUE)
@@
   g[["Energy savings"]] + theme(plot.margin=margin(b=20, l = 10)),
-  g[["Renewables share"]] + theme(plot.margin=margin(b=20, l = 15)),
+  g[["Electricity Demand"]] + theme(plot.margin=margin(b=20, l = 35)),
+  g[["Renewables Share"]] + theme(plot.margin=margin(b=20, l = 15)),
+  g[["Wind capacity"]] + theme(plot.margin=margin(b=20, l = 50)),
   g[["Solar photovoltaics"]] + theme(plot.margin=margin(b=20, l = 10)),
   g[["Carbon Capture and Storage"]] + theme(plot.margin=margin(b=20, l = 15)),
-  g[["Novel CDR"]] + theme(plot.margin=margin(b=20, l = 30)),
-  g[["Direct Electrification"]] + theme(plot.margin=margin(b=20, l = 19)),
+  g[["Novel CDR"]] + theme(plot.margin=margin(b=20, l = 27)),
+  g[["Direct Electrification"]] + theme(plot.margin=margin(b=20, l = 17)),
   g[["Carbon-free electricity share"]] + theme(plot.margin=margin(b=20, l = 24)),

### 2023-06-22 R/aesthetics.R

@@ -41,6 +41,10 @@ options$aesthetics <- list(
       "Gases - Fossil"  = "#999959", # #a1a161",
       "Gases - Biomass" = "#999959", # "#999959",
       "Gases - Efuel"   = "#999959", # "#caca8a",
+      "Syngas"   = "#fef3da", # "#caca8a",
+      "Biogas" = "#00cc00", # "#999959",
+      "Natural gas"  = "#999959", # #a1a161",
+      
       "Heat"        = "#cc0000",
       "Hydrogen"    = "#5ed5b0",
       "Liquids"     = "#0000cc",

### 2023-06-23 paperCharts.Rmd
version submitted to EU feedback on climate target for 2040

@@
 
-mainScen <- "Nzero_55_bio7p5" # "Nzero_55_ff55Eff_bio7p5" #Nzero_55_ff55Eff_bio12" # #Nzero_55_bio12" #"Nzero_55_ff55Eff_bio12"
+mainScen <- "Nzero_57_bio7p5" # "Nzero_55_ff55Eff_bio7p5" #Nzero_55_ff55Eff_bio12" # #Nzero_55_bio12" #"Nzero_55_ff55Eff_bio12"
 
@@
 electricity_demand_upscale <- data.frame(
-  wind_and_Solar_gen_upscale=c("2030","2040"),
+  electricity_demand_upscale=c("2030","2040"),
   reference_value=c(
@@
 Generation <- data.frame(
-  Electricity_Generation=c("coal_in_generation_(%)","gas_in_generation_(%)","nuclear_in_generation_(%)","wind_and_Solar_gen_(%)","wind_and_Solar_cap_(TW)"),
+  Electricity_Generation=c("coal_in_generation_(%)","gas_in_generation_(%)","nuclear_in_generation_(%)","wind_and_Solar_gen_(%)","wind_and_Solar_cap_(TW)"), #,"Solar_gen_(TWh)_2030","Solar_gen_(TWh)_2040"
   reference_value=c(
@@
     round(wind_and_Solar_gen %>% filter(scenario == mainScen) %>% pull(percentage)*100,1),
-    round(wind_and_Solar_cap %>% filter(scenario == mainScen) %>% pull(value)/ 1000,1)
-
+    round(wind_and_Solar_cap %>% filter(scenario == mainScen) %>% pull(value)/ 1000,1)#,
+    #round(df %>% filter(region == "EU27", period == 2030, variable == "SE|Electricity|Solar", scenario == mainScen) %>% mutate(value = round(value * 1/0.0036)) %>% pull(value)/1000,2),
+    #round(df %>% filter(region == "EU27", period == 2045, variable == "SE|Electricity|Solar", scenario == mainScen) %>% mutate(value = round(value * 1/0.0036)) %>% pull(value)/1000,2)
     ),
@@
   "Hybrid Electric" =	"#F37A5E",
-  "Gases" = "#F7EFE8", 
+  "Gases" = "#dddddd" , #"#F7EFE8", 
   "Liquids" = "#282828"
@@
 # geom_line(data=h,linetype="dashed", linewidth = 1, color="black") +
- geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 1) +
+ geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
  geom_label_repel(data=data.frame(period=2030,value=stockData %>% filter(period == 2030) %>% pull(value)), label = "Stock",
@@
                   nudge_x = 5,
-                  nudge_y = 5,
+                  nudge_y = 0.05,
                   #nudge_y = -0.02,
@@
  #theme(axis.title.y = element_blank()) +
- scale_y_continuous(limits = c(0, 1.1), breaks=c(0,1), name = "Sales", # - Million vehicles", 
-                     #breaks = c(round(emi1990), round(emi1990*0.6), round(emi1990*0.45), round(emi1990*0.3), round(emi1990*0.15), 0),
-                     sec.axis = sec_axis( trans=~.*1, name="Stock")) +
+scale_y_continuous(limits = c(0, 1.1), breaks=c(0,1), labels = scales::percent, name = "Sales") +
                                           #, labels = scales::percent, breaks = c(1,0.4,0.55,0.7,0.85, 0))) +
+  # scale_y_continuous(limits = c(0, 1.1), breaks=c(0,1), labels = scales::percent, name = "Sales", # - Million vehicles", 
+ #                     #breaks = c(round(emi1990), round(emi1990*0.6), round(emi1990*0.45), round(emi1990*0.3), round(emi1990*0.15), 0),
+ #                     sec.axis = sec_axis( trans=~.*1, breaks=c(0,1), name="Stock", labels = scales::percent)) +
+ #                                          #, labels = scales::percent, breaks = c(1,0.4,0.55,0.7,0.85, 0))) +
   theme(legend.text=element_text(size=theme.double.text.size),
-        legend.spacing.x = unit(0.2, 'cm'))  +
+        legend.spacing.x = unit(0.4, 'cm'))  +
   guides(color = "none") +
-  theme(axis.title.y = element_text(colour = "#666666"))
+  theme(axis.title.y = element_text(colour = "#666666")) +
+  theme(legend.text=element_text(size=theme.single.text.size)) +
+  theme(legend.key.height = unit(0.7, "cm"),
+    legend.key.width = unit(0.7,"cm")) +
+  theme(axis.title.y = element_blank()) +
+  theme(legend.margin=margin(t = -0.4, unit='cm'))
 
@@
 
-ggsave(paste0(outFolder,"/LDV Sales.svg"), g[["LDV Sales"]] , device="svg", width = 6, height = 5, dpi=100, units = "in")
-ggsave(paste0(outFolder,"/LDV Sales.png"), g[["LDV Sales"]] , device="png", width = 6, height = 5, dpi=300, units = "in")
-
-```
-
-```{r, echo=FALSE, fig.width=6, fig.height=5}
+ggsave(paste0(outFolder,"/LDV Sales.svg"), g[["LDV Sales"]] , device="svg", width = 6, height = 4.5, dpi=100, units = "in")
+ggsave(paste0(outFolder,"/LDV Sales.png"), g[["LDV Sales"]] , device="png", width = 6, height = 4.5, dpi=300, units = "in")
+
+```
+
+```{r, echo=FALSE, fig.width=6, fig.height=4.5}
 

### 2023-07-21 paperCharts.Rmd
first submission

@@
 ---
-title: "2040 greenhouse gas reduction targets"
+title: "2040 greenhouse gas reduction targets and energy transitions in line with the EU Green Deal"
 output:
@@
 
-Rodrigues, R., Pietzcker, R., Luderer, G., Sitarz, J., Merfort, A., Hasse, R., Hoppe, J., Pehl, M., Ershad, A.
-M., Baumstark, L.
+Rodrigues, R., Pietzcker, R., Sitarz, J., Merfort, A., Hasse, R., Hoppe, J., Pehl, M., Ershad, A.
+M., Baumstark, L., Luderer, G.
 2040 greenhouse gas reduction targets and energy transitions in line with the EU Green Deal.
-in preparation (2023).
+under revision (2023).
 
@@
 electricity_share_in_FE <- data.frame(
-  electricity_share_in_FE = c("2040"),
+  electricity_share_in_FE = c("2030","2040"),
   reference_value=c(
+    round(df %>% filter(region == "EU27", period == 2030, variable %in% c("Final Energy|Electricity Share"), scenario == mainScen) %>% pull(value)*100),
     round(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share"), scenario == mainScen) %>% pull(value)*100)
@@
   min=c(
+    round(min(df %>% filter(region == "EU27", period == 2030, variable %in% c("Final Energy|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100)),
     round(min(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100))
@@
   max=c(
+    round(max(df %>% filter(region == "EU27", period == 2030, variable %in% c("Final Energy|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100)),
     round(max(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100))
@@
    round(max(wind_and_Solar_gen_upscale %>% filter(tgt2030 %in% tgt2030Scen, period == "2040") %>% pull(upscale)),1)
+   )
+)
+
+wind_and_Solar_participation <- left_join(
+  df %>%
+  filter(region == "EU27", period == 2040, variable %in% c("SE|Electricity|Wind|Offshore", "SE|Electricity|Wind|Onshore", "SE|Electricity|Solar|PV", "SE|Electricity|Solar|CSP"), tgt2030 %in% tgt2030Scen) %>%
+  group_by(scenario,period) %>%
+  summarize(value = sum(value),.groups = "keep") %>%
+  select(scenario,period,value)
+  ,
+  df %>%
+  filter(region == "EU27", period == 2040, variable == "SE|Electricity", tgt2030 %in% tgt2030Scen) %>%
+  mutate(total = value) %>%  
+  select(scenario,period,total)
+  , by = join_by(scenario == scenario,period == period)
+) %>%
+  mutate(pctg = value/total)
+
+wind_and_Solar_participation <- data.frame(
+  result=c("Wind_and_Solar_participation_2040_%"),
+  reference_value=c(
+    round((wind_and_Solar_participation %>% filter(scenario == mainScen) %>% pull(pctg))*100)
+  ),
+  min = c(
+    round((min(wind_and_Solar_participation %>% pull(pctg)))*100)
+  ),
+  max = c(
+    round((max(wind_and_Solar_participation %>% pull(pctg)))*100)
   )
@@
 
+BEVs_in_LDV_data <- left_join(
+  df %>% 
+  filter(region == "EU27", period == 2040, variable %in% c("Stock|Transport|LDV|BEV"), tgt2030 %in% tgt2030Scen) %>%
+  group_by(scenario) %>%    
+  summarize(value = sum(value),.groups = "keep")
+  ,
+  df %>% 
+  filter(region == "EU27", period == 2040, variable %in% c("Stock|Transport|LDV|BEV","Stock|Transport|LDV|FCEV","Stock|Transport|LDV|Hybrid Electric","Stock|Transport|LDV|Liquids","Stock|Transport|LDV|NG"), tgt2030 %in% tgt2030Scen) %>%
+  group_by(scenario) %>%  
+  summarize(total = sum(value)) %>% 
+  select(scenario,total)  
+  ,
+  by = join_by(scenario == scenario)
+) %>% 
+  mutate(pctg = value/total)
+
+BEVs_in_LDV <- data.frame(
+  FE=c("share_of_EVs_in_LDVs_(%)"),
+  reference_value=c(round(BEVs_in_LDV_data %>% filter(scenario == mainScen) %>% pull(pctg)*100 )),
+  min = c(round(min((BEVs_in_LDV_data %>% pull(pctg)) *100))),
+  max = c(round(max((BEVs_in_LDV_data %>% pull(pctg)) *100)))
+)
+
 ```
@@
 
+wind_and_Solar_participation %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
 Generation %>% 
@@
 share_of_build_FE_in_relation_to_2020 %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+BEVs_in_LDV %>% 
   kbl() %>%
@@
     round((min(rateCDR %>% pull(rate))-1)*100),
-    round(min(totalCDR %>% pull(value)))
+    round(min(totalCDR %>% filter(period == 2040) %>% pull(value)))
   ),
@@
     round((max(rateCDR %>% pull(rate))-1)*100),
-    round(max(totalCDR %>% pull(value)))
+    round(max(totalCDR %>% filter(period == 2040) %>% pull(value)))
   )
@@
 CDR %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+```
+
+---
+
+## Milestones upscaling rates
+
+```{r, echo=FALSE}
+
+# Final Energy
+FEbySector <- left_join(
+  df %>%
+    filter(region == "EU27", period == 2040, variable %in% c("FE|Transport","FE|Buildings","FE|Industry"), tgt2030 %in% tgt2030Scen) %>%
+    mutate(end=value) %>%
+    select(variable,scenario,end)
+  ,
+  df %>%
+    filter(region == "EU27", period == 2020, variable %in% c("FE|Transport","FE|Buildings","FE|Industry"), tgt2030 %in% tgt2030Scen) %>%
+    mutate(base=value) %>%
+    select(variable,scenario,base)
+  , by = join_by(scenario == scenario, variable == variable)
+) %>%
+  mutate(percentage = (end-base)/base)
+
+FEbySector_change <- data.frame(
+  result=c("FE_Transport_change_%","FE_Buildings_change_%","FE_Industry_change_%"),
+  reference_value=c(
+    round((FEbySector %>% filter(scenario == mainScen, variable == "FE|Transport") %>% pull(percentage))*100),
+    round((FEbySector %>% filter(scenario == mainScen, variable == "FE|Buildings") %>% pull(percentage))*100),
+    round((FEbySector %>% filter(scenario == mainScen, variable == "FE|Industry") %>% pull(percentage))*100)
+  ),
+  min = c(
+    round((min(FEbySector %>% filter(variable == "FE|Transport") %>% pull(percentage)))*100),
+    round((min(FEbySector %>% filter(variable == "FE|Buildings") %>% pull(percentage)))*100),
+    round((min(FEbySector %>% filter(variable == "FE|Industry") %>% pull(percentage)))*100)
+  ),
+  max = c(
+    round((max(FEbySector %>% filter(variable == "FE|Transport") %>% pull(percentage)))*100),
+    round((max(FEbySector %>% filter(variable == "FE|Buildings") %>% pull(percentage)))*100),
+    round((max(FEbySector %>% filter(variable == "FE|Industry") %>% pull(percentage)))*100)
+  )
+)
+
+# Renewables Share in Final Energy
+rate2030_2040RenewablesShare <- left_join(
+  df %>%
+    filter(region == "EU27", period == 2040, variable == "SE|Renewables Share", tgt2030 %in% tgt2030Scen) %>%
+    mutate(numerator=value) %>%
+    select(scenario,numerator)
+  ,
+  df %>%
+    filter(region == "EU27", period == 2030, variable == "SE|Renewables Share", tgt2030 %in% tgt2030Scen) %>%
+    mutate(denominator=value) %>%
+    select(scenario,denominator)
+  , by = join_by(scenario == scenario)
+) %>%
+  mutate(percentage = numerator/denominator,
+         rate = percentage ^ (1/10))
+
+rate2021_2030RenewablesShare <- 
+  df %>%
+    filter(region == "EU27", period == 2030, variable == "SE|Renewables Share", tgt2030 %in% tgt2030Scen) %>%
+    mutate(numerator=value) %>%
+    select(scenario,numerator) %>%
+    mutate(denominator=addHist$res %>% filter(type == "RES", period == 2021) %>% pull(value)) %>%
+    mutate(percentage = numerator/denominator,
+           rate = percentage ^ (1/9))
+
+renewablesShare <- data.frame(
+  result=c("Renewables_Share_upscaling_rates_2021_to_2030_%","Renewables_Share_upscaling_rates_2030_to_2040_%"),
+  reference_value=c(
+    round((rate2021_2030RenewablesShare %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
+    round((rate2030_2040RenewablesShare %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1)
+  ),
+  min = c(
+    round((min(rate2021_2030RenewablesShare %>% pull(rate))-1)*100,1),
+    round((min(rate2030_2040RenewablesShare %>% pull(rate))-1)*100,1)
+  ),
+  max = c(
+    round((max(rate2021_2030RenewablesShare %>% pull(rate))-1)*100,1),
+    round((max(rate2030_2040RenewablesShare %>% pull(rate))-1)*100,1)
+  )
+)
+
+# Electricity Share in Final Energy
+rate2030_2040ElectricityShare <- left_join(
+  df %>%
+    filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share","Final Energy|Transport|Electricity Share","Final Energy|Industry|Electricity Share","Final Energy|Buildings|Electricity Share"), tgt2030 %in% tgt2030Scen) %>%
+    mutate(numerator=value) %>%
+    select(variable,scenario,numerator)
+  ,
+  df %>%
+    filter(region == "EU27", period == 2030, variable %in% c("Final Energy|Electricity Share","Final Energy|Transport|Electricity Share","Final Energy|Industry|Electricity Share","Final Energy|Buildings|Electricity Share"), tgt2030 %in% tgt2030Scen) %>%
+    mutate(denominator=value) %>%
+    select(variable,scenario,denominator)
+  , by = join_by(scenario == scenario, variable == variable)
+) %>%
+  mutate(percentage = numerator/denominator,
+         rate = percentage ^ (1/10))
+
+#estimation of historical share in 2021 for FE electricity / FE with non-energy use and with bunkers
+h <- (
+      2550461.10 *1000 / 8.76E+09 * 31.536  # https://ec.europa.eu/eurostat/databrowser/bookmark/12d54df4-7c35-47eb-a103-dd8994d26b80?lang=en
+     ) / (
+      addHist$FE_consumption %>% mutate(value = value/1000000) %>% filter(period==2021) %>% pull(value) + # FE|w/o Non-energy Use w/o Bunkers - EJ
+      df %>% filter(region == "EU27", period == 2020, scenario == "Npi", variable == "FE|Transport|Bunkers") %>% pull(value) +
+      df %>% filter(region == "EU27", period == 2020, scenario == "Npi", variable == "FE|Non-energy Use|Industry") %>% pull(value)
+     )
+
+rate2021_2030ElectricityShare <- 
+  df %>%
+    filter(region == "EU27", period == 2030, variable == "Final Energy|Electricity Share", tgt2030 %in% tgt2030Scen) %>%
+    mutate(numerator=value) %>%
+    select(scenario,numerator) %>%
+    mutate(denominator=h) %>%
+    mutate(percentage = numerator/denominator,
+           rate = percentage ^ (1/9))
+
+ElectricityShare <- data.frame(
+  result=c("Electricity_Share_upscaling_rates_2021_to_2030_%","Electricity_Share_upscaling_rates_2030_to_2040_%","Transport_Electricity_Share_upscaling_rates_2030_to_2040_%","Buildings_Electricity_Share_upscaling_rates_2030_to_2040_%","Industry_Electricity_Share_upscaling_rates_2030_to_2040_%"),
+  reference_value=c(
+    round((rate2021_2030ElectricityShare %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
+    round((rate2030_2040ElectricityShare %>% filter(scenario == mainScen, variable == "Final Energy|Electricity Share") %>% pull(rate)-1)*100,1),
+    round((rate2030_2040ElectricityShare %>% filter(scenario == mainScen, variable == "Final Energy|Transport|Electricity Share") %>% pull(rate)-1)*100,1),
+    round((rate2030_2040ElectricityShare %>% filter(scenario == mainScen, variable == "Final Energy|Buildings|Electricity Share") %>% pull(rate)-1)*100,1),
+    round((rate2030_2040ElectricityShare %>% filter(scenario == mainScen, variable == "Final Energy|Industry|Electricity Share") %>% pull(rate)-1)*100,1)
+  ),
+  min = c(
+    round((min(rate2021_2030ElectricityShare %>% pull(rate))-1)*100,1),
+    round((min(rate2030_2040ElectricityShare %>% filter(variable == "Final Energy|Electricity Share") %>% pull(rate))-1)*100,1),
+    round((min(rate2030_2040ElectricityShare %>% filter(variable == "Final Energy|Transport|Electricity Share") %>% pull(rate))-1)*100,1),
+    round((min(rate2030_2040ElectricityShare %>% filter(variable == "Final Energy|Buildings|Electricity Share") %>% pull(rate))-1)*100,1),
+    round((min(rate2030_2040ElectricityShare %>% filter(variable == "Final Energy|Industry|Electricity Share") %>% pull(rate))-1)*100,1)
+  ),
+  max = c(
+    round((max(rate2021_2030ElectricityShare %>% pull(rate))-1)*100,1),
+    round((max(rate2030_2040ElectricityShare %>% filter(variable == "Final Energy|Electricity Share") %>% pull(rate))-1)*100,1),
+    round((max(rate2030_2040ElectricityShare %>% filter(variable == "Final Energy|Transport|Electricity Share") %>% pull(rate))-1)*100,1),
+    round((max(rate2030_2040ElectricityShare %>% filter(variable == "Final Energy|Buildings|Electricity Share") %>% pull(rate))-1)*100,1),
+    round((max(rate2030_2040ElectricityShare %>% filter(variable == "Final Energy|Industry|Electricity Share") %>% pull(rate))-1)*100,1)
+  )
+)
+
+# Hydrogen production
+rate2030_2040hydrogenProduction <- left_join(
+  df %>%
+    filter(region == "EU27", period == 2040, variable == "SE|Hydrogen", tgt2030 %in% tgt2030Scen) %>%
+    mutate(numerator=value) %>%
+    select(scenario,numerator)
+  ,
+  df %>%
+    filter(region == "EU27", period == 2030, variable == "SE|Hydrogen", tgt2030 %in% tgt2030Scen) %>%
+    mutate(denominator=value) %>%
+    select(scenario,denominator)
+  , by = join_by(scenario == scenario)
+) %>%
+  mutate(percentage = numerator/denominator,
+         rate = percentage ^ (1/10))
+
+rate2040_2050hydrogenProduction <- left_join(
+  df %>%
+    filter(region == "EU27", period == 2050, variable == "SE|Hydrogen", tgt2030 %in% tgt2030Scen) %>%
+    mutate(numerator=value) %>%
+    select(scenario,numerator)
+  ,
+  df %>%
+    filter(region == "EU27", period == 2040, variable == "SE|Hydrogen", tgt2030 %in% tgt2030Scen) %>%
+    mutate(denominator=value) %>%
+    select(scenario,denominator)
+  , by = join_by(scenario == scenario)
+) %>%
+  mutate(percentage = numerator/denominator,
+         rate = percentage ^ (1/10))
+
+hydrogenProduction <- data.frame(
+  result=c("Hydrogen_upscaling_rates_2030_to_2040_%","Hydrogen_upscaling_rates_2040_to_2050_%"),
+  reference_value=c(
+    round((rate2030_2040hydrogenProduction %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
+    round((rate2040_2050hydrogenProduction %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1)
+  ),
+  min = c(
+    round((min(rate2030_2040hydrogenProduction %>% pull(rate))-1)*100,1),
+    round((min(rate2040_2050hydrogenProduction %>% pull(rate))-1)*100,1)
+  ),
+  max = c(
+    round((max(rate2030_2040hydrogenProduction %>% pull(rate))-1)*100,1),
+    round((max(rate2040_2050hydrogenProduction %>% pull(rate))-1)*100,1)
+  )
+)
+
+# Electricity Demand
+rate2030_2040ElectricityDemand <- left_join(
+  df %>%
+    filter(region == "EU27", period == 2040, variable == "FE|Electricity", tgt2030 %in% tgt2030Scen) %>%
+    mutate(numerator = value * 1/0.0036) %>%
+    select(scenario,numerator)
+  ,
+  df %>%
+    filter(region == "EU27", period == 2030, variable == "FE|Electricity", tgt2030 %in% tgt2030Scen) %>%
+    mutate(denominator = value * 1/0.0036) %>%
+    select(scenario,denominator)
+  , by = join_by(scenario == scenario)
+) %>%
+  mutate(diff = (numerator - denominator)/10,
+         percentage = numerator/denominator,
+         rate = percentage ^ (1/10))
+
+#2022 = 2469471.42 GWh = 2469471.42 *1000 / 8.76E+09 * 31.536 EJ - FE electricity - https://ec.europa.eu/eurostat/databrowser/bookmark/d19a01c7-6099-4b88-8ccd-c6bcc01c3ddc?lang=en
+h <- 2469471.42 /1000
+
+rate2022_2030ElectricityDemand <- 
+  df %>%
+    filter(region == "EU27", period == 2030, variable == "FE|Electricity", tgt2030 %in% tgt2030Scen) %>%
+    mutate(numerator = value * 1/0.0036) %>%
+    select(scenario,numerator) %>%
+    mutate(denominator=h) %>%
+    mutate(diff = (numerator - denominator)/8,
+           percentage = numerator/denominator,
+           rate = percentage ^ (1/8))
+
+rate2020_2030ElectricityDemand <- left_join(
+  df %>%
+    filter(region == "EU27", period == 2030, variable == "FE|Electricity", tgt2030 %in% tgt2030Scen) %>%
+    mutate(numerator = value * 1/0.0036) %>%
+    select(scenario,numerator)
+  ,
+  df %>%
+    filter(region == "EU27", period == 2020, variable == "FE|Electricity", tgt2030 %in% tgt2030Scen) %>%
+    mutate(denominator = value * 1/0.0036) %>%
+    select(scenario,denominator)
+  , by = join_by(scenario == scenario)
+) %>%
+  mutate(diff = (numerator - denominator)/10,
+         percentage = numerator/denominator,
+         rate = percentage ^ (1/10))
+
+ElectricityDemand <- data.frame(
+  result=c("Electricity_Demand_yearly_install_2022_to_2030_(Twh)","Electricity_Demand_yearly_install_2030_to_2040_(Twh)","Electricity_Demand_upscaling_rates_2022_to_2030_%","Electricity_Demand_upscaling_rates_2020_to_2030_%","Electricity_Demand_upscaling_rates_2030_to_2040_%"),
+  reference_value=c(
+    round(rate2022_2030ElectricityDemand %>% filter(scenario == mainScen) %>% pull(diff)),
+    round(rate2030_2040ElectricityDemand %>% filter(scenario == mainScen) %>% pull(diff)),
+    round((rate2022_2030ElectricityDemand %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
+    round((rate2020_2030ElectricityDemand %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
+    round((rate2030_2040ElectricityDemand %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1)
+  ),
+  min = c(
+    round((min(rate2022_2030ElectricityDemand %>% pull(diff)))),
+    round((min(rate2030_2040ElectricityDemand %>% pull(diff)))),
+    round((min(rate2022_2030ElectricityDemand %>% pull(rate))-1)*100,1),
+    round((min(rate2020_2030ElectricityDemand %>% pull(rate))-1)*100,1),
+    round((min(rate2030_2040ElectricityDemand %>% pull(rate))-1)*100,1)
+  ),
+  max = c(
+    round((max(rate2022_2030ElectricityDemand %>% pull(diff)))),
+    round((max(rate2030_2040ElectricityDemand %>% pull(diff)))),
+    round((max(rate2022_2030ElectricityDemand %>% pull(rate))-1)*100,1),
+    round((max(rate2020_2030ElectricityDemand %>% pull(rate))-1)*100,1),
+    round((max(rate2030_2040ElectricityDemand %>% pull(rate))-1)*100,1)
+  )
+)
+
+# # Electricity Supply
+# rate2030_2040ElectricitySupply <- left_join(
+#   df %>%
+#     filter(region == "EU27", period == 2040, variable == "SE|Electricity", tgt2030 %in% tgt2030Scen) %>%
+#     mutate(numerator = value * 1/0.0036) %>%
+#     select(scenario,numerator)
+#   ,
+#   df %>%
+#     filter(region == "EU27", period == 2030, variable == "SE|Electricity", tgt2030 %in% tgt2030Scen) %>%
+#     mutate(denominator = value * 1/0.0036) %>%
+#     select(scenario,denominator)
+#   , by = join_by(scenario == scenario)
+# ) %>%
+#   mutate(percentage = numerator/denominator,
+#          rate = percentage ^ (1/10))
+# 
+# rate2020_2030ElectricitySupply <- left_join(
+#   df %>%
+#     filter(region == "EU27", period == 2030, variable == "SE|Electricity", tgt2030 %in% tgt2030Scen) %>%
+#     mutate(numerator = value * 1/0.0036) %>%
+#     select(scenario,numerator)
+#   ,
+#   df %>%
+#     filter(region == "EU27", period == 2020, variable == "SE|Electricity", tgt2030 %in% tgt2030Scen) %>%
+#     mutate(denominator = value * 1/0.0036) %>%
+#     select(scenario,denominator)
+#   , by = join_by(scenario == scenario)
+# ) %>%
+#   mutate(percentage = numerator/denominator,
+#          rate = percentage ^ (1/10))
+# 
+# # #2022 = 2469471.42 GWh = 2469471.42 *1000 / 8.76E+09 * 31.536 EJ - FE electricity - https://ec.europa.eu/eurostat/databrowser/bookmark/d19a01c7-6099-4b88-8ccd-c6bcc01c3ddc?lang=en
+# # h <- 2469471.42 /1000
+# # 
+# # rate2022_2030ElectricitySupply <- 
+# #   df %>%
+# #     filter(region == "EU27", period == 2030, variable == "SE|Electricity", tgt2030 %in% tgt2030Scen) %>%
+# #     mutate(numerator = value * 1/0.0036) %>%
+# #     select(scenario,numerator) %>%
+# #     mutate(denominator=h) %>%
+# #     mutate(percentage = numerator/denominator,
+# #            rate = percentage ^ (1/8))
+# 
+# ElectricitySupply <- data.frame(
+#   result=c("Electricity_Supply_upscaling_rates_2022_to_2030_%","Electricity_Supply_upscaling_rates_2030_to_2040_%"),
+#   reference_value=c(
+#     round((rate2022_2030ElectricitySupply %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
+#     round((rate2030_2040ElectricitySupply %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1)
+#   ),
+#   min = c(
+#     round((min(rate2022_2030ElectricitySupply %>% pull(rate))-1)*100,1),
+#     round((min(rate2030_2040ElectricitySupply %>% pull(rate))-1)*100,1)
+#   ),
+#   max = c(
+#     round((max(rate2022_2030ElectricitySupply %>% pull(rate))-1)*100,1),
+#     round((max(rate2030_2040ElectricitySupply %>% pull(rate))-1)*100,1)
+#   )
+# )
+
+# Solar Photovoltaics
+rate2030_2040SolarPV <- left_join(
+  df %>%
+    filter(region == "EU27", period == 2040, variable == "Cap|Electricity|Solar|PV", tgt2030 %in% tgt2030Scen) %>%
+    mutate(numerator=value) %>%
+    select(scenario,numerator)
+  ,
+  df %>%
+    filter(region == "EU27", period == 2030, variable == "Cap|Electricity|Solar|PV", tgt2030 %in% tgt2030Scen) %>%
+    mutate(denominator=value) %>%
+    select(scenario,denominator)
+  , by = join_by(scenario == scenario)
+) %>%
+  mutate(percentage = numerator/denominator,
+         rate = percentage ^ (1/10))
+
+rate2022_2030SolarPV <- 
+  df %>%
+    filter(region == "EU27", period == 2030, variable == "Cap|Electricity|Solar|PV", tgt2030 %in% tgt2030Scen) %>%
+    mutate(numerator=value) %>%
+    select(scenario,numerator) %>%
+    mutate(denominator=208.9) %>%
+    mutate(percentage = numerator/denominator,
+           rate = percentage ^ (1/8))
+
+rate2022_2040SolarPV <- 
+  df %>%
+    filter(region == "EU27", period == 2040, variable == "Cap|Electricity|Solar|PV", tgt2030 %in% tgt2030Scen) %>%
+    mutate(numerator=value) %>%
+    select(scenario,numerator) %>%
+    mutate(denominator=208.9) %>%
+    mutate(percentage = numerator/denominator,
+           rate = percentage ^ (1/18))
+
+SolarPV <- data.frame(
+  result=c("SolarPV_2022_vs_2040_X", "SolarPV_upscaling_rates_2030_to_2040_%","SolarPV_upscaling_rates_2022_to_2040_%","SolarPV_upscaling_rates_2022_to_2030_%"),
+  reference_value=c(
+    round((rate2022_2040SolarPV %>% filter(scenario == mainScen) %>% pull(percentage)),1),
+    round((rate2030_2040SolarPV %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
+    round((rate2022_2040SolarPV %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
+    round((rate2022_2030SolarPV %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1)
+  ),
+  min = c(
+    round((min(rate2022_2040SolarPV %>% pull(percentage))),1),
+    round((min(rate2030_2040SolarPV %>% pull(rate))-1)*100,1),
+    round((min(rate2022_2040SolarPV %>% pull(rate))-1)*100,1),
+    round((min(rate2022_2030SolarPV %>% pull(rate))-1)*100,1)
+  ),
+  max = c(
+    round((max(rate2022_2040SolarPV %>% pull(percentage))),1),
+    round((max(rate2030_2040SolarPV %>% pull(rate))-1)*100,1),
+    round((max(rate2022_2040SolarPV %>% pull(rate))-1)*100,1),
+    round((max(rate2022_2030SolarPV %>% pull(rate))-1)*100,1)
+  )
+)
+
+# Wind
+rate2030_2040Wind <- left_join(
+  df %>%
+    filter(region == "EU27", period == 2040, variable == "Cap|Electricity|Wind", tgt2030 %in% tgt2030Scen) %>%
+    mutate(numerator=value) %>%
+    select(scenario,numerator)
+  ,
+  df %>%
+    filter(region == "EU27", period == 2030, variable == "Cap|Electricity|Wind", tgt2030 %in% tgt2030Scen) %>%
+    mutate(denominator=value) %>%
+    select(scenario,denominator)
+  , by = join_by(scenario == scenario)
+) %>%
+  mutate(percentage = numerator/denominator,
+         rate = percentage ^ (1/10))
+
+rate2022_2030Wind <- 
+  df %>%
+    filter(region == "EU27", period == 2030, variable == "Cap|Electricity|Wind", tgt2030 %in% tgt2030Scen) %>%
+    mutate(numerator=value) %>%
+    select(scenario,numerator) %>%
+    mutate(denominator=255) %>%
+    mutate(percentage = numerator/denominator,
+           rate = percentage ^ (1/8))
+
+rate2022_2040Wind <- 
+  df %>%
+    filter(region == "EU27", period == 2040, variable == "Cap|Electricity|Wind", tgt2030 %in% tgt2030Scen) %>%
+    mutate(numerator=value) %>%
+    select(scenario,numerator) %>%
+    mutate(denominator=255) %>%
+    mutate(percentage = numerator/denominator,
+           rate = percentage ^ (1/18))
+
+Wind <- data.frame(
+  result=c("wind_2022_vs_2040_X","Wind_upscaling_rates_2030_to_2040_%","Wind_upscaling_rates_2022_to_2040_%","Wind_upscaling_rates_2022_to_2030_%"),
+  reference_value=c(
+    round((rate2022_2040Wind %>% filter(scenario == mainScen) %>% pull(percentage)),1),
+    round((rate2030_2040Wind %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
+    round((rate2022_2040Wind %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1),
+    round((rate2022_2030Wind %>% filter(scenario == mainScen) %>% pull(rate)-1)*100,1)
+  ),
+  min = c(
+    round((min(rate2022_2040Wind %>% pull(percentage))),1),
+    round((min(rate2030_2040Wind %>% pull(rate))-1)*100,1),
+    round((min(rate2022_2040Wind %>% pull(rate))-1)*100,1),
+    round((min(rate2022_2030Wind %>% pull(rate))-1)*100,1)
+  ),
+  max = c(
+    round((max(rate2022_2040Wind %>% pull(percentage))),1),
+    round((max(rate2030_2040Wind %>% pull(rate))-1)*100,1),
+    round((max(rate2022_2040Wind %>% pull(rate))-1)*100,1),
+    round((max(rate2022_2030Wind %>% pull(rate))-1)*100,1)
+  )
+)
+
+#residual fossils
+residualFossils <- data.frame(
+  result=c("residual_fossil_MtCO2_2030","residual_fossil_MtCO2_2040","residual_fossil_MtCO2_2050"),
+  reference_value=c(
+    round((df %>% filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% filter(scenario == mainScen) %>% pull(value))),
+    round((df %>% filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% filter(scenario == mainScen) %>% pull(value))),
+    round((df %>% filter(region == "EU27", period == 2050, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% filter(scenario == mainScen) %>% pull(value)))
+  ),
+  min = c(
+    round((min(df %>% filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% pull(value)))),
+    round((min(df %>% filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% pull(value)))),
+    round((min(df %>% filter(region == "EU27", period == 2050, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% pull(value))))
+  ),
+  max = c(
+    round((max(df %>% filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% pull(value)))),
+    round((max(df %>% filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% pull(value)))),
+    round((max(df %>% filter(region == "EU27", period == 2050, tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% pull(value))))
+  )
+)
+
+```
+
+```{r, echo=FALSE, fig.width=12, fig.height=5}
+
+renewablesShare %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+ElectricityShare %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+hydrogenProduction %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+ElectricityDemand %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+SolarPV %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+Wind %>% 
   kbl() %>%
@@
 
+linearProjection <- data.frame(period=c(2030,2035,2040,2045,2050),value=((1-seq(0,1,1/4))*(emi1990*(1-0.57))))
+
 g[["GHG emi"]] <- ggplot(plotData, aes(x=period,y=value)) +
@@
     geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min), alpha = 0.5, fill = "#545454") + 
-     geom_segment(data=plotData %>% filter(scenario == mainScen, period == 2040), aes(x=2040, xend=2040, y=0, yend=value), linetype="dashed", color="black") +
     geom_line(data=plotData %>% filter(scenario == mainScen), linewidth=1.5) +
@@
     geom_line(data=h,linewidth=0.7,linetype="dashed") +
+    geom_line(data=linearProjection,linewidth=0.8,linetype="dashed") +
+    #geom_segment(data=plotData %>% filter(scenario == mainScen, period == 2040), aes(x=2040, xend=2040, y=0, yend=value), linetype="dashed", color="black") +
+    geom_segment(data=linearProjection %>% filter(period == 2040), aes(x=2040, xend=2040, y=0, yend=value), linetype="dashed", color="black") +
     geom_point(data=plotData %>% filter(scenario == mainScen, period == 2040),size=3,shape=21,fill="white",stroke=1.5) +
+    geom_point(data=linearProjection %>% filter(period == 2040),size=3,shape=21,fill="white",stroke=1.5) +
+    geom_label_repel(data=data.frame(period=c(2042),value=(((2050-2042)/20)*(emi1990*(1-0.57)))), label = "linear reduction",
+                     nudge_x = 10,
+                     nudge_y = 800,
+                     segment.square = TRUE,
+                     point.padding = 0.6,
+                     hjust = 0,
+                     direction="y",
+                     size = geom.text.double.size*0.9) + 
     theme_doubleColumn() +
@@
   theme(legend.position = "none") +
-  scale_y_continuous(breaks=c(2020,2030,2040), labels=c("today",2030,2040), minor_breaks = NULL, limits=c(2008,2047)) +
+  scale_y_continuous(breaks=c(2020,2030,2040), labels=c("current",2030,2040), minor_breaks = NULL, limits=c(2008,2047)) +
   theme(axis.title.x=element_blank(),
@@
   #annotate(geom = "text", x = 2023, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage - 0.06, label = "and nuclear", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) +
-  annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geom.text.double.size) +
+  #annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geom.text.double.size) +
+  annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, label = "renewables\nand nuclear", color = "#666666",angle = 90, hjust=0.5, vjust=-0.5, size=geom.text.double.size, lineheight = 0.8) +
+  annotate(geom = "text", x = 2020, y = (1-plotDataRenewables[plotDataRenewables$period == 2020,]$percentage)/2+plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "fossil", color = "#666666",angle = 90, hjust=0.5, vjust=-2, size=geom.text.double.size) +
+  annotation_custom(grob = linesGrob(gp=gpar(col="#666666",lwd = 3,lty="dashed")), xmin = 2016, xmax = 2019.8, ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage) +
   theme(axis.text.y=element_blank()) +
@@
         #,legend.margin=margin(l = -2, unit='cm')
-        )
+        ) #+
+  #annotation_custom(
+  #  grob = textGrob(label = "renewables\nand nuclear",hjust=0.5, vjust=-0.5, rot = 90, gp=gpar(col="#666666", fontsize=geom.text.double.size)),
+  #  ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2,
+  #  xmin = 2020, xmax = 2020)
 
@@
 ggsave(paste0(outFolder,"/Electricity Generation.png"), g[["Electricity Generation"]] , device="png", width = 6, height = 10, dpi=300, units = "in")
+
+g[["Electricity Generation - wide"]] <- 
+  ggplot(plotData,aes(x=period,y=percentage)) +
+  geom_area(aes(fill=variable),alpha=0.4) +
+  geom_line(data=plotDataRenewables, linetype = "dashed", linewidth = 1.5, color="#666666") +
+  geom_bar(data=plotData2040,aes(fill=variable),stat='identity', show.legend = FALSE, alpha = 0.7, color="white", width = 3, linewidth = 1.5) +
+  #ggrepel::geom_text_repel(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(round(percentage,2)*100,"%"), y=cumPercentage-percentage/2, x = 2043.5), vjust=0.5, hjust=0.5, na.rm=TRUE, color = "black", size = 12) +
+  #geom_text(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(inv_vars[variable], " (",round(percentage,2)*100,"%)"), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size = 12) +
+  geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geom.text.double.size) +
+  theme_doubleColumn()  +
+  scale_y_continuous(minor_breaks = seq(0.2, 0.8, 0.2), breaks=c(0,1),labels = scales::percent) +
+  scale_x_continuous(breaks=c(2020,2040,2060)) +
+  scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
+  theme(axis.title.y=element_blank()) + 
+  theme(legend.position="right") +
+  theme(legend.key.height = unit(0.8, "cm"),
+    legend.key.width = unit(0.8,"cm")) +
+  theme(legend.margin=margin(b = -2, unit='cm')
+        )
+
+#ggsave(paste0(outFolder_conference,"/Electricity Generation - wide.svg"), g[["Electricity Generation - wide"]] , device="svg", width = 12, height = 5, dpi=100, units = "in")
+#ggsave(paste0(outFolder_conference,"/Electricity Generation - wide.png"), g[["Electricity Generation - wide"]] , device="png", width = 12, height = 5, dpi=300, units = "in")
 
@@
 # Primary Energy
-vars <- c("Biomass" = "PE|Biomass",
+vars <- c("Oil"="PE|Oil",
+          "Gas"="PE|Gas",
           "Coal"="PE|Coal",
-          "Gas"="PE|Gas",
-          "Oil"="PE|Oil")
+          "Biomass" = "PE|Biomass")
 
@@
   filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
+  mutate(variable = factor(variable, levels=vars))  %>% 
   group_by(model,region,variable,period) %>% 
@@
     expand_limits(y=c(0,1)) +
-    guides(color=guide_legend(nrow=2)) +
+    guides(color=guide_legend(nrow=1)) +
     theme(axis.title.y = element_blank()) +
-    expand_limits(y = 30)
+    expand_limits(y = 30) +
+    theme(legend.margin=margin(l = -2, unit='cm'))
     #guides(fill = FALSE)
 
-ggsave(paste0(outFolder,"/Primary Energy.svg"), g[["Primary Energy"]] , device="svg", width = 6, height = 6, dpi=100, units = "in")
-ggsave(paste0(outFolder,"/Primary Energy.png"), g[["Primary Energy"]] , device="png", width = 6, height = 6, dpi=300, units = "in")
+ggsave(paste0(outFolder,"/Primary Energy.svg"), g[["Primary Energy"]] , device="svg", width = 6, height = 5, dpi=100, units = "in")
+ggsave(paste0(outFolder,"/Primary Energy.png"), g[["Primary Energy"]] , device="png", width = 6, height = 5, dpi=300, units = "in")
 
@@
 
-ggsave(paste0(outFolder,"/FE Gases.svg"), g[["FE Gases"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
-ggsave(paste0(outFolder,"/FE Gases.png"), g[["FE Gases"]] , device="png", width = 6, height = 4, dpi=300, units = "in")
+#ggsave(paste0(outFolder,"/FE Gases.svg"), g[["FE Gases"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
+#ggsave(paste0(outFolder,"/FE Gases.png"), g[["FE Gases"]] , device="png", width = 6, height = 4, dpi=300, units = "in")
+
+g[["FE Gases - alt axis"]] <- 
+  ggplot(plotData,aes(x=period,y=value)) +
+  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = variable, alpha=factor(period))) +
+  #geom_errorbar(data=plotData %>% filter(period != 2020), aes(ymin=ribbon.min, ymax=ribbon.max, group=variable), width=8, colour="black", alpha=0.9, size=1,position = position_dodge(width=2)) +
+  geom_errorbar(data=plotData %>% filter(period != 2020, variable == vars[1], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, linewidth=1,position = position_dodge(width=2)) +
+  # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
+  coord_flip() +
+  theme_doubleColumn() +
+  theme(panel.grid.minor.x = element_blank(),
+        panel.grid.major.y = element_blank()) +
+  #guides(y = "none") +
+  theme(axis.title.y=element_blank()) +
+  #theme(legend.position = "none") #+
+  scale_fill_manual(values = setNames(options$aesthetics$legend$color[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(reverse = TRUE, nrow = 1)) +
+  scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
+  theme(legend.text=element_text(size=theme.double.text.size)) +
+  theme(legend.key.height = unit(0.7, "cm"),
+    legend.key.width = unit(0.7,"cm")) +
+  scale_y_continuous(breaks = seq(0,10,2)) +
+  expand_limits(y=c(0,10)) + 
+  #scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == 2020) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2030) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value)),1))) +
+  #scale_x_reverse()
+  theme(legend.margin=margin(l = -2, unit='cm'))
+
+ggsave(paste0(outFolder,"/FE Gases - alt axis.svg"), g[["FE Gases - alt axis"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
+ggsave(paste0(outFolder,"/FE Gases - alt axis.png"), g[["FE Gases - alt axis"]] , device="png", width = 6, height = 4, dpi=300, units = "in")
 
@@
 
-g[["FE Gases"]]
+g[["FE Gases - alt axis"]]
 
@@
 vars <- list(
+ "Oil" = c("Trade|Imports|Oil","Trade|Exports|Oil"),
+ "Gas" = c("Trade|Imports|Gas|Adj","Trade|Exports|Gas|Adj"),
  "Coal" = c("Trade|Imports|Coal","Trade|Exports|Coal"),
- "Oil" = c("Trade|Imports|Oil","Trade|Exports|Oil"),
- "Gas" = c("Trade|Imports|Gas","Trade|Exports|Gas"),
  "Biomass" = c("Trade|Imports|Biomass","Trade|Exports|Biomass")
@@
 
-plotData$carrier <- factor(plotData$carrier, levels=c("Coal","Oil","Gas","Biomass"))
+plotData$carrier <- factor(plotData$carrier, levels=c("Oil","Gas","Coal","Biomass"))
 
@@
 
-ggsave(paste0(outFolder,"/security of supply - fossil.svg"), g[["security of supply - fossil"]] , device="svg", width = 6, height = 6, dpi=100, units = "in")
-ggsave(paste0(outFolder,"/security of supply - fossil.png"), g[["security of supply - fossil"]] , device="png", width = 6, height = 6, dpi=300, units = "in")
+#ggsave(paste0(outFolder,"/security of supply - fossil.svg"), g[["security of supply - fossil"]] , device="svg", width = 6, height = 6, dpi=100, units = "in")
+#ggsave(paste0(outFolder,"/security of supply - fossil.png"), g[["security of supply - fossil"]] , device="png", width = 6, height = 6, dpi=300, units = "in")
+
+g[["security of supply - net fossil"]] <- ggplot(plotDataTotal %>% filter(period <= 2050, carrier != "Biomass"),aes(x=period,y=value)) +
+  geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
+  geom_bar(aes(fill=as.factor(period)),stat='identity', alpha = 0.7) +
+  facet_wrap(~carrier,nrow=1) +
+  theme_doubleColumn()  +
+  theme(axis.title.y=element_blank()) +
+  scale_fill_manual(values = c("2020" = "black", "2030"= "black", "2040" = "#5a788b", "2050" = "black")) +
+  theme(legend.position = "none")
+
+ggsave(paste0(outFolder,"/security of supply - net fossil.svg"), g[["security of supply - net fossil"]] , device="svg", width = 6, height = 4.5, dpi=100, units = "in")
+ggsave(paste0(outFolder,"/security of supply - net fossil.png"), g[["security of supply - net fossil"]] , device="png", width = 6, height = 4.5, dpi=300, units = "in")
 
@@
 
-  g[["security of supply - fossil"]]
+  g[["security of supply - net fossil"]]
 
@@
 
-ggsave(paste0(outFolder,"/Hydrogen.svg"), g[["Hydrogen"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
-ggsave(paste0(outFolder,"/Hydrogen.png"), g[["Hydrogen"]] , device="png", width = 6, height = 4, dpi=300, units = "in")
+#ggsave(paste0(outFolder,"/Hydrogen.svg"), g[["Hydrogen"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
+#ggsave(paste0(outFolder,"/Hydrogen.png"), g[["Hydrogen"]] , device="png", width = 6, height = 4, dpi=300, units = "in")
+
+g[["Hydrogen - alt axis"]] <- 
+  ggplot(plotData,aes(x=period,y=value)) +
+  geom_hline(yintercept= target[1,]$value, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = 2015, y = target[1,]$value, label = "REPowerEU\ndomestic", angle=90, vjust = 0.4, hjust = 0, color = "black", alpha = 0.5, size = 0.3*theme.single.text.size) +
+  geom_hline(yintercept= target[2,]$value, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = 2015, y = target[2,]$value, label = "REPowerEU\ntotal", angle=90, vjust = 0.4, hjust = 0, color = "black", alpha = 0.5, size = 0.3*theme.single.text.size) +
+  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = variable, alpha=factor(period))) +
+  geom_errorbar(data=plotData %>% filter(period != 2020, variable == vars[1], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, linewidth=1,position = position_dodge(width=2)) +
+  # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
+  coord_flip() +
+  theme_doubleColumn() +
+  theme(panel.grid.minor.x = element_blank(),
+        panel.grid.major.y = element_blank()) +
+  #guides(y = "none") +
+  theme(axis.title.y=element_blank()) +
+  #theme(legend.position = "none") #+
+  scale_fill_manual(values = color,
+                    labels = setNames(names(vars), vars)[c("SE|Hydrogen|Electricity", "SE|Hydrogen|Gas|w/o CC", "SE|Hydrogen|Biomass|w/ CC")],
+                    breaks = c("SE|Hydrogen|Electricity", "SE|Hydrogen|Gas|w/o CC", "SE|Hydrogen|Biomass|w/ CC"), guide = guide_legend(nrow = 1)) +
+  scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
+  theme(legend.text=element_text(size=theme.double.text.size)) +
+  theme(legend.key.height = unit(0.7, "cm"),
+    legend.key.width = unit(0.7,"cm")) +
+  scale_y_continuous(breaks = seq(0,6,1)) +
+  expand_limits(y=c(0,6)) + 
+  #scale_y_continuous(breaks = c(0,plotData %>% filter(scenario == mainScen, period == 2030, variable == vars[1]) %>% pull(sum),plotData %>% filter(scenario == mainScen, period == 2040, variable == vars[1]) %>% pull(sum),plotData %>% filter(scenario == mainScen, period == 2050, variable == vars[1]) %>% pull(sum)),
+   #                  labels = c(format(0,nsmall = 1),format(round(plotData %>% filter(scenario == mainScen, period == 2030, variable == vars[1]) %>% pull(sum),1),nsmall = 1),format(round(plotData %>% filter(scenario == mainScen, period == 2040, variable == vars[1]) %>% pull(sum),1),nsmall = 1),format(round(plotData %>% filter(scenario == mainScen, period == 2050, variable == vars[1]) %>% pull(sum),1),nsmall = 1))) +
+  #scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == 2030) %>% pull(value))),round(sum(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value))),round(sum(plotData %>% filter(scenario == mainScen, period == 2050) %>% pull(value))))) +
+  #scale_x_reverse() +
+  theme(legend.margin=margin(l = -2, unit='cm'))
+
+ggsave(paste0(outFolder,"/Hydrogen - alt axis.svg"), g[["Hydrogen - alt axis"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
+ggsave(paste0(outFolder,"/Hydrogen - alt axis.png"), g[["Hydrogen - alt axis"]] , device="png", width = 6, height = 4, dpi=300, units = "in")
 
@@
 
-g[["Hydrogen"]]
+g[["Hydrogen - alt axis"]]
 
@@
   theme(legend.key.height = unit(0.7, "cm"),
-    legend.key.width = unit(0.7,"cm"))
+    legend.key.width = unit(0.7,"cm")) +
+  theme(legend.margin=margin(t = -0.4, unit='cm'))
 #+ scale_y_continuous(name = "Final Energy")
@@
 # Industry Emissions
-vars <- c("Cement" = "Emi|CO2|Energy|Demand|Industry|Cement",
+vars <- c("Chemicals"="Emi|CO2|Energy|Demand|Industry|Chemicals",
+          "Other Industry"="Emi|CO2|Energy|Demand|Industry|Other Industry",
           "Steel"="Emi|CO2|Energy|Demand|Industry|Steel",
-          "Chemicals"="Emi|CO2|Energy|Demand|Industry|Chemicals",
-          "Other Industry"="Emi|CO2|Energy|Demand|Industry|Other Industry")
+          "Cement" = "Emi|CO2|Energy|Demand|Industry|Cement"
+          )
 
@@
     guides(color=guide_legend(nrow=2)) +
-  theme(axis.title.y = element_blank())
-
-ggsave(paste0(outFolder,"/Industry Emissions.svg"), g[["Industry Emissions"]] , device="svg", width = 6, height = 6, dpi=100, units = "in")
-ggsave(paste0(outFolder,"/Industry Emissions.png"), g[["Industry Emissions"]] , device="png", width = 6, height = 6, dpi=300, units = "in")
-
-```
-
-```{r, echo=FALSE, fig.width=6, fig.height=6}
+    theme(axis.title.y = element_blank()) +
+    theme(legend.text=element_text(size=theme.double.text.size)) #+
+    #theme(legend.key.height = unit(0.7, "cm"), legend.key.width = unit(0.7,"cm"))
+
+ggsave(paste0(outFolder,"/Industry Emissions.svg"), g[["Industry Emissions"]] , device="svg", width = 6, height = 5.5, dpi=100, units = "in")
+ggsave(paste0(outFolder,"/Industry Emissions.png"), g[["Industry Emissions"]] , device="png", width = 6, height = 5.5, dpi=300, units = "in")
+
+```
+
+```{r, echo=FALSE, fig.width=6, fig.height=5.5}
 
@@
 
-(c) Buildings useful energy
-    Electricity based heating (EJ/yr)
+(c) Buildings useful energy Electricity based heating (EJ/yr)
 
@@
 
-ggsave(paste0(outFolder,"/Buildings Heating - Useful energy - Electricity Based.svg"), g[["Buildings Heating - Useful energy - Electricity Based"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
-ggsave(paste0(outFolder,"/Buildings Heating - Useful energy - Electricity Based.png"), g[["Buildings Heating - Useful energy - Electricity Based"]] , device="png", width = 6, height = 4, dpi=300, units = "in")
+#ggsave(paste0(outFolder,"/Buildings Heating - Useful energy - Electricity Based.svg"), g[["Buildings Heating - Useful energy - Electricity Based"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
+#ggsave(paste0(outFolder,"/Buildings Heating - Useful energy - Electricity Based.png"), g[["Buildings Heating - Useful energy - Electricity Based"]] , device="png", width = 6, height = 4, dpi=300, units = "in")
+
+g[["Buildings Heating - Useful energy - Electricity Based - alt axis"]] <- 
+  ggplot(plotData,aes(x=period,y=value)) +
+  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = variable, alpha=factor(period))) +
+  geom_errorbar(data=plotData %>% filter(period != 2020, variable == vars[1], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, size=1,position = position_dodge(width=2)) +
+  # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
+  coord_flip() +
+  theme_doubleColumn() +
+  theme(panel.grid.minor.x = element_blank(),
+        panel.grid.major.y = element_blank()) +
+  #guides(y = "none") +
+  theme(axis.title.y=element_blank()) +
+  #theme(legend.position = "none") #+
+  scale_fill_manual(values = setNames(colors[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(reverse = TRUE, nrow = 1)) +
+  scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
+  theme(legend.text=element_text(size=theme.double.text.size)) +
+  theme(legend.key.height = unit(0.7, "cm"),
+    legend.key.width = unit(0.7,"cm")) #+
+  #scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == "2020") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2030") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2040") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2050") %>% pull(value)),1))) #+
+  #scale_x_reverse()
+
+ggsave(paste0(outFolder,"/Buildings Heating - Useful energy - Electricity Based - alt axis.svg"), g[["Buildings Heating - Useful energy - Electricity Based - alt axis"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
+ggsave(paste0(outFolder,"/Buildings Heating - Useful energy - Electricity Based - alt axis.png"), g[["Buildings Heating - Useful energy - Electricity Based - alt axis"]] , device="png", width = 6, height = 4, dpi=300, units = "in")
 
@@
 
-g[["Buildings Heating - Useful energy - Electricity Based"]]
+g[["Buildings Heating - Useful energy - Electricity Based - alt axis"]]
 
@@
 
- ggsave(paste0(outFolder,"/Carbon Management.svg"), g[["Carbon Management"]] , device="svg", width = 6, height = 6, dpi=100, units = "in")
- ggsave(paste0(outFolder,"/Carbon Management.png"), g[["Carbon Management"]] , device="png", width = 6, height = 6, dpi=300, units = "in")
-
-```
-
-```{r, echo=FALSE, fig.width=6, fig.height=6}
+ ggsave(paste0(outFolder,"/Carbon Management.svg"), g[["Carbon Management"]] , device="svg", width = 6, height = 5.5, dpi=100, units = "in")
+ ggsave(paste0(outFolder,"/Carbon Management.png"), g[["Carbon Management"]] , device="png", width = 6, height = 5.5, dpi=300, units = "in")
+
+```
+
+```{r, echo=FALSE, fig.width=6, fig.height=5.5}
 
@@
 
+fullPlotData <- plotData
+
+h <- refEmi %>% filter(variable == "Emissions with LULUCF and with international transport", region == "EU27", pollutant == "All greenhouse gases - (CO2 equivalent)") %>% ungroup() %>% select(region,variable,period,value)
+emi1990 <- tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)
+reduction_h <- 1- (h %>% filter(period==2021) %>% pull(value) / emi1990)
+
 g[["Emissions reductions"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
@@
   annotate("text", x = "Emissions\nreductions", y = 0.55, label = "FitFor55", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
+  geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = "Emissions\nreductions", y = reduction_h, label = "2021", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
   facet_grid(target~period, scales="free") +
@@
   geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.4, na.rm = TRUE)
+
+g[["milestone - vert"]][["Emissions reductions"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 0.55, label = "FitFor55", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
+  geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = reduction_h, label = "2021", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+  expand_limits(y=c(0,1)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(strip.text = element_text(angle = 90)) +
+  coord_cartesian(clip = 'off') +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+
+g[["milestone - hor"]][["Emissions reductions"]] <- ggplot(plotData %>% mutate(target = gsub("\n", " ", target)), aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 0.55, label = "FitFor55", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5) +
+  geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = reduction_h, label = "2021", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,1)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
+  annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=0.8*geom.text.double.size)
 
@@
         max = max(value))
+
+fullPlotData <- rbind(fullPlotData,plotData)
+
+h <- addHist$FE_consumption %>% #TJ
+  mutate(value = value/1000000) %>% #EJ
+  mutate(value = round(value * 23.8845896627496)) # 1EJ = 23.8845896627496 Mtoe
 
@@
   annotate("text", x = "Final Energy\nDemand", y = 750, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0.7, color = "black", alpha = 0.5) +
+  geom_hline(yintercept=h %>% filter(period==2021) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = "Final Energy\nDemand", y = h %>% filter(period==2021) %>% pull(value), label = "2021", angle=90, vjust = -0.5, hjust = 0.7, color = "black", alpha = 0.5) +
   facet_grid(target~period, scales="free") +
@@
   geom_text(data=data.frame(period=c(2030,2040),label=c("(Mtoe)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.2, na.rm = TRUE)
+
+g[["milestone - vert"]][["Energy savings"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 750, label = "REPowerEU", vjust = 1.5, hjust = 1, color = "black", alpha = 0.5) +
+  annotate("text", x = Inf, y = 787, label = "FitFor55", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
+  geom_hline(yintercept=h %>% filter(period==2021) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = h %>% filter(period==2021) %>% pull(value), label = "2021", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+  expand_limits(y=c(0,400,1000)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(strip.text = element_text(angle = 90)) +
+  coord_cartesian(clip = 'off') +
+  annotate("text", x = -Inf, y = Inf, label = "(Mtoe)", hjust = 1, color = "black", alpha = 0.5) +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+
+g[["milestone - hor"]][["Energy savings"]] <- ggplot(plotData %>% mutate(target = gsub("\n", " ", target)), aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 750, label = "REPowerEU", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5) +
+  annotate("text", x = Inf, y = 787, label = "FitFor55", angle=90, vjust = 1, hjust = 0, color = "black", alpha = 0.5) +
+  geom_hline(yintercept=h %>% filter(period==2021) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = h %>% filter(period==2021) %>% pull(value), label = "2021", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,400,1000)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
+  annotate("text", x = -Inf, y = -Inf, label = "(Mtoe)", hjust = 1, color = "#666666", size=0.8*geom.text.double.size)
 
@@
 
+fullPlotData <- rbind(fullPlotData,plotData)
+
+#2022 = 2469471.42 GWh = 2469471.42 *1000 / 8.76E+09 * 31.536 EJ - FE electricity - https://ec.europa.eu/eurostat/databrowser/bookmark/d19a01c7-6099-4b88-8ccd-c6bcc01c3ddc?lang=en
+h <- 2469471.42 /1000
+# old value? 2641
+
 g[["Electricity Demand"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
@@
   geom_boxplot(outlier.shape = NA, width=0.6) +
-  geom_hline(yintercept=2641, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Electricity\nDemand", y = 2641, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5) +
+  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = "Electricity\nDemand", y = h, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5) +
   facet_grid(target~period, scales="free") +
@@
 
+g[["milestone - vert"]][["Electricity Demand"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+  expand_limits(y=c(0,5000)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(strip.text = element_text(angle = 90)) +
+  coord_cartesian(clip = 'off') +
+  annotate("text", x = -Inf, y = Inf, label = "(TWh)", hjust = 1, color = "black", alpha = 0.5) +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+
+g[["milestone - hor"]][["Electricity Demand"]] <- ggplot(plotData %>% mutate(target = gsub("\n", " ", target)), aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,5000)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
+  annotate("text", x = -Inf, y = -Inf, label = "(TWh)", hjust = 1, color = "#666666", size=0.8*geom.text.double.size)
+
 # Renewables share
@@
         max = max(value))
+
+fullPlotData <- rbind(fullPlotData,plotData)
 
@@
   annotate("text", x = "Renewables\nShare in\nFinal Energy", y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0.6, color = "black", alpha = 0.5) +
+  geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2021) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = "Renewables\nShare in\nFinal Energy", y = addHist$res %>% filter(type == "RES", period == 2021) %>% pull(value), label = "2021", angle=90, vjust = -0.5, hjust = 0.6, color = "black", alpha = 0.5) +
   facet_grid(target~period, scales="free") +
@@
 
+g[["milestone - vert"]][["Renewables Share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 0.4, label = "RED II revised", vjust = 1.5, hjust = 1, color = "black", alpha = 0.5) +
+  geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 0.45, label = "REPowerEU", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
+  geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2021) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = addHist$res %>% filter(type == "RES", period == 2021) %>% pull(value), label = "2021", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+  expand_limits(y=c(0,1)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(strip.text = element_text(angle = 90)) +
+  coord_cartesian(clip = 'off') +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+
+g[["milestone - hor"]][["Renewables Share"]] <- ggplot(plotData %>% mutate(target = gsub("\n", " ", target)), aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5) +
+  geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0, color = "black", alpha = 0.5) +
+  geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2021) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = addHist$res %>% filter(type == "RES", period == 2021) %>% pull(value), label = "2021", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,1)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
+  annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=0.8*geom.text.double.size)
+
 # Wind
@@
 
+fullPlotData <- rbind(fullPlotData,plotData)
+
 #target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2025,2030),value=c(320,600)) 
@@
 
+g[["milestone - vert"]][["Wind capacity"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 255, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+  expand_limits(y=c(0,1000)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(strip.text = element_text(angle = 90)) +
+  coord_cartesian(clip = 'off') +
+  annotate("text", x = -Inf, y = Inf, label = "(GW)", hjust = 1, color = "black", alpha = 0.5) +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+
+g[["milestone - hor"]][["Wind capacity"]] <- ggplot(plotData %>% mutate(target = gsub("\n", " ", target)), aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 255, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,1000)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
+  annotate("text", x = -Inf, y = -Inf, label = "(GW)", hjust = 1, color = "#666666", size=0.8*geom.text.double.size)
+
 # Solar photovoltaics
@@
 
+g[["milestone - vert"]][["Solar photovoltaics"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 600, label = "REPowerEU", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
+  geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 208.9, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+  expand_limits(y=c(0,2500)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(strip.text = element_text(angle = 90)) +
+  coord_cartesian(clip = 'off') +
+  annotate("text", x = -Inf, y = Inf, label = "(GW)", hjust = 1, color = "black", alpha = 0.5) +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+
+g[["milestone - hor"]][["Solar photovoltaics"]] <- ggplot(plotData %>% mutate(target = gsub("\n", " ", target)), aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 600, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0, color = "black", alpha = 0.5) +
+  geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 208.9, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,2500)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
+  annotate("text", x = -Inf, y = -Inf, label = "(GW)", hjust = 1, color = "#666666", size=0.8*geom.text.double.size)
+
 # Carbon Capture and Storage 
@@
 
+g[["milestone - vert"]][["Carbon Capture and Storage"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 50, label = "Net-Zero\nIndustry Act", vjust = 0.5, hjust = 1, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+  expand_limits(y=c(0,400)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(strip.text = element_text(angle = 90)) +
+  coord_cartesian(clip = 'off') +
+  annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5) +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+
+g[["milestone - hor"]][["Carbon Capture and Storage"]] <- ggplot(plotData %>% mutate(target = gsub("\n", " ", target)), aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 50, label = "Net-Zero\nIndustry Act", angle=90, vjust = 0.5, hjust = 0, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,400)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
+  annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size=0.8*geom.text.double.size)
+
 # Novel CDR = atmospheric/biogenic CO2 (CDR) 
@@
   filter(tgt2050 != "Npi") %>%
-  mutate(target = "Novel CDR") %>%
+  mutate(target = "BECCS\nand\nDACCS") %>%
   group_by(period) %>% 
@@
 
+g[["milestone - vert"]][["Novel CDR"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+  expand_limits(y=c(0,250)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(strip.text = element_text(angle = 90)) +
+  coord_cartesian(clip = 'off') +
+  annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5) +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+
+g[["milestone - hor"]][["Novel CDR"]] <- ggplot(plotData %>% mutate(target = gsub("\n", " ", target)), aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,250)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
+  annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size=0.8*geom.text.double.size)
+
 # Direct Electrification
@@
 
+fullPlotData <- rbind(fullPlotData,plotData)
+
+#estimation of historical share in 2021 for FE electricity / FE with non-energy use and with bunkers
+h <- (
+      2550461.10 *1000 / 8.76E+09 * 31.536  # https://ec.europa.eu/eurostat/databrowser/bookmark/12d54df4-7c35-47eb-a103-dd8994d26b80?lang=en
+     ) / (
+      addHist$FE_consumption %>% mutate(value = value/1000000) %>% filter(period==2021) %>% pull(value) + # FE|w/o Non-energy Use w/o Bunkers - EJ
+      df %>% filter(region == "EU27", period == 2020, scenario == "Npi", variable == "FE|Transport|Bunkers") %>% pull(value) +
+      df %>% filter(region == "EU27", period == 2020, scenario == "Npi", variable == "FE|Non-energy Use|Industry") %>% pull(value)
+     )
+
 g[["Direct Electrification"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
@@
          #      hjust=-1, angle = 90) +
+  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = "Electricity\nShare in\nFinal Energy", y = h, label = "2021", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5) +
   facet_grid(target~period, scales="free") +
@@
 
+g[["milestone - vert"]][["Direct Electrification"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = h, label = "2021", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+  expand_limits(y=c(0,1)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(strip.text = element_text(angle = 90)) +
+  coord_cartesian(clip = 'off') +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+
+g[["milestone - hor"]][["Direct Electrification"]] <- ggplot(plotData %>% mutate(target = gsub("\n", " ", target)), aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = h, label = "2021", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,1)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
+  annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=0.8*geom.text.double.size)
+
 # Carbon-free electricity share
@@
 
+fullPlotData <- rbind(fullPlotData,plotData)
+
+#historical - 2022 - https://ec.europa.eu/eurostat/statistics-explained/index.php?title=Electricity_and_heat_statistics&oldid=347519
+#solid fossil	453180
+#oil	54277
+#gas	571687
+#nuclear	609169
+#renewables	1076710
+#other	32822
+h <- (609169 + 1076710)	/ (453180 + 54277 + 571687 + 609169 + 1076710 + 32822)
+
 g[["Carbon-free electricity share"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
@@
          #      hjust=-1, angle = 90) +
+  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = "Carbon-free\nelectricity\nshare", y = h, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5) +
   facet_grid(target~period, scales="free") +
@@
 
+g[["milestone - vert"]][["Carbon-free electricity share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+  expand_limits(y=c(0,1)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(strip.text = element_text(angle = 90)) +
+  coord_cartesian(clip = 'off') +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+
+g[["milestone - hor"]][["Carbon-free electricity share"]] <- ggplot(plotData %>% mutate(target = gsub("\n", " ", target)), aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,1)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
+  annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=0.8*geom.text.double.size)
+
 # Residual Fossil Emissions
@@
 
+g[["milestone - vert"]][["Residual Fossil Emissions"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+  expand_limits(y=c(0,2500)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(strip.text = element_text(angle = 90)) +
+  coord_cartesian(clip = 'off') +
+  annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5) +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+
+g[["milestone - hor"]][["Residual Fossil Emissions"]] <- ggplot(plotData %>% mutate(target = gsub("\n", " ", target)), aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,2500)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
+  annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size=0.8*geom.text.double.size)
+
+# Domestic Hydrogen Production
+plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "SE|Hydrogen") %>% select(-variable) %>%
+  mutate(value = value*8)  %>% #1EJ <- 8 million tons adrian
+  filter(tgt2050 != "Npi") %>%
+  mutate(target = "Domestic\nHydrogen\nProduction") %>%
+  group_by(period) %>% 
+  mutate(min = min(value),
+        max = max(value))
+
+fullPlotData <- rbind(fullPlotData,plotData)
+
+target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2030,2030),value=c(10,20))
+
+g[["Domestic Hydrogen Production"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
+  geom_boxplot(outlier.shape = NA, width=0.6) +
+  geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = "Domestic\nHydrogen\nProduction", y = 10, label = "REPowerEU\ndomestic", angle=90, vjust = 0.5, hjust = 0.5, color = "black", alpha = 0.5) +
+  facet_grid(target~period, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  expand_limits(y=c(0,20)) + 
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  theme(strip.text.x = element_blank()) +
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
+  geom_text(data=data.frame(period=c(2030,2040),label=c("(Mtoe)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.4, na.rm = TRUE)
+
+g[["milestone - vert"]][["Domestic Hydrogen Production"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = -Inf, y = 10, label = "REPowerEU\ndomestic", vjust = 0.5, hjust = 0, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+  expand_limits(y=c(0,20)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(strip.text = element_text(angle = 90)) +
+  coord_cartesian(clip = 'off') +
+  annotate("text", x = -Inf, y = Inf, label = "(Mtoe)", hjust = 1, color = "black", alpha = 0.5) +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+
+g[["milestone - hor"]][["Domestic Hydrogen Production"]] <- ggplot(plotData %>% mutate(target = gsub("\n", " ", target)), aes(x = period, y = value, group=period)) +
+  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = -Inf, y = 10, label = "REPowerEU\ndomestic", angle=90, vjust = 0.5, hjust = 1, color = "black", alpha = 0.5) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,20)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
+  annotate("text", x = -Inf, y = -Inf, label = "(Mtoe)", hjust = 1, color = "#666666", size=0.8*geom.text.double.size)
+
 g[["Targets"]] <- gridExtra::arrangeGrob(
@@
   g[["Carbon Capture and Storage"]] + theme(plot.margin=margin(b=20, l = 15)),
-  g[["Novel CDR"]] + theme(plot.margin=margin(b=20, l = 27)),
+  g[["Novel CDR"]] + theme(plot.margin=margin(b=20, l = 50)),
   g[["Direct Electrification"]] + theme(plot.margin=margin(b=20, l = 17)),
   g[["Carbon-free electricity share"]] + theme(plot.margin=margin(b=20, l = 24)),
+  g[["Domestic Hydrogen Production"]] + theme(plot.margin=margin(b=20,l = 35)),
   g[["Residual Fossil Emissions"]] + theme(plot.margin=margin(b=20, l = 39)),
@@
 
-ggsave(paste0(outFolder,"/targets.svg"), g[["Targets"]] , device="svg", width = 12, height = 17, dpi=100, units = "in")
-ggsave(paste0(outFolder,"/targets.png"), g[["Targets"]] , device="png", width = 12, height = 17, dpi=300, units = "in")
+#ggsave(paste0(outFolder,"/targets.svg"), g[["Targets"]] , device="svg", width = 12, height = 17, dpi=100, units = "in")
+#ggsave(paste0(outFolder,"/targets.png"), g[["Targets"]] , device="png", width = 12, height = 17, dpi=300, units = "in")
+
+g[["milestone - vert targets"]] <- gridExtra::arrangeGrob(
+  g[["milestone - vert"]][["Emissions reductions"]] + theme(plot.margin=margin(r=30,t = 30)), #+ theme(plot.margin=margin(10,10,30,10)),margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
+  g[["milestone - vert"]][["Energy savings"]] + theme(plot.margin=margin(r=30,t = 10)),
+  g[["milestone - vert"]][["Renewables Share"]] + theme(plot.margin=margin(r=30,t = 15)),
+  g[["milestone - vert"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(r=30,t = 39)),
+  g[["milestone - vert"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(r=30,t = 15)),
+  g[["milestone - vert"]][["Novel CDR"]] + theme(plot.margin=margin(t = 50)),
+
+  g[["milestone - vert"]][["Electricity Demand"]] + theme(plot.margin=margin(r=30,t = 35)),
+  g[["milestone - vert"]][["Wind capacity"]] + theme(plot.margin=margin(r=30,t = 50)),
+  g[["milestone - vert"]][["Solar photovoltaics"]] + theme(plot.margin=margin(r=30,t = 10)),
+  g[["milestone - vert"]][["Direct Electrification"]] + theme(plot.margin=margin(r=30,t = 17)),
+  g[["milestone - vert"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(t = 24)),
+  g[["milestone - vert"]][["Domestic Hydrogen Production"]] + theme(plot.margin=margin(r=30,t = 35)),
+  nrow = 2
+)
+
+#ggsave(paste0(outFolder,"/milestone - vert targets.svg"), g[["milestone - vert targets"]] , device="svg", width = 12, height = 17, dpi=100, units = "in")
+#ggsave(paste0(outFolder,"/milestone - vert targets.png"), g[["milestone - vert targets"]] , device="png", width = 12, height = 17, dpi=300, units = "in")
+
+g[["milestone - hor targets"]] <- gridExtra::arrangeGrob(
+  g[["milestone - hor"]][["Emissions reductions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - hor"]][["Energy savings"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - hor"]][["Renewables Share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - hor"]][["Direct Electrification"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - hor"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - hor"]][["Domestic Hydrogen Production"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+
+  g[["milestone - hor"]][["Electricity Demand"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - hor"]][["Wind capacity"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - hor"]][["Solar photovoltaics"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+
+  g[["milestone - hor"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - hor"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - hor"]][["Novel CDR"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+
+  ncol = 2
+)
+
+ggsave(paste0(outFolder,"/milestone - hor targets.svg"), g[["milestone - hor targets"]] , device="svg", width = 12, height = 14, dpi=100, units = "in")
+ggsave(paste0(outFolder,"/milestone - hor targets.png"), g[["milestone - hor targets"]] , device="png", width = 12, height = 14, dpi=300, units = "in")
 
@@
 grid.newpage()
-grid.draw(g[["Targets"]])
-
-```
+grid.draw(g[["milestone - hor targets"]])
+
+```

### 2023-07-21 R/harmonizeData.R

@@ -27,6 +27,28 @@ harmonizeData <- function(data,scaleFactor){ #,nzero=NULL
   # }
   # #})
   
+  
+  #Adjust gas trade to real world magnitudes
+  #https://ec.europa.eu/eurostat/databrowser/bookmark/ff60b17b-792b-4a89-b352-fe04bcf2dbac?lang=en
+  prodPeGas <- left_join(
+    data %>% filter(region == "EU27")  %>% calc_addVariable("`Prod|PE|Gas`" = "`PE|Gas` - `Trade|Imports|Gas` + `Trade|Exports|Gas`", units = "EJ/yr", only.new=T)
+    ,
+    data.frame(period = seq(2005,2060,5),
+               max = c(4.53, 4.53, 3.70, 1.44, 1.22, 1, 0.75, 0.50, 0.50, 0.50, 0.50, 0.50))
+    ,
+    by = join_by(period == period)
+  ) %>% rowwise() %>% mutate(value = min(value, max)) %>% select(-max) 
+  
+  ExportsAdj <- data %>% filter(variable %in% "Trade|Exports|Gas", region == "EU27") %>% mutate(value = value + ifelse(period <= 2010, 1, 8), variable = "Trade|Exports|Gas|Adj")
+  
+  data <- rbind(data,
+              prodPeGas,
+              ExportsAdj)
+  
+  data <- rbind(data,
+              data %>% filter(region == "EU27")  %>% calc_addVariable("`Trade|Imports|Gas|Adj`" = "`PE|Gas` - `Prod|PE|Gas` + `Trade|Exports|Gas|Adj`", units = "EJ/yr", only.new=T)
+  )
+  
   return(data)
 }
 

### 2023-07-21 R/loadData.R

@@ -142,6 +142,9 @@ dataFolder <- rownames(folders)[which.max(folders$mtime)]
 outFolder <- paste0("./output/",gsub("./data/","",dataFolder))
 dir.create(outFolder, recursive = TRUE, showWarnings = FALSE)
 
+outFolder_conference <- paste0("./output/",gsub("./data/","",dataFolder), "/conference")
+dir.create(outFolder_conference, recursive = TRUE, showWarnings = FALSE)
+
 if((forceUpdateData) || ! file.exists(paste0(dataFolder,"/data_EU27andDEU.rds"))){
   
   ### Load data 

### 2024-08-30 report_additionalCharts.Rmd
revision1

---
title: "additional charts"
output:
  html_document:
    theme: paper
    toc: true
    toc_float:
      collapsed: false
---

<!-- Setting default chunk options -->
```{r chunkOptions, echo=FALSE, include = FALSE}
#knitr::opts_chunk$set(echo = TRUE)
# setting global R chunk options (https://yihui.name/knitr/options/#chunk_options)
  knitr::opts_chunk$set(dev='svglite', # svg, png,...
                        fig.ext = ".svg",
                        #fig.asp = .8 # default aspect ratio
                        fig.width = 12,
                        fig.height = 6,
                        dpi=100
                        )
```

```{r loading_packages, echo=FALSE, include = FALSE}

  #Loading required packages
  # install.packages("remotes")
  #remotes::install_github("coolbutuseless/ggpattern")
  #install.packages('rsvg')
  #remotes::install_github('coolbutuseless/ggsvg')
  packagesList <- c("quitte","ggplot2","geomtextpath","ggpattern","tidyr","grid","stringr","gridExtra","ggrepel","kableExtra","dplyr","remind2","rsvg","ggsvg","plotly")
  packages <- suppressWarnings(suppressMessages(lapply(packagesList, function(x){ if(!require(x, character.only = T, quietly = T)){ install.packages(x); return(paste0("installed missing package: ", x)) } else paste0("required package is installed: ", x) } )))

```

<!-- Preprocess: prepare and load the data for use in the charts and markdown -->

```{r preprocess, echo=FALSE, include = FALSE}

#Options
forceUpdateData = FALSE
loadHist = TRUE

# data and output folders
folders <- file.info(list.files(path="./data", full.names = T))
dataFolder <- folders %>% tibble::rownames_to_column(var = "path") %>% arrange(desc(path)) %>% slice(1) %>% pull(path)

source("./R/preprocess.R")

outFolder <- paste0("./output/",gsub("./data/","",dataFolder))
outChartsFolder <- paste0(outFolder,"/report_additionalCharts")
dir.create(paste0(outChartsFolder, "/png"), recursive = TRUE, showWarnings = FALSE)
dir.create(paste0(outChartsFolder, "/svg"), recursive = TRUE, showWarnings = FALSE)

```

# Targets debug {.tabset}

## Reduction Matrix

```{r data_emissionReductionMatrix, echo=FALSE, include = FALSE}

## Reduction Matrix
reductionMatrix <- df_beforeFilter %>% 
  filter(region == "EU27", 
         period == 2040, 
         tgt2030 == "57",
         !grepl("eedEff|ff55Eff|RpEUEff",scenario)) %>% 
  calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
  mutate(reduction = round((1 - (value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)))*100 ,2)) %>%
  select(bioLim,lim,reduction) %>%
  pivot_wider(names_from=lim,values_from=reduction) %>%
  mutate(bioLim = factor(c("BioLim4","BioLim7.5","BioLim12","BioLim20")))

if("limVRE" %in% colnames(reductionMatrix)){
  colors <- spec_color(c(reductionMatrix$default,reductionMatrix$limCCS,reductionMatrix$limH2,reductionMatrix$limVRE), end = 0.9, option = "A", direction = -1)

redMatrix <- reductionMatrix %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(1, bold = T) %>%
  column_spec(2,color = colors[1:3]) %>%
  column_spec(3,color = colors[4:6]) %>%
  column_spec(4,color = colors[7:9]) %>%
  column_spec(5,color = colors[10:12])
} else {
  colors <- spec_color(c(reductionMatrix$default,reductionMatrix$limCCS,reductionMatrix$limH2), end = 0.9, option = "A", direction = -1)

redMatrix <- reductionMatrix %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(1, bold = T) %>%
  column_spec(2,color = colors[1:3]) %>%
  column_spec(3,color = colors[4:6]) %>%
  column_spec(4,color = colors[7:9])
}

redMatrix2 <- df_beforeFilter %>%
    filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
    mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)),
           tgtAchieved = (1-reduction)*100,
           diff = as.numeric(as.character(tgt2030)) - ((1-reduction)*100)) %>%
  mutate(text = paste0(round(tgtAchieved,2), "%"))

g[["reduction matrix"]][["ggplot"]] <- ggplot(redMatrix2, aes(x=bioLim, y=lim, fill= tgtAchieved, text = text)) + 
  geom_tile() +
  facet_grid(tgt2030 ~ efficiency, scales = "free") +
  scale_fill_distiller(palette = "Blues", direction = 1, breaks = seq(floor(min(redMatrix2$tgtAchieved)), ceiling(max(redMatrix2$tgtAchieved)),2)) +
  theme_doubleColumn() +
  theme(strip.clip = "off") +
  guides(fill = guide_colorbar(barwidth = 20, barheight = 1)) +
  theme(legend.position="bottom") +
  theme(legend.title=element_blank())

g[["reduction matrix"]][["plotly"]] <- ggplotly(g[["reduction matrix"]][["ggplot"]],tooltip = c("text")) %>% layout(autosize = TRUE)

ggsave(paste0(outChartsFolder,"/svg/Emission Reduction 2040.svg"), g[["reduction matrix"]][["ggplot"]] , device="svg", width = 10, height = 6, dpi=100, units = "in")
ggsave(paste0(outChartsFolder,"/png/Emission Reduction 2040.png"), g[["reduction matrix"]][["ggplot"]] , device="png", width = 10, height = 6, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=10, fig.height=6}

g[["reduction matrix"]][["plotly"]]

```

- Reduction Matrix for the 2030 57% target

```{r, echo=FALSE}

redMatrix

```

## non-achieved 2030

<!-- Debug non-achieved targets -->
```{r, echo=FALSE, include = FALSE}

plotData <- left_join(
  df_beforeFilter %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
    mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)),
           tgtAchieved = (1-reduction)*100,
           diff = as.numeric(as.character(tgt2030)) - ((1-reduction)*100)) %>%
    group_by(tgt2030) %>% 
    mutate(min = min(value),
           max = max(value)),
  df_beforeFilter %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Price|Carbon") %>%
    mutate(price_2030 = 1.17*value) %>%
    select(scenario, price_2030),
  by = "scenario") %>%
  mutate(text = paste0("Target Achieved: ", tgtAchieved, " % reduction", "\n2030 price: ", round(price_2030,2), " €/t CO2", "\nScenario: ", scenario, "\nTarget 2030: ", tgt2030, "%", "\nEfficiency: ", efficiency, "\nBiomass Limit: ", bioLim, "\nSensititivy limit: ", lim))

g[["2030 targets"]][["ggplot"]] <-  ggplot(plotData,aes(x=period,y=tgtAchieved)) +
  geom_point(aes(shape = lim, fill = bioLim, color = efficiency, text = text), size = 3) +
  geom_segment(aes(x=2029, xend=2031, y=as.numeric(as.character(tgt2030)), yend=as.numeric(as.character(tgt2030))), linetype="dashed", color="black") +
  #geom_errorbar(aes(ymin=min, ymax=max), colour="black", alpha=0.9, linewidth=1) +
  #geom_boxplot(outlier.shape = NA) +
  facet_grid(~ tgt2030) +
  theme_doubleColumn() +
  scale_fill_manual(values = c("BioLim4"="#fedc97", "BioLim7.5"="#b5b682", "BioLim12"="#7c9885", "BioLim20"="#28666e"), guide = guide_legend(nrow =2, byrow = F, override.aes = list(shape = 21, size = 6, colour = "transparent"), order = 3)) +
  scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 6))) +
  scale_color_manual(values = c("reference"="#ae0000", "EED 2018 Eff"="#db4646", "FitFor55 eff"="#0090ab", "RePowerEU eff"="#095786"), guide = guide_legend(nrow =2, byrow = F, order = 2, override.aes = list(shape = 1, linewidth = 1.5))) + 
  scale_x_continuous(breaks=2030) +
  scale_y_continuous(breaks=seq(53,61,1)) +
  theme(legend.position="none")

g[["2030 targets"]][["plotly"]] <- ggplotly(g[["2030 targets"]][["ggplot"]],tooltip = c("text")) %>% layout(autosize = TRUE)

ggsave(paste0(outChartsFolder,"/svg/Emission Reduction 2030.svg"), g[["2030 targets"]][["ggplot"]], device="svg", width = 8, height = 4, dpi=100, units = "in")
ggsave(paste0(outChartsFolder,"/png/Emission Reduction 2030.png"), g[["2030 targets"]][["ggplot"]], device="png", width = 8, height = 4, dpi=300, units = "in")

## Function to extract legend
g_legend <- function(a.gplot){ 
    tmp <- ggplot_gtable(ggplot_build(a.gplot)) 
    leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box") 
    legend <- tmp$grobs[[leg]] 
    legend
}

legend <- g_legend(
  g[["2030 targets"]][["ggplot"]] +
  theme(legend.position="bottom") +  
  theme(legend.title=element_blank(),
        legend.margin=margin(c(0,0,0,0))) +
  theme(plot.margin=margin(0,0,0,0))
)

nonAchieved2030 <- left_join(
  df_beforeFilter %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
    mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)),
           tgtAchieved = (1-reduction)*100,
           diff = as.numeric(as.character(tgt2030)) - ((1-reduction)*100)) %>%
    group_by(tgt2030) %>% 
    mutate(min = min(value),
           max = max(value)),
  df_beforeFilter %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Price|Carbon") %>%
    mutate(price_2030 = 1.17*value) %>%
    select(scenario, price_2030),
  by = "scenario") %>%
  filter(diff >= 0.5 | diff <= -0.5) %>%
  select(scenario, price_2030, tgt2030, tgtAchieved, diff) %>%
  arrange(desc(abs(diff)))

#View(nonAchieved2030)

```

```{r, echo=FALSE, fig.width=8, fig.height=4}

g[["2030 targets"]][["plotly"]]

```

```{r, echo=FALSE, fig.width=8, fig.height=2}

grid.newpage()
grid.draw(legend)

```

```{r, echo=FALSE}

nonAchieved2030 %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

## non-achieved 2050

<!-- Debug non-achieved targets -->
```{r, echo=FALSE, include = FALSE}

plotData <- df_beforeFilter %>%
  filter(region == "EU27", period == 2050, tgt2030 %in% tgt2030Scen) %>%
  calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%
  mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)),
         tgtAchieved = (1-reduction)*100) %>% 
  mutate(min = min(value),
         max = max(value))

g[["2050 targets"]][["ggplot"]] <-  ggplot(plotData,aes(x=period,y=tgtAchieved)) +
  geom_point(aes(shape = lim, fill = bioLim, color = efficiency), size = 3) +
  geom_segment(aes(x=2049, xend=2051, y=100, yend=100), linetype="dashed", color="black") +
  theme_doubleColumn() +
  scale_fill_manual(values = c("BioLim4"="#fedc97", "BioLim7.5"="#b5b682", "BioLim12"="#7c9885", "BioLim20"="#28666e"), guide = guide_legend(nrow =2, byrow = F, override.aes = list(shape = 21, size = 6, colour = "transparent"), order = 3)) +
  scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 6))) +
  scale_color_manual(values = c("reference"="#ae0000", "EED 2018 Eff"="#db4646", "FitFor55 eff"="#0090ab", "RePowerEU eff"="#095786"), guide = guide_legend(nrow =2, byrow = F, order = 2, override.aes = list(shape = 1, linewidth = 1.5))) + 
  scale_x_continuous(breaks=2050) +
  scale_y_continuous(breaks=c(99.5,100,100.5)) +
  expand_limits(y=c(99.5,100.5)) +
  theme(legend.position="none")

  g[["2050 targets"]][["plotly"]] <- ggplotly(g[["2050 targets"]][["ggplot"]]) %>% layout(autosize = TRUE)

ggsave(paste0(outChartsFolder,"/svg/Emission Reduction 2050.svg"), g[["2050 targets"]][["ggplot"]], device="svg", width = 4, height = 4, dpi=100, units = "in")
ggsave(paste0(outChartsFolder,"/png/Emission Reduction 2050.png"), g[["2050 targets"]][["ggplot"]], device="png", width = 4, height = 4, dpi=300, units = "in")

nonAchieved2050 <- df_beforeFilter %>%
  filter(region == "EU27", period == 2050, tgt2030 %in% tgt2030Scen) %>%
  calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%
  mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)),
         tgtAchieved = (1-reduction)*100) %>%
  filter(tgtAchieved >= 100.3 | tgtAchieved <= 99.7) %>%
  select(scenario, reduction, tgtAchieved) %>%
  arrange(desc(abs(reduction)))

#View(nonAchieved2050)

```

```{r, echo=FALSE, fig.width=4, fig.height=4}

g[["2050 targets"]][["plotly"]]

```

```{r, echo=FALSE, fig.width=8, fig.height=2}

grid.newpage()
grid.draw(legend)

```

```{r, echo=FALSE}

nonAchieved2050 %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

<!-- Initializing charts object -->
```{r chart_initialization, echo=FALSE, include = FALSE}

#loading theme and colors
source("./R/aesthetics.R")

g <- NULL

```

# Fuel Shares {.tabset}

```{r, echo=FALSE, include=FALSE}

vars <- list(
  "Liquids" = list(
    "Transport" = c(
      "FE|Transport|Liquids|Biomass",
      "FE|Transport|Liquids|Hydrogen",
      "FE|Transport|Liquids|Fossil"
    ),
    "Buildings" = c(
      "FE|Buildings|Liquids|Biomass",
      "FE|Buildings|Liquids|Hydrogen",
      "FE|Buildings|Liquids|Fossil"
    ),
    "Industry" = c(
      "FE|Industry|Liquids|Biomass",
      "FE|Industry|Liquids|Hydrogen",
      "FE|Industry|Liquids|Fossil"
    )
  ),
  "Gases" = list(
    "Transport" = c(
      "FE|Transport|Gases|Biomass",
      "FE|Transport|Gases|Hydrogen",
      "FE|Transport|Gases|Fossil"
    ),
    "Buildings" = c(
      "FE|Buildings|Gases|Biomass",
      "FE|Buildings|Gases|Hydrogen",
      "FE|Buildings|Gases|Fossil"
    ),
    "Industry" = c(
      "FE|Industry|Gases|Biomass",
      "FE|Industry|Gases|Hydrogen",
      "FE|Industry|Gases|Fossil"
    )
  ),
  "Solids" = list(
    "Buildings" = c(
      "FE|Buildings|Solids|Biomass",
      "FE|Buildings|Solids|Fossil"
    ),
    "Industry" = c(
      "FE|Industry|Solids|Biomass",
      "FE|Industry|Solids|Fossil"
    )
  )
  )

plotColor <- c(
    "Biomass"  = "#597445",
    "Hydrogen" = "#F96666",
    "Fossil"   = "#bbbbbb"
  )

#tgt2050 tgt2030 efficiency bioLim lim

fullPlotData <- df_beforeFilter %>%
  filter(region == "EU27", period %in% c(2010:2050), variable %in% unlist(vars)) %>%
  mutate(sector = factor(unlist(regmatches(variable, gregexpr('Transport|Industry|Buildings', variable))),levels=c("Industry", "Buildings", "Transport")),
         carrier= factor(unlist(regmatches(variable, gregexpr('Liquids|Gases|Solids', variable))),levels=c("Liquids", "Gases", "Solids")),
         type   = factor(unlist(regmatches(variable, gregexpr('Biomass|Hydrogen|Fossil', variable))),levels=c("Biomass", "Fossil", "Hydrogen")))

plotData <- fullPlotData %>%
  filter(tgt2030 == 57, 
         efficiency == "reference", 
         #bioLim == "BioLim7.5", 
         lim == "default")

g[["Fuel shares"]][["BioLim"]] <-  ggplot(plotData,aes(x=period,y=value)) +
    geom_bar(aes(fill=type),stat='identity', position="fill") +
    facet_grid(carrier~bioLim+sector) +
    theme_doubleColumn() +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(values = plotColor) + 
    theme(plot.background = element_rect(fill = 'white', colour = 'white'))

ggsave(paste0(outChartsFolder,"/svg/Fuel shares - tgt57,effRef,limDef - BioLim.svg"), g[["Fuel shares"]][["BioLim"]], device="svg", width = 12, height = 8, dpi=100, units = "in")
ggsave(paste0(outChartsFolder,"/png/Fuel shares - tgt57,effRef,limDef - BioLim.png"), g[["Fuel shares"]][["BioLim"]], device="png", width = 12, height = 8, dpi=300, units = "in")

plotData <- fullPlotData %>%
  filter(tgt2030 == 57, 
         #efficiency == "reference", 
         bioLim == "BioLim7.5", 
         lim == "default")

g[["Fuel shares"]][["efficiency"]] <-  ggplot(plotData,aes(x=period,y=value)) +
    geom_bar(aes(fill=type),stat='identity', position="fill") +
    facet_grid(carrier~efficiency+sector) +
    theme_doubleColumn() +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(values = plotColor) + 
    theme(plot.background = element_rect(fill = 'white', colour = 'white'))

ggsave(paste0(outChartsFolder,"/svg/Fuel shares - tgt57,bio7p5,limDef - efficiency.svg"), g[["Fuel shares"]][["efficiency"]], device="svg", width = 12, height = 8, dpi=100, units = "in")
ggsave(paste0(outChartsFolder,"/png/Fuel shares - tgt57,bio7p5,limDef - efficiency.png"), g[["Fuel shares"]][["efficiency"]], device="png", width = 12, height = 8, dpi=300, units = "in")

plotData <- fullPlotData %>%
  filter(#tgt2030 == 57, 
         efficiency == "reference", 
         bioLim == "BioLim7.5", 
         lim == "default")

g[["Fuel shares"]][["tgt2030"]] <-  ggplot(plotData,aes(x=period,y=value)) +
    geom_bar(aes(fill=type),stat='identity', position="fill") +
    facet_grid(carrier~tgt2030+sector) +
    theme_doubleColumn() +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(values = plotColor) + 
    theme(plot.background = element_rect(fill = 'white', colour = 'white'))

ggsave(paste0(outChartsFolder,"/svg/Fuel shares - effRef,bio7p5,limDef - tgt2030.svg"), g[["Fuel shares"]][["tgt2030"]], device="svg", width = 12, height = 8, dpi=100, units = "in")
ggsave(paste0(outChartsFolder,"/png/Fuel shares - effRef,bio7p5,limDef - tgt2030.png"), g[["Fuel shares"]][["tgt2030"]], device="png", width = 12, height = 8, dpi=300, units = "in")

plotData <- fullPlotData %>%
  filter(tgt2030 == 57, 
         efficiency == "reference", 
         bioLim == "BioLim7.5"#, 
         #lim == "default"
         )

g[["Fuel shares"]][["lim"]] <-  ggplot(plotData,aes(x=period,y=value)) +
    geom_bar(aes(fill=type),stat='identity', position="fill") +
    facet_grid(carrier~lim+sector) +
    theme_doubleColumn() +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(values = plotColor) + 
    theme(plot.background = element_rect(fill = 'white', colour = 'white'))

ggsave(paste0(outChartsFolder,"/svg/Fuel shares - tgt57,effRef,bio7p5 - lim.svg"), g[["Fuel shares"]][["lim"]], device="svg", width = 12, height = 8, dpi=100, units = "in")
ggsave(paste0(outChartsFolder,"/png/Fuel shares - tgt57,effRef,bio7p5 - lim.png"), g[["Fuel shares"]][["lim"]], device="png", width = 12, height = 8, dpi=300, units = "in")

```

## tgt2030

```{r, echo=FALSE, fig.width=12, fig.height=8}

g[["Fuel shares"]][["tgt2030"]]

```

## Efficiency

```{r, echo=FALSE, fig.width=12, fig.height=8}

g[["Fuel shares"]][["efficiency"]]

```

## BioLim

```{r, echo=FALSE, fig.width=12, fig.height=8}

g[["Fuel shares"]][["BioLim"]]

```

## Lim

```{r, echo=FALSE, fig.width=12, fig.height=8}

g[["Fuel shares"]][["lim"]]

```

<!-- <!-- # GHG Emissions --> -->

<!-- ```{r chart_, echo=FALSE, include=FALSE} -->

<!-- library(plotly) -->
<!-- plotData <- df %>%  -->
<!--   filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen) %>%  -->
<!--   calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>% -->
<!--   mutate(reduction = round((1 - (value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference))) ,2)) -->

<!-- g[["GHG emi_plotly"]] <- ggplotly(ggplot(plotData, aes(x=period,y=reduction, color=scenario)) + -->
<!--            geom_line() + -->
<!--            guides(color="none") + -->
<!--            theme_doubleColumn() + -->
<!--            scale_y_continuous(labels = scales::percent, trans="reverse") + -->
<!--            theme(axis.title.y=element_blank()) -->
<!--   ) -->

<!-- g[["GHG emi_plotly_limit"]] <- ggplotly(ggplot(plotData %>% filter(!grepl("limVRE|bio20|Nzero_55", scenario)), aes(x=period,y=reduction, color=scenario)) + -->
<!--            geom_line() + -->
<!--            guides(color="none") + -->
<!--            theme_doubleColumn() + -->
<!--            scale_y_continuous(labels = scales::percent, trans="reverse") + -->
<!--            theme(axis.title.y=element_blank()) -->
<!--   ) -->
<!-- #min(plotData %>% filter(!grepl("limVRE|bio20|Nzero_55", scenario), period == 2040) %>% pull(reduction)) -->
<!-- ``` -->

<!-- <!-- ```{r, echo=FALSE, fig.width=6, fig.height=10} --> -->

<!-- <!-- g[["GHG emi_plotly"]] --> -->

<!-- <!-- ``` --> -->

<!-- # Electricity Capacity -->

<!-- <!-- Electricity Capacity (%) --> -->

<!-- ```{r, echo=FALSE} -->

<!-- vars <- c( -->
<!-- #  "Net Imports" = "Cap|Electricity|Imports", -->
<!--   "Coal w/ CC" = "Cap|Electricity|Coal|w/ CC", -->
<!--   "Coal w/o CC" = "Cap|Electricity|Coal|w/o CC", -->
<!--   "Oil" = "Cap|Electricity|Oil", -->
<!--   "Gas w/ CC" = "Cap|Electricity|Gas|w/ CC", -->
<!--   "Gas w/o CC" = "Cap|Electricity|Gas|w/o CC", -->
<!--   "Hydrogen" = "Cap|Electricity|Hydrogen", -->
<!--   "Nuclear" = "Cap|Electricity|Nuclear", -->
<!--   "Geothermal" = "Cap|Electricity|Geothermal", -->
<!--   "Hydro" = "Cap|Electricity|Hydro", -->
<!--   "Biomass w/ CC" = "Cap|Electricity|Biomass|w/ CC", -->
<!--   "Biomass w/o CC" = "Cap|Electricity|Biomass|w/o CC", -->
<!--   "Solar CSP" = "Cap|Electricity|Solar|CSP", -->
<!--   "Solar PV" = "Cap|Electricity|Solar|PV", -->
<!--   "Wind Onshore" = "Cap|Electricity|Wind|Onshore", -->
<!--   "Wind Offshore" = "Cap|Electricity|Wind|Offshore", -->
<!--   "Storage Battery" = "Cap|Electricity|Storage|Battery" -->
<!--   ) -->

<!-- inv_vars <- setNames(names(vars),vars) -->

<!-- color <- c( -->
<!-- #  "Net Imports"   = "#472b62", -->
<!--   "Coal w/ CC"    = "#b2b2b2", -->
<!--   "Coal w/o CC"   = "#0c0c0c", -->
<!--   "Oil"           = "#b30000", -->
<!--   "Gas w/ CC"     = "#b79e38", -->
<!--   "Gas w/o CC"    = "#999959", -->
<!--   "Hydrogen"      = "#5ed5b0", -->
<!--   "Nuclear"       = "#ff33ff", -->
<!--   "Geothermal"    = "#e51900", -->
<!--   "Hydro"         = "#191999", -->
<!--   "Biomass w/ CC" = "#33ff00", -->
<!--   "Biomass w/o CC"= "#005900", -->
<!--   "Solar CSP"     = "#ffcc00", -->
<!--   "Solar PV"      = "#ffe600", -->
<!--   "Wind Onshore"  = "#193F7F", -->
<!--   "Wind Offshore" = "#337fff", -->
<!--   "Storage Battery" = "#472b62") -->

<!-- plotData <- df %>%  -->
<!--   filter(region == "EU27", period >= 2020, period <= 2060, scenario  == mainScen, variable %in% unlist(vars)) %>%  -->
<!--   mutate(variable = factor(variable, levels=vars)) %>%  -->
<!--   arrange(factor(variable, levels = rev(vars))) %>% -->
<!--   group_by(model,scenario,region,period) %>% -->
<!--   mutate(cumValue = cumsum(value), -->
<!--          n = sum(value), -->
<!--          percentage = value / n, -->
<!--          cumPercentage = cumValue / n)  -->

<!-- plotData2040 <- plotData[plotData$period == 2040,] -->
<!-- #plotData$value <- plotData$value / plotData[plotData$period == "2020",]$value -->
<!-- #plotData$period <- as.character(plotData$period) -->
<!-- #plotData$period <- factor(plotData$period , levels = rev(c("2020","2030","2040","2050"))) -->

<!-- plotData2040$xPos <- 2042.5 -->
<!-- #plotData2040[plotData2040$variable %in% c("SE|Electricity|Hydro"),]$xPos <- 2028.5 -->
<!-- #plotData2040[plotData2040$variable %in% c("SE|Electricity|Biomass|w/o CC"),]$xPos <- 2020 -->
<!-- plotData2040[plotData2040$variable %in% c("SE|Electricity|Nuclear","SE|Electricity|Biomass|w/o CC"),]$xPos <- 2035 -->

<!-- plotDataRenewables <- plotData %>% -->
<!--   filter(variable %in% c("Cap|Electricity|Hydrogen","Cap|Electricity|Geothermal","Cap|Electricity|Hydro","Cap|Electricity|Biomass|w/ CC","Cap|Electricity|Biomass|w/o CC","Cap|Electricity|Solar|CSP","Cap|Electricity|Solar|PV","Cap|Electricity|Wind|Onshore","Cap|Electricity|Wind|Offshore","Cap|Electricity|Nuclear","Cap|Electricity|Storage|Battery")) %>% -->
<!--   group_by(model,scenario,region,period) %>% -->
<!--   summarize(percentage = sum(percentage),.groups = "keep") -->

<!-- g[["Electricity Capacity"]] <-  -->
<!--   ggplot(plotData,aes(x=period,y=percentage)) + -->
<!--   geom_area(aes(fill=variable),alpha=0.4) + -->
<!--   geom_line(data=plotDataRenewables, linetype = "dashed", linewidth = 1.5, color="#666666") + -->
<!--   geom_bar(data=plotData2040,aes(fill=variable),stat='identity', show.legend = FALSE, alpha = 0.7, color="white", width = 3, linewidth = 1.5) + -->
<!--   #ggrepel::geom_text_repel(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(round(percentage,2)*100,"%"), y=cumPercentage-percentage/2, x = 2043.5), vjust=0.5, hjust=0.5, na.rm=TRUE, color = "black", size = 12) + -->
<!--   #geom_text(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(inv_vars[variable], " (",round(percentage,2)*100,"%)"), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size = 12) + -->
<!--   geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geom.text.double.size) + -->
<!--   theme_doubleColumn()  + -->
<!--   scale_y_continuous(minor_breaks = seq(0.2, 0.8, 0.2), breaks=c(0,1),labels = scales::percent) + -->
<!--   scale_x_continuous(breaks=c(2020,2040,2060)) + -->
<!--   scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) + -->
<!--   theme(axis.title.y=element_blank()) + -->
<!--   guides(fill=guide_legend(nrow=8,override.aes = list(alpha=1), byrow = TRUE)) + -->
<!--   #annotate(geom = "text", x = 2022, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage + 0.06, label = "renewables", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) + -->
<!--   #annotate(geom = "text", x = 2023, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage - 0.06, label = "and nuclear", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) + -->
<!--   #annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geom.text.double.size) + -->
<!--   annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, label = "renewables,\nnuclear and hydrogen", color = "#666666",angle = 90, hjust=0.5, vjust=-0.5, size=geom.text.double.size, lineheight = 0.8) + -->
<!--   annotate(geom = "text", x = 2020, y = (1-plotDataRenewables[plotDataRenewables$period == 2020,]$percentage)/2+plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "fossil", color = "#666666",angle = 90, hjust=0.5, vjust=-2, size=geom.text.double.size) + -->
<!--   annotation_custom(grob = linesGrob(gp=gpar(col="#666666",lwd = 3,lty="dashed")), xmin = 2016, xmax = 2019.8, ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage) + -->
<!--   theme(axis.text.y=element_blank()) + -->
<!--   theme(legend.key.height = unit(0.8, "cm"), -->
<!--     legend.key.width = unit(0.8,"cm")) + -->
<!--   theme(legend.spacing.y = unit(0.1, 'cm')) + -->
<!--   theme() + -->
<!--   annotate(geom = "text", label = "100%", x = 2020, y = 1, hjust=1.2, color = "#666666", size=geom.text.double.size) + -->
<!--   annotate(geom = "text", label = "0%", x = 2020, y = 0, hjust=1.2, color = "#666666", size=geom.text.double.size) + -->
<!--   coord_cartesian(clip = 'off') + -->
<!--   theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 20, unit = "pt") -->
<!--         #,legend.margin=margin(l = -2, unit='cm') -->
<!--         ) #+ -->
<!--   #annotation_custom( -->
<!--   #  grob = textGrob(label = "renewables\nand nuclear",hjust=0.5, vjust=-0.5, rot = 90, gp=gpar(col="#666666", fontsize=geom.text.double.size)), -->
<!--   #  ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, -->
<!--   #  xmin = 2020, xmax = 2020) -->

<!-- ggsave(paste0(outChartsFolder,"/svg/Electricity Capacity.svg"), g[["Electricity Capacity"]] , device="svg", width = 6, height = 10, dpi=100, units = "in") -->
<!-- ggsave(paste0(outChartsFolder,"/png/Electricity Capacity.png"), g[["Electricity Capacity"]] , device="png", width = 6, height = 10, dpi=300, units = "in") -->

<!-- ``` -->

<!-- ```{r, echo=FALSE, fig.width=6, fig.height=10} -->

<!-- g[["Electricity Capacity"]] -->

<!-- ``` -->

<!-- --- -->

<!-- # Electricity flexible Capacity -->

<!-- <!-- Electricity flexible Capacity (GW) --> -->

<!-- ```{r, echo=FALSE} -->

<!-- vars <- list( -->
<!--   "Variable Renewables" = c( -->
<!--     "Cap|Electricity|Solar|CSP", "Cap|Electricity|Solar|PV", "Cap|Electricity|Wind|Onshore", "Cap|Electricity|Wind|Offshore" -->

<!--   ), -->
<!--   "Hydrogen and batteries" = c( -->
<!--     "Cap|Electricity|Hydrogen","Cap|Electricity|Storage|Battery" -->

<!--   ), -->
<!--   "Dispatchable fossil" = c( -->
<!--     "Cap|Electricity|Coal|w/ CC", "Cap|Electricity|Coal|w/o CC", "Cap|Electricity|Oil", "Cap|Electricity|Gas|w/ CC", "Cap|Electricity|Gas|w/o CC" -->
<!--   ), -->
<!--   "Other non dispatchable" = c("Cap|Electricity|Nuclear", "Cap|Electricity|Geothermal", "Cap|Electricity|Hydro", "Cap|Electricity|Biomass|w/ CC", "Cap|Electricity|Biomass|w/o CC" -->
<!--   ) -->
<!-- ) -->

<!-- plotData <- NULL -->
<!-- for(group in names(vars)){ -->
<!--   plotData <- rbind( -->
<!--     plotData, -->
<!--     df %>%  -->
<!--       filter(region == "EU27",  -->
<!--              period >= 2020, period <= 2060,  -->
<!--              scenario  == mainScen,  -->
<!--              variable %in% unlist(vars[[group]])) %>% -->
<!--       group_by(model,scenario,region,period) %>% -->
<!--       summarize(value = sum(value),.groups = "keep") %>% -->
<!--       mutate(variable = group) -->
<!--     ) -->
<!--   } -->

<!-- plotData <- plotData %>% -->
<!--    mutate(variable = factor(variable, levels=names(vars))) %>%  -->
<!--    arrange(factor(variable, levels = names(vars)))  -->

<!-- # plotData <- plotData %>% -->
<!-- #   mutate(variable = factor(variable, levels=names(vars))) %>%  -->
<!-- #   arrange(factor(variable, levels = names(vars))) %>% -->
<!-- #   group_by(model,scenario,region,period) %>% -->
<!-- #   mutate(cumValue = cumsum(value), -->
<!-- #          n = sum(value), -->
<!-- #          percentage = value / n, -->
<!-- #          cumPercentage = cumValue / n)  -->

<!-- #inv_vars <- setNames(names(vars),vars) -->

<!-- color <- c( -->
<!--   "Variable Renewables"       = "#003b6d", -->
<!--   "Hydrogen and batteries"   = "#6699cc", -->
<!--   "Dispatchable fossil"   = "#bdbdbd", -->
<!--   "Other non dispatchable"    = "#676767") -->

<!-- #plotData2040 <- plotData[plotData$period == 2040,] -->
<!-- #  -->
<!-- #plotData2040$xPos <- 2042.5 -->
<!-- #plotData2040[plotData2040$variable %in% c("SE|Electricity|Nuclear","SE|Electricity|Biomass|w/o CC"),]$xPos <- 2035 -->
<!-- #  -->
<!-- # plotDataRenewables <- plotData %>% -->
<!-- #   filter(variable %in% c("Cap|Electricity|Hydrogen","Cap|Electricity|Geothermal","Cap|Electricity|Hydro","Cap|Electricity|Biomass|w/ CC","Cap|Electricity|Biomass|w/o CC","Cap|Electricity|Solar|CSP","Cap|Electricity|Solar|PV","Cap|Electricity|Wind|Onshore","Cap|Electricity|Wind|Offshore","Cap|Electricity|Nuclear","Cap|Electricity|Storage|Battery")) %>% -->
<!-- #   group_by(model,scenario,region,period) %>% -->
<!-- #   summarize(percentage = sum(percentage),.groups = "keep") -->

<!-- g[["Electricity flexible capacity"]] <-  -->
<!--   ggplot(plotData,aes(x=period,y=value)) + -->
<!--   geom_area(aes(fill=variable), alpha = 0.9) + -->
<!--   #geom_line(data=plotDataRenewables, linetype = "dashed", linewidth = 1.5, color="#666666") + -->
<!--   #geom_bar(data=plotData2040,aes(fill=variable),stat='identity', show.legend = FALSE, alpha = 0.7, color="white", width = 3, linewidth = 1.5) + -->
<!--   #ggrepel::geom_text_repel(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(round(percentage,2)*100,"%"), y=cumPercentage-percentage/2, x = 2043.5), vjust=0.5, hjust=0.5, na.rm=TRUE, color = "black", size = 12) + -->
<!--   #geom_text(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(inv_vars[variable], " (",round(percentage,2)*100,"%)"), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size = 12) + -->
<!--   #geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geom.text.double.size) + -->
<!--   theme_doubleColumn()  + -->
<!--   #scale_y_continuous(minor_breaks = seq(0.2, 0.8, 0.2), breaks=c(0,1),labels = scales::percent) + -->
<!--   scale_x_continuous(breaks=c(2020,2040,2060)) + -->
<!--   scale_fill_manual(values = color) + -->
<!--   theme(axis.title.y=element_blank()) + -->
<!--   guides(fill=guide_legend(nrow=8,override.aes = list(alpha=1), byrow = TRUE)) + -->
<!--   #annotate(geom = "text", x = 2022, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage + 0.06, label = "renewables", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) + -->
<!--   #annotate(geom = "text", x = 2023, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage - 0.06, label = "and nuclear", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) + -->
<!--   #annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geom.text.double.size) + -->
<!--   #annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, label = "renewables,\nnuclear and hydrogen", color = "#666666",angle = 90, hjust=0.5, vjust=-0.5, size=geom.text.double.size, lineheight = 0.8) + -->
<!--   #annotate(geom = "text", x = 2020, y = (1-plotDataRenewables[plotDataRenewables$period == 2020,]$percentage)/2+plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "fossil", color = "#666666",angle = 90, hjust=0.5, vjust=-2, size=geom.text.double.size) + -->
<!--   #annotation_custom(grob = linesGrob(gp=gpar(col="#666666",lwd = 3,lty="dashed")), xmin = 2016, xmax = 2019.8, ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage) + -->
<!--   #theme(axis.text.y=element_blank()) + -->
<!--   theme(legend.key.height = unit(0.8, "cm"), -->
<!--     legend.key.width = unit(0.8,"cm")) + -->
<!--   theme(legend.spacing.y = unit(0.1, 'cm')) + -->
<!--   theme() + -->
<!--   #annotate(geom = "text", label = "100%", x = 2020, y = 1, hjust=1.2, color = "#666666", size=geom.text.double.size) + -->
<!--   #annotate(geom = "text", label = "0%", x = 2020, y = 0, hjust=1.2, color = "#666666", size=geom.text.double.size) + -->
<!--   coord_cartesian(clip = 'off') + -->
<!--   theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 20, unit = "pt") -->
<!--         #,legend.margin=margin(l = -2, unit='cm') -->
<!--         ) #+ -->
<!--   #annotation_custom( -->
<!--   #  grob = textGrob(label = "renewables\nand nuclear",hjust=0.5, vjust=-0.5, rot = 90, gp=gpar(col="#666666", fontsize=geom.text.double.size)), -->
<!--   #  ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, -->
<!--   #  xmin = 2020, xmax = 2020) -->

<!-- ggsave(paste0(outChartsFolder,"/svg/Electricity flexible capacity.svg"), g[["Electricity flexible capacity"]] , device="svg", width = 6, height = 10, dpi=100, units = "in") -->
<!-- ggsave(paste0(outChartsFolder,"/png/Electricity flexible capacity.png"), g[["Electricity flexible capacity"]] , device="png", width = 6, height = 10, dpi=300, units = "in") -->

<!-- ``` -->

<!-- ```{r, echo=FALSE, fig.width=6, fig.height=10} -->

<!-- g[["Electricity flexible capacity"]] -->

<!-- ``` -->

<!-- Electricity Generation - Hydrogen input (%) -->

<!-- ```{r, echo=FALSE} -->

<!-- vars <- c( -->
<!--   "Net Imports" = "SE|Electricity|Net Imports", -->
<!--   "Coal w/ CC" = "SE|Electricity|Coal|w/ CC", -->
<!--   "Coal w/o CC" = "SE|Electricity|Coal|w/o CC", -->
<!--   "Oil" = "SE|Electricity|Oil", -->
<!--   "Gas w/ CC" = "SE|Electricity|Gas|w/ CC", -->
<!--   "Gas w/o CC" = "SE|Electricity|Gas|w/o CC", -->
<!--   "Hydrogen" = "SE|Input|Electricity|Hydrogen", -->
<!--   "Nuclear" = "SE|Electricity|Nuclear", -->
<!--   "Geothermal" = "SE|Electricity|Geothermal", -->
<!--   "Hydro" = "SE|Electricity|Hydro", -->
<!--   "Biomass w/ CC" = "SE|Electricity|Biomass|w/ CC", -->
<!--   "Biomass w/o CC" = "SE|Electricity|Biomass|w/o CC", -->
<!--   "Solar CSP" = "SE|Electricity|Solar|CSP", -->
<!--   "Solar PV" = "SE|Electricity|Solar|PV", -->
<!--   "Wind Onshore" = "SE|Electricity|Wind|Onshore", -->
<!--   "Wind Offshore" = "SE|Electricity|Wind|Offshore") -->

<!-- inv_vars <- setNames(names(vars),vars) -->

<!-- color <- c( -->
<!--   "Net Imports"   = "#472b62", -->
<!--   "Coal w/ CC"    = "#b2b2b2", -->
<!--   "Coal w/o CC"   = "#0c0c0c", -->
<!--   "Oil"           = "#b30000", -->
<!--   "Gas w/ CC"     = "#b79e38", -->
<!--   "Gas w/o CC"    = "#999959", -->
<!--   "Hydrogen"      = "#5ed5b0", -->
<!--   "Nuclear"       = "#ff33ff", -->
<!--   "Geothermal"    = "#e51900", -->
<!--   "Hydro"         = "#191999", -->
<!--   "Biomass w/ CC" = "#33ff00", -->
<!--   "Biomass w/o CC"= "#005900", -->
<!--   "Solar CSP"     = "#ffcc00", -->
<!--   "Solar PV"      = "#ffe600", -->
<!--   "Wind Onshore"  = "#193F7F", -->
<!--   "Wind Offshore" = "#337fff") -->

<!-- plotData <- df %>%  -->
<!--   filter(region == "EU27", period >= 2020, period <= 2060, scenario  == mainScen, variable %in% unlist(vars)) %>%  -->
<!--   mutate(variable = factor(variable, levels=vars)) %>%  -->
<!--   arrange(factor(variable, levels = rev(vars))) %>% -->
<!--   group_by(model,scenario,region,period) %>% -->
<!--   mutate(cumValue = cumsum(value), -->
<!--          n = sum(value), -->
<!--          percentage = value / n, -->
<!--          cumPercentage = cumValue / n)  -->

<!-- plotData2040 <- plotData[plotData$period == 2040,] -->
<!-- #plotData$value <- plotData$value / plotData[plotData$period == "2020",]$value -->
<!-- #plotData$period <- as.character(plotData$period) -->
<!-- #plotData$period <- factor(plotData$period , levels = rev(c("2020","2030","2040","2050"))) -->

<!-- plotData2040$xPos <- 2042.5 -->
<!-- #plotData2040[plotData2040$variable %in% c("SE|Electricity|Hydro"),]$xPos <- 2028.5 -->
<!-- #plotData2040[plotData2040$variable %in% c("SE|Electricity|Biomass|w/o CC"),]$xPos <- 2020 -->
<!-- plotData2040[plotData2040$variable %in% c("SE|Electricity|Nuclear","SE|Electricity|Biomass|w/o CC"),]$xPos <- 2035 -->

<!-- plotDataRenewables <- plotData %>% -->
<!--   filter(variable %in% c("SE|Input|Electricity|Hydrogen", "SE|Electricity|Geothermal","SE|Electricity|Hydro","SE|Electricity|Biomass|w/ CC","SE|Electricity|Biomass|w/o CC","SE|Electricity|Solar|CSP","SE|Electricity|Solar|PV","SE|Electricity|Wind|Onshore","SE|Electricity|Wind|Offshore","SE|Electricity|Nuclear")) %>% -->
<!--   group_by(model,scenario,region,period) %>% -->
<!--   summarize(percentage = sum(percentage),.groups = "keep") -->

<!-- g[["Electricity Generation - Hydrogen input"]] <-  -->
<!--   ggplot(plotData,aes(x=period,y=percentage)) + -->
<!--   geom_area(aes(fill=variable),alpha=0.4) + -->
<!--   geom_line(data=plotDataRenewables, linetype = "dashed", linewidth = 1.5, color="#666666") + -->
<!--   geom_bar(data=plotData2040,aes(fill=variable),stat='identity', show.legend = FALSE, alpha = 0.7, color="white", width = 3, linewidth = 1.5) + -->
<!--   #ggrepel::geom_text_repel(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(round(percentage,2)*100,"%"), y=cumPercentage-percentage/2, x = 2043.5), vjust=0.5, hjust=0.5, na.rm=TRUE, color = "black", size = 12) + -->
<!--   #geom_text(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(inv_vars[variable], " (",round(percentage,2)*100,"%)"), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size = 12) + -->
<!--   geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geom.text.double.size) + -->
<!--   theme_doubleColumn()  + -->
<!--   scale_y_continuous(minor_breaks = seq(0.2, 0.8, 0.2), breaks=c(0,1),labels = scales::percent) + -->
<!--   scale_x_continuous(breaks=c(2020,2040,2060)) + -->
<!--   scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) + -->
<!--   theme(axis.title.y=element_blank()) + -->
<!--   guides(fill=guide_legend(nrow=8,override.aes = list(alpha=1), byrow = TRUE)) + -->
<!--   #annotate(geom = "text", x = 2022, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage + 0.06, label = "renewables", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) + -->
<!--   #annotate(geom = "text", x = 2023, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage - 0.06, label = "and nuclear", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) + -->
<!--   #annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geom.text.double.size) + -->
<!--   annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, label = "renewables,\nnuclear and hydrogen", color = "#666666",angle = 90, hjust=0.5, vjust=-0.5, size=geom.text.double.size, lineheight = 0.8) + -->
<!--   annotate(geom = "text", x = 2020, y = (1-plotDataRenewables[plotDataRenewables$period == 2020,]$percentage)/2+plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "fossil", color = "#666666",angle = 90, hjust=0.5, vjust=-2, size=geom.text.double.size) + -->
<!--   annotation_custom(grob = linesGrob(gp=gpar(col="#666666",lwd = 3,lty="dashed")), xmin = 2016, xmax = 2019.8, ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage) + -->
<!--   theme(axis.text.y=element_blank()) + -->
<!--   theme(legend.key.height = unit(0.8, "cm"), -->
<!--     legend.key.width = unit(0.8,"cm")) + -->
<!--   theme(legend.spacing.y = unit(0.1, 'cm')) + -->
<!--   theme() + -->
<!--   annotate(geom = "text", label = "100%", x = 2020, y = 1, hjust=1.2, color = "#666666", size=geom.text.double.size) + -->
<!--   annotate(geom = "text", label = "0%", x = 2020, y = 0, hjust=1.2, color = "#666666", size=geom.text.double.size) + -->
<!--   coord_cartesian(clip = 'off') + -->
<!--   theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 20, unit = "pt") -->
<!--         #,legend.margin=margin(l = -2, unit='cm') -->
<!--         ) #+ -->
<!--   #annotation_custom( -->
<!--   #  grob = textGrob(label = "renewables\nand nuclear",hjust=0.5, vjust=-0.5, rot = 90, gp=gpar(col="#666666", fontsize=geom.text.double.size)), -->
<!--   #  ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, -->
<!--   #  xmin = 2020, xmax = 2020) -->

<!-- ggsave(paste0(outChartsFolder,"/svg/Electricity Generation - Hydrogen input.svg"), g[["Electricity Generation - Hydrogen input"]] , device="svg", width = 6, height = 10, dpi=100, units = "in") -->
<!-- ggsave(paste0(outChartsFolder,"/png/Electricity Generation - Hydrogen input.png"), g[["Electricity Generation - Hydrogen input"]] , device="png", width = 6, height = 10, dpi=300, units = "in") -->

<!-- ``` -->

<!-- ```{r, echo=FALSE, fig.width=6, fig.height=10} -->

<!-- g[["Electricity Generation - Hydrogen input"]] -->

<!-- ``` -->

<!-- --- -->

<!-- ```{r chart_figure5, echo=FALSE} -->

<!-- # “existent targets” -->
<!-- # emission reduction - 2030 (FitFor55) - 2030 scenarios - 2040 scenarios -->
<!-- # energy savings  - 2030 (FitFor55 and REPowerEU) - 2030 scenarios - 2040 scenarios -->
<!-- # renewables target - 2030 (RED II, RED II revised, REPowerEU) - 2030 scenarios - 2040 scenarios -->
<!-- # solar photovoltaics capacity - 2030 (REPowerEU) - 2030 scenarios - 2040 scenarios -->
<!-- # CCS capacity target - 2030 EU-wide 50 MtCO2/y “Net-Zero Industry Act" -->
<!-- # “implicit targets” -->
<!-- # electrification? -> fe electrification share -> 45% -->
<!-- # “carbon-content in electricity” ->“carbon-free electricity” (>95%)  -->
<!-- # Total Residual Fossil emissions -->
<!-- # sectoral emissions -> Transport emissions -> 23% of 2020  -->
<!-- #                                   -> Industry and buildings emissions -> 27% of 2020 -->
<!-- # “residual fossil”     -> Complete coal-phase by 2040 -->
<!-- #                                  -> natural gas -->
<!-- #                                 -> oil -->
<!-- # “net trade” -> net-supply independency of gas by 2040 -->
<!-- #                       -> one third of oil imports by 2040 -->

<!-- #Emissions Reduction -->
<!-- plotData <- rbind( -->
<!--     df %>%  -->
<!--       filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>% -->
<!--       calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%  -->
<!--       mutate(value = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)) ,2)) %>%  -->
<!--       select(-variable) -->
<!--     , -->
<!--     df %>%  -->
<!--       filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>% -->
<!--       calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%  -->
<!--       mutate(value = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)) ,2)) %>%  -->
<!--       select(-variable) -->
<!--   ) %>% -->
<!--   filter(tgt2050 != "Npi") %>% -->
<!--   mutate(target = "Emissions\nreductions") %>% -->
<!--   group_by(period) %>%  -->
<!--   mutate(min = min(value), -->
<!--         max = max(value)) -->

<!-- fullPlotData <- plotData  -->

<!-- h <- refEmi %>% filter(variable == "Emissions with LULUCF and with international transport", region == "EU27", pollutant == "All greenhouse gases - (CO2 equivalent)") %>% ungroup() %>% select(region,variable,period,value) -->
<!-- emi1990 <- tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference) -->
<!-- reduction_h <- 1- (h %>% filter(period==2022) %>% pull(value) / emi1990) -->

<!-- g[["milestone - vert"]][["Emissions reductions"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
<!--   geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
<!--   annotate("text", x = Inf, y = 0.55, label = "FitFor55", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
<!--   geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
<!--   annotate("text", x = Inf, y = reduction_h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
<!--   facet_grid(.~target, scales="free") + -->
<!--   theme_doubleColumn() + -->
<!--   theme(axis.title.y=element_blank()) + -->
<!--   theme(strip.text.y = element_blank()) + -->
<!--   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) + -->
<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
<!--   expand_limits(y=c(0,1)) +  -->
<!--   theme(panel.spacing = unit(4, "lines")) + -->
<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
<!--   theme(strip.placement = "outside") + -->
<!--   theme(strip.text = element_text(angle = 90)) + -->
<!--   coord_cartesian(clip = 'off') #+ -->
<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->

<!-- # Final Energy Demand - Energy savings -->
<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "FE|w/o Non-energy Use w/o Bunkers") %>% select(-variable) %>% -->
<!--   mutate(value = round(value * 23.8845896627496)) %>% -->
<!--   filter(tgt2050 != "Npi") %>% -->
<!--   mutate(target = "Final Energy\nDemand") %>% -->
<!--   group_by(period) %>%  -->
<!--   mutate(min = min(value), -->
<!--         max = max(value)) -->

<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->

<!-- h <- addHist$FE_consumption %>% #TJ -->
<!--   mutate(value = value/1000000) %>% #EJ -->
<!--   mutate(value = round(value * 23.8845896627496)) # 1EJ = 23.8845896627496 Mtoe -->

<!-- g[["milestone - vert"]][["Energy savings"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
<!--   geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
<!--   geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
<!--   annotate("text", x = Inf, y = 750, label = "REPowerEU", vjust = 1.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
<!--   annotate("text", x = Inf, y = 787, label = "FitFor55", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
<!--   geom_hline(yintercept=h %>% filter(period==2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
<!--   annotate("text", x = Inf, y = h %>% filter(period==2022) %>% pull(value), label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
<!--   facet_grid(.~target, scales="free") + -->
<!--   theme_doubleColumn() + -->
<!--   theme(axis.title.y=element_blank()) + -->
<!--   theme(strip.text.y = element_blank()) + -->
<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
<!--   expand_limits(y=c(0,400,1000)) +  -->
<!--   theme(panel.spacing = unit(4, "lines")) + -->
<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
<!--   theme(strip.placement = "outside") + -->
<!--   theme(strip.text = element_text(angle = 90)) + -->
<!--   coord_cartesian(clip = 'off') + -->
<!--   annotate("text", x = -Inf, y = Inf, label = "(Mtoe)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+ -->
<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->

<!-- # Electricity Demand -->
<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "FE|Electricity") %>% select(-variable) %>% -->
<!--   mutate(value = round(value * 1/0.0036)) %>% -->
<!--   filter(tgt2050 != "Npi") %>% -->
<!--   mutate(target = "Electricity\nDemand") %>% -->
<!--   group_by(period) %>%  -->
<!--   mutate(min = min(value), -->
<!--         max = max(value)) -->

<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->

<!-- #2022 = 2469471.42 GWh = 2469471.42 *1000 / 8.76E+09 * 31.536 EJ - FE electricity - https://ec.europa.eu/eurostat/databrowser/bookmark/d19a01c7-6099-4b88-8ccd-c6bcc01c3ddc?lang=en -->
<!-- h <- 2469471.42 /1000 -->
<!-- # old value? 2641 -->

<!-- g[["milestone - vert"]][["Electricity Demand"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
<!--   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
<!--   annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
<!--   facet_grid(.~target, scales="free") + -->
<!--   theme_doubleColumn() + -->
<!--   theme(axis.title.y=element_blank()) + -->
<!--   theme(strip.text.y = element_blank()) + -->
<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
<!--   expand_limits(y=c(0,5000)) +  -->
<!--   theme(panel.spacing = unit(4, "lines")) + -->
<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
<!--   theme(strip.placement = "outside") + -->
<!--   theme(strip.text = element_text(angle = 90)) + -->
<!--   coord_cartesian(clip = 'off') + -->
<!--   annotate("text", x = -Inf, y = Inf, label = "(TWh)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+ -->
<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->

<!-- # Renewables share -->
<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "SE|Renewables Share") %>% select(-variable) %>% -->
<!--   filter(tgt2050 != "Npi") %>% -->
<!--   mutate(target = "Renewables\nShare in\nFinal Energy")  -->

<!-- plotData$value <- plotData$value*( -->
<!--   addHist$res %>% filter(type == "RES", period == 2020) %>% pull(value) / -->
<!--    df %>% filter(region == "EU27", period == 2020, variable == "SE|Renewables Share", scenario == mainScen) %>% pull(value)  -->
<!-- ) -->

<!-- plotData <- plotData %>% -->
<!--   group_by(period) %>%  -->
<!--   mutate(min = min(value), -->
<!--         max = max(value)) -->

<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->

<!-- g[["milestone - vert"]][["Renewables Share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
<!--   geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
<!--   annotate("text", x = Inf, y = 0.4, label = "RED II revised", vjust = 1.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
<!--   geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
<!--   annotate("text", x = Inf, y = 0.45, label = "REPowerEU", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
<!--   geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
<!--   annotate("text", x = Inf, y = addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
<!--   facet_grid(.~target, scales="free") + -->
<!--   theme_doubleColumn() + -->
<!--   theme(axis.title.y=element_blank()) + -->
<!--   theme(strip.text.y = element_blank()) + -->
<!--   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) + -->
<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
<!--   expand_limits(y=c(0,1)) +  -->
<!--   theme(panel.spacing = unit(4, "lines")) + -->
<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
<!--   theme(strip.placement = "outside") + -->
<!--   theme(strip.text = element_text(angle = 90)) + -->
<!--   coord_cartesian(clip = 'off') #+ -->
<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->

<!-- # Wind -->
<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Cap|Electricity|Wind") %>% select(-variable) %>% -->
<!--   filter(tgt2050 != "Npi") %>% -->
<!--   mutate(target = "Wind\ncapacity") %>% -->
<!--   group_by(period) %>%  -->
<!--   mutate(min = min(value), -->
<!--         max = max(value))  -->

<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->

<!-- g[["milestone - vert"]][["Wind capacity"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
<!--   geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
<!--   annotate("text", x = Inf, y = 255, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
<!--   facet_grid(.~target, scales="free") + -->
<!--   theme_doubleColumn() + -->
<!--   theme(axis.title.y=element_blank()) + -->
<!--   theme(strip.text.y = element_blank()) + -->
<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
<!--   expand_limits(y=c(0,1000)) +  -->
<!--   theme(panel.spacing = unit(4, "lines")) + -->
<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
<!--   theme(strip.placement = "outside") + -->
<!--   theme(strip.text = element_text(angle = 90)) + -->
<!--   coord_cartesian(clip = 'off') + -->
<!--   annotate("text", x = -Inf, y = Inf, label = "(GW)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+ -->
<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->

<!-- # Solar photovoltaics -->
<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Cap|Electricity|Solar|PV") %>% select(-variable) %>% -->
<!--   filter(tgt2050 != "Npi") %>% -->
<!--   mutate(target = "Solar\nphotovoltaics") %>% -->
<!--   group_by(period) %>%  -->
<!--   mutate(min = min(value), -->
<!--         max = max(value))  -->

<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->

<!-- g[["milestone - vert"]][["Solar photovoltaics"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
<!--   geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
<!--   annotate("text", x = Inf, y = 600, label = "REPowerEU", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
<!--   geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
<!--   annotate("text", x = Inf, y = 208.9, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
<!--   facet_grid(.~target, scales="free") + -->
<!--   theme_doubleColumn() + -->
<!--   theme(axis.title.y=element_blank()) + -->
<!--   theme(strip.text.y = element_blank()) + -->
<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
<!--   expand_limits(y=c(0,2500)) +  -->
<!--   theme(panel.spacing = unit(4, "lines")) + -->
<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
<!--   theme(strip.placement = "outside") + -->
<!--   theme(strip.text = element_text(angle = 90)) + -->
<!--   coord_cartesian(clip = 'off') + -->
<!--   annotate("text", x = -Inf, y = Inf, label = "(GW)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+ -->
<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->

<!-- # Carbon Capture and Storage  -->
<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Carbon Management|Storage") %>% select(-variable) %>% -->
<!--   filter(tgt2050 != "Npi") %>% -->
<!--   mutate(target = "Carbon\nCapture and\nStorage") %>% -->
<!--   group_by(period) %>%  -->
<!--   mutate(min = min(value), -->
<!--         max = max(value))  -->

<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->

<!-- g[["milestone - vert"]][["Carbon Capture and Storage"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
<!--   geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
<!--   annotate("text", x = Inf, y = 50, label = "Net-Zero\nIndustry Act", vjust = 0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
<!--   facet_grid(.~target, scales="free") + -->
<!--   theme_doubleColumn() + -->
<!--   theme(axis.title.y=element_blank()) + -->
<!--   theme(strip.text.y = element_blank()) + -->
<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
<!--   expand_limits(y=c(0,400)) +  -->
<!--   theme(panel.spacing = unit(4, "lines")) + -->
<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
<!--   theme(strip.placement = "outside") + -->
<!--   theme(strip.text = element_text(angle = 90)) + -->
<!--   coord_cartesian(clip = 'off') + -->
<!--   annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+ -->
<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->

<!-- # Novel CDR = atmospheric/biogenic CO2 (CDR)  -->
<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Carbon Management|atmospheric/biogenic CO2 - CDR") %>% select(-variable) %>% -->
<!--   filter(tgt2050 != "Npi") %>% -->
<!--   mutate(target = "BECCS\nand\nDACCS") %>% -->
<!--   group_by(period) %>%  -->
<!--   mutate(min = min(value), -->
<!--         max = max(value))  -->

<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->

<!-- g[["milestone - vert"]][["Novel CDR"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
<!--   facet_grid(.~target, scales="free") + -->
<!--   theme_doubleColumn() + -->
<!--   theme(axis.title.y=element_blank()) + -->
<!--   theme(strip.text.y = element_blank()) + -->
<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
<!--   expand_limits(y=c(0,400)) +  -->
<!--   theme(panel.spacing = unit(4, "lines")) + -->
<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
<!--   theme(strip.placement = "outside") + -->
<!--   theme(strip.text = element_text(angle = 90)) + -->
<!--   coord_cartesian(clip = 'off') + -->
<!--   annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+ -->
<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->

<!-- # Direct Electrification -->
<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Final Energy|Electricity Share") %>% select(-variable) %>% -->
<!--   filter(tgt2050 != "Npi") %>% -->
<!--   mutate(target = "Electricity\nShare in\nFinal Energy") %>% -->
<!--   group_by(period) %>%  -->
<!--   mutate(min = min(value), -->
<!--         max = max(value))  -->

<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->

<!-- #estimation of historical share in 2022 for FE electricity / FE with non-energy use and with bunkers -->
<!-- h <- ( -->
<!--       2550461.10 *1000 / 8.76E+09 * 31.536  # https://ec.europa.eu/eurostat/databrowser/bookmark/12d54df4-7c35-47eb-a103-dd8994d26b80?lang=en -->
<!--      ) / ( -->
<!--       addHist$FE_consumption %>% mutate(value = value/1000000) %>% filter(period==2022) %>% pull(value) + # FE|w/o Non-energy Use w/o Bunkers - EJ -->
<!--       df %>% filter(region == "EU27", period == 2020, scenario == "Npi", variable == "FE|Transport|Bunkers") %>% pull(value) + -->
<!--       df %>% filter(region == "EU27", period == 2020, scenario == "Npi", variable == "FE|Non-energy Use|Industry") %>% pull(value) -->
<!--      ) -->

<!-- g[["milestone - vert"]][["Direct Electrification"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
<!--   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
<!--   annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
<!--   facet_grid(.~target, scales="free") + -->
<!--   theme_doubleColumn() + -->
<!--   theme(axis.title.y=element_blank()) + -->
<!--   theme(strip.text.y = element_blank()) + -->
<!--   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) + -->
<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
<!--   expand_limits(y=c(0,1)) +  -->
<!--   theme(panel.spacing = unit(4, "lines")) + -->
<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
<!--   theme(strip.placement = "outside") + -->
<!--   theme(strip.text = element_text(angle = 90)) + -->
<!--   coord_cartesian(clip = 'off') #+ -->
<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->

<!-- # Carbon-free electricity share -->
<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "SE|Electricity|carbon-free") %>% select(-variable) %>% -->
<!--   filter(tgt2050 != "Npi") %>% -->
<!--   mutate(target = "Carbon-free\nelectricity\nshare") %>% -->
<!--   group_by(period) %>%  -->
<!--   mutate(min = min(value), -->
<!--         max = max(value))   -->

<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->

<!-- #historical - 2022 - https://ec.europa.eu/eurostat/statistics-explained/index.php?title=Electricity_and_heat_statistics&oldid=347519 -->
<!-- #solid fossil	453180 -->
<!-- #oil	54277 -->
<!-- #gas	571687 -->
<!-- #nuclear	609169 -->
<!-- #renewables	1076710 -->
<!-- #other	32822 -->
<!-- h <- (609169 + 1076710)	/ (453180 + 54277 + 571687 + 609169 + 1076710 + 32822) -->

<!-- g[["milestone - vert"]][["Carbon-free electricity share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
<!--   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
<!--   annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
<!--   facet_grid(.~target, scales="free") + -->
<!--   theme_doubleColumn() + -->
<!--   theme(axis.title.y=element_blank()) + -->
<!--   theme(strip.text.y = element_blank()) + -->
<!--   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) + -->
<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
<!--   expand_limits(y=c(0,1)) +  -->
<!--   theme(panel.spacing = unit(4, "lines")) + -->
<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
<!--   theme(strip.placement = "outside") + -->
<!--   theme(strip.text = element_text(angle = 90)) + -->
<!--   coord_cartesian(clip = 'off') #+ -->
<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->

<!-- # Residual Fossil Emissions -->
<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% select(-variable) %>% -->
<!--   filter(tgt2050 != "Npi") %>% -->
<!--   mutate(target = "Residual\nFossil\nEmissions") %>% -->
<!--   group_by(period) %>%  -->
<!--   mutate(min = min(value), -->
<!--         max = max(value))   -->

<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->

<!-- g[["milestone - vert"]][["Residual Fossil Emissions"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
<!--   facet_grid(.~target, scales="free") + -->
<!--   theme_doubleColumn() + -->
<!--   theme(axis.title.y=element_blank()) + -->
<!--   theme(strip.text.y = element_blank()) + -->
<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
<!--   expand_limits(y=c(0,2500)) +  -->
<!--   theme(panel.spacing = unit(4, "lines")) + -->
<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
<!--   theme(strip.placement = "outside") + -->
<!--   theme(strip.text = element_text(angle = 90)) + -->
<!--   coord_cartesian(clip = 'off') + -->
<!--   annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+ -->
<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->

<!-- # Domestic Hydrogen Production -->
<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "SE|Hydrogen") %>% select(-variable) %>% -->
<!--   mutate(value = value*8)  %>% #1EJ <- 8 million tons adrian -->
<!--   filter(tgt2050 != "Npi") %>% -->
<!--   mutate(target = "Domestic\nHydrogen\nProduction") %>% -->
<!--   group_by(period) %>%  -->
<!--   mutate(min = min(value), -->
<!--         max = max(value))  -->

<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->

<!-- target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2030,2030),value=c(10,20)) -->

<!-- g[["milestone - vert"]][["Domestic Hydrogen Production"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
<!--   geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
<!--   annotate("text", x = -Inf, y = 10, label = "REPowerEU\ndomestic", vjust = 0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
<!--   facet_grid(.~target, scales="free") + -->
<!--   theme_doubleColumn() + -->
<!--   theme(axis.title.y=element_blank()) + -->
<!--   theme(strip.text.y = element_blank()) + -->
<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
<!--   expand_limits(y=c(0,20)) +  -->
<!--   theme(panel.spacing = unit(4, "lines")) + -->
<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
<!--   theme(strip.placement = "outside") + -->
<!--   theme(strip.text = element_text(angle = 90)) + -->
<!--   coord_cartesian(clip = 'off') + -->
<!--   annotate("text", x = -Inf, y = Inf, label = "(Mtoe)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+ -->
<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->

<!-- ``` -->

<!-- ```{r, echo=FALSE} -->

<!-- g[["ECEMP abstract"]] <- gridExtra::arrangeGrob( -->
<!--   g[["milestone - vert"]][["Electricity Demand"]] + theme(plot.margin=margin(r=30,t = 35)), -->
<!--   g[["milestone - vert"]][["Direct Electrification"]] + theme(plot.margin=margin(r=30,t = 17)), -->
<!--   g[["milestone - vert"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(t = 24)), -->
<!--   g[["milestone - vert"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(r=30,t = 39)), -->
<!--   g[["milestone - vert"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(r=30,t = 15)), -->
<!--   g[["milestone - vert"]][["Novel CDR"]] + theme(plot.margin=margin(t = 50)), -->
<!--   nrow = 1 -->
<!-- ) -->

<!-- ggsave(paste0(outChartsFolder,"/png/ECEMP abstract.png"), g[["ECEMP abstract"]] , device="png", width = 12, height = 8, dpi=300, units = "in") -->

<!-- ``` -->

### 2024-08-30 report_paperCharts.Rmd
revision1

---
title: "2040 greenhouse gas reduction targets and energy transitions in line with the EU Green Deal"
output:
  html_document:
    theme: paper
    toc: true
    toc_float:
      collapsed: false
params:
  forceUpdateData: FALSE
  loadHist: TRUE
  energyInMtoe: TRUE
  chartsFolder: "report_paperCharts_Mtoe"
---

<style>
  .main-container {
    max-width: 95% !important;
  }
  .toc-content {
    padding-left: 0px !important;
  }
  .svg-container {
    margin: auto !important;
  }
</style>

Description:
Charts created for the paper:

Rodrigues, R., Pietzcker, R., Sitarz, J., Merfort, A., Hasse, R., Hoppe, J., Pehl, M., Ershad, A. M., Baumstark, L., Luderer, G. 2040 greenhouse gas reduction targets and energy transitions in line with the EU Green Deal. under revision (2023).

<!-- Setting default chunk options -->
```{r chunkOptions, echo=FALSE, include = FALSE}
#knitr::opts_chunk$set(echo = TRUE)
# setting global R chunk options (https://yihui.name/knitr/options/#chunk_options)
  knitr::opts_chunk$set(dev='svglite', # svg, png,...
                        fig.ext = ".svg",
                        #fig.asp = .8 # default aspect ratio
                        fig.width = 12,
                        fig.height = 6,
                        dpi=100
                        )
```

```{r loading_packages, echo=FALSE, include = FALSE}

  #Loading required packages
  # install.packages("remotes")
  #remotes::install_github("coolbutuseless/ggpattern")
  #install.packages('rsvg')
  #remotes::install_github('coolbutuseless/ggsvg')
  packagesList <- c("quitte","ggplot2","geomtextpath","ggpattern","tidyr","grid","stringr","gridExtra","ggrepel","kableExtra","dplyr","remind2","rsvg","ggsvg")
  packages <- suppressWarnings(suppressMessages(lapply(packagesList, function(x){ if(!require(x, character.only = T, quietly = T)){ install.packages(x); return(paste0("installed missing package: ", x)) } else paste0("required package is installed: ", x) } )))

```

```{r options, echo=FALSE, include = FALSE}

#Options
forceUpdateData <- params$forceUpdateData
loadHist <- params$loadHist
energyInMtoe <- params$energyInMtoe
chartsFolder <- params$chartsFolder

```

<!-- Preprocess: prepare and load the data for use in the charts and markdown -->

```{r preprocess, echo=FALSE, include = FALSE}

# data and output folders
folders <- file.info(list.files(path="./data", full.names = T))
dataFolder <- folders %>% tibble::rownames_to_column(var = "path") %>% arrange(desc(path)) %>% slice(1) %>% pull(path)

source("./R/preprocess.R")

#create output folders
outFolder <- paste0("./output/",gsub("./data/","",dataFolder))
outChartsFolder <- paste0(outFolder,"/", chartsFolder)
dir.create(paste0(outChartsFolder,"/png"), recursive = TRUE, showWarnings = FALSE)
dir.create(paste0(outChartsFolder,"/svg"), recursive = TRUE, showWarnings = FALSE)

```

<!-- units conversion -->

```{r unitsConversion, echo=FALSE, include = FALSE}

# conversion factors
  EJ2Mtoe <- 23.8845896627496 # 1EJ = 23.8845896627496 Mtoe

  #1EJ <- 7 million tons #https://hydrogencouncil.com/wp-content/uploads/2017/11/Hydrogen-Scaling-up_Hydrogen-Council_2017.compressed.pdf
  #1 EJ is provided by 7 million tons or 78 billion cubic meters of gaseous hydrogen.
  #It is equivalent to 990 billion British thermal units, 278 TWh of electricity, and roughly 170 million barrels of oil or 290 billion cubic feet of natural gas.
  #1EJ <- 8 million tons adrian
  EJ2MtH2 <- 8

  EJ2TWh <- 1/0.0036

```

<!-- Markdown Data Section -->

<!-- Calculating results specifically for the paper -->
```{r calculatingPaperResults, echo=FALSE, include=FALSE}

mainScen <- "Nzero_57_bio7p5" # "Nzero_55_ff55Eff_bio7p5" #Nzero_55_ff55Eff_bio12" # #Nzero_55_bio12" #"Nzero_55_ff55Eff_bio12"
tgt2030Scen <- c(55,57,59)

#loading reference emissions
source("./R/calcResults.R")

```

---

# Data {.tabset}

<!-- Outputs -->

## Reference emissions

```{r data_referenceEmissions, echo=FALSE}

selectedTgt %>%
  replace(is.na(.),"") %>% 
  select(target,region,period,tgt55,tgt57,tgt59,tgt61,tgt63,tgt65) %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

---

## Efficiency targets

```{r data_efficiencyTargets, echo=FALSE}

effTgt %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

---

## 2040 Emission Reductions

```{r data_emissionsReductions, echo=FALSE}

budget %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

---

## Results

```{r data_results, echo=FALSE, fig.width=12, fig.height=5}

indirect_electrification %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

electricity_demand_upscale %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

electricity_share_in_FE %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

gen_upscale %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

wind_and_Solar_participation %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

Generation %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

share_of_fossil_in_electricity %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

primaryEnergy %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

primaryEnergyImports %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

fe_gas_and_hydrogen %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

FE_electricity %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

FE %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

share_of_sustainable_fuel %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

share_of_build_UE_heating %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

share_of_build_FE_in_relation_to_2020 %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

BEVs_in_LDV %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

chemicals_df %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

other_industry_df %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

---

## Carbon Management Results

```{r data_carbonManagement, echo=FALSE, fig.width=12, fig.height=5}

CDR %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

---

## Milestones upscaling rates

```{r data_milestones, echo=FALSE, fig.width=12, fig.height=5}

electShare %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

FEbySector_change %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

renewablesShare %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

ElectricityShare %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

hydrogenProduction %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

ElectricityDemand %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

SolarPV %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

Wind %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

residualFossils %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

<!-- Markdown Charts Section -->

<!-- Charts aesthetics -->
```{r chart_aesthetics, echo=FALSE, include=FALSE}

#loading theme and colors
source("./R/aesthetics.R")

```

<!-- Initializing charts object -->
```{r chart_initialization, echo=FALSE}

g <- NULL

```

---

# Figure 1. Emission results panel

<!-- (a) Total GHG emissions (Mt CO2eq/yr)                    (b) Emission reductions (%) -->

```{r chart_figure1a_figure1b, echo=FALSE}

# all emission reductions were calculated relative to 1990 emissions with LULUCF and international transport (4814 Mt CO2e), except for 2030 emission reduction calculated relative to 1990 emissions with LULUCF and intra-EU aviation only (4713 Mt CO2e).

plotData <- df %>% 
  filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen) %>% 
  calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T)  %>%
  group_by(model,region,variable,period) %>% 
  filter(tgt2050 != "Npi") %>% 
  mutate(ribbon.max=max(value),
         ribbon.min=min(value))

minValue <- min(plotData$value)

h <- refEmi %>% filter(variable == "Emissions with LULUCF and with international transport", region == "EU27", pollutant == "All greenhouse gases - (CO2 equivalent)") %>% ungroup() %>% select(region,variable,period,value)

emi1990 <- tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)
#linearProjection <- data.frame(period=c(2030,2035,2040,2045,2050),value=((1-seq(0,1,1/4))*(emi1990*(1-0.57))))

##emi2030 <- tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(tgt57)
emi2030 <- plotData %>% filter(scenario == mainScen, period == 2030) %>% pull(value)
linearProjection <- data.frame(period=c(2030,2035,2040,2045,2050),value=((1-seq(0,1,1/4))*(emi2030)))

g[["GHG emi"]] <- ggplot(plotData, aes(x=period,y=value)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min), alpha = 0.5, fill = "#545454") + 
    geom_line(data=plotData %>% filter(scenario == mainScen), linewidth=1.5) +
    #geom_line(data=plotData, color= "#545454", linewidth=0.2, alpha=0.2, aes(group=scenario)) +
    geom_line(data=h,linewidth=0.7,linetype="dashed") +
    geom_line(data=linearProjection,linewidth=0.8,linetype="dashed") +
    #geom_segment(data=plotData %>% filter(scenario == mainScen, period == 2040), aes(x=2040, xend=2040, y=0, yend=value), linetype="dashed", color="black") +
    geom_segment(data=linearProjection %>% filter(period == 2040), aes(x=2040, xend=2040, y=0, yend=value), linetype="dashed", color="black") +
    geom_point(data=plotData %>% filter(scenario == mainScen, period == 2040),size=3,shape=21,fill="white",stroke=1.5) +
    geom_point(data=linearProjection %>% filter(period == 2040),size=3,shape=21,fill="white",stroke=1.5) +
    geom_label_repel(data=data.frame(period=c(2042.5),value=mean(linearProjection %>% filter(period %in% c(2040,2045)) %>% pull(value))),
                     label = "linear reduction",
                     nudge_x = 10,
                     nudge_y = 800,
                     segment.square = TRUE,
                     point.padding = 0.6,
                     hjust = 0,
                     direction="y",
                     size = geomText.size) + 
    theme_doubleColumn() +
    theme(axis.title.y=element_blank()) +
    expand_limits(y=emi1990) +
    scale_y_continuous(breaks = c(0,1000,2000,3000,4000,5000)) +
    scale_x_continuous(breaks = seq(1990,2060,10)) +
    labs(title = expression(paste("(a) Total GHG emissions (Mt ", CO[2],"eq/yr)"))) + 
    #theme(plot.title = element_text(hjust = -0.2)) +
    theme(plot.title = element_text(margin=margin(b=20)))

plotData <- rbind(
  df %>% 
    filter(region == "EU27", period %in% c(2030:2040), tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>% 
    mutate(reduction = round(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference) ,2)) %>% 
    select(-variable)
  ,
  df %>% 
    filter(region == "EU27", period %in% c(2045:2050), tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>% 
    mutate(reduction = round(value / tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference) ,2)) %>% 
    select(-variable)
  ) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(x=ifelse(reduction>=0,period+1,NA),
         xend=ifelse(reduction>=0,period+1,NA),
         y=ifelse(reduction>=0,1,NA),
         yend=ifelse(reduction>=0,ifelse(reduction<=0,0,reduction),NA),
         bar = ifelse(period==2040,"2040","emi"),
         #label = ifelse(value>0,paste0( "- ", (1-value) * 100, "% (-", (1-intraEURed) * 100 ,"%)"),NA),
         labelY = reduction + (1-reduction)/2,
         labelX=period+1) %>%
  group_by(model,region,period) %>% 
  mutate(max=max(reduction),
         min=min(reduction),
         range=max-min,
         label= ifelse(round((1-max) * 100) == round((1-min) * 100), paste0(round((1-max) * 100), "%"), paste0(round((1-max) * 100), "% to ", round((1-min) * 100) ,"%")))

g[["target"]] <- ggplot(data=plotData,aes(x=period,y=reduction,fill=bar)) +
  geom_bar(data=plotData %>% filter(scenario == mainScen), stat='identity', show.legend = FALSE, alpha = 0.7, color="black") +
  geom_errorbar(aes(ymin=min, ymax=max), width=1, colour="black", alpha=0.9, linewidth=1.3) +
  geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
  theme_doubleColumn() +
  scale_fill_manual(values = c("emi" = "black", "2040" = "#5a788b")) + 
  guides(y = "none") +
  geom_segment(data=plotData %>% filter(scenario == mainScen), aes(x=x, y=y, xend=xend, yend=yend), arrow = arrow(length=unit(.5, 'cm')), na.rm=TRUE) +
  geom_text(data=plotData %>% filter(scenario == mainScen), aes(label = label, y=labelY, x=labelX, color=factor(period)), vjust=-1, hjust=0.5, na.rm=TRUE, size = geomText.size, angle = 90) +
  scale_color_manual(values = c("2030" = "black", "2035" = "#777777","2040" = "black", "2045" = "#777777","2050" = "black"), breaks=c("2030", "2035","2040", "2045","2050")) +
  expand_limits(y=minValue/emi1990) +
  annotate("text", x=2052, y=1, label= "1990 emissions", vjust=-1, hjust=1, size = geomText.size) +
  geom_hline(yintercept=1, color = "black", linetype="dashed", linewidth=1.5, alpha = 0.5) +
  coord_cartesian(clip = 'off') +
  scale_y_continuous(breaks = c(0,1000/emi1990,2000/emi1990,3000/emi1990,4000/emi1990,5000/emi1990)) + 
  theme(legend.position = "none") +
  labs(title = "(b) Emission reductions (%)") + 
  theme(plot.title = element_text(margin=margin(b=20)))

g[["GHG Emission reductions"]] <- gridExtra::arrangeGrob(
  g[["GHG emi"]], #+ theme(plot.margin=margin(10,10,30,10)),
  g[["target"]], # + theme(plot.margin=margin(10,10,10,10)),
  layout_matrix = rbind(c(1, 1, 1, 1, 2, 2),
                        c(1, 1, 1, 1, 2, 2))
   )
# 
#  ggsave(paste0(outChartsFolder,"/svg/Figure 1. Emission results panel - (a) GHG and (b) reduction.svg"), g[["GHG Emission reductions"]] , device="svg", width = 12, height = 5, dpi=100, units = "in")
#  ggsave(paste0(outChartsFolder,"/png/Figure 1. Emission results panel - (a) GHG and (b) reduction.png"), g[["GHG Emission reductions"]] , device="png", width = 12, height = 5, dpi=300, units = "in")

```

<!-- (c) Breakdown of residual CO2 emissions from energy and industrial processes (% in relation to 2020) -->

```{r chart_figure1c, echo=FALSE}

vars <- list(
  "Industrial\nProcesses" = "Emi|GHG|Industrial Processes",
  "Industry" = "Emi|GHG|Gross|Energy|Demand|Industry",
  "Buildings" ="Emi|GHG|Energy|Demand|Buildings",
  "Transportation" ="Emi|GHG|Energy|Demand|Transport",
  "Bunkers" = "Emi|CO2|Energy|Demand|Transport|International Bunkers",
#  "CDR" = "Emi|GHG|Gross|Energy|Demand|CDR",
#  "AFOFI" = "Emissions|CO2|Energy|Demand|AFOFI",
#  "Other Sector" ="Emissions|CO2|Energy|Demand|Other Sector",
  "Heat"="Emi|CO2|Gross|Energy|Supply|Heat",
  "Other Energy\nConversion" = "Emi|CO2|Gross|Other Energy Conversion",
    #"Hydrogen" ="Emi|CO2|Gross|Energy|Supply|Hydrogen",
    #"Liquids"="Emi|CO2|Gross|Energy|Supply|Liquids",
    #"Gases"="Emi|CO2|Gross|Energy|Supply|Gases",
    #"Solids"="Emi|CO2|Gross|Energy|Supply|Solids",
#  "Other"="Emissions|CO2|Energy|Supply|Other",
  "Electricity"="Emi|GHG|Gross|Energy|Supply|Electricity"
)
# "Emi|GHG|Agriculture",
#   "Emi|GHG|Land-Use Change",
#   "Emi|GHG|Waste",
#   "Emi|CO2|CDR|BECCS",
#   "Emi|CO2|CDR|Industry CCS|Synthetic Fuels",
#   "Emi|CO2|CDR|DACCS",
#   "Emi|CO2|CDR|EW"

plotColor <- c(
  "Electricity"= "#ffb200",
  "Heat"= "#cc0000",
  "Other Energy\nConversion" = "#0000cc",
  #"Gases"= "#999959",
  #"Liquids"= "#0000cc",
  #"Solids"= "#0c0c0c",
  #"Other" = "#79a6d2",
  #"Hydrogen" = "#5ed5b0",
  "Transportation" = "#a1dd70",
  "Bunkers" = "#ffc0cb",
  "Buildings" = "#5edfff",
  "Other Sector" = "#999959",
  "AFOFI" = "#005900",
  "Industry" = "#5f6769",
  "Industrial\nProcesses" = "#5c5c5c",
  "Other" = "#5b0d8f",
  "Waste" = "#A52A2A",
  "AFOLU" = "#4DAF4A",
  "Agriculture" = "#357933",
  "LULUCF" = "#6ec16b"
)

labels <- setNames(names(vars),vars[names(vars)])

fulldata <- df %>%
  filter(region == "EU27",
         period %in% c(2020,2030,2040),
         tgt2030 %in% tgt2030Scen,
         variable %in% unlist(vars)) %>%
  mutate(labels = factor(labels[as.character(variable)],levels = names(vars)),
         variable = factor(variable, levels = vars)) %>%
  group_by(period,variable) %>%
  mutate(min = min(value),
         max = max(value))

plotData <- fulldata %>%
  filter(scenario == mainScen) %>%
  mutate(complement = FALSE) %>%
  group_by(variable) %>%
  mutate(pct = paste0(round(value / value[period==2020],2)*100, "%")) %>%
  bind_rows(
    fulldata %>%
      filter(scenario == mainScen) %>%
      mutate(complement = TRUE) %>%
      group_by(variable) %>%
      mutate(value = value[period==2020] - value) %>%
      mutate(labels=NA)
  ) %>%
  mutate(ext_Var = ifelse(complement, paste0(as.character(variable),"_"), as.character(variable))) %>%
  arrange(period,ext_Var) %>%
  group_by(period) %>%
  arrange(variable) %>%
  mutate(ymid = as.numeric(sub("\\D+", "", period)),
         ymax = ymid + 4, ymin = ymid - 4,
         xmin = c(0, head(cumsum(value), -1)),
         xmax = cumsum(value),
         xmid = (xmax + xmin) / 2,
         ) %>%
  ungroup() %>%
  filter(complement == FALSE)

g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] <- plotData %>% 
  ggplot(aes(xmid, ymid, fill = ext_Var)) +
  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax,
                alpha = factor(period), color = variable)) +
  geom_errorbar(data=plotData %>% filter(period == 2040), aes(xmin=xmax-value+min, xmax=xmax-value+max), width=4, colour="black", alpha=0.9, linewidth=0.8) +
  geom_text(data=plotData %>% filter(period == 2020), aes(y = 2015, label = labels, group = labels, hjust=1, angle = 90), vjust=0.5, hjust=1.1, na.rm=TRUE, size = geomText.size, angle = 90, lineheight = 0.8) +
  geom_text(data=plotData %>% filter(period == 2040), aes(x=xmid , y = 2045, label = pct), vjust=0.5, hjust=-0.1, na.rm=TRUE, size = geomText.size, angle = 90) +
  scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) + 
  scale_alpha_manual(values = c(0.2, 0.3, 1)) +
  scale_color_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) +
  theme_doubleColumn() +
  theme(legend.position = "none") +
  scale_y_continuous(breaks=c(2020,2030,2040), labels=c("current",2030,2040), minor_breaks = NULL, limits=c(2008,2047)) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank()) +
  scale_x_continuous(breaks = NULL) +
  coord_cartesian(clip="off") +
  theme(plot.margin = margin(t = 30, r = 0, b = 100, l = 0, unit = "pt")) +
  labs(title = "(c) Sectoral breakdown of residual gross CO2 emissions from energy and industrial processes (% of average 2018-2022)") + 
  theme(plot.title = element_text(margin=margin(t=0,r=0,b=35,l=-200), hjust=1))

# ggsave(paste0(outChartsFolder,"/svg/Figure 1. Emission results panel - (c) Energy and Industrial Processes.svg"), g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] , device="svg", width = 12, height = 3.2, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Figure 1. Emission results panel - (c) Energy and Industrial Processes.png"), g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] , device="png", width = 12, height = 3.2, dpi=300, units = "in")

```

```{r, echo=FALSE, include=FALSE}

g[["Figure 1"]] <- gridExtra::arrangeGrob(
  g[["GHG emi"]],
  g[["target"]],
  g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]],
  layout_matrix = rbind(c(1, 1, 1, 1, 2, 2),
                        c(1, 1, 1, 1, 2, 2),
                        c(1, 1, 1, 1, 2, 2),
                        c(1, 1, 1, 1, 2, 2),
                        c(3, 3, 3, 3, 3, 3),
                        c(3, 3, 3, 3, 3, 3),
                        c(3, 3, 3, 3, 3, 3))
   )

ggsave(paste0(outChartsFolder,"/png/Figure 1. Emission results panel.png"), g[["Figure 1"]], device="png", width = 12, height = 8, dpi=300, units = "in")
ggsave(paste0(outChartsFolder,"/svg/Figure 1. Emission results panel.svg"), g[["Figure 1"]], device="svg", width = 12, height = 8, dpi=100, units = "in")

```

```{r, echo=FALSE, fig.width=12, fig.height=8}

grid.newpage()
grid.draw(g[["Figure 1"]])

```

Figure 1. Greenhouse gas emission reductions for scenarios reaching climate neutrality by 2050. Central values are given for the reference scenario (57% reduction by 2030, reference final energy projections, biomass availability limited to 7.5 EJ/yr and default CCS assumption), ranges for the full scenario ensemble.

---

# Figure 2. Electricity panel

<!-- (a) Electricity Generation (%) -->

```{r chart_figure2a, echo=FALSE}

vars <- c(
  "Net Imports" = "SE|Electricity|Net Imports",
  "Coal w/ CC" = "SE|Electricity|Coal|w/ CC",
  "Coal w/o CC" = "SE|Electricity|Coal|w/o CC",
  "Oil" = "SE|Electricity|Oil",
  "Gas w/ CC" = "SE|Electricity|Gas|w/ CC",
  "Gas w/o CC" = "SE|Electricity|Gas|w/o CC",
  "Hydrogen" = "SE|Electricity|Hydrogen",
  "Nuclear" = "SE|Electricity|Nuclear",
  "Geothermal" = "SE|Electricity|Geothermal",
  "Hydro" = "SE|Electricity|Hydro",
  "Biomass w/ CC" = "SE|Electricity|Biomass|w/ CC",
  "Biomass w/o CC" = "SE|Electricity|Biomass|w/o CC",
  "Solar CSP" = "SE|Electricity|Solar|CSP",
  "Solar PV" = "SE|Electricity|Solar|PV",
  "Wind Onshore" = "SE|Electricity|Wind|Onshore",
  "Wind Offshore" = "SE|Electricity|Wind|Offshore")

inv_vars <- setNames(names(vars),vars)

color <- c(
  "Net Imports"   = "#472b62",
  "Coal w/ CC"    = "#b2b2b2",
  "Coal w/o CC"   = "#0c0c0c",
  "Oil"           = "#b30000",
  "Gas w/ CC"     = "#b79e38",
  "Gas w/o CC"    = "#999959",
  "Hydrogen"      = "#5ed5b0",
  "Nuclear"       = "#ff33ff",
  "Geothermal"    = "#e51900",
  "Hydro"         = "#191999",
  "Biomass w/ CC" = "#33ff00",
  "Biomass w/o CC"= "#005900",
  "Solar CSP"     = "#ffcc00",
  "Solar PV"      = "#ffe600",
  "Wind Onshore"  = "#193F7F",
  "Wind Offshore" = "#337fff")

plotData <- df %>% 
  filter(region == "EU27", period >= 2020, period <= 2060, scenario  == mainScen, variable %in% unlist(vars)) %>% 
  mutate(variable = factor(variable, levels=vars)) %>% 
  arrange(factor(variable, levels = rev(vars))) %>%
  group_by(model,scenario,region,period) %>%
  mutate(cumValue = cumsum(value),
         n = sum(value),
         percentage = value / n,
         cumPercentage = cumValue / n)

plotData2040 <- plotData[plotData$period == 2040,]
#plotData$value <- plotData$value / plotData[plotData$period == "2020",]$value
#plotData$period <- as.character(plotData$period)
#plotData$period <- factor(plotData$period , levels = rev(c("2020","2030","2040","2050")))

plotData2040$xPos <- 2042.5
#plotData2040[plotData2040$variable %in% c("SE|Electricity|Hydro"),]$xPos <- 2028.5
#plotData2040[plotData2040$variable %in% c("SE|Electricity|Biomass|w/o CC"),]$xPos <- 2020
plotData2040[plotData2040$variable %in% c("SE|Electricity|Nuclear","SE|Electricity|Biomass|w/o CC"),]$xPos <- 2035

plotDataRenewables <- plotData %>%
  filter(variable %in% c("SE|Electricity|Geothermal","SE|Electricity|Hydro","SE|Electricity|Biomass|w/ CC","SE|Electricity|Biomass|w/o CC","SE|Electricity|Solar|CSP","SE|Electricity|Solar|PV","SE|Electricity|Wind|Onshore","SE|Electricity|Wind|Offshore","SE|Electricity|Nuclear")) %>%
  group_by(model,scenario,region,period) %>%
  summarize(percentage = sum(percentage),.groups = "keep")

g[["Electricity Generation"]] <- 
  ggplot(plotData,aes(x=period,y=percentage)) +
  geom_area(aes(fill=variable),alpha=0.4) +
  geom_line(data=plotDataRenewables, linetype = "dashed", linewidth = 1.5, color="#666666") +
  geom_bar(data=plotData2040,aes(fill=variable),stat='identity', show.legend = FALSE, alpha = 0.7, color="white", width = 3, linewidth = 1.5) +
  geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geomText.size) +
  theme_doubleColumn()  +
  scale_y_continuous(minor_breaks = seq(0.2, 0.8, 0.2), breaks=c(0,1),labels = scales::percent) +
  scale_x_continuous(breaks=c(2020,2040,2060)) +
  scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
  guides(fill=guide_legend(ncol=3,override.aes = list(alpha=1))) + #, byrow = TRUE
  annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, label = "renewables\nand nuclear", color = "#666666",angle = 90, hjust=0.5, vjust=-0.5, size=geomText.size, lineheight = 0.8) +
  annotate(geom = "text", x = 2020, y = (1-plotDataRenewables[plotDataRenewables$period == 2020,]$percentage)/2+plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "fossil", color = "#666666",angle = 90, hjust=0.5, vjust=-2, size=geomText.size) +
  annotation_custom(grob = linesGrob(gp=gpar(col="#666666",lwd = 3,lty="dashed")), xmin = 2016, xmax = 2019.8, ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage) +
  #annotate(geom = "text", label = "100%", x = 2020, y = 1, hjust=1.2, color = "#666666", size=geomText.size) +
  #annotate(geom = "text", label = "0%", x = 2020, y = 0, hjust=1.2, color = "#666666", size=geomText.size) +
  coord_cartesian(clip = 'off') +
  #theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 20, unit = "pt")) +
  labs(title = "(a) Electricity Generation (%)") #+ 
  #theme(plot.title = element_text(hjust = -0.1))

# ggsave(paste0(outChartsFolder,"/svg/Figure 2. Electricity panel - (a) generation.svg"), g[["Electricity Generation"]] , device="svg", width = 6, height = 10, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Figure 2. Electricity panel - (a) generation.png"), g[["Electricity Generation"]] , device="png", width = 6, height = 10, dpi=300, units = "in")

# g[["Electricity Generation - wide"]] <- 
#   ggplot(plotData,aes(x=period,y=percentage)) +
#   geom_area(aes(fill=variable),alpha=0.4) +
#   geom_line(data=plotDataRenewables, linetype = "dashed", linewidth = 1.5, color="#666666") +
#   geom_bar(data=plotData2040,aes(fill=variable),stat='identity', show.legend = FALSE, alpha = 0.7, color="white", width = 3, linewidth = 1.5) +
#   geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geomText.size) +
#   theme_doubleColumn()  +
#   scale_y_continuous(minor_breaks = seq(0.2, 0.8, 0.2), breaks=c(0,1),labels = scales::percent) +
#   scale_x_continuous(breaks=c(2020,2040,2060)) +
#   scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
#   theme(legend.position="right") +
#   theme(legend.margin=margin(b = -2, unit='cm'))

#ggsave(paste0(outFolder_conference,"/Electricity Generation - wide.svg"), g[["Electricity Generation - wide"]] , device="svg", width = 12, height = 5, dpi=100, units = "in")
#ggsave(paste0(outFolder_conference,"/Electricity Generation - wide.png"), g[["Electricity Generation - wide"]] , device="png", width = 12, height = 5, dpi=300, units = "in")

```

<!-- (b) Solar Photovoltaics capacity (GW) -->

```{r chart_figure2b, echo=FALSE}

# Solar photovoltaics roll out
plotData <- df %>% 
  filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable == "Cap|Electricity|Solar|PV") %>% 
  filter(tgt2050 != "Npi") %>% 
  group_by(model,region,variable,period) %>% 
  mutate(ribbon.max=max(value),
         ribbon.min=min(value))

target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2025,2030),value=c(320,600))

#value <- data.frame(period=c(2025,2030,2040),value=c(plotData[plotData$period==2025,]$value,plotData[plotData$period==2030,]$value,plotData[plotData$period==2040,]$value))

# historical data
h <- hist %>% filter(model == "IRENA", region == "EU27", variable == "Cap|Electricity|Solar|PV", period >= 2005) %>% drop_na(value)

yendValue <- plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value)

g[["Solar_Photovoltaics_capacity"]] <- ggplot(plotData,aes(x=period,y=value)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_segment(aes(x=2040, y=0, xend=2040, yend=yendValue), linetype="dashed", color="black") +
    geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min), alpha = 0.5, fill = "#545454") + 
    geom_line(data=plotData %>% filter(scenario == mainScen),linewidth=1.5) +
    geom_line(data=h,linewidth=1,linetype="dashed") +
    geom_point(data=plotData %>% filter(scenario == mainScen, period %in% c(2030,2040)),size=3,shape=21,fill="white",stroke=1.5) +
    geom_point(data=target, size=3, shape=4, stroke = 1.5) +
    geom_label_repel(data=target, aes(label = paste0(round(value),"GW - ", target)),box.padding = 0.1,
                  #segment.curvature = -0.1,
                  segment.square = TRUE,
                  point.padding = 0.6,
                  nudge_x = 5,
                  #nudge_y = -0.02,
                  #force = 0.5,
                  hjust = 0,
                  direction="y", size = geomText.size, xlim = c(2020, 2070)) +
  geom_label_repel(data=plotData %>% filter(scenario == mainScen, period == 2030), aes(label = paste0(round(value),"GW")),box.padding = 0.1,
                  point.padding = 1,
                  nudge_x = -2,
                  nudge_y = 500,
                  hjust = 1, direction="y",
                  size = geomText.size) +
  geom_label_repel(data=plotData %>% filter(scenario == mainScen, period == 2040), aes(label = paste0(round(value),"GW")),box.padding = 0.1,
                  point.padding = 1,
                  nudge_x = -2,
                  nudge_y =500,
                  #hjust = 0, 
                  direction="y",
                  size = geomText.size) +
    theme_doubleColumn() + 
    coord_cartesian(clip = 'off') +
    expand_limits(y = 3000) +
    labs(title = "(b) Solar Photovoltaics capacity (GW)") #+ 
    #theme(plot.title = element_text(hjust = -0.4))

# ggsave(paste0(outChartsFolder,"/svg/Figure 2. Electricity panel - (b) solar.svg"), g[["Solar_Photovoltaics_capacity"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Figure 2. Electricity panel - (b) solar.png"), g[["Solar_Photovoltaics_capacity"]] , device="png", width = 6, height = 4, dpi=300, units = "in")

```

<!-- (c) Electricity share in final energy (%) -->

```{r chart_figure2c, echo=FALSE}

# Electricity share
vars <- c("Total" = "Final Energy|Electricity Share",
          "Transport"="Final Energy|Transport|Electricity Share",
          "Industry"="Final Energy|Industry|Electricity Share",
          "Buildings"="Final Energy|Buildings|Electricity Share")

plotData <- df %>% 
  filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
  group_by(model,region,variable,period) %>% 
  filter(tgt2050 != "Npi") %>% 
  mutate(ribbon.max=max(value),
         ribbon.min=min(value))

h_Orig <- hist[hist$model == "IEA" & hist$region == "EU27" & hist$variable %in% c("FE","FE|Electricity","FE|Transport","FE|Transport|Electricity","FE|Industry", "FE|Industry|Electricity","FE|Buildings","FE|Buildings|Electricity"),] %>% drop_na(value)

h <- rbind(
  h_Orig %>% calc_addVariable("`Final Energy|Electricity Share`" = "`FE|Electricity` / `FE`", units = "%", only.new=T),
  h_Orig %>% calc_addVariable("`Final Energy|Transport|Electricity Share`" = "`FE|Transport|Electricity` / `FE|Transport`", units = "%", only.new=T),
  h_Orig %>% calc_addVariable("`Final Energy|Industry|Electricity Share`"  = "`FE|Industry|Electricity`  / `FE|Industry`", units = "%", only.new=T),
  h_Orig %>% calc_addVariable("`Final Energy|Buildings|Electricity Share`" = "`FE|Buildings|Electricity` / `FE|Buildings`", units = "%", only.new=T))

g[["Electricity_Share"]] <- ggplot(plotData,aes(x=period,y=value)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_segment(aes(x=2040, y=0, xend=2040, yend=max(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value))), linetype="dashed", color="black") +
    geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min, fill=variable), alpha = 0.3) + 
    geom_line(data=plotData %>% filter(scenario == mainScen), linewidth=1.5,aes(color=variable)) +
    #geom_line(data=h,linewidth=1,linetype="dashed") +
    geom_point(data=plotData %>% filter(scenario == mainScen, period == 2040),size=3,shape=21,fill="white",stroke=1.5) +
    geom_line(data=h %>% filter(period >= 2005),linetype="dashed", linewidth = 1, aes(color=variable)) +
    geom_label_repel(data= plotData %>% filter(scenario == mainScen, period == 2040),
                         aes(
                           label = paste0(round(value*100),"%")),
                      box.padding = 3,
                      #segment.curvature = -0.1,
                      segment.square = TRUE,
                      point.padding = 0.6,
                      nudge_x = 5,
                      nudge_y = c(0.55,0.27,-0.05,-0.6),
                      #force = 0.5,
                      #hjust = 0,
                      direction="y"
                      , size = geomText.size
                      #, xlim = c(2020, 2070)
                      ) +
    scale_colour_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
    scale_fill_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
    theme_doubleColumn() + 
    scale_y_continuous(breaks = seq(0, 1, 0.2),labels = scales::percent) +
    expand_limits(y=c(0,1)) +
    guides(color=guide_legend(nrow=2)) +
    labs(title = "(c) Electricity share in final energy (%)\n    (includes bunker fuels and non-energy use)") #+ 
    #theme(plot.title = element_text(hjust = -0.4))

# ggsave(paste0(outChartsFolder,"/svg/Figure 2. Electricity panel - (c) electrification.svg"), g[["Electricity_Share"]] , device="svg", width = 6, height = 6, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Figure 2. Electricity panel - (c) electrification.png"), g[["Electricity_Share"]] , device="png", width = 6, height = 6, dpi=300, units = "in")

```

```{r, echo=FALSE, include=FALSE}

g[["Figure 2"]] <- gridExtra::arrangeGrob(
  g[["Electricity Generation"]],
  g[["Solar_Photovoltaics_capacity"]],
  g[["Electricity_Share"]],
  layout_matrix = rbind(c(1,1, 2,2),
                        c(1,1, 2,2),
                        c(1,1, 2,2),
                        c(1,1, 3,3),
                        c(1,1, 3,3),
                        c(1,1, 3,3),
                        c(1,1, 3,3))
   )

ggsave(paste0(outChartsFolder,"/png/Figure 2. Electricity supply and demand.png"), g[["Figure 2"]], device="png", width = 12, height = 8, dpi=300, units = "in")
ggsave(paste0(outChartsFolder,"/svg/Figure 2. Electricity supply and demand.svg"), g[["Figure 2"]], device="svg", width = 12, height = 8, dpi=100, units = "in")

```

```{r, echo=FALSE, fig.width=12, fig.height=8}

grid.newpage()
grid.draw(g[["Figure 2"]])

```

---

# Figure 3. Energy supply panel

<!-- (a) Primary energy -->

```{r chart_figure3a, echo=FALSE}

# Primary Energy
vars <- c("Oil"="PE|Oil",
          "Gas"="PE|Gas",
          "Coal"="PE|Coal",
          "Biomass" = "PE|Biomass")

plotData <- df %>% 
  filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
  mutate(variable = factor(variable, levels=vars))  %>% 
  group_by(model,region,variable,period) %>% 
  filter(tgt2050 != "Npi") %>% 
  mutate(ribbon.max=max(value),
         ribbon.min=min(value))

# historical data
h <- hist %>% filter(model == "IEA", region == "EU27", variable %in% vars, period >= 2005, period <= 2020) %>% drop_na(value) %>% filter(value != 0)

# convert unit if necessary
if(energyInMtoe){
  plotData <- plotData %>%
    mutate(value = value * EJ2Mtoe,
           ribbon.min = ribbon.min * EJ2Mtoe,
           ribbon.max = ribbon.max * EJ2Mtoe,
           unit = "Mtoe/yr")
  h <- h %>%
    mutate(value = value * EJ2Mtoe,
           unit = "Mtoe/yr")
}

g[["Primary Energy"]] <- ggplot(plotData,aes(x=period,y=value)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_segment(aes(x=2040, y=0, xend=2040, yend=max(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value))), linetype="dashed", color="black") +
    geom_line(data=plotData %>% filter(scenario == mainScen), aes(color=variable), linewidth=1.5) +
    geom_line(data=h,aes(color=variable),linewidth=1,linetype="dashed") +
    geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min, fill=variable), alpha = 0.3) + 
    #geom_point(data=plotData[plotData$period %in% c(2020,2030,2040),],size=4,shape=21,fill="white") +
    geom_point(data=plotData %>% filter(scenario == mainScen, period == 2040),aes(color=variable),size=3,shape=21,fill="white",stroke=1.5) +
    #annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geomText.size) +
    scale_color_manual(values = c(setNames(options$aesthetics$legend$color[names(vars)],vars)), labels = setNames(names(vars), vars)) +
    scale_fill_manual(values = c(setNames(options$aesthetics$legend$color[names(vars)],vars)), labels = setNames(names(vars), vars)) +
    theme_doubleColumn() + 
    expand_limits(y=c(0,1)) +
    guides(color=guide_legend(nrow=1)) +
    expand_limits(y = 30) +
    theme(legend.margin=margin(l = -2, unit='cm')) +
    labs(title = paste0("(a) Primary energy demand (", unique(plotData$unit), ")")) #+ 
    #theme(plot.title = element_text(hjust = -0.3))
    #guides(fill = FALSE)

# ggsave(paste0(outChartsFolder,"/svg/Figure 3. Energy supply panel - (a) primary energy.svg"), g[["Primary Energy"]] , device="svg", width = 6, height = 5, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Figure 3. Energy supply panel - (a) primary energy.png"), g[["Primary Energy"]] , device="png", width = 6, height = 5, dpi=300, units = "in")

```

<!-- (c) Natural gas and syngas final energy demand -->

```{r chart_figure3c, echo=FALSE}

vars <- c(
  "Hydrogen"="FE|Hydrogen",
  "Gases"="FE|Gases"
  #"Syngas" = "FE|Gases|Hydrogen",
  #"Biogas" = "FE|Gases|Biomass",
  #"Natural gas" = "FE|Gases|Fossil"
)

plotData <- df %>% 
  filter(region == "EU27", period %in% c(2020,2030,2040,2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars), tgt2050 != "Npi") %>% 
  mutate(variable = factor(variable, levels=vars))  %>% 
  group_by(model,scenario,region,period) %>% 
  mutate(cumsum = cumsum(value),
         sum = sum(value)) %>% 
  group_by(model,region,variable,period) %>% 
  mutate(ribbon.max=max(cumsum),
         ribbon.min=min(cumsum)) %>% 
  group_by(model,region,period) %>% 
  mutate(ribbon.max.total=max(sum),
         ribbon.min.total=min(sum))

# convert unit if necessary
if(energyInMtoe){
  plotData <- plotData %>%
    mutate(value = value * EJ2Mtoe,
           ribbon.min = ribbon.min * EJ2Mtoe,
           ribbon.max = ribbon.max * EJ2Mtoe,
           ribbon.min.total = ribbon.min.total * EJ2Mtoe,
           ribbon.max.total = ribbon.max.total * EJ2Mtoe,
           unit = "Mtoe/yr")
}

g[["FE Gases"]] <- 
  ggplot(plotData,aes(x=period,y=value)) +
  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = variable, alpha=factor(period))) +
  #geom_errorbar(data=plotData %>% filter(period != 2020), aes(ymin=ribbon.min, ymax=ribbon.max, group=variable), width=8, colour="black", alpha=0.9, size=1,position = position_dodge(width=2)) +
  geom_errorbar(data=plotData %>% filter(period != 2020, variable == vars[1], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, linewidth=1,position = position_dodge(width=2)) +
  # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
  coord_flip() +
  theme_doubleColumn() +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank()) +
  #guides(y = "none") +
  theme(axis.title.y=element_blank()) +
  #theme(legend.position = "none") #+
  scale_fill_manual(values = setNames(options$aesthetics$legend$color[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(reverse = TRUE, nrow = 1)) +
  scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
  #theme(legend.text=element_text(size=theme.double.text.size)) +
  #scale_y_continuous(breaks = seq(0,round(ceiling(max(plotData$ribbon.max.total)),0),2)) +
  scale_y_continuous(  labels = scales::number_format(accuracy = 1)) +
  expand_limits(y=c(0,round(ceiling(max(plotData$ribbon.max.total)),0))) + 
  #scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == 2020) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2030) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value)),1))) +
  #scale_x_reverse()
  theme(legend.margin=margin(l = -2, unit='cm')) +
  labs(title = paste0("(c) Gaseous final energy demand (", unique(plotData$unit), ")")) #+ 
  #theme(plot.title = element_text(hjust = -0.5))

# ggsave(paste0(outChartsFolder,"/svg/Figure 3. Energy supply panel - (c) final energy gases.svg"), g[["FE Gases"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Figure 3. Energy supply panel - (c) final energy gases.png"), g[["FE Gases"]] , device="png", width = 6, height = 4, dpi=300, units = "in")

```

<!-- (b) Fossil trade -->

```{r chart_figure3b, echo=FALSE}

vars <- list(
 "Oil" = c("Trade|Imports|Oil","Trade|Exports|Oil"),
 "Gas" = c("Trade|Imports|Gas|Adj","Trade|Exports|Gas|Adj"),
 "Coal" = c("Trade|Imports|Coal","Trade|Exports|Coal"),
 "Biomass" = c("Trade|Imports|Biomass","Trade|Exports|Biomass")
)

carrier <- c()
for(c in names(vars)){
  for(var in vars[[c]]){
    v <- c
    names(v) <- var
    carrier <- c(carrier,v)
  }
}

plotColor <- c(
  "Imports"= "#e56b6f",
  "Exports"= "#355070"
)

# with range
plotData <- df %>% 
  filter(region == "EU27", period %in% c(2020,2030,2040,2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars), tgt2050 != "Npi") %>% 
  #mutate(variable = factor(variable, levels=vars))  %>%
  mutate(type = ifelse(grepl("Imports",variable),"Imports","Exports"),
         carrier = carrier[as.character(variable)]) %>%
  filter(carrier != "Biomass") %>%
  mutate(value = ifelse(type == "Exports", -value,value)) %>%
  mutate(carrier = factor(carrier, levels=c("Oil","Gas","Coal","Biomass"))) %>%
  group_by(model,scenario,region,unit,period,carrier) %>%
  summarize(value=sum(value),.groups = "keep") %>%
  mutate(type="EU-27 Net-trade") %>%
  group_by(model,region,carrier,period) %>% 
  mutate(ribbon.max=max(value),
         ribbon.min=min(value))

# convert unit if necessary
if(energyInMtoe){
  plotData <- plotData %>%
    mutate(value = value * EJ2Mtoe,
           ribbon.min = ribbon.min * EJ2Mtoe,
           ribbon.max = ribbon.max * EJ2Mtoe,
           unit = "Mtoe/yr")
}

g[["security of supply - net fossil with range"]] <- 
  ggplot(plotData,aes(x=period,y=value)) +
  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = factor(period), alpha=factor(period))) +
  geom_errorbar(data=plotData %>% filter(period == 2040, scenario == mainScen), aes(ymin=ribbon.min, ymax=ribbon.max), width=4, colour="black", alpha=0.9, linewidth=1,position = position_dodge(width=2)) +
  # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
  #coord_flip() +
  facet_wrap(~carrier,nrow=1) +
  theme_doubleColumn() +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank()) +
  scale_fill_manual(values = c("2020" = "black", "2030"= "black", "2040" = "#5a788b", "2050" = "black")) +
  scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
  theme(legend.position = "none") +
  labs(title = paste0("(b) Fossil energy carriers net imports (", unique(plotData$unit), ")")) #+ 
  #theme(plot.title = element_text(hjust = -0.4))

# ggsave(paste0(outChartsFolder,"/svg/Figure 3. Energy supply panel - (b) fossil security of supply.svg"), g[["security of supply - net fossil with range"]] , device="svg", width = 6, height = 4.5, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Figure 3. Energy supply panel - (b) fossil security of supply.png"), g[["security of supply - net fossil with range"]] , device="png", width = 6, height = 4.5, dpi=300, units = "in")

```

<!-- (d) Hydrogen production (EJ/yr) -->

```{r chart_figure3d, echo=FALSE}

vars <- c(
  "Black H2 (coal)" = "SE|Hydrogen|Coal|w/o CC",
  "Gray H2 (gas)" = "SE|Hydrogen|Gas|w/o CC",
  "Blue H2 (fossil w/ CCS)" = c("SE|Hydrogen|Coal|w/ CC", "SE|Hydrogen|Gas|w/ CC"),
  "H2 imports" = "SE|Hydrogen|Net Imports",
#  "Bio-based H2 (gasification)" = c("SE|Hydrogen|Biomass|w/ CC","SE|Hydrogen|Biomass|w/o CC"),
#  "Green H2 (electrolysis)" = "SE|Hydrogen|Electricity",
  "Green and bio-based H2" = c("SE|Hydrogen|Electricity", "SE|Hydrogen|Biomass|w/ CC","SE|Hydrogen|Biomass|w/o CC")
  #"VRE Storage Electrolysis" = "SE|Hydrogen|Electricity|VRE Storage Electrolysis",
  #"Standard Electrolysis" = "SE|Hydrogen|Electricity|Standard Electrolysis",
  )

color <- c(
  "Black H2 (coal)" = "#000000",
  "Gray H2 (gas)" = "#88888a",
  "Blue H2 (fossil w/ CCS)" = "#02abed",
  "H2 imports" = "#c18f4a",
  "Bio-based H2 (gasification)" = "#2eab83",
  "Green H2 (electrolysis)" = "#a1c44e",
  "Green and bio-based H2" = "#2eab83"
  )
#color <- setNames(options$aesthetics$legend$color[names(vars)],vars)
#color["SE|Hydrogen|Biomass|w/ CC"] <- color["SE|Hydrogen|Biomass|w/o CC"]

invertVars <- setNames(names(vars),vars)

plotData <- df %>% 
  filter(region == "EU27", period %in% c(2020,2030,2040,2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
  mutate(type = gsub("\\d$", "", as.character(invertVars[as.character(variable)]))) %>%
  group_by(model,scenario,region,unit,period,type) %>%
  summarize(value=sum(value),.groups = "keep") %>%
  mutate(type=factor(type, levels=unique(gsub("\\d$", "", names(vars))))) %>%
  #mutate(value = value*8) %>% #1EJ <- 8 million tons adrian
  group_by(model,scenario,region,period) %>% 
  mutate(cumsum = cumsum(value),
         sum = sum(value)) %>% 
  group_by(model,region,type,period) %>% 
  mutate(ribbon.max=max(cumsum),
         ribbon.min=min(cumsum)) %>% 
  group_by(model,region,period) %>% 
  mutate(ribbon.max.total=max(sum),
         ribbon.min.total=min(sum))

target <- data.frame(target=c("REPowerEU","REPowerEU"),type=c("domestic","total"),period=c(2030,2030),value=c(10,20)) %>%
  mutate(value = value/EJ2MtH2)

# convert unit if necessary
if(energyInMtoe){
  plotData <- plotData %>%
    mutate(value = value * EJ2MtH2,
           ribbon.min = ribbon.min * EJ2MtH2,
           ribbon.max = ribbon.max * EJ2MtH2,
           ribbon.min.total = ribbon.min.total * EJ2MtH2,
           ribbon.max.total = ribbon.max.total * EJ2MtH2,
           unit = "Mt H2/yr")

  target <- target %>%
    mutate(value = value * EJ2MtH2)
}

g[["Hydrogen"]] <- 
  ggplot(plotData,aes(x=period,y=value)) +
  geom_hline(yintercept= target %>% filter(type == "domestic", period == 2030) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = 2015, y = target %>% filter(type == "domestic", period == 2030) %>% pull(value), label = "REPowerEU\ndomestic", angle=90, vjust = 0.4, hjust = 0, color = "black", alpha = 0.5, size = geomText.size) +
  geom_hline(yintercept= target %>% filter(type == "total", period == 2030) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = 2015, y = target %>% filter(type == "total", period == 2030) %>% pull(value), label = "REPowerEU\ntotal", angle=90, vjust = 0.4, hjust = 0, color = "black", alpha = 0.5, size = geomText.size) +
  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = type, alpha=factor(period))) +
  geom_errorbar(data=plotData %>% filter(period != 2020, type == names(vars)[1], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, linewidth=1,position = position_dodge(width=2)) +
  coord_flip() +
  theme_doubleColumn() +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank()) +
  scale_fill_manual(values = color,
                    #labels = setNames(names(vars), vars)[c("SE|Hydrogen|Electricity", "SE|Hydrogen|Gas|w/o CC", "SE|Hydrogen|Biomass|w/ CC")],
                    #breaks = c("SE|Hydrogen|Electricity", "SE|Hydrogen|Gas|w/o CC", "SE|Hydrogen|Biomass|w/ CC"), 
                    guide = guide_legend(nrow = 3, reverse = TRUE)) +
  scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
  #theme(legend.text=element_text(size=theme.double.text.size)) +
  #scale_y_continuous(breaks = seq(0,6,1)) +
  #scale_y_continuous(breaks = seq(0,round(ceiling(max(plotData$ribbon.max.total)),0),1)) +
  scale_y_continuous(  labels = scales::number_format(accuracy = 1)) +
  theme(legend.margin=margin(l = -2, unit='cm')) +
  labs(title = paste0("(d) Hydrogen production (", unique(plotData$unit), ")")) #+ 
  #theme(plot.title = element_text(hjust = -0.4))

# ggsave(paste0(outChartsFolder,"/svg/Figure 3. Energy supply panel - (d) hydrogen.svg"), g[["Hydrogen"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Figure 3. Energy supply panel - (d) hydrogen.png"), g[["Hydrogen"]] , device="png", width = 6, height = 4, dpi=300, units = "in")

```

```{r, echo=FALSE, include=FALSE}

g[["Figure 3"]] <- gridExtra::arrangeGrob(
  g[["Primary Energy"]] + theme(plot.title = element_text(margin=margin(b=28)), plot.margin=margin(b = 10, r=10)),
  g[["security of supply - net fossil with range"]] + theme(plot.margin=margin(t = 0, b = 47, l=10)),
  g[["FE Gases"]] + theme(legend.margin=margin(b = 27, t = 10)) + theme(plot.margin=margin(r=10)),
  g[["Hydrogen"]] + theme(plot.margin=margin(l=10)),
  layout_matrix = rbind(c(1,2),
                        c(3,4))
   )

ggsave(paste0(outChartsFolder,"/png/Figure 3. Fuel Supply and Demand.png"), g[["Figure 3"]], device="png", width = 12, height = 10, dpi=300, units = "in")
ggsave(paste0(outChartsFolder,"/svg/Figure 3. Fuel Supply and Demand.svg"), g[["Figure 3"]], device="svg", width = 12, height = 10, dpi=100, units = "in")

```

```{r, echo=FALSE, fig.width=12, fig.height=10}

grid.newpage()
grid.draw(g[["Figure 3"]])

```

---

# Figure 4. Demand panel

<!-- (a) Transport final energy -->

```{r chart_figure4a, echo=FALSE}

if("FE|Transport|Freight|Navigation|Liquids|Fossil" %in% unique(df$variable)){
  FEvars <- list(
    "Domestic" = list(
      "LDV" = c(
        "FE|Transport|Pass|Road|LDV|Electricity" = "Electricity",
        "FE|Transport|Pass|Road|LDV|Gases" = "Gases",
        "FE|Transport|Pass|Road|LDV|Hydrogen" = "Hydrogen",
  #      "FE|Transport|Pass|Road|LDV|Liquids" = "Liquids"
         "FE|Transport|Pass|Road|LDV|Liquids|Fossil" = "Liquids - Fossil",
         "FE|Transport|Pass|Road|LDV|Liquids|Biomass" = "Liquids - Biomass",
          "FE|Transport|Pass|Road|LDV|Liquids|Hydrogen" = "Liquids - Synthetic"
      ),
      "Buses" = c(
        "FE|Transport|Pass|Road|Bus|Electricity" = "Electricity",
        "FE|Transport|Pass|Road|Bus|Gases" = "Gases",
        "FE|Transport|Pass|Road|Bus|Hydrogen" = "Hydrogen",
  #      "FE|Transport|Pass|Road|Bus|Liquids" = "Liquids"
          "FE|Transport|Pass|Road|Bus|Liquids|Fossil" = "Liquids - Fossil",
          "FE|Transport|Pass|Road|Bus|Liquids|Biomass" = "Liquids - Biomass",
          "FE|Transport|Pass|Road|Bus|Liquids|Hydrogen" = "Liquids - Synthetic"

      ),
      "Trucks" = c(
        "FE|Transport|Freight|Road|Electricity" = "Electricity",
        "FE|Transport|Freight|Road|Gases" = "Gases",
        "FE|Transport|Freight|Road|Hydrogen" = "Hydrogen",
  #      "FE|Transport|Freight|Road|Liquids" = "Liquids"
          "FE|Transport|Freight|Road|Liquids|Fossil" = "Liquids - Fossil",
          "FE|Transport|Freight|Road|Liquids|Biomass" = "Liquids - Biomass",
          "FE|Transport|Freight|Road|Liquids|Hydrogen" = "Liquids - Synthetic"
      ),
      "Rail" = c(
        "FE|Transport|Pass|Rail|Electricity" = "Electricity",
        "FE|Transport|Pass|Rail|Gases" = "Gases",
        "FE|Transport|Pass|Rail|Hydrogen" = "Hydrogen",
  #      "FE|Transport|Pass|Rail|Liquids" = "Liquids",
          "FE|Transport|Pass|Rail|Liquids|Fossil" = "Liquids - Fossil",
          "FE|Transport|Pass|Rail|Liquids|Biomass" = "Liquids - Biomass",
          "FE|Transport|Pass|Rail|Liquids|Hydrogen" = "Liquids - Synthetic",
        "FE|Transport|Freight|Rail|Electricity" = "Electricity",
        "FE|Transport|Freight|Rail|Gases" = "Gases",
        "FE|Transport|Freight|Rail|Hydrogen" = "Hydrogen",
  #      "FE|Transport|Freight|Rail|Liquids" = "Liquids"
          "FE|Transport|Freight|Rail|Liquids|Fossil" = "Liquids - Fossil",
          "FE|Transport|Freight|Rail|Liquids|Biomass" = "Liquids - Biomass",
          "FE|Transport|Freight|Rail|Liquids|Hydrogen" = "Liquids - Synthetic"
      ),
      "Aviation" = c(
        "FE|Transport|Pass|Aviation|Domestic|Electricity" = "Electricity",
        "FE|Transport|Pass|Aviation|Domestic|Gases" = "Gases",
        "FE|Transport|Pass|Aviation|Domestic|Hydrogen" = "Hydrogen",
  #      "FE|Transport|Pass|Aviation|Domestic|Liquids" = "Liquids"
          "FE|Transport|Pass|Aviation|Domestic|Liquids|Fossil" = "Liquids - Fossil",
          "FE|Transport|Pass|Aviation|Domestic|Liquids|Biomass" = "Liquids - Biomass",
          "FE|Transport|Pass|Aviation|Domestic|Liquids|Hydrogen" = "Liquids - Synthetic"
      )
    ),
    "International" = list(
      "Aviation" = c(
        "FE|Transport|Pass|Aviation|International|Electricity" = "Electricity",
        "FE|Transport|Pass|Aviation|International|Gases" = "Gases",
        "FE|Transport|Pass|Aviation|International|Hydrogen" = "Hydrogen",
  #      "FE|Transport|Pass|Aviation|International|Liquids" = "Liquids"
          "FE|Transport|Pass|Aviation|International|Liquids|Fossil" = "Liquids - Fossil",
          "FE|Transport|Pass|Aviation|International|Liquids|Biomass" = "Liquids - Biomass",
          "FE|Transport|Pass|Aviation|International|Liquids|Hydrogen" = "Liquids - Synthetic"
      ),
      "Shipping" = c(
        "FE|Transport|Freight|Navigation|Electricity" = "Electricity",
        "FE|Transport|Freight|Navigation|Gases" = "Gases",
        "FE|Transport|Freight|Navigation|Hydrogen" = "Hydrogen",
  #      "FE|Transport|Freight|Navigation|Liquids" = "Liquids",
          "FE|Transport|Freight|Navigation|Liquids|Fossil" = "Liquids - Fossil",
          "FE|Transport|Freight|Navigation|Liquids|Biomass" = "Liquids - Biomass",
          "FE|Transport|Freight|Navigation|Liquids|Hydrogen" = "Liquids - Synthetic",
        "FE|Transport|Freight|International Shipping|Electricity" = "Electricity",
        "FE|Transport|Freight|International Shipping|Gases" = "Gases",
        "FE|Transport|Freight|International Shipping|Hydrogen" = "Hydrogen",
  #      "FE|Transport|Freight|International Shipping|Liquids" = "Liquids"
          "FE|Transport|Freight|International Shipping|Liquids|Fossil" = "Liquids - Fossil",
          "FE|Transport|Freight|International Shipping|Liquids|Biomass" = "Liquids - Biomass",
          "FE|Transport|Freight|International Shipping|Liquids|Hydrogen" = "Liquids - Synthetic"
      )
    )
  )

} else {
  FEvars <- list(
    "Domestic" = list(
      "LDV" = c(
        "FE|Transport|Pass|Road|LDV|Electricity" = "Electricity",
        "FE|Transport|Pass|Road|LDV|Gases" = "Gases",
        # "FE|Transport|Pass|Road|LDV|Gases|Fossil" = "Gases - Fossil",
        # "FE|Transport|Pass|Road|LDV|Gases|Biomass" = "Gases - Biomass",
        # "FE|Transport|Pass|Road|LDV|Gases|Hydrogen" = "Gases - Synthetic",
        "FE|Transport|Pass|Road|LDV|Hydrogen" = "Hydrogen",
  #      "FE|Transport|Pass|Road|LDV|Liquids" = "Liquids"
         "FE|Transport|Pass|Road|LDV|Liquids|Fossil" = "Liquids - Fossil",
         "FE|Transport|Pass|Road|LDV|Liquids|Biomass" = "Liquids - Biomass",
          "FE|Transport|Pass|Road|LDV|Liquids|Hydrogen" = "Liquids - Synthetic"
      ),
      "Buses" = c(
        "FE|Transport|Pass|Road|Bus|Electricity" = "Electricity",
        "FE|Transport|Pass|Road|Bus|Gases" = "Gases",
        # "FE|Transport|Pass|Road|Bus|Gases|Fossil" = "Gases - Fossil",
        # "FE|Transport|Pass|Road|Bus|Gases|Biomass" = "Gases - Biomass",
        # "FE|Transport|Pass|Road|Bus|Gases|Hydrogen" = "Gases - Synthetic",
        "FE|Transport|Pass|Road|Bus|Hydrogen" = "Hydrogen",
  #      "FE|Transport|Pass|Road|Bus|Liquids" = "Liquids"
          "FE|Transport|Pass|Road|Bus|Liquids|Fossil" = "Liquids - Fossil",
          "FE|Transport|Pass|Road|Bus|Liquids|Biomass" = "Liquids - Biomass",
          "FE|Transport|Pass|Road|Bus|Liquids|Hydrogen" = "Liquids - Synthetic"
      ),
      "Trucks" = c(
        "FE|Transport|Freight|Road|Electricity" = "Electricity",
        "FE|Transport|Freight|Road|Gases" = "Gases",
        # "FE|Transport|Freight|Road|Bus|Gases|Fossil" = "Gases - Fossil",
        # "FE|Transport|Freight|Road|Bus|Gases|Biomass" = "Gases - Biomass",
        # "FE|Transport|Freight|Road|Bus|Gases|Hydrogen" = "Gases - Synthetic",
        "FE|Transport|Freight|Road|Hydrogen" = "Hydrogen",
  #      "FE|Transport|Freight|Road|Liquids" = "Liquids"
          "FE|Transport|Freight|Road|Liquids|Fossil" = "Liquids - Fossil",
          "FE|Transport|Freight|Road|Liquids|Biomass" = "Liquids - Biomass",
          "FE|Transport|Freight|Road|Liquids|Hydrogen" = "Liquids - Synthetic"
      ),
      "Rail" = c(
        "FE|Transport|Pass|Rail|Electricity" = "Electricity",
        "FE|Transport|Pass|Rail|Gases" = "Gases",
        # "FE|Transport|Pass|Rail|Bus|Gases|Fossil" = "Gases - Fossil",
        # "FE|Transport|Pass|Rail|Bus|Gases|Biomass" = "Gases - Biomass",
        # "FE|Transport|Pass|Rail|Bus|Gases|Hydrogen" = "Gases - Synthetic",
        "FE|Transport|Pass|Rail|Hydrogen" = "Hydrogen",
  #      "FE|Transport|Pass|Rail|Liquids" = "Liquids",
          "FE|Transport|Pass|Rail|Liquids|Fossil" = "Liquids - Fossil",
          "FE|Transport|Pass|Rail|Liquids|Biomass" = "Liquids - Biomass",
          "FE|Transport|Pass|Rail|Liquids|Hydrogen" = "Liquids - Synthetic",
        "FE|Transport|Freight|Rail|Electricity" = "Electricity",
        "FE|Transport|Freight|Rail|Gases" = "Gases",
        # "FE|Transport|Freight|Rail|Bus|Gases|Fossil" = "Gases - Fossil",
        # "FE|Transport|Freight|Rail|Bus|Gases|Biomass" = "Gases - Biomass",
        # "FE|Transport|Freight|Rail|Bus|Gases|Hydrogen" = "Gases - Synthetic",
        "FE|Transport|Freight|Rail|Hydrogen" = "Hydrogen",
  #      "FE|Transport|Freight|Rail|Liquids" = "Liquids"
          "FE|Transport|Freight|Rail|Liquids|Fossil" = "Liquids - Fossil",
          "FE|Transport|Freight|Rail|Liquids|Biomass" = "Liquids - Biomass",
          "FE|Transport|Freight|Rail|Liquids|Hydrogen" = "Liquids - Synthetic"
      ),
  #     "Shipping" = c(
  #       "FE|Transport|Freight|Domestic Shipping|Electricity" = "Electricity",
  #       "FE|Transport|Freight|Domestic Shipping|Gases" = "Gases",
  #       # "FE|Transport|Freight|Domestic Shipping|Gases|Fossil" = "Gases - Fossil",
  #       # "FE|Transport|Freight|Domestic Shipping|Gases|Biomass" = "Gases - Biomass",
  #       # "FE|Transport|Freight|Domestic Shipping|Gases|Hydrogen" = "Gases - Synthetic",
  #       "FE|Transport|Freight|Domestic Shipping|Hydrogen" = "Hydrogen",
  # #      "FE|Transport|Freight|Domestic Shipping|Liquids" = "Liquids"
  #         "FE|Transport|Freight|Domestic Shipping|Liquids|Fossil" = "Liquids - Fossil",
  #         "FE|Transport|Freight|Domestic Shipping|Liquids|Biomass" = "Liquids - Biomass",
  #         "FE|Transport|Freight|Domestic Shipping|Liquids|Hydrogen" = "Liquids - Synthetic"
  #     ),
      "Aviation" = c(
        "FE|Transport|Pass|Domestic Aviation|Electricity" = "Electricity",
        "FE|Transport|Pass|Domestic Aviation|Gases" = "Gases",
        # "FE|Transport|Pass|Domestic Aviation|Gases|Fossil" = "Gases - Fossil",
        # "FE|Transport|Pass|Domestic Aviation|Gases|Biomass" = "Gases - Biomass",
        # "FE|Transport|Pass|Domestic Aviation|Gases|Hydrogen" = "Gases - Synthetic",
        "FE|Transport|Pass|Domestic Aviation|Hydrogen" = "Hydrogen",
  #      "FE|Transport|Pass|Domestic Aviation|Liquids" = "Liquids"
          "FE|Transport|Pass|Domestic Aviation|Liquids|Fossil" = "Liquids - Fossil",
          "FE|Transport|Pass|Domestic Aviation|Liquids|Biomass" = "Liquids - Biomass",
          "FE|Transport|Pass|Domestic Aviation|Liquids|Hydrogen" = "Liquids - Synthetic"
      )
    ),
    "International" = list(
      "Aviation" = c(
        "FE|Transport|Bunkers|Pass|International Aviation|Electricity" = "Electricity",
        "FE|Transport|Bunkers|Pass|International Aviation|Gases" = "Gases",
        # "FE|Transport|Bunkers|Pass|International Aviation|Gases|Fossil" = "Gases - Fossil",
        # "FE|Transport|Bunkers|Pass|International Aviation|Gases|Biomass" = "Gases - Biomass",
        # "FE|Transport|Bunkers|Pass|International Aviation|Gases|Hydrogen" = "Gases - Synthetic",
        "FE|Transport|Bunkers|Pass|International Aviation|Hydrogen" = "Hydrogen",
  #      "FE|Transport|Bunkers|Pass|International Aviation|Liquids" = "Liquids"
          "FE|Transport|Bunkers|Pass|International Aviation|Liquids|Fossil" = "Liquids - Fossil",
          "FE|Transport|Bunkers|Pass|International Aviation|Liquids|Biomass" = "Liquids - Biomass",
          "FE|Transport|Bunkers|Pass|International Aviation|Liquids|Hydrogen" = "Liquids - Synthetic"
      ),
      "Shipping" = c(
        "FE|Transport|Bunkers|Freight|International Shipping|Electricity" = "Electricity",
        "FE|Transport|Bunkers|Freight|International Shipping|Gases" = "Gases",
        # "FE|Transport|Bunkers|Freight|International Shipping|Gases|Fossil" = "Gases - Fossil",
        # "FE|Transport|Bunkers|Freight|International Shipping|Gases|Biomass" = "Gases - Biomass",
        # "FE|Transport|Bunkers|Freight|International Shipping|Gases|Hydrogen" = "Gases - Synthetic",
        "FE|Transport|Bunkers|Freight|International Shipping|Hydrogen" = "Hydrogen",
  #      "FE|Transport|Bunkers|Freight|International Shipping|Liquids" = "Liquids",
          "FE|Transport|Bunkers|Freight|International Shipping|Liquids|Fossil" = "Liquids - Fossil",
          "FE|Transport|Bunkers|Freight|International Shipping|Liquids|Biomass" = "Liquids - Biomass",
          "FE|Transport|Bunkers|Freight|International Shipping|Liquids|Hydrogen" = "Liquids - Synthetic"
      )
    )
  )
}

  FEvarList <- unlist(c(FEvars$Domestic$LDV,FEvars$Domestic$Buses,FEvars$Domestic$Trucks,FEvars$Domestic$Rail,FEvars$Domestic$Aviation,FEvars$International$Aviation,FEvars$International$Shipping))

typeVar <- c()
for(national in names(FEvars)){
  for(mode in names(FEvars[[national]])){
    for(var in names(FEvars[[national]][[mode]])){
      v <- mode
      names(v) <- var
      typeVar <- c(typeVar,v)
    }
  }
}

FEplotData <- df %>% 
  filter(region == "EU27", period >= 2020, period <= 2060, scenario == mainScen, variable %in% names(FEvarList))

FEplotData <- FEplotData %>%
  mutate(national = ifelse(variable %in% names(c(FEvars$Domestic$LDV,FEvars$Domestic$Buses,FEvars$Domestic$Trucks,FEvars$Domestic$Rail,FEvars$Domestic$Aviation)), "Domestic", "International"),
         name = FEvarList[as.character(variable)],
         type="Final Energy",
         mode = typeVar[as.character(variable)]) %>%
  group_by(model,scenario,region,unit,period,national,name,type,mode) %>%
  summarize(value=sum(value),.groups = "keep")

FEplotData$mode <- factor(FEplotData$mode, levels=c("LDV","Buses","Trucks","Rail","Shipping","Aviation"))

FEplotData$name <- factor(FEplotData$name, levels=c("Electricity","Hydrogen","Liquids","Liquids - Biomass","Liquids - Synthetic","Liquids - Fossil","Gases"))

plotColor <- c(
  "Electricity" = "#F3E16B",
  "Hydrogen" = "#82c9d9",
  "Liquids" = "#282828",
  "Liquids - Fossil" = "#282828",
  "Liquids - Biomass" = "#005900",
  "Liquids - Synthetic" = "#b56576",
  "Gases" = "#999959"
)

FEplotData <- FEplotData %>%
  mutate(cat = factor(ifelse(mode %in% c("Aviation","Shipping"), paste0(as.character(national),"\n", as.character(mode)), as.character(mode)),levels=c("LDV","Buses","Trucks","Rail","Domestic\nAviation","International\nShipping","International\nAviation")))

# convert unit if necessary
if(energyInMtoe){
  FEplotData <- FEplotData %>%
    mutate(value = value * EJ2Mtoe,
           unit = "Mtoe/yr")
}

logoURL <- c(
  "LDV" = "./img/LDV.svg",
  "Buses" = "./img/buses.svg",
  "Trucks" = "./img/truck.svg",
  "Rail" = "./img/rail.svg",
  "Domestic\nAviation" = "./img/aviation.svg",
  "International\nShipping" = "./img/shipping.svg",
  "International\nAviation" = "./img/aviation.svg"
)
logoSVG <- NULL
for (logo in names(logoURL)){
  logoSVG <- c(logoSVG, setNames(paste(readLines(logoURL[logo]), collapse = "\n"),logo))
}

logoData <- data.frame(cat = factor(names(logoSVG),levels=c("LDV","Buses","Trucks","Rail","Domestic\nAviation","International\nShipping","International\nAviation")), period = 2040, value = max(FEplotData$value)) %>%
  mutate(logo = logoSVG[cat])

g[["transport fe"]] <- ggplot(FEplotData,aes(x=period,y=value)) +
  geom_bar(aes(fill=name, alpha=factor(period)),stat='identity') +
  geom_point_svg(data=logoData, aes(x=period,y=value, svg = logo),vjust=1,size=15) + 
  facet_wrap(~cat,nrow=1) +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank()) +
  scale_fill_manual(values = plotColor, guide = guide_legend(nrow = 1)) + #, guide = guide_legend(nrow = 2)
  scale_alpha_manual(values = c("2020"=0.7,"2025"=0.7,"2030"=0.7,"2035"=0.7,"2040"=1,"2045"=0.7,"2050"=0.7,"2055"=0.7,"2060"=0.7), guide = 'none') +
  scale_x_continuous(breaks = c(2020,2040,2060)) + 
  theme(
    strip.background = element_blank(),
    #strip.text.x = element_blank()
    ) +
  #theme(legend.text=element_text(size=theme.single.text.size)) +
  #theme(strip.text.x = element_text(size = 1.2*theme.double.text.size, vjust=0.5)) +
  theme(strip.clip = "off") +
  labs(title = paste0("(a) Transport Final energy (", unique(FEplotData$unit), ")"))

# ggsave(paste0(outChartsFolder,"/svg/Figure 4. Demand panel - (a) transport final energy.svg"), g[["transport fe"]] , device="svg", width = 12, height = 5, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Figure 4. Demand panel - (a) transport final energy.png"), g[["transport fe"]] , device="png", width = 12, height = 5, dpi=300, units = "in")

```

<!-- (b) LDV sales and ICE stock (Millions of vehicles) -->

```{r chart_figure4b, echo=FALSE}

#LDV
if("Sales|Transport|LDV" %in% unique(df$variable)){
  Sales <- list(
    "BEV" = "Sales|Transport|LDV|BEV",
    "FCEV" = "Sales|Transport|LDV|FCEV",
    "Hybrid Electric" =	"Sales|Transport|LDV|Hybrid Electric",
    "Liquids" = "Sales|Transport|LDV|Liquids",
    "Gases" = "Sales|Transport|LDV|NG"
  )
  salesTotal <- c("Sales|Transport|LDV")
} else {
  Sales <- list(
    "BEV" = "Sales|Transport|Pass|Road|LDV|BEV",
    "FCEV" = "Sales|Transport|Pass|Road|LDV|FCEV",
    "Hybrid Electric" =	"Sales|Transport|Pass|Road|LDV|Hybrid electric",
    "Liquids" = "Sales|Transport|Pass|Road|LDV|Liquids",
    "Gases" = "Sales|Transport|Pass|Road|LDV|Gases"
  ) 
  salesTotal <- c("Sales|Transport|Pass|Road|LDV")
}

if("Stock|Transport|LDV" %in% unique(df$variable)){
  Stock <- list(
    "BEV" = "Stock|Transport|LDV|BEV",
    "FCEV" = "Stock|Transport|LDV|FCEV",
    "Hybrid Electric" =	"Stock|Transport|LDV|Hybrid Electric",
    "Liquids" = "Stock|Transport|LDV|Liquids",
    "Gases" = "Stock|Transport|LDV|NG"
  )
  StockFossil = c("Stock|Transport|LDV|Liquids","Stock|Transport|LDV|NG")
  StockTotal <- c("Stock|Transport|LDV")
} else {
  Stock <- list(
    "BEV" = "Stock|Transport|Pass|Road|LDV|BEV",
    "FCEV" = "Stock|Transport|Pass|Road|LDV|FCEV",
    "Hybrid Electric" =	"Stock|Transport|Pass|Road|LDV|Hybrid electric",
    "Liquids" = "Stock|Transport|Pass|Road|LDV|Liquids",
    "Gases" = "Stock|Transport|Pass|Road|LDV|Gases"
  ) 
  StockFossil = c("Stock|Transport|Pass|Road|LDV|Liquids","Stock|Transport|Pass|Road|LDV|Gases")
  StockTotal <- c("Stock|Transport|Pass|Road|LDV")
}

plotColor <- c(
  "BEV" = "#F3E16B",
  "FCEV" = "#82c9d9",
  "Hybrid Electric" =	"#F37A5E",
  "Gases" = "#dddddd" , #"#F7EFE8", 
  "Liquids" = "#282828"
)

vars <- Sales

plotData <- df %>% 
  filter(region == "EU27", period >= 2020, period <= 2060, scenario == mainScen, variable %in% unlist(vars)) %>% 
  mutate(variable = factor(variable, levels=vars))

salestot <- df %>% 
  filter(region == "EU27", period >= 2020, period <= 2060, scenario == mainScen, variable %in% Sales) %>% 
  group_by(period) %>%
  summarize(value = sum(value)) %>%
  rename(tot = value)

plotData <- inner_join(plotData, salestot, by = "period") %>%
  mutate(value = value/tot)

labels <- setNames(names(vars),vars[names(vars)])

plotData$labels <- labels[as.character(plotData$variable)]

#stock
stockData <- df %>% 
  filter(region == "EU27", period >= 2020, period <= 2060, scenario == mainScen, variable %in% unlist(Stock)) %>% 
  mutate(variable = factor(variable, levels=Stock)) %>%
  filter(variable %in% StockFossil) %>%
  group_by(period) %>%
  summarize(value = sum(value),.groups = "keep") %>%
  mutate(variable = "ICE Stock")

totstockData <- df %>% 
  filter(region == "EU27", period >= 2020, period <= 2060, scenario == mainScen, variable %in% StockTotal) %>% 
  select(period, value) %>%
  rename(tot = value)

stockData <- inner_join(stockData,totstockData, by = "period") %>% 
  mutate(value = value/tot, variable = "ICE Stock")

logoData <- data.frame(period = 2050, value = 0.7, logo = paste(readLines("./img/LDV.svg"), collapse = "\n"))

g[["LDV Sales"]] <-
  ggplot(plotData,aes(x=period,y=value)) +
  geom_bar(aes(fill=variable, alpha=factor(period)),stat='identity') +
  geom_line(data=stockData, aes(color=variable),linetype=11, lwd = 1) +
# geom_line(data=h,linetype="dashed", linewidth = 1, color="black") +
 geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
 geom_label_repel(data=data.frame(period=2030,value=stockData %>% filter(period == 2030) %>% pull(value)), label = "Stock",
                  #box.padding = 0.1,
                  #segment.curvature = -0.1,
                  #segment.square = TRUE,
                  #point.padding = 0.6,
                  nudge_x = 5,
                  nudge_y = 0.05,
                  #nudge_y = -0.02,
                  #force = 0.5,
                  hjust = 0,
                  direction="x", size = geomText.size) +
  geom_point_svg(data=logoData, aes(x=period,y=value, svg = logo),vjust=0.5,size=20) +
  theme_doubleColumn() +
 scale_fill_manual(values = setNames(plotColor[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(nrow = 3, order = 1)) + #, guide = guide_legend(nrow = 2)
 scale_color_manual(values = c("ICE Stock"="black"), guide = guide_legend(order = 2, keywidth = unit(2, 'cm'))) +
 scale_alpha_manual(values = c("2020"=0.7,"2025"=0.7,"2030"=0.7,"2035"=0.7,"2040"=1,"2045"=0.7,"2050"=0.7,"2055"=0.7,"2060"=0.7), guide = 'none') +
 scale_x_continuous(breaks=c(2020,2030,2040,2050,2060)) +
 scale_y_continuous(limits = c(0, 1.1), breaks=c(0,1), labels = scales::percent, name = "Sales") +
 #theme(legend.text=element_text(size=theme.double.text.size),
#        legend.spacing.x = unit(0.4, 'cm'))  +
  guides(color = "none") +
  #theme(legend.text=element_text(size=theme.double.text.size)) +
  labs(title = "(b) LDV sales shares &  share of ICE in LDV stock (%)") +
  theme(plot.title = element_text(hjust=-0.5))

# ggsave(paste0(outChartsFolder,"/svg/Figure 4. Demand panel - (b) LDV sales.svg"), g[["LDV Sales"]] , device="svg", width = 6, height = 4.5, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Figure 4. Demand panel - (b) LDV sales.png"), g[["LDV Sales"]] , device="png", width = 6, height = 4.5, dpi=300, units = "in")

```

<!-- (d) Industry CO2 emissions per sub-sector (Mt CO2/yr) -->

```{r chart_figure4d, echo=FALSE}

# Industry Emissions
vars <- c("Chemicals"="Emi|CO2|Energy|Demand|Industry|Chemicals",
          "Other Industry"="Emi|CO2|Energy|Demand|Industry|Other Industry",
          "Steel"="Emi|CO2|Energy|Demand|Industry|Steel",
          "Cement" = "Emi|CO2|Energy|Demand|Industry|Cement"
          )

plotColor <- c(
  "Cement" = "#355070",
  "Steel" = "#219ebc",
  "Chemicals" = "#eaac8b",
  "Other Industry" = "#e56b6f"
)

plotData <- df %>% 
  filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
  mutate(variable = factor(variable, levels=vars)) %>%
  group_by(model,region,variable,period) %>% 
  filter(tgt2050 != "Npi") %>% 
  mutate(ribbon.max=max(value),
         ribbon.min=min(value))

# historical data #missing non-energy
#h <- hist[hist$model == "UNFCCC" & hist$region == "EU27" & hist$variable %in% vars,] %>% drop_na(value)

#View(hist[hist$model == "UNFCCC" & hist$region == "EU27" & hist$variable == "Emi|CO2|Industrial Processes",] %>% drop_na(value))
# Emi|CO2|Energy|Demand|Industry
# Emi|CO2|Energy|Demand|Industry|Cement
# Emi|CO2|Energy|Demand|Industry|Chemicals
# Emi|CO2|Energy|Demand|Industry|Other Industry
# Emi|CO2|Energy|Demand|Industry|Other Industry|AFOFI
# Emi|CO2|Energy|Demand|Industry|Steel
# Emi|CO2|Industrial Processes
# Emi|CO2|Industrial Processes|Chemicals
# Emi|CO2|Industrial Processes|Metals
# Emi|CO2|Industrial Processes|Minerals
# Emi|GHG|Energy|Demand|Industry
# Emi|GHG|Industrial Processes

g[["Industry Emissions"]] <- ggplot(plotData,aes(x=period,y=value)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_segment(aes(x=2040, y=0, xend=2040, yend=max(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value))), linetype="dashed", color="black") +
    geom_line(data=plotData %>% filter(scenario == mainScen), aes(color=variable), linewidth=1.5) +
    #geom_line(data=h,linewidth=1,linetype="dashed") +
    geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min, fill=variable), alpha = 0.3) + 
    geom_point(data=plotData %>% filter(scenario == mainScen, period == 2040), aes(color=variable),size=3,shape=21,fill="white",stroke=1.5) +
    scale_color_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) +
    scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) +
    theme_doubleColumn() + 
    expand_limits(y=c(0,1)) +
    guides(color=guide_legend(nrow=2)) +
    #theme(legend.text=element_text(size=theme.double.text.size)) +
    #theme(legend.text=element_text(size=theme.double.text.size))  +
    labs(title = expression(paste("(d) Industrial sectors’ ", CO[2], " emissions (Mt ", CO[2], "/yr)"))) #+
    #theme(plot.title = element_text(hjust=-0.3))

# ggsave(paste0(outChartsFolder,"/svg/Figure 4. Demand panel - (d) industrial emissions.svg"), g[["Industry Emissions"]] , device="svg", width = 6, height = 5.5, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Figure 4. Demand panel - (d) industrial emissions.png"), g[["Industry Emissions"]] , device="png", width = 6, height = 5.5, dpi=300, units = "in")

```

<!-- (c) Buildings useful energy Electricity based heating (EJ/yr) -->

```{r chart_figure4c, echo=FALSE}

# full useful energy
vars <- c(
  "Electricity (appliances)" = "UE|Buildings|non-Heating|Electricity|Conventional",
  "Electricity (heat pumps)" = "UE|Buildings|Heating|Electricity|Heat pump",
  "Electricity (resistence)" = "UE|Buildings|Heating|Electricity|Resistance",
  "Heating - Hydrogen" = "UE|Buildings|Heating|Hydrogen",
  "District Heating" = "UE|Buildings|Heating|District Heating",
  "Gases" = "UE|Buildings|Heating|Gases",
  "Liquids" = "UE|Buildings|Heating|Liquids",
  "Solids" = "UE|Buildings|Heating|Solids"
)

invertVars <- setNames(names(vars),vars)

# origData <- df %>%
#   filter(region == "EU27", period >= 2020, period <= 2060, variable %in% vars) %>% #, scenario == mainScen
#   mutate(name = invertVars[as.character(variable)]) %>%
#   mutate(name = factor(invertVars[as.character(variable)], levels = names(vars)),
#          variable = factor(variable, levels=vars))

plotData <- df %>%
  filter(region == "EU27", period >= 2020, period <= 2060, variable %in% vars) %>% #, scenario == mainScen
  mutate(name = invertVars[as.character(variable)]) %>%
  filter(name %in% c("Electricity (heat pumps)", "Electricity (resistence)", "District Heating", "Gases", "Liquids", "Solids")) %>%
  filter(region == "EU27", period %in% c(2020,2030,2040,2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>%
  mutate(variable = factor(variable, levels=vars))  %>%
  mutate(name = factor(name, levels = names(vars)))  %>%
  filter(tgt2050 != "Npi")  %>%
  group_by(model,scenario,region,period) %>%
  mutate(cumsum = cumsum(value),
         sum = sum(value)) %>%
  group_by(model,region,variable,period) %>%
  mutate(ribbon.max=max(cumsum),
         ribbon.min=min(cumsum)) %>%
  group_by(model,region,period) %>%
  mutate(ribbon.max.total=max(sum),
         ribbon.min.total=min(sum))

plotColor <- c(
  "Electricity (appliances)" = as.vector(options$aesthetics$legend$color["Electricity"]),
  "Electricity (heat pumps)" = "#F3E16B", #"#D62828",
  "Electricity (resistence)" = "#F77F00",
  "Heating - Hydrogen" = as.vector(options$aesthetics$legend$color["Hydrogen"]),
  "District Heating" = "#E07A5F",
  "Gases" = as.vector(options$aesthetics$legend$color["Gases"]),
  "Liquids" = as.vector(options$aesthetics$legend$color["Liquids"]),
  "Solids" = as.vector(options$aesthetics$legend$color["Solids"])
)

# convert unit if necessary
if(energyInMtoe){
  plotData <- plotData %>%
    mutate(value = value * EJ2Mtoe,
           ribbon.max = ribbon.max * EJ2Mtoe,
           ribbon.min = ribbon.min * EJ2Mtoe,
           ribbon.max.total = ribbon.max.total * EJ2Mtoe,
           ribbon.min.total = ribbon.min.total * EJ2Mtoe,
           unit = "Mtoe/yr")
}

g[["Buildings heating useful energy"]] <-
  ggplot(plotData,aes(x=period,y=value)) +
  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = name, alpha=factor(period))) +
  geom_errorbar(data=plotData %>% filter(period != 2020, variable == vars["Electricity (heat pumps)"], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, linewidth=1,position = position_dodge(width=2)) +
  # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
  coord_flip() +
  theme_doubleColumn() +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank()) +
  scale_fill_manual(values = plotColor, guide = guide_legend(reverse = TRUE, nrow = 3)) +
  scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
  #theme(legend.text=element_text(size=theme.double.text.size)) +
  #theme(legend.margin=margin(l = -2.5, t = -0.5, unit='cm')) +
  labs(title = paste0("(c) Buildings space and water heating useful energy (", unique(plotData$unit), ")")) +
  theme(plot.title = element_text(hjust=1)) #+
  #scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == "2020") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2030") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2040") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2050") %>% pull(value)),1))) #+
  #scale_x_reverse()

# ggsave(paste0(outChartsFolder,"/svg/Figure 4. Demand panel - (c) buildings heating useful energy.svg"), g[["Buildings heating useful energy"]] , device="svg", width = 6, height = 4.3, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Figure 4. Demand panel - (c) buildings heating useful energy.png"), g[["Buildings heating useful energy"]] , device="png", width =6, height = 4.3, dpi=300, units = "in")

```

<!-- (e) Carbon Management (Mt CO2/yr) -->

```{r chart_figure4e, echo=FALSE}

vars <- list(
  #"Usage"
  "e-liquids" = "Carbon Management|Usage|Synthetic Liquids",
  "e-gases" = "Carbon Management|Usage|Synthetic Gases",
  "stored carbon" = "Carbon Management|Storage",
  # "Capture type"
  "atmospheric/biogenic" = "Carbon Management|Carbon Capture|atmospheric/biogenic CO2",
  "fossil" = "Carbon Management|Carbon Capture|fossil origin",
  #"Capture"
  "DAC" = "Carbon Management|Carbon Capture|DAC",
  "BECC" = "Carbon Management|Carbon Capture|Biomass|Pe2Se", 
  "fossil (energy)" = "Carbon Management|Carbon Capture|Fossil|Pe2Se",
  "industry and waste" = "Carbon Management|Carbon Capture|Industry and Waste"
  #"industry" = "Carbon Management|Carbon Capture|Industry",
  #"waste" = "Carbon Management|Carbon Capture|Waste|Plastics Incineration"
  #"Storage type"
  # "atmospheric/biogenic" = "Carbon Management|atmospheric/biogenic CO2 - CDR",
  # "fossil" = "Carbon Management|CCS of fossil origin",
  #
  # "DAC" = "Carbon Management|Storage|DAC",
  # "BECCS" = "Carbon Management|Storage|Biomass|Pe2Se", 
  # "Fossil CCS" = "Carbon Management|Storage|Fossil|Pe2Se", 
  # "Industry CCS" = "Carbon Management|Storage|Industry CCS"
    # "Industry Energy" = "Carbon Management|Storage|Industry Energy",
    # "Industry Process" = "Carbon Management|Storage|Industry Process"
)

plotColor <- c(
  "e-liquids" = "#6f65b5",
  "e-gases" = "#b59765",
  "stored carbon" = "#b56576",
  "atmospheric/biogenic" = "#c1d8f0",
  "fossil" = "#6b5b4b",
  "DAC" = "#CC6666",
  "BECC" = "#8bc18b",
  #"Industry CCS" = "#5f6769",
  #"Fossil CCS" = "#47331f",
  "fossil (energy)" = "#6b5b4b",
  "industry and waste" = "#5f6769"#,
  #"industry" = "#5f6769",
  #"waste" = "#543a0f"
  #"fossil" = "#47331f"
)

plotData <- df %>% 
  filter(region == "EU27", period %in% c(2030, 2040, 2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
  mutate(CDRGroup = 
    ifelse(as.character(variable) %in% c("Carbon Management|Carbon Capture|fossil origin","Carbon Management|Carbon Capture|atmospheric/biogenic CO2"), "Capture type",
    ifelse(as.character(variable) %in% c("Carbon Management|CCS of fossil origin","Carbon Management|atmospheric/biogenic CO2 - CDR"), "Storage type",
    ifelse(as.character(variable) %in% c("Carbon Management|Storage","Carbon Management|Usage|Synthetic Gases","Carbon Management|Usage|Synthetic Liquids"), "Usage",
    ifelse(as.character(variable) %in% c("Carbon Management|Carbon Capture|DAC", "Carbon Management|Carbon Capture|Biomass|Pe2Se", "Carbon Management|Carbon Capture|Fossil|Pe2Se","Carbon Management|Carbon Capture|Industry and Waste"
                                         #"Carbon Management|Carbon Capture|Industry", "Carbon Management|Carbon Capture|Waste|Plastics Incineration"
                                         ), "Capture","CCS")))),
    variable = factor(variable, levels=c( "Carbon Management|Usage|Synthetic Liquids", "Carbon Management|Usage|Synthetic Gases", "Carbon Management|Storage", "destination", "empty1", "empty2", "Carbon Management|Carbon Capture|atmospheric/biogenic CO2", "Carbon Management|Carbon Capture|fossil origin", "type",
          #"empty1", "empty2", "Carbon Management|atmospheric/biogenic CO2 - CDR", "Carbon Management|CCS of fossil origin", "type",
          #"Carbon Management|Storage|DAC", "Carbon Management|Storage|Biomass|Pe2Se", "Carbon Management|Storage|Fossil|Pe2Se", "Carbon Management|Storage|Industry CCS", "origin")
          "Carbon Management|Carbon Capture|DAC", "Carbon Management|Carbon Capture|Biomass|Pe2Se", "Carbon Management|Carbon Capture|Fossil|Pe2Se", "Carbon Management|Carbon Capture|Industry and Waste"
          #"Carbon Management|Carbon Capture|Industry", "Carbon Management|Carbon Capture|Waste|Plastics Incineration"
          , "origin")),
         value = ifelse(grepl("Emi",variable,fixed = TRUE), -value, value))  %>% 
  mutate(CDRGroup = factor(CDRGroup, levels=c("Usage","Capture type", "Storage type", "Capture", "CCS"))) %>%
  group_by(model,scenario,region,period, CDRGroup) %>% 
  mutate(cumsum = cumsum(value),
         sum = sum(value)) %>% 
  group_by(model,region,variable,period, CDRGroup) %>% 
  mutate(ribbon.max=max(cumsum),
         ribbon.min=min(cumsum)) %>% 
  group_by(model,region,period, CDRGroup) %>% 
  mutate(ribbon.max.total=max(sum),
         ribbon.min.total=min(sum)) %>% 
  mutate(period = factor(period, levels=c(2050,2040,2030)))

 g[["Carbon Management"]] <- ggplot(plotData,aes(x=CDRGroup,y=value)) +
  #geom_area(aes(fill=variable)) +
  geom_bar(data=plotData %>% filter(scenario == mainScen), aes(fill=variable, alpha=factor(period)),stat='identity') + 
  geom_errorbar(data=plotData %>% filter(variable == vars[4], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=0.4, colour="black", alpha=0.9, linewidth=1) +
  facet_wrap(period ~ ., ncol=1, strip.position="left") +
  coord_flip() +
  theme_doubleColumn() +
  scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars), "empty1" = "transparent", "empty2" = "transparent", "destination" = "transparent", "type" = "transparent", "origin" = "transparent"), 
                    labels = c(setNames(names(vars[! vars %in% c("Carbon Management|atmospheric/biogenic CO2 - CDR", "Carbon Management|Carbon Capture|atmospheric/biogenic CO2")] ), vars[! vars %in% c("Carbon Management|atmospheric/biogenic CO2 - CDR", "Carbon Management|Carbon Capture|atmospheric/biogenic CO2")] ),
                               #"Carbon Management|atmospheric/biogenic CO2 - CDR" = "atmospheric",
                               "Carbon Management|Carbon Capture|atmospheric/biogenic CO2" = "atmospheric",
                               "empty1" = "", "empty2" = "or biogenic", "destination" = "Destination", "type" = "Type", "origin" = "Origin"), guide = guide_legend(nrow = 5, reverse = TRUE), drop = FALSE) + 
  scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
  theme(legend.title = element_blank()) +
  theme(legend.margin=margin(l = -1, unit='cm')) + 
  theme(strip.text.y.left = element_text(angle = 0)) +
  # theme(
  #   strip.background = element_blank(),
  #   strip.text.x = element_blank()
  # ) +
  theme(axis.text.y=element_blank(), #remove x axis labels
        axis.ticks.y=element_blank(), #remove x axis ticks
        ) +
  labs(title = expression(paste("(e) Carbon Capture and Storage (Mt ", CO[2], "/yr)"))) +
  theme(plot.title = element_text(hjust=-0.3))   #+

 # ggsave(paste0(outChartsFolder,"/svg/Figure 4. Demand panel - (e) carbon management.svg"), g[["Carbon Management"]] , device="svg", width = 6, height = 5.5, dpi=100, units = "in")
 # ggsave(paste0(outChartsFolder,"/png/Figure 4. Demand panel - (e) carbon management.png"), g[["Carbon Management"]] , device="png", width = 6, height = 5.5, dpi=300, units = "in")

```

```{r, echo=FALSE, include=FALSE}

g[["Figure 4"]] <- gridExtra::arrangeGrob(
  g[["transport fe"]] + theme(legend.margin=margin(b = 10, t = 10)),
  g[["LDV Sales"]],
  g[["Buildings heating useful energy"]] + theme(plot.title = element_text(margin=margin(b=30))),
  g[["Industry Emissions"]],
  g[["Carbon Management"]],
  layout_matrix = rbind(
    c(1,1),
    c(2,3),
		c(4,5))
   )

ggsave(paste0(outChartsFolder,"/png/Figure 4. Sectoral transformation indicators.png"), g[["Figure 4"]], device="png", width = 12, height = 16, dpi=300, units = "in")
ggsave(paste0(outChartsFolder,"/svg/Figure 4. Sectoral transformation indicators.svg"), g[["Figure 4"]], device="svg", width = 12, height = 16, dpi=100, units = "in")

```

```{r, echo=FALSE, fig.width=12, fig.height=16}

grid.newpage()
grid.draw(g[["Figure 4"]])

```

---

# Figure 5. Targets update

```{r chart_figure5, echo=FALSE}

# “existent targets”
# emission reduction - 2030 (FitFor55) - 2030 scenarios - 2040 scenarios
# energy savings  - 2030 (FitFor55 and REPowerEU) - 2030 scenarios - 2040 scenarios
# renewables target - 2030 (RED II, RED II revised, REPowerEU) - 2030 scenarios - 2040 scenarios
# solar photovoltaics capacity - 2030 (REPowerEU) - 2030 scenarios - 2040 scenarios
# CCS capacity target - 2030 EU-wide 50 MtCO2/y “Net-Zero Industry Act"
# “implicit targets”
# electrification? -> fe electrification share -> 45%
# “carbon-content in electricity” ->“carbon-free electricity” (>95%) 
# Total Residual Fossil emissions
# sectoral emissions -> Transport emissions -> 23% of 2020 
#                                   -> Industry and buildings emissions -> 27% of 2020
# “residual fossil”     -> Complete coal-phase by 2040
#                                  -> natural gas
#                                 -> oil
# “net trade” -> net-supply independency of gas by 2040
#                       -> one third of oil imports by 2040

#Emissions Reduction
plotData <- rbind(
    df %>% 
      filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
      calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>% 
      mutate(value = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)) ,2)) %>% 
      select(-variable)
    ,
    df %>% 
      filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>%
      calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>% 
      mutate(value = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)) ,2)) %>% 
      select(-variable)
  ) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Emissions\nreductions") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

fullPlotData <- plotData

h <- refEmi %>% filter(variable == "Emissions with LULUCF and with international transport", region == "EU27", pollutant == "All greenhouse gases - (CO2 equivalent)") %>% ungroup() %>% select(region,variable,period,value)
emi1990 <- tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)
reduction_h <- 1- (h %>% filter(period==2022) %>% pull(value) / emi1990)

g[["Emissions reductions"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=0.57, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Emissions\nreductions", y = 0.57, label = "FitFor55", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
  geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Emissions\nreductions", y = reduction_h, label = "2022", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geomText.size, hjust=1.4, na.rm = TRUE)

g[["milestone - vert"]][["Emissions reductions"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 0.55, label = "FitFor55", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = reduction_h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  theme(strip.text = element_text(angle = 90)) +
  coord_cartesian(clip = 'off') #+
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))

g[["milestone - hor"]][["Emissions reductions"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 0.55, label = "FitFor55", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = reduction_h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=0.8*geomText.size)

# Final Energy Demand - Energy savings
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "FE|w/o Non-energy Use w/o Bunkers") %>% select(-variable) %>%
  mutate(value = round(value * EJ2Mtoe)) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Final Energy\nDemand") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

fullPlotData <- rbind(fullPlotData,plotData)

h <- addHist$FE_consumption %>%
  mutate(value = round(value * EJ2Mtoe)) # 1EJ = 23.8845896627496 Mtoe

g[["Energy savings"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Final Energy\nDemand", y = 787, label = "FitFor55", angle=90, vjust = 1.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Final Energy\nDemand", y = 750, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0.7, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=h %>% filter(period==2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Final Energy\nDemand", y = h %>% filter(period==2022) %>% pull(value), label = "2022", angle=90, vjust = -0.5, hjust = 0.7, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  expand_limits(y=c(400,1000)) + 
  theme(panel.spacing = unit(4, "lines")) +
  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(Mtoe/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.2, na.rm = TRUE)

g[["milestone - vert"]][["Energy savings"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 750, label = "REPowerEU", vjust = 1.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  annotate("text", x = Inf, y = 787, label = "FitFor55", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=h %>% filter(period==2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = h %>% filter(period==2022) %>% pull(value), label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
  expand_limits(y=c(0,400,1000)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  theme(strip.text = element_text(angle = 90)) +
  coord_cartesian(clip = 'off') +
  annotate("text", x = -Inf, y = Inf, label = "(Mtoe/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))

g[["milestone - hor"]][["Energy savings"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mtoe/yr)")), aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 750, label = "REPowerEU", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  annotate("text", x = Inf, y = 787, label = "FitFor55", angle=90, vjust = 1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=h %>% filter(period==2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = h %>% filter(period==2022) %>% pull(value), label = "2022", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,400,1000)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(Mtoe/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)

# Electricity Demand
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "FE|Electricity") %>% select(-variable) %>%
  mutate(value = round(value * EJ2TWh)) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Electricity\nDemand") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

fullPlotData <- rbind(fullPlotData,plotData)

#2022 = 2469471.42 GWh = 2469471.42 *1000 / 8.76E+09 * 31.536 EJ - FE electricity - https://ec.europa.eu/eurostat/databrowser/bookmark/d19a01c7-6099-4b88-8ccd-c6bcc01c3ddc?lang=en
h <- 2469471.42 /1000
# old value? 2641

g[["Electricity Demand"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Electricity\nDemand", y = h, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  expand_limits(y=c(0,5000)) + 
  theme(panel.spacing = unit(4, "lines")) +
  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(TWh)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.2, na.rm = TRUE)

g[["milestone - vert"]][["Electricity Demand"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
  expand_limits(y=c(0,5000)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  theme(strip.text = element_text(angle = 90)) +
  coord_cartesian(clip = 'off') +
  annotate("text", x = -Inf, y = Inf, label = "(TWh)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))

g[["milestone - hor"]][["Electricity Demand"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (TWh)")), aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,5000)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(TWh)", hjust = 1, color = "#666666", size = 0.8*geomText.size)

# Renewables share
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "SE|Renewables Share") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Renewables\nShare in\nFinal Energy")

plotData$value <- plotData$value*(
  addHist$res %>% filter(type == "RES", period == 2020) %>% pull(value) /
   df %>% filter(region == "EU27", period == 2020, variable == "SE|Renewables Share", scenario == mainScen) %>% pull(value) 
)

plotData <- plotData %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

fullPlotData <- rbind(fullPlotData,plotData)

g[["Renewables Share"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Renewables\nShare in\nFinal Energy", y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0.5, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Renewables\nShare in\nFinal Energy", y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0.6, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Renewables\nShare in\nFinal Energy", y = addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), label = "2022", angle=90, vjust = -0.5, hjust = 0.6, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.4, na.rm = TRUE)

g[["milestone - vert"]][["Renewables Share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 0.4, label = "RED II revised", vjust = 1.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 0.45, label = "REPowerEU", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  theme(strip.text = element_text(angle = 90)) +
  coord_cartesian(clip = 'off') #+
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))

g[["milestone - hor"]][["Renewables Share"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size = 0.8*geomText.size)

# Wind
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Cap|Electricity|Wind") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Wind\ncapacity") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

fullPlotData <- rbind(fullPlotData,plotData)

#target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2025,2030),value=c(320,600)) 
g[["Wind capacity"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
  geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Wind\ncapacity", y = 255, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  expand_limits(y=c(0,1000)) + 
  theme(panel.spacing = unit(4, "lines")) +
  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(GW)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.3, na.rm = TRUE)

g[["milestone - vert"]][["Wind capacity"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 255, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
  expand_limits(y=c(0,1000)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  theme(strip.text = element_text(angle = 90)) +
  coord_cartesian(clip = 'off') +
  annotate("text", x = -Inf, y = Inf, label = "(GW)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))

g[["milestone - hor"]][["Wind capacity"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (GW)")), aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 255, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,1000)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(GW)", hjust = 1, color = "#666666", size = 0.8*geomText.size)

# Solar photovoltaics
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Cap|Electricity|Solar|PV") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Solar\nphotovoltaics") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

fullPlotData <- rbind(fullPlotData,plotData)

#target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2025,2030),value=c(320,600)) 
g[["Solar photovoltaics"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Solar\nphotovoltaics", y = 600, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0.6, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Solar\nphotovoltaics", y = 208.9, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  expand_limits(y=c(0,2500)) + 
  theme(panel.spacing = unit(4, "lines")) +
  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(GW)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.3, na.rm = TRUE)

g[["milestone - vert"]][["Solar photovoltaics"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 600, label = "REPowerEU", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 208.9, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
  expand_limits(y=c(0,2500)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  theme(strip.text = element_text(angle = 90)) +
  coord_cartesian(clip = 'off') +
  annotate("text", x = -Inf, y = Inf, label = "(GW)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))

g[["milestone - hor"]][["Solar photovoltaics"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (GW)")), aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 600, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 208.9, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,2500)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(GW)", hjust = 1, color = "#666666", size = 0.8*geomText.size)

# Carbon Capture and Storage 
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Carbon Management|Storage") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Carbon\nCapture and\nStorage") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

fullPlotData <- rbind(fullPlotData,plotData)

g[["Carbon Capture and Storage"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Carbon\nCapture and\nStorage", y = 50, label = "Net-Zero\nIndustry Act", angle=90, vjust = -0.2, hjust = 0.6, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  #expand_limits(y=c(0,ceiling(max(plotData$value)/50)*50)) + 
  expand_limits(y=c(0,400)) + 
  theme(panel.spacing = unit(4, "lines")) +
  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(Mt CO2/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.1, na.rm = TRUE)

g[["milestone - vert"]][["Carbon Capture and Storage"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 50, label = "Net-Zero\nIndustry Act", vjust = 0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
  expand_limits(y=c(0,400)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  theme(strip.text = element_text(angle = 90)) +
  coord_cartesian(clip = 'off') +
  annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))

g[["milestone - hor"]][["Carbon Capture and Storage"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 50, label = "Net-Zero\nIndustry Act", angle=90, vjust = 0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,400)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
  theme(strip.clip = "off")#+
  #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)

# Novel CDR = atmospheric/biogenic CO2 (CDR) 
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Carbon Management|atmospheric/biogenic CO2 - CDR") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "BECCS\nand\nDACCS") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

fullPlotData <- rbind(fullPlotData,plotData)

g[["Novel CDR"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  expand_limits(y=c(0,400)) + 
  #expand_limits(y=c(0,ceiling(max(plotData$value)/50)*50)) + 
  theme(panel.spacing = unit(4, "lines")) +
  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(Mt CO2/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.1, na.rm = TRUE)

g[["milestone - vert"]][["Novel CDR"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
  expand_limits(y=c(0,400)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  theme(strip.text = element_text(angle = 90)) +
  coord_cartesian(clip = 'off') +
  annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))

g[["milestone - hor"]][["Novel CDR"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,400)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)

# Direct Electrification
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Final Energy|Electricity Share") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Electricity\nShare in\nFinal Energy") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

fullPlotData <- rbind(fullPlotData,plotData)

#estimation of historical share in 2022 for FE electricity / FE with non-energy use and with bunkers
h <- (
      2550461.10 *1000 / 8.76E+09 * 31.536  # https://ec.europa.eu/eurostat/databrowser/bookmark/12d54df4-7c35-47eb-a103-dd8994d26b80?lang=en
     ) / (
      addHist$FE_consumption %>% mutate(value = value/1000000) %>% filter(period==2022) %>% pull(value) + # FE|w/o Non-energy Use w/o Bunkers - EJ
      df %>% filter(region == "EU27", period == 2020, scenario == "Npi", variable == "FE|Transport|Bunkers") %>% pull(value) +
      df %>% filter(region == "EU27", period == 2020, scenario == "Npi", variable == "FE|Non-energy Use|Industry") %>% pull(value)
     )

g[["Direct Electrification"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
    geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Electricity\nShare in\nFinal Energy", y = h, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.4, na.rm = TRUE)

g[["milestone - vert"]][["Direct Electrification"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  theme(strip.text = element_text(angle = 90)) +
  coord_cartesian(clip = 'off') #+
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))

g[["milestone - hor"]][["Direct Electrification"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=geomText.size, size = 0.8*geomText.size)

# Carbon-free electricity share
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "SE|Electricity|carbon-free") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Carbon-free\nelectricity\nshare") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

fullPlotData <- rbind(fullPlotData,plotData)

#historical - 2022 - https://ec.europa.eu/eurostat/statistics-explained/index.php?title=Electricity_and_heat_statistics&oldid=347519
#solid fossil	453180
#oil	54277
#gas	571687
#nuclear	609169
#renewables	1076710
#other	32822
h <- (609169 + 1076710)	/ (453180 + 54277 + 571687 + 609169 + 1076710 + 32822)

g[["Carbon-free electricity share"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
    geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Carbon-free\nelectricity\nshare", y = h, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.4, na.rm = TRUE)

g[["milestone - vert"]][["Carbon-free electricity share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  theme(strip.text = element_text(angle = 90)) +
  coord_cartesian(clip = 'off') #+
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))

g[["milestone - hor"]][["Carbon-free electricity share"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=geomText.size, size = 0.8*geomText.size)

# Residual Fossil Emissions
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Residual\nFossil\nEmissions") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

fullPlotData <- rbind(fullPlotData,plotData)

g[["Residual Fossil Emissions"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  expand_limits(y=c(0,2500)) + 
  theme(panel.spacing = unit(4, "lines")) +
  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(Mt CO2/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.05, na.rm = TRUE)

g[["milestone - vert"]][["Residual Fossil Emissions"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
  expand_limits(y=c(0,2500)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  theme(strip.text = element_text(angle = 90)) +
  coord_cartesian(clip = 'off') +
  annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))

g[["milestone - hor"]][["Residual Fossil Emissions"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,2500)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)

# Domestic Hydrogen Production
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "SE|Hydrogen") %>% select(-variable) %>%
  mutate(value = value*EJ2MtH2)  %>% #1EJ <- 8 million tons adrian
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Domestic\nHydrogen\nProduction") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

fullPlotData <- rbind(fullPlotData,plotData)

target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2030,2030),value=c(10,20))

g[["Domestic Hydrogen Production"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
  geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Domestic\nHydrogen\nProduction", y = 10, label = "REPowerEU\ndomestic", angle=90, vjust = 0.5, hjust = 0.5, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  expand_limits(y=c(0,20)) + 
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  theme(panel.spacing = unit(4, "lines")) +
  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(Mtoe/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.4, na.rm = TRUE)

g[["milestone - vert"]][["Domestic Hydrogen Production"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = -Inf, y = 10, label = "REPowerEU\ndomestic", vjust = 0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
  expand_limits(y=c(0,20)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  theme(strip.text = element_text(angle = 90)) +
  coord_cartesian(clip = 'off') +
  annotate("text", x = -Inf, y = Inf, label = "(Mtoe/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))

g[["milestone - hor"]][["Domestic Hydrogen Production"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mtoe/yr)")), aes(x = period, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=6) +
  geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = -Inf, y = 10, label = "REPowerEU\ndomestic", angle=90, vjust = 0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,20)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(Mtoe/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)

g[["Targets"]] <- gridExtra::arrangeGrob(
  g[["Emissions reductions"]] + theme(strip.text.x = element_blank()) + theme(plot.margin=margin(b=20, l = 30)), #+ theme(plot.margin=margin(10,10,30,10)),margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
  g[["Energy savings"]] + theme(plot.margin=margin(b=20, l = 10)),
  g[["Electricity Demand"]] + theme(plot.margin=margin(b=20, l = 35)),
  g[["Renewables Share"]] + theme(plot.margin=margin(b=20, l = 15)),
  g[["Wind capacity"]] + theme(plot.margin=margin(b=20, l = 50)),
  g[["Solar photovoltaics"]] + theme(plot.margin=margin(b=20, l = 10)),
  g[["Carbon Capture and Storage"]] + theme(plot.margin=margin(b=20, l = 15)),
  g[["Novel CDR"]] + theme(plot.margin=margin(b=20, l = 50)),
  g[["Direct Electrification"]] + theme(plot.margin=margin(b=20, l = 17)),
  g[["Carbon-free electricity share"]] + theme(plot.margin=margin(b=20, l = 24)),
  g[["Domestic Hydrogen Production"]] + theme(plot.margin=margin(b=20,l = 35)),
  g[["Residual Fossil Emissions"]] + theme(plot.margin=margin(b=20, l = 39)),
  ncol = 1
)

#ggsave(paste0(outChartsFolder,"/svg/targets.svg"), g[["Targets"]] , device="svg", width = 12, height = 17, dpi=100, units = "in")
#ggsave(paste0(outChartsFolder,"/png/targets.png"), g[["Targets"]] , device="png", width = 12, height = 17, dpi=300, units = "in")

g[["milestone - vert targets"]] <- gridExtra::arrangeGrob(
  g[["milestone - vert"]][["Emissions reductions"]] + theme(plot.margin=margin(r=30,t = 30)), #+ theme(plot.margin=margin(10,10,30,10)),margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
  g[["milestone - vert"]][["Energy savings"]] + theme(plot.margin=margin(r=30,t = 10)),
  g[["milestone - vert"]][["Renewables Share"]] + theme(plot.margin=margin(r=30,t = 15)),
  g[["milestone - vert"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(r=30,t = 39)),
  g[["milestone - vert"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(r=30,t = 15)),
  g[["milestone - vert"]][["Novel CDR"]] + theme(plot.margin=margin(t = 50)),

  g[["milestone - vert"]][["Electricity Demand"]] + theme(plot.margin=margin(r=30,t = 35)),
  g[["milestone - vert"]][["Wind capacity"]] + theme(plot.margin=margin(r=30,t = 50)),
  g[["milestone - vert"]][["Solar photovoltaics"]] + theme(plot.margin=margin(r=30,t = 10)),
  g[["milestone - vert"]][["Direct Electrification"]] + theme(plot.margin=margin(r=30,t = 17)),
  g[["milestone - vert"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(t = 24)),
  g[["milestone - vert"]][["Domestic Hydrogen Production"]] + theme(plot.margin=margin(r=30,t = 35)),
  nrow = 2
)

#ggsave(paste0(outChartsFolder,"/svg/milestone - vert targets.svg"), g[["milestone - vert targets"]] , device="svg", width = 12, height = 17, dpi=100, units = "in")
#ggsave(paste0(outChartsFolder,"/png/milestone - vert targets.png"), g[["milestone - vert targets"]] , device="png", width = 12, height = 17, dpi=300, units = "in")

g[["milestone - hor targets"]] <- gridExtra::arrangeGrob(
  g[["milestone - hor"]][["Emissions reductions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - hor"]][["Energy savings"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - hor"]][["Renewables Share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - hor"]][["Direct Electrification"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - hor"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - hor"]][["Domestic Hydrogen Production"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),

  g[["milestone - hor"]][["Electricity Demand"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - hor"]][["Wind capacity"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - hor"]][["Solar photovoltaics"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),

  g[["milestone - hor"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - hor"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - hor"]][["Novel CDR"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),

  ncol = 2
)

ggsave(paste0(outChartsFolder,"/svg/Figure 5. Milestones Panel.svg"), g[["milestone - hor targets"]] , device="svg", width = 12, height = 14, dpi=100, units = "in")
ggsave(paste0(outChartsFolder,"/png/Figure 5. Milestones Panel.png"), g[["milestone - hor targets"]] , device="png", width = 12, height = 14, dpi=300, units = "in")

```

<!-- ```{r, echo=FALSE} -->

<!-- g[["ECEMP abstract"]] <- gridExtra::arrangeGrob( -->
<!--   g[["milestone - vert"]][["Electricity Demand"]] + theme(plot.margin=margin(r=30,t = 35)), -->
<!--   g[["milestone - vert"]][["Direct Electrification"]] + theme(plot.margin=margin(r=30,t = 17)), -->
<!--   g[["milestone - vert"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(t = 24)), -->
<!--   g[["milestone - vert"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(r=30,t = 39)), -->
<!--   g[["milestone - vert"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(r=30,t = 15)), -->
<!--   g[["milestone - vert"]][["Novel CDR"]] + theme(plot.margin=margin(t = 50)), -->
<!--   nrow = 1 -->
<!-- ) -->

<!-- ggsave(paste0(outChartsFolder,"/png/ECEMP abstract.png"), g[["ECEMP abstract"]] , device="png", width = 12, height = 8, dpi=300, units = "in") -->

<!-- ``` -->

```{r, echo=FALSE, fig.width=12, fig.height=14}

grid.newpage()
grid.draw(g[["milestone - hor targets"]])

```

---

# Supplementary Information:

### Supplementary Figure 1 - Variable renewables sensitivity panel

<!-- (a) Wind and Solar generation (TWh) -->

```{r supplChart_figure1a, echo=FALSE}

vars <- c(
#  "Solar CSP" = "SE|Electricity|Solar|CSP",
  "Solar PV" = "SE|Electricity|Solar|PV",
  "Wind Onshore" = "SE|Electricity|Wind|Onshore",
  "Wind Offshore" = "SE|Electricity|Wind|Offshore")

color <- c(
  "Solar CSP"     = "#ffcc00",
  "Solar PV"      = "#ffe600",
  "Wind Onshore"  = "#193F7F",
  "Wind Offshore" = "#337fff")

pattern <- c(
  "default"="none",
  "limited VRE"="stripe"
)

plotData <- df_beforeFilter %>%
  filter(region == "EU27", period %in% c(2020,2030,2040,2050), scenario %in% c(mainScen,"Nzero_57_bio7p5_limVRE"), variable %in% vars) %>%
  mutate(scenName = ifelse(scenario == mainScen, "default", "limited VRE"),
         value = round(value * EJ2TWh),
         unit = "TWh")

#plotData %>% filter( period == 2040) %>% group_by(scenario) %>% summarise(value = sum(value))
#value2040 <- plotData %>% filter( period == 2040) %>% group_by(scenario) %>% summarise(value = sum(value)) %>% pull(value)
#round((1-value2040[2]/value2040[1])*100,2)

barwidth <- 3

g[["Wind and Solar generation"]] <- ggplot() +
  geom_bar_pattern(data = plotData %>% filter(scenario == mainScen), mapping = aes(x=period - (barwidth + 1)/2,y=value, fill=variable, pattern=scenName), stat='identity', position="stack", width = barwidth) +
  geom_bar_pattern(data = plotData %>% filter(scenario == "Nzero_57_bio7p5_limVRE"), mapping = aes(x=period + (barwidth + 1)/2,y=value, fill=variable, pattern=scenName), stat='identity', position="stack", width = barwidth, pattern_key_scale_factor = 0.3, pattern_density=0.3, pattern_spacing = 0.03, pattern_colour = "white", pattern_fill = "white", pattern_alpha=0.4) +
  geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
  theme_doubleColumn() +
  scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(nrow = 1, order = 1, override.aes = list(pattern = "none"))) +
  scale_pattern_manual(values = pattern, breaks=c("default","limited VRE"), guide = guide_legend(nrow = 2, order = 1)) +
  scale_x_continuous(breaks=c(2020,2030,2040,2050), minor_breaks = NULL) +
  theme(axis.title.y = element_blank()) +
  #ylab("TWh") +
  #theme(legend.text=element_text(size=theme.single.text.size)) +
  theme(legend.margin=margin(t = -0.4, unit='cm')) +
  labs(title = "(a) Wind and Solar Generation (TWh)") + 
  #theme(plot.title = element_text(hjust=-0.1))
  theme(legend.box = "horizontal", 
        legend.box.just = "center")

 # ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 1 - Variable renewables sensitivity panel - (a) Wind and Solar generation.svg"), g[["Wind and Solar generation"]] , device="svg", width = 9, height = 6, dpi=100, units = "in")
 # ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 1 - Variable renewables sensitivity panel - (a) Wind and Solar generation.png"), g[["Wind and Solar generation"]] , device="png", width = 9, height = 6, dpi=300, units = "in")

```

(b) Limited VRE target reduction (%)

```{r supplChart_figure1b, echo=FALSE}

# error bars for scenarios with and without limVRE

plotData <- rbind(
  df %>%
    filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
    mutate(reduction = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)) ,2),
           scenName = "default") %>%
    select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  group_by(period) %>%
  mutate(min = min(reduction),
        max = max(reduction))
  ,
  df_beforeFilter %>%
    filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen, grepl("limVRE", scenario)) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
    mutate(reduction = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)) ,2),
           scenName = "limited VRE") %>%
    select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  group_by(period) %>%
  mutate(min = min(reduction),
        max = max(reduction))
)

g[["limVRE target reduction"]] <- ggplot(plotData, aes(x = scenName, y = reduction, group=scenName)) +
  geom_errorbar(mapping = aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=0.3) +
  geom_hline(yintercept=1, color = "black", linewidth=2, alpha = 0.5) +
  #geom_hline(yintercept=1, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  theme_doubleColumn() +
  scale_y_reverse(breaks=c(1,0.95,0.9,0.85,0.8, 0.75), minor_breaks = NULL, labels = scales::percent) +
  expand_limits(y=c(1,0.75)) +
  labs(title = "(b) 2040 target (%)")

 # ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 1 - Variable renewables sensitivity panel - (b) 2040 target.svg"), g[["limVRE target reduction"]] , device="svg", width = 3, height = 6, dpi=100, units = "in")
 # ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 1 - Variable renewables sensitivity panel - (a) 2040 target.png"), g[["limVRE target reduction"]] , device="png", width = 3, height = 6, dpi=300, units = "in")

# g[["Supplementary Figure 1 - Variable renewables sensitivity panel"]] <- gridExtra::arrangeGrob(
#   g[["Wind and Solar generation"]], #+ theme(plot.margin=margin(80,5,50,0)), #margin(t = 0, r = 0, b = 0, l = 0
#   g[["limVRE target reduction"]], #+ theme(plot.margin=margin(80,5,50,0)), #margin(t = 0, r = 0, b = 0, l = 0
#   layout_matrix = rbind(c(1,1,1,2))
#   )

# ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 1 - Variable renewables sensitivity panel.svg"), g[["Supplementary Figure 1 - Variable renewables sensitivity panel"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 1 - Variable renewables sensitivity panel.png"), g[["Supplementary Figure 1 - Variable renewables sensitivity panel(GW)"]] , device="png", width = 12, height = 6, dpi=300, units = "in")

```

```{r, echo=FALSE, include=FALSE}

g[["Supplementary figure 1"]] <- gridExtra::arrangeGrob(
  g[["Wind and Solar generation"]] + theme(plot.margin=margin(t=10)), 
  g[["limVRE target reduction"]] + theme(plot.margin=margin(l=20, b=10, t=10)), 
  layout_matrix = rbind(c(1,1,1,2))
)

ggsave(paste0(outChartsFolder,"/png/Supplementary figure 1. Variable Renewable Energy.png"), g[["Supplementary figure 1"]], device="png", width = 12, height = 6, dpi=300, units = "in")
ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 1. Variable Renewable Energy.svg"), g[["Supplementary figure 1"]], device="svg", width = 12, height = 6, dpi=100, units = "in")

```

```{r, echo=FALSE, fig.width=12, fig.height=6}

grid.newpage()
grid.draw(g[["Supplementary figure 1"]])

```

---

### Supplementary Figure 2 - Mitigation costs panel

<!-- :::: {style="display: flex;"} -->

<!-- ::: {} -->

<!-- (a) Carbon price (€/t CO2) -->

```{r supplChart_figure2a, echo=FALSE, include=FALSE}

vars <- c(
  "Carbon price" = "Price|Carbon"
)

plotData <- df_beforeFilter %>%
  filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
  mutate(period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"),
         value = 1.17*value)

ETS_price <- addHist$ETS_price %>%
  mutate(scenario = "ETS price")

g[["Carbon Price"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
  geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
  geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
  geom_line(size = 0.5, aes(linetype=tgt2030, color = efficiency)) +
  geom_point(size = 3, aes(shape = lim, fill = bioLim)) +
  geom_line(data=ETS_price,aes(x=Date, y=Price),size=0.5, color = "#000000") +
  scale_x_date(date_labels = "%Y") +
  scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1))) +   
  scale_color_manual(values = c("reference"="#ae0000", "EED 2018 Eff"="#db4646", "FitFor55 eff"="#0090ab", "RePowerEU eff"="#095786"), guide = guide_legend(nrow =2, byrow = F, order = 2, override.aes = list(linewidth = 1.5))) + 
  scale_fill_manual(values = c("BioLim4"="#fedc97", "BioLim7.5"="#b5b682", "BioLim12"="#7c9885", "BioLim20"="#28666e"), guide = guide_legend(nrow =2, byrow = F, override.aes = list(shape = 21, size = 6, colour = "transparent"), order = 3)) +
  scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 6))) +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  #guides(fill = guide_legend(nrow = 2, byrow = T)) +
  #theme(legend.text=element_text(size=theme.single.text.size)) +
  theme(legend.key.width = unit(2,"cm")) +
  theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical") + 
  #theme(legend.key.width = unit(2,"cm")) +
  #ylab("€/t CO2") +
  theme(legend.spacing.y = unit(0.2, "lines")) +
  labs(title = "(a) Carbon price (€/t CO2)") #+ 
  #theme(plot.title = element_text(hjust=-0.1))
  #guides(linetype=guide_legend(keywidth = 3))

#  theme(legend.position="right", legend.direction = "vertical")

# ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 2 - Mitigation costs panel - (a) Carbon Price.svg"), g[["Carbon Price"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Supplementary figure 2 - Mitigation costs panel - (a) Carbon Price.png"), g[["Carbon Price"]] , device="png", width = 12, height = 6, dpi=300, units = "in")

```

<!-- ```{r, echo=FALSE, fig.width=12, fig.height=5} -->

<!-- g[["Carbon Price"]] -->

<!-- ``` -->

<!-- (b) Energy supply electricity investments (billion €/yr) -->

```{r supplChart_figure2b, echo=FALSE, include=FALSE}

vars <- c(
#  "Grid" = "Energy Investments|Electricity|Grid",
  "Grid - BEV Chargers" = "Energy Investments|Electricity|Grid|BEV Chargers",
  "Grid - VRE support" = "Energy Investments|Electricity|Grid|VRE support",
  "Grid - T&D" = "Energy Investments|Electricity|Grid|Normal",
  "Hydrogen"   = "Energy Investments|Electricity|Hydrogen",
  "Storage"    = "Energy Investments|Electricity|Storage",
  "Solar" = "Energy Investments|Electricity|Solar",
  "Wind" = "Energy Investments|Electricity|Wind",
  "Hydro" = "Energy Investments|Electricity|Hydro",
  "Nuclear" = "Energy Investments|Electricity|Nuclear",
  "Geothermal" = "Energy Investments|Electricity|Geothermal",
  "Biomass w/ CC" = "Energy Investments|Electricity|Biomass|w/ CC",
  "Biomass w/o CC" = "Energy Investments|Electricity|Biomass|w/o CC",
  "Oil" = "Energy Investments|Electricity|Oil",
  "Gas w/ CC" = "Energy Investments|Electricity|Gas|w/ CC",
  "Gas w/o CC" = "Energy Investments|Electricity|Gas|w/o CC",
  "Coal w/ CC" = "Energy Investments|Electricity|Coal|w/ CC",
  "Coal w/o CC" = "Energy Investments|Electricity|Coal|w/o CC")

color <- c(
#   "Grid" = "",
  "Grid - BEV Chargers" = "#BC4873",
  "Grid - VRE support"  ="#003F5C",
  "Grid - T&D"     = "#472b62",
  "Storage"        = "#9500da",
  "Wind"           = "#337fff",
  "Solar"          = "#ffe600",
  "Biomass w/o CC" = "#005900",
  "Biomass w/ CC"  = "#33ff00",
  "Hydro"          = "#191999",
  "Geothermal"     = "#e51900",
  "Nuclear"        = "#ff33ff",
  "Hydrogen"       = "#5ed5b0",
  "Gas w/o CC"     = "#999959",
  "Gas w/ CC"      = "#b79e38",
  "Oil"            = "#b30000",
  "Coal w/o CC"    = "#0c0c0c",
  "Coal w/ CC"     = "#b2b2b2")

plotData <- df %>% 
  filter(region == "EU27", period >= 2020, period <= 2050, scenario  == mainScen, variable %in% unlist(vars)) %>% 
  mutate(variable = factor(variable, levels=vars),
   value = 1.17*value) #%>% 
 # arrange(factor(variable, levels = rev(vars)))

g[["Energy Supply Investments"]] <- ggplot(plotData, aes(x=period,y=value, fill=variable)) +
  geom_bar(stat='identity', position="stack") +
  geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank()) +
  scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(ncol = 1, order = 1)) +
  #ylab("billion €/yr") +
  theme(#legend.text=element_text(size=0.8*geomText.size),
        legend.key.height = unit(0.6, "cm"),
        legend.key.width = unit(0.6,"cm")) +
  theme(legend.position="left", legend.direction = "vertical", legend.box = "vertical",
        legend.margin=margin(t = 40)) +
  labs(title = "(b) Energy supply investments (billion €/yr) ") #+ 
  #theme(plot.title = element_text(hjust=-0.6))

# ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 2 - Mitigation costs panel - (b) Energy Supply Investments.svg"), g[["Energy Supply Investments"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Supplementary figure 2 - Mitigation costs panel - (b) Energy Supply Investments.png"), g[["Energy Supply Investments"]] , device="png", width = 12, height = 6, dpi=300, units = "in")

```

<!-- ```{r, echo=FALSE, fig.width=12, fig.height=5} -->

<!-- g[["Energy Supply Investments"]] -->

<!-- ``` -->

```{r, echo=FALSE, include=FALSE}

g[["Supplementary figure 2"]] <- gridExtra::arrangeGrob(
  g[["Carbon Price"]], 
  g[["Energy Supply Investments"]], 
  layout_matrix = rbind(
    c(1),
    c(2)
  ))

ggsave(paste0(outChartsFolder,"/png/Supplementary figure 2. EU-27 mitigation costs panel.png"), g[["Supplementary figure 2"]], device="png", width = 12, height = 10, dpi=300, units = "in")
ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 2. EU-27 mitigation costs panel.svg"), g[["Supplementary figure 2"]], device="svg", width = 12, height = 10, dpi=100, units = "in")

```

```{r, echo=FALSE, fig.width=12, fig.height=10}

grid.newpage()
grid.draw(g[["Supplementary figure 2"]])

```

---

### Supplementary Figure 3 - Country results electricity capacity panel (GW)

```{r supplChart_figure3, echo=FALSE, include=FALSE}

vars <- c(
  "Net Imports" = "Cap|Electricity|Net Imports",
  "Coal w/ CC" = "Cap|Electricity|Coal|w/ CC",
  "Coal w/o CC" = "Cap|Electricity|Coal|w/o CC",
  "Oil" = "Cap|Electricity|Oil",
  "Gas w/ CC" = "Cap|Electricity|Gas|w/ CC",
  "Gas w/o CC" = "Cap|Electricity|Gas|w/o CC",
  "Hydrogen" = "Cap|Electricity|Hydrogen",
  "Nuclear" = "Cap|Electricity|Nuclear",
  "Geothermal" = "Cap|Electricity|Geothermal",
  "Hydro" = "Cap|Electricity|Hydro",
  "Biomass w/ CC" = "Cap|Electricity|Biomass|w/ CC",
  "Biomass w/o CC" = "Cap|Electricity|Biomass|w/o CC",
  "Solar CSP" = "Cap|Electricity|Solar|CSP",
  "Solar PV" = "Cap|Electricity|Solar|PV",
  "Wind Onshore" = "Cap|Electricity|Wind|Onshore",
  "Wind Offshore" = "Cap|Electricity|Wind|Offshore",
  "Battery Storage" = "Cap|Electricity|Storage|Battery")

color <- c(
  "Net Imports"   = "#472b62",
  "Coal w/ CC"    = "#b2b2b2",
  "Coal w/o CC"   = "#0c0c0c",
  "Oil"           = "#b30000",
  "Gas w/ CC"     = "#b79e38",
  "Gas w/o CC"    = "#999959",
  "Hydrogen"      = "#5ed5b0",
  "Nuclear"       = "#ff33ff",
  "Geothermal"    = "#e51900",
  "Hydro"         = "#191999",
  "Biomass w/ CC" = "#33ff00",
  "Biomass w/o CC"= "#005900",
  "Solar CSP"     = "#ffcc00",
  "Solar PV"      = "#ffe600",
  "Wind Onshore"  = "#193F7F",
  "Wind Offshore" = "#337fff",
  "Battery Storage"="#9500da")

regName <- c(
  "EU27" = "European Union",
  "DEU" = "Germany",
  "FRA" = "France"
)

plotData <- df %>% 
  filter(region %in% c("EU27","DEU","FRA"), period >= 2020, period <= 2060, scenario  == mainScen, variable %in% unlist(vars)) %>% 
  mutate(variable = factor(variable, levels=rev(vars)),
         region = factor(region, levels=c("EU27","DEU","FRA"))) %>% 
  arrange(factor(variable, levels = rev(vars))) %>%
  mutate(regionName = regName[region])

g[["Capacity"]] <- lapply(setNames(c("EU27","DEU","FRA"),c("EU27","DEU","FRA")), function(reg){
  gg <- ggplot(plotData %>% filter(region == reg),aes(x=period,y=value)) +
  geom_area(aes(fill=variable),alpha=0.8) +
  facet_wrap(~regionName, scales = "free_y") +
  theme_doubleColumn() +
  scale_x_continuous(breaks=c(2020,2040,2060)) +
  scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
  theme(legend.position="none") +
  theme(axis.title.y=element_blank()) +
  theme(strip.clip = "off")
})

g[["Capacity_2040"]] <- lapply(setNames(c("EU27","DEU","FRA"),c("EU27","DEU","FRA")), function(reg){
  gg <- ggplot(plotData %>%
                 filter(region == reg, period == 2040) %>%
                 group_by(model,scenario,region,period) %>%
                 mutate(n = sum(value), percentage = value / n),
               aes(x=period,y=percentage)) +
  geom_bar(aes(fill=variable),alpha=0.8,stat='identity') +
  facet_wrap(~period, scales = "free_y") +
  theme_doubleColumn() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(breaks=c(2040)) +
  scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
  theme(legend.position="none") +
  theme(axis.title.y=element_blank()) +
  theme(strip.clip = "off")
})

## Function to extract legend
g_legend <- function(a.gplot){ 
    tmp <- ggplot_gtable(ggplot_build(a.gplot)) 
    leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box") 
    legend <- tmp$grobs[[leg]] 
    legend
}

legend <- g_legend(
  ggplot(plotData,aes(x=period,y=value)) +
  geom_area(aes(fill=variable),alpha=0.8) +
  theme_doubleColumn() +
  scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
  guides(fill=guide_legend(nrow=2,override.aes = list(alpha=1))) +
  theme(#legend.text = element_text(size = theme.double.text.size),
        #legend.key.height = unit(0.8, "cm"),
        #legend.key.width = unit(0.8,"cm"),
        legend.spacing.x = unit(0.3, 'cm')) +
  theme(legend.title=element_blank(),
        legend.margin=margin(c(0,0,0,0))) +
  theme(plot.margin=margin(0,0,0,0)) + 
  theme(legend.margin=margin(l=-10))
)

g[["Supplementary Figure 3 - Country results electricity capacity panel (GW)"]] <- gridExtra::arrangeGrob(
  g[["Capacity"]][["EU27"]] + theme(plot.margin=margin(b=0)), #+ theme(plot.margin=margin(80,5,50,0)), #margin(t = 0, r = 0, b = 0, l = 0
  g[["Capacity_2040"]][["EU27"]] + theme(plot.margin=margin(0,20,37,0)), #+ theme(plot.margin=margin(80,5,50,0)), #margin(t = 0, r = 0, b = 0, l = 0
  g[["Capacity"]][["DEU"]] + theme(plot.margin=margin(b=0)), #+ theme(plot.margin=margin(80,5,50,0)), #margin(t = 0, r = 0, b = 0, l = 0
  g[["Capacity_2040"]][["DEU"]] + theme(plot.margin=margin(0,20,37,0)), #+ theme(plot.margin=margin(80,5,50,0)), #margin(t = 0, r = 0, b = 0, l = 0
  g[["Capacity"]][["FRA"]] + theme(plot.margin=margin(b=0)), #+ theme(plot.margin=margin(80,5,50,0)), #margin(t = 0, r = 0, b = 0, l = 0
  g[["Capacity_2040"]][["FRA"]] + theme(plot.margin=margin(0,20,37,0)), #+ theme(plot.margin=margin(80,5,50,0)), #margin(t = 0, r = 0, b = 0, l = 0
  legend,
  layout_matrix = rbind(c(1,1,1,1, 2,2, 3,3,3,3, 4,4, 5,5,5,5, 6,6),
                        c(1,1,1,1, 2,2, 3,3,3,3, 4,4, 5,5,5,5, 6,6),
                        c(1,1,1,1, 2,2, 3,3,3,3, 4,4, 5,5,5,5, 6,6),
                        rep(7,18))
  )

 ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 3 - Country results electricity capacity panel (GW).svg"), g[["Supplementary Figure 3 - Country results electricity capacity panel (GW)"]] , device="svg", width = 12, height = 5, dpi=100, units = "in")
 ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 3 - Country results electricity capacity panel (GW).png"), g[["Supplementary Figure 3 - Country results electricity capacity panel (GW)"]] , device="png", width = 12, height = 5, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=12, fig.height=5}

grid.newpage()
grid.draw(g[["Supplementary Figure 3 - Country results electricity capacity panel (GW)"]])

```

---

### Supplementary Figure 4 - Sectoral mitigation - Energy and non-energy use panel

<!-- :::: {style="display: flex;"} -->

<!-- ::: {} -->

<!-- (a) per sector and carrier -->

```{r supplChart_figure4a, echo=FALSE, include=FALSE}

vars <- list(
  "Transport - Electricity" = "FE|Transport|Electricity",
  "Buildings - Electricity" = "FE|Buildings|Electricity",
  "Industry - Electricity" = "FE|Industry|Electricity",
  "Transport - Hydrogen" = "FE|Transport|Hydrogen",
  "Buildings - Hydrogen" = "FE|Buildings|Hydrogen",
  "Industry - Hydrogen" = "FE|Industry|Hydrogen",
  "Buildings - Heat" = "FE|Buildings|Heat",
  "Industry - Heat" = "FE|Industry|Heat",
  "Transport - Gases" = "FE|Transport|Gases",
  "Buildings - Gases" = "FE|Buildings|Gases",
  "Industry - Gases" = "FE|Industry|Gases",
  "Transport - Liquids" = "FE|Transport|Liquids",
  "Buildings - Liquids" = "FE|Buildings|Liquids",
  "Industry - Liquids" = "FE|Industry|Liquids",
  "Buildings - Solids" = "FE|Buildings|Solids",
  "Industry - Solids" = "FE|Industry|Solids"
)

plotColor <- list(
  "Transport - Electricity" = "#ffb200",
  "Buildings - Electricity" = "#ffcc55",
  "Industry - Electricity" = "#fa8c02",
  "Transport - Hydrogen" = "#46fc02",
  "Buildings - Hydrogen" = "#94ff6c",
  "Industry - Hydrogen" = "#2b7c0d",
  "Buildings - Heat" = "#ff7a59",
  "Industry - Heat" = "#b92400",
  "Transport - Gases" = "#b200ff",
  "Buildings - Gases" = "#c875ec",
  "Industry - Gases" = "#610d85",
  "Transport - Liquids" = "#0f30ec",
  "Buildings - Liquids" = "#7e8fef",
  "Industry - Liquids" = "#04167c",
  "Buildings - Solids" = "#a5a5a5",
  "Industry - Solids" = "#1b1b1b"
)

plotData <- df %>%
  filter(region == "EU27", period %in% c(2010:2050), variable %in% vars, scenario == mainScen) %>%
  mutate(variable=factor(variable, levels=vars))

#total
totalData <- df %>%
  filter(region == "EU27", period %in% c(2010:2050), variable == "FE", scenario == mainScen)

if(energyInMtoe){
  plotData <- plotData %>%
    mutate(
      value = value*EJ2Mtoe,
      unit  = "Mtoe/yr")
  totalData <- totalData %>%
    mutate(
      value = value*EJ2Mtoe,
      unit  = "Mtoe/yr")
}

g[["Supplementary Figure 4a. Final energy demand per sector and carrier"]] <- ggplot(plotData,aes(x=period,y=value)) +
  geom_area(aes(fill=variable), alpha = 0.8) +
  geom_line(data=totalData, linewidth = 1, color="black") +
  geom_vline(xintercept=2020, color = "black", linetype="dashed", linewidth=1, alpha = 0.5) +
  geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
  theme_doubleColumn() +
  #ylab("Final Energy Demand - EJ/yr") + 
  #ggtitle("(a) per sector and carrier") +
  scale_fill_manual(values = setNames(plotColor[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(nrow = 6)) +
  theme(legend.margin=margin(l = -1, unit='cm')) +
  scale_x_continuous(breaks=c(2010, 2010, 2020,2030,2040,2050)) + 
  theme(axis.title.x=element_blank()) +
  theme(axis.title.y=element_blank()) +
  theme(legend.title = element_blank()) +
  theme(#legend.text = element_text(size = theme.double.text.size*0.7),
        #legend.key.height = unit(0.7, "cm"),
        #legend.key.width = unit(0.7,"cm"),
        legend.spacing.x = unit(0.2, 'cm')) + 
  #  theme(plot.title = element_text(size = 1.2*theme.double.text.size)) +
  labs(title = paste0("(a) Energy and non-energy use per sector and carrier (", unique(plotData$unit), ")")) +
  theme(plot.title = element_text(hjust=1))

ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 4a. Final energy demand per sector and carrier.svg"), g[["Supplementary Figure 4a. Final energy demand per sector and carrier"]] , device="svg", width = 6, height = 8, dpi=100, units = "in")
ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 4a. Final energy demand per sector and carrier.png"), g[["Supplementary Figure 4a. Final energy demand per sector and carrier"]] , device="png", width = 6, height = 8, dpi=300, units = "in")

```

<!-- ```{r, echo=FALSE, fig.width=6, fig.height=8} -->

<!-- g[["Supplementary Figure 4a. Final energy demand per sector and carrier"]] -->

<!-- ``` -->

<!-- ::: -->

<!-- ::: {} -->

<!-- (b) per fossil content -->

```{r supplChart_figure4b, echo=FALSE, include=FALSE}

vars <- list(
  "Electric - Non-Fossil" = c(
    "FE|Transport|Electricity|Non-Fossil",
    "FE|Buildings|Electricity|Non-Fossil",
    "FE|Industry|Electricity|Non-Fossil"
   ),
  "Non-Electric - Non-Fossil" = c(
    "FE|Transport|Hydrogen",
    "FE|Buildings|Hydrogen",
    "FE|Industry|Hydrogen",
    "FE|Buildings|Heat",
    "FE|Industry|Heat",
    "FE|Transport|Gases|Biomass",
    "FE|Transport|Gases|Hydrogen",
    "FE|Buildings|Gases|Biomass",
    "FE|Buildings|Gases|Hydrogen",
    "FE|Industry|Gases|Biomass",
    "FE|Industry|Gases|Hydrogen",
    "FE|Transport|Liquids|Biomass",
    "FE|Transport|Liquids|Hydrogen",
    "FE|Buildings|Liquids|Biomass",
    "FE|Buildings|Liquids|Hydrogen",
    "FE|Industry|Liquids|Biomass",
    "FE|Industry|Liquids|Hydrogen",
    "FE|Buildings|Solids|Biomass",
    "FE|Industry|Solids|Biomass"
  ), 
  "Electric - Fossil" = c(
    "FE|Transport|Electricity|Fossil",
    "FE|Buildings|Electricity|Fossil",
    "FE|Industry|Electricity|Fossil"
   ),
  "Non-Electric - Fossil" = c(
    "FE|Buildings|Gases|Fossil",
    "FE|Transport|Gases|Fossil",
    "FE|Industry|Gases|Fossil",
    "FE|Transport|Liquids|Fossil",
    "FE|Buildings|Liquids|Fossil",
    "FE|Industry|Liquids|Fossil",
    "FE|Buildings|Solids|Fossil",
    "FE|Industry|Solids|Fossil"
  )
)

plotColor <- list(
  "Electric - Non-Fossil" = "#e56b6f",
  "Non-Electric - Non-Fossil" = "#6d597a",
  "Electric - Fossil" = "#474973",
  "Non-Electric - Fossil" = "#161b33"
)

var2label <- c()
for(label in names(vars)){
  for (var in vars[[label]]){
    tmp <- as.character(label)
    names(tmp) <- as.character(var)
    var2label <- c(var2label,tmp)
  }
}

plotData <- df %>%
  filter(region == "EU27", period %in% c(2010:2050), variable %in% unlist(vars), scenario == mainScen) %>%
  mutate(label=as.character(var2label[as.character(variable)])) %>%
  mutate(label=factor(label, levels=names(vars))) %>%
  group_by(period,label,unit) %>%
  summarize(value = sum(value))

#total
totalData <- df %>%
  filter(region == "EU27", period %in% c(2010:2050), variable == "FE", scenario == mainScen)

if(energyInMtoe){
  plotData <- plotData %>%
    mutate(
      value = value*EJ2Mtoe,
      unit  = "Mtoe/yr")
  totalData <- totalData %>%
    mutate(
      value = value*EJ2Mtoe,
      unit  = "Mtoe/yr")
}

g[["Supplementary Figure 4b. Final energy demand per fossil content"]] <- ggplot(plotData,aes(x=period,y=value)) +
  geom_area(aes(fill=label), alpha = 0.8) +
  geom_line(data=totalData, linewidth = 1, color="black") +
  geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
  geom_vline(xintercept=2020, color = "black", linetype="dashed", linewidth=1, alpha = 0.5) +
  theme_doubleColumn() +
  scale_fill_manual(values = plotColor, guide = guide_legend(nrow = 6)) +
  #ggtitle("(b) per fossil content") +
  theme(legend.margin=margin(l = -1, unit='cm')) +
  scale_x_continuous(breaks=c(2010, 2010, 2020,2030,2040,2050)) + 
  theme(axis.title.x=element_blank()) +
  theme(axis.title.y=element_blank()) +
  theme(legend.title = element_blank()) +
  theme(#legend.text = element_text(size = theme.double.text.size*0.7),
        #legend.key.height = unit(0.7, "cm"),
        #legend.key.width = unit(0.7,"cm"),
        legend.spacing.x = unit(0.2, 'cm')) + 
  #  theme(plot.title = element_text(size = 1.2*theme.double.text.size)) +
  labs(title = paste0("(b) Energy and non-energy use per fossil content (", unique(plotData$unit), ")")) +
  theme(plot.title = element_text(hjust=1))

# ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 4b. Final energy demand per fossil content.svg"), g[["Supplementary Figure 4b. Final energy demand per fossil content"]] , device="svg", width = 6, height = 8, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 4b. Final energy demand per fossil content.png"), g[["Supplementary Figure 4b. Final energy demand per fossil content"]] , device="png", width = 6, height = 8, dpi=300, units = "in")

```

<!-- ```{r, echo=FALSE, fig.width=6, fig.height=8} -->

<!-- g[["Supplementary Figure 4b. Final energy demand per fossil content"]] -->

<!-- ``` -->
<!-- ::: -->

<!-- :::: -->

```{r, echo=FALSE, include=FALSE}

g[["Supplementary figure 4"]] <- gridExtra::arrangeGrob(
  g[["Supplementary Figure 4a. Final energy demand per sector and carrier"]], 
  g[["Supplementary Figure 4b. Final energy demand per fossil content"]], 
  layout_matrix = rbind(
    c(1,2)
  ))

ggsave(paste0(outChartsFolder,"/png/Supplementary figure 4. Energy and non-energy use.png"), g[["Supplementary figure 4"]], device="png", width = 12, height = 8, dpi=300, units = "in")
ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 4. Energy and non-energy use.svg"), g[["Supplementary figure 4"]], device="svg", width = 12, height = 8, dpi=100, units = "in")

```

```{r, echo=FALSE, fig.width=12, fig.height=8}

grid.newpage()
grid.draw(g[["Supplementary figure 4"]])

```

---

### Supplementary Figure 5 - Sectoral mitigation - GHG Emissions per sector (Mt CO2/yr)

```{r supplChart_figure5, echo=FALSE, include=FALSE}

vars <- c(
  "Energy Supply - Electricity"               = "Emi|GHG|Gross|Energy|Supply|Electricity",
  "Energy Supply - Non-electric"              = "Emi|GHG|Gross|Energy|Supply|Non-electric",
  "Energy Demand - Transport"                 = "Emi|GHG|Energy|Demand|Transport",
  "Energy Demand - International Bunkers"     = "Emi|CO2|Energy|Demand|Transport|International Bunkers",
  "Energy Demand - Buildings"                 = "Emi|GHG|Energy|Demand|Buildings",
  "Energy Demand - Industry and Agriculture"  = "Emi|GHG|Gross|Energy|Demand|Industry",
  "Energy Demand - Carbon Dioxide Removal"    = "Emi|GHG|Energy|Demand|CDR",
  "Industrial Processes"                      = "Emi|GHG|Industrial Processes",
  "Agriculture"                               = "Emi|GHG|Agriculture",
  "Land-Use Change"                           = "Emi|GHG|Land-Use Change|LULUCF national accounting", #"Emi|GHG|Land-Use Change",
  "Waste"                                     = "Emi|GHG|Waste",
  "BECCS"                                     = "Emi|CO2|CDR|BECCS",
  "Industry CCS"                              = "Emi|CO2|CDR|Industry CCS|Synthetic Fuels",
  "DACCS"                                     = "Emi|CO2|CDR|DACCS",
  "Enhanced Weathering"                       = "Emi|CO2|CDR|EW")

plotColor <- c(
  "Energy Supply - Electricity"               = "#ffb200",
  "Energy Supply - Non-electric"              = "#0000cc",
  "Energy Demand - Transport"                 = "#a1dd70",
  "Energy Demand - International Bunkers"     = "#ffc0cb",
  "Energy Demand - Buildings"                 = "#5edfff",
  "Energy Demand - Industry and Agriculture"  = "#5f6769",
  "Energy Demand - Carbon Dioxide Removal"    = "#999959",
  "Industrial Processes"                      = "#5c5c5c",
  "Agriculture"                               = "#357933",
  "Land-Use Change"                           = "#6ec16b",
  "Waste"                                     = "#A52A2A",
  "BECCS"                                     = "#377EB8",
  "Industry CCS"                              = "#5ed5b0",
  "DACCS"                                     = "#CC6666",
  "Enhanced Weathering"                       = "#5b0d8f")

plotData <- df %>%
  filter(region == "EU27", period %in% c(2010:2050), variable %in% vars, scenario == mainScen) %>%
  mutate(variable=factor(variable, levels=vars))

#total
totalData <- df %>%
  calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%
  filter(region == "EU27", period %in% c(2010:2050), variable == "Emissions with LULUCF and with international transport", scenario == mainScen)

# check <- left_join(
#   plotData %>% group_by(period) %>% summarize(value = sum(value)),
#   totalData %>% group_by(period) %>% summarize(total = sum(value)),
#   by = join_by(period == period)
# ) %>%
#   mutate(diff= round(total-value,2))
# 
# left_join(
#   plotData %>% filter(period == 2010) %>% mutate(value2010 = value),
#   plotData %>% filter(period == 2015) %>% mutate(value2015 = value),
#   by = join_by(variable == variable)
# ) %>%
#   mutate(diff= round(value2015-value2010,2)) %>%
#   select(variable,value2010,value2015,diff)

g[["Supplementary Figure 5 - Sectoral mitigation - GHG Emissions per sector"]] <- ggplot(plotData,aes(x=period,y=value)) +
  geom_area(aes(fill=variable), alpha = 0.8) +
  geom_line(data=totalData, linewidth = 1, color="black") +
  geom_vline(xintercept=2020, color = "black", linetype="dashed", linewidth=1, alpha = 0.5) +
  geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
  theme_doubleColumn() +
  #ylab("Final Energy Demand - EJ/yr") + 
  #ggtitle("(a) per sector and carrier") +
  scale_fill_manual(values = setNames(plotColor[names(vars)],vars), labels = setNames(names(vars), vars)) +
  #theme(legend.margin=margin(l = -1, unit='cm')) +
  scale_x_continuous(breaks=c(2010, 2010, 2020,2030,2040,2050)) + 
  theme(axis.title.x=element_blank()) +
  theme(axis.title.y=element_blank()) +
  theme(legend.title = element_blank()) +
  theme(#legend.text = element_text(size = theme.double.text.size*0.7),
        #legend.key.height = unit(0.7, "cm"),
        #legend.key.width = unit(0.7,"cm"),
        legend.spacing.x = unit(0.2, 'cm')) + 
  #  theme(plot.title = element_text(size = 1.2*theme.double.text.size)) +
  theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical")

ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 5 - Sectoral mitigation - GHG Emissions per sector.svg"), g[["Supplementary Figure 5 - Sectoral mitigation - GHG Emissions per sector"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 5 - Sectoral mitigation - GHG Emissions per sector.png"), g[["Supplementary Figure 5 - Sectoral mitigation - GHG Emissions per sector"]] , device="png", width = 12, height = 6, dpi=300, units = "in")

```

```{r, echo=FALSE, fig.width=12, fig.height=6}

g[["Supplementary Figure 5 - Sectoral mitigation - GHG Emissions per sector"]]

```

<!-- explain LULUCF and agriculture assumptions  -->

---

### Supplementary Figure 6 - GHG emissions per gases (Mt CO2/yr)

```{r supplChart_figure6, echo=FALSE, include=FALSE}

vars <- c(
  "CO2 - Energy"                = "Emi|CO2|Energy",
  "CO2 - International Bunkers" = "Emi|CO2|Energy|Demand|Transport|International Bunkers",
  "CO2 - Industrial Processes"  = "Emi|CO2|Industrial Processes",
  "CO2 - Land-Use Change"       = "Emi|CO2|Land-Use Change|LULUCF national accounting", #"Emi|CO2|Land-Use Change",
  "CO2 - non-BECCS CDR"         = "Emi|CO2|non-BECCS CDR",
  "CH4"                         = "Emi|GHG|CH4",
  "N2O"                         = "Emi|GHG|N2O",
  "F-Gases"                     = "Emi|GHG|F-Gases"
  )

plotColor <- c(
  "CO2 - Energy"                = "#3D4849",
  "CO2 - International Bunkers" = "#ffc0cb",
  "CO2 - Industrial Processes"  = "#5c5c5c",
  "CO2 - Land-Use Change"       = "#6ec16b",
  "CO2 - non-BECCS CDR"         = "#5b0d8f",
  "CH4"                         = "#ffe7a0",
  "N2O"                         = "#44ba97",
  "F-Gases"                     = "#ff9977"
)

plotData <- df %>%
  filter(region == "EU27", period %in% c(2010:2050), variable %in% vars, scenario == mainScen) %>%
  mutate(variable=factor(variable, levels=vars))

#plotData %>% group_by(period) %>% summarize(value = sum(value))

#total
totalData <- df %>%
  calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%
  filter(region == "EU27", period %in% c(2010:2050), variable == "Emissions with LULUCF and with international transport", scenario == mainScen)

g[["Supplementary Figure 6 - GHG emissions per gases"]] <- ggplot(plotData,aes(x=period,y=value)) +
  geom_area(aes(fill=variable), alpha = 0.8) +
  geom_line(data=totalData, linewidth = 1, color="black") +
  geom_vline(xintercept=2020, color = "black", linetype="dashed", linewidth=1, alpha = 0.5) +
  geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
  theme_doubleColumn() +
  #ylab("Final Energy Demand - EJ/yr") + 
  #ggtitle("(a) per sector and carrier") +
  scale_fill_manual(values = setNames(plotColor[names(vars)],vars), labels = setNames(names(vars), vars)) +
  #theme(legend.margin=margin(l = -1, unit='cm')) +
  scale_x_continuous(breaks=c(2010, 2010, 2020,2030,2040,2050)) + 
  theme(axis.title.x=element_blank()) +
  theme(axis.title.y=element_blank()) +
  theme(legend.title = element_blank()) +
  theme(#legend.text = element_text(size = theme.double.text.size*0.7),
        #legend.key.height = unit(0.7, "cm"),
        #legend.key.width = unit(0.7,"cm"),
        legend.spacing.x = unit(0.2, 'cm')) + 
  #  theme(plot.title = element_text(size = 1.2*theme.double.text.size)) +
  theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical")

ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 6 - GHG emissions per gases.svg"), g[["Supplementary Figure 6 - GHG emissions per gases"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 6 - GHG emissions per gases.png"), g[["Supplementary Figure 6 - GHG emissions per gases"]] , device="png", width = 12, height = 6, dpi=300, units = "in")

# 
#   "Emi|CO2|Energy",
#   "Emi|CO2|Industrial Processes",
#   "Emi|CO2|Land-Use Change",
#   "Emi|GHG|CH4",
#   "Emi|GHG|N2O",
#   "Emi|GHG|F-Gases",
#   "Emi|CO2|non-BECCS CDR")
# 
# 
# Emi|CH4
# Emi|CH4|Extraction
# Emi|CH4|Agriculture
# Emi|CH4|Land-Use Change
# Emi|CH4|Waste
# Emi|CH4|Energy Supply
# Emi|N2O
# Emi|N2O|Agriculture
# Emi|N2O|Land-Use Change
# Emi|N2O|Waste
# Emi|N2O|Transport
# Emi|N2O|Industry
# Emi|N2O|Energy Supply
# Emi|GHG|F-Gases

# Emi|CO2
# Emi|CO2|Land-Use Change
# Emi|CO2|Industrial Processes
# Emi|CO2|Energy|Demand|Transport
# Emi|CO2|Energy|Demand|Industry
# Emi|CO2|Energy|Demand|Buildings
# Emi|CO2|Energy|Supply|Non-electric
# Emi|CO2|Energy|Supply|Electricity w/ couple prod
# Emi|CO2|CDR|DACCS
# Emi|CO2|CDR|EW
# Emi|CO2|Energy|Waste

```

```{r, echo=FALSE, fig.width=12, fig.height=6}

g[["Supplementary Figure 6 - GHG emissions per gases"]]

```

---

### Supplementary Figure 7 - Carbon-dioxide removal

<!-- :::: {style="display: flex;"} -->

<!-- ::: {} -->

<!-- (a) Bioenergy with Carbon Capture and Storage - BECCS (Mt CO2/yr) -->

```{r supplChart_figure7a, echo=FALSE, include=FALSE}

vars <- c(
  "BECCS" = "Emi|CO2|CDR|BECCS"
)

plotData <- df_beforeFilter %>%
  filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
  mutate(min = min(value), max = max(value))

limitsBECCS <- c(
  min(
    df_beforeFilter %>%
      filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen, variable %in% vars) %>% pull(value)),
  max(
    df_beforeFilter %>%
      filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen, variable %in% vars) %>% pull(value)
    ))

limY <- min(plotData %>% pull(min))

g[["BECCS"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
  geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
  geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
  geom_line(size = 0.5, aes(linetype=tgt2030, color = efficiency)) +
  geom_point(size = 3, aes(shape = lim, fill = bioLim)) +
  #scale_x_date(date_labels = "%Y") +
  scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) + 
  scale_color_manual(values = c("reference"="#ae0000", "EED 2018 Eff"="#db4646", "FitFor55 eff"="#0090ab", "RePowerEU eff"="#095786"), guide = guide_legend(nrow =4, byrow = T, order = 2, override.aes = list(linewidth = 1.5))) + 
  scale_fill_manual(values = c("BioLim4"="#fedc97", "BioLim7.5"="#b5b682", "BioLim12"="#7c9885", "BioLim20"="#28666e"), guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) +
  scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  #guides(fill = guide_legend(nrow = 2, byrow = T)) +
  #theme(legend.text=element_text(size=theme.single.text.size)) +
  theme(legend.key.width = unit(2,"cm")) +
  theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical") + 
  #theme(legend.key.width = unit(2,"cm")) +
  theme(legend.spacing.y = unit(0.5, "lines")) +
  theme(legend.position="none") +
  expand_limits(y=limitsBECCS) +
  labs(title = expression(paste("(a) BECCS (Mt ", CO[2],"/yr)"))) +
  theme(plot.title = element_text(hjust=-0.1))

#  theme(legend.position="right", legend.direction = "vertical")

# ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 7 - Carbon-dioxide removal - (a) Bioenergy with Carbon Capture and Storage - BECCS.svg"), g[["BECCS"]] , device="svg", width = 4, height = 6, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Supplementary figure 7 - Carbon-dioxide removal - (a) Bioenergy with Carbon Capture and Storage - BECCS.png"), g[["BECCS"]] , device="png", width = 4, height = 6, dpi=300, units = "in")

```

<!-- ```{r, echo=FALSE, fig.width=4, fig.height=6} -->

<!-- g[["BECCS"]] -->

<!-- ``` -->

<!-- ::: -->

<!-- ::: {} -->

<!-- (b) Direct Air Capture (Mt CO2/yr) -->

```{r supplChart_figure7b, echo=FALSE, include=FALSE}

#"Emi|CO2|CDR|BECCS","Emi|CO2|CDR|DACCS","Emi|CO2|CDR|Industry CCS|Synthetic Fuels"

vars <- c(
  "DAC" = "Emi|CO2|CDR|DACCS"
)

plotData <- df_beforeFilter %>%
  filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars)

limitsDAC <- df_beforeFilter %>%
  filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
  group_by(lim) %>%
  summarize (min = min(value), max = max(value))

g[["DAC"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
  geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
  geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
  geom_line(size = 0.5, aes(linetype=tgt2030, color = efficiency)) +
  geom_point(size = 3, aes(shape = lim, fill = bioLim)) +
  #scale_x_date(date_labels = "%Y") +
  scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1))) +   scale_color_manual(values = c("reference"="#ae0000", "EED 2018 Eff"="#db4646", "FitFor55 eff"="#0090ab", "RePowerEU eff"="#095786"), guide = guide_legend(nrow =2, byrow = F, order = 2, override.aes = list(linewidth = 1.5))) + 
  scale_fill_manual(values = c("BioLim4"="#fedc97", "BioLim7.5"="#b5b682", "BioLim12"="#7c9885", "BioLim20"="#28666e"), guide = guide_legend(nrow =2, byrow = F, override.aes = list(shape = 21, size = 6, colour = "transparent"), order = 3)) +
  scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 6))) +
  theme_doubleColumn() +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  #guides(fill = guide_legend(nrow = 2, byrow = T)) +
  #theme(legend.text=element_text(size=theme.single.text.size)) +
  theme(legend.key.width = unit(2,"cm")) +
  theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical") + 
  #theme(legend.key.width = unit(2,"cm")) +
  theme(legend.spacing.y = unit(0.3, "lines")) +
  expand_limits(y=limY) +
  labs(title = expression(paste("(b) Direct Air Capture (Mt ", CO[2],"/yr)"))) +
  theme(plot.title = element_text(hjust=-0.1))

#  theme(legend.position="right", legend.direction = "vertical")

# ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 7 - Carbon-dioxide removal - (b) Direct Air Capture.svg"), g[["DAC"]] , device="svg", width = 8, height = 6, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Supplementary figure 7 - Carbon-dioxide removal - (b) Direct Air Capture.png"), g[["DAC"]] , device="png", width = 8, height = 6, dpi=300, units = "in")

```

<!-- ```{r, echo=FALSE, fig.width=8, fig.height=6} -->

<!-- g[["DAC"]] -->

<!-- ``` -->

<!-- ::: -->

<!-- :::: -->

```{r, echo=FALSE, include=FALSE}

g[["Supplementary figure 7"]] <- gridExtra::arrangeGrob(
  g[["BECCS"]], 
  g[["DAC"]], 
  layout_matrix = rbind(
    c(1,1,1,2,2,2,2,2,2,2))
  )

ggsave(paste0(outChartsFolder,"/png/Supplementary figure 7. Carbon-dioxide removal.png"), g[["Supplementary figure 7"]], device="png", width = 12, height = 6, dpi=300, units = "in")
ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 7. Carbon-dioxide removal.svg"), g[["Supplementary figure 7"]], device="svg", width = 12, height = 6, dpi=100, units = "in")

```

```{r, echo=FALSE, fig.width=12, fig.height=6}

grid.newpage()
grid.draw(g[["Supplementary figure 7"]])

```

### 2024-08-30 report_plotlyCharts.Rmd
revision1

---
title: "plotly charts for sensitivity iteractive explorer html"
output:
  html_document:
    theme: paper
    toc: true
    toc_float:
      collapsed: false
---

<style>
  .main-container {
    max-width: 95% !important;
  }
  .toc-content {
    padding-left: 0px !important;
  }
  .svg-container {
    margin: auto !important;
  }
</style>

Description:
Plotly charts to be used in iteractive html

Rodrigues, R., Pietzcker, R., Sitarz, J., Merfort, A., Hasse, R., Hoppe, J., Pehl, M., Ershad, A. M., Baumstark, L., Luderer, G. 2040 greenhouse gas reduction targets and energy transitions in line with the EU Green Deal. under revision (2023).

<!-- Setting default chunk options -->
```{r chunkOptions, echo=FALSE, include = FALSE}
#knitr::opts_chunk$set(echo = TRUE)
# setting global R chunk options (https://yihui.name/knitr/options/#chunk_options)
  knitr::opts_chunk$set(dev='svglite', # svg, png,...
                        fig.ext = ".svg",
                        #fig.asp = .8 # default aspect ratio
                        fig.width = 12,
                        fig.height = 6,
                        dpi=100
                        )
```

```{r loading_packages, echo=FALSE, include = FALSE}

  #Loading required packages
  # install.packages("remotes")
  #remotes::install_github("coolbutuseless/ggpattern")
  #install.packages('rsvg')
  #remotes::install_github('coolbutuseless/ggsvg')
  packagesList <- c("quitte","ggplot2","geomtextpath","ggpattern","tidyr","grid","stringr","gridExtra","ggrepel","kableExtra","dplyr","remind2","rsvg","ggsvg","plotly")
  packages <- suppressWarnings(suppressMessages(lapply(packagesList, function(x){ if(!require(x, character.only = T, quietly = T)){ install.packages(x); return(paste0("installed missing package: ", x)) } else paste0("required package is installed: ", x) } )))

```

<!-- Preprocess: prepare and load the data for use in the charts and markdown -->

```{r preprocess, echo=FALSE, include = FALSE}

#Options
forceUpdateData = FALSE
loadHist = TRUE

# data and output folders
folders <- file.info(list.files(path="./data", full.names = T))
dataFolder <- folders %>% tibble::rownames_to_column(var = "path") %>% arrange(desc(path)) %>% slice(1) %>% pull(path)

source("./R/preprocess.R")

#create output folders
outFolder <- paste0("./output/",gsub("./data/","",dataFolder))
jsOutputFolder <- paste0(outFolder, "/report_sensitivityExplorer/charts")
dir.create(jsOutputFolder, recursive = TRUE, showWarnings = FALSE)

```

<!-- Function to convert plotly charts to js file  -->

```{r loadAuxFunction, echo=FALSE, include = FALSE}

source("./R/plotly2js.R")

```

<!-- Initializing charts object -->
```{r chart_initialization, echo=FALSE, include = FALSE}

g <- NULL

```

---

# Carbon price

```{r chart_carbonPrice, echo=FALSE, include = FALSE}

  vars <- c(
    "Carbon price" = "Price|Carbon"
  )

  plotData <- df_beforeFilter %>%
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"),
           value = 1.17*value) %>%
    mutate(value = round(value,2))

  ETS_price <- addHist$ETS_price %>%
    mutate(scenario = "ETS price")

  cc <- c("reference"="#ae0000", "EED 2018 Eff"="#db4646", "FitFor55 eff"="#0090ab", "RePowerEU eff"="#095786")
  tmp <- plotData %>% mutate(color = cc[efficiency])   
  scenarioColor <- setNames(tmp$color,tmp$scenario)

  ff <- c("BioLim4"="#fedc97", "BioLim7.5"="#b5b682", "BioLim12"="#7c9885", "BioLim20"="#28666e")
  tmp <- plotData %>% mutate(color = cc[bioLim])   
  scenarioFill <- setNames(tmp$color,tmp$scenario)

  g[["Carbon Price"]][["ggplot"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth = 0.5, aes(linetype=tgt2030, color = scenario)) +
    geom_point(size = 3, aes(shape = lim, fill = scenario)) +
    geom_line(data=ETS_price,aes(x=Date, y=Price),size=0.5, color = "#000000") +
    scale_x_date(date_labels = "%Y") +
    scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) + 
    scale_color_manual(values = scenarioColor, guide = guide_legend(nrow =4, byrow = T, order = 2, override.aes = list(linewidth = 1.5))) + 
    scale_fill_manual(values = scenarioFill, guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) +
    scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) +
    theme_doubleColumn() +
    theme(strip.text.y = element_blank()) +
    #guides(fill = guide_legend(nrow = 2, byrow = T)) +
    theme(legend.text=element_text(size=theme.single.text.size)) +
    theme(legend.key.height = unit(0.7, "cm"),
          legend.key.width = unit(2,"cm")) +
    theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical") + 
    #theme(legend.key.width = unit(2,"cm")) +
    #ylab("€/t CO2") +
    theme(legend.spacing.y = unit(0.5, "lines")) + 
    theme(legend.position = "none")

  g[["Carbon Price"]][["plotly"]] <- ggplotly(g[["Carbon Price"]][["ggplot"]]) %>% layout(autosize = TRUE)

  #save plotly js
  plotly2js(
    g[["Carbon Price"]][["plotly"]],
    div.id = "carbonPrice", output.html = TRUE, output.file = "carbonPrice.js", 
    output.dir = jsOutputFolder, output.url = paste0(jsOutputFolder, "/carbonPrice.html"))

```

```{r, echo=FALSE, fig.width=8, fig.height=6}

  g[["Carbon Price"]][["plotly"]]

```

---

# Emissions

```{r chart_emissions, echo=FALSE, include = FALSE}

  h <- refEmi %>% filter(variable == "Emissions with LULUCF and with international transport", region == "EU27", pollutant == "All greenhouse gases - (CO2 equivalent)") %>% ungroup() %>% select(region,variable,period,value) %>%
    mutate(scenario = "historical") %>%
    mutate(value = round(value,2))

  plotData <- df_beforeFilter %>% 
    filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`emiIntTrnsp`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr") %>%
    calc_addVariable( "`emiIntraEU`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr") %>%
    filter(variable %in% c("emiIntTrnsp","emiIntraEU")) %>%
    pivot_wider(names_from = variable, values_from = value) %>%
    mutate(ref_emiIntTrnsp = tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference),
           ref_emiIntraEU = tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)) %>%
    mutate(red_emiIntTrnsp = emiIntTrnsp/ref_emiIntTrnsp,
           red_emiIntraEU = emiIntraEU/ref_emiIntraEU) %>%
    mutate(value = emiIntTrnsp,
           reduction = ifelse(period >= 2045, red_emiIntTrnsp, red_emiIntraEU)) %>%
    mutate(text = paste0("Emissions: ", round(value), " Mt CO2/yr", "\nReduction: ", round(1-reduction,3)*100, "%", "\nPeriod: ", period, "\nScenario: ", scenario, "\nTarget 2030: ", tgt2030, "%", "\nEfficiency: ", efficiency, "\nBiomass Limit: ", bioLim, "\nSensititivy limit: ", lim)) %>%
    mutate(value = round(value,2))

  g[["Emissions"]][["ggplot"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(size = 0.5, aes(linetype=tgt2030, color = scenario, text = text)) +
    geom_point(size = 3, aes(shape = lim, fill = scenario, text = text)) +
    geom_line(data=h,size=0.5, color = "#000000") +
    scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) +   scale_color_manual(values = scenarioColor, guide = guide_legend(nrow =4, byrow = T, order = 2, override.aes = list(linewidth = 1.5))) + 
    scale_fill_manual(values = scenarioFill, guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) +
    scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) +
    theme_doubleColumn() +
    theme(strip.text.y = element_blank()) +
    #guides(fill = guide_legend(nrow = 2, byrow = T)) +
    theme(legend.text=element_text(size=theme.single.text.size)) +
    theme(legend.key.height = unit(0.7, "cm"),
          legend.key.width = unit(2,"cm")) +
    theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical") + 
    #theme(legend.key.width = unit(2,"cm")) +
    theme(legend.spacing.y = unit(0.5, "lines")) + 
    theme(legend.position = "none") +
    scale_x_continuous(breaks = seq(1990,2060,10))

  g[["Emissions"]][["plotly"]] <- ggplotly(g[["Emissions"]][["ggplot"]],tooltip = c("text")) %>% layout(autosize = TRUE)

  plotly2js(
    g[["Emissions"]][["plotly"]],
    div.id = "emissions", output.html = TRUE, output.file = "emissions.js", 
    output.dir = jsOutputFolder, output.url = paste0(jsOutputFolder, "/emissions.html"))

```

```{r, echo=FALSE, fig.width=8, fig.height=6}

  g[["Emissions"]][["plotly"]]

```

---

# Final Energy

```{r chart_finalEnergy, echo=FALSE, include = FALSE}

  plotData <- df_beforeFilter %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable == "FE") %>%
    mutate(value = round(value,2))

  h <- hist %>% filter(model == "IEA", region == "EU27", variable == "FE", period >= 2005) %>% drop_na(value) %>% filter(value != 0) %>%
    mutate(value = round(value,2))

  g[["finalEnergy"]][["ggplot"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(size = 0.5, aes(linetype=tgt2030, color = scenario)) +
    geom_point(size = 3, aes(shape = lim, fill = scenario)) +
    geom_line(data=h,size=0.5, color = "#000000") +
    scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) + 
    scale_color_manual(values = scenarioColor, guide = guide_legend(nrow =4, byrow = T, order = 2, override.aes = list(linewidth = 1.5))) + 
    scale_fill_manual(values = scenarioFill, guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) +
    scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) +
    theme_doubleColumn() +
    theme(strip.text.y = element_blank()) +
    #guides(fill = guide_legend(nrow = 2, byrow = T)) +
    theme(legend.text=element_text(size=theme.single.text.size)) +
    theme(legend.key.height = unit(0.7, "cm"),
          legend.key.width = unit(2,"cm")) +
    theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical") + 
    #theme(legend.key.width = unit(2,"cm")) +
    theme(legend.spacing.y = unit(0.5, "lines")) + 
    theme(legend.position = "none") +
    scale_x_continuous(breaks = seq(1990,2060,10))

  g[["finalEnergy"]][["plotly"]] <- ggplotly(g[["finalEnergy"]][["ggplot"]]) %>% layout(autosize = TRUE)

  plotly2js(
    g[["finalEnergy"]][["plotly"]],
    div.id = "finalEnergy", output.html = TRUE, output.file = "finalEnergy.js", 
    output.dir = jsOutputFolder, output.url = paste0(jsOutputFolder, "/finalEnergy.html"))

```

```{r, echo=FALSE, fig.width=8, fig.height=6}

  g[["Emissions"]][["plotly"]]

```

---

# Electricity share

```{r chart_electricityShare, echo=FALSE, include = FALSE}

  vars <- c("Total" = "Final Energy|Electricity Share",
            "Transport"="Final Energy|Transport|Electricity Share",
            "Industry"="Final Energy|Industry|Electricity Share",
            "Buildings"="Final Energy|Buildings|Electricity Share")

  invertVars <- setNames(names(vars),vars)

  plotData <- df_beforeFilter %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>%
    mutate(sector = factor(invertVars[as.character(variable)], c("Total", "Transport", "Industry", "Buildings"))) %>%
    mutate(value = round(value,4))

  h_Orig <- hist[hist$model == "IEA" & hist$region == "EU27" & hist$variable %in% c("FE","FE|Electricity","FE|Transport","FE|Transport|Electricity","FE|Industry", "FE|Industry|Electricity","FE|Buildings","FE|Buildings|Electricity"),] %>%
    drop_na(value) %>%
    mutate(value = round(value,4))

  h <- rbind(
    h_Orig %>% calc_addVariable("`Final Energy|Electricity Share`" = "`FE|Electricity` / `FE`", units = "%", only.new=T),
    h_Orig %>% calc_addVariable("`Final Energy|Transport|Electricity Share`" = "`FE|Transport|Electricity` / `FE|Transport`", units = "%", only.new=T),
    h_Orig %>% calc_addVariable("`Final Energy|Industry|Electricity Share`"  = "`FE|Industry|Electricity`  / `FE|Industry`", units = "%", only.new=T),
    h_Orig %>% calc_addVariable("`Final Energy|Buildings|Electricity Share`" = "`FE|Buildings|Electricity` / `FE|Buildings`", units = "%", only.new=T)) %>%
    mutate(sector = factor(invertVars[as.character(variable)], c("Total", "Transport", "Industry", "Buildings"))) %>%
    filter(period >= 2010)

  g[["Electricity Share"]][["ggplot"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(size = 0.5, aes(linetype=tgt2030, color = scenario)) +
    geom_point(size = 1.5, aes(shape = lim, fill = scenario)) +
    geom_line(data=h,size=0.5, color = "#000000") +
    #geom_point(size = 3, aes(shape = lim, fill = scenario)) +
    facet_wrap(~ sector) +
    #geom_line(data=h %>% filter(period >= 2005),linetype="dashed", linewidth = 1, aes(color=variable)) +
    # scale_colour_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
    # scale_fill_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
    scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) + 
    scale_color_manual(values = scenarioColor) + 
    scale_fill_manual(values = scenarioFill, guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) +
    scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) +
    theme_doubleColumn() +
    scale_y_continuous(breaks = seq(0, 1, 0.2),labels = scales::percent) +
    expand_limits(y=c(0,1)) +
    theme(legend.position = "none") +
    theme(axis.title.y=element_blank())

  g[["Electricity Share"]][["plotly"]] <- ggplotly(g[["Electricity Share"]][["ggplot"]]) %>% layout(autosize = TRUE)

  plotly2js(
    g[["Electricity Share"]][["ggplot"]],
    div.id = "electricityShare", output.html = TRUE, output.file = "electricityShare.js", 
    output.dir = jsOutputFolder, output.url = paste0(jsOutputFolder, "/electricityShare.html"))

```

```{r, echo=FALSE, fig.width=8, fig.height=6}

  g[["Electricity Share"]][["plotly"]]

```

---

#Hydrogen

```{r chart_hydrogen, echo=FALSE, include = FALSE}

  vars <- c(
    "Black H2 (coal)" = "SE|Hydrogen|Coal|w/o CC",
    "Gray H2 (gas)" = "SE|Hydrogen|Gas|w/o CC",
    "Blue H2 (fossil w/ CCS)" = c("SE|Hydrogen|Coal|w/ CC", "SE|Hydrogen|Gas|w/ CC"),
    "H2 imports" = "SE|Hydrogen|Net Imports",
    #  "Bio-based H2 (gasification)" = c("SE|Hydrogen|Biomass|w/ CC","SE|Hydrogen|Biomass|w/o CC"),
    #  "Green H2 (electrolysis)" = "SE|Hydrogen|Electricity",
    "Green and bio-based H2" = c("SE|Hydrogen|Electricity", "SE|Hydrogen|Biomass|w/ CC","SE|Hydrogen|Biomass|w/o CC")
    #"VRE Storage Electrolysis" = "SE|Hydrogen|Electricity|VRE Storage Electrolysis",
    #"Standard Electrolysis" = "SE|Hydrogen|Electricity|Standard Electrolysis",
  )

  invertVars <- setNames(names(vars),vars)

  plotData <- df_beforeFilter %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>%
    mutate(type = gsub("\\d$", "", as.character(invertVars[as.character(variable)]))) %>%
    group_by(model,scenario,region,unit,period,type,tgt2030,lim) %>%
    summarize(value=sum(value),.groups = "keep") %>%
    mutate(type=factor(type, levels=unique(gsub("\\d$", "", names(vars))))) %>%
    mutate(value = round(value,2))

  g[["hydrogen"]][["ggplot"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(size = 0.5, aes(linetype=tgt2030, color = scenario)) +
    geom_point(size = 1.5, aes(shape = lim, fill = scenario)) +
    facet_wrap(~ type, nrow=2) +
    scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) + 
    scale_color_manual(values = scenarioColor) + 
    scale_fill_manual(values = scenarioFill, guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) +
    scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) +
    theme_doubleColumn() +
    theme(legend.position = "none") +
    theme(axis.title.y=element_blank())

  g[["hydrogen"]][["plotly"]] <- ggplotly(g[["hydrogen"]][["ggplot"]]) %>% layout(autosize = TRUE)

  plotly2js(
    g[["hydrogen"]][["plotly"]],
    div.id = "hydrogen", output.html = TRUE, output.file = "hydrogen.js", 
    output.dir = jsOutputFolder, output.url = paste0(jsOutputFolder, "/hydrogen.html"))

```

```{r, echo=FALSE, fig.width=8, fig.height=6}

  g[["hydrogen"]][["plotly"]]

```

---

#BECCS

```{r chart_beccs, echo=FALSE, include = FALSE}

  vars <- c(
    "BECCS" = "Emi|CO2|CDR|BECCS"
  )

  plotData <- df_beforeFilter %>%
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(value = round(value,2))

  g[["BECCS"]][["ggplot"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(size = 0.5, aes(linetype=tgt2030, color = scenario)) +
    geom_point(size = 3, aes(shape = lim, fill = scenario)) +
    #scale_x_date(date_labels = "%Y") +
    scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) + 
    scale_color_manual(values = scenarioColor) + 
    #scale_color_manual(values = c("reference"="#ae0000", "EED 2018 Eff"="#db4646", "FitFor55 eff"="#0090ab", "RePowerEU eff"="#095786"), guide = guide_legend(nrow =4, byrow = T, order = 2, override.aes = list(linewidth = 1.5))) + 
    #scale_fill_manual(values = c("BioLim4"="#fedc97", "BioLim7.5"="#b5b682", "BioLim12"="#7c9885", "BioLim20"="#28666e"), guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) +
    scale_fill_manual(values = scenarioFill, guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) +
    scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) +
    theme_doubleColumn() +
    theme(strip.text.y = element_blank()) +
    #guides(fill = guide_legend(nrow = 2, byrow = T)) +
    theme(legend.text=element_text(size=theme.single.text.size)) +
    theme(legend.key.height = unit(0.7, "cm"),
          legend.key.width = unit(2,"cm")) +
    theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical") + 
    #theme(legend.key.width = unit(2,"cm")) +
    theme(legend.spacing.y = unit(0.5, "lines")) +
    theme(legend.position = "none")

  g[["BECCS"]][["plotly"]] <- ggplotly(g[["BECCS"]][["ggplot"]]) %>% layout(autosize = TRUE)

  plotly2js(
    g[["BECCS"]][["plotly"]],
    div.id = "beccs", output.html = TRUE, output.file = "beccs.js", 
    output.dir = jsOutputFolder, output.url = paste0(jsOutputFolder, "/beccs.html"))

```

```{r, echo=FALSE, fig.width=8, fig.height=6}

  g[["BECCS"]][["plotly"]]

```

---

#DAC

```{r chart_dac, echo=FALSE, include = FALSE}

  vars <- c(
    "DAC" = "Emi|CO2|CDR|DACCS"
  )

  plotData <- df_beforeFilter %>%
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(value = round(value,2))

  g[["DAC"]][["ggplot"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(size = 0.5, aes(linetype=tgt2030, color = scenario)) +
    geom_point(size = 3, aes(shape = lim, fill = scenario)) +
    #scale_x_date(date_labels = "%Y") +
    scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) + 
    scale_color_manual(values = scenarioColor) + 
    #scale_color_manual(values = c("reference"="#ae0000", "EED 2018 Eff"="#db4646", "FitFor55 eff"="#0090ab", "RePowerEU eff"="#095786"), guide = guide_legend(nrow =4, byrow = T, order = 2, override.aes = list(linewidth = 1.5))) + 
    #scale_fill_manual(values = c("BioLim4"="#fedc97", "BioLim7.5"="#b5b682", "BioLim12"="#7c9885", "BioLim20"="#28666e"), guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) +
    scale_fill_manual(values = scenarioFill, guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) +
    scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) +
    theme_doubleColumn() +
    theme(strip.text.y = element_blank()) +
    #guides(fill = guide_legend(nrow = 2, byrow = T)) +
    theme(legend.text=element_text(size=theme.single.text.size)) +
    theme(legend.key.height = unit(0.7, "cm"),
          legend.key.width = unit(2,"cm")) +
    theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical") + 
    #theme(legend.key.width = unit(2,"cm")) +
    theme(legend.spacing.y = unit(0.5, "lines")) +
    theme(legend.position = "none")

  g[["DAC"]][["plotly"]] <- ggplotly(g[["DAC"]][["ggplot"]]) %>% layout(autosize = TRUE)

  plotly2js(
    g[["DAC"]][["plotly"]],
    div.id = "dac", output.html = TRUE, output.file = "dac.js", 
    output.dir = jsOutputFolder, output.url = paste0(jsOutputFolder, "/dac.html"))

```

```{r, echo=FALSE, fig.width=8, fig.height=6}

  g[["DAC"]][["plotly"]]

```

---

#Emissions per sector

```{r chart_sectorEmi, echo=FALSE, include = FALSE}

  vars <- c(
    "Industrial Processes" = "Emi|GHG|Industrial Processes",
    "Industry" = "Emi|GHG|Gross|Energy|Demand|Industry",
    "Buildings" ="Emi|GHG|Energy|Demand|Buildings",
    "Transportation" ="Emi|GHG|Energy|Demand|Transport",
    "Bunkers" = "Emi|CO2|Energy|Demand|Transport|International Bunkers",
    "Heat"="Emi|CO2|Gross|Energy|Supply|Heat",
    "Other Energy Conversion" = "Emi|CO2|Gross|Other Energy Conversion",
    "Electricity"="Emi|GHG|Gross|Energy|Supply|Electricity"
  )

  invertVars <- setNames(names(vars),vars)

  plotData <- df_beforeFilter %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(sector = factor(invertVars[as.character(variable)], names(vars))) %>%
    mutate(value = round(value,2))

  g[["sectorEmi"]][["ggplot"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(size = 0.5, aes(linetype=tgt2030, color = scenario)) +
    geom_point(size = 1.5, aes(shape = lim, fill = scenario)) +
    #geom_point(size = 3, aes(shape = lim, fill = scenario)) +
    facet_wrap(~ sector, nrow=2) +
    #geom_line(data=h %>% filter(period >= 2005),linetype="dashed", linewidth = 1, aes(color=variable)) +
    # scale_colour_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
    # scale_fill_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
    scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) + 
    scale_color_manual(values = scenarioColor) + 
    scale_fill_manual(values = scenarioFill, guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) +
    scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) +
    theme_doubleColumn() +
    theme(legend.position = "none") +
    theme(axis.title.y=element_blank())

  g[["sectorEmi"]][["plotly"]] <- ggplotly(g[["sectorEmi"]][["ggplot"]]) %>% layout(autosize = TRUE)

  plotly2js(
    g[["sectorEmi"]][["plotly"]],
    div.id = "sectorEmi", output.html = TRUE, output.file = "sectorEmi.js", 
    output.dir = jsOutputFolder, output.url = paste0(jsOutputFolder, "/sectorEmi.html"))

```

```{r, echo=FALSE, fig.width=8, fig.height=6}

  g[["sectorEmi"]][["plotly"]]

```

---

# Primary Energy

```{r chart_primaryEnergy, echo=FALSE, include = FALSE}

  vars <- c("Oil"="PE|Oil",
            "Gas"="PE|Gas",
            "Coal"="PE|Coal",
            "Biomass" = "PE|Biomass")

  invertVars <- setNames(names(vars),vars)

  plotData <- df_beforeFilter %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(pe = factor(invertVars[as.character(variable)], names(vars))) %>%
    mutate(value = round(value,2))

  h <- hist %>% filter(model == "IEA", region == "EU27", variable %in% vars, period >= 2005, period <= 2020) %>% drop_na(value) %>% filter(value != 0) %>%
    mutate(pe = factor(invertVars[as.character(variable)], names(vars))) %>%
    mutate(value = round(value,2))

  g[["primaryEnergy"]][["ggplot"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(size = 0.5, aes(linetype=tgt2030, color = scenario)) +
    geom_point(size = 1.5, aes(shape = lim, fill = scenario)) +
    geom_line(data=h,size=0.5, color = "#000000") +
    #geom_point(size = 3, aes(shape = lim, fill = scenario)) +
    facet_wrap(~ pe, nrow=2) +
    #geom_line(data=h %>% filter(period >= 2005),linetype="dashed", linewidth = 1, aes(color=variable)) +
    # scale_colour_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
    # scale_fill_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
    scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) + 
    scale_color_manual(values = scenarioColor) + 
    scale_fill_manual(values = scenarioFill, guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) +
    scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) +
    theme_doubleColumn() +
    theme(legend.position = "none") +
    theme(axis.title.y=element_blank())

  g[["primaryEnergy"]][["plotly"]] <- ggplotly(g[["primaryEnergy"]][["ggplot"]]) %>% layout(autosize = TRUE)

  plotly2js(
    g[["primaryEnergy"]][["plotly"]],
    div.id = "primaryEnergy", output.html = TRUE, output.file = "primaryEnergy.js", 
    output.dir = jsOutputFolder, output.url = paste0(jsOutputFolder, "/primaryEnergy.html"))

```

```{r, echo=FALSE, fig.width=8, fig.height=6}

  g[["primaryEnergy"]][["plotly"]]

```

---

# Electricity Generation

```{r chart_generation, echo=FALSE, include = FALSE}

  vars <- c(
    #"Net Imports" = "SE|Electricity|Net Imports",
    "Coal" = "SE|Electricity|Coal",
    #"Coal w/ CC" = "SE|Electricity|Coal|w/ CC",
    #"Coal w/o CC" = "SE|Electricity|Coal|w/o CC",
    #"Oil" = "SE|Electricity|Oil",
    "Gas w/ CC" = "SE|Electricity|Gas|w/ CC",
    "Gas w/o CC" = "SE|Electricity|Gas|w/o CC",
    "Hydrogen" = "SE|Electricity|Hydrogen",
    "Nuclear" = "SE|Electricity|Nuclear",
    #"Geothermal" = "SE|Electricity|Geothermal",
    #"Hydro" = "SE|Electricity|Hydro",
    "Biomass" = "SE|Electricity|Biomass",
    #"Biomass w/ CC" = "SE|Electricity|Biomass|w/ CC",
    #"Biomass w/o CC" = "SE|Electricity|Biomass|w/o CC",
    "Solar" = "SE|Electricity|Solar",
    #"Solar CSP" = "SE|Electricity|Solar|CSP",
    #"Solar PV" = "SE|Electricity|Solar|PV",
    "Wind" = "SE|Electricity|Wind"
    #"Wind Onshore" = "SE|Electricity|Wind|Onshore",
    #"Wind Offshore" = "SE|Electricity|Wind|Offshore"
  )

  invertVars <- setNames(names(vars),vars)

  plotData <- df_beforeFilter %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(seel = factor(invertVars[as.character(variable)], names(vars))) %>%
    mutate(value = round(value * 1/0.0036))

  g[["generation"]][["ggplot"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(size = 0.5, aes(linetype=tgt2030, color = scenario)) +
    geom_point(size = 1.5, aes(shape = lim, fill = scenario)) +
    #geom_point(size = 3, aes(shape = lim, fill = scenario)) +
    facet_wrap(~ seel, nrow=2) +
    #geom_line(data=h %>% filter(period >= 2005),linetype="dashed", linewidth = 1, aes(color=variable)) +
    # scale_colour_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
    # scale_fill_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
    scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) + 
    scale_color_manual(values = scenarioColor) + 
    scale_fill_manual(values = scenarioFill, guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) +
    scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) +
    theme_doubleColumn() +
    theme(legend.position = "none") +
    theme(axis.title.y=element_blank())

  g[["generation"]][["plotly"]] <- ggplotly(g[["generation"]][["ggplot"]]) %>% layout(autosize = TRUE)

  plotly2js(
    ggplotly(ggplotly(g[["generation"]][["plotly"]])) %>% layout(autosize = TRUE),
    div.id = "generation", output.html = TRUE, output.file = "generation.js", 
    output.dir = jsOutputFolder, output.url = paste0(jsOutputFolder, "/generation.html"))

```

```{r, echo=FALSE, fig.width=8, fig.height=6}

  g[["generation"]][["plotly"]]

```

<!-- # # Final Energy -->
<!-- # vars <- c( -->
<!-- #   "Electricity" = "FE|Electricity", -->
<!-- #   "Heat" = "FE|Heat", -->
<!-- #   "Hydrogen" = "FE|Hydrogen", -->
<!-- #   "Gases" = "FE|Gases", -->
<!-- #   #"Gases" = "FE|Gases|Biomass", -->
<!-- #   #"Gases" = "FE|Gases|Hydrogen", -->
<!-- #   #"Gases" = "FE|Gases|Fossil", -->
<!-- #   "Liquids" = "FE|Liquids", -->
<!-- #   #"Liquids" = "FE|Liquids|Biomass", -->
<!-- #   #"Liquids" = "FE|Liquids|Hydrogen", -->
<!-- #   #"Liquids" = "FE|Liquids|Fossil", -->
<!-- #   "Solids" = "FE|Solids"	 -->
<!-- #   #"Solids" = "FE|Solids|Biomass",	 -->
<!-- #   #"Solids" = "FE|Solids|Fossil"	 -->
<!-- # ) -->
<!-- #  -->
<!-- # invertVars <- setNames(names(vars),vars) -->
<!-- #  -->
<!-- # plotData <- df_beforeFilter %>%  -->
<!-- #   filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable %in% vars) %>% -->
<!-- #   mutate(fe = factor(invertVars[as.character(variable)], names(vars))) -->
<!-- #  -->
<!-- # g[["finalEnergy"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) + -->
<!-- #     geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) + -->
<!-- #     geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") + -->
<!-- #     geom_line(size = 0.5, aes(linetype=tgt2030, color = scenario)) + -->
<!-- #     facet_wrap(~ fe, nrow=2) + -->
<!-- #     scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) +  -->
<!-- #     scale_color_manual(values = scenarioColor) +  -->
<!-- #     scale_fill_manual(values = scenarioFill, guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) + -->
<!-- #     scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) + -->
<!-- #     theme_doubleColumn() + -->
<!-- #     theme(legend.position = "none") + -->
<!-- #     theme(axis.title.y=element_blank())  -->
<!-- #  -->
<!-- # plotly2js( -->
<!-- #   ggplotly(ggplotly(g[["finalEnergy"]])) %>% layout(autosize = TRUE), -->
<!-- #              div.id = "finalEnergy", output.html = TRUE, output.file = "finalEnergy.js",  -->
<!-- #              output.dir = jsOutputFolder, output.url = paste0(jsOutputFolder, "/finalEnergy.html")) -->

### 2024-08-30 R/aesthetics.R

@@ -210,38 +210,47 @@ theme_singleColumn <- function(){
       #axis.text = element_text(size = 1.25*theme.single.text.size),
       #axis.text.x = element_text(size = theme.single.text.size, angle = 90, hjust = 1, vjust = 0.5),
       #axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 10)),
-      legend.key.height = unit(1, "cm"),
-      legend.key.width = unit(1,"cm"),
+      legend.key.height = unit(0.7, "cm"),
+      legend.key.width = unit(0.7,"cm"),
+      legend.spacing.y = unit(0.1, 'cm')
       #panel.spacing = unit(3, "lines"),
       #plot.title = element_text(size = 0.75*theme.single.text.size, face = "plain"),
       #strip.text.x = element_text(size = 1.25*theme.single.text.size)
     )
 }
 
-theme.double.text.size = 15
-geom.text.double.size = theme.double.text.size/.pt
+#theme.double.text.size = 15
+#geom.text.double.size = theme.double.text.size/.pt
+#defaultText_doubleColumn <- theme_minimal(base_size = 25)[["text"]] 
 
-defaultText_doubleColumn <- theme_minimal(base_size = 25)[["text"]] 
+textSize.double = 15
+geomText.size = textSize.double/.pt
 
 theme_doubleColumn <- function(){
-  theme_minimal(base_size = 25) +
+  theme_minimal(base_size = textSize.double) +
     theme(
+      plot.title = element_text(size=15),
       legend.position="bottom",
       legend.title = element_blank(),
       axis.title.x=element_blank(),
       axis.ticks.x=element_blank(),
+      #axis.text.x = element_text(size = 15,angle = 90, hjust = 1, vjust = 0.5),
       axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
+      axis.title.y=element_blank(),
+      #axis.text.y = element_text(size = 15),
       #axis.text = element_text(size = theme.double.text.size),
       #legend.text=element_text(size= theme.double.text.size),
       #axis.text.x = element_text(size = 0.8*theme.double.text.size, angle = 90, hjust = 1, vjust = 0.5),
       #axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 10)),
-      legend.key.height = unit(1, "cm"),
-      legend.key.width = unit(1,"cm"),
[…]

### 2024-08-30 R/calcResults.R

@@ -1,0 +1,1314 @@
+
+
+# Emission Reductions
+
+reductions2040 <- rbind(
+  df %>% 
+    filter(variable == "Emi|GHG|with LULUCF and with international transport", region == "EU27", period == 2040, tgt2050 != "Npi") %>% 
+    mutate(value = 1-(value / tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)))
+  ,
+  df %>% 
+    filter(variable == "Emi|GHG|without LULUCF and with international transport", region == "EU27", period == 2040, tgt2050 != "Npi") %>% 
+    mutate(value = 1-(value / tgt %>% filter(target == "Emissions without LULUCF and with international transport") %>% pull(reference)))
+  ,
+  df %>% 
+    filter(variable == "Emi|GHG|with LULUCF and with intra-EU aviation", region == "EU27", period == 2040, tgt2050 != "Npi") %>% 
+    mutate(value = 1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)))
+  ,
+  df %>% 
+    filter(variable == "Emi|GHG|without LULUCF and with intra-EU aviation", region == "EU27", period == 2040, tgt2050 != "Npi") %>% 
+    mutate(value = 1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)))
+  ,
+  df %>% 
+    filter(variable == "Emi|GHG|Gross|without LULUCF and with international transport", region == "EU27", period == 2040, tgt2050 != "Npi") %>% 
+    mutate(value = 1-(value / tgt %>% filter(target == "Gross Emissions without LULUCF and with international transport") %>% pull(reference)))
+)
+
+reductions2040 %>% 
+  filter(tgt2030 %in% tgt2030Scen) %>% 
+  group_by(variable) %>%
+  summarize(minTarget = min(value), maxTarget=max(value),.groups = "keep") %>%
+  mutate(minTarget = paste0(round(minTarget*100), "%"),
+         maxTarget = paste0(round(maxTarget*100), "%"),
+         period = 2040) %>% 
+  rename(TargetReference = variable) %>%
+  relocate(period, .after=TargetReference) %>%
+  kbl() %>%
[…]

### 2024-08-30 R/harmonizeData.R

@@ -49,6 +49,55 @@ harmonizeData <- function(data,scaleFactor){ #,nzero=NULL
               data %>% filter(region == "EU27")  %>% calc_addVariable("`Trade|Imports|Gas|Adj`" = "`PE|Gas` - `Prod|PE|Gas` + `Trade|Exports|Gas|Adj`", units = "EJ/yr", only.new=T)
   )
   
+  # Harmonizing fossil useful energy with JRC-IDEES values (to exclude additional mappings from REMIND)
+  IDEES2020 <- data.frame(variable=c("UE|Buildings|Heating|Gases", "UE|Buildings|Heating|Liquids"),idees=c(3.48,0.994)) # average 2018-2022 UE
+  
+  # Share of liquids and gases UE that is reduced to harmonize values to JRC-IDEES numbers
+  harmonizingShare <-  left_join(
+    data %>% 
+      filter(region == "EU27", period == 2020, scenario == data$scenario[1], variable %in% c("UE|Buildings|Heating|Gases", "UE|Buildings|Heating|Liquids","UE|Buildings|Heating|Electricity|Heat pump")),
+    IDEES2020,
+    by = join_by(variable == variable)
+  ) %>%
+    mutate(share = ifelse(is.na(idees),1,idees/value),
+           diff = ifelse(is.na(idees),0,idees - value)) %>%
+    select(variable,share,diff)
+  
+  # assume that electricity heat pumps would be the natural substitute for the liquids and gases UE reduction that is not doen directly by them. 
+  harmonizingCompensation <- left_join(
+    data %>% 
+      filter(region == "EU27", variable %in% c("UE|Buildings|Heating|Gases", "UE|Buildings|Heating|Liquids")),
+    harmonizingShare,
+    by = join_by(variable == variable)
+  ) %>% 
+    mutate(remaining = diff + value * (1-share)) %>%
+    group_by(scenario,period) %>%
+    summarize(remaining = sum(remaining)) %>%
+    mutate(variable = "UE|Buildings|Heating|Electricity|Heat pump")
+  
+  # harmonized useful energy data
+  harmonizedData <- left_join(
+    left_join(
+      data %>% 
+        filter(region == "EU27", period >= 2020, variable %in% c("UE|Buildings|Heating|Gases", "UE|Buildings|Heating|Liquids", "UE|Buildings|Heating|Electricity|Heat pump")),
+      harmonizingShare,
+      by = join_by(variable == variable)) %>% 
[…]

### 2024-08-30 R/loadData.R

@@ -2,13 +2,13 @@
 
 # commands to modify input data
 modifyData <- function(data){
-  
+
   # #removing edge-t duplicates
   # data <- data[!data$variable %in% c("ES|Transport|Freight", "ES|Transport|Pass", "FE|Transport", "FE|Transport|Electricity", "FE|Transport|Gases", "FE|Transport|Hydrogen", "FE|Transport|Liquids", "FE|Transport|Freight", "FE|Transport|Freight|Electricity", "FE|Transport|Freight|Gases", "FE|Transport|Freight|Hydrogen", "FE|Transport|Freight|Liquids", "FE|Transport|Pass", "FE|Transport|Pass|Electricity", "FE|Transport|Pass|Gases", "FE|Transport|Pass|Hydrogen", "FE|Transport|Pass|Liquids", "FE|Transport|w/o Bunkers", "FE|Transport|w/o Bunkers|Electricity", "FE|Transport|w/o Bunkers|Gases", "FE|Transport|w/o Bunkers|Hydrogen", "FE|Transport|w/o Bunkers|Liquids", "ES|Transport|Road", "ES|Transport|Road", "ES|Transport|Pass", "ES|Transport|Freight", "FE|Transport|Pass", "FE|Transport|Freight", "FE|Transport", "FE|Transport|w/o bunkers", "FE|Transport|Pass|Liquids", "FE|Transport|Pass|Hydrogen", "FE|Transport|Pass|Gases", "FE|Transport|Pass|Electricity", "FE|Transport|Freight|Liquids", "FE|Transport|Freight|Hydrogen", "FE|Transport|Freight|Gases", "FE|Transport|Freight|Electricity", "FE|Transport|Liquids", "FE|Transport|Hydrogen", "FE|Transport|Gases", "FE|Transport|Electricity", "FE|Transport|w/o bunkers|Liquids", "FE|Transport|w/o bunkers|Hydrogen", "FE|Transport|w/o bunkers|Gases", "FE|Transport|w/o bunkers|Electricity"),]
-  
+
   #remove pluses
-  data <- remind2::deletePlus(data)
-  
+  #data <- remind2::deletePlus(data)
+
   #remove number at the beginning of the scenario name
   data$scenario <- gsub("^\\d\\d\\_*","",data$scenario)
   #remove "0b" at the beginning of the scenario name
@@ -16,215 +16,191 @@ modifyData <- function(data){
[…]

### 2024-08-30 R/loadHistoricalData.R

@@ -1,0 +1,64 @@
+
+loadAdditionalHistoricalData <- function(path){
+  if(! file.exists(paste0(path,"/addHist.rds"))){
+    # additional historical data
+    addHist <- list()
+    #renewables shares historical data - eurostat
+    #https://ec.europa.eu/eurostat/web/energy/database > Sustainable Development indicators Goal 7 - Affordable and clean energy > Share of renewable energy in gross final energy consumption by sector
+    #https://ec.europa.eu/eurostat/cache/metadata/en/sdg_07_40_esmsip2.htm
+    addHist$res <- read.csv2("./hist/renewablesShares.csv", stringsAsFactors = FALSE,check.names=FALSE) %>%
+      pivot_longer(-type,names_to = "period", values_to = "value") %>%
+      mutate(period = as.numeric(period),
+             value = as.numeric(value))
+
+    addHist$ETS_price <- read.csv("./hist/Carbon Emissions Futures Historical Data.csv") %>% #downloaded from https://www.investing.com/commodities/carbon-emissions-historical-data
+      mutate(Date = as.Date(Date,format="%m/%d/%Y"),
+             Price = as.numeric(Price),
+             variable = "ETS price")
+
+    #https://ec.europa.eu/eurostat/databrowser/view/NRG_BAL_C__custom_6123838/default/table?lang=en
+    #Dataset: 	Complete energy balances [NRG_BAL_C__custom_6124583]
+    #Energy balance		Final energy consumption (Europe 2020-2030)
+    #Standard international energy product classification (SIEC)		Total
+    #Unit of measure		Terajoule
+    addHist$FE_consumption <- data.frame(period = c(1990:2022),
+                                         value  = c(39872769.14, 39884283.38, 38793652.46, 38838315.81, 38591654.06, 39373233.31, 41059096.04, 40692888.88, 40922960.92, 40820057.93,
+                                                    41024326.68, 41987629.93, 41709757.85, 42962908.94, 43386870.54, 43595062.82, 43787162.83, 43061606.56, 43404792.31, 41065315.12,
+                                                    42923730.71, 41251193.45, 41164990.35, 41074138.59, 39320940.69, 40136464.77, 40931954.98, 41443151.18, 41545190.01, 41299901.69,
[…]

### 2024-08-30 R/preprocess.R

@@ -1,0 +1,26 @@
+
+
+# preprocess: prepare and load the data for use in the charts and markdown
+
+# load data
+source("./R/loadData.R")
+
+# load historical data
+if(loadHist){
+  source("./R/loadHistoricalData.R")
+}
+
+#loading reference emissions -->
+source("./R/loadReferenceEmissions.R")
+#correctedTgt #to be used in the scenario config to adjust the targets according the historical harmonization based on 2020 NPi run values
+#scaleFactor
+
+#harmonizing data (scale emissions to match historical values)
+source("./R/harmonizeData.R")
+df_beforeFilter <- df
+df <- df %>%
+  filter(!grepl("limVRE", scenario)) # filter VRE scenario out of main charts
+
+#loading efficiency targets
+source("./R/efficiencyTarget.R")
+

### 2024-08-30 createReports.R

@@ -1,0 +1,32 @@
+
+library(rmarkdown)
+library(dplyr)
+
+#Check latest results folder and create output folder for reports
+folders <- file.info(list.files(path="./data", full.names = T))
+dataFolder <- folders %>% tibble::rownames_to_column(var = "path") %>% arrange(desc(path)) %>% slice(1) %>% pull(path)
+outFolder <- paste0("./output/",gsub("./data/","",dataFolder))
+dir.create(outFolder, recursive = TRUE, showWarnings = FALSE)
+
+# Create paper charts in EJ
+rmarkdown::render("./report_paperCharts.Rmd", output_file = paste0(outFolder, "/report_paperCharts-EJ.html"), params = list(forceUpdateData = FALSE, loadHist = TRUE, energyInMtoe = FALSE, chartsFolder = "report_paperCharts_EJ"))
+
+# Create paper charts in Mtoe and MtH2
+rmarkdown::render("./report_paperCharts.Rmd", output_file = paste0(outFolder, "/report_paperCharts-Mtoe_and_MtH2.html"), params = list(forceUpdateData = FALSE, loadHist = TRUE, energyInMtoe = TRUE, chartsFolder = "report_paperCharts_Mtoe"))
+
+# Create plotly charts for the Sensitivity Iterative Explorer
+rmarkdown::render("./report_plotlyCharts.Rmd", output_file = paste0(outFolder, "/report_plotlyCharts.html"))
+# Copy html, js and css files to the Sensitivity Iterative Explorer output folder 
+file.copy(list("./publish/report_sensitivityExplorer/index.html","./publish/report_sensitivityExplorer/script.js","./publish/report_sensitivityExplorer/style.css"), paste0(outFolder, "/report_sensitivityExplorer"), overwrite = TRUE)
+
+#Create additional charts
+rmarkdown::render("./report_additionalCharts.Rmd", output_file = paste0(outFolder, "/report_additionalCharts.html"))
+
+# Publish the latest paper results
+dir.create("./publish/report_paperCharts", recursive = TRUE, showWarnings = FALSE)
+file.copy(paste0(outFolder, "/report_paperCharts-Mtoe_and_MtH2.html"), "./publish/paper_results/index.html", overwrite = TRUE)
+
+# Publish the latest sensitivity iterative explorer results
[…]

### 2024-09-05 report_paperCharts.Rmd
small changes

@@
   theme(legend.position = "none") +
-  labs(title = paste0("(b) Fossil energy carriers net imports (", unique(plotData$unit), ")")) #+ 
+  labs(title = paste0("(b) Fossil energy carriers’ net imports (", unique(plotData$unit), ")")) #+ 
   #theme(plot.title = element_text(hjust = -0.4))
@@
 
+violin_scale <- 3 
+violin_color = "#bbbbbb"
+violin_boxPlotWidth <- 1.5
+
 #Emissions Reduction
@@
 
+g[["milestone - violin"]][["Emissions reductions"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
+  geom_violin(fill="#bbbbbb", scale = violin_scale) + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=1, colour="black", alpha=0.9, linewidth=0.5) +
+  geom_boxplot(outlier.shape = NA, width=1.5) +
+  geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 0.55, label = "FitFor55", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = reduction_h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,1)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=0.8*geomText.size)
+
 # Final Energy Demand - Energy savings
@@
 
+g[["milestone - violin"]][["Energy savings"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mtoe/yr)")), aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
+  geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 750, label = "REPowerEU", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  annotate("text", x = Inf, y = 787, label = "FitFor55", angle=90, vjust = 1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  geom_hline(yintercept=h %>% filter(period==2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = h %>% filter(period==2022) %>% pull(value), label = "2022", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,400,1000)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  #annotate("text", x = -Inf, y = -Inf, label = "(Mtoe/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+
 # Electricity Demand
@@
   geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,5000)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  #annotate("text", x = -Inf, y = -Inf, label = "(TWh)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+
+g[["milestone - violin"]][["Electricity Demand"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (TWh)")), aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
@@
 
+g[["milestone - violin"]][["Renewables Share"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
+  geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,1)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+
 # Wind
@@
 
+g[["milestone - violin"]][["Wind capacity"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (GW)")), aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
+  geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 255, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,1000)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  #annotate("text", x = -Inf, y = -Inf, label = "(GW)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
 # Solar photovoltaics
@@
 
+g[["milestone - violin"]][["Solar photovoltaics"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (GW)")), aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
+  geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 600, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 208.9, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,2500)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  #annotate("text", x = -Inf, y = -Inf, label = "(GW)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
 # Carbon Capture and Storage 
@@
 
+g[["milestone - violin"]][["Carbon Capture and Storage"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
+  geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 50, label = "Net-Zero\nIndustry Act", angle=90, vjust = 0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,400)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
+  theme(strip.clip = "off")#+
+  #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+
 # Novel CDR = atmospheric/biogenic CO2 (CDR) 
@@
 
+g[["milestone - violin"]][["Novel CDR"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,400)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
 # Direct Electrification
@@
 
+g[["milestone - violin"]][["Direct Electrification"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
+  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,1)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=geomText.size, size = 0.8*geomText.size)
 # Carbon-free electricity share
@@
 
+g[["milestone - violin"]][["Carbon-free electricity share"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
+  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,1)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=geomText.size, size = 0.8*geomText.size)
 # Residual Fossil Emissions
@@
 
+g[["milestone - violin"]][["Residual Fossil Emissions"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,2500)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+
 # Domestic Hydrogen Production
@@
   geom_boxplot(outlier.shape = NA, width=6) +
+  geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = -Inf, y = 10, label = "REPowerEU\ndomestic", angle=90, vjust = 0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  facet_grid(.~target, scales="free") +
+  theme_doubleColumn() +
+  coord_flip(clip = 'off') +
+  theme(axis.title.y=element_blank()) +
+  theme(strip.text.y = element_blank()) +
+  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+  expand_limits(y=c(0,20)) + 
+  theme(panel.spacing = unit(4, "lines")) +
+  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+  theme(strip.placement = "outside") +
+  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  #annotate("text", x = -Inf, y = -Inf, label = "(Mtoe/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+
+g[["milestone - violin"]][["Domestic Hydrogen Production"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mtoe/yr)")), aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
   geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
@@
 
-ggsave(paste0(outChartsFolder,"/svg/Figure 5. Milestones Panel.svg"), g[["milestone - hor targets"]] , device="svg", width = 12, height = 14, dpi=100, units = "in")
-ggsave(paste0(outChartsFolder,"/png/Figure 5. Milestones Panel.png"), g[["milestone - hor targets"]] , device="png", width = 12, height = 14, dpi=300, units = "in")
+g[["milestone - violin targets"]] <- gridExtra::arrangeGrob(
+  g[["milestone - violin"]][["Emissions reductions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Energy savings"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Renewables Share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Direct Electrification"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Domestic Hydrogen Production"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+
+  g[["milestone - violin"]][["Electricity Demand"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Wind capacity"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Solar photovoltaics"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+
+  g[["milestone - violin"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Novel CDR"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+
+  ncol = 2
+)
+
+ggsave(paste0(outChartsFolder,"/svg/Figure 5. Milestones Panel.svg"), g[["milestone - violin targets"]] , device="svg", width = 12, height = 14, dpi=100, units = "in")
+ggsave(paste0(outChartsFolder,"/png/Figure 5. Milestones Panel.png"), g[["milestone - violin targets"]] , device="png", width = 12, height = 14, dpi=300, units = "in")
 

### 2024-09-05 calcHarmonizedTargets.R

@@ -30,3 +30,5 @@ source("./R/loadReferenceEmissions.R")
 #to be used in the scenario config to adjust the targets according the historical harmonization based on 2020 NPi run values
 correctedTgt 
 
+#scaleFactor
+

### 2025-04-10 report_additionalCharts.Rmd
release candidate - revision 1

@@
 dir.create(paste0(outChartsFolder, "/svg"), recursive = TRUE, showWarnings = FALSE)
+
+```
+
+<!-- Initializing charts object -->
+```{r chart_initialization, echo=FALSE, include = FALSE}
+
+#loading theme and colors
+source("./R/aesthetics.R")
+
+g <- NULL
+
+```
+
+# Emission reduction {.tabset}
+
+## Gross
+
+<!-- (c) Breakdown of residual CO2 emissions from energy and industrial processes (% in relation to 2020) -->
+
+```{r, echo=FALSE}
+
+vars <- list(
+  "Industrial\nProcesses" = "Emi|GHG|Industrial Processes",
+  "Industry" = "Emi|GHG|Gross|Energy|Demand|Industry",
+  "Buildings" ="Emi|GHG|Energy|Demand|Buildings",
+  "Transportation" ="Emi|GHG|Energy|Demand|Transport",
+  "Bunkers" = "Emi|CO2|Energy|Demand|Transport|International Bunkers",
+#  "CDR" = "Emi|GHG|Gross|Energy|Demand|CDR",
+#  "AFOFI" = "Emissions|CO2|Energy|Demand|AFOFI",
+#  "Other Sector" ="Emissions|CO2|Energy|Demand|Other Sector",
+  "Heat"="Emi|CO2|Gross|Energy|Supply|Heat",
+  "Other Energy\nConversion" = "Emi|CO2|Gross|Other Energy Conversion",
+    #"Hydrogen" ="Emi|CO2|Gross|Energy|Supply|Hydrogen",
+    #"Liquids"="Emi|CO2|Gross|Energy|Supply|Liquids",
+    #"Gases"="Emi|CO2|Gross|Energy|Supply|Gases",
+    #"Solids"="Emi|CO2|Gross|Energy|Supply|Solids",
+#  "Other"="Emissions|CO2|Energy|Supply|Other",
+  "Electricity"="Emi|GHG|Gross|Energy|Supply|Electricity"
+)
+# "Emi|GHG|Agriculture",
+#   "Emi|GHG|Land-Use Change",
+#   "Emi|GHG|Waste",
+#   "Emi|CO2|CDR|BECCS",
+#   "Emi|CO2|CDR|Industry CCS|Synthetic Fuels",
+#   "Emi|CO2|CDR|DACCS",
+#   "Emi|CO2|CDR|EW"
+
+plotColor <- c(
+  "Electricity"= "#ffb200",
+  "Heat"= "#cc0000",
+  "Other Energy\nConversion" = "#0000cc",
+  #"Gases"= "#999959",
+  #"Liquids"= "#0000cc",
+  #"Solids"= "#0c0c0c",
+  #"Other" = "#79a6d2",
+  #"Hydrogen" = "#5ed5b0",
+  "Transportation" = "#a1dd70",
+  "Bunkers" = "#ffc0cb",
+  "Buildings" = "#5edfff",
+  "Other Sector" = "#999959",
+  "AFOFI" = "#005900",
+  "Industry" = "#5f6769",
+  "Industrial\nProcesses" = "#5c5c5c",
+  "Other" = "#5b0d8f",
+  "Waste" = "#A52A2A",
+  "AFOLU" = "#4DAF4A",
+  "Agriculture" = "#357933",
+  "LULUCF" = "#6ec16b"
+)
+
+labels <- setNames(names(vars),vars[names(vars)])
+
+fulldata <- df %>%
+  filter(region == "EU27",
+         period %in% c(2020,2030,2040),
+         tgt2030 %in% tgt2030Scen,
+         variable %in% unlist(vars)) %>%
+  mutate(labels = factor(labels[as.character(variable)],levels = names(vars)),
+         variable = factor(variable, levels = vars)) %>%
+  group_by(period,variable) %>%
+  mutate(min = min(value),
+         max = max(value))
+
+plotData <- fulldata %>%
+  filter(scenario == mainScen) %>%
+  mutate(complement = FALSE) %>%
+  group_by(variable) %>%
+  mutate(pct = paste0(round(value / value[period==2020],2)*100, "%")) %>%
+  bind_rows(
+    fulldata %>%
+      filter(scenario == mainScen) %>%
+      mutate(complement = TRUE) %>%
+      group_by(variable) %>%
+      mutate(value = value[period==2020] - value) %>%
+      mutate(labels=NA)
+  ) %>%
+  mutate(ext_Var = ifelse(complement, paste0(as.character(variable),"_"), as.character(variable))) %>%
+  arrange(period,ext_Var) %>%
+  group_by(period) %>%
+  arrange(variable) %>%
+  mutate(ymid = as.numeric(sub("\\D+", "", period)),
+         ymax = ymid + 4, ymin = ymid - 4,
+         xmin = c(0, head(cumsum(value), -1)),
+         xmax = cumsum(value),
+         xmid = (xmax + xmin) / 2,
+         ) %>%
+  ungroup() %>%
+  filter(complement == FALSE)
+
+g[["2040 Emissions - Energy and Industrial Processes - Gross"]] <- plotData %>% 
+  ggplot(aes(xmid, ymid, fill = ext_Var)) +
+  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax,
+                alpha = factor(period), color = variable)) +
+  geom_errorbar(data=plotData %>% filter(period == 2040), aes(xmin=xmax-value+min, xmax=xmax-value+max), width=4, colour="black", alpha=0.9, linewidth=0.8) +
+  geom_text(data=plotData %>% filter(period == 2020), aes(y = 2015, label = labels, group = labels, hjust=1, angle = 90), vjust=0.5, hjust=1.1, na.rm=TRUE, size = geomText.size, angle = 90, lineheight = 0.8) +
+  geom_text(data=plotData %>% filter(period == 2040), aes(x=xmid , y = 2045, label = pct), vjust=0.5, hjust=-0.1, na.rm=TRUE, size = geomText.size, angle = 90) +
+  scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) + 
+  scale_alpha_manual(values = c(0.2, 0.3, 1)) +
+  scale_color_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) +
+  theme_doubleColumn() +
+  theme(legend.position = "none") +
+  scale_y_continuous(breaks=c(2020,2030,2040), labels=c("current",2030,2040), minor_breaks = NULL, limits=c(2008,2047)) +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.title.y=element_blank()) +
+  scale_x_continuous(breaks = NULL) +
+  coord_cartesian(clip="off") +
+  theme(plot.margin = margin(t = 30, r = 0, b = 100, l = 0, unit = "pt")) +
+  labs(title = "(c) Sectoral breakdown of residual gross CO2 emissions from energy and industrial processes (% of average 2018-2022)") + 
+  theme(plot.title = element_text(margin=margin(t=0,r=0,b=35,l=-200), hjust=1))
+
+# ggsave(paste0(outChartsFolder,"/svg/Figure 1.
+Emission results panel - (c) Energy and Industrial Processes.svg"), g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] , device="svg", width = 12, height = 3.2, dpi=100, units = "in")
+# ggsave(paste0(outChartsFolder,"/png/Figure 1.
+Emission results panel - (c) Energy and Industrial Processes.png"), g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] , device="png", width = 12, height = 3.2, dpi=300, units = "in")
 
@@
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
-
-```
-
-<!-- Initializing charts object -->
-```{r chart_initialization, echo=FALSE, include = FALSE}
-
-#loading theme and colors
-source("./R/aesthetics.R")
-
-g <- NULL
 
@@
 <!-- ``` -->
+
+# Power sector Emissions
+
+```{r, echo=FALSE, include=FALSE}
+
+baseSize <- 24
+
+theme_white <- function(){
+  theme_minimal(base_size = baseSize) +
+    theme(
+      legend.position="bottom",
+      legend.title = element_blank(),
+      axis.title.x=element_blank(),
+      axis.ticks.x=element_blank(),
+      axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
+      #axis.text = element_text(size = theme.double.text.size),
+      #legend.text=element_text(size= theme.double.text.size),
+      #axis.text.x = element_text(size = 0.8*theme.double.text.size, angle = 90, hjust = 1, vjust = 0.5),
+      #axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 10)),
+      legend.key.height = unit(1, "cm"),
+      legend.key.width = unit(1,"cm"),
+      panel.background = element_rect(fill="#FFFFFF", color = NA),
+      plot.background = element_rect(fill="#FFFFFF", color = NA),
+      #panel.spacing = unit(1, "lines"),
+      #plot.title = element_text(size = theme.double.text.size, face = "plain"),
+      #strip.text.x = element_text(size = theme.double.text.size)
+    )
+}
+
+histEmber <- data.frame(period=seq(2000,2023,1),value=c(1079, 1084, 1122, 1166, 1157, 1156, 1170, 1188, 1128, 1039, 1048, 1054, 1033, 980, 917, 948, 934, 942, 879, 769, 660, 722, 750, 596))
+
+mainScen <- "Nzero_57_bio7p5"
+
+plotData <- df_beforeFilter %>%
+  filter(region == "EU27", period %in% c(2010:2050), variable == "Emi|CO2|Energy|Supply|Electricity w/ couple prod", scenario != "Npi") %>%
+  group_by(period) %>%
+  summarise_at(vars(value), list(
+    Min = min,
+    Mean = mean,
+    Median = median,
+    Max = max,
+    Sd = sd,
+    Q1=~quantile(., probs = 0.25),
+    Q3=~quantile(., probs = 0.75)))
+
+plotData2 <- df_beforeFilter %>%
+  filter(region == "EU27", period %in% c(2010:2050), variable == "Emi|CO2|Energy|Supply|Electricity w/ couple prod", scenario != "Npi") %>%
+  filter(scenario == mainScen)
+
+g[["power_sector_emissions"]] <- ggplot(plotData,aes(x=period,y=Median)) +
+    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
+    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
+    #geom_line(linewidth=1,color="black") +
+    geom_line(data = histEmber,aes(x=period,y=value), linewidth=1,color="black",linetype="dashed") +
+    geom_line(data = plotData2,aes(x=period,y=value), linewidth=1,color="black") +
+    geom_ribbon(aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") +
+    geom_ribbon(aes(ymax = Max, ymin = Min), alpha = 0.5, fill = "#545454") +
+    #geom_line(aes(y=Min),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) +
+    #geom_line(aes(y=Max),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) +
+    #geom_line(data=h,linewidth=1,aes(linetype=Source)) +
+    #geom_point() +
+    theme_white() +
+    ylab(expression(paste("Mt ", CO[2],"/yr")))
+
+ggsave(paste0(outChartsFolder,"/svg/power_sector_emissions.svg"), g[["power_sector_emissions"]], device="svg", width = 12, height = 8, dpi=100, units = "in")
+ggsave(paste0(outChartsFolder,"/png/power_sector_emissions.png"), g[["power_sector_emissions"]], device="png", width = 12, height = 8, dpi=300, units = "in")
+
+plotData <- df %>%
+  filter(region == "EU27", period %in% c(2010:2050), variable == "Emi|CO2|Energy|Supply|Electricity w/ couple prod", scenario != "Npi") %>%
+  group_by(period) %>%
+  summarise_at(vars(value), list(
+    Min = min,
+    Mean = mean,
+    Median = median,
+    Max = max,
+    Sd = sd,
+    Q1=~quantile(., probs = 0.25),
+    Q3=~quantile(., probs = 0.75)))
+
+plotData2 <- df %>%
+  filter(region == "EU27", period %in% c(2010:2050), variable == "Emi|CO2|Energy|Supply|Electricity w/ couple prod", scenario != "Npi") %>%
+  filter(scenario == mainScen)
+
+g[["power_sector_emissions_noLimVRE"]] <- ggplot(plotData,aes(x=period,y=Median)) +
+    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
+    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
+    #geom_line(linewidth=1,color="black") +
+    geom_line(data = histEmber,aes(x=period,y=value), linewidth=1,color="black",linetype="dashed") +
+    geom_line(data = plotData2,aes(x=period,y=value), linewidth=1,color="black") +
+    geom_ribbon(aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") +
+    geom_ribbon(aes(ymax = Max, ymin = Min), alpha = 0.5, fill = "#545454") +
+    #geom_line(aes(y=Min),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) +
+    #geom_line(aes(y=Max),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) +
+    #geom_line(data=h,linewidth=1,aes(linetype=Source)) +
+    #geom_point() +
+    theme_white() +
+    ylab(expression(paste("Mt ", CO[2],"/yr")))
+
+ggsave(paste0(outChartsFolder,"/svg/power_sector_emissions_noLimVRE.svg"), g[["power_sector_emissions_noLimVRE"]], device="svg", width = 12, height = 8, dpi=100, units = "in")
+ggsave(paste0(outChartsFolder,"/png/power_sector_emissions_noLimVRE.png"), g[["power_sector_emissions_noLimVRE"]], device="png", width = 12, height = 8, dpi=300, units = "in")
+
+```

### 2025-04-10 report_paperCharts.Rmd
release candidate - revision 1

--- 2024-08-30 report_paperCharts.Rmd
@@
 plotData <- df %>% 
-  filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen) %>% 
+  filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen) %>% 
   calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T)  %>%
@@
     geom_label_repel(data=data.frame(period=c(2042.5),value=mean(linearProjection %>% filter(period %in% c(2040,2045)) %>% pull(value))),
-                     label = "linear reduction",
-                     nudge_x = 10,
-                     nudge_y = 800,
+                     label = "linear\nreduction",
+                     nudge_x = 0,
+                     nudge_y = 2500,
                      segment.square = TRUE,
-                     point.padding = 0.6,
-                     hjust = 0,
+                     point.padding = 0,
+                     hjust = 0.5,
                      direction="y",
@@
     scale_y_continuous(breaks = c(0,1000,2000,3000,4000,5000)) +
-    scale_x_continuous(breaks = seq(1990,2060,10)) +
+    scale_x_continuous(breaks = seq(1990,2050,10)) +
     labs(title = expression(paste("(a) Total GHG emissions (Mt ", CO[2],"eq/yr)"))) + 
     #theme(plot.title = element_text(hjust = -0.2)) +
-    theme(plot.title = element_text(margin=margin(b=20)))
+    theme(plot.title = element_text(margin=margin(b=35)))
 
@@
          range=max-min,
-         label= ifelse(round((1-max) * 100) == round((1-min) * 100), paste0(round((1-max) * 100), "%"), paste0(round((1-max) * 100), "% to ", round((1-min) * 100) ,"%")))
+         labelRange = ifelse(round((1-max) * 100) == round((1-min) * 100), paste0(round((1-max) * 100), "%"), paste0(round((1-max) * 100), "% to ", round((1-min) * 100) ,"%")))
+
+mainScenRedDF <- plotData %>%
+  filter(scenario == mainScen, period %in% c(2030, 2035, 2040, 2045)) %>%
+  ungroup() %>%
+  select(period,reduction)
+mainScenRed <- setNames(paste0(round((1-mainScenRedDF$reduction) * 100), "%"), as.character(mainScenRedDF$period))
+
+plotData <- plotData %>%
+  mutate(label = ifelse(period %in% c(2030, 2035, 2040, 2045), paste0(as.character(mainScenRed[as.character(period)]), "\n(", labelRange, ")"), labelRange))
 
@@
   geom_segment(data=plotData %>% filter(scenario == mainScen), aes(x=x, y=y, xend=xend, yend=yend), arrow = arrow(length=unit(.5, 'cm')), na.rm=TRUE) +
-  geom_text(data=plotData %>% filter(scenario == mainScen), aes(label = label, y=labelY, x=labelX, color=factor(period)), vjust=-1, hjust=0.5, na.rm=TRUE, size = geomText.size, angle = 90) +
+  geom_text(data=plotData %>% filter(scenario == mainScen), aes(label = label, y=labelY, x=labelX, color=factor(period)), vjust=-0.2, hjust=0.5, na.rm=TRUE, size = geomText.size * 0.8, angle = 90) +
   scale_color_manual(values = c("2030" = "black", "2035" = "#777777","2040" = "black", "2045" = "#777777","2050" = "black"), breaks=c("2030", "2035","2040", "2045","2050")) +
@@
   labs(title = "(b) Emission reductions (%)") + 
-  theme(plot.title = element_text(margin=margin(b=20)))
+  theme(plot.title = element_text(margin=margin(b=35)))
 
@@
   g[["target"]], # + theme(plot.margin=margin(10,10,10,10)),
-  layout_matrix = rbind(c(1, 1, 1, 1, 2, 2),
-                        c(1, 1, 1, 1, 2, 2))
+  layout_matrix = rbind(c(1, 1, 1, 1, 2, 2, 2),
+                        c(1, 1, 1, 1, 2, 2, 2))
    )
@@
 #  ggsave(paste0(outChartsFolder,"/png/Figure 1. Emission results panel - (a) GHG and (b) reduction.png"), g[["GHG Emission reductions"]] , device="png", width = 12, height = 5, dpi=300, units = "in")
+
+#conclusion
+# df %>% 
+#     filter(region == "EU27", period %in% c(2040), tgt2030 %in% tgt2030Scen) %>%
+#     calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%
+#     mutate(reduction = round(value / tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference) ,2)) %>% 
+#     select(-variable) %>%
+#     filter(tgt2050 != "Npi") %>%
+#     mutate(x=ifelse(reduction>=0,period+1,NA),
+#            xend=ifelse(reduction>=0,period+1,NA),
+#            y=ifelse(reduction>=0,1,NA),
+#            yend=ifelse(reduction>=0,ifelse(reduction<=0,0,reduction),NA),
+#            bar = ifelse(period==2040,"2040","emi"),
+#            #label = ifelse(value>0,paste0( "- ", (1-value) * 100, "% (-", (1-intraEURed) * 100 ,"%)"),NA),
+#            labelY = reduction + (1-reduction)/2,
+#            labelX=period+1) %>%
+#     group_by(model,region,period) %>% 
+#     mutate(max=max(reduction),
+#            min=min(reduction),
+#            range=max-min,
+#            labelRange = ifelse(round((1-max) * 100) == round((1-min) * 100), paste0(round((1-max) * 100), "%"), paste0(round((1-max) * 100), "% to ", round((1-min) * 100) ,"%"))) %>%
+#   filter(scenario == mainScen, period == 2040) %>% pull(labelRange)
 
@@
   mutate(labels = factor(labels[as.character(variable)],levels = names(vars)),
-         variable = factor(variable, levels = vars)) %>%
+         variable = factor(variable, levels = vars),
+         type = "gross") %>%
   group_by(period,variable) %>%
@@
   theme(plot.margin = margin(t = 30, r = 0, b = 100, l = 0, unit = "pt")) +
-  labs(title = "(c) Sectoral breakdown of residual gross CO2 emissions from energy and industrial processes (% of average 2018-2022)") + 
-  theme(plot.title = element_text(margin=margin(t=0,r=0,b=35,l=-200), hjust=1))
-
-# ggsave(paste0(outChartsFolder,"/svg/Figure 1.
-Emission results panel - (c) Energy and Industrial Processes.svg"), g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] , device="svg", width = 12, height = 3.2, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Figure 1.
-Emission results panel - (c) Energy and Industrial Processes.png"), g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] , device="png", width = 12, height = 3.2, dpi=300, units = "in")
+  #labs(title = "(c) Sectoral breakdown of residual gross CO2 emissions from energy and industrial processes (% of average 2018-2022)") + 
+  #theme(plot.title = element_text(margin=margin(t=0,r=0,b=45,l=-200), hjust=1))
+  labs(title = "(c) Sectoral breakdown of net CO2 emissions from energy and industrial processes (%)") + 
+  theme(plot.title = element_text(margin=margin(t=0,r=0,b=45,l=0), hjust=1))
 
@@
 
-g[["Figure 1"]] <- gridExtra::arrangeGrob(
+g[["Figure 1 - gross"]] <- gridExtra::arrangeGrob(
   g[["GHG emi"]],
@@
                         c(1, 1, 1, 1, 2, 2),
+                        c(1, 1, 1, 1, 2, 2),
+                        c(3, 3, 3, 3, 3, 3),
                         c(3, 3, 3, 3, 3, 3),
@@
 
-ggsave(paste0(outChartsFolder,"/png/Figure 1. Emission results panel.png"), g[["Figure 1"]], device="png", width = 12, height = 8, dpi=300, units = "in")
-ggsave(paste0(outChartsFolder,"/svg/Figure 1. Emission results panel.svg"), g[["Figure 1"]], device="svg", width = 12, height = 8, dpi=100, units = "in")
-
-```
-
-```{r, echo=FALSE, fig.width=12, fig.height=8}
+ggsave(paste0(outChartsFolder,"/png/Figure 1. Emission results panel (gross).png"), g[["Figure 1 - gross"]], device="png", width = 12, height = 8, dpi=300, units = "in")
+ggsave(paste0(outChartsFolder,"/svg/Figure 1. Emission results panel (gross).svg"), g[["Figure 1 - gross"]], device="svg", width = 12, height = 8, dpi=100, units = "in")
+
+```
+
+```{r, echo=FALSE, fig.width=12, fig.height=10}
+
+#grid.newpage()
+#grid.draw(g[["Figure 1 - gross"]])
+
+```
+
+<!-- Figure 1.
+Greenhouse gas emission reductions for scenarios reaching climate neutrality by 2050.
+Central values are given for the reference scenario (57% reduction by 2030, reference final energy projections, biomass availability limited to 7.5 EJ/yr and default CCS assumption), ranges for the full scenario ensemble.
+-->
+
+<!-- (c) Breakdown of residual net CO2 emissions from energy and industrial processes (% in relation to 2020) -->
+
+```{r chart_figure1c_gross, echo=FALSE}
+
+vars <- list(
+  "Industrial\nProcesses" = "Emi|GHG|Industrial Processes",
+  "Industry" = "Emi|GHG|Gross|Energy|Demand|Industry",
+  "Buildings" ="Emi|GHG|Energy|Demand|Buildings",
+  "Transportation" ="Emi|GHG|Energy|Demand|Transport",
+  "Bunkers" = "Emi|CO2|Energy|Demand|Transport|International Bunkers",
+#  "CDR" = "Emi|GHG|Gross|Energy|Demand|CDR",
+#  "AFOFI" = "Emissions|CO2|Energy|Demand|AFOFI",
+#  "Other Sector" ="Emissions|CO2|Energy|Demand|Other Sector",
+  "Heat"="Emi|CO2|Gross|Energy|Supply|Heat",
+  "Other Energy\nConversion" = "Emi|CO2|Gross|Other Energy Conversion",
+    #"Hydrogen" ="Emi|CO2|Gross|Energy|Supply|Hydrogen",
+    #"Liquids"="Emi|CO2|Gross|Energy|Supply|Liquids",
+    #"Gases"="Emi|CO2|Gross|Energy|Supply|Gases",
+    #"Solids"="Emi|CO2|Gross|Energy|Supply|Solids",
+#  "Other"="Emissions|CO2|Energy|Supply|Other",
+  "Electricity"="Emi|GHG|Gross|Energy|Supply|Electricity"
+)
+# "Emi|GHG|Agriculture",
+#   "Emi|GHG|Land-Use Change",
+#   "Emi|GHG|Waste",
+#   "Emi|CO2|CDR|BECCS",
+#   "Emi|CO2|CDR|Industry CCS|Synthetic Fuels",
+#   "Emi|CO2|CDR|DACCS",
+#   "Emi|CO2|CDR|EW"
+
+plotColor <- c(
+  "Electricity"= "#ffb200",
+  "Heat"= "#cc0000",
+  "Other Energy\nConversion" = "#0000cc",
+  #"Gases"= "#999959",
+  #"Liquids"= "#0000cc",
+  #"Solids"= "#0c0c0c",
+  #"Other" = "#79a6d2",
+  #"Hydrogen" = "#5ed5b0",
+  "Transportation" = "#a1dd70",
+  "Bunkers" = "#ffc0cb",
+  "Buildings" = "#5edfff",
+  "Other Sector" = "#999959",
+  "AFOFI" = "#005900",
+  "Industry" = "#5f6769",
+  "Industrial\nProcesses" = "#5c5c5c",
+  "Other" = "#5b0d8f",
+  "Waste" = "#A52A2A",
+  "AFOLU" = "#4DAF4A",
+  "Agriculture" = "#357933",
+  "LULUCF" = "#6ec16b"
+)
+
+labels <- setNames(names(vars),vars[names(vars)])
+
+grossData <- df %>%
+  filter(region == "EU27",
+         period %in% c(2020,2030,2040),
+         tgt2030 %in% tgt2030Scen,
+         variable %in% unlist(vars)) %>%
+  mutate(labels = factor(labels[as.character(variable)],levels = names(vars)),
+         variable = factor(variable, levels = vars)) %>%
+  group_by(period,variable) %>%
+  mutate(min = min(value),
+         max = max(value)) %>%
+  ungroup()
+
+if(!("Carbon Management|Storage|Pe2Se|Other" %in% unique(df$variable))){
+  df <- rbind(df,df %>% calc_addVariable("`Carbon Management|Storage|Pe2Se|Other`" = "`Carbon Management|Storage|Biomass|Pe2Se|Gases w/ couple prod` + `Carbon Management|Storage|Biomass|Pe2Se|Hydrogen w/ couple prod` + `Carbon Management|Storage|Biomass|Pe2Se|Liquids w/ couple prod` + `Carbon Management|Storage|Fossil|Pe2Se|Gases w/ couple prod` + `Carbon Management|Storage|Fossil|Pe2Se|Hydrogen w/ couple prod` + `Carbon Management|Storage|Fossil|Pe2Se|Liquids w/ couple prod`", units = "Mt CO2/yr", only.new=T))
+  df <- rbind(df,df %>% calc_addVariable("`Carbon Management|Storage|Pe2Se|Electricity`" = "`Carbon Management|Storage|Biomass|Pe2Se|Electricity w/ couple prod` + `Carbon Management|Storage|Fossil|Pe2Se|Electricity w/ couple prod`", units = "Mt CO2/yr", only.new=T))
+
+  df <- rbind(df,df %>% calc_addVariable("`Carbon Management|Storage|Industry Extended`" = "`Carbon Management|Storage|Industry Energy` + `Carbon Management|Storage|Waste|Plastics Incineration`", units = "Mt CO2/yr", only.new=T))
+}
+
+varsCC <- list(
+  "Industrial\nProcesses" = "Carbon Management|Storage|Industry Process",
+  "Industry" = "Carbon Management|Storage|Industry Extended",
+  "Other Energy\nConversion" = "Carbon Management|Storage|Pe2Se|Other",
+  "Electricity" = "Carbon Management|Storage|Pe2Se|Electricity"
+)
+
+labelsCC <- setNames(names(varsCC),varsCC[names(varsCC)])
+
+# allCCVars <- c(
+#   "Carbon Management|Storage",
+#     "Carbon Management|Storage|+|Biomass|Pe2Se", 
+#       "Carbon Management|Storage|Biomass|Pe2Se|+|Electricity w/ couple prod",
+#       "Carbon Management|Storage|Biomass|Pe2Se|+|Gases w/ couple prod",
+#       "Carbon Management|Storage|Biomass|Pe2Se|+|Hydrogen w/ couple prod",
+#       "Carbon Management|Storage|Biomass|Pe2Se|+|Liquids w/ couple prod",
+#     "Carbon Management|Storage|+|Fossil|Pe2Se",
+#       "Carbon Management|Storage|Fossil|Pe2Se|+|Electricity w/ couple prod",
+#       "Carbon Management|Storage|Fossil|Pe2Se|+|Gases w/ couple prod",
+#       "Carbon Management|Storage|Fossil|Pe2Se|+|Hydrogen w/ couple prod",
+#       "Carbon Management|Storage|Fossil|Pe2Se|+|Liquids w/ couple prod",
+#     "Carbon Management|Storage|+|Industry Energy",
+#     "Carbon Management|Storage|+|Industry Process",
+#     "Carbon Management|Storage|+|CDR energy",
+#     "Carbon Management|Storage|+|DAC",
+#     "Carbon Management|Storage|+|OAE calcination",
+#     "Carbon Management|Storage|+|Waste|Plastics Incineration"
+#   )
+# 
+# View(df %>%
+#        filter(region == "EU27",
+#               period %in% c(2020,2030,2040),
+#               tgt2030 %in% tgt2030Scen,
+#               variable %in% allCCVars) %>%
+#   filter(scenario == mainScen)
+#   )
+
+CCData <- df %>%
+  filter(region == "EU27",
+         period %in% c(2020,2030,2040),
+         tgt2030 %in% tgt2030Scen,
+         variable %in% unlist(varsCC)) %>%
+  mutate(CCData = -as.numeric(value),
+         labels = factor(labelsCC[as.character(variable)],levels = names(vars)),
+         #variable = factor(variable, levels = varsCC)
+         ) %>%
+  select(-value)
+
+#View(CCData %>% filter(scenario == mainScen))
+
+fulldata <- left_join(
+  grossData,
+  CCData %>%
+    select(-variable, -unit),
+  by = join_by(model == model, scenario == scenario, region == region, period == period, tgt2050 == tgt2050, tgt2030 == tgt2030, efficiency == efficiency, bioLim == bioLim, lim == lim, labels == labels)
+  ) %>%
+  mutate(CCData = replace_na(CCData, 0),
+         net = value + CCData)
+
+plotData <- fulldata %>%
+  filter(scenario == mainScen) %>%
+  mutate(complement = FALSE) %>%
+  group_by(variable) %>%
+  mutate(pct = paste0(round(net / net[period==2020],2)*100, "%")) %>%
+  bind_rows(
+    fulldata %>%
+      filter(scenario == mainScen) %>%
+      mutate(complement = TRUE) %>%
+      group_by(variable) %>%
+      mutate(value = value[period==2020] - value) %>%
+      mutate(labels=NA)
+  ) %>%
+  mutate(ext_Var = ifelse(complement, paste0(as.character(variable),"_"), as.character(variable))) %>%
+  arrange(period,ext_Var) %>%
+  group_by(period) %>%
+  arrange(variable) %>%
+  mutate(ymid = as.numeric(sub("\\D+", "", period)),
+         ymax = ymid + 4, ymin = ymid - 4,
+         xmin = c(0, head(cumsum(value), -1)),
+         xmax = cumsum(value),
+         xmid = (xmax + xmin) / 2,
+         ) %>%
+  ungroup() %>%
+  filter(complement == FALSE)
+
+g[["2040 Net Emissions - Energy and Industrial Processes - horizontal bar"]] <- plotData %>% 
+  ggplot(aes(xmid, ymid, fill = ext_Var)) +
+  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax,
+                alpha = factor(period), color = variable)) +
+
+  geom_rect_pattern(data = plotData %>% filter(CCData != 0), aes(xmin = xmax + CCData, xmax = xmax, ymin = ymin, ymax = ymax, alpha = factor(period), fill = ext_Var, color = variable, pattern_alpha = factor(period)), pattern_color = NA, pattern_fill = "white", pattern="stripe", pattern_spacing = 0.05, pattern_aspect_ratio = 1, pattern_density      = 0.2) +
+
+  geom_errorbar(data=plotData %>% filter(period == 2040), aes(xmin=xmax-value+min+CCData, xmax=xmax-value+max+CCData), width=4, colour="black", alpha=0.9, linewidth=0.8) +
+
+  geom_text(data=plotData %>% filter(period == 2020), aes(y = 2015, label = labels, group = labels, hjust=1, angle = 90), vjust=0.5, hjust=1.1, na.rm=TRUE, size = geomText.size * 0.8, angle = 90, lineheight = 0.8) +
+  geom_text(data=plotData %>% filter(period == 2040), aes(x=xmid , y = 2045, label = pct), vjust=0.5, hjust=-0.1, na.rm=TRUE, size = geomText.size, angle = 90) +
+  scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) + 
+  scale_alpha_manual(values = c(0.2, 0.3, 1)) +
+  scale_color_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) +
+  theme_doubleColumn() +
+  theme(legend.position = "none") +
+  scale_y_continuous(breaks=c(2020,2030,2040), labels=c("current",2030,2040), minor_breaks = NULL, limits=c(2008,2047)) +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.title.y=element_blank()) +
+  scale_x_continuous(breaks = NULL) +
+  coord_cartesian(clip="off") +
+  theme(plot.margin = margin(t = 30, r = 0, b = 100, l = 0, unit = "pt")) +
+  #labs(title = "(c) Sectoral breakdown of net CO2 emissions from energy and industrial processes (% of average 2018-2022)") + 
+  #theme(plot.title = element_text(margin=margin(t=0,r=0,b=45,l=0)))
+  labs(title = "(c) Sectoral breakdown of net CO2 emissions from energy and industrial processes (%)") + 
+  theme(plot.title = element_text(margin=margin(t=0,r=0,b=45,l=0), hjust=1))
+
+g[["2040 Net Emissions - Energy and Industrial Processes - horizontal bar - net only"]] <- plotData %>% 
+  ggplot(aes(xmid, ymid, fill = ext_Var)) +
+  geom_rect(aes(xmin = xmin, xmax = xmax+CCData, ymin = ymin, ymax = ymax,
+                alpha = factor(period), color = variable)) +
+
+  geom_errorbar(data=plotData %>% filter(period == 2040), aes(xmin=xmax-value+min+CCData, xmax=xmax-value+max+CCData), width=4, colour="black", alpha=0.9, linewidth=0.8) +
+
+  geom_text(data=plotData %>% filter(period == 2020), aes(y = 2015, label = labels, group = labels, hjust=1, angle = 90), vjust=0.5, hjust=1.1, na.rm=TRUE, size = geomText.size * 0.8, angle = 90, lineheight = 0.8) +
+  geom_text(data=plotData %>% filter(period == 2040), aes(x=xmid , y = 2045, label = pct), vjust=0.5, hjust=-0.1, na.rm=TRUE, size = geomText.size, angle = 90) +
+  scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) + 
+  scale_alpha_manual(values = c(0.2, 0.3, 1)) +
+  scale_color_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) +
+  theme_doubleColumn() +
+  theme(legend.position = "none") +
+  scale_y_continuous(breaks=c(2020,2030,2040), labels=c("current",2030,2040), minor_breaks = NULL, limits=c(2008,2047)) +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.title.y=element_blank()) +
+  scale_x_continuous(breaks = NULL) +
+  coord_cartesian(clip="off") +
+  theme(plot.margin = margin(t = 30, r = 0, b = 100, l = 0, unit = "pt")) +
+  labs(title = "(c) Sectoral breakdown of net CO2 emissions from energy and industrial processes (%)") + 
+  theme(plot.title = element_text(margin=margin(t=0,r=0,b=45,l=0)))
+
+```
+
+```{r, echo=FALSE, include=FALSE}
+
+g[["Figure 1 - net"]] <- gridExtra::arrangeGrob(
+  g[["GHG emi"]],
+  g[["target"]],
+  g[["2040 Net Emissions - Energy and Industrial Processes - horizontal bar"]],
+  layout_matrix = rbind(c(1, 1, 1, 1, 2, 2),
+                        c(1, 1, 1, 1, 2, 2),
+                        c(1, 1, 1, 1, 2, 2),
+                        c(1, 1, 1, 1, 2, 2),
+                        c(1, 1, 1, 1, 2, 2),
+                        c(3, 3, 3, 3, 3, 3),
+                        c(3, 3, 3, 3, 3, 3),
+                        c(3, 3, 3, 3, 3, 3),
+                        c(3, 3, 3, 3, 3, 3))
+   )
+
+ggsave(paste0(outChartsFolder,"/png/Figure 1. Emission results panel (net).png"), g[["Figure 1 - net"]], device="png", width = 12, height = 8, dpi=300, units = "in")
+ggsave(paste0(outChartsFolder,"/svg/Figure 1. Emission results panel (net).svg"), g[["Figure 1 - net"]], device="svg", width = 12, height = 8, dpi=100, units = "in")
+
+```
+
+```{r, echo=FALSE, fig.width=12, fig.height=10}
+
+#grid.newpage()
+#grid.draw(g[["Figure 1 - net"]])
+
+```
+
+<!-- Figure 1.
+Greenhouse gas emission reductions for scenarios reaching climate neutrality by 2050.
+Central values are given for the reference scenario (57% reduction by 2030, reference final energy projections, biomass availability limited to 7.5 EJ/yr and default CCS assumption), ranges for the full scenario ensemble.
+Pattern in net emissions represents carbon captured in the energy sector.
+-->
+
+```{r, echo=FALSE, include=FALSE}
+
+g[["Figure 1 - net only"]] <- gridExtra::arrangeGrob(
+  g[["GHG emi"]],
+  g[["target"]],
+  g[["2040 Net Emissions - Energy and Industrial Processes - horizontal bar - net only"]],
+  layout_matrix = rbind(c(1, 1, 1, 1, 2, 2),
+                        c(1, 1, 1, 1, 2, 2),
+                        c(1, 1, 1, 1, 2, 2),
+                        c(1, 1, 1, 1, 2, 2),
+                        c(1, 1, 1, 1, 2, 2),
+                        c(3, 3, 3, 3, 3, 3),
+                        c(3, 3, 3, 3, 3, 3),
+                        c(3, 3, 3, 3, 3, 3),
+                        c(3, 3, 3, 3, 3, 3))
+   )
+
+ggsave(paste0(outChartsFolder,"/png/Figure 1. Emission results panel (net only).png"), g[["Figure 1 - net only"]], device="png", width = 12, height = 8, dpi=300, units = "in")
+ggsave(paste0(outChartsFolder,"/svg/Figure 1. Emission results panel (net only).svg"), g[["Figure 1 - net only"]], device="svg", width = 12, height = 8, dpi=100, units = "in")
+
+```
+
+```{r, echo=FALSE, fig.width=12, fig.height=10}
 
 grid.newpage()
-grid.draw(g[["Figure 1"]])
+grid.draw(g[["Figure 1 - net only"]])
 
@@
 plotData <- df %>% 
-  filter(region == "EU27", period >= 2020, period <= 2060, scenario  == mainScen, variable %in% unlist(vars)) %>% 
+  filter(region == "EU27", period >= 2020, period <= 2050, scenario  == mainScen, variable %in% unlist(vars)) %>% 
   mutate(variable = factor(variable, levels=vars)) %>% 
@@
 
+label <- c(
+
+)
+
+plotData2040 <- plotData2040 %>%
+  mutate(label = paste0(round(percentage,2)*100,"%")) %>%
+  mutate(label = ifelse(inv_vars[variable] == "Solar PV", paste0(label, " - Solar\n            PV"), 
+                        ifelse(inv_vars[variable] == "Wind Onshore", paste0(label, " - Wind\n    Onshore"), 
+                               ifelse(inv_vars[variable] == "Wind Offshore", paste0(label, " - Wind\n   Offshore"), 
+                                      label))))
+
 g[["Electricity Generation"]] <- 
@@
   geom_bar(data=plotData2040,aes(fill=variable),stat='identity', show.legend = FALSE, alpha = 0.7, color="white", width = 3, linewidth = 1.5) +
-  geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geomText.size) +
+  geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = label, y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geomText.size*0.8) +
+  #geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geomText.size) +
   theme_doubleColumn()  +
   scale_y_continuous(minor_breaks = seq(0.2, 0.8, 0.2), breaks=c(0,1),labels = scales::percent) +
-  scale_x_continuous(breaks=c(2020,2040,2060)) +
+  scale_x_continuous(breaks=c(2020,2040,2050)) +
   scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
-  guides(fill=guide_legend(ncol=3,override.aes = list(alpha=1))) + #, byrow = TRUE
+  guides(fill=guide_legend(ncol=2,override.aes = list(alpha=1))) + #, byrow = TRUE
   annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, label = "renewables\nand nuclear", color = "#666666",angle = 90, hjust=0.5, vjust=-0.5, size=geomText.size, lineheight = 0.8) +
@@
 #   scale_y_continuous(minor_breaks = seq(0.2, 0.8, 0.2), breaks=c(0,1),labels = scales::percent) +
-#   scale_x_continuous(breaks=c(2020,2040,2060)) +
+#   scale_x_continuous(breaks=c(2020,2040,2050)) +
 #   scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
@@
 plotData <- df %>% 
-  filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable == "Cap|Electricity|Solar|PV") %>% 
+  filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable == "Cap|Electricity|Solar|PV") %>% 
   filter(tgt2050 != "Npi") %>% 
@@
                   segment.square = TRUE,
-                  point.padding = 0.6,
-                  nudge_x = 5,
+                  point.padding = 0.1,
+                  nudge_x = c(4,1.5),
                   #nudge_y = -0.02,
@@
                   hjust = 0,
-                  direction="y", size = geomText.size, xlim = c(2020, 2070)) +
+                  direction="y", size = geomText.size * 0.8, xlim = c(2020, 2070)) +
   geom_label_repel(data=plotData %>% filter(scenario == mainScen, period == 2030), aes(label = paste0(round(value),"GW")),box.padding = 0.1,
@@
                   direction="y",
-                  size = geomText.size) +
+                  size = geomText.size * 0.8) +
     theme_doubleColumn() + 
@@
 # Electricity share
-vars <- c("Total" = "Final Energy|Electricity Share",
-          "Transport"="Final Energy|Transport|Electricity Share",
-          "Industry"="Final Energy|Industry|Electricity Share",
-          "Buildings"="Final Energy|Buildings|Electricity Share")
+vars <- c("Total" = "Final Energy|w/o Bunkers|w/o Non-energy Use|Electricity Share",
+          "Transport"="Final Energy|w/o Bunkers|w/o Non-energy Use|Transport|Electricity Share",
+          "Industry"="Final Energy|w/o Bunkers|w/o Non-energy Use|Industry|Electricity Share",
+          "Buildings"="Final Energy|w/o Bunkers|w/o Non-energy Use|Buildings|Electricity Share")
 
 plotData <- df %>% 
-  filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
+  filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
   group_by(model,region,variable,period) %>% 
@@
 
-h_Orig <- hist[hist$model == "IEA" & hist$region == "EU27" & hist$variable %in% c("FE","FE|Electricity","FE|Transport","FE|Transport|Electricity","FE|Industry", "FE|Industry|Electricity","FE|Buildings","FE|Buildings|Electricity"),] %>% drop_na(value)
+h_Orig_1 <- hist[hist$model == "IEA" & hist$region == "EU27" & hist$variable %in% c("FE","FE|Electricity","FE|Transport","FE|Transport|Electricity","FE|Industry", "FE|Industry|Electricity","FE|Buildings","FE|Buildings|Electricity"),] %>% drop_na(value)
+
+h_Orig_2 <- hist[hist$model == "Eurostat" & hist$region == "EU27" & hist$variable %in% c("FE|Non-energy Use|Industry", "FE|Transport|Bunkers"),] %>% drop_na(value)
+
+h_Orig <- rbind(h_Orig_1,h_Orig_2) %>% select(-model)
 
 h <- rbind(
-  h_Orig %>% calc_addVariable("`Final Energy|Electricity Share`" = "`FE|Electricity` / `FE`", units = "%", only.new=T),
-  h_Orig %>% calc_addVariable("`Final Energy|Transport|Electricity Share`" = "`FE|Transport|Electricity` / `FE|Transport`", units = "%", only.new=T),
-  h_Orig %>% calc_addVariable("`Final Energy|Industry|Electricity Share`"  = "`FE|Industry|Electricity`  / `FE|Industry`", units = "%", only.new=T),
-  h_Orig %>% calc_addVariable("`Final Energy|Buildings|Electricity Share`" = "`FE|Buildings|Electricity` / `FE|Buildings`", units = "%", only.new=T))
+  h_Orig %>% calc_addVariable("`Final Energy|w/o Bunkers|w/o Non-energy Use|Electricity Share`" = "`FE|Electricity` / (`FE` - `FE|Non-energy Use|Industry` - `FE|Transport|Bunkers`)", units = "%", only.new=T),
+  h_Orig %>% calc_addVariable("`Final Energy|w/o Bunkers|w/o Non-energy Use|Transport|Electricity Share`" = "`FE|Transport|Electricity` / (`FE|Transport` - `FE|Transport|Bunkers`)", units = "%", only.new=T),
+  h_Orig %>% calc_addVariable("`Final Energy|w/o Bunkers|w/o Non-energy Use|Industry|Electricity Share`"  = "`FE|Industry|Electricity`  / (`FE|Industry` - `FE|Non-energy Use|Industry`)", units = "%", only.new=T),
+  h_Orig %>% calc_addVariable("`Final Energy|w/o Bunkers|w/o Non-energy Use|Buildings|Electricity Share`" = "`FE|Buildings|Electricity` / `FE|Buildings`", units = "%", only.new=T))
+
+#FE|Non-energy Use|Industry
+#hist[hist$model == "Eurostat" & hist$region == "EU27" & hist$variable %in% c("FE|Non-energy Use|Industry"),] %>% drop_na(value)
+#hist[hist$model == "Eurostat" & hist$region == "EU27" & hist$variable %in% c("FE|Transport|Bunkers"),] %>% drop_na(value)
 
@@
                            label = paste0(round(value*100),"%")),
-                      box.padding = 3,
+                      #box.padding = 4,
                       #segment.curvature = -0.1,
@@
                       point.padding = 0.6,
-                      nudge_x = 5,
-                      nudge_y = c(0.55,0.27,-0.05,-0.6),
-                      #force = 0.5,
+                      nudge_x = -12,
+                      nudge_y = -0.05,
+                      #nudge_y = c(0.9,0.5,-0.5,-0.5),
+                      force = 2,
                       #hjust = 0,
                       direction="y"
-                      , size = geomText.size
+                      , size = geomText.size * 0.8,
+                      #force_pull = 2,
                       #, xlim = c(2020, 2070)
                       ) +
-    scale_colour_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
-    scale_fill_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
+    scale_colour_manual(values = c("Final Energy|w/o Bunkers|w/o Non-energy Use|Electricity Share"="black","Final Energy|w/o Bunkers|w/o Non-energy Use|Transport|Electricity Share"="#a1dd70","Final Energy|w/o Bunkers|w/o Non-energy Use|Industry|Electricity Share"="#5f6769","Final Energy|w/o Bunkers|w/o Non-energy Use|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
+    scale_fill_manual(values = c("Final Energy|w/o Bunkers|w/o Non-energy Use|Electricity Share"="black","Final Energy|w/o Bunkers|w/o Non-energy Use|Transport|Electricity Share"="#a1dd70","Final Energy|w/o Bunkers|w/o Non-energy Use|Industry|Electricity Share"="#5f6769","Final Energy|w/o Bunkers|w/o Non-energy Use|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
     theme_doubleColumn() + 
@@
     guides(color=guide_legend(nrow=2)) +
-    labs(title = "(c) Electricity share in final energy (%)\n    (includes bunker fuels and non-energy use)") #+ 
+    labs(title = "(c) Electricity share in final energy (%)\nwithout bunker fuels and non-energy use") #+ 
     #theme(plot.title = element_text(hjust = -0.4))
@@
 
-```{r, echo=FALSE, fig.width=12, fig.height=8}
+```{r, echo=FALSE, fig.width=12, fig.height=10}
 
@@
 plotData <- df %>% 
-  filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
+  filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
   mutate(variable = factor(variable, levels=vars))  %>% 
@@
     labs(title = paste0("(a) Primary energy demand (", unique(plotData$unit), ")")) #+
+    #theme(plot.margin=margin(b = 1, unit='cm'))
     #theme(plot.title = element_text(hjust = -0.3))
@@
   theme(legend.position = "none") +
-  labs(title = paste0("(b) Fossil energy carriers net imports (", unique(plotData$unit), ")")) #+ 
+  labs(title = paste0("(b) Fossil energy carriers’ net imports (", unique(plotData$unit), ")")) +
+  theme(plot.title = element_text(hjust = 1)) #+
+  #theme(plot.margin=margin(b = 1, unit='cm'))
   #theme(plot.title = element_text(hjust = -0.4))
@@
   ggplot(plotData,aes(x=period,y=value)) +
-  geom_hline(yintercept= target %>% filter(type == "domestic", period == 2030) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = 2015, y = target %>% filter(type == "domestic", period == 2030) %>% pull(value), label = "REPowerEU\ndomestic", angle=90, vjust = 0.4, hjust = 0, color = "black", alpha = 0.5, size = geomText.size) +
-  geom_hline(yintercept= target %>% filter(type == "total", period == 2030) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = 2015, y = target %>% filter(type == "total", period == 2030) %>% pull(value), label = "REPowerEU\ntotal", angle=90, vjust = 0.4, hjust = 0, color = "black", alpha = 0.5, size = geomText.size) +
+  geom_segment(aes(x = 2015, xend = 2035, y = target %>% filter(type == "domestic", period == 2030) %>% pull(value), yend = target %>% filter(type == "domestic", period == 2030) %>% pull(value)), color = "#888888", linewidth=1, linetype = "dashed") +
+  #geom_hline(yintercept= target %>% filter(type == "domestic", period == 2030) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = 2015, y = target %>% filter(type == "domestic", period == 2030) %>% pull(value), label = "REPowerEU\ndomestic", angle=90, vjust = 0.4, hjust = 0, color = "black", alpha = 0.5, size = geomText.size * 0.8) +
+  geom_segment(aes(x = 2015, xend = 2035, y = target %>% filter(type == "total", period == 2030) %>% pull(value), yend = target %>% filter(type == "total", period == 2030) %>% pull(value)), color = "#888888", linewidth=1, linetype = "dashed") +
+  #geom_hline(yintercept= target %>% filter(type == "total", period == 2030) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = 2015, y = target %>% filter(type == "total", period == 2030) %>% pull(value), label = "REPowerEU\ntotal", angle=90, vjust = 0.4, hjust = 0, color = "black", alpha = 0.5, size = geomText.size * 0.8) +
   geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = type, alpha=factor(period))) +
@@
 FEplotData <- df %>% 
-  filter(region == "EU27", period >= 2020, period <= 2060, scenario == mainScen, variable %in% names(FEvarList))
+  filter(region == "EU27", period >= 2020, period <= 2050, scenario == mainScen, variable %in% names(FEvarList))
 
@@
 
-logoData <- data.frame(cat = factor(names(logoSVG),levels=c("LDV","Buses","Trucks","Rail","Domestic\nAviation","International\nShipping","International\nAviation")), period = 2040, value = max(FEplotData$value)) %>%
+logoData <- data.frame(cat = factor(names(logoSVG),levels=c("LDV","Buses","Trucks","Rail","Domestic\nAviation","International\nShipping","International\nAviation")), period = 2035, value = max(FEplotData$value)) %>%
   mutate(logo = logoSVG[cat])
@@
   scale_fill_manual(values = plotColor, guide = guide_legend(nrow = 1)) + #, guide = guide_legend(nrow = 2)
-  scale_alpha_manual(values = c("2020"=0.7,"2025"=0.7,"2030"=0.7,"2035"=0.7,"2040"=1,"2045"=0.7,"2050"=0.7,"2055"=0.7,"2060"=0.7), guide = 'none') +
-  scale_x_continuous(breaks = c(2020,2040,2060)) + 
+  scale_alpha_manual(values = c("2020"=0.7,"2025"=0.7,"2030"=0.7,"2035"=0.7,"2040"=1,"2045"=0.7,"2050"=0.7), guide = 'none') +
+  scale_x_continuous(breaks = c(2020,2030,2040,2050)) + 
   theme(
@@
 plotData <- df %>% 
-  filter(region == "EU27", period >= 2020, period <= 2060, scenario == mainScen, variable %in% unlist(vars)) %>% 
+  filter(region == "EU27", period >= 2020, period <= 2050, scenario == mainScen, variable %in% unlist(vars)) %>% 
   mutate(variable = factor(variable, levels=vars))
@@
 salestot <- df %>% 
-  filter(region == "EU27", period >= 2020, period <= 2060, scenario == mainScen, variable %in% Sales) %>% 
+  filter(region == "EU27", period >= 2020, period <= 2050, scenario == mainScen, variable %in% Sales) %>% 
   group_by(period) %>%
@@
 stockData <- df %>% 
-  filter(region == "EU27", period >= 2020, period <= 2060, scenario == mainScen, variable %in% unlist(Stock)) %>% 
+  filter(region == "EU27", period >= 2020, period <= 2050, scenario == mainScen, variable %in% unlist(Stock)) %>% 
   mutate(variable = factor(variable, levels=Stock)) %>%
@@
 totstockData <- df %>% 
-  filter(region == "EU27", period >= 2020, period <= 2060, scenario == mainScen, variable %in% StockTotal) %>% 
+  filter(region == "EU27", period >= 2020, period <= 2050, scenario == mainScen, variable %in% StockTotal) %>% 
   select(period, value) %>%
@@
 
-logoData <- data.frame(period = 2050, value = 0.7, logo = paste(readLines("./img/LDV.svg"), collapse = "\n"))
+logoData <- data.frame(period = 2045, value = 0.7, logo = paste(readLines("./img/LDV.svg"), collapse = "\n"))
 
@@
  scale_color_manual(values = c("ICE Stock"="black"), guide = guide_legend(order = 2, keywidth = unit(2, 'cm'))) +
- scale_alpha_manual(values = c("2020"=0.7,"2025"=0.7,"2030"=0.7,"2035"=0.7,"2040"=1,"2045"=0.7,"2050"=0.7,"2055"=0.7,"2060"=0.7), guide = 'none') +
- scale_x_continuous(breaks=c(2020,2030,2040,2050,2060)) +
+ scale_alpha_manual(values = c("2020"=0.7,"2025"=0.7,"2030"=0.7,"2035"=0.7,"2040"=1,"2045"=0.7,"2050"=0.7), guide = 'none') +
+ scale_x_continuous(breaks=c(2020,2030,2040,2050)) +
  scale_y_continuous(limits = c(0, 1.1), breaks=c(0,1), labels = scales::percent, name = "Sales") +
@@
   #theme(legend.text=element_text(size=theme.double.text.size)) +
-  labs(title = "(b) LDV sales shares &  share of ICE in LDV stock (%)") +
-  theme(plot.title = element_text(hjust=-0.5))
+  labs(title = "(b) LDV sales shares &  share of ICE in\nLDV stock (%)") +
+  theme(plot.title = element_text(hjust=1))
 
@@
 plotData <- df %>% 
-  filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
+  filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
   mutate(variable = factor(variable, levels=vars)) %>%
@@
     #theme(legend.text=element_text(size=theme.double.text.size))  +
-    labs(title = expression(paste("(d) Industrial sectors’ ", CO[2], " emissions (Mt ", CO[2], "/yr)"))) #+
+    labs(title = "(d) Industrial sectors’ CO2 emissions\n(Mt CO2/yr)")
+    labs(title = expression(paste("(d) Industrial sectors’ ", CO[2], " emissions\n(Mt ", CO[2], "/yr)")))  +
+    theme(plot.title = element_text(hjust=1))  
     #theme(plot.title = element_text(hjust=-0.3))
@@
 # origData <- df %>%
-#   filter(region == "EU27", period >= 2020, period <= 2060, variable %in% vars) %>% #, scenario == mainScen
+#   filter(region == "EU27", period >= 2020, period <= 2050, variable %in% vars) %>% #, scenario == mainScen
 #   mutate(name = invertVars[as.character(variable)]) %>%
@@
 plotData <- df %>%
-  filter(region == "EU27", period >= 2020, period <= 2060, variable %in% vars) %>% #, scenario == mainScen
+  filter(region == "EU27", period >= 2020, period <= 2050, variable %in% vars) %>% #, scenario == mainScen
   mutate(name = invertVars[as.character(variable)]) %>%
@@
   #theme(legend.margin=margin(l = -2.5, t = -0.5, unit='cm')) +
-  labs(title = paste0("(c) Buildings space and water heating useful energy (", unique(plotData$unit), ")")) +
+  labs(title = paste0("(c) Buildings space and water heating\nuseful energy (", unique(plotData$unit), ")")) +
   theme(plot.title = element_text(hjust=1)) #+
@@
   "fossil (energy)" = "Carbon Management|Carbon Capture|Fossil|Pe2Se",
-  "industry and waste" = "Carbon Management|Carbon Capture|Industry and Waste"
+  "industry & waste" = "Carbon Management|Carbon Capture|Industry and Waste"
   #"industry" = "Carbon Management|Carbon Capture|Industry",
@@
   "fossil (energy)" = "#6b5b4b",
-  "industry and waste" = "#5f6769"#,
+  "industry & waste" = "#5f6769"#,
   #"industry" = "#5f6769",
@@
         ) +
-  labs(title = expression(paste("(e) Carbon Capture and Storage (Mt ", CO[2], "/yr)"))) +
-  theme(plot.title = element_text(hjust=-0.3))   #+
+  labs(title = "(e) Carbon Capture and Storage\n(Mt CO2/yr)") +
+  theme(legend.spacing.x = unit(0.3, 'cm'),
+        legend.margin=margin(l=-50))
+
+  #labs(title = expression(paste("(e) Carbon Capture and Storage\n(Mt ", CO[2], "/yr)")))  #+
+  #theme(plot.title = element_text(hjust=0))
 
@@
 #                       -> one third of oil imports by 2040
+
+violin_scale <- 3 
+violin_color = "#bbbbbb"
+violin_boxPlotWidth <- 1.5
 
@@
 
-g[["Emissions reductions"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=0.6) +
-         #stat_summary(geom = "text", fun = quantile,
-        #              aes(label = paste0(round(..y..*100),"%")),
-        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-         #      hjust=-1, angle = 90) +
-  geom_hline(yintercept=0.57, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Emissions\nreductions", y = 0.57, label = "FitFor55", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
-  geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Emissions\nreductions", y = reduction_h, label = "2022", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
-  facet_grid(target~period, scales="free") +
-  theme_doubleColumn() +
-  coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-  expand_limits(y=c(0,1)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-  geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geomText.size, hjust=1.4, na.rm = TRUE)
-
-g[["milestone - vert"]][["Emissions reductions"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = 0.55, label = "FitFor55", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = reduction_h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-  expand_limits(y=c(0,1)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  theme(strip.text = element_text(angle = 90)) +
-  coord_cartesian(clip = 'off') #+
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-
-g[["milestone - hor"]][["Emissions reductions"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = 0.55, label = "FitFor55", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+target <- data.frame(period = 2030, value = 0.57, label = "FitFor55")
+
+g[["Emissions reductions"]] <- NULL
+# 
+# g[["Emissions reductions"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=0.6) +
+#          #stat_summary(geom = "text", fun = quantile,
+#         #              aes(label = paste0(round(..y..*100),"%")),
+#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
+#          #      hjust=-1, angle = 90) +
+#   geom_hline(data=target, aes(yintercept = value), color = "black", linewidth=1, alpha = 0.5, linetype = "dotted") +
+#   geom_text(data = target, aes(x=value, label = label), angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5 ) +
+#   #geom_hline(yintercept=0.57, color = "black", linewidth=1, alpha = 0.5, linetype = "dotted") +
+#   #annotate("text", x = "Emissions\nreductions", y = 0.57, label = "FitFor55", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
+#   geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = "Emissions\nreductions", y = reduction_h, label = "2022", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
+#   facet_grid(target~period, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+#   expand_limits(y=c(0,1)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
+#   geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geomText.size, hjust=1.4, na.rm = TRUE)
+# 
+# g[["milestone - vert"]][["Emissions reductions"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(data=target, aes(yintercept = value), color = "black", linewidth=1, alpha = 0.5, linetype = "dotted") +
+#   geom_text(data = target, aes(x = Inf, y = value, label = label), vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   #geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   #annotate("text", x = Inf, y = 0.55, label = "FitFor55", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = reduction_h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+#   expand_limits(y=c(0,1)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   theme(strip.text = element_text(angle = 90)) +
+#   coord_cartesian(clip = 'off') #+
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+# 
+# g[["milestone - hor"]][["Emissions reductions"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = 0.55, label = "FitFor55", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = reduction_h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+#   expand_limits(y=c(0,1)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+#   #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=0.8*geomText.size)
+
+target <- data.frame(period = 2030, x = 2025, xend= 2035, value = 0.55, label = "FitFor55")
+
+g[["milestone - violin"]][["Emissions reductions"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
+  geom_violin(fill="#bbbbbb", scale = violin_scale) + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=1, colour="black", alpha=0.9, linewidth=0.5) +
+  geom_boxplot(outlier.shape = NA, width=1.5) +
+  geom_segment(data = target, aes(x=x, xend=xend, y=value, yend=value), color = "black", linewidth=1, alpha = 0.5, linetype = "dotted") +
+  #geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = -Inf, y = 0.55, label = "FitFor55", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
   geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
@@
   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
   #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=0.8*geomText.size)
@@
 
-g[["Energy savings"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-  geom_boxplot(outlier.shape = NA, width=0.6) +
-         #stat_summary(geom = "text", fun = quantile,
-        #              aes(label = paste0(round(..y..*100),"%")),
-        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-         #      hjust=-1, angle = 90) +
-  geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Final Energy\nDemand", y = 787, label = "FitFor55", angle=90, vjust = 1.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Final Energy\nDemand", y = 750, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0.7, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+g[["Energy savings"]] <- NULL
+
+# g[["Energy savings"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
+#   geom_boxplot(outlier.shape = NA, width=0.6) +
+#          #stat_summary(geom = "text", fun = quantile,
+#         #              aes(label = paste0(round(..y..*100),"%")),
+#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
+#          #      hjust=-1, angle = 90) +
+#   geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = "Final Energy\nDemand", y = 787, label = "FitFor55", angle=90, vjust = 1.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = "Final Energy\nDemand", y = 750, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0.7, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   geom_hline(yintercept=h %>% filter(period==2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = "Final Energy\nDemand", y = h %>% filter(period==2022) %>% pull(value), label = "2022", angle=90, vjust = -0.5, hjust = 0.7, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(target~period, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   theme(strip.text.x = element_blank()) +
+#   expand_limits(y=c(400,1000)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
+#   geom_text(data=data.frame(period=c(2030,2040),label=c("(Mtoe/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.2, na.rm = TRUE)
+# 
+# 
+# g[["milestone - vert"]][["Energy savings"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = 750, label = "REPowerEU", vjust = 1.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   annotate("text", x = Inf, y = 787, label = "FitFor55", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   geom_hline(yintercept=h %>% filter(period==2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = h %>% filter(period==2022) %>% pull(value), label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+#   expand_limits(y=c(0,400,1000)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   theme(strip.text = element_text(angle = 90)) +
+#   coord_cartesian(clip = 'off') +
+#   annotate("text", x = -Inf, y = Inf, label = "(Mtoe/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+# 
+# g[["milestone - hor"]][["Energy savings"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mtoe/yr)")), aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = 750, label = "REPowerEU", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   annotate("text", x = Inf, y = 787, label = "FitFor55", angle=90, vjust = 1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   geom_hline(yintercept=h %>% filter(period==2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = h %>% filter(period==2022) %>% pull(value), label = "2022", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+#   expand_limits(y=c(0,400,1000)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+#   #annotate("text", x = -Inf, y = -Inf, label = "(Mtoe/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+
+plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mtoe/yr)"))
+
+target <- data.frame(period = 2030, x = c(2025,2025), xend= c(2035,2035), value = c(750,787), label = c("FitFor55","REPowerEU"))
+
+mainScenarioValue <- plotData %>% filter(scenario == mainScen)
+
+g[["milestone - violin"]][["Energy savings"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
+  geom_segment(data = target, aes(x=x, xend=xend, y=value, yend=value), color = "black", linewidth=1, alpha = 0.5, linetype = "dotted") +
+  #geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  #geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 750, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  annotate("text", x = Inf, y = 787, label = "FitFor55", angle=90, vjust = 1.5, hjust = 0.3, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
   geom_hline(yintercept=h %>% filter(period==2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Final Energy\nDemand", y = h %>% filter(period==2022) %>% pull(value), label = "2022", angle=90, vjust = -0.5, hjust = 0.7, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(target~period, scales="free") +
-  theme_doubleColumn() +
-  coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  theme(strip.text.x = element_blank()) +
-  expand_limits(y=c(400,1000)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-  geom_text(data=data.frame(period=c(2030,2040),label=c("(Mtoe/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.2, na.rm = TRUE)
-
-g[["milestone - vert"]][["Energy savings"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = 750, label = "REPowerEU", vjust = 1.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  annotate("text", x = Inf, y = 787, label = "FitFor55", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  geom_hline(yintercept=h %>% filter(period==2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = h %>% filter(period==2022) %>% pull(value), label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-  expand_limits(y=c(0,400,1000)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  theme(strip.text = element_text(angle = 90)) +
-  coord_cartesian(clip = 'off') +
-  annotate("text", x = -Inf, y = Inf, label = "(Mtoe/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-
-g[["milestone - hor"]][["Energy savings"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mtoe/yr)")), aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = 750, label = "REPowerEU", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  annotate("text", x = Inf, y = 787, label = "FitFor55", angle=90, vjust = 1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  geom_hline(yintercept=h %>% filter(period==2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = h %>% filter(period==2022) %>% pull(value), label = "2022", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  annotate("text", x = Inf, y = h %>% filter(period==2022) %>% pull(value), label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  geom_point(data=mainScenarioValue, shape=4, size = 2, stroke = 1.5, alpha = 0.6, color = "red") +
   facet_grid(.~target, scales="free") +
@@
   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
   #annotate("text", x = -Inf, y = -Inf, label = "(Mtoe/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
@@
 
-g[["Electricity Demand"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-  geom_boxplot(outlier.shape = NA, width=0.6) +
-  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Electricity\nDemand", y = h, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(target~period, scales="free") +
-  theme_doubleColumn() +
-  coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  theme(strip.text.x = element_blank()) +
-  expand_limits(y=c(0,5000)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-  geom_text(data=data.frame(period=c(2030,2040),label=c("(TWh)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.2, na.rm = TRUE)
-
-g[["milestone - vert"]][["Electricity Demand"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-  expand_limits(y=c(0,5000)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  theme(strip.text = element_text(angle = 90)) +
-  coord_cartesian(clip = 'off') +
-  annotate("text", x = -Inf, y = Inf, label = "(TWh)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-
-g[["milestone - hor"]][["Electricity Demand"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (TWh)")), aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
+g[["Electricity Demand"]] <- NULL
+
+# g[["Electricity Demand"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
+#   geom_boxplot(outlier.shape = NA, width=0.6) +
+#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = "Electricity\nDemand", y = h, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(target~period, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   theme(strip.text.x = element_blank()) +
+#   expand_limits(y=c(0,5000)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
+#   geom_text(data=data.frame(period=c(2030,2040),label=c("(TWh)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.2, na.rm = TRUE)
+# 
+# g[["milestone - vert"]][["Electricity Demand"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+#   expand_limits(y=c(0,5000)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   theme(strip.text = element_text(angle = 90)) +
+#   coord_cartesian(clip = 'off') +
+#   annotate("text", x = -Inf, y = Inf, label = "(TWh)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+# 
+# g[["milestone - hor"]][["Electricity Demand"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (TWh)")), aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+#   expand_limits(y=c(0,5000)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+#   #annotate("text", x = -Inf, y = -Inf, label = "(TWh)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+
+plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (TWh)"))
+
+mainScenarioValue <- plotData %>% filter(scenario == mainScen)
+
+g[["milestone - violin"]][["Electricity Demand"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
   annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  geom_point(data=mainScenarioValue, shape=4, size = 2, stroke = 1.5, alpha = 0.6, color = "red") +
   facet_grid(.~target, scales="free") +
@@
   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
   #annotate("text", x = -Inf, y = -Inf, label = "(TWh)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
@@
 
-g[["Renewables Share"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-  geom_boxplot(outlier.shape = NA, width=0.6) +
-         #stat_summary(geom = "text", fun = quantile,
-        #              aes(label = paste0(round(..y..*100),"%")),
-        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-         #      hjust=-1, angle = 90) +
-  geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Renewables\nShare in\nFinal Energy", y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0.5, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Renewables\nShare in\nFinal Energy", y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0.6, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Renewables\nShare in\nFinal Energy", y = addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), label = "2022", angle=90, vjust = -0.5, hjust = 0.6, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(target~period, scales="free") +
-  theme_doubleColumn() +
-  coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  theme(strip.text.x = element_blank()) +
-  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-  expand_limits(y=c(0,1)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-  geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.4, na.rm = TRUE)
-
-g[["milestone - vert"]][["Renewables Share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = 0.4, label = "RED II revised", vjust = 1.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = 0.45, label = "REPowerEU", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-  expand_limits(y=c(0,1)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  theme(strip.text = element_text(angle = 90)) +
-  coord_cartesian(clip = 'off') #+
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-
-g[["milestone - hor"]][["Renewables Share"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+g[["Renewables Share"]] <- NULL
+
+# g[["Renewables Share"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
+#   geom_boxplot(outlier.shape = NA, width=0.6) +
+#          #stat_summary(geom = "text", fun = quantile,
+#         #              aes(label = paste0(round(..y..*100),"%")),
+#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
+#          #      hjust=-1, angle = 90) +
+#   geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = "Renewables\nShare in\nFinal Energy", y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0.5, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = "Renewables\nShare in\nFinal Energy", y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0.6, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = "Renewables\nShare in\nFinal Energy", y = addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), label = "2022", angle=90, vjust = -0.5, hjust = 0.6, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(target~period, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   theme(strip.text.x = element_blank()) +
+#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+#   expand_limits(y=c(0,1)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
+#   geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.4, na.rm = TRUE)
+# 
+# g[["milestone - vert"]][["Renewables Share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = 0.4, label = "RED II revised", vjust = 1.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = 0.45, label = "REPowerEU", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+#   expand_limits(y=c(0,1)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   theme(strip.text = element_text(angle = 90)) +
+#   coord_cartesian(clip = 'off') #+
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+# 
+# g[["milestone - hor"]][["Renewables Share"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+#   expand_limits(y=c(0,1)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+#   #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+
+target <- data.frame(period = 2030, x = c(2025,2025), xend= c(2035,2035), value = c(0.4,0.45), label = c("RED II revised","REPowerEU"))
+
+plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)"))
+
+mainScenarioValue <- plotData %>% filter(scenario == mainScen)
+
+g[["milestone - violin"]][["Renewables Share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
+  geom_segment(data = target, aes(x=x, xend=xend, y=value, yend=value), color = "black", linewidth=1, alpha = 0.5, linetype = "dotted") +
+  #geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = Inf, y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0.075, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  #geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
   annotate("text", x = Inf, y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
@@
   annotate("text", x = Inf, y = addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  geom_point(data=mainScenarioValue, shape=4, size = 2, stroke = 1.5, alpha = 0.6, color = "red") +
   facet_grid(.~target, scales="free") +
@@
   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
   #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
@@
 
+g[["Wind capacity"]] <- NULL
+
 #target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2025,2030),value=c(320,600)) 
-g[["Wind capacity"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-  geom_boxplot(outlier.shape = NA, width=0.6) +
-  geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Wind\ncapacity", y = 255, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(target~period, scales="free") +
-  theme_doubleColumn() +
-  coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  theme(strip.text.x = element_blank()) +
-  expand_limits(y=c(0,1000)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-  geom_text(data=data.frame(period=c(2030,2040),label=c("(GW)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.3, na.rm = TRUE)
-
-g[["milestone - vert"]][["Wind capacity"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = 255, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-  expand_limits(y=c(0,1000)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  theme(strip.text = element_text(angle = 90)) +
-  coord_cartesian(clip = 'off') +
-  annotate("text", x = -Inf, y = Inf, label = "(GW)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-
-g[["milestone - hor"]][["Wind capacity"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (GW)")), aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
+# g[["Wind capacity"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
+#   geom_boxplot(outlier.shape = NA, width=0.6) +
+#   geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = "Wind\ncapacity", y = 255, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(target~period, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   theme(strip.text.x = element_blank()) +
+#   expand_limits(y=c(0,1000)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
+#   geom_text(data=data.frame(period=c(2030,2040),label=c("(GW)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.3, na.rm = TRUE)
+# 
+# g[["milestone - vert"]][["Wind capacity"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = 255, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+#   expand_limits(y=c(0,1000)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   theme(strip.text = element_text(angle = 90)) +
+#   coord_cartesian(clip = 'off') +
+#   annotate("text", x = -Inf, y = Inf, label = "(GW)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+# 
+# g[["milestone - hor"]][["Wind capacity"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (GW)")), aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = 255, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+#   expand_limits(y=c(0,1000)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+#   #annotate("text", x = -Inf, y = -Inf, label = "(GW)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+
+plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (GW)"))
+
+mainScenarioValue <- plotData %>% filter(scenario == mainScen)
+
+g[["milestone - violin"]][["Wind capacity"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
   geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
   annotate("text", x = Inf, y = 255, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  geom_point(data=mainScenarioValue, shape=4, size = 2, stroke = 1.5, alpha = 0.6, color = "red") +
   facet_grid(.~target, scales="free") +
@@
   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
   #annotate("text", x = -Inf, y = -Inf, label = "(GW)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
@@
 
-#target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2025,2030),value=c(320,600)) 
-g[["Solar photovoltaics"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-  geom_boxplot(outlier.shape = NA, width=0.6) +
-         #stat_summary(geom = "text", fun = quantile,
-        #              aes(label = paste0(round(..y..*100),"%")),
-        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-         #      hjust=-1, angle = 90) +
-  geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Solar\nphotovoltaics", y = 600, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0.6, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Solar\nphotovoltaics", y = 208.9, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(target~period, scales="free") +
-  theme_doubleColumn() +
-  coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  theme(strip.text.x = element_blank()) +
-  expand_limits(y=c(0,2500)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-  geom_text(data=data.frame(period=c(2030,2040),label=c("(GW)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.3, na.rm = TRUE)
-
-g[["milestone - vert"]][["Solar photovoltaics"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = 600, label = "REPowerEU", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = 208.9, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-  expand_limits(y=c(0,2500)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  theme(strip.text = element_text(angle = 90)) +
-  coord_cartesian(clip = 'off') +
-  annotate("text", x = -Inf, y = Inf, label = "(GW)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-
-g[["milestone - hor"]][["Solar photovoltaics"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (GW)")), aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = 600, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+g[["Solar photovoltaics"]] <- NULL
+
+# #target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2025,2030),value=c(320,600)) 
+# g[["Solar photovoltaics"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
+#   geom_boxplot(outlier.shape = NA, width=0.6) +
+#          #stat_summary(geom = "text", fun = quantile,
+#         #              aes(label = paste0(round(..y..*100),"%")),
+#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
+#          #      hjust=-1, angle = 90) +
+#   geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = "Solar\nphotovoltaics", y = 600, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0.6, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = "Solar\nphotovoltaics", y = 208.9, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(target~period, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   theme(strip.text.x = element_blank()) +
+#   expand_limits(y=c(0,2500)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
+#   geom_text(data=data.frame(period=c(2030,2040),label=c("(GW)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.3, na.rm = TRUE)
+# 
+# g[["milestone - vert"]][["Solar photovoltaics"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = 600, label = "REPowerEU", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = 208.9, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+#   expand_limits(y=c(0,2500)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   theme(strip.text = element_text(angle = 90)) +
+#   coord_cartesian(clip = 'off') +
+#   annotate("text", x = -Inf, y = Inf, label = "(GW)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+# 
+# g[["milestone - hor"]][["Solar photovoltaics"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (GW)")), aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = 600, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = 208.9, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+#   expand_limits(y=c(0,2500)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+#   #annotate("text", x = -Inf, y = -Inf, label = "(GW)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+
+target <- data.frame(period = 2030, x = 2025, xend= 2035, value = 600, label = "REPowerEU")
+
+plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (GW)"))
+
+mainScenarioValue <- plotData %>% filter(scenario == mainScen)
+
+g[["milestone - violin"]][["Solar photovoltaics"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
+  geom_segment(data = target, aes(x=x, xend=xend, y=value, yend=value), color = "black", linewidth=1, alpha = 0.5, linetype = "dotted") +
+  annotate("text", x = Inf, y = 600, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
   geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
   annotate("text", x = Inf, y = 208.9, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  geom_point(data=mainScenarioValue, shape=4, size = 2, stroke = 1.5, alpha = 0.6, color = "red") +
   facet_grid(.~target, scales="free") +
@@
   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
-  expand_limits(y=c(0,2500)) + 
+  expand_limits(y=c(0,2250)) + 
   theme(panel.spacing = unit(4, "lines")) +
@@
 
-g[["Carbon Capture and Storage"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-  geom_boxplot(outlier.shape = NA, width=0.6) +
-         #stat_summary(geom = "text", fun = quantile,
-        #              aes(label = paste0(round(..y..*100),"%")),
-        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-         #      hjust=-1, angle = 90) +
-  geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Carbon\nCapture and\nStorage", y = 50, label = "Net-Zero\nIndustry Act", angle=90, vjust = -0.2, hjust = 0.6, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(target~period, scales="free") +
-  theme_doubleColumn() +
-  coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  theme(strip.text.x = element_blank()) +
-  #expand_limits(y=c(0,ceiling(max(plotData$value)/50)*50)) + 
-  expand_limits(y=c(0,400)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-  geom_text(data=data.frame(period=c(2030,2040),label=c("(Mt CO2/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.1, na.rm = TRUE)
-
-g[["milestone - vert"]][["Carbon Capture and Storage"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = 50, label = "Net-Zero\nIndustry Act", vjust = 0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-  expand_limits(y=c(0,400)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  theme(strip.text = element_text(angle = 90)) +
-  coord_cartesian(clip = 'off') +
-  annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-
-g[["milestone - hor"]][["Carbon Capture and Storage"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = 50, label = "Net-Zero\nIndustry Act", angle=90, vjust = 0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+g[["Carbon Capture and Storage"]] <- NULL
+
+# g[["Carbon Capture and Storage"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
+#   geom_boxplot(outlier.shape = NA, width=0.6) +
+#          #stat_summary(geom = "text", fun = quantile,
+#         #              aes(label = paste0(round(..y..*100),"%")),
+#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
+#          #      hjust=-1, angle = 90) +
+#   geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = "Carbon\nCapture and\nStorage", y = 50, label = "Net-Zero\nIndustry Act", angle=90, vjust = -0.2, hjust = 0.6, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(target~period, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   theme(strip.text.x = element_blank()) +
+#   #expand_limits(y=c(0,ceiling(max(plotData$value)/50)*50)) + 
+#   expand_limits(y=c(0,400)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
+#   geom_text(data=data.frame(period=c(2030,2040),label=c("(Mt CO2/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.1, na.rm = TRUE)
+# 
+# g[["milestone - vert"]][["Carbon Capture and Storage"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = 50, label = "Net-Zero\nIndustry Act", vjust = 0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+#   expand_limits(y=c(0,400)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   theme(strip.text = element_text(angle = 90)) +
+#   coord_cartesian(clip = 'off') +
+#   annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+# 
+# g[["milestone - hor"]][["Carbon Capture and Storage"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = 50, label = "Net-Zero\nIndustry Act", angle=90, vjust = 0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+#   expand_limits(y=c(0,400)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
+#   theme(strip.clip = "off")#+
+#   #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+# 
+# target <- data.frame(period = 2030, x = 2025, xend= 2035, value = 50, label = "Net-Zero\nIndustry Act")
+
+plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)"))
+
+mainScenarioValue <- plotData %>% filter(scenario == mainScen)
+
+target <- data.frame(period = 2030, x = 2025, xend= 2035, value = 50, label = c("Net-Zero\nIndustry Act"))
+
+g[["milestone - violin"]][["Carbon Capture and Storage"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
+
+  geom_segment(data = target, aes(x=x, xend=xend, y=value, yend=value), color = "black", linewidth=1, alpha = 0.5, linetype = "dotted") +
+
+  #geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = -Inf, y = 50, label = "Net-Zero\nIndustry Act", angle=90, vjust = 0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  geom_point(data=mainScenarioValue, shape=4, size = 2, stroke = 1.5, alpha = 0.6, color = "red") +
   facet_grid(.~target, scales="free") +
@@
   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
-  expand_limits(y=c(0,400)) + 
+  expand_limits(y=c(0,300)) + 
   theme(panel.spacing = unit(4, "lines")) +
@@
   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
+  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) +
   theme(strip.clip = "off")#+
@@
 
-g[["Novel CDR"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-  geom_boxplot(outlier.shape = NA, width=0.6) +
-         #stat_summary(geom = "text", fun = quantile,
-        #              aes(label = paste0(round(..y..*100),"%")),
-        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-         #      hjust=-1, angle = 90) +
-  facet_grid(target~period, scales="free") +
-  theme_doubleColumn() +
-  coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  theme(strip.text.x = element_blank()) +
-  expand_limits(y=c(0,400)) + 
-  #expand_limits(y=c(0,ceiling(max(plotData$value)/50)*50)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-  geom_text(data=data.frame(period=c(2030,2040),label=c("(Mt CO2/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.1, na.rm = TRUE)
-
-g[["milestone - vert"]][["Novel CDR"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-  expand_limits(y=c(0,400)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  theme(strip.text = element_text(angle = 90)) +
-  coord_cartesian(clip = 'off') +
-  annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-
-g[["milestone - hor"]][["Novel CDR"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
+g[["Novel CDR"]] <- NULL
+
+# g[["Novel CDR"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
+#   geom_boxplot(outlier.shape = NA, width=0.6) +
+#          #stat_summary(geom = "text", fun = quantile,
+#         #              aes(label = paste0(round(..y..*100),"%")),
+#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
+#          #      hjust=-1, angle = 90) +
+#   facet_grid(target~period, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   theme(strip.text.x = element_blank()) +
+#   expand_limits(y=c(0,400)) + 
+#   #expand_limits(y=c(0,ceiling(max(plotData$value)/50)*50)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
+#   geom_text(data=data.frame(period=c(2030,2040),label=c("(Mt CO2/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.1, na.rm = TRUE)
+# 
+# g[["milestone - vert"]][["Novel CDR"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+#   expand_limits(y=c(0,400)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   theme(strip.text = element_text(angle = 90)) +
+#   coord_cartesian(clip = 'off') +
+#   annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+# 
+# g[["milestone - hor"]][["Novel CDR"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+#   expand_limits(y=c(0,400)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+#   #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+
+plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)"))
+
+mainScenarioValue <- plotData %>% filter(scenario == mainScen)
+
+g[["milestone - violin"]][["Novel CDR"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
+  geom_point(data=mainScenarioValue, shape=4, size = 2, stroke = 1.5, alpha = 0.6, color = "red") +
   facet_grid(.~target, scales="free") +
@@
   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
   #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
@@
 # Direct Electrification
-plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Final Energy|Electricity Share") %>% select(-variable) %>%
+#plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Final Energy|w/o Bunkers|w/o Non-energy Use|Electricity Share") %>% select(-variable) %>%
+plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Final Energy|w/o Bunkers|w/o Non-energy Use|Electricity Share") %>% select(-variable) %>%
   filter(tgt2050 != "Npi") %>%
@@
 #estimation of historical share in 2022 for FE electricity / FE with non-energy use and with bunkers
-h <- (
-      2550461.10 *1000 / 8.76E+09 * 31.536  # https://ec.europa.eu/eurostat/databrowser/bookmark/12d54df4-7c35-47eb-a103-dd8994d26b80?lang=en
-     ) / (
-      addHist$FE_consumption %>% mutate(value = value/1000000) %>% filter(period==2022) %>% pull(value) + # FE|w/o Non-energy Use w/o Bunkers - EJ
-      df %>% filter(region == "EU27", period == 2020, scenario == "Npi", variable == "FE|Transport|Bunkers") %>% pull(value) +
-      df %>% filter(region == "EU27", period == 2020, scenario == "Npi", variable == "FE|Non-energy Use|Industry") %>% pull(value)
-     )
-
-g[["Direct Electrification"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-    geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-  geom_boxplot(outlier.shape = NA, width=0.6) +
-         #stat_summary(geom = "text", fun = quantile,
-        #              aes(label = paste0(round(..y..*100),"%")),
-        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-         #      hjust=-1, angle = 90) +
-  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Electricity\nShare in\nFinal Energy", y = h, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(target~period, scales="free") +
-  theme_doubleColumn() +
-  coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  theme(strip.text.x = element_blank()) +
-  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-  expand_limits(y=c(0,1)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-  geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.4, na.rm = TRUE)
-
-g[["milestone - vert"]][["Direct Electrification"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-  expand_limits(y=c(0,1)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  theme(strip.text = element_text(angle = 90)) +
-  coord_cartesian(clip = 'off') #+
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-
-g[["milestone - hor"]][["Direct Electrification"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+# h <- (
+#       2550461.10 *1000 / 8.76E+09 * 31.536  # https://ec.europa.eu/eurostat/databrowser/bookmark/12d54df4-7c35-47eb-a103-dd8994d26b80?lang=en
+#      ) / (
+#       addHist$FE_consumption %>% mutate(value = value/1000000) %>% filter(period==2022) %>% pull(value) + # FE|w/o Non-energy Use w/o Bunkers - EJ
+#       df %>% filter(region == "EU27", period == 2020, scenario == "Npi", variable == "FE|Transport|Bunkers") %>% pull(value) +
+#       df %>% filter(region == "EU27", period == 2020, scenario == "Npi", variable == "FE|Non-energy Use|Industry") %>% pull(value)
+#      )
+
+g[["Direct Electrification"]] <- NULL
+
+# g[["Direct Electrification"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
+#     geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
+#   geom_boxplot(outlier.shape = NA, width=0.6) +
+#          #stat_summary(geom = "text", fun = quantile,
+#         #              aes(label = paste0(round(..y..*100),"%")),
+#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
+#          #      hjust=-1, angle = 90) +
+#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = "Electricity\nShare in\nFinal Energy", y = h, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(target~period, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   theme(strip.text.x = element_blank()) +
+#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+#   expand_limits(y=c(0,1)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
+#   geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.4, na.rm = TRUE)
+# 
+# g[["milestone - vert"]][["Direct Electrification"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+#   expand_limits(y=c(0,1)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   theme(strip.text = element_text(angle = 90)) +
+#   coord_cartesian(clip = 'off') #+
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+# 
+# g[["milestone - hor"]][["Direct Electrification"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+#   expand_limits(y=c(0,1)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+#   #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=geomText.size, size = 0.8*geomText.size)
+
+plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)"))
+
+mainScenarioValue <- plotData %>% filter(scenario == mainScen)
+
+g[["milestone - violin"]][["Direct Electrification"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
+  #geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  #annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  geom_point(data=mainScenarioValue, shape=4, size = 2, stroke = 1.5, alpha = 0.6, color = "red") +
   facet_grid(.~target, scales="free") +
@@
   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
   #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=geomText.size, size = 0.8*geomText.size)
@@
 
-g[["Carbon-free electricity share"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-    geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-  geom_boxplot(outlier.shape = NA, width=0.6) +
-         #stat_summary(geom = "text", fun = quantile,
-        #              aes(label = paste0(round(..y..*100),"%")),
-        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-         #      hjust=-1, angle = 90) +
-  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Carbon-free\nelectricity\nshare", y = h, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(target~period, scales="free") +
-  theme_doubleColumn() +
-  coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  theme(strip.text.x = element_blank()) +
-  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-  expand_limits(y=c(0,1)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-  geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.4, na.rm = TRUE)
-
-g[["milestone - vert"]][["Carbon-free electricity share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-  expand_limits(y=c(0,1)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  theme(strip.text = element_text(angle = 90)) +
-  coord_cartesian(clip = 'off') #+
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-
-g[["milestone - hor"]][["Carbon-free electricity share"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
+g[["Carbon-free electricity share"]] <- NULL
+
+# g[["Carbon-free electricity share"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
+#     geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
+#   geom_boxplot(outlier.shape = NA, width=0.6) +
+#          #stat_summary(geom = "text", fun = quantile,
+#         #              aes(label = paste0(round(..y..*100),"%")),
+#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
+#          #      hjust=-1, angle = 90) +
+#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = "Carbon-free\nelectricity\nshare", y = h, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(target~period, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   theme(strip.text.x = element_blank()) +
+#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+#   expand_limits(y=c(0,1)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
+#   geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.4, na.rm = TRUE)
+# 
+# g[["milestone - vert"]][["Carbon-free electricity share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+#   expand_limits(y=c(0,1)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   theme(strip.text = element_text(angle = 90)) +
+#   coord_cartesian(clip = 'off') #+
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+# 
+# g[["milestone - hor"]][["Carbon-free electricity share"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
+#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+#   expand_limits(y=c(0,1)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+#   #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=geomText.size, size = 0.8*geomText.size)
+
+plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)"))
+
+mainScenarioValue <- plotData %>% filter(scenario == mainScen)
+
+g[["milestone - violin"]][["Carbon-free electricity share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
   annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  geom_point(data=mainScenarioValue, shape=4, size = 2, stroke = 1.5, alpha = 0.6, color = "red") +
   facet_grid(.~target, scales="free") +
@@
   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
   #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=geomText.size, size = 0.8*geomText.size)
@@
 
-g[["Residual Fossil Emissions"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-  geom_boxplot(outlier.shape = NA, width=0.6) +
-         #stat_summary(geom = "text", fun = quantile,
-        #              aes(label = paste0(round(..y..*100),"%")),
-        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-         #      hjust=-1, angle = 90) +
-  facet_grid(target~period, scales="free") +
-  theme_doubleColumn() +
-  coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  theme(strip.text.x = element_blank()) +
-  expand_limits(y=c(0,2500)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-  geom_text(data=data.frame(period=c(2030,2040),label=c("(Mt CO2/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.05, na.rm = TRUE)
-
-g[["milestone - vert"]][["Residual Fossil Emissions"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-  expand_limits(y=c(0,2500)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  theme(strip.text = element_text(angle = 90)) +
-  coord_cartesian(clip = 'off') +
-  annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-
-g[["milestone - hor"]][["Residual Fossil Emissions"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
+g[["Residual Fossil Emissions"]] <- NULL
+
+# g[["Residual Fossil Emissions"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
+#   geom_boxplot(outlier.shape = NA, width=0.6) +
+#          #stat_summary(geom = "text", fun = quantile,
+#         #              aes(label = paste0(round(..y..*100),"%")),
+#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
+#          #      hjust=-1, angle = 90) +
+#   facet_grid(target~period, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   theme(strip.text.x = element_blank()) +
+#   expand_limits(y=c(0,2500)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
+#   geom_text(data=data.frame(period=c(2030,2040),label=c("(Mt CO2/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.05, na.rm = TRUE)
+# 
+# g[["milestone - vert"]][["Residual Fossil Emissions"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+#   expand_limits(y=c(0,2500)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   theme(strip.text = element_text(angle = 90)) +
+#   coord_cartesian(clip = 'off') +
+#   annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+# 
+# g[["milestone - hor"]][["Residual Fossil Emissions"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+#   expand_limits(y=c(0,2500)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+#   #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+
+plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)"))
+
+mainScenarioValue <- plotData %>% filter(scenario == mainScen)
+
+g[["milestone - violin"]][["Residual Fossil Emissions"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
+  geom_point(data=mainScenarioValue, shape=4, size = 2, stroke = 1.5, alpha = 0.6, color = "red") +
   facet_grid(.~target, scales="free") +
@@
 
-g[["Domestic Hydrogen Production"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-  geom_boxplot(outlier.shape = NA, width=0.6) +
-  geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = "Domestic\nHydrogen\nProduction", y = 10, label = "REPowerEU\ndomestic", angle=90, vjust = 0.5, hjust = 0.5, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(target~period, scales="free") +
-  theme_doubleColumn() +
-  coord_flip(clip = 'off') +
-  expand_limits(y=c(0,20)) + 
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  theme(strip.text.x = element_blank()) +
-  theme(panel.spacing = unit(4, "lines")) +
-  #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-  geom_text(data=data.frame(period=c(2030,2040),label=c("(Mtoe/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.4, na.rm = TRUE)
-
-g[["milestone - vert"]][["Domestic Hydrogen Production"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = -Inf, y = 10, label = "REPowerEU\ndomestic", vjust = 0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-  expand_limits(y=c(0,20)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  theme(strip.text = element_text(angle = 90)) +
-  coord_cartesian(clip = 'off') +
-  annotate("text", x = -Inf, y = Inf, label = "(Mtoe/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-
-g[["milestone - hor"]][["Domestic Hydrogen Production"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mtoe/yr)")), aes(x = period, y = value, group=period)) +
-  geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=6) +
-  geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  annotate("text", x = -Inf, y = 10, label = "REPowerEU\ndomestic", angle=90, vjust = 0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+g[["Domestic Hydrogen Production"]] <- NULL
+
+# g[["Domestic Hydrogen Production"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
+#   geom_boxplot(outlier.shape = NA, width=0.6) +
+#   geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = "Domestic\nHydrogen\nProduction", y = 10, label = "REPowerEU\ndomestic", angle=90, vjust = 0.5, hjust = 0.5, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(target~period, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   expand_limits(y=c(0,20)) + 
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   theme(strip.text.x = element_blank()) +
+#   theme(panel.spacing = unit(4, "lines")) +
+#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
+#   geom_text(data=data.frame(period=c(2030,2040),label=c("(Mtoe/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.4, na.rm = TRUE)
+# 
+# g[["milestone - vert"]][["Domestic Hydrogen Production"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = -Inf, y = 10, label = "REPowerEU\ndomestic", vjust = 0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
+#   expand_limits(y=c(0,20)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   theme(strip.text = element_text(angle = 90)) +
+#   coord_cartesian(clip = 'off') +
+#   annotate("text", x = -Inf, y = Inf, label = "(Mtoe/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
+# 
+# g[["milestone - hor"]][["Domestic Hydrogen Production"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mtoe/yr)")), aes(x = period, y = value, group=period)) +
+#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+#   geom_boxplot(outlier.shape = NA, width=6) +
+#   geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+#   annotate("text", x = -Inf, y = 10, label = "REPowerEU\ndomestic", angle=90, vjust = 0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+#   facet_grid(.~target, scales="free") +
+#   theme_doubleColumn() +
+#   coord_flip(clip = 'off') +
+#   theme(axis.title.y=element_blank()) +
+#   theme(strip.text.y = element_blank()) +
+#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
+#   expand_limits(y=c(0,20)) + 
+#   theme(panel.spacing = unit(4, "lines")) +
+#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
+#   theme(strip.placement = "outside") +
+#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
+#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
+#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+#   #annotate("text", x = -Inf, y = -Inf, label = "(Mtoe/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+
+target <- data.frame(period = 2030, x = 2025, xend= 2035, value = 10, label = "REPowerEU")
+
+plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mtoe/yr)"))
+
+mainScenarioValue <- plotData %>% filter(scenario == mainScen)
+
+g[["milestone - violin"]][["Domestic Hydrogen Production"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
+  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
+  geom_segment(data = target, aes(x=x, xend=xend, y=value, yend=value), color = "black", linewidth=1, alpha = 0.5, linetype = "dotted") +
+  #geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
+  annotate("text", x = -Inf, y = 10, label = "REPowerEU\ndomestic", angle=90, vjust = 0.5, hjust = 0.8, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
+  geom_point(data=mainScenarioValue, shape=4, size = 2, stroke = 1.5, alpha = 0.6, color = "red") +
   facet_grid(.~target, scales="free") +
@@
   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
+  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=-15, b=20)),
+        strip.clip = "off") #+
   #annotate("text", x = -Inf, y = -Inf, label = "(Mtoe/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
 
-g[["Targets"]] <- gridExtra::arrangeGrob(
-  g[["Emissions reductions"]] + theme(strip.text.x = element_blank()) + theme(plot.margin=margin(b=20, l = 30)), #+ theme(plot.margin=margin(10,10,30,10)),margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
-  g[["Energy savings"]] + theme(plot.margin=margin(b=20, l = 10)),
-  g[["Electricity Demand"]] + theme(plot.margin=margin(b=20, l = 35)),
-  g[["Renewables Share"]] + theme(plot.margin=margin(b=20, l = 15)),
-  g[["Wind capacity"]] + theme(plot.margin=margin(b=20, l = 50)),
-  g[["Solar photovoltaics"]] + theme(plot.margin=margin(b=20, l = 10)),
-  g[["Carbon Capture and Storage"]] + theme(plot.margin=margin(b=20, l = 15)),
-  g[["Novel CDR"]] + theme(plot.margin=margin(b=20, l = 50)),
-  g[["Direct Electrification"]] + theme(plot.margin=margin(b=20, l = 17)),
-  g[["Carbon-free electricity share"]] + theme(plot.margin=margin(b=20, l = 24)),
-  g[["Domestic Hydrogen Production"]] + theme(plot.margin=margin(b=20,l = 35)),
-  g[["Residual Fossil Emissions"]] + theme(plot.margin=margin(b=20, l = 39)),
-  ncol = 1
-)
+# g[["Targets"]] <- gridExtra::arrangeGrob(
+#   g[["Emissions reductions"]] + theme(strip.text.x = element_blank()) + theme(plot.margin=margin(b=20, l = 30)), #+ theme(plot.margin=margin(10,10,30,10)),margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
+#   g[["Energy savings"]] + theme(plot.margin=margin(b=20, l = 10)),
+#   g[["Electricity Demand"]] + theme(plot.margin=margin(b=20, l = 35)),
+#   g[["Renewables Share"]] + theme(plot.margin=margin(b=20, l = 15)),
+#   g[["Wind capacity"]] + theme(plot.margin=margin(b=20, l = 50)),
+#   g[["Solar photovoltaics"]] + theme(plot.margin=margin(b=20, l = 10)),
+#   g[["Carbon Capture and Storage"]] + theme(plot.margin=margin(b=20, l = 15)),
+#   g[["Novel CDR"]] + theme(plot.margin=margin(b=20, l = 50)),
+#   g[["Direct Electrification"]] + theme(plot.margin=margin(b=20, l = 17)),
+#   g[["Carbon-free electricity share"]] + theme(plot.margin=margin(b=20, l = 24)),
+#   g[["Domestic Hydrogen Production"]] + theme(plot.margin=margin(b=20,l = 35)),
+#   g[["Residual Fossil Emissions"]] + theme(plot.margin=margin(b=20, l = 39)),
+#   ncol = 1
+# )
 
@@
 
-g[["milestone - vert targets"]] <- gridExtra::arrangeGrob(
-  g[["milestone - vert"]][["Emissions reductions"]] + theme(plot.margin=margin(r=30,t = 30)), #+ theme(plot.margin=margin(10,10,30,10)),margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
-  g[["milestone - vert"]][["Energy savings"]] + theme(plot.margin=margin(r=30,t = 10)),
-  g[["milestone - vert"]][["Renewables Share"]] + theme(plot.margin=margin(r=30,t = 15)),
-  g[["milestone - vert"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(r=30,t = 39)),
-  g[["milestone - vert"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(r=30,t = 15)),
-  g[["milestone - vert"]][["Novel CDR"]] + theme(plot.margin=margin(t = 50)),
-
-  g[["milestone - vert"]][["Electricity Demand"]] + theme(plot.margin=margin(r=30,t = 35)),
-  g[["milestone - vert"]][["Wind capacity"]] + theme(plot.margin=margin(r=30,t = 50)),
-  g[["milestone - vert"]][["Solar photovoltaics"]] + theme(plot.margin=margin(r=30,t = 10)),
-  g[["milestone - vert"]][["Direct Electrification"]] + theme(plot.margin=margin(r=30,t = 17)),
-  g[["milestone - vert"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(t = 24)),
-  g[["milestone - vert"]][["Domestic Hydrogen Production"]] + theme(plot.margin=margin(r=30,t = 35)),
-  nrow = 2
-)
+# g[["milestone - vert targets"]] <- gridExtra::arrangeGrob(
+#   g[["milestone - vert"]][["Emissions reductions"]] + theme(plot.margin=margin(r=30,t = 30)), #+ theme(plot.margin=margin(10,10,30,10)),margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
+#   g[["milestone - vert"]][["Energy savings"]] + theme(plot.margin=margin(r=30,t = 10)),
+#   g[["milestone - vert"]][["Renewables Share"]] + theme(plot.margin=margin(r=30,t = 15)),
+#   g[["milestone - vert"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(r=30,t = 39)),
+#   g[["milestone - vert"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(r=30,t = 15)),
+#   g[["milestone - vert"]][["Novel CDR"]] + theme(plot.margin=margin(t = 50)),
+#   
+#   g[["milestone - vert"]][["Electricity Demand"]] + theme(plot.margin=margin(r=30,t = 35)),
+#   g[["milestone - vert"]][["Wind capacity"]] + theme(plot.margin=margin(r=30,t = 50)),
+#   g[["milestone - vert"]][["Solar photovoltaics"]] + theme(plot.margin=margin(r=30,t = 10)),
+#   g[["milestone - vert"]][["Direct Electrification"]] + theme(plot.margin=margin(r=30,t = 17)),
+#   g[["milestone - vert"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(t = 24)),
+#   g[["milestone - vert"]][["Domestic Hydrogen Production"]] + theme(plot.margin=margin(r=30,t = 35)),
+#   nrow = 2
+# )
 
@@
 
-g[["milestone - hor targets"]] <- gridExtra::arrangeGrob(
-  g[["milestone - hor"]][["Emissions reductions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - hor"]][["Energy savings"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - hor"]][["Renewables Share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - hor"]][["Direct Electrification"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - hor"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - hor"]][["Domestic Hydrogen Production"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-
-  g[["milestone - hor"]][["Electricity Demand"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - hor"]][["Wind capacity"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - hor"]][["Solar photovoltaics"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-
-  g[["milestone - hor"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - hor"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - hor"]][["Novel CDR"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+# 
+# g[["milestone - hor targets"]] <- gridExtra::arrangeGrob(
+#   g[["milestone - hor"]][["Emissions reductions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+#   g[["milestone - hor"]][["Energy savings"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+#   g[["milestone - hor"]][["Renewables Share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+#   g[["milestone - hor"]][["Direct Electrification"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+#   g[["milestone - hor"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+#   g[["milestone - hor"]][["Domestic Hydrogen Production"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+#   
+#   g[["milestone - hor"]][["Electricity Demand"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+#   g[["milestone - hor"]][["Wind capacity"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+#   g[["milestone - hor"]][["Solar photovoltaics"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+#   
+#   g[["milestone - hor"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+#   g[["milestone - hor"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+#   g[["milestone - hor"]][["Novel CDR"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+#   
+#   
+#   ncol = 2
+# )
+
+g[["milestone - violin targets"]] <- gridExtra::arrangeGrob(
+  g[["milestone - violin"]][["Emissions reductions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Energy savings"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Renewables Share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Direct Electrification"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Domestic Hydrogen Production"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+
+  g[["milestone - violin"]][["Electricity Demand"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Wind capacity"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Solar photovoltaics"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+
+  g[["milestone - violin"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone - violin"]][["Novel CDR"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
 
@@
 
-ggsave(paste0(outChartsFolder,"/svg/Figure 5. Milestones Panel.svg"), g[["milestone - hor targets"]] , device="svg", width = 12, height = 14, dpi=100, units = "in")
-ggsave(paste0(outChartsFolder,"/png/Figure 5. Milestones Panel.png"), g[["milestone - hor targets"]] , device="png", width = 12, height = 14, dpi=300, units = "in")
+ggsave(paste0(outChartsFolder,"/svg/Figure 5. Milestones Panel.svg"), g[["milestone - violin targets"]] , device="svg", width = 12, height = 14, dpi=100, units = "in")
+ggsave(paste0(outChartsFolder,"/png/Figure 5. Milestones Panel.png"), g[["milestone - violin targets"]] , device="png", width = 12, height = 14, dpi=300, units = "in")
 
@@
 grid.newpage()
-grid.draw(g[["milestone - hor targets"]])
+grid.draw(g[["milestone - violin targets"]])
 
@@
   expand_limits(y=c(1,0.75)) +
-  labs(title = "(b) 2040 target (%)")
+  labs(title = "(b) 2040 target (%)") +
+  theme(plot.title = element_text(hjust=1))
+  #theme(plot.title = element_text(margin=margin(l=-100)))
 
@@
   geom_line(data=ETS_price,aes(x=Date, y=Price),size=0.5, color = "#000000") +
+  geom_label_repel(data=ETS_price %>% filter(Date == "2008-09-19"), aes(x=Date, y=Price, label = variable),
+                     #label = "ETS Price",
+                     nudge_x = 0,
+                     nudge_y = 250,
+                     segment.square = TRUE,
+                     point.padding = 0,
+                     hjust = 0,
+                     direction="y",
+                     size = geomText.size*0.8) +
   scale_x_date(date_labels = "%Y") +
@@
 plotData <- df %>% 
-  filter(region %in% c("EU27","DEU","FRA"), period >= 2020, period <= 2060, scenario  == mainScen, variable %in% unlist(vars)) %>% 
+  filter(region %in% c("EU27","DEU","FRA"), period >= 2020, period <= 2050, scenario  == mainScen, variable %in% unlist(vars)) %>% 
   mutate(variable = factor(variable, levels=rev(vars)),
@@
   theme_doubleColumn() +
-  scale_x_continuous(breaks=c(2020,2040,2060)) +
+  scale_x_continuous(breaks=c(2020,2030,2040,2050)) +
   scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
@@
   scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
-  guides(fill=guide_legend(nrow=2,override.aes = list(alpha=1))) +
+  guides(fill=guide_legend(nrow=3,override.aes = list(alpha=1))) +
   theme(#legend.text = element_text(size = theme.double.text.size),
@@
   theme(legend.title = element_blank()) +
-  theme(#legend.text = element_text(size = theme.double.text.size*0.7),
+  theme(legend.text = element_text(size = theme.double.text.size*0.8),
         #legend.key.height = unit(0.7, "cm"),
@@
   #  theme(plot.title = element_text(size = 1.2*theme.double.text.size)) +
-  labs(title = paste0("(a) Energy and non-energy use per sector and carrier (", unique(plotData$unit), ")")) +
-  theme(plot.title = element_text(hjust=1))
-
-ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 4a.
+  labs(title = paste0("(a) Energy and non-energy use\nper sector and carrier (", unique(plotData$unit), ")")) +
+  theme(plot.title = element_text(hjust=0))
+
+#ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 4a.
 Final energy demand per sector and carrier.svg"), g[["Supplementary Figure 4a.
 Final energy demand per sector and carrier"]] , device="svg", width = 6, height = 8, dpi=100, units = "in")
-ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 4a.
+#ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 4a.
 Final energy demand per sector and carrier.png"), g[["Supplementary Figure 4a.
@@
   #  theme(plot.title = element_text(size = 1.2*theme.double.text.size)) +
-  labs(title = paste0("(b) Energy and non-energy use per fossil content (", unique(plotData$unit), ")")) +
-  theme(plot.title = element_text(hjust=1))
+  labs(title = paste0("(b) Energy and non-energy use\nper fossil content (", unique(plotData$unit), ")")) +
+  theme(plot.title = element_text(hjust=0))
 

### 2025-04-10 report_plotlyCharts.Rmd
release candidate - revision 1

@@
 
+# df_beforeFilter <- df_beforeFilter %>%
+#   filter(tgt2030 != 59)
+# df <- df %>%
+#   filter(tgt2030 != 59)
+
 ```
@@
     geom_point(size = 3, aes(shape = lim, fill = scenario)) +
-    geom_line(data=ETS_price,aes(x=Date, y=Price),size=0.5, color = "#000000") +
+    geom_line(data=ETS_price,aes(x=Date, y=Price),linewidth=0.5, color = "#000000") +
     scale_x_date(date_labels = "%Y") +
@@
   plotData <- df_beforeFilter %>% 
-    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable == "FE") %>%
+    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable == "FE|w/o Non-energy Use w/o Bunkers") %>%
     mutate(value = round(value,2))
 
-  h <- hist %>% filter(model == "IEA", region == "EU27", variable == "FE", period >= 2005) %>% drop_na(value) %>% filter(value != 0) %>%
-    mutate(value = round(value,2))
+  #h <- hist %>% filter(model == "IEA", region == "EU27", variable == "FE", period >= 2005) %>% drop_na(value) %>% filter(value != 0) %>%
+  #  mutate(value = round(value,2))
+
+  h <- addHist$FE_eurostat %>%
+    mutate(value = round(as.numeric(value),2),
+           scenario = "historical",
+           model = "Eurostat")
+
+  factor <- h %>% filter(period %in% c(2018:2022)) %>% summarize (value = mean(value)) %>% pull(value) / plotData %>% filter(period == 2020, scenario == "Nzero_57_bio7p5") %>% pull(value)
+
+  plotData <- plotData %>% mutate(value = factor*value)
 
@@
 
-  g[["Emissions"]][["plotly"]]
+  g[["finalEnergy"]][["plotly"]]
 
@@
 
+---
+
+<!-- # Emission reduction -->
+
+<!-- ```{r chart_emissions, echo=FALSE, include = FALSE} -->
+
+<!--   h <- refEmi %>% filter(variable == "Emissions with LULUCF and with international transport", region == "EU27", pollutant == "All greenhouse gases - (CO2 equivalent)") %>% ungroup() %>% select(region,variable,period,value) %>% -->
+<!--     mutate(scenario = "historical") %>% -->
+<!--     mutate(value = round(value,2)) -->
+
+<!--   plotData <- df_beforeFilter %>%  -->
+<!--     filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>% -->
+<!--     calc_addVariable( "`emiIntTrnsp`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr") %>% -->
+<!--     calc_addVariable( "`emiIntraEU`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr") %>% -->
+<!--     filter(variable %in% c("emiIntTrnsp","emiIntraEU")) %>% -->
+<!--     pivot_wider(names_from = variable, values_from = value) %>% -->
+<!--     mutate(ref_emiIntTrnsp = tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference), -->
+<!--            ref_emiIntraEU = tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)) %>% -->
+<!--     mutate(red_emiIntTrnsp = emiIntTrnsp/ref_emiIntTrnsp, -->
+<!--            red_emiIntraEU = emiIntraEU/ref_emiIntraEU) %>% -->
+<!--     mutate(value = emiIntTrnsp, -->
+<!--            reduction = ifelse(period >= 2045, red_emiIntTrnsp, red_emiIntraEU)) %>% -->
+<!--     mutate(text = paste0("Emissions: ", round(value), " Mt CO2/yr", "\nReduction: ", round(1-reduction,3)*100, "%", "\nPeriod: ", period, "\nScenario: ", scenario, "\nTarget 2030: ", tgt2030, "%", "\nEfficiency: ", efficiency, "\nBiomass Limit: ", bioLim, "\nSensititivy limit: ", lim)) %>% -->
+<!--     mutate(value = round(value,2)) -->
+
+<!--   g[["Emission reduction"]][["ggplot"]] <- ggplot(plotData,aes(x=period,y=1-reduction,group = scenario)) + -->
+<!--     geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) + -->
+<!--     geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") + -->
+<!--     geom_line(size = 0.5, aes(linetype=tgt2030, color = scenario, text = text)) + -->
+<!--     #geom_point(size = 3, aes(shape = lim, fill = scenario, text = text)) + -->
+<!--     #geom_line(data=h,size=0.5, color = "#000000") + -->
+<!--     scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) +   scale_color_manual(values = scenarioColor, guide = guide_legend(nrow =4, byrow = T, order = 2, override.aes = list(linewidth = 1.5))) +  -->
+<!--     scale_fill_manual(values = scenarioFill, guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) + -->
+<!--     scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) + -->
+<!--     theme_doubleColumn() + -->
+<!--     theme(strip.text.y = element_blank()) + -->
+<!--     #guides(fill = guide_legend(nrow = 2, byrow = T)) + -->
+<!--     theme(legend.text=element_text(size=theme.single.text.size)) + -->
+<!--     theme(legend.key.height = unit(0.7, "cm"), -->
+<!--           legend.key.width = unit(2,"cm")) + -->
+<!--     theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical") +  -->
+<!--     #theme(legend.key.width = unit(2,"cm")) + -->
+<!--     theme(legend.spacing.y = unit(0.5, "lines")) +  -->
+<!--     theme(legend.position = "none") + -->
+<!--     scale_x_continuous(breaks = seq(1990,2060,10)) -->
+
+<!--   g[["Emission reduction"]][["plotly"]] <- ggplotly(g[["Emission reduction"]][["ggplot"]],tooltip = c("text")) %>% layout(autosize = TRUE) -->
+
+<!--   plotly2js( -->
+<!--     g[["Emission reduction"]][["plotly"]], -->
+<!--     div.id = "emission reduction", output.html = TRUE, output.file = "emission reduction.js",  -->
+<!--     output.dir = jsOutputFolder, output.url = paste0(jsOutputFolder, "/emission reduction.html")) -->
+
+<!-- ``` -->
+
+<!-- ```{r, echo=FALSE, fig.width=8, fig.height=6} -->
+
+<!--   g[["Emission reduction"]][["plotly"]] -->
+
+<!-- ``` -->
+
 <!-- # # Final Energy -->

### 2025-04-10 R/aesthetics.R

@@ -1,7 +1,7 @@
 
 # Aestethics
 
-baseTextSize <- 2
+baseTextSize <- 3
 
 options <- list()
 options$aesthetics <- list(
@@ -193,14 +193,16 @@ options$aesthetics <- list(
 
 # Theme
 
-theme.single.text.size = 15
+text_size <- 20 #15
+
+theme.single.text.size = text_size
 geom.text.single.size = theme.single.text.size/.pt
 
-defaultText_singleColumn <- theme_minimal(base_size = 30)[["text"]] 
+defaultText_singleColumn <- theme_minimal(base_size = text_size*2)[["text"]] 
 
 #themes
 theme_singleColumn <- function(){
-  theme_minimal(base_size = 30) +
+  theme_minimal(base_size = text_size*2) +
     theme(
       legend.position="bottom",
       legend.title = element_blank(),
@@ -212,7 +214,10 @@ theme_singleColumn <- function(){
       #axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 10)),
       legend.key.height = unit(0.7, "cm"),
       legend.key.width = unit(0.7,"cm"),
-      legend.spacing.y = unit(0.1, 'cm')
+      legend.spacing.y = unit(0.1, 'cm'),
+      panel.background = element_rect(fill="#FFFFFF", color = NA),
+      plot.background = element_rect(fill="#FFFFFF", color = NA)#,
+      #strip.text.x = element_text(size = textSize.double)
       #panel.spacing = unit(3, "lines"),
       #plot.title = element_text(size = 0.75*theme.single.text.size, face = "plain"),
       #strip.text.x = element_text(size = 1.25*theme.single.text.size)
@@ -223,13 +228,13 @@ theme_singleColumn <- function(){
 #geom.text.double.size = theme.double.text.size/.pt
 #defaultText_doubleColumn <- theme_minimal(base_size = 25)[["text"]] 
 
-textSize.double = 15
+textSize.double = text_size
 geomText.size = textSize.double/.pt
 
 theme_doubleColumn <- function(){
   theme_minimal(base_size = textSize.double) +
     theme(
-      plot.title = element_text(size=15),
+      plot.title = element_text(size=textSize.double),
       legend.position="bottom",
       legend.title = element_blank(),
       axis.title.x=element_blank(),
@@ -244,7 +249,10 @@ theme_doubleColumn <- function(){
[…]

### 2025-04-10 R/calcResults.R

@@ -160,20 +160,19 @@ electricity_demand_upscale <- data.frame(
   )
 )
 
-
 electricity_share_in_FE <- data.frame(
   electricity_share_in_FE = c("2030","2040"),
   reference_value=c(
-    round(df %>% filter(region == "EU27", period == 2030, variable %in% c("Final Energy|Electricity Share"), scenario == mainScen) %>% pull(value)*100),
-    round(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share"), scenario == mainScen) %>% pull(value)*100)
+    round(df %>% filter(region == "EU27", period == 2030, variable %in% c("Final Energy|w/o Bunkers|w/o Non-energy Use|Electricity Share"), scenario == mainScen) %>% pull(value)*100),
+    round(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|w/o Bunkers|w/o Non-energy Use|Electricity Share"), scenario == mainScen) %>% pull(value)*100)
   ),
   min=c(
-    round(min(df %>% filter(region == "EU27", period == 2030, variable %in% c("Final Energy|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100)),
-    round(min(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100))
+    round(min(df %>% filter(region == "EU27", period == 2030, variable %in% c("Final Energy|w/o Bunkers|w/o Non-energy Use|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100)),
+    round(min(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|w/o Bunkers|w/o Non-energy Use|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100))
   ),
   max=c(
-    round(max(df %>% filter(region == "EU27", period == 2030, variable %in% c("Final Energy|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100)),
[…]

### 2025-04-10 R/harmonizeData.R

@@ -10,6 +10,10 @@ harmonizeData <- function(data,scaleFactor){ #,nzero=NULL
   data[data$variable %in% grep("Emi\\|", unique(data$variable), value = TRUE),]$value <- data[data$variable %in% grep("Emi\\|", unique(data$variable), value = TRUE),]$value / scaleFactor
   data[data$variable %in% grep("Carbon Management\\|", unique(data$variable), value = TRUE),]$value <- data[data$variable %in% grep("Carbon Management\\|", unique(data$variable), value = TRUE),]$value / scaleFactor
   
+  #EUregions <- c("DEU","ECE","ECS","ENC","ESC","ESW","EWN","FRA","EU27")
+  #data[data$variable %in% grep("Emi\\|", unique(data$variable), value = TRUE) & data$region %in% EUregions & data$scenario != "Npi",]$value <- data[data$variable %in% grep("Emi\\|", unique(data$variable), value = TRUE) & data$region %in% EUregions & data$scenario != "Npi",]$value  / scaleFactor
+  #data[data$variable %in% grep("Carbon Management\\|", unique(data$variable), value = TRUE) & data$region %in% EUregions & data$scenario != "Npi",]$value <- data[data$variable %in% grep("Carbon Management\\|", unique(data$variable), value = TRUE) & data$region %in% EUregions & data$scenario != "Npi",]$value  / scaleFactor
+  
   # #copying prices from NZero_bioLim7p5 to other scenarios
   # if (is.null(nzero)){
   #   nzero <- data 

### 2025-04-10 R/loadData.R

@@ -69,6 +69,11 @@ addVariables <- function(data){
 
   data <- rbind(data,data %>% calc_addVariable("`Emi|CO2|CDR|Other CDR`" = "`Emi|CO2|CDR|DACCS` + `Emi|CO2|CDR|EW` + `Emi|CO2|CDR|Industry CCS|Synthetic Fuels`", units = "Mt CO2/yr", only.new=T))
 
+  data <- rbind(data,data %>% calc_addVariable("`Final Energy|w/o Bunkers|w/o Non-energy Use|Electricity Share`" = "(`FE|Electricity` - `FE|Transport|Bunkers|Electricity`) / (`FE` - `FE|Transport|Bunkers` - `FE|Non-energy Use`)", units = "%", only.new=T))
+  data <- rbind(data,data %>% calc_addVariable("`Final Energy|w/o Bunkers|w/o Non-energy Use|Transport|Electricity Share`" = "(`FE|Transport|Electricity` - `FE|Transport|Bunkers|Electricity`) / (`FE|Transport` - `FE|Transport|Bunkers`)", units = "%", only.new=T))
+  data <- rbind(data,data %>% calc_addVariable("`Final Energy|w/o Bunkers|w/o Non-energy Use|Industry|Electricity Share`"  = "`FE|Industry|Electricity`  / (`FE|Industry` - `FE|Non-energy Use`)", units = "%", only.new=T))
+  data <- rbind(data,data %>% calc_addVariable("`Final Energy|w/o Bunkers|w/o Non-energy Use|Buildings|Electricity Share`" = "`FE|Buildings|Electricity` / `FE|Buildings`", units = "%", only.new=T))
+
   data <- rbind(data,data %>% calc_addVariable("`Final Energy|Electricity Share`" = "`FE|Electricity` / `FE`", units = "%", only.new=T))
   data <- rbind(data,data %>% calc_addVariable("`Final Energy|Transport|Electricity Share`" = "`FE|Transport|Electricity` / `FE|Transport`", units = "%", only.new=T))
   data <- rbind(data,data %>% calc_addVariable("`Final Energy|Industry|Electricity Share`"  = "`FE|Industry|Electricity`  / `FE|Industry`", units = "%", only.new=T))

### 2025-04-10 R/loadHistoricalData.R

@@ -42,6 +42,10 @@ loadAdditionalHistoricalData <- function(path){
     addHist$eeaEmissions <- rbind(addHist$eeaEmissions,
                                   addHist$eeaEmissions %>% filter(Sector_name == "1.D.1 - International Bunkers") %>% mutate(emissions = emissions*0.35, Sector_name = "Intra-EU International Aviation", Sector_code = "-", Parent_sector_code = "-"))
 
+    addHist$FE_eurostat <- read.csv2("./hist/nrg_bal_c_page_spreadsheet.csv", stringsAsFactors = FALSE,check.names=FALSE) %>%
+      mutate(period = as.numeric(period),
+             value = as.numeric(value))
+      
     saveRDS(addHist,paste0(path,"/addHist.rds"))
   } else {
     addHist <- readRDS(paste0(path,"/addHist.rds"))

### 2025-04-10 calcHarmonizedTargets.R

@@ -1,10 +1,14 @@
 
 library(remind2)
+library(tidyr)
 library(dplyr)
+library(quitte)
 
 #Check latest results folder and create output folder for reports
 folders <- file.info(list.files(path="./data", full.names = T))
 dataFolder <- folders %>% tibble::rownames_to_column(var = "path") %>% arrange(desc(path)) %>% slice(1) %>% pull(path)
+
+#dataFolder
 
 # load npi mif
 npiMifFile <- list.files(path=dataFolder, pattern="*Npi.mif", full.names=TRUE, recursive=FALSE)
@@ -24,6 +28,8 @@ tmpdf$scenario <- gsub("^0c_","",tmpdf$scenario)
 tmpdf$scenario <- gsub("_EU27","",tmpdf$scenario)
 
 dfFull <- tmpdf
+
+source("./R/loadHistoricalData.R")
 
 source("./R/loadReferenceEmissions.R")
 

### 2025-04-10 createReports.R

@@ -16,6 +16,10 @@ rmarkdown::render("./report_paperCharts.Rmd", output_file = paste0(outFolder, "/
 
 # Create plotly charts for the Sensitivity Iterative Explorer
 rmarkdown::render("./report_plotlyCharts.Rmd", output_file = paste0(outFolder, "/report_plotlyCharts.html"))
+
+## Create plotly charts for the Sensitivity Iterative Explorer
+#rmarkdown::render("./report_plotlyCharts_darkTheme.Rmd", output_file = paste0(outFolder, "/report_plotlyCharts_darkTheme.html"))
+
 # Copy html, js and css files to the Sensitivity Iterative Explorer output folder 
 file.copy(list("./publish/report_sensitivityExplorer/index.html","./publish/report_sensitivityExplorer/script.js","./publish/report_sensitivityExplorer/style.css"), paste0(outFolder, "/report_sensitivityExplorer"), overwrite = TRUE)
 

### 2025-04-11 report_additionalCharts.Rmd
correcting currency conversion rate

@@
 dir.create(paste0(outChartsFolder, "/svg"), recursive = TRUE, showWarnings = FALSE)
+
+```
+
+<!-- units conversion -->
+
+```{r unitsConversion, echo=FALSE, include = FALSE}
+
+# conversion factors
+  USS2017_2_EURO2020 <- 0.9502 # 1 USD 2017 = 0.9502 EURO 2020
 
@@
     filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Price|Carbon") %>%
-    mutate(price_2030 = 1.17*value) %>%
+    mutate(price_2030 = USS2017_2_EURO2020*value) %>%
     select(scenario, price_2030),

### 2025-04-11 report_paperCharts.Rmd
correcting currency conversion rate

@@
   EJ2TWh <- 1/0.0036
+
+  USS2017_2_EURO2020 <- 0.9502 # 1 USD 2017 = 0.9502 EURO 2020
 
@@
   mutate(period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"),
-         value = 1.17*value)
+         value = USS2017_2_EURO2020*value)
 
@@
   mutate(variable = factor(variable, levels=vars),
-   value = 1.17*value) #%>% 
+   value = USS2017_2_EURO2020*value) #%>% 
  # arrange(factor(variable, levels = rev(vars)))

### 2025-04-11 report_plotlyCharts.Rmd
correcting currency conversion rate

@@
 
+<!-- units conversion -->
+
+```{r unitsConversion, echo=FALSE, include = FALSE}
+
+# conversion factors
+  USS2017_2_EURO2020 <- 0.9502 # 1 USD 2017 = 0.9502 EURO 2020
+
+```
+
 <!-- Initializing charts object -->
@@
     mutate(period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"),
-           value = 1.17*value) %>%
+           value = USS2017_2_EURO2020*value) %>%
     mutate(value = round(value,2))

### 2025-04-11 output/2024_12_11/report_sensitivityExplorer/charts/dac.js

@@ -9032,32 +9032,32 @@
   },
   "source": "A",
   "attrs": {
-    "35d4785a44c9": {
+    "35d44d4649a": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d42239490c": {
+    "35d412bb53aa": {
       "xintercept": {}
     },
-    "35d424a84c9b": {
+    "35d4713e447f": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "35d4677a6c17": {
+    "35d42dd3810": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     }
   },
-  "cur_data": "35d4785a44c9",
+  "cur_data": "35d44d4649a",
   "visdat": {
-    "35d4785a44c9": ["function (y) ", "x"],
-    "35d42239490c": ["function (y) ", "x"],
-    "35d424a84c9b": ["function (y) ", "x"],
-    "35d4677a6c17": ["function (y) ", "x"]
+    "35d44d4649a": ["function (y) ", "x"],
+    "35d412bb53aa": ["function (y) ", "x"],
+    "35d4713e447f": ["function (y) ", "x"],
+    "35d42dd3810": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 output/2024_12_11/report_sensitivityExplorer/charts/electricityShare.js

@@ -35978,41 +35978,41 @@
   },
   "source": "A",
   "attrs": {
-    "35d4407d4b18": {
+    "35d41c192c4c": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d43af92211": {
+    "35d426f07c13": {
       "xintercept": {}
     },
-    "35d473846e86": {
+    "35d4208a7b27": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "35d42698764d": {
+    "35d449cf28fb": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     },
-    "35d428b061f0": {
+    "35d41598d0c": {
       "x": {},
       "y": {}
     },
-    "35d4674f11cc": {
+    "35d42d3c7ade": {
       "y": {}
     }
   },
-  "cur_data": "35d4407d4b18",
+  "cur_data": "35d41c192c4c",
   "visdat": {
-    "35d4407d4b18": ["function (y) ", "x"],
-    "35d43af92211": ["function (y) ", "x"],
-    "35d473846e86": ["function (y) ", "x"],
-    "35d42698764d": ["function (y) ", "x"],
-    "35d428b061f0": ["function (y) ", "x"],
-    "35d4674f11cc": ["function (y) ", "x"]
+    "35d41c192c4c": ["function (y) ", "x"],
+    "35d426f07c13": ["function (y) ", "x"],
+    "35d4208a7b27": ["function (y) ", "x"],
+    "35d449cf28fb": ["function (y) ", "x"],
+    "35d41598d0c": ["function (y) ", "x"],
+    "35d42d3c7ade": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 output/2024_12_11/report_sensitivityExplorer/charts/finalEnergy.js

@@ -9050,37 +9050,37 @@
   },
   "source": "A",
   "attrs": {
-    "35d41fbd5566": {
+    "35d451893ecd": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d425861275": {
+    "35d45f4c18d": {
       "xintercept": {}
     },
-    "35d42ab1495b": {
+    "35d45b2f495d": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "35d411d1345a": {
+    "35d424fc67d7": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     },
-    "35d41c83fc6": {
+    "35d45127e4": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "35d41fbd5566",
+  "cur_data": "35d451893ecd",
   "visdat": {
-    "35d41fbd5566": ["function (y) ", "x"],
-    "35d425861275": ["function (y) ", "x"],
-    "35d42ab1495b": ["function (y) ", "x"],
-    "35d411d1345a": ["function (y) ", "x"],
-    "35d41c83fc6": ["function (y) ", "x"]
+    "35d451893ecd": ["function (y) ", "x"],
+    "35d45f4c18d": ["function (y) ", "x"],
+    "35d45b2f495d": ["function (y) ", "x"],
+    "35d424fc67d7": ["function (y) ", "x"],
+    "35d45127e4": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 publish/sensitivity_explorer/charts/beccs.js

@@ -9032,32 +9032,32 @@
   },
   "source": "A",
   "attrs": {
-    "35d4170918e6": {
+    "35d46f1eb4": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d462a658d": {
+    "35d43eeb369": {
       "xintercept": {}
     },
-    "35d466c0b08": {
+    "35d41d0b4845": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "35d462587953": {
+    "35d460a51eeb": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     }
   },
-  "cur_data": "35d4170918e6",
+  "cur_data": "35d46f1eb4",
   "visdat": {
-    "35d4170918e6": ["function (y) ", "x"],
-    "35d462a658d": ["function (y) ", "x"],
-    "35d466c0b08": ["function (y) ", "x"],
-    "35d462587953": ["function (y) ", "x"]
+    "35d46f1eb4": ["function (y) ", "x"],
+    "35d43eeb369": ["function (y) ", "x"],
+    "35d41d0b4845": ["function (y) ", "x"],
+    "35d460a51eeb": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 publish/sensitivity_explorer/charts/emissions.js

@@ -9050,39 +9050,39 @@
   },
   "source": "A",
   "attrs": {
-    "35d467325030": {
+    "35d4184244b0": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d44c042b01": {
+    "35d46d40369f": {
       "xintercept": {}
     },
-    "35d453344ed8": {
+    "35d435573d63": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {},
       "text": {}
     },
-    "35d448952445": {
+    "35d44d06712": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {},
       "text": {}
     },
-    "35d471bd3f47": {
+    "35d4665a51ef": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "35d467325030",
+  "cur_data": "35d4184244b0",
   "visdat": {
-    "35d467325030": ["function (y) ", "x"],
-    "35d44c042b01": ["function (y) ", "x"],
-    "35d453344ed8": ["function (y) ", "x"],
-    "35d448952445": ["function (y) ", "x"],
-    "35d471bd3f47": ["function (y) ", "x"]
+    "35d4184244b0": ["function (y) ", "x"],
+    "35d46d40369f": ["function (y) ", "x"],
+    "35d435573d63": ["function (y) ", "x"],
+    "35d44d06712": ["function (y) ", "x"],
+    "35d4665a51ef": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 publish/sensitivity_explorer/charts/hydrogen.js

@@ -44826,32 +44826,32 @@
   },
   "source": "A",
   "attrs": {
-    "35d4208ce56": {
+    "35d46c564f60": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d42ceb562e": {
+    "35d4f53492": {
       "xintercept": {}
     },
-    "35d422684c7a": {
+    "35d4721b6537": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "35d479836300": {
+    "35d46ee71ca2": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     }
   },
-  "cur_data": "35d4208ce56",
+  "cur_data": "35d46c564f60",
   "visdat": {
-    "35d4208ce56": ["function (y) ", "x"],
-    "35d42ceb562e": ["function (y) ", "x"],
-    "35d422684c7a": ["function (y) ", "x"],
-    "35d479836300": ["function (y) ", "x"]
+    "35d46c564f60": ["function (y) ", "x"],
+    "35d4f53492": ["function (y) ", "x"],
+    "35d4721b6537": ["function (y) ", "x"],
+    "35d46ee71ca2": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 publish/sensitivity_explorer/charts/primaryEnergy.js

@@ -35947,37 +35947,37 @@
   },
   "source": "A",
   "attrs": {
-    "35d426a438eb": {
+    "35d42ae599e": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d439465100": {
+    "35d42d8e14fa": {
       "xintercept": {}
     },
-    "35d4279f4499": {
+    "35d467944d99": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "35d427383b3f": {
+    "35d41d864503": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     },
-    "35d46c3d17f3": {
+    "35d4534928bc": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "35d426a438eb",
+  "cur_data": "35d42ae599e",
   "visdat": {
-    "35d426a438eb": ["function (y) ", "x"],
-    "35d439465100": ["function (y) ", "x"],
-    "35d4279f4499": ["function (y) ", "x"],
-    "35d427383b3f": ["function (y) ", "x"],
-    "35d46c3d17f3": ["function (y) ", "x"]
+    "35d42ae599e": ["function (y) ", "x"],
+    "35d42d8e14fa": ["function (y) ", "x"],
+    "35d467944d99": ["function (y) ", "x"],
+    "35d41d864503": ["function (y) ", "x"],
+    "35d4534928bc": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 report_paperCharts.Rmd
updating reports with new currency conversion files

@@
   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) +
+  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=-10, b=20))) +
   theme(strip.clip = "off")#+

### 2025-04-11 output/2024_12_11/report_sensitivityExplorer/charts/carbonPrice.js

@@ -9050,37 +9050,37 @@
   },
   "source": "A",
   "attrs": {
-    "35d4722f334c": {
+    "35d4120e3f04": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d43fcf1af3": {
+    "35d43dcb6dba": {
       "xintercept": {}
     },
-    "35d422d44573": {
+    "35d44ecf400f": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "35d4102e1ef6": {
+    "35d4610f5b18": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     },
-    "35d42647645b": {
+    "35d431941168": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "35d4722f334c",
+  "cur_data": "35d4120e3f04",
   "visdat": {
-    "35d4722f334c": ["function (y) ", "x"],
-    "35d43fcf1af3": ["function (y) ", "x"],
-    "35d422d44573": ["function (y) ", "x"],
-    "35d4102e1ef6": ["function (y) ", "x"],
-    "35d42647645b": ["function (y) ", "x"]
+    "35d4120e3f04": ["function (y) ", "x"],
+    "35d43dcb6dba": ["function (y) ", "x"],
+    "35d44ecf400f": ["function (y) ", "x"],
+    "35d4610f5b18": ["function (y) ", "x"],
+    "35d431941168": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 output/2024_12_11/report_sensitivityExplorer/charts/dac.js

@@ -9032,32 +9032,32 @@
   },
   "source": "A",
   "attrs": {
-    "35d44d4649a": {
+    "35d45eb1fbc": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d412bb53aa": {
+    "35d44ab32274": {
       "xintercept": {}
     },
-    "35d4713e447f": {
+    "35d443a8270e": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "35d42dd3810": {
+    "35d42eb560c": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     }
   },
-  "cur_data": "35d44d4649a",
+  "cur_data": "35d45eb1fbc",
   "visdat": {
-    "35d44d4649a": ["function (y) ", "x"],
-    "35d412bb53aa": ["function (y) ", "x"],
-    "35d4713e447f": ["function (y) ", "x"],
-    "35d42dd3810": ["function (y) ", "x"]
+    "35d45eb1fbc": ["function (y) ", "x"],
+    "35d44ab32274": ["function (y) ", "x"],
+    "35d443a8270e": ["function (y) ", "x"],
+    "35d42eb560c": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 output/2024_12_11/report_sensitivityExplorer/charts/electricityShare.js

@@ -35607,10 +35607,10 @@
   ],
   "layout": {
     "margin": {
-      "t": 63.820672478206731,
-      "r": 13.283520132835205,
-      "b": 75.716064757160652,
-      "l": 62.432544624325445
+      "t": 57.79232337333724,
+      "r": 13.283520132835198,
+      "b": 69.687715652291175,
+      "l": 62.432544624325438
     },
     "plot_bgcolor": "rgba(255,255,255,1)",
     "paper_bgcolor": "rgba(255,255,255,1)",
@@ -35620,7 +35620,7 @@
       "size": 26.567040265670411
     },
     "xaxis": {
-      "domain": [0, 0.48846916655135836],
+      "domain": [0, 0.48973981452149701],
       "automargin": true,
       "type": "linear",
       "autorange": false,
@@ -35654,7 +35654,7 @@
       "hoverformat": ".2f"
     },
     "yaxis": {
-      "domain": [0.55996033393293665, 1],
+      "domain": [0.54124659913858064, 1],
       "automargin": true,
       "type": "linear",
       "autorange": false,
@@ -35667,7 +35667,7 @@
       "nticks": null,
       "ticks": "",
       "tickcolor": null,
-      "ticklen": 6.6417600664176026,
+      "ticklen": 6.6417600664175991,
       "tickwidth": 0,
       "showticklabels": true,
       "tickfont": {
@@ -35699,8 +35699,8 @@
         "yref": "paper",
         "xref": "paper",
         "x0": 0,
-        "x1": 0.48846916655135836,
-        "y0": 0.55996033393293665,
+        "x1": 0.48973981452149701,
+        "y0": 0.54124659913858064,
         "y1": 1
       },
       {
@@ -35714,7 +35714,7 @@
         "yref": "paper",
         "xref": "paper",
         "x0": 0,
-        "x1": 0.48846916655135836,
+        "x1": 0.48973981452149701,
         "y0": 0,
         "y1": 42.507264425072641,
         "yanchor": 1,
@@ -35730,9 +35730,9 @@
         },
         "yref": "paper",
         "xref": "paper",
-        "x0": 0.5115308334486417,
+        "x0": 0.51026018547850294,
         "x1": 1,
-        "y0": 0.55996033393293665,
+        "y0": 0.54124659913858064,
         "y1": 1
       },
       {
@@ -35745,7 +35745,7 @@
         },
         "yref": "paper",
[…]

### 2025-04-11 output/2024_12_11/report_sensitivityExplorer/charts/hydrogen.js

@@ -44826,32 +44826,32 @@
   },
   "source": "A",
   "attrs": {
-    "35d46c564f60": {
+    "35d41f6d4f33": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d4f53492": {
+    "35d42b511720": {
       "xintercept": {}
     },
-    "35d4721b6537": {
+    "35d483f1f92": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "35d46ee71ca2": {
+    "35d4c613618": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     }
   },
-  "cur_data": "35d46c564f60",
+  "cur_data": "35d41f6d4f33",
   "visdat": {
-    "35d46c564f60": ["function (y) ", "x"],
-    "35d4f53492": ["function (y) ", "x"],
-    "35d4721b6537": ["function (y) ", "x"],
-    "35d46ee71ca2": ["function (y) ", "x"]
+    "35d41f6d4f33": ["function (y) ", "x"],
+    "35d42b511720": ["function (y) ", "x"],
+    "35d483f1f92": ["function (y) ", "x"],
+    "35d4c613618": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 output/2024_12_11/report_sensitivityExplorer/charts/primaryEnergy.js

@@ -35947,37 +35947,37 @@
   },
   "source": "A",
   "attrs": {
-    "35d42ae599e": {
+    "35d4347a3ddd": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d42d8e14fa": {
+    "35d457ea2379": {
       "xintercept": {}
     },
-    "35d467944d99": {
+    "35d45692879": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "35d41d864503": {
+    "35d46a3130a9": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     },
-    "35d4534928bc": {
+    "35d42ef8675f": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "35d42ae599e",
+  "cur_data": "35d4347a3ddd",
   "visdat": {
-    "35d42ae599e": ["function (y) ", "x"],
-    "35d42d8e14fa": ["function (y) ", "x"],
-    "35d467944d99": ["function (y) ", "x"],
-    "35d41d864503": ["function (y) ", "x"],
-    "35d4534928bc": ["function (y) ", "x"]
+    "35d4347a3ddd": ["function (y) ", "x"],
+    "35d457ea2379": ["function (y) ", "x"],
+    "35d45692879": ["function (y) ", "x"],
+    "35d46a3130a9": ["function (y) ", "x"],
+    "35d42ef8675f": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 publish/sensitivity_explorer/charts/beccs.js

@@ -9032,32 +9032,32 @@
   },
   "source": "A",
   "attrs": {
-    "35d46f1eb4": {
+    "35d4a731159": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d43eeb369": {
+    "35d458b82701": {
       "xintercept": {}
     },
-    "35d41d0b4845": {
+    "35d4181410a5": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "35d460a51eeb": {
+    "35d4636970d2": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     }
   },
-  "cur_data": "35d46f1eb4",
+  "cur_data": "35d4a731159",
   "visdat": {
-    "35d46f1eb4": ["function (y) ", "x"],
-    "35d43eeb369": ["function (y) ", "x"],
-    "35d41d0b4845": ["function (y) ", "x"],
-    "35d460a51eeb": ["function (y) ", "x"]
+    "35d4a731159": ["function (y) ", "x"],
+    "35d458b82701": ["function (y) ", "x"],
+    "35d4181410a5": ["function (y) ", "x"],
+    "35d4636970d2": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 publish/sensitivity_explorer/charts/emissions.js

@@ -9050,39 +9050,39 @@
   },
   "source": "A",
   "attrs": {
-    "35d4184244b0": {
+    "35d43f8c6ffe": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d46d40369f": {
+    "35d410ff2ca5": {
       "xintercept": {}
     },
-    "35d435573d63": {
+    "35d42063642d": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {},
       "text": {}
     },
-    "35d44d06712": {
+    "35d4a616732": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {},
       "text": {}
     },
-    "35d4665a51ef": {
+    "35d4e0b3c34": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "35d4184244b0",
+  "cur_data": "35d43f8c6ffe",
   "visdat": {
-    "35d4184244b0": ["function (y) ", "x"],
-    "35d46d40369f": ["function (y) ", "x"],
-    "35d435573d63": ["function (y) ", "x"],
-    "35d44d06712": ["function (y) ", "x"],
-    "35d4665a51ef": ["function (y) ", "x"]
+    "35d43f8c6ffe": ["function (y) ", "x"],
+    "35d410ff2ca5": ["function (y) ", "x"],
+    "35d42063642d": ["function (y) ", "x"],
+    "35d4a616732": ["function (y) ", "x"],
+    "35d4e0b3c34": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 publish/sensitivity_explorer/charts/finalEnergy.js

@@ -9050,37 +9050,37 @@
   },
   "source": "A",
   "attrs": {
-    "35d451893ecd": {
+    "35d47b33cb1": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d45f4c18d": {
+    "35d462e57e09": {
       "xintercept": {}
     },
-    "35d45b2f495d": {
+    "35d4330d22e8": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "35d424fc67d7": {
+    "35d425147e45": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     },
-    "35d45127e4": {
+    "35d45f6b64f2": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "35d451893ecd",
+  "cur_data": "35d47b33cb1",
   "visdat": {
-    "35d451893ecd": ["function (y) ", "x"],
-    "35d45f4c18d": ["function (y) ", "x"],
-    "35d45b2f495d": ["function (y) ", "x"],
-    "35d424fc67d7": ["function (y) ", "x"],
-    "35d45127e4": ["function (y) ", "x"]
+    "35d47b33cb1": ["function (y) ", "x"],
+    "35d462e57e09": ["function (y) ", "x"],
+    "35d4330d22e8": ["function (y) ", "x"],
+    "35d425147e45": ["function (y) ", "x"],
+    "35d45f6b64f2": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 report_additionalCharts.Rmd
updating monetary units to euro 2025

@@
   USS2017_2_EURO2020 <- 0.9502 # 1 USD 2017 = 0.9502 EURO 2020
+
+  USS2017_2_EURO2025 <- 1.212 # 1 USD 2017 = 1.212 EURO 2020 (1 US$2017 = 1.30 * 0.932642 €2025 = 1.212 €2025)
+  # exchange rate = average of February 28, March 31, April 11, 2025 (0.960138 +  0.925734 + 0.912056)/3 = 0.932642 https://www.ofx.com/en-au/forex-news/historical-exchange-rates/yearly-average-rates/
+  # CPI -> 1 $2017 = 1.30$2025 -> https://www.in2013dollars.com/us/inflation/2017?amount=1
+
+  currencyConversion <- USS2017_2_EURO2025
 
@@
     filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Price|Carbon") %>%
-    mutate(price_2030 = USS2017_2_EURO2020*value) %>%
+    mutate(price_2030 = currencyConversion*value) %>%
     select(scenario, price_2030),

### 2025-04-11 report_paperCharts.Rmd
updating monetary units to euro 2025

@@
   mutate(period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"),
-         value = USS2017_2_EURO2020*value)
+         value = currencyConversion*value)
 
@@
   mutate(variable = factor(variable, levels=vars),
-   value = USS2017_2_EURO2020*value) #%>% 
+   value = currencyConversion*value) #%>% 
  # arrange(factor(variable, levels = rev(vars)))

### 2025-04-11 report_plotlyCharts.Rmd
updating monetary units to euro 2025

@@
 
+  USS2017_2_EURO2025 <- 1.212 # 1 USD 2017 = 1.212 EURO 2020 (1 US$2017 = 1.30 * 0.932642 €2025 = 1.212 €2025)
+  # exchange rate = average of February 28, March 31, April 11, 2025 (0.960138 +  0.925734 + 0.912056)/3 = 0.932642 https://www.ofx.com/en-au/forex-news/historical-exchange-rates/yearly-average-rates/
+  # CPI -> 1 $2017 = 1.30$2025 -> https://www.in2013dollars.com/us/inflation/2017?amount=1
+
+  currencyConversion <- USS2017_2_EURO2025
+
 ```
@@
     mutate(period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"),
-           value = USS2017_2_EURO2020*value) %>%
+           value = currencyConversion*value) %>%
     mutate(value = round(value,2))

### 2025-04-11 output/2024_12_11/report_sensitivityExplorer/charts/dac.js

@@ -9032,32 +9032,32 @@
   },
   "source": "A",
   "attrs": {
-    "35d45eb1fbc": {
+    "4b5464a01487": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d44ab32274": {
+    "4b541181183": {
       "xintercept": {}
     },
-    "35d443a8270e": {
+    "4b549b84303": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "35d42eb560c": {
+    "4b5442f164d8": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     }
   },
-  "cur_data": "35d45eb1fbc",
+  "cur_data": "4b5464a01487",
   "visdat": {
-    "35d45eb1fbc": ["function (y) ", "x"],
-    "35d44ab32274": ["function (y) ", "x"],
-    "35d443a8270e": ["function (y) ", "x"],
-    "35d42eb560c": ["function (y) ", "x"]
+    "4b5464a01487": ["function (y) ", "x"],
+    "4b541181183": ["function (y) ", "x"],
+    "4b549b84303": ["function (y) ", "x"],
+    "4b5442f164d8": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 output/2024_12_11/report_sensitivityExplorer/charts/electricityShare.js

@@ -35607,10 +35607,10 @@
   ],
   "layout": {
     "margin": {
-      "t": 57.79232337333724,
-      "r": 13.283520132835198,
-      "b": 69.687715652291175,
-      "l": 62.432544624325438
+      "t": 63.820672478206731,
+      "r": 13.283520132835205,
+      "b": 75.716064757160652,
+      "l": 62.432544624325445
     },
     "plot_bgcolor": "rgba(255,255,255,1)",
     "paper_bgcolor": "rgba(255,255,255,1)",
@@ -35620,7 +35620,7 @@
       "size": 26.567040265670411
     },
     "xaxis": {
-      "domain": [0, 0.48973981452149701],
+      "domain": [0, 0.48846916655135836],
       "automargin": true,
       "type": "linear",
       "autorange": false,
@@ -35654,7 +35654,7 @@
       "hoverformat": ".2f"
     },
     "yaxis": {
-      "domain": [0.54124659913858064, 1],
+      "domain": [0.55996033393293665, 1],
       "automargin": true,
       "type": "linear",
       "autorange": false,
@@ -35667,7 +35667,7 @@
       "nticks": null,
       "ticks": "",
       "tickcolor": null,
-      "ticklen": 6.6417600664175991,
+      "ticklen": 6.6417600664176026,
       "tickwidth": 0,
       "showticklabels": true,
       "tickfont": {
@@ -35699,8 +35699,8 @@
         "yref": "paper",
         "xref": "paper",
         "x0": 0,
-        "x1": 0.48973981452149701,
-        "y0": 0.54124659913858064,
+        "x1": 0.48846916655135836,
+        "y0": 0.55996033393293665,
         "y1": 1
       },
       {
@@ -35714,7 +35714,7 @@
         "yref": "paper",
         "xref": "paper",
         "x0": 0,
-        "x1": 0.48973981452149701,
+        "x1": 0.48846916655135836,
         "y0": 0,
         "y1": 42.507264425072641,
         "yanchor": 1,
@@ -35730,9 +35730,9 @@
         },
         "yref": "paper",
         "xref": "paper",
-        "x0": 0.51026018547850294,
+        "x0": 0.5115308334486417,
         "x1": 1,
-        "y0": 0.54124659913858064,
+        "y0": 0.55996033393293665,
         "y1": 1
       },
       {
@@ -35745,7 +35745,7 @@
         },
         "yref": "paper",
[…]

### 2025-04-11 output/2024_12_11/report_sensitivityExplorer/charts/finalEnergy.js

@@ -9050,37 +9050,37 @@
   },
   "source": "A",
   "attrs": {
-    "35d47b33cb1": {
+    "4b54797a4027": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d462e57e09": {
+    "4b547a001807": {
       "xintercept": {}
     },
-    "35d4330d22e8": {
+    "4b545ead3a7": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "35d425147e45": {
+    "4b5468f8119d": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     },
-    "35d45f6b64f2": {
+    "4b546c2d1dd4": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "35d47b33cb1",
+  "cur_data": "4b54797a4027",
   "visdat": {
-    "35d47b33cb1": ["function (y) ", "x"],
-    "35d462e57e09": ["function (y) ", "x"],
-    "35d4330d22e8": ["function (y) ", "x"],
-    "35d425147e45": ["function (y) ", "x"],
-    "35d45f6b64f2": ["function (y) ", "x"]
+    "4b54797a4027": ["function (y) ", "x"],
+    "4b547a001807": ["function (y) ", "x"],
+    "4b545ead3a7": ["function (y) ", "x"],
+    "4b5468f8119d": ["function (y) ", "x"],
+    "4b546c2d1dd4": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 publish/sensitivity_explorer/charts/beccs.js

@@ -9032,32 +9032,32 @@
   },
   "source": "A",
   "attrs": {
-    "35d4a731159": {
+    "4b542d80aa6": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d458b82701": {
+    "4b5418502757": {
       "xintercept": {}
     },
-    "35d4181410a5": {
+    "4b54101958d7": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "35d4636970d2": {
+    "4b547cb72640": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     }
   },
-  "cur_data": "35d4a731159",
+  "cur_data": "4b542d80aa6",
   "visdat": {
-    "35d4a731159": ["function (y) ", "x"],
-    "35d458b82701": ["function (y) ", "x"],
-    "35d4181410a5": ["function (y) ", "x"],
-    "35d4636970d2": ["function (y) ", "x"]
+    "4b542d80aa6": ["function (y) ", "x"],
+    "4b5418502757": ["function (y) ", "x"],
+    "4b54101958d7": ["function (y) ", "x"],
+    "4b547cb72640": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 publish/sensitivity_explorer/charts/emissions.js

@@ -9050,39 +9050,39 @@
   },
   "source": "A",
   "attrs": {
-    "35d43f8c6ffe": {
+    "4b5450bf73e5": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d410ff2ca5": {
+    "4b544b6418a0": {
       "xintercept": {}
     },
-    "35d42063642d": {
+    "4b54608362d3": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {},
       "text": {}
     },
-    "35d4a616732": {
+    "4b545b0d61e8": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {},
       "text": {}
     },
-    "35d4e0b3c34": {
+    "4b547a73718d": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "35d43f8c6ffe",
+  "cur_data": "4b5450bf73e5",
   "visdat": {
-    "35d43f8c6ffe": ["function (y) ", "x"],
-    "35d410ff2ca5": ["function (y) ", "x"],
-    "35d42063642d": ["function (y) ", "x"],
-    "35d4a616732": ["function (y) ", "x"],
-    "35d4e0b3c34": ["function (y) ", "x"]
+    "4b5450bf73e5": ["function (y) ", "x"],
+    "4b544b6418a0": ["function (y) ", "x"],
+    "4b54608362d3": ["function (y) ", "x"],
+    "4b545b0d61e8": ["function (y) ", "x"],
+    "4b547a73718d": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 publish/sensitivity_explorer/charts/hydrogen.js

@@ -44826,32 +44826,32 @@
   },
   "source": "A",
   "attrs": {
-    "35d41f6d4f33": {
+    "4b54403779a2": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d42b511720": {
+    "4b546aa92750": {
       "xintercept": {}
     },
-    "35d483f1f92": {
+    "4b542cfd7b1c": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "35d4c613618": {
+    "4b54291f559e": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     }
   },
-  "cur_data": "35d41f6d4f33",
+  "cur_data": "4b54403779a2",
   "visdat": {
-    "35d41f6d4f33": ["function (y) ", "x"],
-    "35d42b511720": ["function (y) ", "x"],
-    "35d483f1f92": ["function (y) ", "x"],
-    "35d4c613618": ["function (y) ", "x"]
+    "4b54403779a2": ["function (y) ", "x"],
+    "4b546aa92750": ["function (y) ", "x"],
+    "4b542cfd7b1c": ["function (y) ", "x"],
+    "4b54291f559e": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-11 publish/sensitivity_explorer/charts/primaryEnergy.js

@@ -35947,37 +35947,37 @@
   },
   "source": "A",
   "attrs": {
-    "35d4347a3ddd": {
+    "4b54647f50d0": {
       "yintercept": {},
       "type": "scatter"
     },
-    "35d457ea2379": {
+    "4b54e03781a": {
       "xintercept": {}
     },
-    "35d45692879": {
+    "4b543cd8640c": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "35d46a3130a9": {
+    "4b5419b67b2c": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     },
-    "35d42ef8675f": {
+    "4b54283a5679": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "35d4347a3ddd",
+  "cur_data": "4b54647f50d0",
   "visdat": {
-    "35d4347a3ddd": ["function (y) ", "x"],
-    "35d457ea2379": ["function (y) ", "x"],
-    "35d45692879": ["function (y) ", "x"],
-    "35d46a3130a9": ["function (y) ", "x"],
-    "35d42ef8675f": ["function (y) ", "x"]
+    "4b54647f50d0": ["function (y) ", "x"],
+    "4b54e03781a": ["function (y) ", "x"],
+    "4b543cd8640c": ["function (y) ", "x"],
+    "4b5419b67b2c": ["function (y) ", "x"],
+    "4b54283a5679": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-24 report_paperCharts.Rmd
limVRE capacity based

@@
 
-budget %>% 
+reductions2040 %>% 
   kbl() %>%
@@
 
+direct_electrification %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
 indirect_electrification %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+indirect_electrification_detail %>% 
   kbl() %>%
@@
 
-#conclusion
-# df %>% 
-#     filter(region == "EU27", period %in% c(2040), tgt2030 %in% tgt2030Scen) %>%
-#     calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%
-#     mutate(reduction = round(value / tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference) ,2)) %>% 
-#     select(-variable) %>%
-#     filter(tgt2050 != "Npi") %>%
-#     mutate(x=ifelse(reduction>=0,period+1,NA),
-#            xend=ifelse(reduction>=0,period+1,NA),
-#            y=ifelse(reduction>=0,1,NA),
-#            yend=ifelse(reduction>=0,ifelse(reduction<=0,0,reduction),NA),
-#            bar = ifelse(period==2040,"2040","emi"),
-#            #label = ifelse(value>0,paste0( "- ", (1-value) * 100, "% (-", (1-intraEURed) * 100 ,"%)"),NA),
-#            labelY = reduction + (1-reduction)/2,
-#            labelX=period+1) %>%
-#     group_by(model,region,period) %>% 
-#     mutate(max=max(reduction),
-#            min=min(reduction),
-#            range=max-min,
-#            labelRange = ifelse(round((1-max) * 100) == round((1-min) * 100), paste0(round((1-max) * 100), "%"), paste0(round((1-max) * 100), "% to ", round((1-min) * 100) ,"%"))) %>%
-#   filter(scenario == mainScen, period == 2040) %>% pull(labelRange)
-
-```
-
-<!-- (c) Breakdown of residual CO2 emissions from energy and industrial processes (% in relation to 2020) -->
-
-```{r chart_figure1c, echo=FALSE}
+```
+
+<!-- (c) GHG Emissions per sector in the reference scenario (Mt CO2/yr) -->
+
+```{r chart_figure1c_sectorEmi, echo=FALSE, include=FALSE}
+
+vars <- c(
+  "Energy Supply - Electricity"               = "Emi|GHG|Gross|Energy|Supply|Electricity",
+  "Energy Supply - Non-electric"              = "Emi|GHG|Gross|Energy|Supply|Non-electric",
+  "Energy Demand - Transport"                 = "Emi|GHG|Energy|Demand|Transport",
+  "Energy Demand - International Bunkers"     = "Emi|CO2|Energy|Demand|Transport|International Bunkers",
+  "Energy Demand - Buildings"                 = "Emi|GHG|Energy|Demand|Buildings",
+  "Energy Demand - Industry and Agriculture"  = "Emi|GHG|Gross|Energy|Demand|Industry",
+  "Energy Demand - Carbon Dioxide Removal"    = "Emi|GHG|Energy|Demand|CDR",
+  "Industrial Processes"                      = "Emi|GHG|Industrial Processes",
+  "Agriculture"                               = "Emi|GHG|Agriculture",
+  "Land-Use Change"                           = "Emi|GHG|Land-Use Change|LULUCF national accounting", #"Emi|GHG|Land-Use Change",
+  "Waste"                                     = "Emi|GHG|Waste",
+  "BECCS"                                     = "Emi|CO2|CDR|BECCS",
+  "Industry CCS"                              = "Emi|CO2|CDR|Industry CCS|Synthetic Fuels",
+  "DACCS"                                     = "Emi|CO2|CDR|DACCS",
+  "Enhanced Weathering"                       = "Emi|CO2|CDR|EW")
+
+plotColor <- c(
+  "Energy Supply - Electricity"               = "#ffb200",
+  "Energy Supply - Non-electric"              = "#0000cc",
+  "Energy Demand - Transport"                 = "#a1dd70",
+  "Energy Demand - International Bunkers"     = "#ffc0cb",
+  "Energy Demand - Buildings"                 = "#5edfff",
+  "Energy Demand - Industry and Agriculture"  = "#a5a5a5",
+  "Energy Demand - Carbon Dioxide Removal"    = "#999959",
+  "Industrial Processes"                      = "#5c5c5c",
+  "Agriculture"                               = "#357933",
+  "Land-Use Change"                           = "#6ec16b",
+  "Waste"                                     = "#A52A2A",
+  "BECCS"                                     = "#377EB8",
+  "Industry CCS"                              = "#5ed5b0",
+  "DACCS"                                     = "#CC6666",
+  "Enhanced Weathering"                       = "#5b0d8f")
+
+plotData <- df %>%
+  filter(region == "EU27", period %in% c(2010:2050), variable %in% vars, scenario == mainScen) %>%
+  mutate(variable=factor(variable, levels=vars))
+
+#total
+totalData <- df %>%
+  calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%
+  filter(region == "EU27", period %in% c(2010:2050), variable == "Emissions with LULUCF and with international transport", scenario == mainScen)
+
+# check <- left_join(
+#   plotData %>% group_by(period) %>% summarize(value = sum(value)),
+#   totalData %>% group_by(period) %>% summarize(total = sum(value)),
+#   by = join_by(period == period)
+# ) %>%
+#   mutate(diff= round(total-value,2))
+# 
+# left_join(
+#   plotData %>% filter(period == 2010) %>% mutate(value2010 = value),
+#   plotData %>% filter(period == 2015) %>% mutate(value2015 = value),
+#   by = join_by(variable == variable)
+# ) %>%
+#   mutate(diff= round(value2015-value2010,2)) %>%
+#   select(variable,value2010,value2015,diff)
+
+g[["GHG Emissions per sector"]] <- ggplot(plotData,aes(x=period,y=value)) +
+  geom_area(aes(fill=variable), alpha = 0.8) +
+  geom_line(data=totalData, linewidth = 1, color="black") +
+  geom_vline(xintercept=2020, color = "black", linetype="dashed", linewidth=1, alpha = 0.5) +
+  geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
+  theme_doubleColumn() +
+  #ylab("Final Energy Demand - EJ/yr") + 
+  #ggtitle("(a) per sector and carrier") +
+  scale_fill_manual(values = setNames(plotColor[names(vars)],vars), labels = setNames(names(vars), vars)) +
+  #theme(legend.margin=margin(l = -1, unit='cm')) +
+  scale_x_continuous(breaks=c(2010, 2010, 2020,2030,2040,2050)) + 
+  theme(axis.title.x=element_blank()) +
+  theme(axis.title.y=element_blank()) +
+  theme(legend.title = element_blank()) +
+  theme(#legend.text = element_text(size = theme.double.text.size*0.7),
+        #legend.key.height = unit(0.7, "cm"),
+        #legend.key.width = unit(0.7,"cm"),
+        legend.spacing.x = unit(0.2, 'cm')) + 
+  #  theme(plot.title = element_text(size = 1.2*theme.double.text.size)) +
+  theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical") +
+  labs(title = "(c) GHG Emissions per sector in the reference scenario (Mt CO2/yr)") + 
+  theme(legend.margin=margin(t=30)) +
+  theme(plot.margin = margin(t = 15, unit = "pt"))
+
+```
+
+<!-- (d) Breakdown of residual net CO2 emissions from energy and industrial processes (% in relation to 2020) -->
+
+```{r chart_figure1d_gross, echo=FALSE}
 
@@
   "Industry" = "Emi|GHG|Gross|Energy|Demand|Industry",
-  "Buildings" ="Emi|GHG|Energy|Demand|Buildings",
   "Transportation" ="Emi|GHG|Energy|Demand|Transport",
   "Bunkers" = "Emi|CO2|Energy|Demand|Transport|International Bunkers",
-#  "CDR" = "Emi|GHG|Gross|Energy|Demand|CDR",
-#  "AFOFI" = "Emissions|CO2|Energy|Demand|AFOFI",
-#  "Other Sector" ="Emissions|CO2|Energy|Demand|Other Sector",
-  "Heat"="Emi|CO2|Gross|Energy|Supply|Heat",
-  "Other Energy\nConversion" = "Emi|CO2|Gross|Other Energy Conversion",
-    #"Hydrogen" ="Emi|CO2|Gross|Energy|Supply|Hydrogen",
-    #"Liquids"="Emi|CO2|Gross|Energy|Supply|Liquids",
-    #"Gases"="Emi|CO2|Gross|Energy|Supply|Gases",
-    #"Solids"="Emi|CO2|Gross|Energy|Supply|Solids",
-#  "Other"="Emissions|CO2|Energy|Supply|Other",
-  "Electricity"="Emi|GHG|Gross|Energy|Supply|Electricity"
-)
-# "Emi|GHG|Agriculture",
-#   "Emi|GHG|Land-Use Change",
-#   "Emi|GHG|Waste",
-#   "Emi|CO2|CDR|BECCS",
-#   "Emi|CO2|CDR|Industry CCS|Synthetic Fuels",
-#   "Emi|CO2|CDR|DACCS",
-#   "Emi|CO2|CDR|EW"
+  "Buildings" ="Emi|GHG|Energy|Demand|Buildings",
+  "Energy\nSupply"="Emi|CO2|Gross|Energy|Supply"
+)
 
 plotColor <- c(
-  "Electricity"= "#ffb200",
-  "Heat"= "#cc0000",
-  "Other Energy\nConversion" = "#0000cc",
-  #"Gases"= "#999959",
-  #"Liquids"= "#0000cc",
-  #"Solids"= "#0c0c0c",
-  #"Other" = "#79a6d2",
-  #"Hydrogen" = "#5ed5b0",
+  "Industrial\nProcesses" = "#5c5c5c",
+  "Industry" = "#5f6769",
   "Transportation" = "#a1dd70",
@@
   "Buildings" = "#5edfff",
-  "Other Sector" = "#999959",
-  "AFOFI" = "#005900",
-  "Industry" = "#5f6769",
-  "Industrial\nProcesses" = "#5c5c5c",
-  "Other" = "#5b0d8f",
-  "Waste" = "#A52A2A",
-  "AFOLU" = "#4DAF4A",
-  "Agriculture" = "#357933",
-  "LULUCF" = "#6ec16b"
+  "Energy\nSupply"= "#ffb200"
 )
@@
 
-fulldata <- df %>%
-  filter(region == "EU27",
-         period %in% c(2020,2030,2040),
-         tgt2030 %in% tgt2030Scen,
-         variable %in% unlist(vars)) %>%
-  mutate(labels = factor(labels[as.character(variable)],levels = names(vars)),
-         variable = factor(variable, levels = vars),
-         type = "gross") %>%
-  group_by(period,variable) %>%
-  mutate(min = min(value),
-         max = max(value))
-
-plotData <- fulldata %>%
-  filter(scenario == mainScen) %>%
-  mutate(complement = FALSE) %>%
-  group_by(variable) %>%
-  mutate(pct = paste0(round(value / value[period==2020],2)*100, "%")) %>%
-  bind_rows(
-    fulldata %>%
-      filter(scenario == mainScen) %>%
-      mutate(complement = TRUE) %>%
-      group_by(variable) %>%
-      mutate(value = value[period==2020] - value) %>%
-      mutate(labels=NA)
-  ) %>%
-  mutate(ext_Var = ifelse(complement, paste0(as.character(variable),"_"), as.character(variable))) %>%
-  arrange(period,ext_Var) %>%
-  group_by(period) %>%
-  arrange(variable) %>%
-  mutate(ymid = as.numeric(sub("\\D+", "", period)),
-         ymax = ymid + 4, ymin = ymid - 4,
-         xmin = c(0, head(cumsum(value), -1)),
-         xmax = cumsum(value),
-         xmid = (xmax + xmin) / 2,
-         ) %>%
-  ungroup() %>%
-  filter(complement == FALSE)
-
-g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] <- plotData %>% 
-  ggplot(aes(xmid, ymid, fill = ext_Var)) +
-  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax,
-                alpha = factor(period), color = variable)) +
-  geom_errorbar(data=plotData %>% filter(period == 2040), aes(xmin=xmax-value+min, xmax=xmax-value+max), width=4, colour="black", alpha=0.9, linewidth=0.8) +
-  geom_text(data=plotData %>% filter(period == 2020), aes(y = 2015, label = labels, group = labels, hjust=1, angle = 90), vjust=0.5, hjust=1.1, na.rm=TRUE, size = geomText.size, angle = 90, lineheight = 0.8) +
-  geom_text(data=plotData %>% filter(period == 2040), aes(x=xmid , y = 2045, label = pct), vjust=0.5, hjust=-0.1, na.rm=TRUE, size = geomText.size, angle = 90) +
-  scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) + 
-  scale_alpha_manual(values = c(0.2, 0.3, 1)) +
-  scale_color_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) +
-  theme_doubleColumn() +
-  theme(legend.position = "none") +
-  scale_y_continuous(breaks=c(2020,2030,2040), labels=c("current",2030,2040), minor_breaks = NULL, limits=c(2008,2047)) +
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank(),
-        axis.title.y=element_blank()) +
-  scale_x_continuous(breaks = NULL) +
-  coord_cartesian(clip="off") +
-  theme(plot.margin = margin(t = 30, r = 0, b = 100, l = 0, unit = "pt")) +
-  #labs(title = "(c) Sectoral breakdown of residual gross CO2 emissions from energy and industrial processes (% of average 2018-2022)") + 
-  #theme(plot.title = element_text(margin=margin(t=0,r=0,b=45,l=-200), hjust=1))
-  labs(title = "(c) Sectoral breakdown of net CO2 emissions from energy and industrial processes (%)") + 
-  theme(plot.title = element_text(margin=margin(t=0,r=0,b=45,l=0), hjust=1))
-
-```
-
-```{r, echo=FALSE, include=FALSE}
-
-g[["Figure 1 - gross"]] <- gridExtra::arrangeGrob(
-  g[["GHG emi"]],
-  g[["target"]],
-  g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]],
-  layout_matrix = rbind(c(1, 1, 1, 1, 2, 2),
-                        c(1, 1, 1, 1, 2, 2),
-                        c(1, 1, 1, 1, 2, 2),
-                        c(1, 1, 1, 1, 2, 2),
-                        c(1, 1, 1, 1, 2, 2),
-                        c(3, 3, 3, 3, 3, 3),
-                        c(3, 3, 3, 3, 3, 3),
-                        c(3, 3, 3, 3, 3, 3),
-                        c(3, 3, 3, 3, 3, 3))
-   )
-
-ggsave(paste0(outChartsFolder,"/png/Figure 1. Emission results panel (gross).png"), g[["Figure 1 - gross"]], device="png", width = 12, height = 8, dpi=300, units = "in")
-ggsave(paste0(outChartsFolder,"/svg/Figure 1. Emission results panel (gross).svg"), g[["Figure 1 - gross"]], device="svg", width = 12, height = 8, dpi=100, units = "in")
-
-```
-
-```{r, echo=FALSE, fig.width=12, fig.height=10}
-
-#grid.newpage()
-#grid.draw(g[["Figure 1 - gross"]])
-
-```
-
-<!-- Figure 1.
-Greenhouse gas emission reductions for scenarios reaching climate neutrality by 2050.
-Central values are given for the reference scenario (57% reduction by 2030, reference final energy projections, biomass availability limited to 7.5 EJ/yr and default CCS assumption), ranges for the full scenario ensemble.
--->
-
-<!-- (c) Breakdown of residual net CO2 emissions from energy and industrial processes (% in relation to 2020) -->
-
-```{r chart_figure1c_gross, echo=FALSE}
-
-vars <- list(
-  "Industrial\nProcesses" = "Emi|GHG|Industrial Processes",
-  "Industry" = "Emi|GHG|Gross|Energy|Demand|Industry",
-  "Buildings" ="Emi|GHG|Energy|Demand|Buildings",
-  "Transportation" ="Emi|GHG|Energy|Demand|Transport",
-  "Bunkers" = "Emi|CO2|Energy|Demand|Transport|International Bunkers",
-#  "CDR" = "Emi|GHG|Gross|Energy|Demand|CDR",
-#  "AFOFI" = "Emissions|CO2|Energy|Demand|AFOFI",
-#  "Other Sector" ="Emissions|CO2|Energy|Demand|Other Sector",
-  "Heat"="Emi|CO2|Gross|Energy|Supply|Heat",
-  "Other Energy\nConversion" = "Emi|CO2|Gross|Other Energy Conversion",
-    #"Hydrogen" ="Emi|CO2|Gross|Energy|Supply|Hydrogen",
-    #"Liquids"="Emi|CO2|Gross|Energy|Supply|Liquids",
-    #"Gases"="Emi|CO2|Gross|Energy|Supply|Gases",
-    #"Solids"="Emi|CO2|Gross|Energy|Supply|Solids",
-#  "Other"="Emissions|CO2|Energy|Supply|Other",
-  "Electricity"="Emi|GHG|Gross|Energy|Supply|Electricity"
-)
-# "Emi|GHG|Agriculture",
-#   "Emi|GHG|Land-Use Change",
-#   "Emi|GHG|Waste",
-#   "Emi|CO2|CDR|BECCS",
-#   "Emi|CO2|CDR|Industry CCS|Synthetic Fuels",
-#   "Emi|CO2|CDR|DACCS",
-#   "Emi|CO2|CDR|EW"
-
-plotColor <- c(
-  "Electricity"= "#ffb200",
-  "Heat"= "#cc0000",
-  "Other Energy\nConversion" = "#0000cc",
-  #"Gases"= "#999959",
-  #"Liquids"= "#0000cc",
-  #"Solids"= "#0c0c0c",
-  #"Other" = "#79a6d2",
-  #"Hydrogen" = "#5ed5b0",
-  "Transportation" = "#a1dd70",
-  "Bunkers" = "#ffc0cb",
-  "Buildings" = "#5edfff",
-  "Other Sector" = "#999959",
-  "AFOFI" = "#005900",
-  "Industry" = "#5f6769",
-  "Industrial\nProcesses" = "#5c5c5c",
-  "Other" = "#5b0d8f",
-  "Waste" = "#A52A2A",
-  "AFOLU" = "#4DAF4A",
-  "Agriculture" = "#357933",
-  "LULUCF" = "#6ec16b"
-)
-
-labels <- setNames(names(vars),vars[names(vars)])
-
-grossData <- df %>%
+df_ext <- df %>%
+  calc_addVariable("`Emi|CO2|Gross|Energy|Supply`" = "`Emi|GHG|Gross|Energy|Supply|Electricity` + `Emi|GHG|Gross|Energy|Supply|Non-electric`", units = "Mt CO2/yr") %>%
+  calc_addVariable("`Carbon Management|Storage|Pe2Se|Electricity, Heat and Other Energy Conversions`" = "`Carbon Management|Storage|Biomass|Pe2Se|Electricity w/ couple prod` + `Carbon Management|Storage|Fossil|Pe2Se|Electricity w/ couple prod` + `Carbon Management|Storage|Biomass|Pe2Se|Gases w/ couple prod` + `Carbon Management|Storage|Biomass|Pe2Se|Hydrogen w/ couple prod` + `Carbon Management|Storage|Biomass|Pe2Se|Liquids w/ couple prod` + `Carbon Management|Storage|Fossil|Pe2Se|Gases w/ couple prod` + `Carbon Management|Storage|Fossil|Pe2Se|Hydrogen w/ couple prod` + `Carbon Management|Storage|Fossil|Pe2Se|Liquids w/ couple prod`", units = "Mt CO2/yr") %>%
+  calc_addVariable("`Carbon Management|Storage|Industry Extended`" = "`Carbon Management|Storage|Industry Energy` + `Carbon Management|Storage|Waste|Plastics Incineration`", units = "Mt CO2/yr")
+
+grossData <- df_ext %>%
   filter(region == "EU27",
@@
 
-if(!("Carbon Management|Storage|Pe2Se|Other" %in% unique(df$variable))){
-  df <- rbind(df,df %>% calc_addVariable("`Carbon Management|Storage|Pe2Se|Other`" = "`Carbon Management|Storage|Biomass|Pe2Se|Gases w/ couple prod` + `Carbon Management|Storage|Biomass|Pe2Se|Hydrogen w/ couple prod` + `Carbon Management|Storage|Biomass|Pe2Se|Liquids w/ couple prod` + `Carbon Management|Storage|Fossil|Pe2Se|Gases w/ couple prod` + `Carbon Management|Storage|Fossil|Pe2Se|Hydrogen w/ couple prod` + `Carbon Management|Storage|Fossil|Pe2Se|Liquids w/ couple prod`", units = "Mt CO2/yr", only.new=T))
-  df <- rbind(df,df %>% calc_addVariable("`Carbon Management|Storage|Pe2Se|Electricity`" = "`Carbon Management|Storage|Biomass|Pe2Se|Electricity w/ couple prod` + `Carbon Management|Storage|Fossil|Pe2Se|Electricity w/ couple prod`", units = "Mt CO2/yr", only.new=T))
-
-  df <- rbind(df,df %>% calc_addVariable("`Carbon Management|Storage|Industry Extended`" = "`Carbon Management|Storage|Industry Energy` + `Carbon Management|Storage|Waste|Plastics Incineration`", units = "Mt CO2/yr", only.new=T))
-}
-
 varsCC <- list(
@@
   "Industry" = "Carbon Management|Storage|Industry Extended",
-  "Other Energy\nConversion" = "Carbon Management|Storage|Pe2Se|Other",
-  "Electricity" = "Carbon Management|Storage|Pe2Se|Electricity"
+  "Energy\nSupply" = "Carbon Management|Storage|Pe2Se|Electricity, Heat and Other Energy Conversions"
 )
@@
 
-# allCCVars <- c(
-#   "Carbon Management|Storage",
-#     "Carbon Management|Storage|+|Biomass|Pe2Se", 
-#       "Carbon Management|Storage|Biomass|Pe2Se|+|Electricity w/ couple prod",
-#       "Carbon Management|Storage|Biomass|Pe2Se|+|Gases w/ couple prod",
-#       "Carbon Management|Storage|Biomass|Pe2Se|+|Hydrogen w/ couple prod",
-#       "Carbon Management|Storage|Biomass|Pe2Se|+|Liquids w/ couple prod",
-#     "Carbon Management|Storage|+|Fossil|Pe2Se",
-#       "Carbon Management|Storage|Fossil|Pe2Se|+|Electricity w/ couple prod",
-#       "Carbon Management|Storage|Fossil|Pe2Se|+|Gases w/ couple prod",
-#       "Carbon Management|Storage|Fossil|Pe2Se|+|Hydrogen w/ couple prod",
-#       "Carbon Management|Storage|Fossil|Pe2Se|+|Liquids w/ couple prod",
-#     "Carbon Management|Storage|+|Industry Energy",
-#     "Carbon Management|Storage|+|Industry Process",
-#     "Carbon Management|Storage|+|CDR energy",
-#     "Carbon Management|Storage|+|DAC",
-#     "Carbon Management|Storage|+|OAE calcination",
-#     "Carbon Management|Storage|+|Waste|Plastics Incineration"
-#   )
-# 
-# View(df %>%
-#        filter(region == "EU27",
-#               period %in% c(2020,2030,2040),
-#               tgt2030 %in% tgt2030Scen,
-#               variable %in% allCCVars) %>%
-#   filter(scenario == mainScen)
-#   )
-
-CCData <- df %>%
+CCData <- df_ext %>%
   filter(region == "EU27",
@@
          labels = factor(labelsCC[as.character(variable)],levels = names(vars)),
-         #variable = factor(variable, levels = varsCC)
          ) %>%
@@
 
-#View(CCData %>% filter(scenario == mainScen))
+histVars <- list(
+  "Industrial\nProcesses" = "Emi|GHG|Industrial Processes",
+  "Industry" = "Emi|GHG|Industry",
+  "Transportation" ="Emi|GHG|Energy|Demand|Transport",
+  "Bunkers" = "Emi|GHG|Energy|Demand|Transport|International Bunkers",
+  "Buildings" ="Emi|GHG|Energy|Demand|Buildings",
+  "Energy\nSupply"="Emi|CO2|Gross|Energy|Supply"
+)
+
+labelshistVars <- setNames(names(histVars),histVars[names(histVars)])
+
+h <- hist %>% 
+  calc_addVariable("`Emi|CO2|Gross|Energy|Supply`" = "`Emi|GHG|Energy` - `Emi|GHG|Energy|Demand`", units = "Mt CO2/yr") %>%
+  filter(model == "UNFCCC", region == "EU27", variable %in% histVars, period %in% c(1990,2018,2019,2020,2021,2022)) %>% drop_na(value) %>%
+  mutate(labels = factor(labelshistVars[as.character(variable)],levels = names(vars)))
+
+hist1990data <- left_join(
+  grossData %>% filter(period == 2020) %>% select(-period, -value, -min, -max),
+  h %>% filter(period == 1990) %>% select(labels,value) %>% mutate(min = value, max = value),
+  by = join_by(labels == labels)
+) %>%
+  mutate(period = 1990) %>%
+  relocate(any_of(names(grossData)))
+
+hist2018to2020data <- left_join(
+  grossData %>% filter(period == 2020) %>% select(-period, -value, -min, -max),
+  h %>% filter(period %in% c(2018,2019,2020,2021,2022)) %>%
+     group_by(labels) %>%
+     summarize(mean=mean(value, na.rm=TRUE)) %>% mutate(value = mean, min = value, max = value) %>%
+    select(-mean),
+  by = join_by(labels == labels)
+) %>%
+  mutate(period = 2020) %>%
+  relocate(any_of(names(grossData)))
 
 fulldata <- left_join(
-  grossData,
+  rbind(
+    hist1990data,
+    hist2018to2020data,
+    grossData %>% filter(period != 2020)),
   CCData %>%
+    filter(period != 2020) %>%
     select(-variable, -unit),
@@
 
+# tmp <- fulldata %>% filter(scenario == mainScen) %>% select(variable, period, net) %>% pivot_wider(names_from = period, values_from = net) %>%
+#   bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "Total"))
+# write.csv(tmp, "tmp.csv")
+#%>%
+#  bind_rows(summarise(.,
+#                      across(where(is.numeric), sum),
+#                      across(where(is.character), ~"Total")))
+
 plotData <- fulldata %>%
@@
   group_by(variable) %>%
-  mutate(pct = paste0(round(net / net[period==2020],2)*100, "%")) %>%
+  mutate(pct1990 = paste0(round(net / net[period==1990],2)*100, "%"),
+         pct2020 = paste0(round(net / net[period==2020],2)*100, "%")) %>%
   bind_rows(
@@
       group_by(variable) %>%
-      mutate(value = value[period==2020] - value) %>%
+      mutate(value = max(value[period==1990],value[period==2020]) - value) %>%
       mutate(labels=NA)
@@
   arrange(variable) %>%
-  mutate(ymid = as.numeric(sub("\\D+", "", period)),
+  mutate(ymid = ifelse(period==1990, 2010, as.numeric(sub("\\D+", "", period))),
          ymax = ymid + 4, ymin = ymid - 4,
@@
 
-g[["2040 Net Emissions - Energy and Industrial Processes - horizontal bar"]] <- plotData %>% 
+#difference between REMIND 2020 and UNFCCC numbers
+# diff <- left_join(
+#   h %>% filter(period %in% c(2018,2019,2020,2021,2022)) %>%
+#     group_by(labels) %>%
+#     summarize(mean=mean(value, na.rm=TRUE)),
+#   plotData %>% filter(period == 2020) %>% select(labels,net),
+#   by = join_by(labels == labels)
+#  ) %>%
+#    mutate(diff= round(net-mean,2),
+#           pctg=round((diff/net)*100,2))
+
+g[["2040 Net Emissions - Energy and Industrial Processes - horizontal bar - net only"]] <- plotData %>%
   ggplot(aes(xmid, ymid, fill = ext_Var)) +
-  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax,
+  geom_rect(aes(xmin = xmin, xmax = xmax+CCData, ymin = ymin, ymax = ymax,
                 alpha = factor(period), color = variable)) +
 
-  geom_rect_pattern(data = plotData %>% filter(CCData != 0), aes(xmin = xmax + CCData, xmax = xmax, ymin = ymin, ymax = ymax, alpha = factor(period), fill = ext_Var, color = variable, pattern_alpha = factor(period)), pattern_color = NA, pattern_fill = "white", pattern="stripe", pattern_spacing = 0.05, pattern_aspect_ratio = 1, pattern_density      = 0.2) +
-
   geom_errorbar(data=plotData %>% filter(period == 2040), aes(xmin=xmax-value+min+CCData, xmax=xmax-value+max+CCData), width=4, colour="black", alpha=0.9, linewidth=0.8) +
 
-  geom_text(data=plotData %>% filter(period == 2020), aes(y = 2015, label = labels, group = labels, hjust=1, angle = 90), vjust=0.5, hjust=1.1, na.rm=TRUE, size = geomText.size * 0.8, angle = 90, lineheight = 0.8) +
-  geom_text(data=plotData %>% filter(period == 2040), aes(x=xmid , y = 2045, label = pct), vjust=0.5, hjust=-0.1, na.rm=TRUE, size = geomText.size, angle = 90) +
+  geom_text(data=plotData %>% filter(period == 1990), aes(y = 2005, label = labels, group = labels, hjust=1, angle = 90), vjust=0.5, hjust=1.1, na.rm=TRUE, size = geomText.size * 0.8, angle = 90, lineheight = 0.8) +
+
+  geom_text(data=plotData %>% filter(period == 2040), aes(x=xmid , y = 2045, label = pct1990), vjust=0.5, hjust=-0.1, na.rm=TRUE, size = geomText.size, angle = 90) +
   scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) + 
-  scale_alpha_manual(values = c(0.2, 0.3, 1)) +
+  scale_alpha_manual(values = c(0.2, 0.2, 0.3, 1)) +
   scale_color_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) +
@@
   theme(legend.position = "none") +
-  scale_y_continuous(breaks=c(2020,2030,2040), labels=c("current",2030,2040), minor_breaks = NULL, limits=c(2008,2047)) +
+  scale_y_continuous(breaks=c(2010,2020,2030,2040), labels=c("1990","avrg. 2018-2022","2030","2040"), minor_breaks = NULL, limits=c(1998,2047)) +
   theme(axis.title.x=element_blank(),
@@
   coord_cartesian(clip="off") +
-  theme(plot.margin = margin(t = 30, r = 0, b = 100, l = 0, unit = "pt")) +
-  #labs(title = "(c) Sectoral breakdown of net CO2 emissions from energy and industrial processes (% of average 2018-2022)") + 
-  #theme(plot.title = element_text(margin=margin(t=0,r=0,b=45,l=0)))
-  labs(title = "(c) Sectoral breakdown of net CO2 emissions from energy and industrial processes (%)") + 
-  theme(plot.title = element_text(margin=margin(t=0,r=0,b=45,l=0), hjust=1))
-
-g[["2040 Net Emissions - Energy and Industrial Processes - horizontal bar - net only"]] <- plotData %>% 
-  ggplot(aes(xmid, ymid, fill = ext_Var)) +
-  geom_rect(aes(xmin = xmin, xmax = xmax+CCData, ymin = ymin, ymax = ymax,
-                alpha = factor(period), color = variable)) +
-
-  geom_errorbar(data=plotData %>% filter(period == 2040), aes(xmin=xmax-value+min+CCData, xmax=xmax-value+max+CCData), width=4, colour="black", alpha=0.9, linewidth=0.8) +
-
-  geom_text(data=plotData %>% filter(period == 2020), aes(y = 2015, label = labels, group = labels, hjust=1, angle = 90), vjust=0.5, hjust=1.1, na.rm=TRUE, size = geomText.size * 0.8, angle = 90, lineheight = 0.8) +
-  geom_text(data=plotData %>% filter(period == 2040), aes(x=xmid , y = 2045, label = pct), vjust=0.5, hjust=-0.1, na.rm=TRUE, size = geomText.size, angle = 90) +
-  scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) + 
-  scale_alpha_manual(values = c(0.2, 0.3, 1)) +
-  scale_color_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) +
-  theme_doubleColumn() +
-  theme(legend.position = "none") +
-  scale_y_continuous(breaks=c(2020,2030,2040), labels=c("current",2030,2040), minor_breaks = NULL, limits=c(2008,2047)) +
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank(),
-        axis.title.y=element_blank()) +
-  scale_x_continuous(breaks = NULL) +
-  coord_cartesian(clip="off") +
-  theme(plot.margin = margin(t = 30, r = 0, b = 100, l = 0, unit = "pt")) +
-  labs(title = "(c) Sectoral breakdown of net CO2 emissions from energy and industrial processes (%)") + 
-  theme(plot.title = element_text(margin=margin(t=0,r=0,b=45,l=0)))
+  theme(plot.margin = margin(t = 15, r = 0, b = 100, l = 0, unit = "pt")) +
+  #theme(plot.margin = margin(t = 30, r = 0, b = 100, l = 0, unit = "pt")) +
+  labs(title = "(d) Sectoral breakdown of residual net CO2 emissions from energy and industrial processes") + 
+  theme(plot.title = element_text(margin=margin(t=0,r=0,b=55,l=0), hjust=1))
 
@@
 
-g[["Figure 1 - net"]] <- gridExtra::arrangeGrob(
+g[["Figure 1"]] <- gridExtra::arrangeGrob(
   g[["GHG emi"]],
   g[["target"]],
-  g[["2040 Net Emissions - Energy and Industrial Processes - horizontal bar"]],
-  layout_matrix = rbind(c(1, 1, 1, 1, 2, 2),
-                        c(1, 1, 1, 1, 2, 2),
-                        c(1, 1, 1, 1, 2, 2),
-                        c(1, 1, 1, 1, 2, 2),
-                        c(1, 1, 1, 1, 2, 2),
-                        c(3, 3, 3, 3, 3, 3),
-                        c(3, 3, 3, 3, 3, 3),
-                        c(3, 3, 3, 3, 3, 3),
-                        c(3, 3, 3, 3, 3, 3))
-   )
-
-ggsave(paste0(outChartsFolder,"/png/Figure 1. Emission results panel (net).png"), g[["Figure 1 - net"]], device="png", width = 12, height = 8, dpi=300, units = "in")
-ggsave(paste0(outChartsFolder,"/svg/Figure 1. Emission results panel (net).svg"), g[["Figure 1 - net"]], device="svg", width = 12, height = 8, dpi=100, units = "in")
-
-```
-
-```{r, echo=FALSE, fig.width=12, fig.height=10}
-
-#grid.newpage()
-#grid.draw(g[["Figure 1 - net"]])
-
-```
-
-<!-- Figure 1.
-Greenhouse gas emission reductions for scenarios reaching climate neutrality by 2050.
-Central values are given for the reference scenario (57% reduction by 2030, reference final energy projections, biomass availability limited to 7.5 EJ/yr and default CCS assumption), ranges for the full scenario ensemble.
-Pattern in net emissions represents carbon captured in the energy sector.
--->
-
-```{r, echo=FALSE, include=FALSE}
-
-g[["Figure 1 - net only"]] <- gridExtra::arrangeGrob(
-  g[["GHG emi"]],
-  g[["target"]],
+  g[["GHG Emissions per sector"]],
   g[["2040 Net Emissions - Energy and Industrial Processes - horizontal bar - net only"]],
@@
                         c(3, 3, 3, 3, 3, 3),
-                        c(3, 3, 3, 3, 3, 3))
-   )
-
-ggsave(paste0(outChartsFolder,"/png/Figure 1. Emission results panel (net only).png"), g[["Figure 1 - net only"]], device="png", width = 12, height = 8, dpi=300, units = "in")
-ggsave(paste0(outChartsFolder,"/svg/Figure 1. Emission results panel (net only).svg"), g[["Figure 1 - net only"]], device="svg", width = 12, height = 8, dpi=100, units = "in")
-
-```
-
-```{r, echo=FALSE, fig.width=12, fig.height=10}
+                        c(3, 3, 3, 3, 3, 3),
+                        c(3, 3, 3, 3, 3, 3),
+                        c(4, 4, 4, 4, 4, 4),
+                        c(4, 4, 4, 4, 4, 4),
+                        c(4, 4, 4, 4, 4, 4),
+                        c(4, 4, 4, 4, 4, 4))
+   )
+
+ggsave(paste0(outChartsFolder,"/png/Figure 1.
+Greenhouse gas emissions for scenarios reaching climate neutrality by 2050.png"), g[["Figure 1"]], device="png", width = 12, height = 14, dpi=300, units = "in")
+ggsave(paste0(outChartsFolder,"/svg/Figure 1.
+Greenhouse gas emissions for scenarios reaching climate neutrality by 2050.svg"), g[["Figure 1"]], device="svg", width = 12, height = 14, dpi=100, units = "in")
+
+```
+
+```{r, echo=FALSE, fig.width=12, fig.height=14}
 
 grid.newpage()
-grid.draw(g[["Figure 1 - net only"]])
+grid.draw(g[["Figure 1"]])
 
@@
 Figure 1.
-Greenhouse gas emission reductions for scenarios reaching climate neutrality by 2050.
+Greenhouse gas emissions for scenarios reaching climate neutrality by 2050.
 Central values are given for the reference scenario (57% reduction by 2030, reference final energy projections, biomass availability limited to 7.5 EJ/yr and default CCS assumption), ranges for the full scenario ensemble.
+Percentage values in plot (b) are based on GHG emissions with LULUCF and intra-EU aviation for years 2030-2040, and based on GHG emissions with LULUC and all bunkers for years 2045 and 2050.
+Percentage values in plot (c) stand for residual emissions in a sector compared to 1990 emissions.
 
@@
 plotData <- df %>% 
-  filter(region == "EU27", period >= 2020, period <= 2050, scenario  == mainScen, variable %in% unlist(vars)) %>% 
+  filter(region == "EU27", period >= 2015, period <= 2050, scenario  == mainScen, variable %in% unlist(vars)) %>% 
   mutate(variable = factor(variable, levels=vars)) %>% 
@@
 
-plotData2040 <- plotData[plotData$period == 2040,]
+plotDataBars <- plotData %>% 
+  filter(period %in% c(2020,2030,2040)) %>%
+  mutate(xPos = period + 2.5) %>%
+  mutate(label = paste0(round(percentage,2)*100,"%")) %>%
+  mutate(label = ifelse(period == 2040,
+                        ifelse(inv_vars[variable] == "Solar PV", paste0(label, " - Solar\n            PV"),
+                               ifelse(inv_vars[variable] == "Wind Onshore", paste0(label, " - Wind\n    Onshore"), 
+                                      ifelse(inv_vars[variable] == "Wind Offshore", paste0(label, " - Wind\n   Offshore"),
+                                             label))), label))
+
+#plotData2040 <- plotData[plotData$period == 2040,]
 #plotData$value <- plotData$value / plotData[plotData$period == "2020",]$value
@@
 
-plotData2040$xPos <- 2042.5
+#plotData2040$xPos <- 2042.5
 #plotData2040[plotData2040$variable %in% c("SE|Electricity|Hydro"),]$xPos <- 2028.5
 #plotData2040[plotData2040$variable %in% c("SE|Electricity|Biomass|w/o CC"),]$xPos <- 2020
-plotData2040[plotData2040$variable %in% c("SE|Electricity|Nuclear","SE|Electricity|Biomass|w/o CC"),]$xPos <- 2035
+#plotData2040[plotData2040$variable %in% c("SE|Electricity|Nuclear","SE|Electricity|Biomass|w/o CC"),]$xPos <- 2035
 
@@
 
-label <- c(
-
-)
-
-plotData2040 <- plotData2040 %>%
-  mutate(label = paste0(round(percentage,2)*100,"%")) %>%
-  mutate(label = ifelse(inv_vars[variable] == "Solar PV", paste0(label, " - Solar\n            PV"), 
-                        ifelse(inv_vars[variable] == "Wind Onshore", paste0(label, " - Wind\n    Onshore"), 
-                               ifelse(inv_vars[variable] == "Wind Offshore", paste0(label, " - Wind\n   Offshore"), 
-                                      label))))
+#label <- c(
+
+#)
+
+#plotData2040 <- plotDataBars %>%
+#  filter(period == 2040) %>%
+#  mutate(label = paste0(round(percentage,2)*100,"%")) %>%
+#  mutate(label = ifelse(inv_vars[variable] == "Solar PV", paste0(label, " - Solar\n            PV"), 
+#                        ifelse(inv_vars[variable] == "Wind Onshore", paste0(label, " - Wind\n    Onshore"), 
+#                               ifelse(inv_vars[variable] == "Wind Offshore", paste0(label, " - Wind\n   Offshore"), 
+#                                      label))))
+
+#plotData2030 <- plotDataBars %>%
+#  filter(period == 2030) %>%
+#  mutate(label = paste0(round(percentage,2)*100,"%"))
 
@@
   geom_line(data=plotDataRenewables, linetype = "dashed", linewidth = 1.5, color="#666666") +
-  geom_bar(data=plotData2040,aes(fill=variable),stat='identity', show.legend = FALSE, alpha = 0.7, color="white", width = 3, linewidth = 1.5) +
-  geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = label, y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geomText.size*0.8) +
+  geom_bar(data=plotDataBars,aes(fill=variable),stat='identity', show.legend = FALSE, alpha = 0.7, color="white", width = 3, linewidth = 1.5) +
+  geom_text(data=plotDataBars %>% filter(percentage >= 0.02),aes(label = label, y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geomText.size*0.8) +
+  #geom_text(data=plotData2030[plotData2030$percentage >= 0.02,],aes(label = label, y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geomText.size*0.8) +
   #geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geomText.size) +
@@
   scale_y_continuous(minor_breaks = seq(0.2, 0.8, 0.2), breaks=c(0,1),labels = scales::percent) +
-  scale_x_continuous(breaks=c(2020,2040,2050)) +
+  scale_x_continuous(breaks=c(2020,2030,2040,2050)) +
   scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
   guides(fill=guide_legend(ncol=2,override.aes = list(alpha=1))) + #, byrow = TRUE
-  annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, label = "renewables\nand nuclear", color = "#666666",angle = 90, hjust=0.5, vjust=-0.5, size=geomText.size, lineheight = 0.8) +
-  annotate(geom = "text", x = 2020, y = (1-plotDataRenewables[plotDataRenewables$period == 2020,]$percentage)/2+plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "fossil", color = "#666666",angle = 90, hjust=0.5, vjust=-2, size=geomText.size) +
-  annotation_custom(grob = linesGrob(gp=gpar(col="#666666",lwd = 3,lty="dashed")), xmin = 2016, xmax = 2019.8, ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage) +
+  annotate(geom = "text", x = 2015, y = plotDataRenewables[plotDataRenewables$period == 2015,]$percentage/2, label = "renewables\nand nuclear", color = "#666666",angle = 90, hjust=0.5, vjust=-0.5, size=geomText.size, lineheight = 0.8) +
+  annotate(geom = "text", x = 2015, y = (1-plotDataRenewables[plotDataRenewables$period == 2020,]$percentage)/2+plotDataRenewables[plotDataRenewables$period == 2015,]$percentage, label = "fossil", color = "#666666",angle = 90, hjust=0.5, vjust=-2, size=geomText.size) +
+  annotation_custom(grob = linesGrob(gp=gpar(col="#666666",lwd = 3,lty="dashed")), xmin = 2011, xmax = 2014.8, ymin = plotDataRenewables[plotDataRenewables$period == 2015,]$percentage, ymax = plotDataRenewables[plotDataRenewables$period == 2015,]$percentage) +
   #annotate(geom = "text", label = "100%", x = 2020, y = 1, hjust=1.2, color = "#666666", size=geomText.size) +
@@
 
+invVars <- setNames(names(vars), vars)
+
 plotData <- df %>% 
@@
                          aes(
-                           label = paste0(round(value*100),"%")),
+                           label = paste0(invVars[as.character(variable)], ": ", round(value*100),"%")),
                       #box.padding = 4,
@@
                       nudge_x = -12,
-                      nudge_y = -0.05,
+                      nudge_y = 0.2,
                       #nudge_y = c(0.9,0.5,-0.5,-0.5),
@@
                       , size = geomText.size * 0.8,
+                      hjust = 1
                       #force_pull = 2,
@@
 
-ggsave(paste0(outChartsFolder,"/png/Figure 2. Electricity supply and demand.png"), g[["Figure 2"]], device="png", width = 12, height = 8, dpi=300, units = "in")
-ggsave(paste0(outChartsFolder,"/svg/Figure 2. Electricity supply and demand.svg"), g[["Figure 2"]], device="svg", width = 12, height = 8, dpi=100, units = "in")
-
-```
-
-```{r, echo=FALSE, fig.width=12, fig.height=10}
+ggsave(paste0(outChartsFolder,"/png/Figure 2. Electricity supply and demand.png"), g[["Figure 2"]], device="png", width = 12, height = 9, dpi=300, units = "in")
+ggsave(paste0(outChartsFolder,"/svg/Figure 2. Electricity supply and demand.svg"), g[["Figure 2"]], device="svg", width = 12, height = 9, dpi=100, units = "in")
+
+```
+
+```{r, echo=FALSE, fig.width=12, fig.height=9}
 
@@
 ```
+Figure 2. Electricity supply and demand. (a) Electricity decarbonisation in terms of shares, (b) upscaling of photovoltaics, and (c) the transition to electricity as the main energy carrier.
 
@@
 
-plotData <- df %>% 
+plotDataOrig <- df %>% 
   filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>% 
-  mutate(variable = factor(variable, levels=vars))  %>% 
+  mutate(variable = factor(variable, levels=vars))
+
+# historical data
+h <- hist %>% filter(model == "IEA", region == "EU27", variable %in% vars, period >= 2005) %>% drop_na(value) %>% filter(value != 0) #, period <= 2020
+
+# harmonizing 2020 and 2025 values to match historical data
+h2018to2020 <- h %>%
+  filter(period %in% c(2018,2019,2020,2021,2022)) %>%
+  group_by(variable) %>%
+  summarize(hist=mean(value, na.rm=TRUE))
+
+plotData <- left_join(
+  plotDataOrig,
+  h2018to2020,
+  by = join_by(variable == variable)
+) %>%
+  group_by(scenario,variable) %>%
+  mutate(value = ifelse(period <= 2025, value*hist[period==2020]/value[period==2020], value)) %>% 
+  select(-hist) %>%
+  ungroup() %>%
   group_by(model,region,variable,period) %>% 
@@
          ribbon.min=min(value))
-
-# historical data
-h <- hist %>% filter(model == "IEA", region == "EU27", variable %in% vars, period >= 2005, period <= 2020) %>% drop_na(value) %>% filter(value != 0)
 
@@
 ```
+
+Figure 3. Fuel Supply and Demand. Primary Energy use (a), fossil energy carriers trade (b), Gases final energy demand (c), hydrogen production (d).
 
@@
     labs(title = "(d) Industrial sectors’ CO2 emissions\n(Mt CO2/yr)")
-    labs(title = expression(paste("(d) Industrial sectors’ ", CO[2], " emissions\n(Mt ", CO[2], "/yr)")))  +
+    #labs(title = expression(paste("(d) Industrial sectors’ ", CO[2], " emissions\n(Mt ", CO[2], "/yr)")))  +
     theme(plot.title = element_text(hjust=1))  
@@
 vars <- list(
-  #"Usage"
+  #"Destination"
   "e-liquids" = "Carbon Management|Usage|Synthetic Liquids",
@@
   "stored carbon" = "Carbon Management|Storage",
-  # "Capture type"
+  # "Origin"
   "atmospheric/biogenic" = "Carbon Management|Carbon Capture|atmospheric/biogenic CO2",
   "fossil" = "Carbon Management|Carbon Capture|fossil origin",
-  #"Capture"
+  #"Activity"
   "DAC" = "Carbon Management|Carbon Capture|DAC",
@@
                                          ), "Capture","CCS")))),
-    variable = factor(variable, levels=c( "Carbon Management|Usage|Synthetic Liquids", "Carbon Management|Usage|Synthetic Gases", "Carbon Management|Storage", "destination", "empty1", "empty2", "Carbon Management|Carbon Capture|atmospheric/biogenic CO2", "Carbon Management|Carbon Capture|fossil origin", "type",
-          #"empty1", "empty2", "Carbon Management|atmospheric/biogenic CO2 - CDR", "Carbon Management|CCS of fossil origin", "type",
+    variable = factor(variable, levels=c( "Carbon Management|Usage|Synthetic Liquids", "Carbon Management|Usage|Synthetic Gases", "Carbon Management|Storage", "destination", "empty1", "empty2", "Carbon Management|Carbon Capture|atmospheric/biogenic CO2", "Carbon Management|Carbon Capture|fossil origin", "origin",
+          #"empty1", "empty2", "Carbon Management|atmospheric/biogenic CO2 - CDR", "Carbon Management|CCS of fossil origin", "origin",
           #"Carbon Management|Storage|DAC", "Carbon Management|Storage|Biomass|Pe2Se", "Carbon Management|Storage|Fossil|Pe2Se", "Carbon Management|Storage|Industry CCS", "origin")
@@
           #"Carbon Management|Carbon Capture|Industry", "Carbon Management|Carbon Capture|Waste|Plastics Incineration"
-          , "origin")),
+          , "activity")),
          value = ifelse(grepl("Emi",variable,fixed = TRUE), -value, value))  %>% 
@@
   theme_doubleColumn() +
-  scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars), "empty1" = "transparent", "empty2" = "transparent", "destination" = "transparent", "type" = "transparent", "origin" = "transparent"),
+  scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars), "empty1" = "transparent", "empty2" = "transparent", "destination" = "transparent", "origin" = "transparent", "activity" = "transparent"),
                     labels = c(setNames(names(vars[!
@@
                                "Carbon Management|Carbon Capture|atmospheric/biogenic CO2" = "atmospheric",
-                               "empty1" = "", "empty2" = "or biogenic", "destination" = "Destination", "type" = "Type", "origin" = "Origin"), guide = guide_legend(nrow = 5, reverse = TRUE), drop = FALSE) +
+                               "empty1" = "", "empty2" = "or biogenic", "destination" = "Destination", "origin" = "Origin", "activity" = "Activity"), guide = guide_legend(nrow = 5, reverse = TRUE), drop = FALSE) +
   scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
@@
 ```
+
+Figure 4.
+Sectoral transformation indicators.
+(a) Transport final energy; (b) Light duty vehicles sales shares (bars) and share of ICEs in total LDV stock (line); (c) Useful energy demand for heating in buildings; (d) Industry emissions; (e) Carbon Capture and Storage by activity (upper bar), origin (middle bar) and by destination (lower bar).
 
@@
 #Emissions Reduction
-plotData <- rbind(
-    df %>% 
-      filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
+# plotData <- rbind(
+#     df %>% 
+#       filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
+#       calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
+#       mutate(value = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)) ,2)) %>% 
+#       select(-variable)
+#     ,
+#     df %>% 
+#       filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>%
+#       calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%
+#       mutate(value = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)) ,2)) %>% 
+#       select(-variable)
+#   ) %>%
+#   filter(tgt2050 != "Npi") %>%
+#   mutate(target = "Emissions\nreductions") %>%
+#   group_by(period) %>% 
+#   mutate(min = min(value),
+#         max = max(value))
+
+plotData <- df %>%
+  filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen) %>%
   calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
   mutate(value = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)) ,2)) %>%
-      select(-variable)
-    ,
-    df %>% 
-      filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>%
-      calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%
-      mutate(value = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)) ,2)) %>% 
-      select(-variable)
-  ) %>%
   filter(tgt2050 != "Npi") %>%
@@
 
-h <- refEmi %>% filter(variable == "Emissions with LULUCF and with international transport", region == "EU27", pollutant == "All greenhouse gases - (CO2 equivalent)") %>% ungroup() %>% select(region,variable,period,value)
-emi1990 <- tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)
+h <- refEmi %>% filter(variable == "Emissions with LULUCF and with intra-EU aviation", region == "EU27", pollutant == "All greenhouse gases - (CO2 equivalent)") %>% ungroup() %>% select(region,variable,period,value)
+emi1990 <- tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)
 reduction_h <- 1- (h %>% filter(period==2022) %>% pull(value) / emi1990)
 
-target <- data.frame(period = 2030, value = 0.57, label = "FitFor55")
+#target <- data.frame(period = 2030, value = 0.57, label = "FitFor55")
 
@@
 
-g[["milestone - violin targets"]] <- gridExtra::arrangeGrob(
+g[["Figure 5"]] <- gridExtra::arrangeGrob(
   g[["milestone - violin"]][["Emissions reductions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
@@
 
-ggsave(paste0(outChartsFolder,"/svg/Figure 5. Milestones Panel.svg"), g[["milestone - violin targets"]] , device="svg", width = 12, height = 14, dpi=100, units = "in")
-ggsave(paste0(outChartsFolder,"/png/Figure 5. Milestones Panel.png"), g[["milestone - violin targets"]] , device="png", width = 12, height = 14, dpi=300, units = "in")
+ggsave(paste0(outChartsFolder,"/svg/Figure 5.
+Comparison of key energy transformation indicators including fit-for-55 policy targets for 2030 and 2040.svg"), g[["Figure 5"]] , device="svg", width = 12, height = 14, dpi=100, units = "in")
+ggsave(paste0(outChartsFolder,"/png/Figure 5.
+Comparison of key energy transformation indicators including fit-for-55 policy targets for 2030 and 2040.png"), g[["Figure 5"]] , device="png", width = 12, height = 14, dpi=300, units = "in")
 
@@
 grid.newpage()
-grid.draw(g[["milestone - violin targets"]])
-
-```
+grid.draw(g[["Figure 5"]])
+
+```
+
+Figure 5.
+Comparison of key energy transformation indicators including fit-for-55 policy targets for 2030 and 2040.
+Red cross symbols represent the results of the reference scenario.
+Box-plots show the range from first to third quartile of the sensitivity scenarios, while the shaded areas show the distribution of the scenario results.
+More information about the chart symbols and indicators can be found at the supplementary notes.
 
@@
 
-### Supplementary Figure 1 - Variable renewables sensitivity panel
+### Supplementary figure 1. VRE sensitivity.
 
@@
 #value2040 <- plotData %>% filter( period == 2040) %>% group_by(scenario) %>% summarise(value = sum(value)) %>% pull(value)
-#round((1-value2040[2]/value2040[1])*100,2)
+#round((1-(value2040[2]/value2040[1]))*100,2)
 
@@
 
+#plotData %>% filter(scenario %in% c(mainScen,"Nzero_57_bio7p5_limVRE"))
+
 g[["limVRE target reduction"]] <- ggplot(plotData, aes(x = scenName, y = reduction, group=scenName)) +
@@
   theme_doubleColumn() +
+  #scale_y_continuous(breaks=c(1,0.95,0.9,0.85,0.8, 0.75), minor_breaks = NULL, labels = scales::percent) +
   scale_y_reverse(breaks=c(1,0.95,0.9,0.85,0.8, 0.75), minor_breaks = NULL, labels = scales::percent) +
@@
 
-ggsave(paste0(outChartsFolder,"/png/Supplementary figure 1. Variable Renewable Energy.png"), g[["Supplementary figure 1"]], device="png", width = 12, height = 6, dpi=300, units = "in")
-ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 1. Variable Renewable Energy.svg"), g[["Supplementary figure 1"]], device="svg", width = 12, height = 6, dpi=100, units = "in")
+ggsave(paste0(outChartsFolder,"/png/Supplementary figure 1. VRE sensitivity..png"), g[["Supplementary figure 1"]], device="png", width = 12, height = 6, dpi=300, units = "in")
+ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 1. VRE sensitivity..svg"), g[["Supplementary figure 1"]], device="svg", width = 12, height = 6, dpi=100, units = "in")
 
@@
 
+Supplementary figure 1.
+VRE sensitivity.
+(a) EU-27 Variable renewable energy capacity: reference scenario vs.
+limited VRE sensitivity.
+(b) 2040 emission reduction targets: default paper scenarios vs.
+limited VRE cases.
+
 ---
 
-### Supplementary Figure 2 - Mitigation costs panel
+### Supplementary figure 2. EU-27 carbon price
 
@@
 
-```{r supplChart_figure2a, echo=FALSE, include=FALSE}
+```{r supplChart_figure2a_lineplot, echo=FALSE, include=FALSE}
 
@@
   mutate(period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"),
-         value = currencyConversion*value)
+         value = currencyConversion*value,
+         tgt2030 = factor(tgt2030, levels=c(55,57,59)),
+         efficiency = factor(efficiency, levels=c("reference", "EED 2018 Eff", "FitFor55 eff", "RePowerEU eff")),
+         bioLim = factor(bioLim, levels=c("BioLim4", "BioLim7.5", "BioLim12", "BioLim20")),
+         lim = factor(lim, levels=c("default", "limCCS", "limH2", "limVRE"))
+         )
 
@@
 
-g[["Carbon Price"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
+g[["Carbon Price - line"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
   geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
@@
   theme(legend.spacing.y = unit(0.2, "lines")) +
-  labs(title = "(a) Carbon price (€/t CO2)") #+ 
+  labs(title = expression(paste("(a) Carbon price (€/t ", CO[2],")")))
+
   #theme(plot.title = element_text(hjust=-0.1))
@@
 
+```{r supplChart_figure2b_boxPlot, echo=FALSE, include=FALSE}
+
+vars <- c(
+  "Carbon price" = "Price|Carbon"
+)
+
+labels <- c(
+  "55"="55%",
+  "57"="57%",
+  "59"="59%",
+  "reference"="reference", 
+  "EED 2018 Eff"="EED 2018", 
+  "FitFor55 eff"="FitFor55", 
+  "RePowerEU eff"="RePowerEU",
+  "BioLim4"="limited\nto 4 EJ",
+  "BioLim7.5"="limited\nto 7.5 EJ", 
+  "BioLim12"="limited\nto 12 EJ", 
+  "BioLim20"="limited\nto 20 EJ",
+  "default"="default",
+  "limCCS"="limited\nCCS",
+  "limH2"="limited\nH2",
+  "limVRE"="limited\nVRE"
+)
+
+plotDataOrig <- df_beforeFilter %>%
+  filter(region == "EU27", period %in% c(2020,2030,2040,2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
+  mutate(#period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"),
+         value = currencyConversion*value,
+         tgt2030 = labels[as.character(tgt2030)],
+         efficiency = labels[as.character(efficiency)],
+         bioLim = labels[as.character(bioLim)],
+         lim =  labels[as.character(lim)]
+  ) %>%
+  mutate(tgt2030 = factor(tgt2030, levels=labels[c("55","57","59")]),
+         efficiency = factor(efficiency, levels=labels[c("reference", "EED 2018 Eff", "FitFor55 eff", "RePowerEU eff")]),
+         bioLim = factor(bioLim, levels=labels[c("BioLim4", "BioLim7.5", "BioLim12", "BioLim20")]),
+         lim = factor(lim, levels=labels[c("default", "limCCS", "limH2", "limVRE")])
+         )
+
+group_label <- c(
+  "tgt2030" = "Short-term\npolicy",
+  "efficiency" = "Efficiency\ntarget",
+  "bioLim" = "Biomass\navailability",
+  "lim" = "Technology\nevolution"
+)
+
+plotData <- do.call(rbind, lapply(names(group_label), function(x){
+  plotDataOrig %>% mutate(xLabel = (!! sym(x))) %>% group_by((!! sym(x))) %>% mutate(type=group_label[x]) %>% group_by((!! sym(x)),period) %>% mutate(min = min(value), max = max(value))
+})
+) %>%
+  mutate(type = factor(type, levels=group_label))
+
+g[["Carbon Price - boxplot"]] <- ggplot(plotData %>% filter(period == 2040), aes(x=xLabel, y=value)) +
+  geom_errorbar(mapping = aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=0.3) +
+  geom_point(data=plotData %>% filter(scenario == mainScen, period == 2040), shape=4, size = 1, stroke = 1.5, alpha = 0.6, color = "red") +
+  geom_hline(yintercept=0, color = "black", linewidth=1, alpha = 0.5) +
+  facet_grid(period~type, scales = "free_x") +
+  theme_doubleColumn() +
+  labs(title = expression(paste("(b) 2040 carbon price variation (€/t ", CO[2],")")))
+
+g[["Carbon Price - boxplot - all_years"]] <- ggplot(plotData, aes(x=xLabel, y=value)) +
+  geom_errorbar(mapping = aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +
+  geom_boxplot(outlier.shape = NA, width=0.3) +
+  geom_point(data=plotData %>% filter(scenario == mainScen), shape=4, size = 1, stroke = 1.5, alpha = 0.6, color = "red") +
+  geom_hline(yintercept=0, color = "black", linewidth=1, alpha = 0.5) +
+  facet_grid(period~type, scales = "free_x") +
+  theme_doubleColumn() +
+  labs(title = expression(paste("(b) 2040 carbon price variation (€/t ", CO[2],")")))
+
+#ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 2 - Mitigation costs panel - (b) Carbon Price.svg"), g[["Carbon Price - boxplot - all_years"]] , device="svg", width = 12, height = 12, dpi=100, units = "in")
+#ggsave(paste0(outChartsFolder,"/png/Supplementary figure 2 - Mitigation costs panel - (b) Carbon Price.png"), g[["Carbon Price - boxplot - all_years"]] , device="png", width = 12, height = 12, dpi=300, units = "in")
+
+```
+
 <!-- ```{r, echo=FALSE, fig.width=12, fig.height=5} -->
@@
 
-<!-- (b) Energy supply electricity investments (billion €/yr) -->
-
-```{r supplChart_figure2b, echo=FALSE, include=FALSE}
+```{r, echo=FALSE, include=FALSE}
+
+g[["Supplementary figure 2"]] <- gridExtra::arrangeGrob(
+  g[["Carbon Price - line"]], 
+  g[["Carbon Price - boxplot"]], 
+  layout_matrix = rbind(
+    c(1),
+    c(2)
+  ))
+
+ggsave(paste0(outChartsFolder,"/png/Supplementary figure 2. EU-27 carbon price.png"), g[["Supplementary figure 2"]], device="png", width = 12, height = 10, dpi=300, units = "in")
+ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 2. EU-27 carbon price.svg"), g[["Supplementary figure 2"]], device="svg", width = 12, height = 10, dpi=100, units = "in")
+
+```
+
+```{r, echo=FALSE, fig.width=12, fig.height=10}
+
+grid.newpage()
+grid.draw(g[["Supplementary figure 2"]])
+
+```
+
+Supplementary figure 2.
+EU-27 carbon price.
+Carbon price across all scenarios (a), and variation per sensitivity dimension (b).
+Red cross symbols in (b) represent the results of the reference scenario.
+Box-plots in (b) show the range from first to third quartile of the sensitivity scenarios.
+
+---
+
+### Supplementary figure 3. EU-27 mitigation costs.
+
+<!-- Energy Supply Investments (billion €/yr) -->
+
+```{r supplChart_figure3, echo=FALSE, include=FALSE}
 
@@
 
-g[["Energy Supply Investments"]] <- ggplot(plotData, aes(x=period,y=value, fill=variable)) +
+g[["Supplementary figure 3"]] <- ggplot(plotData, aes(x=period,y=value, fill=variable)) +
   geom_bar(stat='identity', position="stack") +
@@
         legend.key.width = unit(0.6,"cm")) +
-  theme(legend.position="left", legend.direction = "vertical", legend.box = "vertical",
+  theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical",
         legend.margin=margin(t = 40)) +
-  labs(title = "(b) Energy supply investments (billion €/yr) ") #+ 
+  labs(title = "Energy supply investments (billion €/yr) ") #+ 
   #theme(plot.title = element_text(hjust=-0.6))
 
-# ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 2 - Mitigation costs panel - (b) Energy Supply Investments.svg"), g[["Energy Supply Investments"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Supplementary figure 2 - Mitigation costs panel - (b) Energy Supply Investments.png"), g[["Energy Supply Investments"]] , device="png", width = 12, height = 6, dpi=300, units = "in")
-
-```
-
-<!-- ```{r, echo=FALSE, fig.width=12, fig.height=5} -->
-
-<!-- g[["Energy Supply Investments"]] -->
-
-<!-- ``` -->
-
-```{r, echo=FALSE, include=FALSE}
-
-g[["Supplementary figure 2"]] <- gridExtra::arrangeGrob(
-  g[["Carbon Price"]], 
-  g[["Energy Supply Investments"]], 
-  layout_matrix = rbind(
-    c(1),
-    c(2)
-  ))
-
-ggsave(paste0(outChartsFolder,"/png/Supplementary figure 2. EU-27 mitigation costs panel.png"), g[["Supplementary figure 2"]], device="png", width = 12, height = 10, dpi=300, units = "in")
-ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 2. EU-27 mitigation costs panel.svg"), g[["Supplementary figure 2"]], device="svg", width = 12, height = 10, dpi=100, units = "in")
-
-```
-
-```{r, echo=FALSE, fig.width=12, fig.height=10}
-
-grid.newpage()
-grid.draw(g[["Supplementary figure 2"]])
-
-```
+ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 3. EU-27 mitigation costs.svg"), g[["Supplementary figure 3"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
+ggsave(paste0(outChartsFolder,"/png/Supplementary figure 3. EU-27 mitigation costs.png"), g[["Supplementary figure 3"]] , device="png", width = 12, height = 6, dpi=300, units = "in")
+
+```
+
+```{r, echo=FALSE, fig.width=12, fig.height=5}
+
+g[["Supplementary figure 3"]]
+
+```
+Supplementary figure 3. EU-27 mitigation costs. Energy supply investments in the reference scenario.
 
@@
 
-### Supplementary Figure 3 - Country results electricity capacity panel (GW)
-
-```{r supplChart_figure3, echo=FALSE, include=FALSE}
+### SSupplementary figure 4. EU-27 Electricity capacity
+
+```{r supplChart_figure4, echo=FALSE, include=FALSE}
 
@@
   "DEU" = "Germany",
-  "FRA" = "France"
-)
+  "FRA" = "France"#,
+#  "EUN" = "EU North",
+#  "EUC" = "EU Central",
+#  "EUS" = "EU South"
+)
+
+regAggList <- list(
+  "EU27" = "EU27",
+  "DEU" = "DEU",
+  "FRA" = "FRA"#,
+#  "EUN" = c("EWN", "ENC"),
+#  "EUC" = c("ECS", "ECE"),
+#  "EUS" = c("ESW", "ESC")
+)
+
+regAgg <- NULL
+for(rAgg in names(regAggList)){
+  for(r in regAggList[[rAgg]]){
+    v <- rAgg
+    names(v) <- r
+    regAgg <- c(regAgg,v)
+  }
+}
+
+df %>% filter(region == "EWN")
 
 plotData <- df %>% 
-  filter(region %in% c("EU27","DEU","FRA"), period >= 2020, period <= 2050, scenario  == mainScen, variable %in% unlist(vars)) %>% 
+  filter(region %in% names(unlist(regAgg)), period >= 2020, period <= 2050, scenario  == mainScen, variable %in% unlist(vars)) %>% 
   mutate(variable = factor(variable, levels=rev(vars)),
-         region = factor(region, levels=c("EU27","DEU","FRA"))) %>% 
-  arrange(factor(variable, levels = rev(vars))) %>%
-  mutate(regionName = regName[region])
-
-g[["Capacity"]] <- lapply(setNames(c("EU27","DEU","FRA"),c("EU27","DEU","FRA")), function(reg){
-  gg <- ggplot(plotData %>% filter(region == reg),aes(x=period,y=value)) +
+         regAgg = regAgg[as.character(region)]) %>%
+  mutate(regAgg = factor(regAgg, levels=names(regAggList))) %>% 
+  group_by(model,scenario,regAgg,period,variable) %>%
+  summarize(value = sum(value),.groups = "keep") %>%
+  group_by(model,scenario,regAgg,period) %>%
+  mutate(regionName = regName[regAgg])
+
+g[["Capacity"]] <- lapply(setNames(names(regAggList),names(regAggList)), function(reg){
+  gg <- ggplot(plotData %>% filter(regAgg == reg),aes(x=period,y=value)) +
     geom_area(aes(fill=variable),alpha=0.8) +
@@
     theme(axis.title.y=element_blank()) +
-  theme(strip.clip = "off")
+    theme(strip.clip = "off") + 
+    theme(plot.margin=margin(b=0))
+  #if(reg %in% c("EU27","DEU","FRA"))
+  #  gg <- gg +
+  #    theme(axis.text.x=element_blank())
+  return(gg)
 })
 
-g[["Capacity_2040"]] <- lapply(setNames(c("EU27","DEU","FRA"),c("EU27","DEU","FRA")), function(reg){
-  gg <- ggplot(plotData %>%
-                 filter(region == reg, period == 2040) %>%
-                 group_by(model,scenario,region,period) %>%
-                 mutate(n = sum(value), percentage = value / n),
-               aes(x=period,y=percentage)) +
-  geom_bar(aes(fill=variable),alpha=0.8,stat='identity') +
+g[["Capacity_2040"]] <- lapply(setNames(names(regAggList),names(regAggList)), function(reg){
+  pData <- plotData %>%
+    filter(regAgg == reg, period == 2040) %>%
+    arrange(factor(variable, levels = vars)) %>%
+    group_by(model,scenario,regAgg,period) %>%
+    mutate(cumValue = cumsum(value),
+         n = sum(value),
+         percentage = value / n,
+         cumPercentage = cumValue / n)
+  gg <- ggplot(pData,aes(x=period,y=percentage)) +
+    geom_bar(aes(fill=variable),alpha=0.8,stat='identity', width=0.7) +
+    geom_text_repel(data=pData %>% filter(percentage >= 0.02),aes(label = paste0(round(percentage,2)*100,"%"), y=cumPercentage-percentage/2, x = 2040), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geomText.size*0.65,
+                    box.padding = 0, direction = "y", nudge_x = -1.6, segment.color = 'transparent') +
+                    #box.padding = 0.1, direction = "y", max.iter = 5, nudge_x = -1) +
+
+                    #direction = "y",box.padding=0) +
+    #geom_text(data=pData %>% filter(percentage >= 0.02),aes(label = paste0(round(percentage,2)*100,"%"), y=cumPercentage-percentage/2, x = 2039.5), vjust=0.5, hjust=1, na.rm=TRUE, color = "black", size=geomText.size*0.65) +
     facet_wrap(~period, scales = "free_y") +
@@
     scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) + 
+    coord_cartesian(clip="off") +
     theme(legend.position="none") +
     theme(axis.title.y=element_blank()) +
-  theme(strip.clip = "off")
+    theme(axis.text.y=element_blank()) +
+    theme(strip.clip = "off") + 
+    theme(plot.margin=margin(0,20,46,0)) #t, r, b, l
+  #if(reg %in% c("EU27","DEU","FRA")){
+  #  gg <- gg +
+  #    theme(axis.text.x=element_blank())
+  #} else {
+  #  gg <- gg +
+  #    theme(plot.margin=margin(0,20,45,0)) #t, r, b, l
+  #}
+  return(gg)
+})
+
+## Function to extract legend
+g_legend <- function(a.gplot){ 
+    tmp <- ggplot_gtable(ggplot_build(a.gplot)) 
+    leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box") 
+    legend <- tmp$grobs[[leg]] 
+    legend
+}
+
+legend <- g_legend(
+  ggplot(plotData,aes(x=period,y=value)) +
+  geom_area(aes(fill=variable),alpha=0.8) +
+  theme_doubleColumn() +
+  scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
+  guides(fill=guide_legend(nrow=3,override.aes = list(alpha=1))) +
+  theme(#legend.text = element_text(size = theme.double.text.size),
+        #legend.key.height = unit(0.8, "cm"),
+        #legend.key.width = unit(0.8,"cm"),
+        legend.spacing.x = unit(0.3, 'cm')) +
+  theme(legend.title=element_blank(),
+        legend.margin=margin(c(0,0,0,0))) +
+  theme(plot.margin=margin(0,0,0,0)) + 
+  theme(legend.margin=margin(l=-10, t= 20))
+)
+
+tg <- textGrob('     Electricity Capacity (GW)', x = 0, y = 0, gp = gpar(fontsize = theme_doubleColumn()$plot.title$size, fontface = "plain"), just = "left", hjust=0, vjust=-1)
+
+g[["Supplementary figure 4"]] <- gridExtra::arrangeGrob(
+  tg,
+  g[["Capacity"]][["EU27"]],
+  g[["Capacity_2040"]][["EU27"]],
+  g[["Capacity"]][["DEU"]],
+  g[["Capacity_2040"]][["DEU"]],
+  g[["Capacity"]][["FRA"]],
+  g[["Capacity_2040"]][["FRA"]],
+  #g[["Capacity"]][["EUN"]],
+  #g[["Capacity_2040"]][["EUN"]],
+  #g[["Capacity"]][["EUS"]],
+  #g[["Capacity_2040"]][["EUS"]],
+  #g[["Capacity"]][["EUC"]],
+  #g[["Capacity_2040"]][["EUC"]],
+  legend,
+  layout_matrix = rbind(rep(1,18),
+                        c(2,2,2,2, 3,3, 4,4,4,4, 5,5, 6,6,6,6, 7,7),
+                        c(2,2,2,2, 3,3, 4,4,4,4, 5,5, 6,6,6,6, 7,7),
+                        c(2,2,2,2, 3,3, 4,4,4,4, 5,5, 6,6,6,6, 7,7),
+                        c(2,2,2,2, 3,3, 4,4,4,4, 5,5, 6,6,6,6, 7,7),
+                        c(2,2,2,2, 3,3, 4,4,4,4, 5,5, 6,6,6,6, 7,7),
+                        c(2,2,2,2, 3,3, 4,4,4,4, 5,5, 6,6,6,6, 7,7),
+                        # c(7,7,7,7, 8,8, 9,9,9,9, 10,10, 11,11,11,11, 12,12),
+                        # c(7,7,7,7, 8,8, 9,9,9,9, 10,10, 11,11,11,11, 12,12),
+                        # c(7,7,7,7, 8,8, 9,9,9,9, 10,10, 11,11,11,11, 12,12),
+                        # c(7,7,7,7, 8,8, 9,9,9,9, 10,10, 11,11,11,11, 12,12),
+                        # c(7,7,7,7, 8,8, 9,9,9,9, 10,10, 11,11,11,11, 12,12),
+                        # c(7,7,7,7, 8,8, 9,9,9,9, 10,10, 11,11,11,11, 12,12),
+                        # rep(13,18),
+                        # rep(13,18))
+                        rep(8,18),
+                        rep(8,18))
+  )
+
+ ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 4. EU-27 Electricity capacity.svg"), g[["Supplementary figure 4"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
+ ggsave(paste0(outChartsFolder,"/png/Supplementary figure 4. EU-27 Electricity capacity..png"), g[["Supplementary figure 4"]] , device="png", width = 12, height = 6, dpi=300, units = "in")
+
+```
+
+```{r, echo=FALSE, fig.width=12, fig.height=6}
+
+grid.newpage()
+grid.draw(g[["Supplementary figure 4"]])
+
+```
+
+Supplementary figure 4. EU-27 Electricity capacity. EU-27, Germany, and France electricity capacity (GW)  in the reference scenario.
+
+### Supplementary figure 5. EU-27 Electricity generation
+
+```{r supplChart_figure5, echo=FALSE, include=FALSE}
+
+vars <- c(
+  #"Net Imports" = "SE|Electricity|Net Imports",
+  "Coal w/ CC" = "SE|Electricity|Coal|w/ CC",
+  "Coal w/o CC" = "SE|Electricity|Coal|w/o CC",
+  "Oil" = "SE|Electricity|Oil",
+  "Gas w/ CC" = "SE|Electricity|Gas|w/ CC",
+  "Gas w/o CC" = "SE|Electricity|Gas|w/o CC",
+  "Hydrogen" = "SE|Electricity|Hydrogen",
+  "Nuclear" = "SE|Electricity|Nuclear",
+  "Geothermal" = "SE|Electricity|Geothermal",
+  "Hydro" = "SE|Electricity|Hydro",
+  "Biomass w/ CC" = "SE|Electricity|Biomass|w/ CC",
+  "Biomass w/o CC" = "SE|Electricity|Biomass|w/o CC",
+  "Solar CSP" = "SE|Electricity|Solar|CSP",
+  "Solar PV" = "SE|Electricity|Solar|PV",
+  "Wind Onshore" = "SE|Electricity|Wind|Onshore",
+  "Wind Offshore" = "SE|Electricity|Wind|Offshore")
+
+#inv_vars <- setNames(names(vars),vars)
+
+color <- c(
+  #"Net Imports"   = "#472b62",
+  "Coal w/ CC"    = "#b2b2b2",
+  "Coal w/o CC"   = "#0c0c0c",
+  "Oil"           = "#b30000",
+  "Gas w/ CC"     = "#b79e38",
+  "Gas w/o CC"    = "#999959",
+  "Hydrogen"      = "#5ed5b0",
+  "Nuclear"       = "#ff33ff",
+  "Geothermal"    = "#e51900",
+  "Hydro"         = "#191999",
+  "Biomass w/ CC" = "#33ff00",
+  "Biomass w/o CC"= "#005900",
+  "Solar CSP"     = "#ffcc00",
+  "Solar PV"      = "#ffe600",
+  "Wind Onshore"  = "#193F7F",
+  "Wind Offshore" = "#337fff")
+
+regName <- c(
+  "EU27" = "European Union",
+  "DEU" = "Germany",
+  "FRA" = "France",
+  "EUN" = "EU North",
+  "EUC" = "EU Central",
+  "EUS" = "EU South"
+)
+
+regAggList <- list(
+  "EU27" = "EU27",
+  "DEU" = "DEU",
+  "FRA" = "FRA",
+  "EUN" = c("EWN", "ENC"),
+  "EUC" = c("ECS", "ECE"),
+  "EUS" = c("ESW", "ESC")
+)
+
+regAgg <- NULL
+for(rAgg in names(regAggList)){
+  for(r in regAggList[[rAgg]]){
+    v <- rAgg
+    names(v) <- r
+    regAgg <- c(regAgg,v)
+  }
+}
+
+df %>% filter(region == "EWN")
+
+plotData <- df %>% 
+  filter(region %in% names(unlist(regAgg)), period >= 2020, period <= 2050, scenario  == mainScen, variable %in% unlist(vars)) %>% 
+  mutate(variable = factor(variable, levels=rev(vars)),
+         regAgg = regAgg[as.character(region)]) %>%
+  mutate(regAgg = factor(regAgg, levels=names(regAggList))) %>% 
+  group_by(model,scenario,regAgg,period,variable) %>%
+  summarize(value = sum(value),.groups = "keep") %>%
+  group_by(model,scenario,regAgg,period) %>%
+  mutate(regionName = regName[regAgg],
+         value = round(value * EJ2TWh))
+
+g[["Generation"]] <- lapply(setNames(names(regAggList),names(regAggList)), function(reg){
+  gg <- ggplot(plotData %>% filter(regAgg == reg),aes(x=period,y=value)) +
+    geom_area(aes(fill=variable),alpha=0.8) +
+    facet_wrap(~regionName, scales = "free_y") +
+    theme_doubleColumn() +
+    scale_x_continuous(breaks=c(2020,2030,2040,2050)) +
+    scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
+    theme(legend.position="none") +
+    theme(axis.title.y=element_blank()) +
+    theme(strip.clip = "off") + 
+    theme(plot.margin=margin(b=0))
+  if(reg %in% c("EU27","DEU","FRA"))
+    gg <- gg +
+      theme(axis.text.x=element_blank())
+  return(gg)
+})
+
+g[["Generation_2040"]] <- lapply(setNames(names(regAggList),names(regAggList)), function(reg){
+  pData <- plotData %>%
+    filter(regAgg == reg, period == 2040) %>%
+    arrange(factor(variable, levels = vars)) %>%
+    group_by(model,scenario,regAgg,period) %>%
+    mutate(cumValue = cumsum(value),
+         n = sum(value),
+         percentage = value / n,
+         cumPercentage = cumValue / n)
+  gg <- ggplot(pData,aes(x=period,y=percentage)) +
+    geom_bar(aes(fill=variable),alpha=0.8,stat='identity', width=0.7) +
+    geom_text_repel(data=pData %>% filter(percentage >= 0.02),aes(label = paste0(round(percentage,2)*100,"%"), y=cumPercentage-percentage/2, x = 2040), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geomText.size*0.65,
+                    box.padding = 0, direction = "y", nudge_x = -1.6, segment.color = 'transparent') +
+                    #box.padding = 0.1, direction = "y", max.iter = 5, nudge_x = -1) +
+
+                    #direction = "y",box.padding=0) +
+    #geom_text(data=pData %>% filter(percentage >= 0.02),aes(label = paste0(round(percentage,2)*100,"%"), y=cumPercentage-percentage/2, x = 2039.5), vjust=0.5, hjust=1, na.rm=TRUE, color = "black", size=geomText.size*0.65) +
+    facet_wrap(~period, scales = "free_y") +
+    theme_doubleColumn() +
+    scale_y_continuous(labels = scales::percent) +
+    scale_x_discrete(breaks=c(2040)) +
+    scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) + 
+    coord_cartesian(clip="off") +
+    theme(legend.position="none") +
+    theme(axis.title.y=element_blank()) +
+    theme(axis.text.y=element_blank()) +
+    theme(strip.clip = "off") + 
+    theme(plot.margin=margin(0,20,5,0)) #t, r, b, l
+  if(reg %in% c("EU27","DEU","FRA")){
+    gg <- gg +
+      theme(axis.text.x=element_blank())
+  } else {
+    gg <- gg +
+      theme(plot.margin=margin(0,20,45,0)) #t, r, b, l
+  }
+  return(gg)
 })
@@
 
-g[["Supplementary Figure 3 - Country results electricity capacity panel (GW)"]] <- gridExtra::arrangeGrob(
-  g[["Capacity"]][["EU27"]] + theme(plot.margin=margin(b=0)), #+ theme(plot.margin=margin(80,5,50,0)), #margin(t = 0, r = 0, b = 0, l = 0
-  g[["Capacity_2040"]][["EU27"]] + theme(plot.margin=margin(0,20,37,0)), #+ theme(plot.margin=margin(80,5,50,0)), #margin(t = 0, r = 0, b = 0, l = 0
-  g[["Capacity"]][["DEU"]] + theme(plot.margin=margin(b=0)), #+ theme(plot.margin=margin(80,5,50,0)), #margin(t = 0, r = 0, b = 0, l = 0
-  g[["Capacity_2040"]][["DEU"]] + theme(plot.margin=margin(0,20,37,0)), #+ theme(plot.margin=margin(80,5,50,0)), #margin(t = 0, r = 0, b = 0, l = 0
-  g[["Capacity"]][["FRA"]] + theme(plot.margin=margin(b=0)), #+ theme(plot.margin=margin(80,5,50,0)), #margin(t = 0, r = 0, b = 0, l = 0
-  g[["Capacity_2040"]][["FRA"]] + theme(plot.margin=margin(0,20,37,0)), #+ theme(plot.margin=margin(80,5,50,0)), #margin(t = 0, r = 0, b = 0, l = 0
+tg <- textGrob('     Electricity Generation (TWh)', x = 0, y = 0, gp = gpar(fontsize = theme_doubleColumn()$plot.title$size, fontface = "plain"), just = "left", hjust=0, vjust=-1)
+
+g[["Supplementary figure 5"]] <- gridExtra::arrangeGrob(
+  tg,
+  g[["Generation"]][["EU27"]],
+  g[["Generation_2040"]][["EU27"]],
+  g[["Generation"]][["DEU"]],
+  g[["Generation_2040"]][["DEU"]],
+  g[["Generation"]][["FRA"]],
+  g[["Generation_2040"]][["FRA"]],
+  g[["Generation"]][["EUN"]],
+  g[["Generation_2040"]][["EUN"]],
+  g[["Generation"]][["EUC"]],
+  g[["Generation_2040"]][["EUC"]],
+  g[["Generation"]][["EUS"]],
+  g[["Generation_2040"]][["EUS"]],
   legend,
-  layout_matrix = rbind(c(1,1,1,1, 2,2, 3,3,3,3, 4,4, 5,5,5,5, 6,6),
-                        c(1,1,1,1, 2,2, 3,3,3,3, 4,4, 5,5,5,5, 6,6),
-                        c(1,1,1,1, 2,2, 3,3,3,3, 4,4, 5,5,5,5, 6,6),
-                        rep(7,18))
-  )
-
- ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 3 - Country results electricity capacity panel (GW).svg"), g[["Supplementary Figure 3 - Country results electricity capacity panel (GW)"]] , device="svg", width = 12, height = 5, dpi=100, units = "in")
- ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 3 - Country results electricity capacity panel (GW).png"), g[["Supplementary Figure 3 - Country results electricity capacity panel (GW)"]] , device="png", width = 12, height = 5, dpi=300, units = "in")
-
-```
-
-```{r, echo=FALSE, fig.width=12, fig.height=5}
+  layout_matrix = rbind(rep(1,18),
+                        c(2,2,2,2, 3,3, 4,4,4,4, 5,5, 6,6,6,6, 7,7),
+                        c(2,2,2,2, 3,3, 4,4,4,4, 5,5, 6,6,6,6, 7,7),
+                        c(2,2,2,2, 3,3, 4,4,4,4, 5,5, 6,6,6,6, 7,7),
+                        c(2,2,2,2, 3,3, 4,4,4,4, 5,5, 6,6,6,6, 7,7),
+                        c(2,2,2,2, 3,3, 4,4,4,4, 5,5, 6,6,6,6, 7,7),
+                        c(2,2,2,2, 3,3, 4,4,4,4, 5,5, 6,6,6,6, 7,7),
+                        c(8,8,8,8, 9,9, 10,10,10,10,  11,11, 12,12,12,12, 13,13),
+                        c(8,8,8,8, 9,9, 10,10,10,10,  11,11, 12,12,12,12, 13,13),
+                        c(8,8,8,8, 9,9, 10,10,10,10,  11,11, 12,12,12,12, 13,13),
+                        c(8,8,8,8, 9,9, 10,10,10,10,  11,11, 12,12,12,12, 13,13),
+                        c(8,8,8,8, 9,9, 10,10,10,10,  11,11, 12,12,12,12, 13,13),
+                        c(8,8,8,8, 9,9, 10,10,10,10,  11,11, 12,12,12,12, 13,13),
+                        c(8,8,8,8, 9,9, 10,10,10,10,  11,11, 12,12,12,12, 13,13),
+                        rep(14,18),
+                        rep(14,18))
+#                        rep(7,18))
+  )
+
+ ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 5. EU-27 Electricity generation.svg"), g[["Supplementary figure 5"]] , device="svg", width = 12, height = 10, dpi=100, units = "in")
+ ggsave(paste0(outChartsFolder,"/png/Supplementary figure 5. EU-27 Electricity generation.png"), g[["Supplementary figure 5"]] , device="png", width = 12, height = 10, dpi=300, units = "in")
+
+```
+
+```{r, echo=FALSE, fig.width=12, fig.height=10}
 
 grid.newpage()
-grid.draw(g[["Supplementary Figure 3 - Country results electricity capacity panel (GW)"]])
-
-```
+grid.draw(g[["Supplementary figure 5"]])
+
+```
+
+Supplementary figure 5.
+EU-27 Electricity generation.
+EU-27, Germany, France, north EU countries (EUN), central and east EU countries (EU Central), south and west EU countries (EU South), electricity generation (TWh) in the reference scenario.
 
@@
 
-### Supplementary Figure 4 - Sectoral mitigation - Energy and non-energy use panel
+### Supplementary figure 6. EU-27 Emissions
 
@@
 
-```{r supplChart_figure4a, echo=FALSE, include=FALSE}
+```{r supplChart_figure6a, echo=FALSE, include=FALSE}
+
+# vars <- list(
+#   "Transport  - Electricity" = "FE|Transport|w/o Bunkers|Electricity",
+#   "Bunkers    - Electricity" = "FE|Transport|Bunkers|Electricity",
+#   "Buildings  - Electricity" = "FE|Buildings|Electricity",
+#   "Industry   - Electricity" = "FE|Industry|Electricity",
+#   "Transport  - Hydrogen"    = "FE|Transport|w/o Bunkers|Hydrogen",
+#   "Bunkers    - Hydrogen"    = "FE|Transport|Bunkers|Hydrogen",
+#   "Buildings  - Hydrogen"    = "FE|Buildings|Hydrogen",
+#   "Industry   - Hydrogen"    = "FE|Industry|Hydrogen",
+#   "Buildings  - Heat"        = "FE|Buildings|Heat",
+#   "Industry   - Heat"        = "FE|Industry|Heat",
+#   "Transport  - Gases"       = "FE|Transport|w/o Bunkers|Gases",
+#   "Bunkers    - Gases"       = "FE|Transport|Bunkers|Gases",
+#   "Buildings  - Gases"       = "FE|Buildings|Gases",
+#   "Industry   - Gases"       = "FE|Industry|Gases",
+#   "Non-energy - Gases"       = "FE|Non-energy Use|Industry|Gases",
+#   "Transport  - Liquids"     = "FE|Transport|w/o Bunkers|Liquids",
+#   "Bunkers    - Liquids"     = "FE|Transport|Bunkers|Liquids",
+#   "Buildings  - Liquids"     = "FE|Buildings|Liquids",
+#   "Industry   - Liquids"     = "FE|Industry|Liquids",
+#   "Non-energy - Liquids"     = "FE|Non-energy Use|Industry|Liquids",
+#   "Buildings  - Solids"      = "FE|Buildings|Solids",
+#   "Industry   - Solids"      = "FE|Industry|Solids",
+#   "Non-energy - Solids"      = "FE|Non-energy Use|Industry|Solids"
+# )
+# 
+# # vars <- list(
+# #   "Transport  - Electricity" = "FE|Transport|w/o Bunkers|Electricity",
+# #   "Bunkers    - Electricity" = "FE|Transport|Bunkers|Electricity",
+# #   "Buildings  - Electricity" = "FE|Buildings|Electricity",
+# #   "Industry   - Electricity" = "FE|Industry|Electricity",
+# #   "Transport  - Hydrogen"    = "FE|Transport|w/o Bunkers|Hydrogen",
+# #   "Bunkers    - Hydrogen"    = "FE|Transport|Bunkers|Hydrogen",
+# #   "Buildings  - Hydrogen"    = "FE|Buildings|Hydrogen",
+# #   "Industry   - Hydrogen"    = "FE|Industry|Hydrogen",
+# #   "Buildings  - Heat"        = "FE|Buildings|Heat",
+# #   "Industry   - Heat"        = "FE|Industry|Heat",
+# #   "Transport  - Gases"       = "FE|Transport|w/o Bunkers|Gases",
+# #   "Bunkers    - Gases"       = "FE|Transport|Bunkers|Gases",
+# #   "Buildings  - Gases"       = "FE|Buildings|Gases",
+# #   "Industry   - Gases"       = "FE|w/o Non-energy Use|Industry|Gases",
+# #   "Non-energy - Gases"       = "FE|Non-energy Use|Industry|Gases",
+# #   "Transport  - Liquids"     = "FE|Transport|w/o Bunkers|Liquids",
+# #   "Bunkers    - Liquids"     = "FE|Transport|Bunkers|Liquids",
+# #   "Buildings  - Liquids"     = "FE|Buildings|Liquids",
+# #   "Industry   - Liquids"     = "FE|w/o Non-energy Use|Industry|Liquids",
+# #   "Non-energy - Liquids"     = "FE|Non-energy Use|Industry|Liquids",
+# #   "Buildings  - Solids"      = "FE|Buildings|Solids",
+# #   "Industry   - Solids"      = "FE|w/o Non-energy Use|Industry|Solids",
+# #   "Non-energy - Solids"      = "FE|Non-energy Use|Industry|Solids"
+# # )
+# 
+# plotColor <- list(
+#   "Transport  - Electricity" = "#ffed9e",
+#   "Bunkers    - Electricity" = "#ffb84c",
+#   "Buildings  - Electricity" = "#ffd27d",
+#   "Industry   - Electricity" = "#fa8c02",
+#   "Transport  - Hydrogen" = "#b8d8be",
+#   "Bunkers    - Hydrogen" = "#31a354",
+#   "Buildings  - Hydrogen" = "#a1d99b",
+#   "Industry   - Hydrogen" = "#2b7c0d",
+#   "Buildings  - Heat" = "#b92400",
+#   "Industry   - Heat" = "#800000",
+#   "Transport  - Gases" = "#9d74b0",
+#   "Bunkers    - Gases" = "#800080",
+#   "Buildings  - Gases" = "#c7a3d4",
+#   "Industry   - Gases" = "#610d85",
+#   "Non-energy - Gases" = "#c875ec",
+#   "Transport  - Liquids" = "#accbff",
+#   "Bunkers    - Liquids" = "#649eff",
+#   "Buildings  - Liquids" = "#98c1d9",
+#   "Industry   - Liquids" = "#3d5a80",
+#   "Non-energy - Liquids" = "#92bbff",
+#   "Buildings  - Solids" = "#a5a5a5",
+#   "Industry   - Solids" = "#1b1b1b",
+#   "Non-energy - Solids" = "#909090"
+# )
+# 
+# plotData <- df %>%
+#   filter(region == "EU27", period %in% c(2010:2050), variable %in% vars, scenario == mainScen) %>%
+#   mutate(variable=factor(variable, levels=vars))
+#   
+# #total
+# totalData <- df %>%
+#   filter(region == "EU27", period %in% c(2010:2050), variable == "FE", scenario == mainScen)
+# 
+# if(energyInMtoe){
+#   plotData <- plotData %>%
+#     mutate(
+#       value = value*EJ2Mtoe,
+#       unit  = "Mtoe/yr")
+#   totalData <- totalData %>%
+#     mutate(
+#       value = value*EJ2Mtoe,
+#       unit  = "Mtoe/yr")
+# }
+# 
+# g[["Supplementary Figure 4a. Final energy demand per sector and carrier"]] <- ggplot(plotData,aes(x=period,y=value)) +
+#   geom_area(aes(fill=variable), alpha = 0.8) +
+#   geom_line(data=totalData, linewidth = 1, color="black") +
+#   geom_vline(xintercept=2020, color = "black", linetype="dashed", linewidth=1, alpha = 0.5) +
+#   geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
+#   theme_doubleColumn() +
+#   #ylab("Final Energy Demand - EJ/yr") + 
+#   #ggtitle("(a) per sector and carrier") +
+#   scale_fill_manual(values = setNames(plotColor[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(ncol = 3)) +
+#   theme(legend.margin=margin(l = -1, unit='cm')) +
+#   scale_x_continuous(breaks=c(2010, 2010, 2020,2030,2040,2050)) + 
+#   theme(axis.title.x=element_blank()) +
+#   theme(axis.title.y=element_blank()) +
+#   theme(legend.title = element_blank()) +
+#   theme(legend.text = element_text(size = theme.double.text.size*0.8),
+#         #legend.key.height = unit(0.7, "cm"),
+#         #legend.key.width = unit(0.7,"cm"),
+#         legend.spacing.x = unit(0.2, 'cm')) + 
+#   #  theme(plot.title = element_text(size = 1.2*theme.double.text.size)) +
+#   labs(title = paste0("(a) Energy and non-energy use\nper sector and carrier (", unique(plotData$unit), ")")) +
+#   theme(plot.title = element_text(hjust=0))
+#
 
 vars <- list(
-  "Transport - Electricity" = "FE|Transport|Electricity",
-  "Buildings - Electricity" = "FE|Buildings|Electricity",
-  "Industry  - Electricity" = "FE|Industry|Electricity",
-  "Transport - Hydrogen" = "FE|Transport|Hydrogen",
-  "Buildings - Hydrogen" = "FE|Buildings|Hydrogen",
-  "Industry  - Hydrogen" = "FE|Industry|Hydrogen",
-  "Buildings - Heat" = "FE|Buildings|Heat",
-  "Industry  - Heat" = "FE|Industry|Heat",
-  "Transport - Gases" = "FE|Transport|Gases",
-  "Buildings - Gases" = "FE|Buildings|Gases",
-  "Industry  - Gases" = "FE|Industry|Gases",
-  "Transport - Liquids" = "FE|Transport|Liquids",
-  "Buildings - Liquids" = "FE|Buildings|Liquids",
-  "Industry  - Liquids" = "FE|Industry|Liquids",
-  "Buildings - Solids" = "FE|Buildings|Solids",
-  "Industry  - Solids" = "FE|Industry|Solids"
+  "Non-Energy Use"=c(
+    "Industry - Gases"   ="FE|Non-energy Use|Industry|Gases",
+    "Industry - Liquids" ="FE|Non-energy Use|Industry|Liquids",
+    "Industry - Solids"  ="FE|Non-energy Use|Industry|Solids"
+  ),
+  # "Industry"=c(
+  #   "Industry - Electricity"="FE|Industry|Electricity",
+  #   "Industry - Hydrogen"   ="FE|Industry|Hydrogen",
+  #   "Industry - Heat"       ="FE|Industry|Heat",
+  #   "Industry - Gases"      ="FE|Industry|Gases",
+  #   "Industry - Liquids"    ="FE|Industry|Liquids",
+  #   "Industry - Solids"     ="FE|Industry|Solids"
+  # ),
+  "Industry"=c(
+    "Industry - Electricity"="FE|Industry|Electricity",
+    "Industry - Hydrogen"   ="FE|Industry|Hydrogen",
+    "Industry - Heat"       ="FE|Industry|Heat",
+    "Industry - Gases"      ="FE|w/o Non-energy Use|Industry|Gases",
+    "Industry - Liquids"    ="FE|w/o Non-energy Use|Industry|Liquids",
+    "Industry - Solids"     ="FE|w/o Non-energy Use|Industry|Solids"
+  ),
+  "Buildings"=c(
+    "Buildings - Electricity"="FE|Buildings|Electricity",
+    "Buildings - Hydrogen"   ="FE|Buildings|Hydrogen",
+    "Buildings - Heat"       ="FE|Buildings|Heat",
+    "Buildings - Gases"      ="FE|Buildings|Gases",
+    "Buildings - Liquids"    ="FE|Buildings|Liquids",
+    "Buildings - Solids"     ="FE|Buildings|Solids"
+  ),
+  "Bunkers"=c(
+    "Transport - Electricity"="FE|Transport|Bunkers|Electricity",
+    "Transport - Hydrogen"   ="FE|Transport|Bunkers|Hydrogen",
+    "Transport - Gases"      ="FE|Transport|Bunkers|Gases",
+    "Transport - Liquids"    ="FE|Transport|Bunkers|Liquids"
+  ),
+  "Transport"=c(
+    "Transport - Electricity"="FE|Transport|w/o Bunkers|Electricity",
+    "Transport - Hydrogen"   ="FE|Transport|w/o Bunkers|Hydrogen",
+    "Transport - Gases"      ="FE|Transport|w/o Bunkers|Gases",
+    "Transport - Liquids"    ="FE|Transport|w/o Bunkers|Liquids"
+  )
 )
@@
   "Industry - Electricity" = "#fa8c02",
-  "Transport - Hydrogen" = "#46fc02",
-  "Buildings - Hydrogen" = "#94ff6c",
+  "Transport - Hydrogen" = "#31a354",
+  "Buildings - Hydrogen" = "#a1d99b",
   "Industry - Hydrogen" = "#2b7c0d",
-  "Buildings - Heat" = "#ff7a59",
-  "Industry  - Heat" = "#b92400",
+  "empty" = "transparent",
+  "Buildings - Heat" = "#b92400",
+  "Industry - Heat" = "#800000",
   "Transport - Gases" = "#b200ff",
@@
   "Industry - Liquids" = "#04167c",
+  "empty2" = "transparent",
   "Buildings - Solids" = "#a5a5a5",
@@
 
+pattern <- c(
+  "Non-Energy Use"="stripe",
+  "Industry"="none",
+  "Buildings"="none",
+  "Bunkers"="stripe",
+  "Transport"="none"
+)
+
+patternAngle <- c(
+  "Non-Energy Use"=45,
+  "Industry"=45,
+  "Buildings"=45,
+  "Bunkers"=135,
+  "Transport"=45
+)
+
+varTosector <- NULL
+varTolabel <- NULL
+for(sector in names(vars)){
+  tmp <- unlist(vars[[sector]])
+  varTosector <- c(varTosector,setNames(rep(sector,length(tmp)), tmp))
+  varTolabel <- c(varTolabel, setNames(names(vars[[sector]]), vars[[sector]])  )
+}
+
 plotData <- df %>%
-  filter(region == "EU27", period %in% c(2010:2050), variable %in% vars, scenario == mainScen) %>%
-  mutate(variable=factor(variable, levels=vars))
+  filter(region == "EU27", period %in% c(2010:2050), variable %in% unlist(vars), scenario == mainScen) %>%
+  mutate(variable=factor(variable, levels=unlist(vars)),
+         sector = varTosector[variable],
+         label = varTolabel[variable]) %>%
+  mutate(label = factor(label, levels=names(plotColor)),
+         sector = factor(sector, levels=names(pattern)))
 
@@
 
-g[["Supplementary Figure 4a. Final energy demand per sector and carrier"]] <- ggplot(plotData,aes(x=period,y=value)) +
-  geom_area(aes(fill=variable), alpha = 0.8) +
+g[["Supplementary Figure 6a. Final energy demand per sector and carrier"]] <- ggplot(plotData,aes(x=period,y=value)) +
+  #geom_area(data=plotData,aes(fill=variable), alpha = 0.8) +
+  geom_area_pattern(data=plotData,aes(fill=label,pattern=sector, pattern_angle = sector), pattern_key_scale_factor = 1, pattern_density=0.1, pattern_spacing = 0.015, pattern_colour = "white", pattern_fill = "white", pattern_alpha=0.4) + #pattern_key_scale_factor = 0.3, pattern_density=0.3, pattern_spacing = 0.03, pattern_colour = "white", pattern_fill = "white", pattern_alpha=0.4) +
   geom_line(data=totalData, linewidth = 1, color="black") +
@@
   theme_doubleColumn() +
-  #ylab("Final Energy Demand - EJ/yr") + 
-  #ggtitle("(a) per sector and carrier") +
-  scale_fill_manual(values = setNames(plotColor[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(nrow = 6)) +
+  scale_fill_manual(values = plotColor, labels = c(varTolabel,"empty" = "","empty2" = ""), guide = guide_legend(order = 1, override.aes = list(pattern = "none"),byrow=TRUE, ncol = 3), drop = FALSE) +
+  scale_pattern_manual("pattern",values = pattern, breaks=c("Non-Energy Use","Bunkers"), guide = guide_legend(order = 2, override.aes = list(fill = "#555555"),byrow=TRUE,ncol = 2)) +
+  scale_pattern_angle_manual("pattern",values = patternAngle, breaks=c("Non-Energy Use","Bunkers"), guide = guide_legend(order = 2,ncol = 1)) +
   theme(legend.margin=margin(l = -1, unit='cm')) +
-  scale_x_continuous(breaks=c(2010, 2010, 2020,2030,2040,2050)) + 
-  theme(axis.title.x=element_blank()) +
-  theme(axis.title.y=element_blank()) +
-  theme(legend.title = element_blank()) +
-  theme(legend.text = element_text(size = theme.double.text.size*0.8),
+  #scale_x_continuous(breaks=c(2010,2020,2030,2040,2050)) +
+  theme(axis.title.x=element_blank(),
+        axis.title.y=element_blank(),
+        legend.title = element_blank(),
+        legend.text = element_text(size = theme.double.text.size*0.8),
         #legend.key.height = unit(0.7, "cm"),
         #legend.key.width = unit(0.7,"cm"),
-        legend.spacing.x = unit(0.2, 'cm')) + 
-  #  theme(plot.title = element_text(size = 1.2*theme.double.text.size)) +
-  labs(title = paste0("(a) Energy and non-energy use\nper sector and carrier (", unique(plotData$unit), ")")) +
-  theme(plot.title = element_text(hjust=0))
-
-#ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 4a.
-Final energy demand per sector and carrier.svg"), g[["Supplementary Figure 4a.
-Final energy demand per sector and carrier"]] , device="svg", width = 6, height = 8, dpi=100, units = "in")
-#ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 4a.
-Final energy demand per sector and carrier.png"), g[["Supplementary Figure 4a.
-Final energy demand per sector and carrier"]] , device="png", width = 6, height = 8, dpi=300, units = "in")
+        legend.spacing.x = unit(0.2, 'cm'),
+        plot.title = element_text(hjust=0),
+        legend.position="bottom", 
+        legend.box = "vertical") +
+  labs(title = paste0("(a) Energy and non-energy use\nper sector and carrier (", unique(plotData$unit), ")"))
 
@@
 
-```{r supplChart_figure4b, echo=FALSE, include=FALSE}
+```{r supplChart_figure6b, echo=FALSE, include=FALSE}
 
@@
 
-g[["Supplementary Figure 4b. Final energy demand per fossil content"]] <- ggplot(plotData,aes(x=period,y=value)) +
+g[["Supplementary figure 6b. Final energy demand per fossil content"]] <- ggplot(plotData,aes(x=period,y=value)) +
   geom_area(aes(fill=label), alpha = 0.8) +
@@
         #legend.key.width = unit(0.7,"cm"),
-        legend.spacing.x = unit(0.2, 'cm')) + 
+        legend.spacing.x = unit(0.2, 'cm'),
+        plot.title = element_text(hjust=0)) + 
   #  theme(plot.title = element_text(size = 1.2*theme.double.text.size)) +
   labs(title = paste0("(b) Energy and non-energy use\nper fossil content (", unique(plotData$unit), ")")) +
-  theme(plot.title = element_text(hjust=0))
+  theme(plot.title = element_text(hjust=0)) +
+  theme(plot.margin=margin(t=10, b = 48)) #t, r, b, l
 
@@
 
-g[["Supplementary figure 4"]] <- gridExtra::arrangeGrob(
-  g[["Supplementary Figure 4a. Final energy demand per sector and carrier"]], 
-  g[["Supplementary Figure 4b. Final energy demand per fossil content"]], 
+g[["Supplementary figure 6"]] <- gridExtra::arrangeGrob(
+  g[["Supplementary Figure 6a. Final energy demand per sector and carrier"]], 
+  g[["Supplementary figure 6b. Final energy demand per fossil content"]], 
   layout_matrix = rbind(
@@
 
-ggsave(paste0(outChartsFolder,"/png/Supplementary figure 4. Energy and non-energy use.png"), g[["Supplementary figure 4"]], device="png", width = 12, height = 8, dpi=300, units = "in")
-ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 4. Energy and non-energy use.svg"), g[["Supplementary figure 4"]], device="svg", width = 12, height = 8, dpi=100, units = "in")
-
-```
-
-```{r, echo=FALSE, fig.width=12, fig.height=8}
+ggsave(paste0(outChartsFolder,"/png/Supplementary figure 6. EU-27 Emissions.png"), g[["Supplementary figure 6"]], device="png", width = 12, height = 9, dpi=300, units = "in")
+ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 6. EU-27 Emissions.svg"), g[["Supplementary figure 6"]], device="svg", width = 12, height = 9, dpi=100, units = "in")
+
+```
+
+```{r, echo=FALSE, fig.width=12, fig.height=9}
 
 grid.newpage()
-grid.draw(g[["Supplementary figure 4"]])
-
-```
+grid.draw(g[["Supplementary figure 6"]])
+
+```
+Supplementary figure 6. EU-27 Emissions. Energy and non-energy use in the reference scenario (a) per sector and carrier and (b) per fossil content.
 
@@
 
-### Supplementary Figure 5 - Sectoral mitigation - GHG Emissions per sector (Mt CO2/yr)
-
-```{r supplChart_figure5, echo=FALSE, include=FALSE}
+### Supplementary figure 7. EU-27 GHG gases
+
+```{r supplChart_figure7, echo=FALSE, include=FALSE}
 
 vars <- c(
-  "Energy Supply - Electricity"               = "Emi|GHG|Gross|Energy|Supply|Electricity",
-  "Energy Supply - Non-electric"              = "Emi|GHG|Gross|Energy|Supply|Non-electric",
-  "Energy Demand - Transport"                 = "Emi|GHG|Energy|Demand|Transport",
-  "Energy Demand - International Bunkers"     = "Emi|CO2|Energy|Demand|Transport|International Bunkers",
-  "Energy Demand - Buildings"                 = "Emi|GHG|Energy|Demand|Buildings",
-  "Energy Demand - Industry and Agriculture"  = "Emi|GHG|Gross|Energy|Demand|Industry",
-  "Energy Demand - Carbon Dioxide Removal"    = "Emi|GHG|Energy|Demand|CDR",
-  "Industrial Processes"                      = "Emi|GHG|Industrial Processes",
-  "Agriculture"                               = "Emi|GHG|Agriculture",
-  "Land-Use Change"                           = "Emi|GHG|Land-Use Change|LULUCF national accounting", #"Emi|GHG|Land-Use Change",
-  "Waste"                                     = "Emi|GHG|Waste",
-  "BECCS"                                     = "Emi|CO2|CDR|BECCS",
-  "Industry CCS"                              = "Emi|CO2|CDR|Industry CCS|Synthetic Fuels",
-  "DACCS"                                     = "Emi|CO2|CDR|DACCS",
-  "Enhanced Weathering"                       = "Emi|CO2|CDR|EW")
+  "CO2 - Energy"                = "Emi|CO2|Energy",
+  "CO2 - International Bunkers" = "Emi|CO2|Energy|Demand|Transport|International Bunkers",
+  "CO2 - Industrial Processes"  = "Emi|CO2|Industrial Processes",
+  "CO2 - Land-Use Change"       = "Emi|CO2|Land-Use Change|LULUCF national accounting", #"Emi|CO2|Land-Use Change",
+  "CO2 - non-BECCS CDR"         = "Emi|CO2|non-BECCS CDR",
+  "CH4"                         = "Emi|GHG|CH4",
+  "N2O"                         = "Emi|GHG|N2O",
+  "F-Gases"                     = "Emi|GHG|F-Gases"
+  )
 
 plotColor <- c(
-  "Energy Supply - Electricity"               = "#ffb200",
-  "Energy Supply - Non-electric"              = "#0000cc",
-  "Energy Demand - Transport"                 = "#a1dd70",
-  "Energy Demand - International Bunkers"     = "#ffc0cb",
-  "Energy Demand - Buildings"                 = "#5edfff",
-  "Energy Demand - Industry and Agriculture"  = "#5f6769",
-  "Energy Demand - Carbon Dioxide Removal"    = "#999959",
-  "Industrial Processes"                      = "#5c5c5c",
-  "Agriculture"                               = "#357933",
-  "Land-Use Change"                           = "#6ec16b",
-  "Waste"                                     = "#A52A2A",
-  "BECCS"                                     = "#377EB8",
-  "Industry CCS"                              = "#5ed5b0",
-  "DACCS"                                     = "#CC6666",
-  "Enhanced Weathering"                       = "#5b0d8f")
+  "CO2 - Energy"                = "#3D4849",
+  "CO2 - International Bunkers" = "#ffc0cb",
+  "CO2 - Industrial Processes"  = "#a5a5a5",
+  "CO2 - Land-Use Change"       = "#6ec16b",
+  "CO2 - non-BECCS CDR"         = "#5b0d8f",
+  "CH4"                         = "#ffe7a0",
+  "N2O"                         = "#44ba97",
+  "F-Gases"                     = "#ff9977"
+)
 
@@
   mutate(variable=factor(variable, levels=vars))
+
+#plotData %>% group_by(period) %>% summarize(value = sum(value))
 
@@
 
-# check <- left_join(
-#   plotData %>% group_by(period) %>% summarize(value = sum(value)),
-#   totalData %>% group_by(period) %>% summarize(total = sum(value)),
-#   by = join_by(period == period)
-# ) %>%
-#   mutate(diff= round(total-value,2))
-# 
-# left_join(
-#   plotData %>% filter(period == 2010) %>% mutate(value2010 = value),
-#   plotData %>% filter(period == 2015) %>% mutate(value2015 = value),
-#   by = join_by(variable == variable)
-# ) %>%
-#   mutate(diff= round(value2015-value2010,2)) %>%
-#   select(variable,value2010,value2015,diff)
-
-g[["Supplementary Figure 5 - Sectoral mitigation - GHG Emissions per sector"]] <- ggplot(plotData,aes(x=period,y=value)) +
+g[["Supplementary figure 7"]] <- ggplot(plotData,aes(x=period,y=value)) +
   geom_area(aes(fill=variable), alpha = 0.8) +
@@
   #  theme(plot.title = element_text(size = 1.2*theme.double.text.size)) +
+  labs(title = expression(paste("Greenhouse gases emissions (Mt ", CO[2],"e/yr)"))) +
   theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical")
 
-ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 5 - Sectoral mitigation - GHG Emissions per sector.svg"), g[["Supplementary Figure 5 - Sectoral mitigation - GHG Emissions per sector"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
-ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 5 - Sectoral mitigation - GHG Emissions per sector.png"), g[["Supplementary Figure 5 - Sectoral mitigation - GHG Emissions per sector"]] , device="png", width = 12, height = 6, dpi=300, units = "in")
-
-```
-
-```{r, echo=FALSE, fig.width=12, fig.height=6}
-
-g[["Supplementary Figure 5 - Sectoral mitigation - GHG Emissions per sector"]]
-
-```
-
-<!-- explain LULUCF and agriculture assumptions  -->
-
----
-
-### Supplementary Figure 6 - GHG emissions per gases (Mt CO2/yr)
-
-```{r supplChart_figure6, echo=FALSE, include=FALSE}
-
-vars <- c(
-  "CO2 - Energy"                = "Emi|CO2|Energy",
-  "CO2 - International Bunkers" = "Emi|CO2|Energy|Demand|Transport|International Bunkers",
-  "CO2 - Industrial Processes"  = "Emi|CO2|Industrial Processes",
-  "CO2 - Land-Use Change"       = "Emi|CO2|Land-Use Change|LULUCF national accounting", #"Emi|CO2|Land-Use Change",
-  "CO2 - non-BECCS CDR"         = "Emi|CO2|non-BECCS CDR",
-  "CH4"                         = "Emi|GHG|CH4",
-  "N2O"                         = "Emi|GHG|N2O",
-  "F-Gases"                     = "Emi|GHG|F-Gases"
-  )
-
-plotColor <- c(
-  "CO2 - Energy"                = "#3D4849",
-  "CO2 - International Bunkers" = "#ffc0cb",
-  "CO2 - Industrial Processes"  = "#5c5c5c",
-  "CO2 - Land-Use Change"       = "#6ec16b",
-  "CO2 - non-BECCS CDR"         = "#5b0d8f",
-  "CH4"                         = "#ffe7a0",
-  "N2O"                         = "#44ba97",
-  "F-Gases"                     = "#ff9977"
-)
-
-plotData <- df %>%
-  filter(region == "EU27", period %in% c(2010:2050), variable %in% vars, scenario == mainScen) %>%
-  mutate(variable=factor(variable, levels=vars))
-
-#plotData %>% group_by(period) %>% summarize(value = sum(value))
-
-#total
-totalData <- df %>%
-  calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%
-  filter(region == "EU27", period %in% c(2010:2050), variable == "Emissions with LULUCF and with international transport", scenario == mainScen)
-
-g[["Supplementary Figure 6 - GHG emissions per gases"]] <- ggplot(plotData,aes(x=period,y=value)) +
-  geom_area(aes(fill=variable), alpha = 0.8) +
-  geom_line(data=totalData, linewidth = 1, color="black") +
-  geom_vline(xintercept=2020, color = "black", linetype="dashed", linewidth=1, alpha = 0.5) +
-  geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
-  theme_doubleColumn() +
-  #ylab("Final Energy Demand - EJ/yr") + 
-  #ggtitle("(a) per sector and carrier") +
-  scale_fill_manual(values = setNames(plotColor[names(vars)],vars), labels = setNames(names(vars), vars)) +
-  #theme(legend.margin=margin(l = -1, unit='cm')) +
-  scale_x_continuous(breaks=c(2010, 2010, 2020,2030,2040,2050)) + 
-  theme(axis.title.x=element_blank()) +
-  theme(axis.title.y=element_blank()) +
-  theme(legend.title = element_blank()) +
-  theme(#legend.text = element_text(size = theme.double.text.size*0.7),
-        #legend.key.height = unit(0.7, "cm"),
-        #legend.key.width = unit(0.7,"cm"),
-        legend.spacing.x = unit(0.2, 'cm')) + 
-  #  theme(plot.title = element_text(size = 1.2*theme.double.text.size)) +
-  theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical")
-
-ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 6 - GHG emissions per gases.svg"), g[["Supplementary Figure 6 - GHG emissions per gases"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
-ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 6 - GHG emissions per gases.png"), g[["Supplementary Figure 6 - GHG emissions per gases"]] , device="png", width = 12, height = 6, dpi=300, units = "in")
+ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 7. EU-27 GHG gases.svg"), g[["Supplementary figure 7"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
+ggsave(paste0(outChartsFolder,"/png/Supplementary figure 7. EU-27 GHG gases.png"), g[["Supplementary figure 7"]] , device="png", width = 12, height = 6, dpi=300, units = "in")
 
@@
 
-g[["Supplementary Figure 6 - GHG emissions per gases"]]
-
-```
+g[["Supplementary figure 7"]]
+
+```
+
+Supplementary figure 7. EU-27 GHG gases. Emissions by gas in the reference scenario (CO2eq).
 
@@
 
-### Supplementary Figure 7 - Carbon-dioxide removal
+### Supplementary figure 8. EU-27 CDR
 
@@
 
-```{r supplChart_figure7a, echo=FALSE, include=FALSE}
+```{r supplChart_figure8a, echo=FALSE, include=FALSE}
 
@@
     ))
+
+#df_beforeFilter %>%
+#    filter(region == "EU27", period == 2040, scenario == mainScen, variable %in% vars) %>% pull(value)
 
@@
 
-```{r supplChart_figure7b, echo=FALSE, include=FALSE}
+```{r supplChart_figure8b, echo=FALSE, include=FALSE}
 
@@
 
-g[["Supplementary figure 7"]] <- gridExtra::arrangeGrob(
+g[["Supplementary figure 8"]] <- gridExtra::arrangeGrob(
   g[["BECCS"]], 
@@
 
-ggsave(paste0(outChartsFolder,"/png/Supplementary figure 7. Carbon-dioxide removal.png"), g[["Supplementary figure 7"]], device="png", width = 12, height = 6, dpi=300, units = "in")
-ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 7. Carbon-dioxide removal.svg"), g[["Supplementary figure 7"]], device="svg", width = 12, height = 6, dpi=100, units = "in")
+ggsave(paste0(outChartsFolder,"/png/Supplementary figure 8. EU-27 CDR.png"), g[["Supplementary figure 8"]], device="png", width = 12, height = 6, dpi=300, units = "in")
+ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 8. EU-27 CDR.svg"), g[["Supplementary figure 8"]], device="svg", width = 12, height = 6, dpi=100, units = "in")
 
@@
 grid.newpage()
-grid.draw(g[["Supplementary figure 7"]])
-
-```
+grid.draw(g[["Supplementary figure 8"]])
+
+```
+
+Supplementary figure 8. EU-27 CDR. CDR deployment: (a) BECCS and (b) DACCS.

### 2025-04-24 R/calcResults.R

@@ -2,65 +2,124 @@
 
 # Emission Reductions
 
-reductions2040 <- rbind(
+
+emiReduction <- rbind(
   df %>% 
-    filter(variable == "Emi|GHG|with LULUCF and with international transport", region == "EU27", period == 2040, tgt2050 != "Npi") %>% 
-    mutate(value = 1-(value / tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)))
+    filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>%
+    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>% 
+    mutate(reduction = 1-round(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference) ,2),
+           variable = "Emissions with LULUCF and with intra-EU aviation") %>% 
+    filter(tgt2050 != "Npi") %>% 
+    select(variable, scenario, reduction)
   ,
   df %>% 
-    filter(variable == "Emi|GHG|without LULUCF and with international transport", region == "EU27", period == 2040, tgt2050 != "Npi") %>% 
-    mutate(value = 1-(value / tgt %>% filter(target == "Emissions without LULUCF and with international transport") %>% pull(reference)))
-  ,
-  df %>% 
-    filter(variable == "Emi|GHG|with LULUCF and with intra-EU aviation", region == "EU27", period == 2040, tgt2050 != "Npi") %>% 
-    mutate(value = 1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)))
-  ,
-  df %>% 
-    filter(variable == "Emi|GHG|without LULUCF and with intra-EU aviation", region == "EU27", period == 2040, tgt2050 != "Npi") %>% 
-    mutate(value = 1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)))
-  ,
-  df %>% 
-    filter(variable == "Emi|GHG|Gross|without LULUCF and with international transport", region == "EU27", period == 2040, tgt2050 != "Npi") %>% 
-    mutate(value = 1-(value / tgt %>% filter(target == "Gross Emissions without LULUCF and with international transport") %>% pull(reference)))
[…]

### 2025-04-24 R/loadData.R

@@ -171,12 +171,19 @@ loadMifFiles <- function(path,filterVars,forceUpdate){
       tmpdf <- suppressWarnings(read.quitte(file))
       tmpdf <- tmpdf %>%
         filter(!(variable %in% unique(reportDuplicates(remind2::deletePlus(tmpdf)) %>% pull(variable)))) %>% #remove duplicates
-        deletePlus() %>% # remove plus
+        deletePlus()
+      tmpdf_filter <- tmpdf %>%
         filter(variable %in% filterVars,
-               region %in% c("EU27","DEU","FRA"),
+               region %in% c("EU27"),
+               period <= 2060)
+      tmpdf_add <- tmpdf %>%
+        filter(variable %in% c("Emi|GHG|LULUCF national accounting", "Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region", "Emi|CO2|Energy|Demand|Transport|International Bunkers", "Emi|GHG|Land-Use Change|LULUCF national accounting", "Carbon Management|Storage|Biomass|Pe2Se", "Carbon Management|Storage|Industry Energy|Biomass", "Carbon Management|Storage|Industry Energy|Synfuel",
+                               "SE|Electricity|Net Imports", "SE|Electricity|Coal|w/ CC", "SE|Electricity|Coal|w/o CC", "SE|Electricity|Oil", "SE|Electricity|Gas|w/ CC", "SE|Electricity|Gas|w/o CC", "SE|Electricity|Hydrogen", "SE|Electricity|Nuclear", "SE|Electricity|Geothermal", "SE|Electricity|Hydro", "SE|Electricity|Biomass|w/ CC", "SE|Electricity|Biomass|w/o CC", "SE|Electricity|Solar|CSP", "SE|Electricity|Solar|PV", "SE|Electricity|Wind|Onshore", "SE|Electricity|Wind|Offshore",
[…]

### 2025-04-24 createReports.R

@@ -9,7 +9,7 @@ outFolder <- paste0("./output/",gsub("./data/","",dataFolder))
 dir.create(outFolder, recursive = TRUE, showWarnings = FALSE)
 
 # Create paper charts in EJ
-rmarkdown::render("./report_paperCharts.Rmd", output_file = paste0(outFolder, "/report_paperCharts-EJ.html"), params = list(forceUpdateData = FALSE, loadHist = TRUE, energyInMtoe = FALSE, chartsFolder = "report_paperCharts_EJ"))
+#rmarkdown::render("./report_paperCharts.Rmd", output_file = paste0(outFolder, "/report_paperCharts-EJ.html"), params = list(forceUpdateData = FALSE, loadHist = TRUE, energyInMtoe = FALSE, chartsFolder = "report_paperCharts_EJ"))
 
 # Create paper charts in Mtoe and MtH2
 rmarkdown::render("./report_paperCharts.Rmd", output_file = paste0(outFolder, "/report_paperCharts-Mtoe_and_MtH2.html"), params = list(forceUpdateData = FALSE, loadHist = TRUE, energyInMtoe = TRUE, chartsFolder = "report_paperCharts_Mtoe"))

### 2025-04-24 output/2024_12_11/report_sensitivityExplorer/charts/beccs.js

@@ -9032,32 +9032,32 @@
   },
   "source": "A",
   "attrs": {
-    "4b542d80aa6": {
+    "607430442555": {
       "yintercept": {},
       "type": "scatter"
     },
-    "4b5418502757": {
+    "6074139a6bf4": {
       "xintercept": {}
     },
-    "4b54101958d7": {
+    "6074169d7bf8": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "4b547cb72640": {
+    "60747203663": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     }
   },
-  "cur_data": "4b542d80aa6",
+  "cur_data": "607430442555",
   "visdat": {
-    "4b542d80aa6": ["function (y) ", "x"],
-    "4b5418502757": ["function (y) ", "x"],
-    "4b54101958d7": ["function (y) ", "x"],
-    "4b547cb72640": ["function (y) ", "x"]
+    "607430442555": ["function (y) ", "x"],
+    "6074139a6bf4": ["function (y) ", "x"],
+    "6074169d7bf8": ["function (y) ", "x"],
+    "60747203663": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-24 output/2024_12_11/report_sensitivityExplorer/charts/carbonPrice.js

@@ -9050,37 +9050,37 @@
   },
   "source": "A",
   "attrs": {
-    "4b54df66d6c": {
+    "60745ae2a49": {
       "yintercept": {},
       "type": "scatter"
     },
-    "4b5428bb67a": {
+    "6074af71387": {
       "xintercept": {}
     },
-    "4b545bd1ffe": {
+    "60741ca41e7b": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "4b5413547077": {
+    "607438ac457c": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     },
-    "4b542d196cc2": {
+    "607452254ee2": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "4b54df66d6c",
+  "cur_data": "60745ae2a49",
   "visdat": {
-    "4b54df66d6c": ["function (y) ", "x"],
-    "4b5428bb67a": ["function (y) ", "x"],
-    "4b545bd1ffe": ["function (y) ", "x"],
-    "4b5413547077": ["function (y) ", "x"],
-    "4b542d196cc2": ["function (y) ", "x"]
+    "60745ae2a49": ["function (y) ", "x"],
+    "6074af71387": ["function (y) ", "x"],
+    "60741ca41e7b": ["function (y) ", "x"],
+    "607438ac457c": ["function (y) ", "x"],
+    "607452254ee2": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-24 output/2024_12_11/report_sensitivityExplorer/charts/electricityShare.js

@@ -35978,41 +35978,41 @@
   },
   "source": "A",
   "attrs": {
-    "4b5433bdb94": {
+    "6074675054cb": {
       "yintercept": {},
       "type": "scatter"
     },
-    "4b545df7268a": {
+    "607477af3b8a": {
       "xintercept": {}
     },
-    "4b548f531e": {
+    "607419774435": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "4b547f2e73fa": {
+    "607413fd7022": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     },
-    "4b5444bc6325": {
+    "6074d916f45": {
       "x": {},
       "y": {}
     },
-    "4b546cf55cf7": {
+    "607445f25432": {
       "y": {}
     }
   },
-  "cur_data": "4b5433bdb94",
+  "cur_data": "6074675054cb",
   "visdat": {
-    "4b5433bdb94": ["function (y) ", "x"],
-    "4b545df7268a": ["function (y) ", "x"],
-    "4b548f531e": ["function (y) ", "x"],
-    "4b547f2e73fa": ["function (y) ", "x"],
-    "4b5444bc6325": ["function (y) ", "x"],
-    "4b546cf55cf7": ["function (y) ", "x"]
+    "6074675054cb": ["function (y) ", "x"],
+    "607477af3b8a": ["function (y) ", "x"],
+    "607419774435": ["function (y) ", "x"],
+    "607413fd7022": ["function (y) ", "x"],
+    "6074d916f45": ["function (y) ", "x"],
+    "607445f25432": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-24 output/2024_12_11/report_sensitivityExplorer/charts/emissions.js

@@ -9050,39 +9050,39 @@
   },
   "source": "A",
   "attrs": {
-    "4b5450bf73e5": {
+    "607459ee2c21": {
       "yintercept": {},
       "type": "scatter"
     },
-    "4b544b6418a0": {
+    "60746f8c6ccd": {
       "xintercept": {}
     },
-    "4b54608362d3": {
+    "60743ef644a9": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {},
       "text": {}
     },
-    "4b545b0d61e8": {
+    "607425fa6e0f": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {},
       "text": {}
     },
-    "4b547a73718d": {
+    "607430281106": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "4b5450bf73e5",
+  "cur_data": "607459ee2c21",
   "visdat": {
-    "4b5450bf73e5": ["function (y) ", "x"],
-    "4b544b6418a0": ["function (y) ", "x"],
-    "4b54608362d3": ["function (y) ", "x"],
-    "4b545b0d61e8": ["function (y) ", "x"],
-    "4b547a73718d": ["function (y) ", "x"]
+    "607459ee2c21": ["function (y) ", "x"],
+    "60746f8c6ccd": ["function (y) ", "x"],
+    "60743ef644a9": ["function (y) ", "x"],
+    "607425fa6e0f": ["function (y) ", "x"],
+    "607430281106": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-24 output/2024_12_11/report_sensitivityExplorer/charts/finalEnergy.js

@@ -9050,37 +9050,37 @@
   },
   "source": "A",
   "attrs": {
-    "4b54797a4027": {
+    "607496e71fd": {
       "yintercept": {},
       "type": "scatter"
     },
-    "4b547a001807": {
+    "60744777c2b": {
       "xintercept": {}
     },
-    "4b545ead3a7": {
+    "6074366366fc": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "4b5468f8119d": {
+    "607427bb67bb": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     },
-    "4b546c2d1dd4": {
+    "607414c21391": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "4b54797a4027",
+  "cur_data": "607496e71fd",
   "visdat": {
-    "4b54797a4027": ["function (y) ", "x"],
-    "4b547a001807": ["function (y) ", "x"],
-    "4b545ead3a7": ["function (y) ", "x"],
-    "4b5468f8119d": ["function (y) ", "x"],
-    "4b546c2d1dd4": ["function (y) ", "x"]
+    "607496e71fd": ["function (y) ", "x"],
+    "60744777c2b": ["function (y) ", "x"],
+    "6074366366fc": ["function (y) ", "x"],
+    "607427bb67bb": ["function (y) ", "x"],
+    "607414c21391": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-24 output/2024_12_11/report_sensitivityExplorer/charts/hydrogen.js

@@ -44826,32 +44826,32 @@
   },
   "source": "A",
   "attrs": {
-    "4b54403779a2": {
+    "6074450d48ee": {
       "yintercept": {},
       "type": "scatter"
     },
-    "4b546aa92750": {
+    "607428005cfc": {
       "xintercept": {}
     },
-    "4b542cfd7b1c": {
+    "60747cde276f": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "4b54291f559e": {
+    "6074220b61cb": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     }
   },
-  "cur_data": "4b54403779a2",
+  "cur_data": "6074450d48ee",
   "visdat": {
-    "4b54403779a2": ["function (y) ", "x"],
-    "4b546aa92750": ["function (y) ", "x"],
-    "4b542cfd7b1c": ["function (y) ", "x"],
-    "4b54291f559e": ["function (y) ", "x"]
+    "6074450d48ee": ["function (y) ", "x"],
+    "607428005cfc": ["function (y) ", "x"],
+    "60747cde276f": ["function (y) ", "x"],
+    "6074220b61cb": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-24 output/2024_12_11/report_sensitivityExplorer/charts/primaryEnergy.js

@@ -35947,37 +35947,37 @@
   },
   "source": "A",
   "attrs": {
-    "4b54647f50d0": {
+    "6074136159cf": {
       "yintercept": {},
       "type": "scatter"
     },
-    "4b54e03781a": {
+    "60747726613c": {
       "xintercept": {}
     },
-    "4b543cd8640c": {
+    "60741f482969": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "4b5419b67b2c": {
+    "607430e61da1": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     },
-    "4b54283a5679": {
+    "6074f9c19c": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "4b54647f50d0",
+  "cur_data": "6074136159cf",
   "visdat": {
-    "4b54647f50d0": ["function (y) ", "x"],
-    "4b54e03781a": ["function (y) ", "x"],
-    "4b543cd8640c": ["function (y) ", "x"],
-    "4b5419b67b2c": ["function (y) ", "x"],
-    "4b54283a5679": ["function (y) ", "x"]
+    "6074136159cf": ["function (y) ", "x"],
+    "60747726613c": ["function (y) ", "x"],
+    "60741f482969": ["function (y) ", "x"],
+    "607430e61da1": ["function (y) ", "x"],
+    "6074f9c19c": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-24 report_additionalCharts.Rmd
update limVRE setup and general cleanup

@@
 
-# Emission reduction {.tabset}
-
-## Gross
-
-<!-- (c) Breakdown of residual CO2 emissions from energy and industrial processes (% in relation to 2020) -->
-
-```{r, echo=FALSE}
-
-vars <- list(
-  "Industrial\nProcesses" = "Emi|GHG|Industrial Processes",
-  "Industry" = "Emi|GHG|Gross|Energy|Demand|Industry",
-  "Buildings" ="Emi|GHG|Energy|Demand|Buildings",
-  "Transportation" ="Emi|GHG|Energy|Demand|Transport",
-  "Bunkers" = "Emi|CO2|Energy|Demand|Transport|International Bunkers",
-#  "CDR" = "Emi|GHG|Gross|Energy|Demand|CDR",
-#  "AFOFI" = "Emissions|CO2|Energy|Demand|AFOFI",
-#  "Other Sector" ="Emissions|CO2|Energy|Demand|Other Sector",
-  "Heat"="Emi|CO2|Gross|Energy|Supply|Heat",
-  "Other Energy\nConversion" = "Emi|CO2|Gross|Other Energy Conversion",
-    #"Hydrogen" ="Emi|CO2|Gross|Energy|Supply|Hydrogen",
-    #"Liquids"="Emi|CO2|Gross|Energy|Supply|Liquids",
-    #"Gases"="Emi|CO2|Gross|Energy|Supply|Gases",
-    #"Solids"="Emi|CO2|Gross|Energy|Supply|Solids",
-#  "Other"="Emissions|CO2|Energy|Supply|Other",
-  "Electricity"="Emi|GHG|Gross|Energy|Supply|Electricity"
-)
-# "Emi|GHG|Agriculture",
-#   "Emi|GHG|Land-Use Change",
-#   "Emi|GHG|Waste",
-#   "Emi|CO2|CDR|BECCS",
-#   "Emi|CO2|CDR|Industry CCS|Synthetic Fuels",
-#   "Emi|CO2|CDR|DACCS",
-#   "Emi|CO2|CDR|EW"
-
-plotColor <- c(
-  "Electricity"= "#ffb200",
-  "Heat"= "#cc0000",
-  "Other Energy\nConversion" = "#0000cc",
-  #"Gases"= "#999959",
-  #"Liquids"= "#0000cc",
-  #"Solids"= "#0c0c0c",
-  #"Other" = "#79a6d2",
-  #"Hydrogen" = "#5ed5b0",
-  "Transportation" = "#a1dd70",
-  "Bunkers" = "#ffc0cb",
-  "Buildings" = "#5edfff",
-  "Other Sector" = "#999959",
-  "AFOFI" = "#005900",
-  "Industry" = "#5f6769",
-  "Industrial\nProcesses" = "#5c5c5c",
-  "Other" = "#5b0d8f",
-  "Waste" = "#A52A2A",
-  "AFOLU" = "#4DAF4A",
-  "Agriculture" = "#357933",
-  "LULUCF" = "#6ec16b"
-)
-
-labels <- setNames(names(vars),vars[names(vars)])
-
-fulldata <- df %>%
-  filter(region == "EU27",
-         period %in% c(2020,2030,2040),
-         tgt2030 %in% tgt2030Scen,
-         variable %in% unlist(vars)) %>%
-  mutate(labels = factor(labels[as.character(variable)],levels = names(vars)),
-         variable = factor(variable, levels = vars)) %>%
-  group_by(period,variable) %>%
-  mutate(min = min(value),
-         max = max(value))
-
-plotData <- fulldata %>%
-  filter(scenario == mainScen) %>%
-  mutate(complement = FALSE) %>%
-  group_by(variable) %>%
-  mutate(pct = paste0(round(value / value[period==2020],2)*100, "%")) %>%
-  bind_rows(
-    fulldata %>%
-      filter(scenario == mainScen) %>%
-      mutate(complement = TRUE) %>%
-      group_by(variable) %>%
-      mutate(value = value[period==2020] - value) %>%
-      mutate(labels=NA)
-  ) %>%
-  mutate(ext_Var = ifelse(complement, paste0(as.character(variable),"_"), as.character(variable))) %>%
-  arrange(period,ext_Var) %>%
-  group_by(period) %>%
-  arrange(variable) %>%
-  mutate(ymid = as.numeric(sub("\\D+", "", period)),
-         ymax = ymid + 4, ymin = ymid - 4,
-         xmin = c(0, head(cumsum(value), -1)),
-         xmax = cumsum(value),
-         xmid = (xmax + xmin) / 2,
-         ) %>%
-  ungroup() %>%
-  filter(complement == FALSE)
-
-g[["2040 Emissions - Energy and Industrial Processes - Gross"]] <- plotData %>% 
-  ggplot(aes(xmid, ymid, fill = ext_Var)) +
-  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax,
-                alpha = factor(period), color = variable)) +
-  geom_errorbar(data=plotData %>% filter(period == 2040), aes(xmin=xmax-value+min, xmax=xmax-value+max), width=4, colour="black", alpha=0.9, linewidth=0.8) +
-  geom_text(data=plotData %>% filter(period == 2020), aes(y = 2015, label = labels, group = labels, hjust=1, angle = 90), vjust=0.5, hjust=1.1, na.rm=TRUE, size = geomText.size, angle = 90, lineheight = 0.8) +
-  geom_text(data=plotData %>% filter(period == 2040), aes(x=xmid , y = 2045, label = pct), vjust=0.5, hjust=-0.1, na.rm=TRUE, size = geomText.size, angle = 90) +
-  scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) + 
-  scale_alpha_manual(values = c(0.2, 0.3, 1)) +
-  scale_color_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) +
-  theme_doubleColumn() +
-  theme(legend.position = "none") +
-  scale_y_continuous(breaks=c(2020,2030,2040), labels=c("current",2030,2040), minor_breaks = NULL, limits=c(2008,2047)) +
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank(),
-        axis.title.y=element_blank()) +
-  scale_x_continuous(breaks = NULL) +
-  coord_cartesian(clip="off") +
-  theme(plot.margin = margin(t = 30, r = 0, b = 100, l = 0, unit = "pt")) +
-  labs(title = "(c) Sectoral breakdown of residual gross CO2 emissions from energy and industrial processes (% of average 2018-2022)") + 
-  theme(plot.title = element_text(margin=margin(t=0,r=0,b=35,l=-200), hjust=1))
-
-# ggsave(paste0(outChartsFolder,"/svg/Figure 1.
-Emission results panel - (c) Energy and Industrial Processes.svg"), g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] , device="svg", width = 12, height = 3.2, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Figure 1.
-Emission results panel - (c) Energy and Industrial Processes.png"), g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] , device="png", width = 12, height = 3.2, dpi=300, units = "in")
-
-```
-
 # Targets debug {.tabset}
@@
 ## Reduction Matrix
-reductionMatrix <- df_beforeFilter %>% 
+reductionMatrix <- df %>% 
   filter(region == "EU27", 
@@
 
-redMatrix2 <- df_beforeFilter %>%
+redMatrix2 <- df %>%
     filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>%
@@
 plotData <- left_join(
-  df_beforeFilter %>%
+  df %>%
     filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
@@
            max = max(value)),
-  df_beforeFilter %>%
+  df %>%
     filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Price|Carbon") %>%
@@
 nonAchieved2030 <- left_join(
-  df_beforeFilter %>%
+  df %>%
     filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
@@
 
-plotData <- df_beforeFilter %>%
+plotData <- df %>%
   filter(region == "EU27", period == 2050, tgt2030 %in% tgt2030Scen) %>%
@@
 
-nonAchieved2050 <- df_beforeFilter %>%
+nonAchieved2050 <- df %>%
   filter(region == "EU27", period == 2050, tgt2030 %in% tgt2030Scen) %>%
@@
 
-fullPlotData <- df_beforeFilter %>%
+fullPlotData <- df %>%
   filter(region == "EU27", period %in% c(2010:2050), variable %in% unlist(vars)) %>%
@@
 
-<!-- <!-- # GHG Emissions --> -->
-
-<!-- ```{r chart_, echo=FALSE, include=FALSE} -->
-
-<!-- library(plotly) -->
-<!-- plotData <- df %>%  -->
-<!--   filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen) %>%  -->
-<!--   calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>% -->
-<!--   mutate(reduction = round((1 - (value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference))) ,2)) -->
-
-<!-- g[["GHG emi_plotly"]] <- ggplotly(ggplot(plotData, aes(x=period,y=reduction, color=scenario)) + -->
-<!--            geom_line() + -->
-<!--            guides(color="none") + -->
-<!--            theme_doubleColumn() + -->
-<!--            scale_y_continuous(labels = scales::percent, trans="reverse") + -->
-<!--            theme(axis.title.y=element_blank()) -->
-<!--   ) -->
-
-<!-- g[["GHG emi_plotly_limit"]] <- ggplotly(ggplot(plotData %>% filter(!grepl("limVRE|bio20|Nzero_55", scenario)), aes(x=period,y=reduction, color=scenario)) + -->
-<!--            geom_line() + -->
-<!--            guides(color="none") + -->
-<!--            theme_doubleColumn() + -->
-<!--            scale_y_continuous(labels = scales::percent, trans="reverse") + -->
-<!--            theme(axis.title.y=element_blank()) -->
-<!--   ) -->
-<!-- #min(plotData %>% filter(!grepl("limVRE|bio20|Nzero_55", scenario), period == 2040) %>% pull(reduction)) -->
-<!-- ``` -->
-
-<!-- <!-- ```{r, echo=FALSE, fig.width=6, fig.height=10} --> -->
-
-<!-- <!-- g[["GHG emi_plotly"]] --> -->
-
-<!-- <!-- ``` --> -->
-
-<!-- # Electricity Capacity -->
-
-<!-- <!-- Electricity Capacity (%) --> -->
-
-<!-- ```{r, echo=FALSE} -->
-
-<!-- vars <- c( -->
-<!-- #  "Net Imports" = "Cap|Electricity|Imports", -->
-<!--   "Coal w/ CC" = "Cap|Electricity|Coal|w/ CC", -->
-<!--   "Coal w/o CC" = "Cap|Electricity|Coal|w/o CC", -->
-<!--   "Oil" = "Cap|Electricity|Oil", -->
-<!--   "Gas w/ CC" = "Cap|Electricity|Gas|w/ CC", -->
-<!--   "Gas w/o CC" = "Cap|Electricity|Gas|w/o CC", -->
-<!--   "Hydrogen" = "Cap|Electricity|Hydrogen", -->
-<!--   "Nuclear" = "Cap|Electricity|Nuclear", -->
-<!--   "Geothermal" = "Cap|Electricity|Geothermal", -->
-<!--   "Hydro" = "Cap|Electricity|Hydro", -->
-<!--   "Biomass w/ CC" = "Cap|Electricity|Biomass|w/ CC", -->
-<!--   "Biomass w/o CC" = "Cap|Electricity|Biomass|w/o CC", -->
-<!--   "Solar CSP" = "Cap|Electricity|Solar|CSP", -->
-<!--   "Solar PV" = "Cap|Electricity|Solar|PV", -->
-<!--   "Wind Onshore" = "Cap|Electricity|Wind|Onshore", -->
-<!--   "Wind Offshore" = "Cap|Electricity|Wind|Offshore", -->
-<!--   "Storage Battery" = "Cap|Electricity|Storage|Battery" -->
-<!--   ) -->
-
-<!-- inv_vars <- setNames(names(vars),vars) -->
-
-<!-- color <- c( -->
-<!-- #  "Net Imports"   = "#472b62", -->
-<!--   "Coal w/ CC"    = "#b2b2b2", -->
-<!--   "Coal w/o CC"   = "#0c0c0c", -->
-<!--   "Oil"           = "#b30000", -->
-<!--   "Gas w/ CC"     = "#b79e38", -->
-<!--   "Gas w/o CC"    = "#999959", -->
-<!--   "Hydrogen"      = "#5ed5b0", -->
-<!--   "Nuclear"       = "#ff33ff", -->
-<!--   "Geothermal"    = "#e51900", -->
-<!--   "Hydro"         = "#191999", -->
-<!--   "Biomass w/ CC" = "#33ff00", -->
-<!--   "Biomass w/o CC"= "#005900", -->
-<!--   "Solar CSP"     = "#ffcc00", -->
-<!--   "Solar PV"      = "#ffe600", -->
-<!--   "Wind Onshore"  = "#193F7F", -->
-<!--   "Wind Offshore" = "#337fff", -->
-<!--   "Storage Battery" = "#472b62") -->
-
-<!-- plotData <- df %>%  -->
-<!--   filter(region == "EU27", period >= 2020, period <= 2060, scenario  == mainScen, variable %in% unlist(vars)) %>%  -->
-<!--   mutate(variable = factor(variable, levels=vars)) %>%  -->
-<!--   arrange(factor(variable, levels = rev(vars))) %>% -->
-<!--   group_by(model,scenario,region,period) %>% -->
-<!--   mutate(cumValue = cumsum(value), -->
-<!--          n = sum(value), -->
-<!--          percentage = value / n, -->
-<!--          cumPercentage = cumValue / n)  -->
-
-<!-- plotData2040 <- plotData[plotData$period == 2040,] -->
-<!-- #plotData$value <- plotData$value / plotData[plotData$period == "2020",]$value -->
-<!-- #plotData$period <- as.character(plotData$period) -->
-<!-- #plotData$period <- factor(plotData$period , levels = rev(c("2020","2030","2040","2050"))) -->
-
-<!-- plotData2040$xPos <- 2042.5 -->
-<!-- #plotData2040[plotData2040$variable %in% c("SE|Electricity|Hydro"),]$xPos <- 2028.5 -->
-<!-- #plotData2040[plotData2040$variable %in% c("SE|Electricity|Biomass|w/o CC"),]$xPos <- 2020 -->
-<!-- plotData2040[plotData2040$variable %in% c("SE|Electricity|Nuclear","SE|Electricity|Biomass|w/o CC"),]$xPos <- 2035 -->
-
-<!-- plotDataRenewables <- plotData %>% -->
-<!--   filter(variable %in% c("Cap|Electricity|Hydrogen","Cap|Electricity|Geothermal","Cap|Electricity|Hydro","Cap|Electricity|Biomass|w/ CC","Cap|Electricity|Biomass|w/o CC","Cap|Electricity|Solar|CSP","Cap|Electricity|Solar|PV","Cap|Electricity|Wind|Onshore","Cap|Electricity|Wind|Offshore","Cap|Electricity|Nuclear","Cap|Electricity|Storage|Battery")) %>% -->
-<!--   group_by(model,scenario,region,period) %>% -->
-<!--   summarize(percentage = sum(percentage),.groups = "keep") -->
-
-<!-- g[["Electricity Capacity"]] <-  -->
-<!--   ggplot(plotData,aes(x=period,y=percentage)) + -->
-<!--   geom_area(aes(fill=variable),alpha=0.4) + -->
-<!--   geom_line(data=plotDataRenewables, linetype = "dashed", linewidth = 1.5, color="#666666") + -->
-<!--   geom_bar(data=plotData2040,aes(fill=variable),stat='identity', show.legend = FALSE, alpha = 0.7, color="white", width = 3, linewidth = 1.5) + -->
-<!--   #ggrepel::geom_text_repel(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(round(percentage,2)*100,"%"), y=cumPercentage-percentage/2, x = 2043.5), vjust=0.5, hjust=0.5, na.rm=TRUE, color = "black", size = 12) + -->
-<!--   #geom_text(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(inv_vars[variable], " (",round(percentage,2)*100,"%)"), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size = 12) + -->
-<!--   geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geom.text.double.size) + -->
-<!--   theme_doubleColumn()  + -->
-<!--   scale_y_continuous(minor_breaks = seq(0.2, 0.8, 0.2), breaks=c(0,1),labels = scales::percent) + -->
-<!--   scale_x_continuous(breaks=c(2020,2040,2060)) + -->
-<!--   scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) + -->
-<!--   theme(axis.title.y=element_blank()) + -->
-<!--   guides(fill=guide_legend(nrow=8,override.aes = list(alpha=1), byrow = TRUE)) + -->
-<!--   #annotate(geom = "text", x = 2022, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage + 0.06, label = "renewables", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) + -->
-<!--   #annotate(geom = "text", x = 2023, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage - 0.06, label = "and nuclear", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) + -->
-<!--   #annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geom.text.double.size) + -->
-<!--   annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, label = "renewables,\nnuclear and hydrogen", color = "#666666",angle = 90, hjust=0.5, vjust=-0.5, size=geom.text.double.size, lineheight = 0.8) + -->
-<!--   annotate(geom = "text", x = 2020, y = (1-plotDataRenewables[plotDataRenewables$period == 2020,]$percentage)/2+plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "fossil", color = "#666666",angle = 90, hjust=0.5, vjust=-2, size=geom.text.double.size) + -->
-<!--   annotation_custom(grob = linesGrob(gp=gpar(col="#666666",lwd = 3,lty="dashed")), xmin = 2016, xmax = 2019.8, ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage) + -->
-<!--   theme(axis.text.y=element_blank()) + -->
-<!--   theme(legend.key.height = unit(0.8, "cm"), -->
-<!--     legend.key.width = unit(0.8,"cm")) + -->
-<!--   theme(legend.spacing.y = unit(0.1, 'cm')) + -->
-<!--   theme() + -->
-<!--   annotate(geom = "text", label = "100%", x = 2020, y = 1, hjust=1.2, color = "#666666", size=geom.text.double.size) + -->
-<!--   annotate(geom = "text", label = "0%", x = 2020, y = 0, hjust=1.2, color = "#666666", size=geom.text.double.size) + -->
-<!--   coord_cartesian(clip = 'off') + -->
-<!--   theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 20, unit = "pt") -->
-<!--         #,legend.margin=margin(l = -2, unit='cm') -->
-<!--         ) #+ -->
-<!--   #annotation_custom( -->
-<!--   #  grob = textGrob(label = "renewables\nand nuclear",hjust=0.5, vjust=-0.5, rot = 90, gp=gpar(col="#666666", fontsize=geom.text.double.size)), -->
-<!--   #  ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, -->
-<!--   #  xmin = 2020, xmax = 2020) -->
-
-<!-- ggsave(paste0(outChartsFolder,"/svg/Electricity Capacity.svg"), g[["Electricity Capacity"]] , device="svg", width = 6, height = 10, dpi=100, units = "in") -->
-<!-- ggsave(paste0(outChartsFolder,"/png/Electricity Capacity.png"), g[["Electricity Capacity"]] , device="png", width = 6, height = 10, dpi=300, units = "in") -->
-
-<!-- ``` -->
-
-<!-- ```{r, echo=FALSE, fig.width=6, fig.height=10} -->
-
-<!-- g[["Electricity Capacity"]] -->
-
-<!-- ``` -->
-
-<!-- --- -->
-
-<!-- # Electricity flexible Capacity -->
-
-<!-- <!-- Electricity flexible Capacity (GW) --> -->
-
-<!-- ```{r, echo=FALSE} -->
-
-<!-- vars <- list( -->
-<!--   "Variable Renewables" = c( -->
-<!--     "Cap|Electricity|Solar|CSP", "Cap|Electricity|Solar|PV", "Cap|Electricity|Wind|Onshore", "Cap|Electricity|Wind|Offshore" -->
-
-<!--   ), -->
-<!--   "Hydrogen and batteries" = c( -->
-<!--     "Cap|Electricity|Hydrogen","Cap|Electricity|Storage|Battery" -->
-
-<!--   ), -->
-<!--   "Dispatchable fossil" = c( -->
-<!--     "Cap|Electricity|Coal|w/ CC", "Cap|Electricity|Coal|w/o CC", "Cap|Electricity|Oil", "Cap|Electricity|Gas|w/ CC", "Cap|Electricity|Gas|w/o CC" -->
-<!--   ), -->
-<!--   "Other non dispatchable" = c("Cap|Electricity|Nuclear", "Cap|Electricity|Geothermal", "Cap|Electricity|Hydro", "Cap|Electricity|Biomass|w/ CC", "Cap|Electricity|Biomass|w/o CC" -->
-<!--   ) -->
-<!-- ) -->
-
-<!-- plotData <- NULL -->
-<!-- for(group in names(vars)){ -->
-<!--   plotData <- rbind( -->
-<!--     plotData, -->
-<!--     df %>%  -->
-<!--       filter(region == "EU27",  -->
-<!--              period >= 2020, period <= 2060,  -->
-<!--              scenario  == mainScen,  -->
-<!--              variable %in% unlist(vars[[group]])) %>% -->
-<!--       group_by(model,scenario,region,period) %>% -->
-<!--       summarize(value = sum(value),.groups = "keep") %>% -->
-<!--       mutate(variable = group) -->
-<!--     ) -->
-<!--   } -->
-
-<!-- plotData <- plotData %>% -->
-<!--    mutate(variable = factor(variable, levels=names(vars))) %>%  -->
-<!--    arrange(factor(variable, levels = names(vars)))  -->
-
-<!-- # plotData <- plotData %>% -->
-<!-- #   mutate(variable = factor(variable, levels=names(vars))) %>%  -->
-<!-- #   arrange(factor(variable, levels = names(vars))) %>% -->
-<!-- #   group_by(model,scenario,region,period) %>% -->
-<!-- #   mutate(cumValue = cumsum(value), -->
-<!-- #          n = sum(value), -->
-<!-- #          percentage = value / n, -->
-<!-- #          cumPercentage = cumValue / n)  -->
-
-<!-- #inv_vars <- setNames(names(vars),vars) -->
-
-<!-- color <- c( -->
-<!--   "Variable Renewables"       = "#003b6d", -->
-<!--   "Hydrogen and batteries"   = "#6699cc", -->
-<!--   "Dispatchable fossil"   = "#bdbdbd", -->
-<!--   "Other non dispatchable"    = "#676767") -->
-
-<!-- #plotData2040 <- plotData[plotData$period == 2040,] -->
-<!-- #  -->
-<!-- #plotData2040$xPos <- 2042.5 -->
-<!-- #plotData2040[plotData2040$variable %in% c("SE|Electricity|Nuclear","SE|Electricity|Biomass|w/o CC"),]$xPos <- 2035 -->
-<!-- #  -->
-<!-- # plotDataRenewables <- plotData %>% -->
-<!-- #   filter(variable %in% c("Cap|Electricity|Hydrogen","Cap|Electricity|Geothermal","Cap|Electricity|Hydro","Cap|Electricity|Biomass|w/ CC","Cap|Electricity|Biomass|w/o CC","Cap|Electricity|Solar|CSP","Cap|Electricity|Solar|PV","Cap|Electricity|Wind|Onshore","Cap|Electricity|Wind|Offshore","Cap|Electricity|Nuclear","Cap|Electricity|Storage|Battery")) %>% -->
-<!-- #   group_by(model,scenario,region,period) %>% -->
-<!-- #   summarize(percentage = sum(percentage),.groups = "keep") -->
-
-<!-- g[["Electricity flexible capacity"]] <-  -->
-<!--   ggplot(plotData,aes(x=period,y=value)) + -->
-<!--   geom_area(aes(fill=variable), alpha = 0.9) + -->
-<!--   #geom_line(data=plotDataRenewables, linetype = "dashed", linewidth = 1.5, color="#666666") + -->
-<!--   #geom_bar(data=plotData2040,aes(fill=variable),stat='identity', show.legend = FALSE, alpha = 0.7, color="white", width = 3, linewidth = 1.5) + -->
-<!--   #ggrepel::geom_text_repel(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(round(percentage,2)*100,"%"), y=cumPercentage-percentage/2, x = 2043.5), vjust=0.5, hjust=0.5, na.rm=TRUE, color = "black", size = 12) + -->
-<!--   #geom_text(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(inv_vars[variable], " (",round(percentage,2)*100,"%)"), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size = 12) + -->
-<!--   #geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geom.text.double.size) + -->
-<!--   theme_doubleColumn()  + -->
-<!--   #scale_y_continuous(minor_breaks = seq(0.2, 0.8, 0.2), breaks=c(0,1),labels = scales::percent) + -->
-<!--   scale_x_continuous(breaks=c(2020,2040,2060)) + -->
-<!--   scale_fill_manual(values = color) + -->
-<!--   theme(axis.title.y=element_blank()) + -->
-<!--   guides(fill=guide_legend(nrow=8,override.aes = list(alpha=1), byrow = TRUE)) + -->
-<!--   #annotate(geom = "text", x = 2022, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage + 0.06, label = "renewables", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) + -->
-<!--   #annotate(geom = "text", x = 2023, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage - 0.06, label = "and nuclear", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) + -->
-<!--   #annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geom.text.double.size) + -->
-<!--   #annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, label = "renewables,\nnuclear and hydrogen", color = "#666666",angle = 90, hjust=0.5, vjust=-0.5, size=geom.text.double.size, lineheight = 0.8) + -->
-<!--   #annotate(geom = "text", x = 2020, y = (1-plotDataRenewables[plotDataRenewables$period == 2020,]$percentage)/2+plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "fossil", color = "#666666",angle = 90, hjust=0.5, vjust=-2, size=geom.text.double.size) + -->
-<!--   #annotation_custom(grob = linesGrob(gp=gpar(col="#666666",lwd = 3,lty="dashed")), xmin = 2016, xmax = 2019.8, ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage) + -->
-<!--   #theme(axis.text.y=element_blank()) + -->
-<!--   theme(legend.key.height = unit(0.8, "cm"), -->
-<!--     legend.key.width = unit(0.8,"cm")) + -->
-<!--   theme(legend.spacing.y = unit(0.1, 'cm')) + -->
-<!--   theme() + -->
-<!--   #annotate(geom = "text", label = "100%", x = 2020, y = 1, hjust=1.2, color = "#666666", size=geom.text.double.size) + -->
-<!--   #annotate(geom = "text", label = "0%", x = 2020, y = 0, hjust=1.2, color = "#666666", size=geom.text.double.size) + -->
-<!--   coord_cartesian(clip = 'off') + -->
-<!--   theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 20, unit = "pt") -->
-<!--         #,legend.margin=margin(l = -2, unit='cm') -->
-<!--         ) #+ -->
-<!--   #annotation_custom( -->
-<!--   #  grob = textGrob(label = "renewables\nand nuclear",hjust=0.5, vjust=-0.5, rot = 90, gp=gpar(col="#666666", fontsize=geom.text.double.size)), -->
-<!--   #  ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, -->
-<!--   #  xmin = 2020, xmax = 2020) -->
-
-<!-- ggsave(paste0(outChartsFolder,"/svg/Electricity flexible capacity.svg"), g[["Electricity flexible capacity"]] , device="svg", width = 6, height = 10, dpi=100, units = "in") -->
-<!-- ggsave(paste0(outChartsFolder,"/png/Electricity flexible capacity.png"), g[["Electricity flexible capacity"]] , device="png", width = 6, height = 10, dpi=300, units = "in") -->
-
-<!-- ``` -->
-
-<!-- ```{r, echo=FALSE, fig.width=6, fig.height=10} -->
-
-<!-- g[["Electricity flexible capacity"]] -->
-
-<!-- ``` -->
-
-<!-- Electricity Generation - Hydrogen input (%) -->
-
-<!-- ```{r, echo=FALSE} -->
-
-<!-- vars <- c( -->
-<!--   "Net Imports" = "SE|Electricity|Net Imports", -->
-<!--   "Coal w/ CC" = "SE|Electricity|Coal|w/ CC", -->
-<!--   "Coal w/o CC" = "SE|Electricity|Coal|w/o CC", -->
-<!--   "Oil" = "SE|Electricity|Oil", -->
-<!--   "Gas w/ CC" = "SE|Electricity|Gas|w/ CC", -->
-<!--   "Gas w/o CC" = "SE|Electricity|Gas|w/o CC", -->
-<!--   "Hydrogen" = "SE|Input|Electricity|Hydrogen", -->
-<!--   "Nuclear" = "SE|Electricity|Nuclear", -->
-<!--   "Geothermal" = "SE|Electricity|Geothermal", -->
-<!--   "Hydro" = "SE|Electricity|Hydro", -->
-<!--   "Biomass w/ CC" = "SE|Electricity|Biomass|w/ CC", -->
-<!--   "Biomass w/o CC" = "SE|Electricity|Biomass|w/o CC", -->
-<!--   "Solar CSP" = "SE|Electricity|Solar|CSP", -->
-<!--   "Solar PV" = "SE|Electricity|Solar|PV", -->
-<!--   "Wind Onshore" = "SE|Electricity|Wind|Onshore", -->
-<!--   "Wind Offshore" = "SE|Electricity|Wind|Offshore") -->
-
-<!-- inv_vars <- setNames(names(vars),vars) -->
-
-<!-- color <- c( -->
-<!--   "Net Imports"   = "#472b62", -->
-<!--   "Coal w/ CC"    = "#b2b2b2", -->
-<!--   "Coal w/o CC"   = "#0c0c0c", -->
-<!--   "Oil"           = "#b30000", -->
-<!--   "Gas w/ CC"     = "#b79e38", -->
-<!--   "Gas w/o CC"    = "#999959", -->
-<!--   "Hydrogen"      = "#5ed5b0", -->
-<!--   "Nuclear"       = "#ff33ff", -->
-<!--   "Geothermal"    = "#e51900", -->
-<!--   "Hydro"         = "#191999", -->
-<!--   "Biomass w/ CC" = "#33ff00", -->
-<!--   "Biomass w/o CC"= "#005900", -->
-<!--   "Solar CSP"     = "#ffcc00", -->
-<!--   "Solar PV"      = "#ffe600", -->
-<!--   "Wind Onshore"  = "#193F7F", -->
-<!--   "Wind Offshore" = "#337fff") -->
-
-<!-- plotData <- df %>%  -->
-<!--   filter(region == "EU27", period >= 2020, period <= 2060, scenario  == mainScen, variable %in% unlist(vars)) %>%  -->
-<!--   mutate(variable = factor(variable, levels=vars)) %>%  -->
-<!--   arrange(factor(variable, levels = rev(vars))) %>% -->
-<!--   group_by(model,scenario,region,period) %>% -->
-<!--   mutate(cumValue = cumsum(value), -->
-<!--          n = sum(value), -->
-<!--          percentage = value / n, -->
-<!--          cumPercentage = cumValue / n)  -->
-
-<!-- plotData2040 <- plotData[plotData$period == 2040,] -->
-<!-- #plotData$value <- plotData$value / plotData[plotData$period == "2020",]$value -->
-<!-- #plotData$period <- as.character(plotData$period) -->
-<!-- #plotData$period <- factor(plotData$period , levels = rev(c("2020","2030","2040","2050"))) -->
-
-<!-- plotData2040$xPos <- 2042.5 -->
-<!-- #plotData2040[plotData2040$variable %in% c("SE|Electricity|Hydro"),]$xPos <- 2028.5 -->
-<!-- #plotData2040[plotData2040$variable %in% c("SE|Electricity|Biomass|w/o CC"),]$xPos <- 2020 -->
-<!-- plotData2040[plotData2040$variable %in% c("SE|Electricity|Nuclear","SE|Electricity|Biomass|w/o CC"),]$xPos <- 2035 -->
-
-<!-- plotDataRenewables <- plotData %>% -->
-<!--   filter(variable %in% c("SE|Input|Electricity|Hydrogen", "SE|Electricity|Geothermal","SE|Electricity|Hydro","SE|Electricity|Biomass|w/ CC","SE|Electricity|Biomass|w/o CC","SE|Electricity|Solar|CSP","SE|Electricity|Solar|PV","SE|Electricity|Wind|Onshore","SE|Electricity|Wind|Offshore","SE|Electricity|Nuclear")) %>% -->
-<!--   group_by(model,scenario,region,period) %>% -->
-<!--   summarize(percentage = sum(percentage),.groups = "keep") -->
-
-<!-- g[["Electricity Generation - Hydrogen input"]] <-  -->
-<!--   ggplot(plotData,aes(x=period,y=percentage)) + -->
-<!--   geom_area(aes(fill=variable),alpha=0.4) + -->
-<!--   geom_line(data=plotDataRenewables, linetype = "dashed", linewidth = 1.5, color="#666666") + -->
-<!--   geom_bar(data=plotData2040,aes(fill=variable),stat='identity', show.legend = FALSE, alpha = 0.7, color="white", width = 3, linewidth = 1.5) + -->
-<!--   #ggrepel::geom_text_repel(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(round(percentage,2)*100,"%"), y=cumPercentage-percentage/2, x = 2043.5), vjust=0.5, hjust=0.5, na.rm=TRUE, color = "black", size = 12) + -->
-<!--   #geom_text(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(inv_vars[variable], " (",round(percentage,2)*100,"%)"), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size = 12) + -->
-<!--   geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geom.text.double.size) + -->
-<!--   theme_doubleColumn()  + -->
-<!--   scale_y_continuous(minor_breaks = seq(0.2, 0.8, 0.2), breaks=c(0,1),labels = scales::percent) + -->
-<!--   scale_x_continuous(breaks=c(2020,2040,2060)) + -->
-<!--   scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) + -->
-<!--   theme(axis.title.y=element_blank()) + -->
-<!--   guides(fill=guide_legend(nrow=8,override.aes = list(alpha=1), byrow = TRUE)) + -->
-<!--   #annotate(geom = "text", x = 2022, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage + 0.06, label = "renewables", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) + -->
-<!--   #annotate(geom = "text", x = 2023, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage - 0.06, label = "and nuclear", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) + -->
-<!--   #annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geom.text.double.size) + -->
-<!--   annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, label = "renewables,\nnuclear and hydrogen", color = "#666666",angle = 90, hjust=0.5, vjust=-0.5, size=geom.text.double.size, lineheight = 0.8) + -->
-<!--   annotate(geom = "text", x = 2020, y = (1-plotDataRenewables[plotDataRenewables$period == 2020,]$percentage)/2+plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "fossil", color = "#666666",angle = 90, hjust=0.5, vjust=-2, size=geom.text.double.size) + -->
-<!--   annotation_custom(grob = linesGrob(gp=gpar(col="#666666",lwd = 3,lty="dashed")), xmin = 2016, xmax = 2019.8, ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage) + -->
-<!--   theme(axis.text.y=element_blank()) + -->
-<!--   theme(legend.key.height = unit(0.8, "cm"), -->
-<!--     legend.key.width = unit(0.8,"cm")) + -->
-<!--   theme(legend.spacing.y = unit(0.1, 'cm')) + -->
-<!--   theme() + -->
-<!--   annotate(geom = "text", label = "100%", x = 2020, y = 1, hjust=1.2, color = "#666666", size=geom.text.double.size) + -->
-<!--   annotate(geom = "text", label = "0%", x = 2020, y = 0, hjust=1.2, color = "#666666", size=geom.text.double.size) + -->
-<!--   coord_cartesian(clip = 'off') + -->
-<!--   theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 20, unit = "pt") -->
-<!--         #,legend.margin=margin(l = -2, unit='cm') -->
-<!--         ) #+ -->
-<!--   #annotation_custom( -->
-<!--   #  grob = textGrob(label = "renewables\nand nuclear",hjust=0.5, vjust=-0.5, rot = 90, gp=gpar(col="#666666", fontsize=geom.text.double.size)), -->
-<!--   #  ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, -->
-<!--   #  xmin = 2020, xmax = 2020) -->
-
-<!-- ggsave(paste0(outChartsFolder,"/svg/Electricity Generation - Hydrogen input.svg"), g[["Electricity Generation - Hydrogen input"]] , device="svg", width = 6, height = 10, dpi=100, units = "in") -->
-<!-- ggsave(paste0(outChartsFolder,"/png/Electricity Generation - Hydrogen input.png"), g[["Electricity Generation - Hydrogen input"]] , device="png", width = 6, height = 10, dpi=300, units = "in") -->
-
-<!-- ``` -->
-
-<!-- ```{r, echo=FALSE, fig.width=6, fig.height=10} -->
-
-<!-- g[["Electricity Generation - Hydrogen input"]] -->
-
-<!-- ``` -->
-
-<!-- --- -->
-
-<!-- ```{r chart_figure5, echo=FALSE} -->
-
-<!-- # “existent targets” -->
-<!-- # emission reduction - 2030 (FitFor55) - 2030 scenarios - 2040 scenarios -->
-<!-- # energy savings  - 2030 (FitFor55 and REPowerEU) - 2030 scenarios - 2040 scenarios -->
-<!-- # renewables target - 2030 (RED II, RED II revised, REPowerEU) - 2030 scenarios - 2040 scenarios -->
-<!-- # solar photovoltaics capacity - 2030 (REPowerEU) - 2030 scenarios - 2040 scenarios -->
-<!-- # CCS capacity target - 2030 EU-wide 50 MtCO2/y “Net-Zero Industry Act" -->
-<!-- # “implicit targets” -->
-<!-- # electrification? -> fe electrification share -> 45% -->
-<!-- # “carbon-content in electricity” ->“carbon-free electricity” (>95%)  -->
-<!-- # Total Residual Fossil emissions -->
-<!-- # sectoral emissions -> Transport emissions -> 23% of 2020  -->
-<!-- #                                   -> Industry and buildings emissions -> 27% of 2020 -->
-<!-- # “residual fossil”     -> Complete coal-phase by 2040 -->
-<!-- #                                  -> natural gas -->
-<!-- #                                 -> oil -->
-<!-- # “net trade” -> net-supply independency of gas by 2040 -->
-<!-- #                       -> one third of oil imports by 2040 -->
-
-<!-- #Emissions Reduction -->
-<!-- plotData <- rbind( -->
-<!--     df %>%  -->
-<!--       filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>% -->
-<!--       calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%  -->
-<!--       mutate(value = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)) ,2)) %>%  -->
-<!--       select(-variable) -->
-<!--     , -->
-<!--     df %>%  -->
-<!--       filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>% -->
-<!--       calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%  -->
-<!--       mutate(value = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)) ,2)) %>%  -->
-<!--       select(-variable) -->
-<!--   ) %>% -->
-<!--   filter(tgt2050 != "Npi") %>% -->
-<!--   mutate(target = "Emissions\nreductions") %>% -->
-<!--   group_by(period) %>%  -->
-<!--   mutate(min = min(value), -->
-<!--         max = max(value)) -->
-
-<!-- fullPlotData <- plotData  -->
-
-<!-- h <- refEmi %>% filter(variable == "Emissions with LULUCF and with international transport", region == "EU27", pollutant == "All greenhouse gases - (CO2 equivalent)") %>% ungroup() %>% select(region,variable,period,value) -->
-<!-- emi1990 <- tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference) -->
-<!-- reduction_h <- 1- (h %>% filter(period==2022) %>% pull(value) / emi1990) -->
-
-<!-- g[["milestone - vert"]][["Emissions reductions"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
-<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
-<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
-<!--   geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
-<!--   annotate("text", x = Inf, y = 0.55, label = "FitFor55", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
-<!--   geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
-<!--   annotate("text", x = Inf, y = reduction_h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
-<!--   facet_grid(.~target, scales="free") + -->
-<!--   theme_doubleColumn() + -->
-<!--   theme(axis.title.y=element_blank()) + -->
-<!--   theme(strip.text.y = element_blank()) + -->
-<!--   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) + -->
-<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
-<!--   expand_limits(y=c(0,1)) +  -->
-<!--   theme(panel.spacing = unit(4, "lines")) + -->
-<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
-<!--   theme(strip.placement = "outside") + -->
-<!--   theme(strip.text = element_text(angle = 90)) + -->
-<!--   coord_cartesian(clip = 'off') #+ -->
-<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
-<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->
-
-<!-- # Final Energy Demand - Energy savings -->
-<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "FE|w/o Non-energy Use w/o Bunkers") %>% select(-variable) %>% -->
-<!--   mutate(value = round(value * 23.8845896627496)) %>% -->
-<!--   filter(tgt2050 != "Npi") %>% -->
-<!--   mutate(target = "Final Energy\nDemand") %>% -->
-<!--   group_by(period) %>%  -->
-<!--   mutate(min = min(value), -->
-<!--         max = max(value)) -->
-
-<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->
-
-<!-- h <- addHist$FE_consumption %>% #TJ -->
-<!--   mutate(value = value/1000000) %>% #EJ -->
-<!--   mutate(value = round(value * 23.8845896627496)) # 1EJ = 23.8845896627496 Mtoe -->
-
-<!-- g[["milestone - vert"]][["Energy savings"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
-<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
-<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
-<!--   geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
-<!--   geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
-<!--   annotate("text", x = Inf, y = 750, label = "REPowerEU", vjust = 1.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
-<!--   annotate("text", x = Inf, y = 787, label = "FitFor55", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
-<!--   geom_hline(yintercept=h %>% filter(period==2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
-<!--   annotate("text", x = Inf, y = h %>% filter(period==2022) %>% pull(value), label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
-<!--   facet_grid(.~target, scales="free") + -->
-<!--   theme_doubleColumn() + -->
-<!--   theme(axis.title.y=element_blank()) + -->
-<!--   theme(strip.text.y = element_blank()) + -->
-<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
-<!--   expand_limits(y=c(0,400,1000)) +  -->
-<!--   theme(panel.spacing = unit(4, "lines")) + -->
-<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
-<!--   theme(strip.placement = "outside") + -->
-<!--   theme(strip.text = element_text(angle = 90)) + -->
-<!--   coord_cartesian(clip = 'off') + -->
-<!--   annotate("text", x = -Inf, y = Inf, label = "(Mtoe)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+ -->
-<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
-<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->
-
-<!-- # Electricity Demand -->
-<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "FE|Electricity") %>% select(-variable) %>% -->
-<!--   mutate(value = round(value * 1/0.0036)) %>% -->
-<!--   filter(tgt2050 != "Npi") %>% -->
-<!--   mutate(target = "Electricity\nDemand") %>% -->
-<!--   group_by(period) %>%  -->
-<!--   mutate(min = min(value), -->
-<!--         max = max(value)) -->
-
-<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->
-
-<!-- #2022 = 2469471.42 GWh = 2469471.42 *1000 / 8.76E+09 * 31.536 EJ - FE electricity - https://ec.europa.eu/eurostat/databrowser/bookmark/d19a01c7-6099-4b88-8ccd-c6bcc01c3ddc?lang=en -->
-<!-- h <- 2469471.42 /1000 -->
-<!-- # old value? 2641 -->
-
-<!-- g[["milestone - vert"]][["Electricity Demand"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
-<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
-<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
-<!--   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
-<!--   annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
-<!--   facet_grid(.~target, scales="free") + -->
-<!--   theme_doubleColumn() + -->
-<!--   theme(axis.title.y=element_blank()) + -->
-<!--   theme(strip.text.y = element_blank()) + -->
-<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
-<!--   expand_limits(y=c(0,5000)) +  -->
-<!--   theme(panel.spacing = unit(4, "lines")) + -->
-<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
-<!--   theme(strip.placement = "outside") + -->
-<!--   theme(strip.text = element_text(angle = 90)) + -->
-<!--   coord_cartesian(clip = 'off') + -->
-<!--   annotate("text", x = -Inf, y = Inf, label = "(TWh)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+ -->
-<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
-<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->
-
-<!-- # Renewables share -->
-<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "SE|Renewables Share") %>% select(-variable) %>% -->
-<!--   filter(tgt2050 != "Npi") %>% -->
-<!--   mutate(target = "Renewables\nShare in\nFinal Energy")  -->
-
-<!-- plotData$value <- plotData$value*( -->
-<!--   addHist$res %>% filter(type == "RES", period == 2020) %>% pull(value) / -->
-<!--    df %>% filter(region == "EU27", period == 2020, variable == "SE|Renewables Share", scenario == mainScen) %>% pull(value)  -->
-<!-- ) -->
-
-<!-- plotData <- plotData %>% -->
-<!--   group_by(period) %>%  -->
-<!--   mutate(min = min(value), -->
-<!--         max = max(value)) -->
-
-<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->
-
-<!-- g[["milestone - vert"]][["Renewables Share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
-<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
-<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
-<!--   geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
-<!--   annotate("text", x = Inf, y = 0.4, label = "RED II revised", vjust = 1.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
-<!--   geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
-<!--   annotate("text", x = Inf, y = 0.45, label = "REPowerEU", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
-<!--   geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
-<!--   annotate("text", x = Inf, y = addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
-<!--   facet_grid(.~target, scales="free") + -->
-<!--   theme_doubleColumn() + -->
-<!--   theme(axis.title.y=element_blank()) + -->
-<!--   theme(strip.text.y = element_blank()) + -->
-<!--   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) + -->
-<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
-<!--   expand_limits(y=c(0,1)) +  -->
-<!--   theme(panel.spacing = unit(4, "lines")) + -->
-<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
-<!--   theme(strip.placement = "outside") + -->
-<!--   theme(strip.text = element_text(angle = 90)) + -->
-<!--   coord_cartesian(clip = 'off') #+ -->
-<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
-<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->
-
-<!-- # Wind -->
-<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Cap|Electricity|Wind") %>% select(-variable) %>% -->
-<!--   filter(tgt2050 != "Npi") %>% -->
-<!--   mutate(target = "Wind\ncapacity") %>% -->
-<!--   group_by(period) %>%  -->
-<!--   mutate(min = min(value), -->
-<!--         max = max(value))  -->
-
-<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->
-
-<!-- g[["milestone - vert"]][["Wind capacity"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
-<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
-<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
-<!--   geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
-<!--   annotate("text", x = Inf, y = 255, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
-<!--   facet_grid(.~target, scales="free") + -->
-<!--   theme_doubleColumn() + -->
-<!--   theme(axis.title.y=element_blank()) + -->
-<!--   theme(strip.text.y = element_blank()) + -->
-<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
-<!--   expand_limits(y=c(0,1000)) +  -->
-<!--   theme(panel.spacing = unit(4, "lines")) + -->
-<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
-<!--   theme(strip.placement = "outside") + -->
-<!--   theme(strip.text = element_text(angle = 90)) + -->
-<!--   coord_cartesian(clip = 'off') + -->
-<!--   annotate("text", x = -Inf, y = Inf, label = "(GW)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+ -->
-<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
-<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->
-
-<!-- # Solar photovoltaics -->
-<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Cap|Electricity|Solar|PV") %>% select(-variable) %>% -->
-<!--   filter(tgt2050 != "Npi") %>% -->
-<!--   mutate(target = "Solar\nphotovoltaics") %>% -->
-<!--   group_by(period) %>%  -->
-<!--   mutate(min = min(value), -->
-<!--         max = max(value))  -->
-
-<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->
-
-<!-- g[["milestone - vert"]][["Solar photovoltaics"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
-<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
-<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
-<!--   geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
-<!--   annotate("text", x = Inf, y = 600, label = "REPowerEU", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
-<!--   geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
-<!--   annotate("text", x = Inf, y = 208.9, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
-<!--   facet_grid(.~target, scales="free") + -->
-<!--   theme_doubleColumn() + -->
-<!--   theme(axis.title.y=element_blank()) + -->
-<!--   theme(strip.text.y = element_blank()) + -->
-<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
-<!--   expand_limits(y=c(0,2500)) +  -->
-<!--   theme(panel.spacing = unit(4, "lines")) + -->
-<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
-<!--   theme(strip.placement = "outside") + -->
-<!--   theme(strip.text = element_text(angle = 90)) + -->
-<!--   coord_cartesian(clip = 'off') + -->
-<!--   annotate("text", x = -Inf, y = Inf, label = "(GW)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+ -->
-<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
-<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->
-
-<!-- # Carbon Capture and Storage  -->
-<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Carbon Management|Storage") %>% select(-variable) %>% -->
-<!--   filter(tgt2050 != "Npi") %>% -->
-<!--   mutate(target = "Carbon\nCapture and\nStorage") %>% -->
-<!--   group_by(period) %>%  -->
-<!--   mutate(min = min(value), -->
-<!--         max = max(value))  -->
-
-<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->
-
-<!-- g[["milestone - vert"]][["Carbon Capture and Storage"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
-<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
-<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
-<!--   geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
-<!--   annotate("text", x = Inf, y = 50, label = "Net-Zero\nIndustry Act", vjust = 0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
-<!--   facet_grid(.~target, scales="free") + -->
-<!--   theme_doubleColumn() + -->
-<!--   theme(axis.title.y=element_blank()) + -->
-<!--   theme(strip.text.y = element_blank()) + -->
-<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
-<!--   expand_limits(y=c(0,400)) +  -->
-<!--   theme(panel.spacing = unit(4, "lines")) + -->
-<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
-<!--   theme(strip.placement = "outside") + -->
-<!--   theme(strip.text = element_text(angle = 90)) + -->
-<!--   coord_cartesian(clip = 'off') + -->
-<!--   annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+ -->
-<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
-<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->
-
-<!-- # Novel CDR = atmospheric/biogenic CO2 (CDR)  -->
-<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Carbon Management|atmospheric/biogenic CO2 - CDR") %>% select(-variable) %>% -->
-<!--   filter(tgt2050 != "Npi") %>% -->
-<!--   mutate(target = "BECCS\nand\nDACCS") %>% -->
-<!--   group_by(period) %>%  -->
-<!--   mutate(min = min(value), -->
-<!--         max = max(value))  -->
-
-<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->
-
-<!-- g[["milestone - vert"]][["Novel CDR"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
-<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
-<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
-<!--   facet_grid(.~target, scales="free") + -->
-<!--   theme_doubleColumn() + -->
-<!--   theme(axis.title.y=element_blank()) + -->
-<!--   theme(strip.text.y = element_blank()) + -->
-<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
-<!--   expand_limits(y=c(0,400)) +  -->
-<!--   theme(panel.spacing = unit(4, "lines")) + -->
-<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
-<!--   theme(strip.placement = "outside") + -->
-<!--   theme(strip.text = element_text(angle = 90)) + -->
-<!--   coord_cartesian(clip = 'off') + -->
-<!--   annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+ -->
-<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
-<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->
-
-<!-- # Direct Electrification -->
-<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Final Energy|Electricity Share") %>% select(-variable) %>% -->
-<!--   filter(tgt2050 != "Npi") %>% -->
-<!--   mutate(target = "Electricity\nShare in\nFinal Energy") %>% -->
-<!--   group_by(period) %>%  -->
-<!--   mutate(min = min(value), -->
-<!--         max = max(value))  -->
-
-<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->
-
-<!-- #estimation of historical share in 2022 for FE electricity / FE with non-energy use and with bunkers -->
-<!-- h <- ( -->
-<!--       2550461.10 *1000 / 8.76E+09 * 31.536  # https://ec.europa.eu/eurostat/databrowser/bookmark/12d54df4-7c35-47eb-a103-dd8994d26b80?lang=en -->
-<!--      ) / ( -->
-<!--       addHist$FE_consumption %>% mutate(value = value/1000000) %>% filter(period==2022) %>% pull(value) + # FE|w/o Non-energy Use w/o Bunkers - EJ -->
-<!--       df %>% filter(region == "EU27", period == 2020, scenario == "Npi", variable == "FE|Transport|Bunkers") %>% pull(value) + -->
-<!--       df %>% filter(region == "EU27", period == 2020, scenario == "Npi", variable == "FE|Non-energy Use|Industry") %>% pull(value) -->
-<!--      ) -->
-
-<!-- g[["milestone - vert"]][["Direct Electrification"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
-<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
-<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
-<!--   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
-<!--   annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
-<!--   facet_grid(.~target, scales="free") + -->
-<!--   theme_doubleColumn() + -->
-<!--   theme(axis.title.y=element_blank()) + -->
-<!--   theme(strip.text.y = element_blank()) + -->
-<!--   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) + -->
-<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
-<!--   expand_limits(y=c(0,1)) +  -->
-<!--   theme(panel.spacing = unit(4, "lines")) + -->
-<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
-<!--   theme(strip.placement = "outside") + -->
-<!--   theme(strip.text = element_text(angle = 90)) + -->
-<!--   coord_cartesian(clip = 'off') #+ -->
-<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
-<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->
-
-<!-- # Carbon-free electricity share -->
-<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "SE|Electricity|carbon-free") %>% select(-variable) %>% -->
-<!--   filter(tgt2050 != "Npi") %>% -->
-<!--   mutate(target = "Carbon-free\nelectricity\nshare") %>% -->
-<!--   group_by(period) %>%  -->
-<!--   mutate(min = min(value), -->
-<!--         max = max(value))   -->
-
-<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->
-
-<!-- #historical - 2022 - https://ec.europa.eu/eurostat/statistics-explained/index.php?title=Electricity_and_heat_statistics&oldid=347519 -->
-<!-- #solid fossil	453180 -->
-<!-- #oil	54277 -->
-<!-- #gas	571687 -->
-<!-- #nuclear	609169 -->
-<!-- #renewables	1076710 -->
-<!-- #other	32822 -->
-<!-- h <- (609169 + 1076710)	/ (453180 + 54277 + 571687 + 609169 + 1076710 + 32822) -->
-
-<!-- g[["milestone - vert"]][["Carbon-free electricity share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
-<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
-<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
-<!--   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
-<!--   annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
-<!--   facet_grid(.~target, scales="free") + -->
-<!--   theme_doubleColumn() + -->
-<!--   theme(axis.title.y=element_blank()) + -->
-<!--   theme(strip.text.y = element_blank()) + -->
-<!--   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) + -->
-<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
-<!--   expand_limits(y=c(0,1)) +  -->
-<!--   theme(panel.spacing = unit(4, "lines")) + -->
-<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
-<!--   theme(strip.placement = "outside") + -->
-<!--   theme(strip.text = element_text(angle = 90)) + -->
-<!--   coord_cartesian(clip = 'off') #+ -->
-<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
-<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->
-
-<!-- # Residual Fossil Emissions -->
-<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% select(-variable) %>% -->
-<!--   filter(tgt2050 != "Npi") %>% -->
-<!--   mutate(target = "Residual\nFossil\nEmissions") %>% -->
-<!--   group_by(period) %>%  -->
-<!--   mutate(min = min(value), -->
-<!--         max = max(value))   -->
-
-<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->
-
-<!-- g[["milestone - vert"]][["Residual Fossil Emissions"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
-<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
-<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
-<!--   facet_grid(.~target, scales="free") + -->
-<!--   theme_doubleColumn() + -->
-<!--   theme(axis.title.y=element_blank()) + -->
-<!--   theme(strip.text.y = element_blank()) + -->
-<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
-<!--   expand_limits(y=c(0,2500)) +  -->
-<!--   theme(panel.spacing = unit(4, "lines")) + -->
-<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
-<!--   theme(strip.placement = "outside") + -->
-<!--   theme(strip.text = element_text(angle = 90)) + -->
-<!--   coord_cartesian(clip = 'off') + -->
-<!--   annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+ -->
-<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
-<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->
-
-<!-- # Domestic Hydrogen Production -->
-<!-- plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "SE|Hydrogen") %>% select(-variable) %>% -->
-<!--   mutate(value = value*8)  %>% #1EJ <- 8 million tons adrian -->
-<!--   filter(tgt2050 != "Npi") %>% -->
-<!--   mutate(target = "Domestic\nHydrogen\nProduction") %>% -->
-<!--   group_by(period) %>%  -->
-<!--   mutate(min = min(value), -->
-<!--         max = max(value))  -->
-
-<!-- fullPlotData <- rbind(fullPlotData,plotData)  -->
-
-<!-- target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2030,2030),value=c(10,20)) -->
-
-<!-- g[["milestone - vert"]][["Domestic Hydrogen Production"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) + -->
-<!--   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) + -->
-<!--   geom_boxplot(outlier.shape = NA, width=6) + -->
-<!--   geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") + -->
-<!--   annotate("text", x = -Inf, y = 10, label = "REPowerEU\ndomestic", vjust = 0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) + -->
-<!--   facet_grid(.~target, scales="free") + -->
-<!--   theme_doubleColumn() + -->
-<!--   theme(axis.title.y=element_blank()) + -->
-<!--   theme(strip.text.y = element_blank()) + -->
-<!--   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") + -->
-<!--   expand_limits(y=c(0,20)) +  -->
-<!--   theme(panel.spacing = unit(4, "lines")) + -->
-<!--   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) + -->
-<!--   theme(strip.placement = "outside") + -->
-<!--   theme(strip.text = element_text(angle = 90)) + -->
-<!--   coord_cartesian(clip = 'off') + -->
-<!--   annotate("text", x = -Inf, y = Inf, label = "(Mtoe)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+ -->
-<!--   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) + -->
-<!--   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) -->
-
-<!-- ``` -->
-
-<!-- ```{r, echo=FALSE} -->
-
-<!-- g[["ECEMP abstract"]] <- gridExtra::arrangeGrob( -->
-<!--   g[["milestone - vert"]][["Electricity Demand"]] + theme(plot.margin=margin(r=30,t = 35)), -->
-<!--   g[["milestone - vert"]][["Direct Electrification"]] + theme(plot.margin=margin(r=30,t = 17)), -->
-<!--   g[["milestone - vert"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(t = 24)), -->
-<!--   g[["milestone - vert"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(r=30,t = 39)), -->
-<!--   g[["milestone - vert"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(r=30,t = 15)), -->
-<!--   g[["milestone - vert"]][["Novel CDR"]] + theme(plot.margin=margin(t = 50)), -->
-<!--   nrow = 1 -->
-<!-- ) -->
-
-<!-- ggsave(paste0(outChartsFolder,"/png/ECEMP abstract.png"), g[["ECEMP abstract"]] , device="png", width = 12, height = 8, dpi=300, units = "in") -->
-
-<!-- ``` -->
-
 # Power sector Emissions
@@
       axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
-      #axis.text = element_text(size = theme.double.text.size),
-      #legend.text=element_text(size= theme.double.text.size),
-      #axis.text.x = element_text(size = 0.8*theme.double.text.size, angle = 90, hjust = 1, vjust = 0.5),
-      #axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 10)),
       legend.key.height = unit(1, "cm"),
@@
       plot.background = element_rect(fill="#FFFFFF", color = NA),
-      #panel.spacing = unit(1, "lines"),
-      #plot.title = element_text(size = theme.double.text.size, face = "plain"),
-      #strip.text.x = element_text(size = theme.double.text.size)
     )
@@
 
-plotData <- df_beforeFilter %>%
+plotData <- df %>%
   filter(region == "EU27", period %in% c(2010:2050), variable == "Emi|CO2|Energy|Supply|Electricity w/ couple prod", scenario != "Npi") %>%
@@
 
-plotData2 <- df_beforeFilter %>%
+plotData2 <- df %>%
   filter(region == "EU27", period %in% c(2010:2050), variable == "Emi|CO2|Energy|Supply|Electricity w/ couple prod", scenario != "Npi") %>%
@@
 
-plotData <- df %>%
-  filter(region == "EU27", period %in% c(2010:2050), variable == "Emi|CO2|Energy|Supply|Electricity w/ couple prod", scenario != "Npi") %>%
-  group_by(period) %>%
-  summarise_at(vars(value), list(
-    Min = min,
-    Mean = mean,
-    Median = median,
-    Max = max,
-    Sd = sd,
-    Q1=~quantile(., probs = 0.25),
-    Q3=~quantile(., probs = 0.75)))
+```
 
-plotData2 <- df %>%
-  filter(region == "EU27", period %in% c(2010:2050), variable == "Emi|CO2|Energy|Supply|Electricity w/ couple prod", scenario != "Npi") %>%
-  filter(scenario == mainScen)
+```{r, echo=FALSE, fig.width=12, fig.height=8}
 
-g[["power_sector_emissions_noLimVRE"]] <- ggplot(plotData,aes(x=period,y=Median)) +
-    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
-    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
-    #geom_line(linewidth=1,color="black") +
-    geom_line(data = histEmber,aes(x=period,y=value), linewidth=1,color="black",linetype="dashed") +
-    geom_line(data = plotData2,aes(x=period,y=value), linewidth=1,color="black") +
-    geom_ribbon(aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") +
-    geom_ribbon(aes(ymax = Max, ymin = Min), alpha = 0.5, fill = "#545454") +
-    #geom_line(aes(y=Min),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) +
-    #geom_line(aes(y=Max),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) +
-    #geom_line(data=h,linewidth=1,aes(linetype=Source)) +
-    #geom_point() +
-    theme_white() +
-    ylab(expression(paste("Mt ", CO[2],"/yr")))
-
-ggsave(paste0(outChartsFolder,"/svg/power_sector_emissions_noLimVRE.svg"), g[["power_sector_emissions_noLimVRE"]], device="svg", width = 12, height = 8, dpi=100, units = "in")
-ggsave(paste0(outChartsFolder,"/png/power_sector_emissions_noLimVRE.png"), g[["power_sector_emissions_noLimVRE"]], device="png", width = 12, height = 8, dpi=300, units = "in")
+g[["power_sector_emissions"]]
 

### 2025-04-24 report_paperCharts.Rmd
update limVRE setup and general cleanup

@@
 
-# all emission reductions were calculated relative to 1990 emissions with LULUCF and international transport (4814 Mt CO2e), except for 2030 emission reduction calculated relative to 1990 emissions with LULUCF and intra-EU aviation only (4713 Mt CO2e).
+# Emission reductions relative to 1990 emissions include LULUCF and intra-EU aviation only (4713 Mt CO2e), except for 2045 and 2050 emission reductions which are calculated relative to 1990 emissions including LULUCF and international transport (4814 Mt CO2e).
 
@@
     geom_line(data=plotData %>% filter(scenario == mainScen), linewidth=1.5) +
-    #geom_line(data=plotData, color= "#545454", linewidth=0.2, alpha=0.2, aes(group=scenario)) +
     geom_line(data=h,linewidth=0.7,linetype="dashed") +
     geom_line(data=linearProjection,linewidth=0.8,linetype="dashed") +
-    #geom_segment(data=plotData %>% filter(scenario == mainScen, period == 2040), aes(x=2040, xend=2040, y=0, yend=value), linetype="dashed", color="black") +
     geom_segment(data=linearProjection %>% filter(period == 2040), aes(x=2040, xend=2040, y=0, yend=value), linetype="dashed", color="black") +
@@
                      size = geomText.size) + 
-    theme_doubleColumn() +
-    theme(axis.title.y=element_blank()) +
     expand_limits(y=emi1990) +
@@
     labs(title = expression(paste("(a) Total GHG emissions (Mt ", CO[2],"eq/yr)"))) + 
-    #theme(plot.title = element_text(hjust = -0.2)) +
-    theme(plot.title = element_text(margin=margin(b=35)))
+    theme_doubleColumn() +
+    theme(axis.title.y=element_blank(),
+          plot.title = element_text(margin=margin(b=35)))
 
@@
   geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
-  theme_doubleColumn() +
   scale_fill_manual(values = c("emi" = "black", "2040" = "#5a788b")) + 
@@
   scale_y_continuous(breaks = c(0,1000/emi1990,2000/emi1990,3000/emi1990,4000/emi1990,5000/emi1990)) + 
-  theme(legend.position = "none") +
   labs(title = "(b) Emission reductions (%)") + 
-  theme(plot.title = element_text(margin=margin(b=35)))
-
-g[["GHG Emission reductions"]] <- gridExtra::arrangeGrob(
-  g[["GHG emi"]], #+ theme(plot.margin=margin(10,10,30,10)),
-  g[["target"]], # + theme(plot.margin=margin(10,10,10,10)),
-  layout_matrix = rbind(c(1, 1, 1, 1, 2, 2, 2),
-                        c(1, 1, 1, 1, 2, 2, 2))
-   )
-# 
-#  ggsave(paste0(outChartsFolder,"/svg/Figure 1. Emission results panel - (a) GHG and (b) reduction.svg"), g[["GHG Emission reductions"]] , device="svg", width = 12, height = 5, dpi=100, units = "in")
-#  ggsave(paste0(outChartsFolder,"/png/Figure 1. Emission results panel - (a) GHG and (b) reduction.png"), g[["GHG Emission reductions"]] , device="png", width = 12, height = 5, dpi=300, units = "in")
+  theme_doubleColumn() +
+  theme(legend.position = "none",
+        plot.title = element_text(margin=margin(b=35)))
 
@@
   "Energy Demand - Industry and Agriculture"  = "Emi|GHG|Gross|Energy|Demand|Industry",
-  "Energy Demand - Carbon Dioxide Removal"    = "Emi|GHG|Energy|Demand|CDR",
+  "Energy Demand - CDR"                       = "Emi|GHG|Energy|Demand|CDR",
   "Industrial Processes"                      = "Emi|GHG|Industrial Processes",
@@
   "Energy Demand - Industry and Agriculture"  = "#a5a5a5",
-  "Energy Demand - Carbon Dioxide Removal"    = "#999959",
+  "Energy Demand - CDR"                       = "#999959",
   "Industrial Processes"                      = "#5c5c5c",
@@
   geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
-  theme_doubleColumn() +
-  #ylab("Final Energy Demand - EJ/yr") + 
-  #ggtitle("(a) per sector and carrier") +
   scale_fill_manual(values = setNames(plotColor[names(vars)],vars), labels = setNames(names(vars), vars)) +
-  #theme(legend.margin=margin(l = -1, unit='cm')) +
   scale_x_continuous(breaks=c(2010, 2010, 2020,2030,2040,2050)) + 
-  theme(axis.title.x=element_blank()) +
-  theme(axis.title.y=element_blank()) +
-  theme(legend.title = element_blank()) +
-  theme(#legend.text = element_text(size = theme.double.text.size*0.7),
-        #legend.key.height = unit(0.7, "cm"),
-        #legend.key.width = unit(0.7,"cm"),
-        legend.spacing.x = unit(0.2, 'cm')) + 
-  #  theme(plot.title = element_text(size = 1.2*theme.double.text.size)) +
-  theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical") +
   labs(title = "(c) GHG Emissions per sector in the reference scenario (Mt CO2/yr)") + 
-  theme(legend.margin=margin(t=30)) +
-  theme(plot.margin = margin(t = 15, unit = "pt"))
+  theme_doubleColumn() +
+  theme(axis.title.x=element_blank(),
+        axis.title.y=element_blank(),
+        legend.title = element_blank(),
+        legend.spacing.x = unit(0.2, 'cm'),
+        legend.position="right", 
+        legend.direction = "vertical", 
+        legend.box = "vertical",
+        legend.margin=margin(t=30),
+        plot.margin = margin(t = 15, unit = "pt"))
 
@@
   "Industry" = "Emi|GHG|Gross|Energy|Demand|Industry",
-  "Transportation" ="Emi|GHG|Energy|Demand|Transport",
+  "Transport" ="Emi|GHG|Energy|Demand|Transport",
   "Bunkers" = "Emi|CO2|Energy|Demand|Transport|International Bunkers",
@@
   "Industry" = "#5f6769",
-  "Transportation" = "#a1dd70",
+  "Transport" = "#a1dd70",
   "Bunkers" = "#ffc0cb",
@@
   "Industry" = "Emi|GHG|Industry",
-  "Transportation" ="Emi|GHG|Energy|Demand|Transport",
+  "Transport" ="Emi|GHG|Energy|Demand|Transport",
   "Bunkers" = "Emi|GHG|Energy|Demand|Transport|International Bunkers",
@@
   scale_color_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) +
-  theme_doubleColumn() +
-  theme(legend.position = "none") +
   scale_y_continuous(breaks=c(2010,2020,2030,2040), labels=c("1990","avrg. 2018-2022","2030","2040"), minor_breaks = NULL, limits=c(1998,2047)) +
-  theme(axis.title.x=element_blank(),
+  scale_x_continuous(breaks = NULL) +
+  coord_cartesian(clip="off") +
+  #theme(plot.margin = margin(t = 30, r = 0, b = 100, l = 0, unit = "pt")) +
+  labs(title = "(d) Sectoral breakdown of residual net CO2 emissions from energy and industrial processes") + 
+  theme_doubleColumn() +
+  theme(legend.position = "none",
+        axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank(),
-        axis.title.y=element_blank()) +
-  scale_x_continuous(breaks = NULL) +
-  coord_cartesian(clip="off") +
-  theme(plot.margin = margin(t = 15, r = 0, b = 100, l = 0, unit = "pt")) +
-  #theme(plot.margin = margin(t = 30, r = 0, b = 100, l = 0, unit = "pt")) +
-  labs(title = "(d) Sectoral breakdown of residual net CO2 emissions from energy and industrial processes") + 
-  theme(plot.title = element_text(margin=margin(t=0,r=0,b=55,l=0), hjust=1))
+        axis.title.y=element_blank(),
+        plot.margin = margin(t = 15, r = 0, b = 100, l = 0, unit = "pt"),
+        plot.title = element_text(margin=margin(t=0,r=0,b=55,l=0), hjust=1))
 
@@
 
-#label <- c(
-
-#)
-
 #plotData2040 <- plotDataBars %>%
@@
   geom_text(data=plotDataBars %>% filter(percentage >= 0.02),aes(label = label, y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geomText.size*0.8) +
-  #geom_text(data=plotData2030[plotData2030$percentage >= 0.02,],aes(label = label, y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geomText.size*0.8) +
-  #geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geomText.size) +
-  theme_doubleColumn()  +
   scale_y_continuous(minor_breaks = seq(0.2, 0.8, 0.2), breaks=c(0,1),labels = scales::percent) +
@@
   annotation_custom(grob = linesGrob(gp=gpar(col="#666666",lwd = 3,lty="dashed")), xmin = 2011, xmax = 2014.8, ymin = plotDataRenewables[plotDataRenewables$period == 2015,]$percentage, ymax = plotDataRenewables[plotDataRenewables$period == 2015,]$percentage) +
-  #annotate(geom = "text", label = "100%", x = 2020, y = 1, hjust=1.2, color = "#666666", size=geomText.size) +
-  #annotate(geom = "text", label = "0%", x = 2020, y = 0, hjust=1.2, color = "#666666", size=geomText.size) +
   coord_cartesian(clip = 'off') +
-  #theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 20, unit = "pt")) +
-  labs(title = "(a) Electricity Generation (%)") #+ 
-  #theme(plot.title = element_text(hjust = -0.1))
-
-# ggsave(paste0(outChartsFolder,"/svg/Figure 2. Electricity panel - (a) generation.svg"), g[["Electricity Generation"]] , device="svg", width = 6, height = 10, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Figure 2. Electricity panel - (a) generation.png"), g[["Electricity Generation"]] , device="png", width = 6, height = 10, dpi=300, units = "in")
-
-# g[["Electricity Generation - wide"]] <- 
-#   ggplot(plotData,aes(x=period,y=percentage)) +
-#   geom_area(aes(fill=variable),alpha=0.4) +
-#   geom_line(data=plotDataRenewables, linetype = "dashed", linewidth = 1.5, color="#666666") +
-#   geom_bar(data=plotData2040,aes(fill=variable),stat='identity', show.legend = FALSE, alpha = 0.7, color="white", width = 3, linewidth = 1.5) +
-#   geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geomText.size) +
-#   theme_doubleColumn()  +
-#   scale_y_continuous(minor_breaks = seq(0.2, 0.8, 0.2), breaks=c(0,1),labels = scales::percent) +
-#   scale_x_continuous(breaks=c(2020,2040,2050)) +
-#   scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
-#   theme(legend.position="right") +
-#   theme(legend.margin=margin(b = -2, unit='cm'))
-
-#ggsave(paste0(outFolder_conference,"/Electricity Generation - wide.svg"), g[["Electricity Generation - wide"]] , device="svg", width = 12, height = 5, dpi=100, units = "in")
-#ggsave(paste0(outFolder_conference,"/Electricity Generation - wide.png"), g[["Electricity Generation - wide"]] , device="png", width = 12, height = 5, dpi=300, units = "in")
+  labs(title = "(a) Electricity Generation (%)") +
+  theme_doubleColumn()
 
@@
                   hjust = 1, direction="y",
-                  size = geomText.size) +
+                  size = geomText.size * 0.8) +
   geom_label_repel(data=plotData %>% filter(scenario == mainScen, period == 2040), aes(label = paste0(round(value),"GW")),box.padding = 0.1,
@@
                   size = geomText.size * 0.8) +
-    theme_doubleColumn() + 
     coord_cartesian(clip = 'off') +
     expand_limits(y = 3000) +
-    labs(title = "(b) Solar Photovoltaics capacity (GW)") #+ 
-    #theme(plot.title = element_text(hjust = -0.4))
-
-# ggsave(paste0(outChartsFolder,"/svg/Figure 2. Electricity panel - (b) solar.svg"), g[["Solar_Photovoltaics_capacity"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Figure 2. Electricity panel - (b) solar.png"), g[["Solar_Photovoltaics_capacity"]] , device="png", width = 6, height = 4, dpi=300, units = "in")
+    labs(title = "(b) Solar Photovoltaics capacity (GW)") + 
+    theme_doubleColumn()
 
@@
     scale_fill_manual(values = c("Final Energy|w/o Bunkers|w/o Non-energy Use|Electricity Share"="black","Final Energy|w/o Bunkers|w/o Non-energy Use|Transport|Electricity Share"="#a1dd70","Final Energy|w/o Bunkers|w/o Non-energy Use|Industry|Electricity Share"="#5f6769","Final Energy|w/o Bunkers|w/o Non-energy Use|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
-    theme_doubleColumn() + 
     scale_y_continuous(breaks = seq(0, 1, 0.2),labels = scales::percent) +
@@
     guides(color=guide_legend(nrow=2)) +
-    labs(title = "(c) Electricity share in final energy (%)\nwithout bunker fuels and non-energy use") #+ 
-    #theme(plot.title = element_text(hjust = -0.4))
-
-# ggsave(paste0(outChartsFolder,"/svg/Figure 2. Electricity panel - (c) electrification.svg"), g[["Electricity_Share"]] , device="svg", width = 6, height = 6, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Figure 2. Electricity panel - (c) electrification.png"), g[["Electricity_Share"]] , device="png", width = 6, height = 6, dpi=300, units = "in")
+    labs(title = "(c) Electricity share in final energy (%)\nwithout bunker fuels and non-energy use") +
+    theme_doubleColumn()
 
@@
     scale_fill_manual(values = c(setNames(options$aesthetics$legend$color[names(vars)],vars)), labels = setNames(names(vars), vars)) +
-    theme_doubleColumn() + 
     expand_limits(y=c(0,1)) +
@@
     expand_limits(y = 30) +
-    theme(legend.margin=margin(l = -2, unit='cm')) +
-    labs(title = paste0("(a) Primary energy demand (", unique(plotData$unit), ")")) #+
-    #theme(plot.margin=margin(b = 1, unit='cm'))
-    #theme(plot.title = element_text(hjust = -0.3))
-    #guides(fill = FALSE)
-
-# ggsave(paste0(outChartsFolder,"/svg/Figure 3. Energy supply panel - (a) primary energy.svg"), g[["Primary Energy"]] , device="svg", width = 6, height = 5, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Figure 3. Energy supply panel - (a) primary energy.png"), g[["Primary Energy"]] , device="png", width = 6, height = 5, dpi=300, units = "in")
+    labs(title = paste0("(a) Primary energy demand (", unique(plotData$unit), ")")) +
+    theme_doubleColumn() +
+    theme(legend.margin=margin(l = -2, unit='cm'))
 
@@
   geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = variable, alpha=factor(period))) +
-  #geom_errorbar(data=plotData %>% filter(period != 2020), aes(ymin=ribbon.min, ymax=ribbon.max, group=variable), width=8, colour="black", alpha=0.9, size=1,position = position_dodge(width=2)) +
   geom_errorbar(data=plotData %>% filter(period != 2020, variable == vars[1], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, linewidth=1,position = position_dodge(width=2)) +
-  # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
   coord_flip() +
-  theme_doubleColumn() +
-  theme(panel.grid.minor.x = element_blank(),
-        panel.grid.major.y = element_blank()) +
-  #guides(y = "none") +
-  theme(axis.title.y=element_blank()) +
-  #theme(legend.position = "none") #+
   scale_fill_manual(values = setNames(options$aesthetics$legend$color[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(reverse = TRUE, nrow = 1)) +
   scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
-  #theme(legend.text=element_text(size=theme.double.text.size)) +
-  #scale_y_continuous(breaks = seq(0,round(ceiling(max(plotData$ribbon.max.total)),0),2)) +
   scale_y_continuous(  labels = scales::number_format(accuracy = 1)) +
   expand_limits(y=c(0,round(ceiling(max(plotData$ribbon.max.total)),0))) + 
-  #scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == 2020) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2030) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value)),1))) +
-  #scale_x_reverse()
-  theme(legend.margin=margin(l = -2, unit='cm')) +
-  labs(title = paste0("(c) Gaseous final energy demand (", unique(plotData$unit), ")")) #+ 
-  #theme(plot.title = element_text(hjust = -0.5))
-
-# ggsave(paste0(outChartsFolder,"/svg/Figure 3. Energy supply panel - (c) final energy gases.svg"), g[["FE Gases"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Figure 3. Energy supply panel - (c) final energy gases.png"), g[["FE Gases"]] , device="png", width = 6, height = 4, dpi=300, units = "in")
+  labs(title = paste0("(c) Gaseous final energy demand (", unique(plotData$unit), ")")) +
+  theme_doubleColumn() +
+  theme(panel.grid.minor.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        axis.title.y=element_blank(),
+        legend.margin=margin(l = -2, unit='cm'))
 
@@
   filter(region == "EU27", period %in% c(2020,2030,2040,2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars), tgt2050 != "Npi") %>% 
-  #mutate(variable = factor(variable, levels=vars))  %>%
   mutate(type = ifelse(grepl("Imports",variable),"Imports","Exports"),
@@
   geom_errorbar(data=plotData %>% filter(period == 2040, scenario == mainScen), aes(ymin=ribbon.min, ymax=ribbon.max), width=4, colour="black", alpha=0.9, linewidth=1,position = position_dodge(width=2)) +
-  # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
-  #coord_flip() +
   facet_wrap(~carrier,nrow=1) +
-  theme_doubleColumn() +
-  theme(panel.grid.minor.x = element_blank(),
-        panel.grid.major.y = element_blank()) +
   scale_fill_manual(values = c("2020" = "black", "2030"= "black", "2040" = "#5a788b", "2050" = "black")) +
   scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
-  theme(legend.position = "none") +
   labs(title = paste0("(b) Fossil energy carriers’ net imports (", unique(plotData$unit), ")")) +
-  theme(plot.title = element_text(hjust = 1)) #+
-  #theme(plot.margin=margin(b = 1, unit='cm'))
-  #theme(plot.title = element_text(hjust = -0.4))
-
-# ggsave(paste0(outChartsFolder,"/svg/Figure 3.
-Energy supply panel - (b) fossil security of supply.svg"), g[["security of supply - net fossil with range"]] , device="svg", width = 6, height = 4.5, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Figure 3.
-Energy supply panel - (b) fossil security of supply.png"), g[["security of supply - net fossil with range"]] , device="png", width = 6, height = 4.5, dpi=300, units = "in")
+  theme_doubleColumn() +
+  theme(panel.grid.minor.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        legend.position = "none",
+        plot.title = element_text(hjust = 1))
 
@@
   "H2 imports" = "SE|Hydrogen|Net Imports",
-#  "Bio-based H2 (gasification)" = c("SE|Hydrogen|Biomass|w/ CC","SE|Hydrogen|Biomass|w/o CC"),
-#  "Green H2 (electrolysis)" = "SE|Hydrogen|Electricity",
   "Green and bio-based H2" = c("SE|Hydrogen|Electricity", "SE|Hydrogen|Biomass|w/ CC","SE|Hydrogen|Biomass|w/o CC")
-  #"VRE Storage Electrolysis" = "SE|Hydrogen|Electricity|VRE Storage Electrolysis",
-  #"Standard Electrolysis" = "SE|Hydrogen|Electricity|Standard Electrolysis",
   )
@@
   "H2 imports" = "#c18f4a",
-  "Bio-based H2 (gasification)" = "#2eab83",
-  "Green H2 (electrolysis)" = "#a1c44e",
   "Green and bio-based H2" = "#2eab83"
   )
-#color <- setNames(options$aesthetics$legend$color[names(vars)],vars)
-#color["SE|Hydrogen|Biomass|w/ CC"] <- color["SE|Hydrogen|Biomass|w/o CC"]
 
@@
   mutate(type=factor(type, levels=unique(gsub("\\d$", "", names(vars))))) %>%
-  #mutate(value = value*8) %>% #1EJ <- 8 million tons adrian
   group_by(model,scenario,region,period) %>% 
@@
   geom_segment(aes(x = 2015, xend = 2035, y = target %>% filter(type == "domestic", period == 2030) %>% pull(value), yend = target %>% filter(type == "domestic", period == 2030) %>% pull(value)), color = "#888888", linewidth=1, linetype = "dashed") +
-  #geom_hline(yintercept= target %>% filter(type == "domestic", period == 2030) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
   annotate("text", x = 2015, y = target %>% filter(type == "domestic", period == 2030) %>% pull(value), label = "REPowerEU\ndomestic", angle=90, vjust = 0.4, hjust = 0, color = "black", alpha = 0.5, size = geomText.size * 0.8) +
   geom_segment(aes(x = 2015, xend = 2035, y = target %>% filter(type == "total", period == 2030) %>% pull(value), yend = target %>% filter(type == "total", period == 2030) %>% pull(value)), color = "#888888", linewidth=1, linetype = "dashed") +
-  #geom_hline(yintercept= target %>% filter(type == "total", period == 2030) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
   annotate("text", x = 2015, y = target %>% filter(type == "total", period == 2030) %>% pull(value), label = "REPowerEU\ntotal", angle=90, vjust = 0.4, hjust = 0, color = "black", alpha = 0.5, size = geomText.size * 0.8) +
@@
   coord_flip() +
+  scale_fill_manual(values = color, guide = guide_legend(nrow = 3, reverse = TRUE)) +
+  scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
+  scale_y_continuous(  labels = scales::number_format(accuracy = 1)) +
+  labs(title = paste0("(d) Hydrogen production (", unique(plotData$unit), ")")) +
   theme_doubleColumn() +
   theme(panel.grid.minor.x = element_blank(),
-        panel.grid.major.y = element_blank()) +
-  scale_fill_manual(values = color,
-                    #labels = setNames(names(vars), vars)[c("SE|Hydrogen|Electricity", "SE|Hydrogen|Gas|w/o CC", "SE|Hydrogen|Biomass|w/ CC")],
-                    #breaks = c("SE|Hydrogen|Electricity", "SE|Hydrogen|Gas|w/o CC", "SE|Hydrogen|Biomass|w/ CC"), 
-                    guide = guide_legend(nrow = 3, reverse = TRUE)) +
-  scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
-  #theme(legend.text=element_text(size=theme.double.text.size)) +
-  #scale_y_continuous(breaks = seq(0,6,1)) +
-  #scale_y_continuous(breaks = seq(0,round(ceiling(max(plotData$ribbon.max.total)),0),1)) +
-  scale_y_continuous(  labels = scales::number_format(accuracy = 1)) +
-  theme(legend.margin=margin(l = -2, unit='cm')) +
-  labs(title = paste0("(d) Hydrogen production (", unique(plotData$unit), ")")) #+ 
-  #theme(plot.title = element_text(hjust = -0.4))
-
-# ggsave(paste0(outChartsFolder,"/svg/Figure 3. Energy supply panel - (d) hydrogen.svg"), g[["Hydrogen"]] , device="svg", width = 6, height = 4, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Figure 3. Energy supply panel - (d) hydrogen.png"), g[["Hydrogen"]] , device="png", width = 6, height = 4, dpi=300, units = "in")
+        panel.grid.major.y = element_blank(),
+        legend.margin=margin(l = -2, unit='cm'))
 
@@
 
-if("FE|Transport|Freight|Navigation|Liquids|Fossil" %in% unique(df$variable)){
-  FEvars <- list(
-    "Domestic" = list(
-      "LDV" = c(
-        "FE|Transport|Pass|Road|LDV|Electricity" = "Electricity",
-        "FE|Transport|Pass|Road|LDV|Gases" = "Gases",
-        "FE|Transport|Pass|Road|LDV|Hydrogen" = "Hydrogen",
-  #      "FE|Transport|Pass|Road|LDV|Liquids" = "Liquids"
-         "FE|Transport|Pass|Road|LDV|Liquids|Fossil" = "Liquids - Fossil",
-         "FE|Transport|Pass|Road|LDV|Liquids|Biomass" = "Liquids - Biomass",
-          "FE|Transport|Pass|Road|LDV|Liquids|Hydrogen" = "Liquids - Synthetic"
-      ),
-      "Buses" = c(
-        "FE|Transport|Pass|Road|Bus|Electricity" = "Electricity",
-        "FE|Transport|Pass|Road|Bus|Gases" = "Gases",
-        "FE|Transport|Pass|Road|Bus|Hydrogen" = "Hydrogen",
-  #      "FE|Transport|Pass|Road|Bus|Liquids" = "Liquids"
-          "FE|Transport|Pass|Road|Bus|Liquids|Fossil" = "Liquids - Fossil",
-          "FE|Transport|Pass|Road|Bus|Liquids|Biomass" = "Liquids - Biomass",
-          "FE|Transport|Pass|Road|Bus|Liquids|Hydrogen" = "Liquids - Synthetic"
-
-      ),
-      "Trucks" = c(
-        "FE|Transport|Freight|Road|Electricity" = "Electricity",
-        "FE|Transport|Freight|Road|Gases" = "Gases",
-        "FE|Transport|Freight|Road|Hydrogen" = "Hydrogen",
-  #      "FE|Transport|Freight|Road|Liquids" = "Liquids"
-          "FE|Transport|Freight|Road|Liquids|Fossil" = "Liquids - Fossil",
-          "FE|Transport|Freight|Road|Liquids|Biomass" = "Liquids - Biomass",
-          "FE|Transport|Freight|Road|Liquids|Hydrogen" = "Liquids - Synthetic"
-      ),
-      "Rail" = c(
-        "FE|Transport|Pass|Rail|Electricity" = "Electricity",
-        "FE|Transport|Pass|Rail|Gases" = "Gases",
-        "FE|Transport|Pass|Rail|Hydrogen" = "Hydrogen",
-  #      "FE|Transport|Pass|Rail|Liquids" = "Liquids",
-          "FE|Transport|Pass|Rail|Liquids|Fossil" = "Liquids - Fossil",
-          "FE|Transport|Pass|Rail|Liquids|Biomass" = "Liquids - Biomass",
-          "FE|Transport|Pass|Rail|Liquids|Hydrogen" = "Liquids - Synthetic",
-        "FE|Transport|Freight|Rail|Electricity" = "Electricity",
-        "FE|Transport|Freight|Rail|Gases" = "Gases",
-        "FE|Transport|Freight|Rail|Hydrogen" = "Hydrogen",
-  #      "FE|Transport|Freight|Rail|Liquids" = "Liquids"
-          "FE|Transport|Freight|Rail|Liquids|Fossil" = "Liquids - Fossil",
-          "FE|Transport|Freight|Rail|Liquids|Biomass" = "Liquids - Biomass",
-          "FE|Transport|Freight|Rail|Liquids|Hydrogen" = "Liquids - Synthetic"
-      ),
-      "Aviation" = c(
-        "FE|Transport|Pass|Aviation|Domestic|Electricity" = "Electricity",
-        "FE|Transport|Pass|Aviation|Domestic|Gases" = "Gases",
-        "FE|Transport|Pass|Aviation|Domestic|Hydrogen" = "Hydrogen",
-  #      "FE|Transport|Pass|Aviation|Domestic|Liquids" = "Liquids"
-          "FE|Transport|Pass|Aviation|Domestic|Liquids|Fossil" = "Liquids - Fossil",
-          "FE|Transport|Pass|Aviation|Domestic|Liquids|Biomass" = "Liquids - Biomass",
-          "FE|Transport|Pass|Aviation|Domestic|Liquids|Hydrogen" = "Liquids - Synthetic"
-      )
-    ),
-    "International" = list(
-      "Aviation" = c(
-        "FE|Transport|Pass|Aviation|International|Electricity" = "Electricity",
-        "FE|Transport|Pass|Aviation|International|Gases" = "Gases",
-        "FE|Transport|Pass|Aviation|International|Hydrogen" = "Hydrogen",
-  #      "FE|Transport|Pass|Aviation|International|Liquids" = "Liquids"
-          "FE|Transport|Pass|Aviation|International|Liquids|Fossil" = "Liquids - Fossil",
-          "FE|Transport|Pass|Aviation|International|Liquids|Biomass" = "Liquids - Biomass",
-          "FE|Transport|Pass|Aviation|International|Liquids|Hydrogen" = "Liquids - Synthetic"
-      ),
-      "Shipping" = c(
-        "FE|Transport|Freight|Navigation|Electricity" = "Electricity",
-        "FE|Transport|Freight|Navigation|Gases" = "Gases",
-        "FE|Transport|Freight|Navigation|Hydrogen" = "Hydrogen",
-  #      "FE|Transport|Freight|Navigation|Liquids" = "Liquids",
-          "FE|Transport|Freight|Navigation|Liquids|Fossil" = "Liquids - Fossil",
-          "FE|Transport|Freight|Navigation|Liquids|Biomass" = "Liquids - Biomass",
-          "FE|Transport|Freight|Navigation|Liquids|Hydrogen" = "Liquids - Synthetic",
-        "FE|Transport|Freight|International Shipping|Electricity" = "Electricity",
-        "FE|Transport|Freight|International Shipping|Gases" = "Gases",
-        "FE|Transport|Freight|International Shipping|Hydrogen" = "Hydrogen",
-  #      "FE|Transport|Freight|International Shipping|Liquids" = "Liquids"
-          "FE|Transport|Freight|International Shipping|Liquids|Fossil" = "Liquids - Fossil",
-          "FE|Transport|Freight|International Shipping|Liquids|Biomass" = "Liquids - Biomass",
-          "FE|Transport|Freight|International Shipping|Liquids|Hydrogen" = "Liquids - Synthetic"
-      )
-    )
-  )
-
-} else {
   FEvars <- list(
@@
   )
-}
 
@@
   facet_wrap(~cat,nrow=1) +
-  theme_doubleColumn() +
-  theme(axis.title.y=element_blank()) +
   scale_fill_manual(values = plotColor, guide = guide_legend(nrow = 1)) + #, guide = guide_legend(nrow = 2)
@@
   scale_x_continuous(breaks = c(2020,2030,2040,2050)) + 
-  theme(
+  labs(title = paste0("(a) Transport Final energy (", unique(FEplotData$unit), ")")) +
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank(),
         strip.background = element_blank(),
-    #strip.text.x = element_blank()
-    ) +
-  #theme(legend.text=element_text(size=theme.single.text.size)) +
-  #theme(strip.text.x = element_text(size = 1.2*theme.double.text.size, vjust=0.5)) +
-  theme(strip.clip = "off") +
-  labs(title = paste0("(a) Transport Final energy (", unique(FEplotData$unit), ")"))
-
-# ggsave(paste0(outChartsFolder,"/svg/Figure 4. Demand panel - (a) transport final energy.svg"), g[["transport fe"]] , device="svg", width = 12, height = 5, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Figure 4. Demand panel - (a) transport final energy.png"), g[["transport fe"]] , device="png", width = 12, height = 5, dpi=300, units = "in")
+        strip.clip = "off")
 
@@
   geom_line(data=stockData, aes(color=variable),linetype=11, lwd = 1) +
-# geom_line(data=h,linetype="dashed", linewidth = 1, color="black") +
   geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
   geom_label_repel(data=data.frame(period=2030,value=stockData %>% filter(period == 2030) %>% pull(value)), label = "Stock",
-                  #box.padding = 0.1,
-                  #segment.curvature = -0.1,
-                  #segment.square = TRUE,
-                  #point.padding = 0.6,
                   nudge_x = 5,
                   nudge_y = 0.05,
-                  #nudge_y = -0.02,
-                  #force = 0.5,
                   hjust = 0,
@@
   geom_point_svg(data=logoData, aes(x=period,y=value, svg = logo),vjust=0.5,size=20) +
-  theme_doubleColumn() +
- scale_fill_manual(values = setNames(plotColor[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(nrow = 3, order = 1)) + #, guide = guide_legend(nrow = 2)
+  scale_fill_manual(values = setNames(plotColor[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(nrow = 3, order = 1)) +
   scale_color_manual(values = c("ICE Stock"="black"), guide = guide_legend(order = 2, keywidth = unit(2, 'cm'))) +
@@
   scale_y_continuous(limits = c(0, 1.1), breaks=c(0,1), labels = scales::percent, name = "Sales") +
- #theme(legend.text=element_text(size=theme.double.text.size),
-#        legend.spacing.x = unit(0.4, 'cm'))  +
   guides(color = "none") +
-  #theme(legend.text=element_text(size=theme.double.text.size)) +
   labs(title = "(b) LDV sales shares &  share of ICE in\nLDV stock (%)") +
+  theme_doubleColumn() +
   theme(plot.title = element_text(hjust=1))
-
-# ggsave(paste0(outChartsFolder,"/svg/Figure 4. Demand panel - (b) LDV sales.svg"), g[["LDV Sales"]] , device="svg", width = 6, height = 4.5, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Figure 4. Demand panel - (b) LDV sales.png"), g[["LDV Sales"]] , device="png", width = 6, height = 4.5, dpi=300, units = "in")
 
@@
 
-# historical data #missing non-energy
-#h <- hist[hist$model == "UNFCCC" & hist$region == "EU27" & hist$variable %in% vars,] %>% drop_na(value)
-
-#View(hist[hist$model == "UNFCCC" & hist$region == "EU27" & hist$variable == "Emi|CO2|Industrial Processes",] %>% drop_na(value))
-# Emi|CO2|Energy|Demand|Industry
-# Emi|CO2|Energy|Demand|Industry|Cement
-# Emi|CO2|Energy|Demand|Industry|Chemicals
-# Emi|CO2|Energy|Demand|Industry|Other Industry
-# Emi|CO2|Energy|Demand|Industry|Other Industry|AFOFI
-# Emi|CO2|Energy|Demand|Industry|Steel
-# Emi|CO2|Industrial Processes
-# Emi|CO2|Industrial Processes|Chemicals
-# Emi|CO2|Industrial Processes|Metals
-# Emi|CO2|Industrial Processes|Minerals
-# Emi|GHG|Energy|Demand|Industry
-# Emi|GHG|Industrial Processes
-
 g[["Industry Emissions"]] <- ggplot(plotData,aes(x=period,y=value)) +
@@
     geom_line(data=plotData %>% filter(scenario == mainScen), aes(color=variable), linewidth=1.5) +
-    #geom_line(data=h,linewidth=1,linetype="dashed") +
     geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min, fill=variable), alpha = 0.3) + 
@@
     scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) +
-    theme_doubleColumn() + 
     expand_limits(y=c(0,1)) +
     guides(color=guide_legend(nrow=2)) +
-    #theme(legend.text=element_text(size=theme.double.text.size)) +
-    #theme(legend.text=element_text(size=theme.double.text.size))  +
-    labs(title = "(d) Industrial sectors’ CO2 emissions\n(Mt CO2/yr)")
-    #labs(title = expression(paste("(d) Industrial sectors’ ", CO[2], " emissions\n(Mt ", CO[2], "/yr)")))  +
+    labs(title = "(d) Industrial sectors’ CO2 emissions   \n(Mt CO2/yr)   ") +
+    theme_doubleColumn() + 
     theme(plot.title = element_text(hjust=1))
-    #theme(plot.title = element_text(hjust=-0.3))
-
-# ggsave(paste0(outChartsFolder,"/svg/Figure 4. Demand panel - (d) industrial emissions.svg"), g[["Industry Emissions"]] , device="svg", width = 6, height = 5.5, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Figure 4. Demand panel - (d) industrial emissions.png"), g[["Industry Emissions"]] , device="png", width = 6, height = 5.5, dpi=300, units = "in")
 
@@
   geom_errorbar(data=plotData %>% filter(period != 2020, variable == vars["Electricity (heat pumps)"], scenario == mainScen), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, linewidth=1,position = position_dodge(width=2)) +
-  # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
   coord_flip() +
-  theme_doubleColumn() +
-  theme(panel.grid.minor.x = element_blank(),
-        panel.grid.major.y = element_blank()) +
   scale_fill_manual(values = plotColor, guide = guide_legend(reverse = TRUE, nrow = 3)) +
   scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
-  #theme(legend.text=element_text(size=theme.double.text.size)) +
-  #theme(legend.margin=margin(l = -2.5, t = -0.5, unit='cm')) +
-  labs(title = paste0("(c) Buildings space and water heating\nuseful energy (", unique(plotData$unit), ")")) +
-  theme(plot.title = element_text(hjust=1)) #+
-  #scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == "2020") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2030") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2040") %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == "2050") %>% pull(value)),1))) #+
-  #scale_x_reverse()
-
-# ggsave(paste0(outChartsFolder,"/svg/Figure 4.
-Demand panel - (c) buildings heating useful energy.svg"), g[["Buildings heating useful energy"]] , device="svg", width = 6, height = 4.3, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Figure 4.
-Demand panel - (c) buildings heating useful energy.png"), g[["Buildings heating useful energy"]] , device="png", width =6, height = 4.3, dpi=300, units = "in")
+  labs(title = paste0("(c) Buildings space and water heating  \nuseful energy (", unique(plotData$unit), ")  ")) +
+  theme_doubleColumn() +
+  theme(panel.grid.minor.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        plot.title = element_text(hjust=1))
 
@@
   "industry & waste" = "Carbon Management|Carbon Capture|Industry and Waste"
-  #"industry" = "Carbon Management|Carbon Capture|Industry",
-  #"waste" = "Carbon Management|Carbon Capture|Waste|Plastics Incineration"
-  #"Storage type"
-  # "atmospheric/biogenic" = "Carbon Management|atmospheric/biogenic CO2 - CDR",
-  # "fossil" = "Carbon Management|CCS of fossil origin",
-  #
-  # "DAC" = "Carbon Management|Storage|DAC",
-  # "BECCS" = "Carbon Management|Storage|Biomass|Pe2Se", 
-  # "Fossil CCS" = "Carbon Management|Storage|Fossil|Pe2Se", 
-  # "Industry CCS" = "Carbon Management|Storage|Industry CCS"
-    # "Industry Energy" = "Carbon Management|Storage|Industry Energy",
-    # "Industry Process" = "Carbon Management|Storage|Industry Process"
 )
@@
   "BECC" = "#8bc18b",
-  #"Industry CCS" = "#5f6769",
-  #"Fossil CCS" = "#47331f",
   "fossil (energy)" = "#6b5b4b",
-  "industry & waste" = "#5f6769"#,
-  #"industry" = "#5f6769",
-  #"waste" = "#543a0f"
-  #"fossil" = "#47331f"
+  "industry & waste" = "#5f6769"
 )
@@
                   ifelse(as.character(variable) %in% c("Carbon Management|Storage","Carbon Management|Usage|Synthetic Gases","Carbon Management|Usage|Synthetic Liquids"), "Usage",
-    ifelse(as.character(variable) %in% c("Carbon Management|Carbon Capture|DAC", "Carbon Management|Carbon Capture|Biomass|Pe2Se", "Carbon Management|Carbon Capture|Fossil|Pe2Se","Carbon Management|Carbon Capture|Industry and Waste"
-                                         #"Carbon Management|Carbon Capture|Industry", "Carbon Management|Carbon Capture|Waste|Plastics Incineration"
-                                         ), "Capture","CCS")))),
-    variable = factor(variable, levels=c( "Carbon Management|Usage|Synthetic Liquids", "Carbon Management|Usage|Synthetic Gases", "Carbon Management|Storage", "destination", "empty1", "empty2", "Carbon Management|Carbon Capture|atmospheric/biogenic CO2", "Carbon Management|Carbon Capture|fossil origin", "origin",
-          #"empty1", "empty2", "Carbon Management|atmospheric/biogenic CO2 - CDR", "Carbon Management|CCS of fossil origin", "origin",
-          #"Carbon Management|Storage|DAC", "Carbon Management|Storage|Biomass|Pe2Se", "Carbon Management|Storage|Fossil|Pe2Se", "Carbon Management|Storage|Industry CCS", "origin")
-          "Carbon Management|Carbon Capture|DAC", "Carbon Management|Carbon Capture|Biomass|Pe2Se", "Carbon Management|Carbon Capture|Fossil|Pe2Se", "Carbon Management|Carbon Capture|Industry and Waste"
-          #"Carbon Management|Carbon Capture|Industry", "Carbon Management|Carbon Capture|Waste|Plastics Incineration"
-          , "activity")),
+                         ifelse(as.character(variable) %in% c("Carbon Management|Carbon Capture|DAC", "Carbon Management|Carbon Capture|Biomass|Pe2Se", "Carbon Management|Carbon Capture|Fossil|Pe2Se","Carbon Management|Carbon Capture|Industry and Waste"), "Capture","CCS")))),
+    variable = factor(variable, levels=c("Carbon Management|Usage|Synthetic Liquids", "Carbon Management|Usage|Synthetic Gases", "Carbon Management|Storage", "destination", "empty1", "empty2", "Carbon Management|Carbon Capture|atmospheric/biogenic CO2", "Carbon Management|Carbon Capture|fossil origin", "origin","Carbon Management|Carbon Capture|DAC", "Carbon Management|Carbon Capture|Biomass|Pe2Se", "Carbon Management|Carbon Capture|Fossil|Pe2Se", "Carbon Management|Carbon Capture|Industry and Waste", "activity")),
          value = ifelse(grepl("Emi",variable,fixed = TRUE), -value, value))  %>% 
@@
  g[["Carbon Management"]] <- ggplot(plotData,aes(x=CDRGroup,y=value)) +
-  #geom_area(aes(fill=variable)) +
   geom_bar(data=plotData %>% filter(scenario == mainScen), aes(fill=variable, alpha=factor(period)),stat='identity') + 
@@
   coord_flip() +
-  theme_doubleColumn() +
   scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars), "empty1" = "transparent", "empty2" = "transparent", "destination" = "transparent", "origin" = "transparent", "activity" = "transparent"),
@@
   scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
-  theme(legend.title = element_blank()) +
-  theme(legend.margin=margin(l = -1, unit='cm')) + 
-  theme(strip.text.y.left = element_text(angle = 0)) +
-  # theme(
-  #   strip.background = element_blank(),
-  #   strip.text.x = element_blank()
-  # ) +
-  theme(axis.text.y=element_blank(), #remove x axis labels
+  labs(title = "(e) Carbon Capture and Storage        \n(Mt CO2/yr)        ") +
+  theme_doubleColumn() +
+  theme(legend.title = element_blank(),
+        strip.text.y.left = element_text(angle = 0),
+        axis.text.y=element_blank(), #remove x axis labels
         axis.ticks.y=element_blank(), #remove x axis ticks
-        ) +
-  labs(title = "(e) Carbon Capture and Storage\n(Mt CO2/yr)") +
-  theme(legend.spacing.x = unit(0.3, 'cm'),
-        legend.margin=margin(l=-50))
-
-  #labs(title = expression(paste("(e) Carbon Capture and Storage\n(Mt ", CO[2], "/yr)")))  #+
-  #theme(plot.title = element_text(hjust=0))
-
- # ggsave(paste0(outChartsFolder,"/svg/Figure 4. Demand panel - (e) carbon management.svg"), g[["Carbon Management"]] , device="svg", width = 6, height = 5.5, dpi=100, units = "in")
- # ggsave(paste0(outChartsFolder,"/png/Figure 4. Demand panel - (e) carbon management.png"), g[["Carbon Management"]] , device="png", width = 6, height = 5.5, dpi=300, units = "in")
+        legend.spacing.x = unit(0.3, 'cm'),
+        legend.margin=margin(l=-50),
+        plot.title = element_text(hjust=1))
 
@@
 
-# “existent targets”
-# emission reduction - 2030 (FitFor55) - 2030 scenarios - 2040 scenarios
-# energy savings  - 2030 (FitFor55 and REPowerEU) - 2030 scenarios - 2040 scenarios
-# renewables target - 2030 (RED II, RED II revised, REPowerEU) - 2030 scenarios - 2040 scenarios
-# solar photovoltaics capacity - 2030 (REPowerEU) - 2030 scenarios - 2040 scenarios
-# CCS capacity target - 2030 EU-wide 50 MtCO2/y “Net-Zero Industry Act"
-# “implicit targets”
-# electrification? -> fe electrification share -> 45%
-# “carbon-content in electricity” ->“carbon-free electricity” (>95%) 
-# Total Residual Fossil emissions
-# sectoral emissions -> Transport emissions -> 23% of 2020 
-#                                   -> Industry and buildings emissions -> 27% of 2020
-# “residual fossil”     -> Complete coal-phase by 2040
-#                                  -> natural gas
-#                                 -> oil
-# “net trade” -> net-supply independency of gas by 2040
-#                       -> one third of oil imports by 2040
+g[["milestone"]] <- NULL
 
@@
 #Emissions Reduction
-# plotData <- rbind(
-#     df %>% 
-#       filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
-#       calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
-#       mutate(value = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)) ,2)) %>% 
-#       select(-variable)
-#     ,
-#     df %>% 
-#       filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>%
-#       calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%
-#       mutate(value = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)) ,2)) %>% 
-#       select(-variable)
-#   ) %>%
-#   filter(tgt2050 != "Npi") %>%
-#   mutate(target = "Emissions\nreductions") %>%
-#   group_by(period) %>% 
-#   mutate(min = min(value),
-#         max = max(value))
 
@@
 
-#target <- data.frame(period = 2030, value = 0.57, label = "FitFor55")
-
-g[["Emissions reductions"]] <- NULL
-# 
-# g[["Emissions reductions"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=0.6) +
-#          #stat_summary(geom = "text", fun = quantile,
-#         #              aes(label = paste0(round(..y..*100),"%")),
-#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-#          #      hjust=-1, angle = 90) +
-#   geom_hline(data=target, aes(yintercept = value), color = "black", linewidth=1, alpha = 0.5, linetype = "dotted") +
-#   geom_text(data = target, aes(x=value, label = label), angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5 ) +
-#   #geom_hline(yintercept=0.57, color = "black", linewidth=1, alpha = 0.5, linetype = "dotted") +
-#   #annotate("text", x = "Emissions\nreductions", y = 0.57, label = "FitFor55", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
-#   geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = "Emissions\nreductions", y = reduction_h, label = "2022", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
-#   facet_grid(target~period, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-#   expand_limits(y=c(0,1)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-#   geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geomText.size, hjust=1.4, na.rm = TRUE)
-# 
-# g[["milestone - vert"]][["Emissions reductions"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(data=target, aes(yintercept = value), color = "black", linewidth=1, alpha = 0.5, linetype = "dotted") +
-#   geom_text(data = target, aes(x = Inf, y = value, label = label), vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   #geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   #annotate("text", x = Inf, y = 0.55, label = "FitFor55", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = reduction_h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-#   expand_limits(y=c(0,1)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   theme(strip.text = element_text(angle = 90)) +
-#   coord_cartesian(clip = 'off') #+
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-# 
-# g[["milestone - hor"]][["Emissions reductions"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = 0.55, label = "FitFor55", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = reduction_h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
-#   expand_limits(y=c(0,1)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
-#   #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=0.8*geomText.size)
-
 target <- data.frame(period = 2030, x = 2025, xend= 2035, value = 0.55, label = "FitFor55")
 
-g[["milestone - violin"]][["Emissions reductions"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
+g[["milestone"]][["Emissions reductions"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
   geom_violin(fill="#bbbbbb", scale = violin_scale) + #, trim=FALSE
-  #geom_errorbar(aes(ymin=min, ymax=max), width=1, colour="black", alpha=0.9, linewidth=0.5) +
   geom_boxplot(outlier.shape = NA, width=1.5) +
   geom_segment(data = target, aes(x=x, xend=xend, y=value, yend=value), color = "black", linewidth=1, alpha = 0.5, linetype = "dotted") +
-  #geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
   annotate("text", x = -Inf, y = 0.55, label = "FitFor55", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
@@
   facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
   coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
@@
   expand_limits(y=c(0,1)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
-  #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=0.8*geomText.size)
-
-# Final Energy Demand - Energy savings
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank(),
+        strip.text.y = element_blank(),
+        panel.spacing = unit(4, "lines"),
+        axis.text.x = element_text(angle = 0, hjust = 0.5),
+        strip.placement = "outside",
+        strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20)))
+
+# Final Energy Demand
+
 plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "FE|w/o Non-energy Use w/o Bunkers") %>% select(-variable) %>%
@@
 
-g[["Energy savings"]] <- NULL
-
-# g[["Energy savings"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-#   geom_boxplot(outlier.shape = NA, width=0.6) +
-#          #stat_summary(geom = "text", fun = quantile,
-#         #              aes(label = paste0(round(..y..*100),"%")),
-#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-#          #      hjust=-1, angle = 90) +
-#   geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = "Final Energy\nDemand", y = 787, label = "FitFor55", angle=90, vjust = 1.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = "Final Energy\nDemand", y = 750, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0.7, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   geom_hline(yintercept=h %>% filter(period==2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = "Final Energy\nDemand", y = h %>% filter(period==2022) %>% pull(value), label = "2022", angle=90, vjust = -0.5, hjust = 0.7, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(target~period, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   theme(strip.text.x = element_blank()) +
-#   expand_limits(y=c(400,1000)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-#   geom_text(data=data.frame(period=c(2030,2040),label=c("(Mtoe/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.2, na.rm = TRUE)
-# 
-# 
-# g[["milestone - vert"]][["Energy savings"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = 750, label = "REPowerEU", vjust = 1.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   annotate("text", x = Inf, y = 787, label = "FitFor55", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   geom_hline(yintercept=h %>% filter(period==2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = h %>% filter(period==2022) %>% pull(value), label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-#   expand_limits(y=c(0,400,1000)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   theme(strip.text = element_text(angle = 90)) +
-#   coord_cartesian(clip = 'off') +
-#   annotate("text", x = -Inf, y = Inf, label = "(Mtoe/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-# 
-# g[["milestone - hor"]][["Energy savings"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mtoe/yr)")), aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = 750, label = "REPowerEU", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   annotate("text", x = Inf, y = 787, label = "FitFor55", angle=90, vjust = 1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   geom_hline(yintercept=h %>% filter(period==2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = h %>% filter(period==2022) %>% pull(value), label = "2022", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
-#   expand_limits(y=c(0,400,1000)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
-#   #annotate("text", x = -Inf, y = -Inf, label = "(Mtoe/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
-
 plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mtoe/yr)"))
@@
 
-g[["milestone - violin"]][["Energy savings"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+g[["milestone"]][["Final Energy Demand"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
   geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
-  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
   geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
   geom_segment(data = target, aes(x=x, xend=xend, y=value, yend=value), color = "black", linewidth=1, alpha = 0.5, linetype = "dotted") +
-  #geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  #geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
   annotate("text", x = Inf, y = 750, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
@@
   facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
   coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
   expand_limits(y=c(0,400,1000)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
-  #annotate("text", x = -Inf, y = -Inf, label = "(Mtoe/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank(),
+        strip.text.y = element_blank(),
+        panel.spacing = unit(4, "lines"),
+        axis.text.x = element_text(angle = 0, hjust = 0.5),
+        strip.placement = "outside",
+        strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20)))
 
 # Electricity Demand
+
 plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "FE|Electricity") %>% select(-variable) %>%
@@
 
-g[["Electricity Demand"]] <- NULL
-
-# g[["Electricity Demand"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-#   geom_boxplot(outlier.shape = NA, width=0.6) +
-#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = "Electricity\nDemand", y = h, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(target~period, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   theme(strip.text.x = element_blank()) +
-#   expand_limits(y=c(0,5000)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-#   geom_text(data=data.frame(period=c(2030,2040),label=c("(TWh)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.2, na.rm = TRUE)
-# 
-# g[["milestone - vert"]][["Electricity Demand"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-#   expand_limits(y=c(0,5000)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   theme(strip.text = element_text(angle = 90)) +
-#   coord_cartesian(clip = 'off') +
-#   annotate("text", x = -Inf, y = Inf, label = "(TWh)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-# 
-# g[["milestone - hor"]][["Electricity Demand"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (TWh)")), aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
-#   expand_limits(y=c(0,5000)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
-#   #annotate("text", x = -Inf, y = -Inf, label = "(TWh)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
-
 plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (TWh)"))
@@
 
-g[["milestone - violin"]][["Electricity Demand"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+g[["milestone"]][["Electricity Demand"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
   geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
-  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
   geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
@@
   facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
   coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
   expand_limits(y=c(0,5000)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
-  #annotate("text", x = -Inf, y = -Inf, label = "(TWh)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank(),
+        strip.text.y = element_blank(),
+        panel.spacing = unit(4, "lines"),
+        axis.text.x = element_text(angle = 0, hjust = 0.5),
+        strip.placement = "outside",
+        strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20)))
 
 # Renewables share
+
 plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "SE|Renewables Share") %>% select(-variable) %>%
@@
 
-g[["Renewables Share"]] <- NULL
-
-# g[["Renewables Share"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-#   geom_boxplot(outlier.shape = NA, width=0.6) +
-#          #stat_summary(geom = "text", fun = quantile,
-#         #              aes(label = paste0(round(..y..*100),"%")),
-#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-#          #      hjust=-1, angle = 90) +
-#   geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = "Renewables\nShare in\nFinal Energy", y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0.5, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = "Renewables\nShare in\nFinal Energy", y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0.6, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = "Renewables\nShare in\nFinal Energy", y = addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), label = "2022", angle=90, vjust = -0.5, hjust = 0.6, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(target~period, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   theme(strip.text.x = element_blank()) +
-#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-#   expand_limits(y=c(0,1)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-#   geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.4, na.rm = TRUE)
-# 
-# g[["milestone - vert"]][["Renewables Share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = 0.4, label = "RED II revised", vjust = 1.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = 0.45, label = "REPowerEU", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-#   expand_limits(y=c(0,1)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   theme(strip.text = element_text(angle = 90)) +
-#   coord_cartesian(clip = 'off') #+
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-# 
-# g[["milestone - hor"]][["Renewables Share"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
-#   expand_limits(y=c(0,1)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
-#   #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
-
 target <- data.frame(period = 2030, x = c(2025,2025), xend= c(2035,2035), value = c(0.4,0.45), label = c("RED II revised","REPowerEU"))
@@
 
-g[["milestone - violin"]][["Renewables Share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+g[["milestone"]][["Renewables Share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
   geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
-  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
   geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
   geom_segment(data = target, aes(x=x, xend=xend, y=value, yend=value), color = "black", linewidth=1, alpha = 0.5, linetype = "dotted") +
-  #geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
   annotate("text", x = Inf, y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0.075, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-  #geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
   annotate("text", x = Inf, y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
@@
   expand_limits(y=c(0,1)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
-  #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank(),
+        strip.text.y = element_blank(),
+        panel.spacing = unit(4, "lines"),
+        axis.text.x = element_text(angle = 0, hjust = 0.5),
+        strip.placement = "outside",
+        strip.text.x = element_text(size = textSize.double, hjust = 1, margin=margin(l=0, b=20)),
+        strip.clip = "off")
 
 # Wind
+
 plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Cap|Electricity|Wind") %>% select(-variable) %>%
@@
 
-g[["Wind capacity"]] <- NULL
-
-#target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2025,2030),value=c(320,600)) 
-# g[["Wind capacity"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-#   geom_boxplot(outlier.shape = NA, width=0.6) +
-#   geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = "Wind\ncapacity", y = 255, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(target~period, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   theme(strip.text.x = element_blank()) +
-#   expand_limits(y=c(0,1000)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-#   geom_text(data=data.frame(period=c(2030,2040),label=c("(GW)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.3, na.rm = TRUE)
-# 
-# g[["milestone - vert"]][["Wind capacity"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = 255, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-#   expand_limits(y=c(0,1000)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   theme(strip.text = element_text(angle = 90)) +
-#   coord_cartesian(clip = 'off') +
-#   annotate("text", x = -Inf, y = Inf, label = "(GW)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-# 
-# g[["milestone - hor"]][["Wind capacity"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (GW)")), aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = 255, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
-#   expand_limits(y=c(0,1000)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
-#   #annotate("text", x = -Inf, y = -Inf, label = "(GW)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
-
 plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (GW)"))
@@
 
-g[["milestone - violin"]][["Wind capacity"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+g[["milestone"]][["Wind capacity"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
   geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
-  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
   geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
@@
   facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
   coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
   expand_limits(y=c(0,1000)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
-  #annotate("text", x = -Inf, y = -Inf, label = "(GW)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank(),
+        strip.text.y = element_blank(),
+        panel.spacing = unit(4, "lines"),
+        axis.text.x = element_text(angle = 0, hjust = 0.5),
+        strip.placement = "outside",
+        strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20)))
 
 # Solar photovoltaics
+
 plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Cap|Electricity|Solar|PV") %>% select(-variable) %>%
@@
 
-g[["Solar photovoltaics"]] <- NULL
-
-# #target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2025,2030),value=c(320,600)) 
-# g[["Solar photovoltaics"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-#   geom_boxplot(outlier.shape = NA, width=0.6) +
-#          #stat_summary(geom = "text", fun = quantile,
-#         #              aes(label = paste0(round(..y..*100),"%")),
-#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-#          #      hjust=-1, angle = 90) +
-#   geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = "Solar\nphotovoltaics", y = 600, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0.6, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = "Solar\nphotovoltaics", y = 208.9, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(target~period, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   theme(strip.text.x = element_blank()) +
-#   expand_limits(y=c(0,2500)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-#   geom_text(data=data.frame(period=c(2030,2040),label=c("(GW)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.3, na.rm = TRUE)
-# 
-# g[["milestone - vert"]][["Solar photovoltaics"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = 600, label = "REPowerEU", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = 208.9, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-#   expand_limits(y=c(0,2500)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   theme(strip.text = element_text(angle = 90)) +
-#   coord_cartesian(clip = 'off') +
-#   annotate("text", x = -Inf, y = Inf, label = "(GW)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-# 
-# g[["milestone - hor"]][["Solar photovoltaics"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (GW)")), aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = 600, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = 208.9, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
-#   expand_limits(y=c(0,2500)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
-#   #annotate("text", x = -Inf, y = -Inf, label = "(GW)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
-
 target <- data.frame(period = 2030, x = 2025, xend= 2035, value = 600, label = "REPowerEU")
@@
 
-g[["milestone - violin"]][["Solar photovoltaics"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+g[["milestone"]][["Solar photovoltaics"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
   geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
-  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
   geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
@@
   facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
   coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
   expand_limits(y=c(0,2250)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
-  #annotate("text", x = -Inf, y = -Inf, label = "(GW)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank(),
+        strip.text.y = element_blank(),
+        panel.spacing = unit(4, "lines"),
+        axis.text.x = element_text(angle = 0, hjust = 0.5),
+        strip.placement = "outside",
+        strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
 
 # Carbon Capture and Storage
+
 plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Carbon Management|Storage") %>% select(-variable) %>%
@@
 
-g[["Carbon Capture and Storage"]] <- NULL
-
-# g[["Carbon Capture and Storage"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-#   geom_boxplot(outlier.shape = NA, width=0.6) +
-#          #stat_summary(geom = "text", fun = quantile,
-#         #              aes(label = paste0(round(..y..*100),"%")),
-#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-#          #      hjust=-1, angle = 90) +
-#   geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = "Carbon\nCapture and\nStorage", y = 50, label = "Net-Zero\nIndustry Act", angle=90, vjust = -0.2, hjust = 0.6, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(target~period, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   theme(strip.text.x = element_blank()) +
-#   #expand_limits(y=c(0,ceiling(max(plotData$value)/50)*50)) + 
-#   expand_limits(y=c(0,400)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-#   geom_text(data=data.frame(period=c(2030,2040),label=c("(Mt CO2/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.1, na.rm = TRUE)
-# 
-# g[["milestone - vert"]][["Carbon Capture and Storage"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = 50, label = "Net-Zero\nIndustry Act", vjust = 0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-#   expand_limits(y=c(0,400)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   theme(strip.text = element_text(angle = 90)) +
-#   coord_cartesian(clip = 'off') +
-#   annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-# 
-# g[["milestone - hor"]][["Carbon Capture and Storage"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = 50, label = "Net-Zero\nIndustry Act", angle=90, vjust = 0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
-#   expand_limits(y=c(0,400)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
-#   theme(strip.clip = "off")#+
-#   #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
-# 
-# target <- data.frame(period = 2030, x = 2025, xend= 2035, value = 50, label = "Net-Zero\nIndustry Act")
-
 plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)"))
@@
 
-g[["milestone - violin"]][["Carbon Capture and Storage"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+g[["milestone"]][["Carbon Capture and Storage"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
   geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
-  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
   geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
@@
   geom_segment(data = target, aes(x=x, xend=xend, y=value, yend=value), color = "black", linewidth=1, alpha = 0.5, linetype = "dotted") +
-
-  #geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
   annotate("text", x = -Inf, y = 50, label = "Net-Zero\nIndustry Act", angle=90, vjust = 0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
@@
   facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
   coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
   expand_limits(y=c(0,300)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=-10, b=20))) +
-  theme(strip.clip = "off")#+
-  #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank(),
+        strip.text.y = element_blank(),
+        panel.spacing = unit(4, "lines"),
+        axis.text.x = element_text(angle = 0, hjust = 0.5),
+        strip.placement = "outside",
+        strip.text.x = element_text(size = textSize.double, hjust = 1, margin=margin(l=-10, b=20)),
+        strip.clip = "off")
 
 # Novel CDR = atmospheric/biogenic CO2 (CDR)
+
 plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Carbon Management|atmospheric/biogenic CO2 - CDR") %>% select(-variable) %>%
@@
 
-g[["Novel CDR"]] <- NULL
-
-# g[["Novel CDR"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-#   geom_boxplot(outlier.shape = NA, width=0.6) +
-#          #stat_summary(geom = "text", fun = quantile,
-#         #              aes(label = paste0(round(..y..*100),"%")),
-#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-#          #      hjust=-1, angle = 90) +
-#   facet_grid(target~period, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   theme(strip.text.x = element_blank()) +
-#   expand_limits(y=c(0,400)) + 
-#   #expand_limits(y=c(0,ceiling(max(plotData$value)/50)*50)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-#   geom_text(data=data.frame(period=c(2030,2040),label=c("(Mt CO2/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.1, na.rm = TRUE)
-# 
-# g[["milestone - vert"]][["Novel CDR"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-#   expand_limits(y=c(0,400)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   theme(strip.text = element_text(angle = 90)) +
-#   coord_cartesian(clip = 'off') +
-#   annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-# 
-# g[["milestone - hor"]][["Novel CDR"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
-#   expand_limits(y=c(0,400)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
-#   #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
-
 plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)"))
@@
 
-g[["milestone - violin"]][["Novel CDR"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+g[["milestone"]][["Novel CDR"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
   geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
-  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
   geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
@@
   facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
   coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
   expand_limits(y=c(0,300)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
-  #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank(),
+        strip.text.y = element_blank(),
+        panel.spacing = unit(4, "lines"),
+        axis.text.x = element_text(angle = 0, hjust = 0.5),
+        strip.placement = "outside",
+        strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20)))
 
 # Direct Electrification
-#plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Final Energy|w/o Bunkers|w/o Non-energy Use|Electricity Share") %>% select(-variable) %>%
+
 plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Final Energy|w/o Bunkers|w/o Non-energy Use|Electricity Share") %>% select(-variable) %>%
@@
 
-g[["Direct Electrification"]] <- NULL
-
-# g[["Direct Electrification"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-#     geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-#   geom_boxplot(outlier.shape = NA, width=0.6) +
-#          #stat_summary(geom = "text", fun = quantile,
-#         #              aes(label = paste0(round(..y..*100),"%")),
-#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-#          #      hjust=-1, angle = 90) +
-#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = "Electricity\nShare in\nFinal Energy", y = h, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(target~period, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   theme(strip.text.x = element_blank()) +
-#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-#   expand_limits(y=c(0,1)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-#   geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.4, na.rm = TRUE)
-# 
-# g[["milestone - vert"]][["Direct Electrification"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-#   expand_limits(y=c(0,1)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   theme(strip.text = element_text(angle = 90)) +
-#   coord_cartesian(clip = 'off') #+
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-# 
-# g[["milestone - hor"]][["Direct Electrification"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
-#   expand_limits(y=c(0,1)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
-#   #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=geomText.size, size = 0.8*geomText.size)
-
 plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)"))
@@
 
-g[["milestone - violin"]][["Direct Electrification"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+g[["milestone"]][["Direct Electrification"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
   geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
-  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
   geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
-  #geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  #annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
   geom_point(data=mainScenarioValue, shape=4, size = 2, stroke = 1.5, alpha = 0.6, color = "red") +
   facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
   coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
@@
   expand_limits(y=c(0,1)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
-  #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=geomText.size, size = 0.8*geomText.size)
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank(),
+        strip.text.y = element_blank(),
+        panel.spacing = unit(4, "lines"),
+        axis.text.x = element_text(angle = 0, hjust = 0.5),
+        strip.placement = "outside",
+        strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20)))
 
 # Carbon-free electricity share
+
 plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "SE|Electricity|carbon-free") %>% select(-variable) %>%
@@
 
-g[["Carbon-free electricity share"]] <- NULL
-
-# g[["Carbon-free electricity share"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-#     geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-#   geom_boxplot(outlier.shape = NA, width=0.6) +
-#          #stat_summary(geom = "text", fun = quantile,
-#         #              aes(label = paste0(round(..y..*100),"%")),
-#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-#          #      hjust=-1, angle = 90) +
-#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = "Carbon-free\nelectricity\nshare", y = h, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(target~period, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   theme(strip.text.x = element_blank()) +
-#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-#   expand_limits(y=c(0,1)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-#   geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.4, na.rm = TRUE)
-# 
-# g[["milestone - vert"]][["Carbon-free electricity share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = h, label = "2022", vjust = -0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-#   expand_limits(y=c(0,1)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   theme(strip.text = element_text(angle = 90)) +
-#   coord_cartesian(clip = 'off') #+
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-# 
-# g[["milestone - hor"]][["Carbon-free electricity share"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
-#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
-#   expand_limits(y=c(0,1)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
-#   #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=geomText.size, size = 0.8*geomText.size)
-
 plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)"))
@@
 
-g[["milestone - violin"]][["Carbon-free electricity share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+g[["milestone"]][["Carbon-free electricity share"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
   geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
-  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
   geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
@@
   expand_limits(y=c(0,1)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
-  #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=geomText.size, size = 0.8*geomText.size)
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank(),
+        strip.text.y = element_blank(),
+        panel.spacing = unit(4, "lines"),
+        axis.text.x = element_text(angle = 0, hjust = 0.5),
+        strip.placement = "outside",
+        strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20)))
 
 # Residual Fossil Emissions
+
 plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% select(-variable) %>%
@@
 
-g[["Residual Fossil Emissions"]] <- NULL
-
-# g[["Residual Fossil Emissions"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-#   geom_boxplot(outlier.shape = NA, width=0.6) +
-#          #stat_summary(geom = "text", fun = quantile,
-#         #              aes(label = paste0(round(..y..*100),"%")),
-#         #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
-#          #      hjust=-1, angle = 90) +
-#   facet_grid(target~period, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   theme(strip.text.x = element_blank()) +
-#   expand_limits(y=c(0,2500)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-#   geom_text(data=data.frame(period=c(2030,2040),label=c("(Mt CO2/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.05, na.rm = TRUE)
-# 
-# g[["milestone - vert"]][["Residual Fossil Emissions"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-#   expand_limits(y=c(0,2500)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   theme(strip.text = element_text(angle = 90)) +
-#   coord_cartesian(clip = 'off') +
-#   annotate("text", x = -Inf, y = Inf, label = "(Mt CO2/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-# 
-# g[["milestone - hor"]][["Residual Fossil Emissions"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
-#   expand_limits(y=c(0,2500)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
-#   #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
-
 plotData <- plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)"))
@@
 
-g[["milestone - violin"]][["Residual Fossil Emissions"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+g[["milestone"]][["Residual Fossil Emissions"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
   geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
-  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
   geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
@@
   facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
   coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
   expand_limits(y=c(0,2250)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20))) #+
-  #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank(),
+        strip.text.y = element_blank(),
+        panel.spacing = unit(4, "lines"),
+        axis.text.x = element_text(angle = 0, hjust = 0.5),
+        strip.placement = "outside",
+        strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20)),
+        strip.clip = "off")
 
 # Domestic Hydrogen Production
+
 plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "SE|Hydrogen") %>% select(-variable) %>%
@@
 
-target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2030,2030),value=c(10,20))
-
-g[["Domestic Hydrogen Production"]] <- NULL
-
-# g[["Domestic Hydrogen Production"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
-#   geom_boxplot(outlier.shape = NA, width=0.6) +
-#   geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = "Domestic\nHydrogen\nProduction", y = 10, label = "REPowerEU\ndomestic", angle=90, vjust = 0.5, hjust = 0.5, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(target~period, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   expand_limits(y=c(0,20)) + 
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   theme(strip.text.x = element_blank()) +
-#   theme(panel.spacing = unit(4, "lines")) +
-#   #theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
-#   geom_text(data=data.frame(period=c(2030,2040),label=c("(Mtoe/yr)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=geomText.size, hjust=1.4, na.rm = TRUE)
-# 
-# g[["milestone - vert"]][["Domestic Hydrogen Production"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = -Inf, y = 10, label = "REPowerEU\ndomestic", vjust = 0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_x_continuous(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL, position = "top") +
-#   expand_limits(y=c(0,20)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   theme(strip.text = element_text(angle = 90)) +
-#   coord_cartesian(clip = 'off') +
-#   annotate("text", x = -Inf, y = Inf, label = "(Mtoe/yr)", hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) #+
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size))
-# 
-# g[["milestone - hor"]][["Domestic Hydrogen Production"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mtoe/yr)")), aes(x = period, y = value, group=period)) +
-#   geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
-#   geom_boxplot(outlier.shape = NA, width=6) +
-#   geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-#   annotate("text", x = -Inf, y = 10, label = "REPowerEU\ndomestic", angle=90, vjust = 0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
-#   facet_grid(.~target, scales="free") +
-#   theme_doubleColumn() +
-#   coord_flip(clip = 'off') +
-#   theme(axis.title.y=element_blank()) +
-#   theme(strip.text.y = element_blank()) +
-#   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
-#   expand_limits(y=c(0,20)) + 
-#   theme(panel.spacing = unit(4, "lines")) +
-#   theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-#   theme(strip.placement = "outside") +
-#   #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-#   #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-#   theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
-#   #annotate("text", x = -Inf, y = -Inf, label = "(Mtoe/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
-
 target <- data.frame(period = 2030, x = 2025, xend= 2035, value = 10, label = "REPowerEU")
@@
 
-g[["milestone - violin"]][["Domestic Hydrogen Production"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
+g[["milestone"]][["Domestic Hydrogen Production"]] <- ggplot(plotData, aes(x = period, y = value, group=period)) +
   geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
-  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
   geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
   geom_segment(data = target, aes(x=x, xend=xend, y=value, yend=value), color = "black", linewidth=1, alpha = 0.5, linetype = "dotted") +
-  #geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
   annotate("text", x = -Inf, y = 10, label = "REPowerEU\ndomestic", angle=90, vjust = 0.5, hjust = 0.8, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
@@
   facet_grid(.~target, scales="free") +
-  theme_doubleColumn() +
   coord_flip(clip = 'off') +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
   scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
   expand_limits(y=c(0,20)) + 
-  theme(panel.spacing = unit(4, "lines")) +
-  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
-  theme(strip.placement = "outside") +
-  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
-  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
-  theme(strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=-15, b=20)),
-        strip.clip = "off") #+
-  #annotate("text", x = -Inf, y = -Inf, label = "(Mtoe/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
-
-# g[["Targets"]] <- gridExtra::arrangeGrob(
-#   g[["Emissions reductions"]] + theme(strip.text.x = element_blank()) + theme(plot.margin=margin(b=20, l = 30)), #+ theme(plot.margin=margin(10,10,30,10)),margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
-#   g[["Energy savings"]] + theme(plot.margin=margin(b=20, l = 10)),
-#   g[["Electricity Demand"]] + theme(plot.margin=margin(b=20, l = 35)),
-#   g[["Renewables Share"]] + theme(plot.margin=margin(b=20, l = 15)),
-#   g[["Wind capacity"]] + theme(plot.margin=margin(b=20, l = 50)),
-#   g[["Solar photovoltaics"]] + theme(plot.margin=margin(b=20, l = 10)),
-#   g[["Carbon Capture and Storage"]] + theme(plot.margin=margin(b=20, l = 15)),
-#   g[["Novel CDR"]] + theme(plot.margin=margin(b=20, l = 50)),
-#   g[["Direct Electrification"]] + theme(plot.margin=margin(b=20, l = 17)),
-#   g[["Carbon-free electricity share"]] + theme(plot.margin=margin(b=20, l = 24)),
-#   g[["Domestic Hydrogen Production"]] + theme(plot.margin=margin(b=20,l = 35)),
-#   g[["Residual Fossil Emissions"]] + theme(plot.margin=margin(b=20, l = 39)),
-#   ncol = 1
-# )
-
-#ggsave(paste0(outChartsFolder,"/svg/targets.svg"), g[["Targets"]] , device="svg", width = 12, height = 17, dpi=100, units = "in")
-#ggsave(paste0(outChartsFolder,"/png/targets.png"), g[["Targets"]] , device="png", width = 12, height = 17, dpi=300, units = "in")
-
-# g[["milestone - vert targets"]] <- gridExtra::arrangeGrob(
-#   g[["milestone - vert"]][["Emissions reductions"]] + theme(plot.margin=margin(r=30,t = 30)), #+ theme(plot.margin=margin(10,10,30,10)),margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
-#   g[["milestone - vert"]][["Energy savings"]] + theme(plot.margin=margin(r=30,t = 10)),
-#   g[["milestone - vert"]][["Renewables Share"]] + theme(plot.margin=margin(r=30,t = 15)),
-#   g[["milestone - vert"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(r=30,t = 39)),
-#   g[["milestone - vert"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(r=30,t = 15)),
-#   g[["milestone - vert"]][["Novel CDR"]] + theme(plot.margin=margin(t = 50)),
-#   
-#   g[["milestone - vert"]][["Electricity Demand"]] + theme(plot.margin=margin(r=30,t = 35)),
-#   g[["milestone - vert"]][["Wind capacity"]] + theme(plot.margin=margin(r=30,t = 50)),
-#   g[["milestone - vert"]][["Solar photovoltaics"]] + theme(plot.margin=margin(r=30,t = 10)),
-#   g[["milestone - vert"]][["Direct Electrification"]] + theme(plot.margin=margin(r=30,t = 17)),
-#   g[["milestone - vert"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(t = 24)),
-#   g[["milestone - vert"]][["Domestic Hydrogen Production"]] + theme(plot.margin=margin(r=30,t = 35)),
-#   nrow = 2
-# )
-
-#ggsave(paste0(outChartsFolder,"/svg/milestone - vert targets.svg"), g[["milestone - vert targets"]] , device="svg", width = 12, height = 17, dpi=100, units = "in")
-#ggsave(paste0(outChartsFolder,"/png/milestone - vert targets.png"), g[["milestone - vert targets"]] , device="png", width = 12, height = 17, dpi=300, units = "in")
-
-# 
-# g[["milestone - hor targets"]] <- gridExtra::arrangeGrob(
-#   g[["milestone - hor"]][["Emissions reductions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-#   g[["milestone - hor"]][["Energy savings"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-#   g[["milestone - hor"]][["Renewables Share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-#   g[["milestone - hor"]][["Direct Electrification"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-#   g[["milestone - hor"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-#   g[["milestone - hor"]][["Domestic Hydrogen Production"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-#   
-#   g[["milestone - hor"]][["Electricity Demand"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-#   g[["milestone - hor"]][["Wind capacity"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-#   g[["milestone - hor"]][["Solar photovoltaics"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-#   
-#   g[["milestone - hor"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-#   g[["milestone - hor"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-#   g[["milestone - hor"]][["Novel CDR"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-#   
-#   
-#   ncol = 2
-# )
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank(),
+        strip.text.y = element_blank(),
+        panel.spacing = unit(4, "lines"),
+        axis.text.x = element_text(angle = 0, hjust = 0.5),
+        strip.placement = "outside",
+        strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=-15, b=20)),
+        strip.clip = "off")
+```
+
+```{r, echo=FALSE, include=FALSE}
 
 g[["Figure 5"]] <- gridExtra::arrangeGrob(
-  g[["milestone - violin"]][["Emissions reductions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - violin"]][["Energy savings"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - violin"]][["Renewables Share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - violin"]][["Direct Electrification"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - violin"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - violin"]][["Domestic Hydrogen Production"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-
-  g[["milestone - violin"]][["Electricity Demand"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - violin"]][["Wind capacity"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - violin"]][["Solar photovoltaics"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-
-  g[["milestone - violin"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - violin"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone - violin"]][["Novel CDR"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-
+  g[["milestone"]][["Emissions reductions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Final Energy Demand"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Renewables Share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Direct Electrification"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Domestic Hydrogen Production"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Electricity Demand"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Wind capacity"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Solar photovoltaics"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Novel CDR"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
   ncol = 2
@@
 ```
-
-<!-- ```{r, echo=FALSE} -->
-
-<!-- g[["ECEMP abstract"]] <- gridExtra::arrangeGrob( -->
-<!--   g[["milestone - vert"]][["Electricity Demand"]] + theme(plot.margin=margin(r=30,t = 35)), -->
-<!--   g[["milestone - vert"]][["Direct Electrification"]] + theme(plot.margin=margin(r=30,t = 17)), -->
-<!--   g[["milestone - vert"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(t = 24)), -->
-<!--   g[["milestone - vert"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(r=30,t = 39)), -->
-<!--   g[["milestone - vert"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(r=30,t = 15)), -->
-<!--   g[["milestone - vert"]][["Novel CDR"]] + theme(plot.margin=margin(t = 50)), -->
-<!--   nrow = 1 -->
-<!-- ) -->
-
-<!-- ggsave(paste0(outChartsFolder,"/png/ECEMP abstract.png"), g[["ECEMP abstract"]] , device="png", width = 12, height = 8, dpi=300, units = "in") -->
-
-<!-- ``` -->
 
@@
 
-plotData <- df_beforeFilter %>%
+plotData <- df %>%
   filter(region == "EU27", period %in% c(2020,2030,2040,2050), scenario %in% c(mainScen,"Nzero_57_bio7p5_limVRE"), variable %in% vars) %>%
@@
   geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
-  theme_doubleColumn() +
   scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(nrow = 1, order = 1, override.aes = list(pattern = "none"))) +
@@
   scale_x_continuous(breaks=c(2020,2030,2040,2050), minor_breaks = NULL) +
-  theme(axis.title.y = element_blank()) +
-  #ylab("TWh") +
-  #theme(legend.text=element_text(size=theme.single.text.size)) +
-  theme(legend.margin=margin(t = -0.4, unit='cm')) +
   labs(title = "(a) Wind and Solar Generation (TWh)") + 
-  #theme(plot.title = element_text(hjust=-0.1))
-  theme(legend.box = "horizontal", 
+  theme_doubleColumn() +
+  theme(axis.title.y = element_blank(),
+        legend.margin=margin(t = -0.4, unit='cm'),
+        legend.box = "horizontal", 
         legend.box.just = "center")
-
- # ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 1 - Variable renewables sensitivity panel - (a) Wind and Solar generation.svg"), g[["Wind and Solar generation"]] , device="svg", width = 9, height = 6, dpi=100, units = "in")
- # ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 1 - Variable renewables sensitivity panel - (a) Wind and Solar generation.png"), g[["Wind and Solar generation"]] , device="png", width = 9, height = 6, dpi=300, units = "in")
 
@@
   df %>%
-    filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>%
+    filter(!grepl("limVRE", scenario), region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>%
     calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
     mutate(reduction = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)) ,2),
-           scenName = "default") %>%
+           scenName = "without\nlim-VRE") %>%
     select(-variable) %>%
@@
   ,
-  df_beforeFilter %>%
-    filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen, grepl("limVRE", scenario)) %>%
+  df %>%
+    filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>%
     calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
     mutate(reduction = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)) ,2),
-           scenName = "limited VRE") %>%
+           scenName = "with\nlim-VRE") %>%
     select(-variable) %>%
@@
   geom_hline(yintercept=1, color = "black", linewidth=2, alpha = 0.5) +
-  #geom_hline(yintercept=1, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
-  theme_doubleColumn() +
-  #scale_y_continuous(breaks=c(1,0.95,0.9,0.85,0.8, 0.75), minor_breaks = NULL, labels = scales::percent) +
   scale_y_reverse(breaks=c(1,0.95,0.9,0.85,0.8, 0.75), minor_breaks = NULL, labels = scales::percent) +
@@
   labs(title = "(b) 2040 target (%)") +
+  theme_doubleColumn() +
   theme(plot.title = element_text(hjust=1))
-  #theme(plot.title = element_text(margin=margin(l=-100)))
-
- # ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 1 - Variable renewables sensitivity panel - (b) 2040 target.svg"), g[["limVRE target reduction"]] , device="svg", width = 3, height = 6, dpi=100, units = "in")
- # ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 1 - Variable renewables sensitivity panel - (a) 2040 target.png"), g[["limVRE target reduction"]] , device="png", width = 3, height = 6, dpi=300, units = "in")
-
-# g[["Supplementary Figure 1 - Variable renewables sensitivity panel"]] <- gridExtra::arrangeGrob(
-#   g[["Wind and Solar generation"]], #+ theme(plot.margin=margin(80,5,50,0)), #margin(t = 0, r = 0, b = 0, l = 0
-#   g[["limVRE target reduction"]], #+ theme(plot.margin=margin(80,5,50,0)), #margin(t = 0, r = 0, b = 0, l = 0
-#   layout_matrix = rbind(c(1,1,1,2))
-#   )
-
-# ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 1 - Variable renewables sensitivity panel.svg"), g[["Supplementary Figure 1 - Variable renewables sensitivity panel"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 1 - Variable renewables sensitivity panel.png"), g[["Supplementary Figure 1 - Variable renewables sensitivity panel(GW)"]] , device="png", width = 12, height = 6, dpi=300, units = "in")
 
@@
 
-<!-- :::: {style="display: flex;"} -->
-
-<!-- ::: {} -->
-
-<!-- (a) Carbon price (€/t CO2) -->
-
 ```{r supplChart_figure2a_lineplot, echo=FALSE, include=FALSE}
@@
 
-plotData <- df_beforeFilter %>%
+plotData <- df %>%
   filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
@@
   scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 6))) +
-  theme_doubleColumn() +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  #guides(fill = guide_legend(nrow = 2, byrow = T)) +
-  #theme(legend.text=element_text(size=theme.single.text.size)) +
-  theme(legend.key.width = unit(2,"cm")) +
-  theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical") + 
-  #theme(legend.key.width = unit(2,"cm")) +
-  #ylab("€/t CO2") +
-  theme(legend.spacing.y = unit(0.2, "lines")) +
-  labs(title = expression(paste("(a) Carbon price (€/t ", CO[2],")")))
-
-  #theme(plot.title = element_text(hjust=-0.1))
-  #guides(linetype=guide_legend(keywidth = 3))
-
-#  theme(legend.position="right", legend.direction = "vertical")
-
-# ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 2 - Mitigation costs panel - (a) Carbon Price.svg"), g[["Carbon Price"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Supplementary figure 2 - Mitigation costs panel - (a) Carbon Price.png"), g[["Carbon Price"]] , device="png", width = 12, height = 6, dpi=300, units = "in")
+  labs(title = expression(paste("(a) Carbon price (€/t ", CO[2],")"))) +
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank(),
+        strip.text.y = element_blank(),
+        legend.key.width = unit(2,"cm"),
+        legend.position="right", 
+        legend.direction = "vertical", 
+        legend.box = "vertical",
+        legend.spacing.y = unit(0.2, "lines"))
 
@@
 
-plotDataOrig <- df_beforeFilter %>%
+plotDataOrig <- df %>%
   filter(region == "EU27", period %in% c(2020,2030,2040,2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
@@
   facet_grid(period~type, scales = "free_x") +
-  theme_doubleColumn() +
-  labs(title = expression(paste("(b) 2040 carbon price variation (€/t ", CO[2],")")))
+  labs(title = expression(paste("(b) 2040 carbon price variation (€/t ", CO[2],")"))) +
+  theme_doubleColumn()
 
@@
   facet_grid(period~type, scales = "free_x") +
-  theme_doubleColumn() +
-  labs(title = expression(paste("(b) 2040 carbon price variation (€/t ", CO[2],")")))
-
-#ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 2 - Mitigation costs panel - (b) Carbon Price.svg"), g[["Carbon Price - boxplot - all_years"]] , device="svg", width = 12, height = 12, dpi=100, units = "in")
-#ggsave(paste0(outChartsFolder,"/png/Supplementary figure 2 - Mitigation costs panel - (b) Carbon Price.png"), g[["Carbon Price - boxplot - all_years"]] , device="png", width = 12, height = 12, dpi=300, units = "in")
-
-```
-
-<!-- ```{r, echo=FALSE, fig.width=12, fig.height=5} -->
-
-<!-- g[["Carbon Price"]] -->
-
-<!-- ``` -->
+  labs(title = expression(paste("(b) 2040 carbon price variation (€/t ", CO[2],")"))) +
+  theme_doubleColumn()
+
+```
 
@@
   geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
-  theme_doubleColumn() +
-  theme(axis.title.y=element_blank()) +
   scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(ncol = 1, order = 1)) +
-  #ylab("billion €/yr") +
-  theme(#legend.text=element_text(size=0.8*geomText.size),
+  theme_doubleColumn() +
+  labs(title = "Energy supply investments (billion €/yr) ") + 
+  theme(axis.title.y=element_blank(),
         legend.key.height = unit(0.6, "cm"),
-        legend.key.width = unit(0.6,"cm")) +
-  theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical",
-        legend.margin=margin(t = 40)) +
-  labs(title = "Energy supply investments (billion €/yr) ") #+ 
-  #theme(plot.title = element_text(hjust=-0.6))
+        legend.key.width = unit(0.6,"cm"),
+        legend.position="right",
+        legend.direction = "vertical", 
+        legend.box = "vertical",
+        legend.margin=margin(t = 40))
 
@@
 
-### SSupplementary figure 4. EU-27 Electricity capacity
+### Supplementary figure 4. EU-27 Electricity capacity
 
@@
   "DEU" = "Germany",
-  "FRA" = "France"#,
-#  "EUN" = "EU North",
-#  "EUC" = "EU Central",
-#  "EUS" = "EU South"
-)
+  "FRA" = "France")
 
@@
   "DEU" = "DEU",
-  "FRA" = "FRA"#,
-#  "EUN" = c("EWN", "ENC"),
-#  "EUC" = c("ECS", "ECE"),
-#  "EUS" = c("ESW", "ESC")
-)
+  "FRA" = "FRA")
 
@@
     facet_wrap(~regionName, scales = "free_y") +
-    theme_doubleColumn() +
     scale_x_continuous(breaks=c(2020,2030,2040,2050)) +
     scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
-    theme(legend.position="none") +
-    theme(axis.title.y=element_blank()) +
-    theme(strip.clip = "off") + 
-    theme(plot.margin=margin(b=0))
-  #if(reg %in% c("EU27","DEU","FRA"))
-  #  gg <- gg +
-  #    theme(axis.text.x=element_blank())
+    theme_doubleColumn() +
+    theme(legend.position="none",
+          axis.title.y=element_blank(),
+          strip.clip = "off",
+          plot.margin=margin(b=0))
+
   return(gg)
@@
          cumPercentage = cumValue / n)
+
   gg <- ggplot(pData,aes(x=period,y=percentage)) +
@@
                     box.padding = 0, direction = "y", nudge_x = -1.6, segment.color = 'transparent') +
-                    #box.padding = 0.1, direction = "y", max.iter = 5, nudge_x = -1) +
-
-                    #direction = "y",box.padding=0) +
-    #geom_text(data=pData %>% filter(percentage >= 0.02),aes(label = paste0(round(percentage,2)*100,"%"), y=cumPercentage-percentage/2, x = 2039.5), vjust=0.5, hjust=1, na.rm=TRUE, color = "black", size=geomText.size*0.65) +
     facet_wrap(~period, scales = "free_y") +
-    theme_doubleColumn() +
     scale_y_continuous(labels = scales::percent) +
@@
     coord_cartesian(clip="off") +
-    theme(legend.position="none") +
-    theme(axis.title.y=element_blank()) +
-    theme(axis.text.y=element_blank()) +
-    theme(strip.clip = "off") + 
-    theme(plot.margin=margin(0,20,46,0)) #t, r, b, l
-  #if(reg %in% c("EU27","DEU","FRA")){
-  #  gg <- gg +
-  #    theme(axis.text.x=element_blank())
-  #} else {
-  #  gg <- gg +
-  #    theme(plot.margin=margin(0,20,45,0)) #t, r, b, l
-  #}
+    theme_doubleColumn() +
+    theme(legend.position="none",
+          axis.title.y=element_blank(),
+          axis.text.y=element_blank(),
+          strip.clip = "off",
+          plot.margin=margin(0,20,46,0)) #t, r, b, l
+
   return(gg)
@@
   geom_area(aes(fill=variable),alpha=0.8) +
-  theme_doubleColumn() +
   scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
   guides(fill=guide_legend(nrow=3,override.aes = list(alpha=1))) +
-  theme(#legend.text = element_text(size = theme.double.text.size),
-        #legend.key.height = unit(0.8, "cm"),
-        #legend.key.width = unit(0.8,"cm"),
-        legend.spacing.x = unit(0.3, 'cm')) +
-  theme(legend.title=element_blank(),
-        legend.margin=margin(c(0,0,0,0))) +
-  theme(plot.margin=margin(0,0,0,0)) + 
-  theme(legend.margin=margin(l=-10, t= 20))
+  theme_doubleColumn() +
+  theme(legend.spacing.x = unit(0.3, 'cm'),
+        legend.title=element_blank(),
+        plot.margin=margin(0,0,0,0),
+        legend.margin=margin(l=-10, b=0, t=20, r=0))
 )
@@
   g[["Capacity_2040"]][["FRA"]],
-  #g[["Capacity"]][["EUN"]],
-  #g[["Capacity_2040"]][["EUN"]],
-  #g[["Capacity"]][["EUS"]],
-  #g[["Capacity_2040"]][["EUS"]],
-  #g[["Capacity"]][["EUC"]],
-  #g[["Capacity_2040"]][["EUC"]],
   legend,
@@
                         c(2,2,2,2, 3,3, 4,4,4,4, 5,5, 6,6,6,6, 7,7),
-                        # c(7,7,7,7, 8,8, 9,9,9,9, 10,10, 11,11,11,11, 12,12),
-                        # c(7,7,7,7, 8,8, 9,9,9,9, 10,10, 11,11,11,11, 12,12),
-                        # c(7,7,7,7, 8,8, 9,9,9,9, 10,10, 11,11,11,11, 12,12),
-                        # c(7,7,7,7, 8,8, 9,9,9,9, 10,10, 11,11,11,11, 12,12),
-                        # c(7,7,7,7, 8,8, 9,9,9,9, 10,10, 11,11,11,11, 12,12),
-                        # c(7,7,7,7, 8,8, 9,9,9,9, 10,10, 11,11,11,11, 12,12),
-                        # rep(13,18),
-                        # rep(13,18))
                         rep(8,18),
@@
  ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 4. EU-27 Electricity capacity.svg"), g[["Supplementary figure 4"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
- ggsave(paste0(outChartsFolder,"/png/Supplementary figure 4. EU-27 Electricity capacity..png"), g[["Supplementary figure 4"]] , device="png", width = 12, height = 6, dpi=300, units = "in")
+ ggsave(paste0(outChartsFolder,"/png/Supplementary figure 4. EU-27 Electricity capacity.png"), g[["Supplementary figure 4"]] , device="png", width = 12, height = 6, dpi=300, units = "in")
 
@@
 
-#inv_vars <- setNames(names(vars),vars)
-
 color <- c(
@@
     facet_wrap(~regionName, scales = "free_y") +
-    theme_doubleColumn() +
     scale_x_continuous(breaks=c(2020,2030,2040,2050)) +
     scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
-    theme(legend.position="none") +
-    theme(axis.title.y=element_blank()) +
-    theme(strip.clip = "off") + 
-    theme(plot.margin=margin(b=0))
+    theme_doubleColumn() +
+    theme(legend.position="none",
+          axis.title.y=element_blank(),
+          strip.clip = "off",
+          plot.margin=margin(b=0))
   if(reg %in% c("EU27","DEU","FRA"))
@@
     coord_cartesian(clip="off") +
-    theme(legend.position="none") +
-    theme(axis.title.y=element_blank()) +
-    theme(axis.text.y=element_blank()) +
-    theme(strip.clip = "off") + 
-    theme(plot.margin=margin(0,20,5,0)) #t, r, b, l
+    theme_doubleColumn() +
+    theme(legend.position="none",
+          axis.title.y=element_blank(),
+          axis.text.y=element_blank(),
+          strip.clip = "off",
+          plot.margin=margin(0,20,5,0)) #t, r, b, l
   if(reg %in% c("EU27","DEU","FRA")){
@@
   geom_area(aes(fill=variable),alpha=0.8) +
-  theme_doubleColumn() +
   scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
   guides(fill=guide_legend(nrow=3,override.aes = list(alpha=1))) +
-  theme(#legend.text = element_text(size = theme.double.text.size),
-        #legend.key.height = unit(0.8, "cm"),
-        #legend.key.width = unit(0.8,"cm"),
-        legend.spacing.x = unit(0.3, 'cm')) +
-  theme(legend.title=element_blank(),
-        legend.margin=margin(c(0,0,0,0))) +
-  theme(plot.margin=margin(0,0,0,0)) + 
-  theme(legend.margin=margin(l=-10))
+  theme_doubleColumn() +
+  theme(legend.spacing.x = unit(0.3, 'cm'),
+        legend.title=element_blank(),
+        plot.margin=margin(0,0,0,0),
+        legend.margin=margin(l=-10, b=0, t=20, r=0))
 )
@@
                         rep(14,18))
-#                        rep(7,18))
   )
@@
 
-<!-- :::: {style="display: flex;"} -->
-
-<!-- ::: {} -->
-
 <!-- (a) per sector and carrier -->
@@
 ```{r supplChart_figure6a, echo=FALSE, include=FALSE}
-
-# vars <- list(
-#   "Transport  - Electricity" = "FE|Transport|w/o Bunkers|Electricity",
-#   "Bunkers    - Electricity" = "FE|Transport|Bunkers|Electricity",
-#   "Buildings  - Electricity" = "FE|Buildings|Electricity",
-#   "Industry   - Electricity" = "FE|Industry|Electricity",
-#   "Transport  - Hydrogen"    = "FE|Transport|w/o Bunkers|Hydrogen",
-#   "Bunkers    - Hydrogen"    = "FE|Transport|Bunkers|Hydrogen",
-#   "Buildings  - Hydrogen"    = "FE|Buildings|Hydrogen",
-#   "Industry   - Hydrogen"    = "FE|Industry|Hydrogen",
-#   "Buildings  - Heat"        = "FE|Buildings|Heat",
-#   "Industry   - Heat"        = "FE|Industry|Heat",
-#   "Transport  - Gases"       = "FE|Transport|w/o Bunkers|Gases",
-#   "Bunkers    - Gases"       = "FE|Transport|Bunkers|Gases",
-#   "Buildings  - Gases"       = "FE|Buildings|Gases",
-#   "Industry   - Gases"       = "FE|Industry|Gases",
-#   "Non-energy - Gases"       = "FE|Non-energy Use|Industry|Gases",
-#   "Transport  - Liquids"     = "FE|Transport|w/o Bunkers|Liquids",
-#   "Bunkers    - Liquids"     = "FE|Transport|Bunkers|Liquids",
-#   "Buildings  - Liquids"     = "FE|Buildings|Liquids",
-#   "Industry   - Liquids"     = "FE|Industry|Liquids",
-#   "Non-energy - Liquids"     = "FE|Non-energy Use|Industry|Liquids",
-#   "Buildings  - Solids"      = "FE|Buildings|Solids",
-#   "Industry   - Solids"      = "FE|Industry|Solids",
-#   "Non-energy - Solids"      = "FE|Non-energy Use|Industry|Solids"
-# )
-# 
-# # vars <- list(
-# #   "Transport  - Electricity" = "FE|Transport|w/o Bunkers|Electricity",
-# #   "Bunkers    - Electricity" = "FE|Transport|Bunkers|Electricity",
-# #   "Buildings  - Electricity" = "FE|Buildings|Electricity",
-# #   "Industry   - Electricity" = "FE|Industry|Electricity",
-# #   "Transport  - Hydrogen"    = "FE|Transport|w/o Bunkers|Hydrogen",
-# #   "Bunkers    - Hydrogen"    = "FE|Transport|Bunkers|Hydrogen",
-# #   "Buildings  - Hydrogen"    = "FE|Buildings|Hydrogen",
-# #   "Industry   - Hydrogen"    = "FE|Industry|Hydrogen",
-# #   "Buildings  - Heat"        = "FE|Buildings|Heat",
-# #   "Industry   - Heat"        = "FE|Industry|Heat",
-# #   "Transport  - Gases"       = "FE|Transport|w/o Bunkers|Gases",
-# #   "Bunkers    - Gases"       = "FE|Transport|Bunkers|Gases",
-# #   "Buildings  - Gases"       = "FE|Buildings|Gases",
-# #   "Industry   - Gases"       = "FE|w/o Non-energy Use|Industry|Gases",
-# #   "Non-energy - Gases"       = "FE|Non-energy Use|Industry|Gases",
-# #   "Transport  - Liquids"     = "FE|Transport|w/o Bunkers|Liquids",
-# #   "Bunkers    - Liquids"     = "FE|Transport|Bunkers|Liquids",
-# #   "Buildings  - Liquids"     = "FE|Buildings|Liquids",
-# #   "Industry   - Liquids"     = "FE|w/o Non-energy Use|Industry|Liquids",
-# #   "Non-energy - Liquids"     = "FE|Non-energy Use|Industry|Liquids",
-# #   "Buildings  - Solids"      = "FE|Buildings|Solids",
-# #   "Industry   - Solids"      = "FE|w/o Non-energy Use|Industry|Solids",
-# #   "Non-energy - Solids"      = "FE|Non-energy Use|Industry|Solids"
-# # )
-# 
-# plotColor <- list(
-#   "Transport  - Electricity" = "#ffed9e",
-#   "Bunkers    - Electricity" = "#ffb84c",
-#   "Buildings  - Electricity" = "#ffd27d",
-#   "Industry   - Electricity" = "#fa8c02",
-#   "Transport  - Hydrogen" = "#b8d8be",
-#   "Bunkers    - Hydrogen" = "#31a354",
-#   "Buildings  - Hydrogen" = "#a1d99b",
-#   "Industry   - Hydrogen" = "#2b7c0d",
-#   "Buildings  - Heat" = "#b92400",
-#   "Industry   - Heat" = "#800000",
-#   "Transport  - Gases" = "#9d74b0",
-#   "Bunkers    - Gases" = "#800080",
-#   "Buildings  - Gases" = "#c7a3d4",
-#   "Industry   - Gases" = "#610d85",
-#   "Non-energy - Gases" = "#c875ec",
-#   "Transport  - Liquids" = "#accbff",
-#   "Bunkers    - Liquids" = "#649eff",
-#   "Buildings  - Liquids" = "#98c1d9",
-#   "Industry   - Liquids" = "#3d5a80",
-#   "Non-energy - Liquids" = "#92bbff",
-#   "Buildings  - Solids" = "#a5a5a5",
-#   "Industry   - Solids" = "#1b1b1b",
-#   "Non-energy - Solids" = "#909090"
-# )
-# 
-# plotData <- df %>%
-#   filter(region == "EU27", period %in% c(2010:2050), variable %in% vars, scenario == mainScen) %>%
-#   mutate(variable=factor(variable, levels=vars))
-#   
-# #total
-# totalData <- df %>%
-#   filter(region == "EU27", period %in% c(2010:2050), variable == "FE", scenario == mainScen)
-# 
-# if(energyInMtoe){
-#   plotData <- plotData %>%
-#     mutate(
-#       value = value*EJ2Mtoe,
-#       unit  = "Mtoe/yr")
-#   totalData <- totalData %>%
-#     mutate(
-#       value = value*EJ2Mtoe,
-#       unit  = "Mtoe/yr")
-# }
-# 
-# g[["Supplementary Figure 4a. Final energy demand per sector and carrier"]] <- ggplot(plotData,aes(x=period,y=value)) +
-#   geom_area(aes(fill=variable), alpha = 0.8) +
-#   geom_line(data=totalData, linewidth = 1, color="black") +
-#   geom_vline(xintercept=2020, color = "black", linetype="dashed", linewidth=1, alpha = 0.5) +
-#   geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
-#   theme_doubleColumn() +
-#   #ylab("Final Energy Demand - EJ/yr") + 
-#   #ggtitle("(a) per sector and carrier") +
-#   scale_fill_manual(values = setNames(plotColor[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(ncol = 3)) +
-#   theme(legend.margin=margin(l = -1, unit='cm')) +
-#   scale_x_continuous(breaks=c(2010, 2010, 2020,2030,2040,2050)) + 
-#   theme(axis.title.x=element_blank()) +
-#   theme(axis.title.y=element_blank()) +
-#   theme(legend.title = element_blank()) +
-#   theme(legend.text = element_text(size = theme.double.text.size*0.8),
-#         #legend.key.height = unit(0.7, "cm"),
-#         #legend.key.width = unit(0.7,"cm"),
-#         legend.spacing.x = unit(0.2, 'cm')) + 
-#   #  theme(plot.title = element_text(size = 1.2*theme.double.text.size)) +
-#   labs(title = paste0("(a) Energy and non-energy use\nper sector and carrier (", unique(plotData$unit), ")")) +
-#   theme(plot.title = element_text(hjust=0))
-#
 
@@
   ),
-  # "Industry"=c(
-  #   "Industry - Electricity"="FE|Industry|Electricity",
-  #   "Industry - Hydrogen"   ="FE|Industry|Hydrogen",
-  #   "Industry - Heat"       ="FE|Industry|Heat",
-  #   "Industry - Gases"      ="FE|Industry|Gases",
-  #   "Industry - Liquids"    ="FE|Industry|Liquids",
-  #   "Industry - Solids"     ="FE|Industry|Solids"
-  # ),
   "Industry"=c(
@@
 
-plotColor <- list(
+plotColor <- c(
+  "Transport        " = "transparent",
+  "Buildings        " = "transparent",
+  "Industry         " = "transparent",
   "Transport - Electricity" = "#ffb200",
@@
 g[["Supplementary Figure 6a. Final energy demand per sector and carrier"]] <- ggplot(plotData,aes(x=period,y=value)) +
-  #geom_area(data=plotData,aes(fill=variable), alpha = 0.8) +
-  geom_area_pattern(data=plotData,aes(fill=label,pattern=sector, pattern_angle = sector), pattern_key_scale_factor = 1, pattern_density=0.1, pattern_spacing = 0.015, pattern_colour = "white", pattern_fill = "white", pattern_alpha=0.4) + #pattern_key_scale_factor = 0.3, pattern_density=0.3, pattern_spacing = 0.03, pattern_colour = "white", pattern_fill = "white", pattern_alpha=0.4) +
-  geom_line(data=totalData, linewidth = 1, color="black") +
+  geom_area_pattern(data=plotData,aes(fill=label,pattern=sector, pattern_angle = sector), pattern_key_scale_factor = 1, pattern_density=0.1, pattern_spacing = 0.015, pattern_colour = "white", pattern_fill = "white", pattern_alpha=0.4) +   geom_line(data=totalData, linewidth = 1, color="black") +
   geom_vline(xintercept=2020, color = "black", linetype="dashed", linewidth=1, alpha = 0.5) +
   geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
-  theme_doubleColumn() +
-  scale_fill_manual(values = plotColor, labels = c(varTolabel,"empty" = "","empty2" = ""), guide = guide_legend(order = 1, override.aes = list(pattern = "none"),byrow=TRUE, ncol = 3), drop = FALSE) +
+  scale_fill_manual(values = plotColor, labels = sub('.*- |empty.*', '', names(plotColor)), guide = guide_legend(order = 1, override.aes = list(pattern = "none"),byrow=TRUE, ncol = 3), drop = FALSE) +
   scale_pattern_manual("pattern",values = pattern, breaks=c("Non-Energy Use","Bunkers"), guide = guide_legend(order = 2, override.aes = list(fill = "#555555"),byrow=TRUE,ncol = 2)) +
   scale_pattern_angle_manual("pattern",values = patternAngle, breaks=c("Non-Energy Use","Bunkers"), guide = guide_legend(order = 2,ncol = 1)) +
-  theme(legend.margin=margin(l = -1, unit='cm')) +
-  #scale_x_continuous(breaks=c(2010,2020,2030,2040,2050)) +
-  theme(axis.title.x=element_blank(),
+  labs(title = paste0("(a) Energy and non-energy use\nper sector and carrier (", unique(plotData$unit), ")")) +
+  theme_doubleColumn() +
+  theme(legend.margin=margin(l = -1, unit='cm'),
+        axis.title.x=element_blank(),
         axis.title.y=element_blank(),
         legend.title = element_blank(),
-        legend.text = element_text(size = theme.double.text.size*0.8),
-        #legend.key.height = unit(0.7, "cm"),
-        #legend.key.width = unit(0.7,"cm"),
-        legend.spacing.x = unit(0.2, 'cm'),
+        #legend.text = element_text(size = geomText.size*0.8),
+        #legend.spacing.x = unit(1, 'cm'),
         plot.title = element_text(hjust=0),
         legend.position="bottom", 
-        legend.box = "vertical") +
-  labs(title = paste0("(a) Energy and non-energy use\nper sector and carrier (", unique(plotData$unit), ")"))
-
-```
-
-<!-- ```{r, echo=FALSE, fig.width=6, fig.height=8} -->
-
-<!-- g[["Supplementary Figure 4a. Final energy demand per sector and carrier"]] -->
-
-<!-- ``` -->
-
-<!-- ::: -->
-
-<!-- ::: {} -->
+        legend.box = "vertical")
+
+```
 
@@
 vars <- list(
-  "Electric - Non-Fossil" = c(
+  "Non-Fossil - Electric" = c(
     "FE|Transport|Electricity|Non-Fossil",
@@
    ),
-  "Non-Electric - Non-Fossil" = c(
+  "Non-Fossil - Non-Electric" = c(
     "FE|Transport|Hydrogen",
@@
   ), 
-  "Electric - Fossil" = c(
+  "Fossil        - Electric" = c(
     "FE|Transport|Electricity|Fossil",
@@
    ),
-  "Non-Electric - Fossil" = c(
+  "Fossil        - Non-Electric" = c(
     "FE|Buildings|Gases|Fossil",
@@
 plotColor <- list(
-  "Electric - Non-Fossil" = "#e56b6f",
-  "Non-Electric - Non-Fossil" = "#6d597a",
-  "Electric - Fossil" = "#474973",
-  "Non-Electric - Fossil" = "#161b33"
+  "Non-Fossil - Electric" = "#e56b6f",
+  "Non-Fossil - Non-Electric" = "#6d597a",
+  "Fossil        - Electric" = "#474973",
+  "Fossil        - Non-Electric" = "#161b33"
 )
@@
   geom_vline(xintercept=2020, color = "black", linetype="dashed", linewidth=1, alpha = 0.5) +
-  theme_doubleColumn() +
   scale_fill_manual(values = plotColor, guide = guide_legend(nrow = 6)) +
-  #ggtitle("(b) per fossil content") +
-  theme(legend.margin=margin(l = -1, unit='cm')) +
   scale_x_continuous(breaks=c(2010, 2010, 2020,2030,2040,2050)) + 
-  theme(axis.title.x=element_blank()) +
-  theme(axis.title.y=element_blank()) +
-  theme(legend.title = element_blank()) +
-  theme(legend.text = element_text(size = theme.double.text.size*0.8),
-        #legend.key.height = unit(0.7, "cm"),
-        #legend.key.width = unit(0.7,"cm"),
+  labs(title = paste0("(b) Energy and non-energy use\nper fossil content (", unique(plotData$unit), ")")) +
+  theme_doubleColumn() +
+  theme(legend.margin=margin(l = -1, unit='cm'),
+        axis.title.x=element_blank(),
+        axis.title.y=element_blank(),
+        legend.title = element_blank(),
+        #legend.text = element_text(size = geomText.size*0.8),
         legend.spacing.x = unit(0.2, 'cm'),
-        plot.title = element_text(hjust=0)) + 
-  #  theme(plot.title = element_text(size = 1.2*theme.double.text.size)) +
-  labs(title = paste0("(b) Energy and non-energy use\nper fossil content (", unique(plotData$unit), ")")) +
-  theme(plot.title = element_text(hjust=0)) +
-  theme(plot.margin=margin(t=10, b = 48)) #t, r, b, l
-
-# ggsave(paste0(outChartsFolder,"/svg/Supplementary Figure 4b.
-Final energy demand per fossil content.svg"), g[["Supplementary Figure 4b.
-Final energy demand per fossil content"]] , device="svg", width = 6, height = 8, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Supplementary Figure 4b.
-Final energy demand per fossil content.png"), g[["Supplementary Figure 4b.
-Final energy demand per fossil content"]] , device="png", width = 6, height = 8, dpi=300, units = "in")
-
-```
-
-<!-- ```{r, echo=FALSE, fig.width=6, fig.height=8} -->
-
-<!-- g[["Supplementary Figure 4b. Final energy demand per fossil content"]] -->
-
-<!-- ``` -->
-<!-- ::: -->
-
-<!-- :::: -->
+        plot.title = element_text(hjust=0),
+        plot.margin=margin(t=10, b = 70)) #t, r, b, l
+
+```
 
@@
 
-#plotData %>% group_by(period) %>% summarize(value = sum(value))
-
 #total
@@
   geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
-  theme_doubleColumn() +
-  #ylab("Final Energy Demand - EJ/yr") + 
-  #ggtitle("(a) per sector and carrier") +
   scale_fill_manual(values = setNames(plotColor[names(vars)],vars), labels = setNames(names(vars), vars)) +
-  #theme(legend.margin=margin(l = -1, unit='cm')) +
   scale_x_continuous(breaks=c(2010, 2010, 2020,2030,2040,2050)) + 
-  theme(axis.title.x=element_blank()) +
-  theme(axis.title.y=element_blank()) +
-  theme(legend.title = element_blank()) +
-  theme(#legend.text = element_text(size = theme.double.text.size*0.7),
-        #legend.key.height = unit(0.7, "cm"),
-        #legend.key.width = unit(0.7,"cm"),
-        legend.spacing.x = unit(0.2, 'cm')) + 
-  #  theme(plot.title = element_text(size = 1.2*theme.double.text.size)) +
   labs(title = expression(paste("Greenhouse gases emissions (Mt ", CO[2],"e/yr)"))) +
-  theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical")
+  theme_doubleColumn() +
+  theme(axis.title.x=element_blank(),
+        axis.title.y=element_blank(),
+        legend.title = element_blank(),
+        legend.spacing.x = unit(0.2, 'cm'),
+        legend.position="right",
+        legend.direction = "vertical",
+        legend.box = "vertical")
 
@@
 
-# 
-#   "Emi|CO2|Energy",
-#   "Emi|CO2|Industrial Processes",
-#   "Emi|CO2|Land-Use Change",
-#   "Emi|GHG|CH4",
-#   "Emi|GHG|N2O",
-#   "Emi|GHG|F-Gases",
-#   "Emi|CO2|non-BECCS CDR")
-# 
-# 
-# Emi|CH4
-# Emi|CH4|Extraction
-# Emi|CH4|Agriculture
-# Emi|CH4|Land-Use Change
-# Emi|CH4|Waste
-# Emi|CH4|Energy Supply
-# Emi|N2O
-# Emi|N2O|Agriculture
-# Emi|N2O|Land-Use Change
-# Emi|N2O|Waste
-# Emi|N2O|Transport
-# Emi|N2O|Industry
-# Emi|N2O|Energy Supply
-# Emi|GHG|F-Gases
-
-# Emi|CO2
-# Emi|CO2|Land-Use Change
-# Emi|CO2|Industrial Processes
-# Emi|CO2|Energy|Demand|Transport
-# Emi|CO2|Energy|Demand|Industry
-# Emi|CO2|Energy|Demand|Buildings
-# Emi|CO2|Energy|Supply|Non-electric
-# Emi|CO2|Energy|Supply|Electricity w/ couple prod
-# Emi|CO2|CDR|DACCS
-# Emi|CO2|CDR|EW
-# Emi|CO2|Energy|Waste
-
 ```
@@
 ### Supplementary figure 8. EU-27 CDR
-
-<!-- :::: {style="display: flex;"} -->
-
-<!-- ::: {} -->
 
@@
   min(
-    df_beforeFilter %>%
+    df %>%
       filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen, variable %in% vars) %>% pull(value)),
   max(
-    df_beforeFilter %>%
+    df %>%
       filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen, variable %in% vars) %>% pull(value)
@@
 
-#df_beforeFilter %>%
+#df %>%
 #    filter(region == "EU27", period == 2040, scenario == mainScen, variable %in% vars) %>% pull(value)
@@
   scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) +
-  theme_doubleColumn() +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  #guides(fill = guide_legend(nrow = 2, byrow = T)) +
-  #theme(legend.text=element_text(size=theme.single.text.size)) +
-  theme(legend.key.width = unit(2,"cm")) +
-  theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical") + 
-  #theme(legend.key.width = unit(2,"cm")) +
-  theme(legend.spacing.y = unit(0.5, "lines")) +
-  theme(legend.position="none") +
   expand_limits(y=limitsBECCS) +
   labs(title = expression(paste("(a) BECCS (Mt ", CO[2],"/yr)"))) +
-  theme(plot.title = element_text(hjust=-0.1))
-
-#  theme(legend.position="right", legend.direction = "vertical")
-
-# ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 7 - Carbon-dioxide removal - (a) Bioenergy with Carbon Capture and Storage - BECCS.svg"), g[["BECCS"]] , device="svg", width = 4, height = 6, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Supplementary figure 7 - Carbon-dioxide removal - (a) Bioenergy with Carbon Capture and Storage - BECCS.png"), g[["BECCS"]] , device="png", width = 4, height = 6, dpi=300, units = "in")
-
-```
-
-<!-- ```{r, echo=FALSE, fig.width=4, fig.height=6} -->
-
-<!-- g[["BECCS"]] -->
-
-<!-- ``` -->
-
-<!-- ::: -->
-
-<!-- ::: {} -->
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank(),
+        strip.text.y = element_blank(),
+        legend.key.width = unit(2,"cm"),
+        legend.direction = "vertical", 
+        legend.box = "vertical",
+        legend.spacing.y = unit(0.5, "lines"),
+        legend.position="none",
+        plot.title = element_text(hjust=-0.1))
+
+```
 
@@
 ```{r supplChart_figure8b, echo=FALSE, include=FALSE}
-
-#"Emi|CO2|CDR|BECCS","Emi|CO2|CDR|DACCS","Emi|CO2|CDR|Industry CCS|Synthetic Fuels"
 
@@
 
-plotData <- df_beforeFilter %>%
+plotData <- df %>%
   filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars)
 
-limitsDAC <- df_beforeFilter %>%
+limitsDAC <- df %>%
   filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
@@
   scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 6))) +
-  theme_doubleColumn() +
-  theme(axis.title.y=element_blank()) +
-  theme(strip.text.y = element_blank()) +
-  #guides(fill = guide_legend(nrow = 2, byrow = T)) +
-  #theme(legend.text=element_text(size=theme.single.text.size)) +
-  theme(legend.key.width = unit(2,"cm")) +
-  theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical") + 
-  #theme(legend.key.width = unit(2,"cm")) +
-  theme(legend.spacing.y = unit(0.3, "lines")) +
   expand_limits(y=limY) +
   labs(title = expression(paste("(b) Direct Air Capture (Mt ", CO[2],"/yr)"))) +
-  theme(plot.title = element_text(hjust=-0.1))
-
-#  theme(legend.position="right", legend.direction = "vertical")
-
-# ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 7 - Carbon-dioxide removal - (b) Direct Air Capture.svg"), g[["DAC"]] , device="svg", width = 8, height = 6, dpi=100, units = "in")
-# ggsave(paste0(outChartsFolder,"/png/Supplementary figure 7 - Carbon-dioxide removal - (b) Direct Air Capture.png"), g[["DAC"]] , device="png", width = 8, height = 6, dpi=300, units = "in")
-
-```
-
-<!-- ```{r, echo=FALSE, fig.width=8, fig.height=6} -->
-
-<!-- g[["DAC"]] -->
-
-<!-- ``` -->
-
-<!-- ::: -->
-
-<!-- :::: -->
+  theme_doubleColumn() +
+  theme(axis.title.y=element_blank(),
+        strip.text.y = element_blank(),
+        legend.key.width = unit(2,"cm"),
+        legend.position="right", legend.direction = "vertical", legend.box = "vertical",
+        legend.spacing.y = unit(0.3, "lines"),
+        plot.title = element_text(hjust=-0.1))
+
+```
 

### 2025-04-24 R/aesthetics.R

@@ -197,37 +197,7 @@ text_size <- 20 #15
 
 theme.single.text.size = text_size
 geom.text.single.size = theme.single.text.size/.pt
-
 defaultText_singleColumn <- theme_minimal(base_size = text_size*2)[["text"]] 
-
-#themes
-theme_singleColumn <- function(){
-  theme_minimal(base_size = text_size*2) +
-    theme(
-      legend.position="bottom",
-      legend.title = element_blank(),
-      axis.title.x=element_blank(),
-      axis.ticks.x=element_blank(),
-      axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
-      #axis.text = element_text(size = 1.25*theme.single.text.size),
-      #axis.text.x = element_text(size = theme.single.text.size, angle = 90, hjust = 1, vjust = 0.5),
-      #axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 10)),
-      legend.key.height = unit(0.7, "cm"),
-      legend.key.width = unit(0.7,"cm"),
-      legend.spacing.y = unit(0.1, 'cm'),
-      panel.background = element_rect(fill="#FFFFFF", color = NA),
-      plot.background = element_rect(fill="#FFFFFF", color = NA)#,
-      #strip.text.x = element_text(size = textSize.double)
-      #panel.spacing = unit(3, "lines"),
-      #plot.title = element_text(size = 0.75*theme.single.text.size, face = "plain"),
-      #strip.text.x = element_text(size = 1.25*theme.single.text.size)
-    )
-}
-
-#theme.double.text.size = 15
-#geom.text.double.size = theme.double.text.size/.pt
-#defaultText_doubleColumn <- theme_minimal(base_size = 25)[["text"]] 
-
 textSize.double = text_size
 geomText.size = textSize.double/.pt
 
@@ -239,23 +209,13 @@ theme_doubleColumn <- function(){
       legend.title = element_blank(),
       axis.title.x=element_blank(),
       axis.ticks.x=element_blank(),
-      #axis.text.x = element_text(size = 15,angle = 90, hjust = 1, vjust = 0.5),
       axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
       axis.title.y=element_blank(),
-      #axis.text.y = element_text(size = 15),
-      #axis.text = element_text(size = theme.double.text.size),
-      #legend.text=element_text(size= theme.double.text.size),
[…]

### 2025-04-24 R/preprocess.R

@@ -17,9 +17,6 @@ source("./R/loadReferenceEmissions.R")
 
 #harmonizing data (scale emissions to match historical values)
 source("./R/harmonizeData.R")
-df_beforeFilter <- df
-df <- df %>%
-  filter(!grepl("limVRE", scenario)) # filter VRE scenario out of main charts
 
 #loading efficiency targets
 source("./R/efficiencyTarget.R")

### 2025-04-24 publish/sensitivity_explorer/charts/beccs.js

@@ -9032,32 +9032,32 @@
   },
   "source": "A",
   "attrs": {
-    "60741bf01670": {
+    "567c5a9ec13": {
       "yintercept": {},
       "type": "scatter"
     },
-    "60746ff35993": {
+    "567c47547a09": {
       "xintercept": {}
     },
-    "607443e751ec": {
+    "567c14e236bb": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "607442dc50af": {
+    "567c57ac1eca": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     }
   },
-  "cur_data": "60741bf01670",
+  "cur_data": "567c5a9ec13",
   "visdat": {
-    "60741bf01670": ["function (y) ", "x"],
-    "60746ff35993": ["function (y) ", "x"],
-    "607443e751ec": ["function (y) ", "x"],
-    "607442dc50af": ["function (y) ", "x"]
+    "567c5a9ec13": ["function (y) ", "x"],
+    "567c47547a09": ["function (y) ", "x"],
+    "567c14e236bb": ["function (y) ", "x"],
+    "567c57ac1eca": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-24 publish/sensitivity_explorer/charts/carbonPrice.js

@@ -9050,37 +9050,37 @@
   },
   "source": "A",
   "attrs": {
-    "607430ef17ca": {
+    "567c252f4b1": {
       "yintercept": {},
       "type": "scatter"
     },
-    "607435ce7256": {
+    "567ce0e7df6": {
       "xintercept": {}
     },
-    "6074525a9ca": {
+    "567c179172ed": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "607441ecc10": {
+    "567c54bc37d1": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     },
-    "60744e875fcb": {
+    "567c63c84c68": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "607430ef17ca",
+  "cur_data": "567c252f4b1",
   "visdat": {
-    "607430ef17ca": ["function (y) ", "x"],
-    "607435ce7256": ["function (y) ", "x"],
-    "6074525a9ca": ["function (y) ", "x"],
-    "607441ecc10": ["function (y) ", "x"],
-    "60744e875fcb": ["function (y) ", "x"]
+    "567c252f4b1": ["function (y) ", "x"],
+    "567ce0e7df6": ["function (y) ", "x"],
+    "567c179172ed": ["function (y) ", "x"],
+    "567c54bc37d1": ["function (y) ", "x"],
+    "567c63c84c68": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-24 publish/sensitivity_explorer/charts/dac.js

@@ -9032,32 +9032,32 @@
   },
   "source": "A",
   "attrs": {
-    "607462073b31": {
+    "567c475446f7": {
       "yintercept": {},
       "type": "scatter"
     },
-    "6074200c3028": {
+    "567c37dd2f9b": {
       "xintercept": {}
     },
-    "60747e131afa": {
+    "567c36452442": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "6074538f7e0a": {
+    "567c1ec4697": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     }
   },
-  "cur_data": "607462073b31",
+  "cur_data": "567c475446f7",
   "visdat": {
-    "607462073b31": ["function (y) ", "x"],
-    "6074200c3028": ["function (y) ", "x"],
-    "60747e131afa": ["function (y) ", "x"],
-    "6074538f7e0a": ["function (y) ", "x"]
+    "567c475446f7": ["function (y) ", "x"],
+    "567c37dd2f9b": ["function (y) ", "x"],
+    "567c36452442": ["function (y) ", "x"],
+    "567c1ec4697": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-24 publish/sensitivity_explorer/charts/electricityShare.js

@@ -35607,9 +35607,9 @@
   ],
   "layout": {
     "margin": {
-      "t": 59.023012836550663,
+      "t": 56.38822668959655,
       "r": 13.283520132835198,
-      "b": 70.918405115504584,
+      "b": 68.283618968550471,
       "l": 62.432544624325438
     },
     "plot_bgcolor": "rgba(255,255,255,1)",
@@ -35617,7 +35617,7 @@
     "font": {
       "color": "rgba(0,0,0,1)",
       "family": "",
-      "size": 26.567040265670396
+      "size": 26.567040265670411
     },
     "xaxis": {
       "domain": [0, 0.48627735523467436],
@@ -35633,7 +35633,7 @@
       "nticks": null,
       "ticks": "",
       "tickcolor": null,
-      "ticklen": 6.6417600664175991,
+      "ticklen": 6.6417600664176026,
       "tickwidth": 0,
       "showticklabels": true,
       "tickfont": {
@@ -35654,7 +35654,7 @@
       "hoverformat": ".2f"
     },
     "yaxis": {
-      "domain": [0.55847147688268317, 1],
+      "domain": [0.55139457194251718, 1],
       "automargin": true,
       "type": "linear",
       "autorange": false,
@@ -35700,7 +35700,7 @@
         "xref": "paper",
         "x0": 0,
         "x1": 0.48627735523467436,
-        "y0": 0.55847147688268317,
+        "y0": 0.55139457194251718,
         "y1": 1
       },
       {
@@ -35732,7 +35732,7 @@
         "xref": "paper",
         "x0": 0.51372264476532559,
         "x1": 1,
-        "y0": 0.55847147688268317,
+        "y0": 0.55139457194251718,
         "y1": 1
       },
       {
@@ -35765,7 +35765,7 @@
         "x0": 0,
         "x1": 0.48627735523467436,
         "y0": 0,
-        "y1": 0.44152852311731683
+        "y1": 0.44860542805748282
       },
       {
         "type": "rect",
@@ -35781,7 +35781,7 @@
         "x1": 0.48627735523467436,
         "y0": 0,
         "y1": 42.507264425072641,
-        "yanchor": 0.44152852311731683,
+        "yanchor": 0.44860542805748282,
         "ysizemode": "pixel"
       },
       {
@@ -35797,7 +35797,7 @@
         "x0": 0.51372264476532559,
         "x1": 1,
         "y0": 0,
[…]

### 2025-04-24 publish/sensitivity_explorer/charts/emissions.js

@@ -9050,39 +9050,39 @@
   },
   "source": "A",
   "attrs": {
-    "60747aea6d47": {
+    "567c5cc3d23": {
       "yintercept": {},
       "type": "scatter"
     },
-    "6074d95a2c": {
+    "567c768e3565": {
       "xintercept": {}
     },
-    "60742c5e22b9": {
+    "567c1d693d23": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {},
       "text": {}
     },
-    "60741aa47eb2": {
+    "567c5fc229fc": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {},
       "text": {}
     },
-    "60742ed02bf0": {
+    "567c176c40df": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "60747aea6d47",
+  "cur_data": "567c5cc3d23",
   "visdat": {
-    "60747aea6d47": ["function (y) ", "x"],
-    "6074d95a2c": ["function (y) ", "x"],
-    "60742c5e22b9": ["function (y) ", "x"],
-    "60741aa47eb2": ["function (y) ", "x"],
-    "60742ed02bf0": ["function (y) ", "x"]
+    "567c5cc3d23": ["function (y) ", "x"],
+    "567c768e3565": ["function (y) ", "x"],
+    "567c1d693d23": ["function (y) ", "x"],
+    "567c5fc229fc": ["function (y) ", "x"],
+    "567c176c40df": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-24 publish/sensitivity_explorer/charts/finalEnergy.js

@@ -9050,37 +9050,37 @@
   },
   "source": "A",
   "attrs": {
-    "60741d11108a": {
+    "567c114e226e": {
       "yintercept": {},
       "type": "scatter"
     },
-    "60746cb75a06": {
+    "567c5e192ccf": {
       "xintercept": {}
     },
-    "60748d44463": {
+    "567c23464a48": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "60744fba2917": {
+    "567c7cfd2695": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     },
-    "60746b7114fa": {
+    "567c74e67737": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "60741d11108a",
+  "cur_data": "567c114e226e",
   "visdat": {
-    "60741d11108a": ["function (y) ", "x"],
-    "60746cb75a06": ["function (y) ", "x"],
-    "60748d44463": ["function (y) ", "x"],
-    "60744fba2917": ["function (y) ", "x"],
-    "60746b7114fa": ["function (y) ", "x"]
+    "567c114e226e": ["function (y) ", "x"],
+    "567c5e192ccf": ["function (y) ", "x"],
+    "567c23464a48": ["function (y) ", "x"],
+    "567c7cfd2695": ["function (y) ", "x"],
+    "567c74e67737": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-24 publish/sensitivity_explorer/charts/hydrogen.js

@@ -44826,32 +44826,32 @@
   },
   "source": "A",
   "attrs": {
-    "6074a5c44ba": {
+    "567c5e114f13": {
       "yintercept": {},
       "type": "scatter"
     },
-    "607410c17195": {
+    "567c2c3e1b7b": {
       "xintercept": {}
     },
-    "607440e57d27": {
+    "567c5c7d465d": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "60743e0b66c5": {
+    "567c6d024f98": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     }
   },
-  "cur_data": "6074a5c44ba",
+  "cur_data": "567c5e114f13",
   "visdat": {
-    "6074a5c44ba": ["function (y) ", "x"],
-    "607410c17195": ["function (y) ", "x"],
-    "607440e57d27": ["function (y) ", "x"],
-    "60743e0b66c5": ["function (y) ", "x"]
+    "567c5e114f13": ["function (y) ", "x"],
+    "567c2c3e1b7b": ["function (y) ", "x"],
+    "567c5c7d465d": ["function (y) ", "x"],
+    "567c6d024f98": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-04-24 publish/sensitivity_explorer/charts/primaryEnergy.js

@@ -35947,37 +35947,37 @@
   },
   "source": "A",
   "attrs": {
-    "607432af4f05": {
+    "567c34c840a4": {
       "yintercept": {},
       "type": "scatter"
     },
-    "607431175624": {
+    "567c68154a34": {
       "xintercept": {}
     },
-    "607433207e37": {
+    "567c37fd18f5": {
       "x": {},
       "y": {},
       "linetype": {},
       "colour": {}
     },
-    "60746d575cfb": {
+    "567c3789125d": {
       "x": {},
       "y": {},
       "shape": {},
       "fill": {}
     },
-    "607418e71b6b": {
+    "567c67795b13": {
       "x": {},
       "y": {}
     }
   },
-  "cur_data": "607432af4f05",
+  "cur_data": "567c34c840a4",
   "visdat": {
-    "607432af4f05": ["function (y) ", "x"],
-    "607431175624": ["function (y) ", "x"],
-    "607433207e37": ["function (y) ", "x"],
-    "60746d575cfb": ["function (y) ", "x"],
-    "607418e71b6b": ["function (y) ", "x"]
+    "567c34c840a4": ["function (y) ", "x"],
+    "567c68154a34": ["function (y) ", "x"],
+    "567c37fd18f5": ["function (y) ", "x"],
+    "567c3789125d": ["function (y) ", "x"],
+    "567c67795b13": ["function (y) ", "x"]
   },
   "highlight": {
     "on": "plotly_click",

### 2025-05-06 report_additionalCharts.Rmd
general update for charts

@@
     select(scenario, price_2030),
-  by = "scenario") %>%
-  filter(diff >= 0.5 | diff <= -0.5) %>%
+  by = "scenario")
+
+underAchieved2030 <- nonAchieved2030 %>%
+  filter(diff >= 0.5) %>%
   select(scenario, price_2030, tgt2030, tgtAchieved, diff) %>%
   arrange(desc(abs(diff)))
+
+overAchieved2030 <- nonAchieved2030 %>%
+  filter(diff <= 0.5) %>%
+  select(scenario, price_2030, tgt2030, tgtAchieved, diff) %>%
+  arrange(desc(abs(diff)))
+
+rerun <- overAchieved2030 %>% filter(tgtAchieved >= 59.5)
 

### 2025-05-06 report_paperCharts.Rmd
general update for charts

@@
 chemicals_df %>% 
+  kbl() %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+steel_df %>% 
   kbl() %>%
@@
 # Industry Emissions
-vars <- c("Chemicals"="Emi|CO2|Energy|Demand|Industry|Chemicals",
-          "Other Industry"="Emi|CO2|Energy|Demand|Industry|Other Industry",
+vars <- c("Other Industry"="Emi|CO2|Energy|Demand|Industry|Other Industry",
+          "Chemicals - Energy"="Emi|CO2|Energy|Demand|Industry|Chemicals",
+          #"Chemicals - Feedstock"="Emi|CO2|Industrial Processes|Chemicals", 
           "Steel"="Emi|CO2|Energy|Demand|Industry|Steel",
@@
   "Steel" = "#219ebc",
-  "Chemicals" = "#eaac8b",
-  "Other Industry" = "#e56b6f"
+  "Chemicals - Energy" = "#eaac8b",
+  "Chemicals - Feedstock" = "#e56b6f",
+  "Other Industry" = "#b59765"
 )
@@
 
+labels <- c(
+  "55"="55%",
+  "57"="57%",
+  "59"="59%",
+  "reference"="reference", 
+  "EED 2018 Eff"="EED 2018", 
+  "FitFor55 eff"="FitFor55", 
+  "RePowerEU eff"="RePowerEU",
+  "BioLim4"="4 EJ",
+  "BioLim7.5"="7.5 EJ", 
+  "BioLim12"="12 EJ", 
+  "BioLim20"="20 EJ",
+  "default"="default",
+  "limCCS"="limited CCS",
+  "limH2"="limited H2",
+  "limVRE"="limited VRE"
+)
+
 plotData <- df %>%
@@
          value = currencyConversion*value,
-         tgt2030 = factor(tgt2030, levels=c(55,57,59)),
-         efficiency = factor(efficiency, levels=c("reference", "EED 2018 Eff", "FitFor55 eff", "RePowerEU eff")),
-         bioLim = factor(bioLim, levels=c("BioLim4", "BioLim7.5", "BioLim12", "BioLim20")),
-         lim = factor(lim, levels=c("default", "limCCS", "limH2", "limVRE"))
+         tgt2030 = labels[as.character(tgt2030)],
+         efficiency = labels[as.character(efficiency)],
+         bioLim = labels[as.character(bioLim)],
+         lim =  labels[as.character(lim)]
+  ) %>%
+  mutate(tgt2030 = factor(tgt2030, levels=labels[c("55","57","59")]),
+         efficiency = factor(efficiency, levels=labels[c("reference", "EED 2018 Eff", "FitFor55 eff", "RePowerEU eff")]),
+         bioLim = factor(bioLim, levels=labels[c("BioLim4", "BioLim7.5", "BioLim12", "BioLim20")]),
+         lim = factor(lim, levels=labels[c("default", "limCCS", "limH2", "limVRE")])
          )
@@
   geom_line(data=ETS_price,aes(x=Date, y=Price),size=0.5, color = "#000000") +
+  geom_line(data=plotData %>% filter(scenario == mainScen), size = 1.5, color = "black") +
   geom_label_repel(data=ETS_price %>% filter(Date == "2008-09-19"), aes(x=Date, y=Price, label = variable),
@@
   scale_x_date(date_labels = "%Y") +
-  scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1))) +   
-  scale_color_manual(values = c("reference"="#ae0000", "EED 2018 Eff"="#db4646", "FitFor55 eff"="#0090ab", "RePowerEU eff"="#095786"), guide = guide_legend(nrow =2, byrow = F, order = 2, override.aes = list(linewidth = 1.5))) +
-  scale_fill_manual(values = c("BioLim4"="#fedc97", "BioLim7.5"="#b5b682", "BioLim12"="#7c9885", "BioLim20"="#28666e"), guide = guide_legend(nrow =2, byrow = F, override.aes = list(shape = 21, size = 6, colour = "transparent"), order = 3)) +
-  scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 6))) +
+  geom_label_repel(data = data.frame(period=as.Date("02/07/2037",format="%m/%d/%Y"), value= plotData %>% filter(scenario == mainScen) %>% filter(period == "2035-01-01" | period == "2040-01-01") %>% pull(value) %>% sum() / 2, scenario=mainScen), aes(x=period,y=value),
+                     label = "Reference scenario",
+                     nudge_x = 0,
+                     nudge_y = 550,
+                     segment.square = TRUE,
+                     point.padding = 0,
+                     hjust = 1,
+                     direction="y",
+                     size = geomText.size*0.8) +
+  scale_x_date(date_labels = "%Y") +
+  scale_linetype_manual(values = c("55%"="twodash", "57%"="solid", "59%"="dashed"), guide = guide_legend(title="Short-term policy", nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1))) +
+  scale_color_manual(values = c("reference"="#ae0000", "EED 2018"="#db4646", "FitFor55"="#0090ab", "RePowerEU"="#095786"), guide = guide_legend(title="Efficiency target", nrow =2, byrow = F, order = 2, override.aes = list(linewidth = 1.5))) +
+  scale_fill_manual(values = c("4 EJ"="#fedc97", "7.5 EJ"="#b5b682", "12 EJ"="#7c9885", "20 EJ"="#28666e"), guide = guide_legend(title="Biomass availability limited to", nrow =2, byrow = F, override.aes = list(shape = 21, size = 6, colour = "transparent"), order = 3)) +
+  scale_shape_manual(values = c("default"=21,"limited CCS"=22,"limited H2"=23,"limited VRE"=24), guide = guide_legend(title="Technology evolution", nrow =2, byrow = T, order = 4, override.aes = list(size = 6))) +
   labs(title = expression(paste("(a) Carbon price (€/t ", CO[2],")"))) +
-  theme_doubleColumn() +
+  theme_doubleColumn_alt() +
   theme(axis.title.y=element_blank(),
         strip.text.y = element_blank(),
-        legend.key.width = unit(2,"cm"),
+        legend.key.width = unit(1.5,"cm"),
         legend.position="right", 
@@
         legend.box = "vertical",
-        legend.spacing.y = unit(0.2, "lines"))
+        legend.spacing.y = unit(0.2, "lines"),
+        legend.title=element_text(size=text_size*0.8)#,
+        #legend.text=element_text(size=2*geomText.size)
+        ) +
+  scale_y_continuous(breaks = seq(0, 1200, by = 300)) +
+  expand_limits(y=1200)
 
@@
 
- ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 5. EU-27 Electricity generation.svg"), g[["Supplementary figure 5"]] , device="svg", width = 12, height = 10, dpi=100, units = "in")
- ggsave(paste0(outChartsFolder,"/png/Supplementary figure 5. EU-27 Electricity generation.png"), g[["Supplementary figure 5"]] , device="png", width = 12, height = 10, dpi=300, units = "in")
-
-```
-
-```{r, echo=FALSE, fig.width=12, fig.height=10}
+ ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 5. EU-27 Electricity generation.svg"), g[["Supplementary figure 5"]] , device="svg", width = 12, height = 9, dpi=100, units = "in")
+ ggsave(paste0(outChartsFolder,"/png/Supplementary figure 5. EU-27 Electricity generation.png"), g[["Supplementary figure 5"]] , device="png", width = 12, height = 9, dpi=300, units = "in")
+
+```
+
+```{r, echo=FALSE, fig.width=12, fig.height=9}
 

### 2025-05-06 R/aesthetics.R

@@ -219,6 +219,23 @@ theme_doubleColumn <- function(){
     )
 }
 
+theme_doubleColumn_alt <- function(){
+  theme_minimal(base_size = textSize.double) +
+    theme(
+      plot.title = element_text(size=textSize.double),
+      legend.position="bottom",
+      axis.title.x=element_blank(),
+      axis.ticks.x=element_blank(),
+      axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
+      axis.title.y=element_blank(),
+      legend.key.height = unit(0.7, "cm"),
+      legend.key.width = unit(0.7,"cm"),
+      legend.spacing.y = unit(0.1, 'cm'),
+      panel.background = element_rect(fill="#FFFFFF", color = NA),
+      plot.background = element_rect(fill="#FFFFFF", color = NA)#,
+    )
+}
+  
 
 # theme_set(
 #   theme_minimal(base_size = 20) +

### 2025-05-06 R/calcResults.R

@@ -149,8 +149,10 @@ indirect_electrification <- data.frame(
     max_Mtoe = round(max_EJ * EJ2Mtoe,1))
 
 indirect_electrification_detail <- data.frame(
-  indirect_electrification_detail = c("total_H2","total_efuels","buildings_H2","buildings_efuels","transport_H2","transport_efuels","industry_H2","industry_efuels"),
+  indirect_electrification_detail = c("total_H2_2050","total_efuels_2050","total_H2_2040","total_efuels_2040","buildings_H2_2040","buildings_efuels_2040","transport_H2_2040","transport_efuels_2040","industry_H2_2040","industry_efuels_2040"),
   reference_value_EJ=c(
+    round(df %>% filter(region == "EU27", period == 2050, variable %in% c("FE|Hydrogen"), scenario == mainScen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value),1),
+    round(df %>% filter(region == "EU27", period == 2050, variable %in% c("FE|Gases|Hydrogen","FE|Liquids|Hydrogen"), scenario == mainScen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value),1),
     round(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Hydrogen"), scenario == mainScen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value),1),
     round(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Gases|Hydrogen","FE|Liquids|Hydrogen"), scenario == mainScen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value),1),
     round(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Buildings|Hydrogen"), scenario == mainScen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value),1),
@@ -161,6 +163,8 @@ indirect_electrification_detail <- data.frame(
[…]

### 2025-05-06 createReports.R

@@ -21,7 +21,7 @@ rmarkdown::render("./report_plotlyCharts.Rmd", output_file = paste0(outFolder, "
 #rmarkdown::render("./report_plotlyCharts_darkTheme.Rmd", output_file = paste0(outFolder, "/report_plotlyCharts_darkTheme.html"))
 
 # Copy html, js and css files to the Sensitivity Iterative Explorer output folder 
-file.copy(list("./publish/report_sensitivityExplorer/index.html","./publish/report_sensitivityExplorer/script.js","./publish/report_sensitivityExplorer/style.css"), paste0(outFolder, "/report_sensitivityExplorer"), overwrite = TRUE)
+file.copy(list("./publish/sensitivity_explorer/index.html","./publish/sensitivity_explorer/script.js","./publish/sensitivity_explorer/style.css"), paste0(outFolder, "/report_sensitivityExplorer"), overwrite = TRUE)
 
 #Create additional charts
 rmarkdown::render("./report_additionalCharts.Rmd", output_file = paste0(outFolder, "/report_additionalCharts.html"))

### 2025-11-28 report_paperCharts.Rmd

@@
     theme(axis.title.y=element_blank(),
-          plot.title = element_text(margin=margin(b=35)))
+          plot.title = element_text(margin=margin(b=30)))
 
@@
   theme(legend.position = "none",
-        plot.title = element_text(margin=margin(b=35)))
+        plot.title = element_text(margin=margin(b=30)))
 
@@
         legend.margin=margin(t=30),
-        plot.margin = margin(t = 15, unit = "pt"))
+        plot.margin = margin(t = 15, r=10, unit = "pt"),
+        plot.title = element_text(margin=margin(b=20)))
 
@@
                 alpha = factor(period), color = variable)) +
-
   geom_errorbar(data=plotData %>% filter(period == 2040), aes(xmin=xmax-value+min+CCData, xmax=xmax-value+max+CCData), width=4, colour="black", alpha=0.9, linewidth=0.8) +
-
   geom_text(data=plotData %>% filter(period == 1990), aes(y = 2005, label = labels, group = labels, hjust=1, angle = 90), vjust=0.5, hjust=1.1, na.rm=TRUE, size = geomText.size * 0.8, angle = 90, lineheight = 0.8) +
-
-  geom_text(data=plotData %>% filter(period == 2040), aes(x=xmid , y = 2045, label = pct1990), vjust=0.5, hjust=-0.1, na.rm=TRUE, size = geomText.size, angle = 90) +
+  geom_text(data=plotData %>% filter(period == 2040), aes(x=xmid , y = 2045, label = pct1990), vjust=0.5, hjust=-0.1, na.rm=TRUE, size = geomText.size * 0.8, angle = 90) +
   scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) + 
@@
         axis.title.y=element_blank(),
-        plot.margin = margin(t = 15, r = 0, b = 100, l = 0, unit = "pt"),
-        plot.title = element_text(margin=margin(t=0,r=0,b=55,l=0), hjust=1))
+        plot.margin = margin(t = 25, r = 0, b = 60, l = 0, unit = "pt"),
+        plot.title = element_text(margin=margin(t=0,r=0,b=35,l=0), hjust=1))
 
@@
 ggsave(paste0(outChartsFolder,"/png/Figure 1.
-Greenhouse gas emissions for scenarios reaching climate neutrality by 2050.png"), g[["Figure 1"]], device="png", width = 12, height = 14, dpi=300, units = "in")
+Greenhouse gas emissions for scenarios reaching climate neutrality by 2050.png"), g[["Figure 1"]], device="png", width = 12, height = 13, dpi=300, units = "in")
 ggsave(paste0(outChartsFolder,"/svg/Figure 1.
-Greenhouse gas emissions for scenarios reaching climate neutrality by 2050.svg"), g[["Figure 1"]], device="svg", width = 12, height = 14, dpi=100, units = "in")
-
-```
-
-```{r, echo=FALSE, fig.width=12, fig.height=14}
+Greenhouse gas emissions for scenarios reaching climate neutrality by 2050.svg"), g[["Figure 1"]], device="svg", width = 12, height = 13, dpi=100, units = "in")
+
+```
+
+```{r, echo=FALSE, fig.width=12, fig.height=13}
 
@@
         strip.placement = "outside",
-        strip.text.x = element_text(size = textSize.double, hjust = 1, margin=margin(l=0, b=20)),
+        strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20)),
+        #strip.text.x = element_text(size = textSize.double, hjust = 1, margin=margin(l=0, b=20)),
         strip.clip = "off")
@@
         strip.placement = "outside",
-        strip.text.x = element_text(size = textSize.double, hjust = 1, margin=margin(l=-10, b=20)),
+        strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20)),
+        #strip.text.x = element_text(size = textSize.double, hjust = 1, margin=margin(l=-10, b=20)),
         strip.clip = "off")
@@
         strip.placement = "outside",
-        strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=-15, b=20)),
+        strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=0, b=20)),
+        #strip.text.x = element_text(size = textSize.double, hjust = 0, margin=margin(l=-15, b=20)),
         strip.clip = "off")
@@
 g[["Figure 5"]] <- gridExtra::arrangeGrob(
-  g[["milestone"]][["Emissions reductions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone"]][["Final Energy Demand"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone"]][["Renewables Share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone"]][["Direct Electrification"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone"]][["Domestic Hydrogen Production"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone"]][["Electricity Demand"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone"]][["Wind capacity"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone"]][["Solar photovoltaics"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
-  g[["milestone"]][["Novel CDR"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Emissions reductions"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Final Energy Demand"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Renewables Share"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Direct Electrification"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Carbon-free electricity share"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Domestic Hydrogen Production"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Electricity Demand"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Wind capacity"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Solar photovoltaics"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Residual Fossil Emissions"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Carbon Capture and Storage"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)),
+  g[["milestone"]][["Novel CDR"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)),
   ncol = 2
@@
 
+<!-- ```{r, echo=FALSE, include=FALSE} -->
+
+<!-- g[["tmp"]] <- gridExtra::arrangeGrob( -->
+<!--   g[["milestone"]][["Final Energy Demand"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)), -->
+<!--   g[["milestone"]][["Electricity Demand"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)), -->
+<!--   #g[["milestone"]][["Emissions reductions"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)), -->
+<!--   g[["milestone"]][["Direct Electrification"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)), -->
+<!--   g[["milestone"]][["Renewables Share"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)), -->
+<!--   g[["milestone"]][["Wind capacity"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)), -->
+<!--   g[["milestone"]][["Solar photovoltaics"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)), -->
+<!--   #g[["milestone"]][["Carbon-free electricity share"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)), -->
+<!--   g[["milestone"]][["Domestic Hydrogen Production"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)), -->
+<!--   #g[["milestone"]][["Residual Fossil Emissions"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)), -->
+<!--   #g[["milestone"]][["Carbon Capture and Storage"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)), -->
+<!--   g[["milestone"]][["Novel CDR"]], #+ theme(plot.margin=margin(l = 30, r = 10,t = 30)), -->
+<!--   ncol = 2 -->
+<!-- ) -->
+
+<!-- ggsave(paste0(outChartsFolder,"/svg/tmp.svg"), g[["tmp"]] , device="svg", width = 12, height = 10, dpi=100, units = "in") -->
+<!-- ggsave(paste0(outChartsFolder,"/png/tmp.png"), g[["tmp"]] , device="png", width = 12, height = 10, dpi=300, units = "in") -->
+
+<!-- ``` -->
+
 ---
@@
 
-### Supplementary figure 1. VRE sensitivity.
-
-<!-- (a) Wind and Solar generation (TWh) -->
-
-```{r supplChart_figure1a, echo=FALSE}
-
-vars <- c(
-#  "Solar CSP" = "SE|Electricity|Solar|CSP",
-  "Solar PV" = "SE|Electricity|Solar|PV",
-  "Wind Onshore" = "SE|Electricity|Wind|Onshore",
-  "Wind Offshore" = "SE|Electricity|Wind|Offshore")
-
-color <- c(
-  "Solar CSP"     = "#ffcc00",
-  "Solar PV"      = "#ffe600",
-  "Wind Onshore"  = "#193F7F",
-  "Wind Offshore" = "#337fff")
-
-pattern <- c(
-  "default"="none",
-  "limited VRE"="stripe"
-)
-
-plotData <- df %>%
-  filter(region == "EU27", period %in% c(2020,2030,2040,2050), scenario %in% c(mainScen,"Nzero_57_bio7p5_limVRE"), variable %in% vars) %>%
-  mutate(scenName = ifelse(scenario == mainScen, "default", "limited VRE"),
-         value = round(value * EJ2TWh),
-         unit = "TWh")
-
-#plotData %>% filter( period == 2040) %>% group_by(scenario) %>% summarise(value = sum(value))
-#value2040 <- plotData %>% filter( period == 2040) %>% group_by(scenario) %>% summarise(value = sum(value)) %>% pull(value)
-#round((1-(value2040[2]/value2040[1]))*100,2)
-
-barwidth <- 3
-
-g[["Wind and Solar generation"]] <- ggplot() +
-  geom_bar_pattern(data = plotData %>% filter(scenario == mainScen), mapping = aes(x=period - (barwidth + 1)/2,y=value, fill=variable, pattern=scenName), stat='identity', position="stack", width = barwidth) +
-  geom_bar_pattern(data = plotData %>% filter(scenario == "Nzero_57_bio7p5_limVRE"), mapping = aes(x=period + (barwidth + 1)/2,y=value, fill=variable, pattern=scenName), stat='identity', position="stack", width = barwidth, pattern_key_scale_factor = 0.3, pattern_density=0.3, pattern_spacing = 0.03, pattern_colour = "white", pattern_fill = "white", pattern_alpha=0.4) +
-  geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
-  scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(nrow = 1, order = 1, override.aes = list(pattern = "none"))) +
-  scale_pattern_manual(values = pattern, breaks=c("default","limited VRE"), guide = guide_legend(nrow = 2, order = 1)) +
-  scale_x_continuous(breaks=c(2020,2030,2040,2050), minor_breaks = NULL) +
-  labs(title = "(a) Wind and Solar Generation (TWh)") + 
-  theme_doubleColumn() +
-  theme(axis.title.y = element_blank(),
-        legend.margin=margin(t = -0.4, unit='cm'),
-        legend.box = "horizontal", 
-        legend.box.just = "center")
-
-```
-
-(b) Limited VRE target reduction (%)
-
-```{r supplChart_figure1b, echo=FALSE}
-
-# error bars for scenarios with and without limVRE
-
-plotData <- rbind(
-  df %>%
-    filter(!grepl("limVRE", scenario), region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>%
-    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
-    mutate(reduction = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)) ,2),
-           scenName = "without\nlim-VRE") %>%
-    select(-variable) %>%
-  filter(tgt2050 != "Npi") %>%
-  group_by(period) %>%
-  mutate(min = min(reduction),
-        max = max(reduction))
-  ,
-  df %>%
-    filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>%
-    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
-    mutate(reduction = round(1-(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)) ,2),
-           scenName = "with\nlim-VRE") %>%
-    select(-variable) %>%
-  filter(tgt2050 != "Npi") %>%
-  group_by(period) %>%
-  mutate(min = min(reduction),
-        max = max(reduction))
-)
-
-#plotData %>% filter(scenario %in% c(mainScen,"Nzero_57_bio7p5_limVRE"))
-
-g[["limVRE target reduction"]] <- ggplot(plotData, aes(x = scenName, y = reduction, group=scenName)) +
-  geom_errorbar(mapping = aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +
-  geom_boxplot(outlier.shape = NA, width=0.3) +
-  geom_hline(yintercept=1, color = "black", linewidth=2, alpha = 0.5) +
-  scale_y_reverse(breaks=c(1,0.95,0.9,0.85,0.8, 0.75), minor_breaks = NULL, labels = scales::percent) +
-  expand_limits(y=c(1,0.75)) +
-  labs(title = "(b) 2040 target (%)") +
-  theme_doubleColumn() +
-  theme(plot.title = element_text(hjust=1))
-
-```
-
-```{r, echo=FALSE, include=FALSE}
-
-g[["Supplementary figure 1"]] <- gridExtra::arrangeGrob(
-  g[["Wind and Solar generation"]] + theme(plot.margin=margin(t=10)), 
-  g[["limVRE target reduction"]] + theme(plot.margin=margin(l=20, b=10, t=10)), 
-  layout_matrix = rbind(c(1,1,1,2))
-)
-
-ggsave(paste0(outChartsFolder,"/png/Supplementary figure 1. VRE sensitivity..png"), g[["Supplementary figure 1"]], device="png", width = 12, height = 6, dpi=300, units = "in")
-ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 1. VRE sensitivity..svg"), g[["Supplementary figure 1"]], device="svg", width = 12, height = 6, dpi=100, units = "in")
-
-```
-
-```{r, echo=FALSE, fig.width=12, fig.height=6}
-
-grid.newpage()
-grid.draw(g[["Supplementary figure 1"]])
-
-```
-
-Supplementary figure 1.
-VRE sensitivity.
-(a) EU-27 Variable renewable energy capacity: reference scenario vs.
-limited VRE sensitivity.
-(b) 2040 emission reduction targets: default paper scenarios vs.
-limited VRE cases.
-
----
-
-### Supplementary figure 2. EU-27 carbon price
-
-```{r supplChart_figure2a_lineplot, echo=FALSE, include=FALSE}
+### Supplementary figure 1. EU-27 carbon price
+
+```{r supplChart_figure1a_lineplot, echo=FALSE, include=FALSE}
 
@@
 
-```{r supplChart_figure2b_boxPlot, echo=FALSE, include=FALSE}
+```{r supplChart_figure1b_boxPlot, echo=FALSE, include=FALSE}
 
@@
 
-g[["Supplementary figure 2"]] <- gridExtra::arrangeGrob(
+g[["Supplementary figure 1"]] <- gridExtra::arrangeGrob(
   g[["Carbon Price - line"]], 
@@
 
-ggsave(paste0(outChartsFolder,"/png/Supplementary figure 2. EU-27 carbon price.png"), g[["Supplementary figure 2"]], device="png", width = 12, height = 10, dpi=300, units = "in")
-ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 2. EU-27 carbon price.svg"), g[["Supplementary figure 2"]], device="svg", width = 12, height = 10, dpi=100, units = "in")
+ggsave(paste0(outChartsFolder,"/png/Supplementary figure 1. EU-27 carbon price.png"), g[["Supplementary figure 1"]], device="png", width = 12, height = 10, dpi=300, units = "in")
+ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 1. EU-27 carbon price.svg"), g[["Supplementary figure 1"]], device="svg", width = 12, height = 10, dpi=100, units = "in")
 
@@
 grid.newpage()
-grid.draw(g[["Supplementary figure 2"]])
-
-```
-
-Supplementary figure 2.
+grid.draw(g[["Supplementary figure 1"]])
+
+```
+Supplementary figure 1.
 EU-27 carbon price.
 Carbon price across all scenarios (a), and variation per sensitivity dimension (b).
-Red cross symbols in (b) represent the results of the reference scenario.
+The black line in (a) and red cross symbols in (b) represent the results of the reference scenario.
 Box-plots in (b) show the range from first to third quartile of the sensitivity scenarios.
@@
 
-### Supplementary figure 3. EU-27 mitigation costs.
+### Supplementary figure 2. EU-27 mitigation costs.
 
@@
 
-```{r supplChart_figure3, echo=FALSE, include=FALSE}
+```{r supplChart_figure2, echo=FALSE, include=FALSE}
 
@@
 
-g[["Supplementary figure 3"]] <- ggplot(plotData, aes(x=period,y=value, fill=variable)) +
+g[["Supplementary figure 2"]] <- ggplot(plotData, aes(x=period,y=value, fill=variable)) +
   geom_bar(stat='identity', position="stack") +
@@
 
-ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 3. EU-27 mitigation costs.svg"), g[["Supplementary figure 3"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
-ggsave(paste0(outChartsFolder,"/png/Supplementary figure 3. EU-27 mitigation costs.png"), g[["Supplementary figure 3"]] , device="png", width = 12, height = 6, dpi=300, units = "in")
+ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 2. EU-27 mitigation costs.svg"), g[["Supplementary figure 2"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
+ggsave(paste0(outChartsFolder,"/png/Supplementary figure 2. EU-27 mitigation costs.png"), g[["Supplementary figure 2"]] , device="png", width = 12, height = 6, dpi=300, units = "in")
 
@@
 
-g[["Supplementary figure 3"]]
-
-```
-Supplementary figure 3. EU-27 mitigation costs. Energy supply investments in the reference scenario.
+g[["Supplementary figure 2"]]
+
+```
+Supplementary figure 2. EU-27 mitigation costs. Energy supply investments in the reference scenario.
 
@@
 
-### Supplementary figure 4. EU-27 Electricity capacity
-
-```{r supplChart_figure4, echo=FALSE, include=FALSE}
+### Supplementary figure 3. EU-27 Electricity capacity
+
+```{r supplChart_figure3, echo=FALSE, include=FALSE}
 
@@
 
-g[["Supplementary figure 4"]] <- gridExtra::arrangeGrob(
+g[["Supplementary figure 3"]] <- gridExtra::arrangeGrob(
   tg,
@@
 
- ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 4. EU-27 Electricity capacity.svg"), g[["Supplementary figure 4"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
- ggsave(paste0(outChartsFolder,"/png/Supplementary figure 4. EU-27 Electricity capacity.png"), g[["Supplementary figure 4"]] , device="png", width = 12, height = 6, dpi=300, units = "in")
+ ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 3. EU-27 Electricity capacity.svg"), g[["Supplementary figure 3"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
+ ggsave(paste0(outChartsFolder,"/png/Supplementary figure 3. EU-27 Electricity capacity.png"), g[["Supplementary figure 3"]] , device="png", width = 12, height = 6, dpi=300, units = "in")
 
@@
 grid.newpage()
-grid.draw(g[["Supplementary figure 4"]])
-
-```
-
-Supplementary figure 4. EU-27 Electricity capacity. EU-27, Germany, and France electricity capacity (GW)  in the reference scenario.
-
-### Supplementary figure 5. EU-27 Electricity generation
-
-```{r supplChart_figure5, echo=FALSE, include=FALSE}
+grid.draw(g[["Supplementary figure 3"]])
+
+```
+
+Supplementary figure 3. EU-27 Electricity capacity. EU-27, Germany, and France electricity capacity (GW)  in the reference scenario.
+
+### Supplementary figure 4. EU-27 Electricity generation
+
+```{r supplChart_figure4, echo=FALSE, include=FALSE}
 
@@
 
-g[["Supplementary figure 5"]] <- gridExtra::arrangeGrob(
+g[["Supplementary figure 4"]] <- gridExtra::arrangeGrob(
   tg,
@@
                         rep(14,18),
+                        rep(14,18),
                         rep(14,18))
@@
 
- ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 5. EU-27 Electricity generation.svg"), g[["Supplementary figure 5"]] , device="svg", width = 12, height = 9, dpi=100, units = "in")
- ggsave(paste0(outChartsFolder,"/png/Supplementary figure 5. EU-27 Electricity generation.png"), g[["Supplementary figure 5"]] , device="png", width = 12, height = 9, dpi=300, units = "in")
+ ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 4. EU-27 Electricity generation.svg"), g[["Supplementary figure 4"]] , device="svg", width = 12, height = 9, dpi=100, units = "in")
+ ggsave(paste0(outChartsFolder,"/png/Supplementary figure 4. EU-27 Electricity generation.png"), g[["Supplementary figure 4"]] , device="png", width = 12, height = 9, dpi=300, units = "in")
 
@@
 grid.newpage()
-grid.draw(g[["Supplementary figure 5"]])
-
-```
-
-Supplementary figure 5.
+grid.draw(g[["Supplementary figure 4"]])
+
+```
+
+Supplementary figure 4.
 EU-27 Electricity generation.
@@
 
-### Supplementary figure 6. EU-27 Emissions
+### Supplementary figure 5. EU-27 Emissions
 
@@
 
-```{r supplChart_figure6a, echo=FALSE, include=FALSE}
+```{r supplChart_figure5a, echo=FALSE, include=FALSE}
 
@@
 
-g[["Supplementary Figure 6a. Final energy demand per sector and carrier"]] <- ggplot(plotData,aes(x=period,y=value)) +
+g[["Supplementary Figure 5a. Final energy demand per sector and carrier"]] <- ggplot(plotData,aes(x=period,y=value)) +
   geom_area_pattern(data=plotData,aes(fill=label,pattern=sector, pattern_angle = sector), pattern_key_scale_factor = 1, pattern_density=0.1, pattern_spacing = 0.015, pattern_colour = "white", pattern_fill = "white", pattern_alpha=0.4) +   geom_line(data=totalData, linewidth = 1, color="black") +
@@
 
-```{r supplChart_figure6b, echo=FALSE, include=FALSE}
+```{r supplChart_figure5b, echo=FALSE, include=FALSE}
 
@@
 
-g[["Supplementary figure 6b. Final energy demand per fossil content"]] <- ggplot(plotData,aes(x=period,y=value)) +
+g[["Supplementary figure 5b. Final energy demand per fossil content"]] <- ggplot(plotData,aes(x=period,y=value)) +
   geom_area(aes(fill=label), alpha = 0.8) +
@@
 
-g[["Supplementary figure 6"]] <- gridExtra::arrangeGrob(
-  g[["Supplementary Figure 6a. Final energy demand per sector and carrier"]], 
-  g[["Supplementary figure 6b. Final energy demand per fossil content"]], 
+g[["Supplementary figure 5"]] <- gridExtra::arrangeGrob(
+  g[["Supplementary Figure 5a. Final energy demand per sector and carrier"]], 
+  g[["Supplementary figure 5b. Final energy demand per fossil content"]], 
   layout_matrix = rbind(
@@
 
-ggsave(paste0(outChartsFolder,"/png/Supplementary figure 6. EU-27 Emissions.png"), g[["Supplementary figure 6"]], device="png", width = 12, height = 9, dpi=300, units = "in")
-ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 6. EU-27 Emissions.svg"), g[["Supplementary figure 6"]], device="svg", width = 12, height = 9, dpi=100, units = "in")
+ggsave(paste0(outChartsFolder,"/png/Supplementary figure 5. EU-27 Emissions.png"), g[["Supplementary figure 5"]], device="png", width = 12, height = 9, dpi=300, units = "in")
+ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 5. EU-27 Emissions.svg"), g[["Supplementary figure 5"]], device="svg", width = 12, height = 9, dpi=100, units = "in")
 
@@
 grid.newpage()
-grid.draw(g[["Supplementary figure 6"]])
-
-```
-Supplementary figure 6. EU-27 Emissions. Energy and non-energy use in the reference scenario (a) per sector and carrier and (b) per fossil content.
+grid.draw(g[["Supplementary figure 5"]])
+
+```
+Supplementary figure 5. EU-27 Emissions. Energy and non-energy use in the reference scenario (a) per sector and carrier and (b) per fossil content.
 
@@
 
-### Supplementary figure 7. EU-27 GHG gases
-
-```{r supplChart_figure7, echo=FALSE, include=FALSE}
+### Supplementary figure 6. EU-27 GHG gases
+
+```{r supplChart_figure6, echo=FALSE, include=FALSE}
 
@@
 
-g[["Supplementary figure 7"]] <- ggplot(plotData,aes(x=period,y=value)) +
+g[["Supplementary figure 6"]] <- ggplot(plotData,aes(x=period,y=value)) +
   geom_area(aes(fill=variable), alpha = 0.8) +
@@
 
-ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 7. EU-27 GHG gases.svg"), g[["Supplementary figure 7"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
-ggsave(paste0(outChartsFolder,"/png/Supplementary figure 7. EU-27 GHG gases.png"), g[["Supplementary figure 7"]] , device="png", width = 12, height = 6, dpi=300, units = "in")
+ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 6. EU-27 GHG gases.svg"), g[["Supplementary figure 6"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
+ggsave(paste0(outChartsFolder,"/png/Supplementary figure 6. EU-27 GHG gases.png"), g[["Supplementary figure 6"]] , device="png", width = 12, height = 6, dpi=300, units = "in")
 
@@
 
-g[["Supplementary figure 7"]]
-
-```
-
-Supplementary figure 7. EU-27 GHG gases. Emissions by gas in the reference scenario (CO2eq).
+g[["Supplementary figure 6"]]
+
+```
+
+Supplementary figure 6. EU-27 GHG gases. Emissions by gas in the reference scenario (CO2eq).
 
@@
 
-### Supplementary figure 8. EU-27 CDR
+### Supplementary figure 7. EU-27 CDR
 
@@
 
-```{r supplChart_figure8a, echo=FALSE, include=FALSE}
+```{r supplChart_figure7a, echo=FALSE, include=FALSE}
 
@@
 
-```{r supplChart_figure8b, echo=FALSE, include=FALSE}
+```{r supplChart_figure7b, echo=FALSE, include=FALSE}
 
@@
 
-g[["Supplementary figure 8"]] <- gridExtra::arrangeGrob(
+g[["Supplementary figure 7"]] <- gridExtra::arrangeGrob(
   g[["BECCS"]], 
@@
 
-ggsave(paste0(outChartsFolder,"/png/Supplementary figure 8. EU-27 CDR.png"), g[["Supplementary figure 8"]], device="png", width = 12, height = 6, dpi=300, units = "in")
-ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 8. EU-27 CDR.svg"), g[["Supplementary figure 8"]], device="svg", width = 12, height = 6, dpi=100, units = "in")
+ggsave(paste0(outChartsFolder,"/png/Supplementary figure 7. EU-27 CDR.png"), g[["Supplementary figure 7"]], device="png", width = 12, height = 6, dpi=300, units = "in")
+ggsave(paste0(outChartsFolder,"/svg/Supplementary figure 7. EU-27 CDR.svg"), g[["Supplementary figure 7"]], device="svg", width = 12, height = 6, dpi=100, units = "in")
 
@@
 grid.newpage()
-grid.draw(g[["Supplementary figure 8"]])
-
-```
-
-Supplementary figure 8. EU-27 CDR. CDR deployment: (a) BECCS and (b) DACCS.
+grid.draw(g[["Supplementary figure 7"]])
+
+```
+
+Supplementary figure 7. EU-27 CDR. CDR deployment: (a) BECCS and (b) DACCS.

### 2025-11-28 report_plotlyCharts.Rmd

@@
 
-# df_beforeFilter <- df_beforeFilter %>%
-#   filter(tgt2030 != 59)
-# df <- df %>%
-#   filter(tgt2030 != 59)
-
 ```
@@
 
-  plotData <- df_beforeFilter %>%
+  plotData <- df %>%
     filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
@@
 
-  plotData <- df_beforeFilter %>% 
+  plotData <- df %>% 
     filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen) %>%
@@
 
-  plotData <- df_beforeFilter %>% 
+  plotData <- df %>% 
     filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable == "FE|w/o Non-energy Use w/o Bunkers") %>%
@@
 
-  plotData <- df_beforeFilter %>% 
+  plotData <- df %>% 
     filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>%
@@
 
-  plotData <- df_beforeFilter %>% 
+  plotData <- df %>% 
     filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
@@
 
-<!--   plotData <- df_beforeFilter %>%  -->
+<!--   plotData <- df %>%  -->
 <!--     filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>% -->
@@
 <!-- #  -->
-<!-- # plotData <- df_beforeFilter %>%  -->
+<!-- # plotData <- df %>%  -->
 <!-- #   filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable %in% vars) %>% -->
